### 2022-10-04 code/process.Rmd
start pipeline, check for intercoder agreement

---
title: "Preliminary stuff"
output: html_document
date: "2022-10-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(tidyverse)
```

# Pull data

```{r}
library(googledrive)

f <- googledrive::as_dribble("https://docs.google.com/spreadsheets/d/1UT6KLRujn6iEQ_s01_4yNfFYqc7hAWTpB-t9mdDp0O8/edit#gid=0")
googledrive::drive_download(f, path="raw_data.xlsx", overwrite=T)
d <- readxl::read_xlsx("raw_data.xlsx", skip=2)

```

# Correlation between replication scores

```{r}
d_corr <- d |> filter(!status %in% c("missing", "non-experiment")) |> 
  mutate(replicated_instructor_code=as.numeric(replicated_instructor_code)) |> #forcibly convert the ?s to NAs
  filter(!is.na(replicated_instructor_code) & !is.na(replicated_report_code))
corr <- cor.test(d_corr$replicated_instructor_code, d_corr$replicated_report_code, method = 'spearman')

d_corr |> filter(replicated_instructor_code!=replicated_report_code) |> nrow()
d_corr |> filter(replicated_instructor_code==replicated_report_code) |> nrow()

ggplot(d_corr |> filter(replicated_instructor_code!=replicated_report_code), aes(x=replicated_instructor_code, y=replicated_report_code))+geom_jitter(width=.04, height=.04)+theme_bw()

d_corr |>
  group_by(replicated_instructor_code, replicated_report_code ) |> tally() |> arrange(replicated_report_code) |> 
  pivot_wider(names_from=replicated_report_code, values_from=n, values_fill=0)
```

# Are the ES's okay?

```{r}
library(metafor)

fill_es <- function(type, value, n){
  if (is.na(type)) {
    return(NA)}
  if (is.na(value)) {
    return(NA)
  }
  if (type=="partial eta sq"){
    d = sqrt( (n-1)/n * abs(value)/(1-abs(value)))
    if (value < 0) {
      return(-d)}
    return(d)
    }
  if (type %in% c("d", "SMD")){
    return(value)
  }
  return(NA)
}

d_es <-  d |> filter(!status %in% c("missing", "non-experiment")) |> 
  rowwise() |> 
  mutate(d_calc_target=fill_es(target_ES_type, target_ES_value, target_N)) |> 
  mutate(d_calc_rep=fill_es(replication_ES_type, replication_ES_value, replication_N)) |> 
  select(target_ES_type, target_ES_value,d_calc_target, replication_ES_type, replication_ES_value, d_calc_rep)

```

### 2022-11-14 code/process.Rmd
check for variable codeability

@@
 ```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE, warning=F, message=F)
+knitr::opts_chunk$set(dev = "png", dev.args = list(type = "cairo-png"))
+options(knitr.table.format = "html")
 knitr::opts_chunk$set(echo = F)
 library(tidyverse)
+library(viridis)
+theme_set(theme_bw())
 ```
+
+# TODOs
+ - will need count of studies excluded for 
+ reproducibility / non-exp / missing
+ - Fill in ES conversion for non d/SMD/partial eta (and check for correct conversion of those)
+ - check & fill on_turk columns
 
@@
 
-```{r}
+```{r, eval=F}
 library(googledrive)
@@
 googledrive::drive_download(f, path="raw_data.xlsx", overwrite=T)
-d <- readxl::read_xlsx("raw_data.xlsx", skip=2)
+
+```
+
+```{r}
+d <- readxl::read_xlsx("raw_data.xlsx", sheet="aligned data", skip=2) |> 
+  select(target_lastauthor_year, status, academic_year, subfield, stanford_internal, 
+         open_data, open_materials, target_on_turk, replication_on_turk, 
+         within_between, single_vignette, repeated_measure,
+         target_N, target_test, target_pvalue, target_ES_type, target_ES_value,
+         replication_N, replication_test, replication_pvalue, replication_ES_type, replication_ES_value,
+         replicated_instructor_code, replicated_report_code)
 
@@
 
-```{r}
+```{r, message=T}
 d_corr <- d |> filter(!status %in% c("missing", "non-experiment")) |> 
@@
   filter(!is.na(replicated_instructor_code) & !is.na(replicated_report_code))
+
 corr <- cor.test(d_corr$replicated_instructor_code, d_corr$replicated_report_code, method = 'spearman')
 
+message("Num not match")
 d_corr |> filter(replicated_instructor_code!=replicated_report_code) |> nrow()
+
+message("Num match")
 d_corr |> filter(replicated_instructor_code==replicated_report_code) |> nrow()
+
+message("distribution of non-matches")
 
@@
   mutate(d_calc_target=fill_es(target_ES_type, target_ES_value, target_N)) |> 
-  mutate(d_calc_rep=fill_es(replication_ES_type, replication_ES_value, replication_N)) |> 
-  select(target_ES_type, target_ES_value,d_calc_target, replication_ES_type, replication_ES_value, d_calc_rep)
+  mutate(d_calc_rep=fill_es(replication_ES_type, replication_ES_value, replication_N))
 
 ```
+
+# Prelim analysis -- Correlation between ES
+
+There's that one ling paper with ES of 10+...
+
+Might want to just hide that point or something instead...
+
+Could weight by precision or something
+
+```{r}
+
+d_es |> ggplot(aes(x=d_calc_target, y=d_calc_rep, color=as.factor(replicated_report_code)))+
+  geom_point()+
+  #coord_cartesian(xlim=c(0,5), ylim=c(-1,5))+
+  geom_abline(slope=1, intercept=0)+
+  scale_color_viridis(discrete=T, direction=-1)
+
+d_es |> ggplot(aes(x=d_calc_target, y=d_calc_rep, color=as.factor(replicated_report_code)))+
+  geom_point()+
+  coord_cartesian(xlim=c(0,2), ylim=c(-1,3))+
+  geom_abline(slope=1, intercept=0)+
+  geom_hline(yintercept=0)+
+  scale_color_viridis(discrete=T, direction=-1)+
+  labs(color="Replicated?", x="Original SMD", y="Replication SMD")
+```
+
+# code vars for models
+
+NOTE: will need to replace replicated_code with the discussion agreed one!!
+
+## demographics
+
+need to code publication year
+
+```{r}
+# needs publication year
+d_demo <- d_es 
+```
+
+## statistics
+
+? will outliers on ratio_ss cause a problem?
+
+```{r}
+d_stats <- d_es |> 
+  mutate(log_p =log(target_pvalue),
+         log_sample =log(target_N),
+         ratio_ss = replication_N/target_N,
+         change_platform=ifelse(replication_on_turk==target_on_turk,0,1)) |> 
+  #this codes 1 if the original was in person, but replication turk/prolific,
+  # 0 if they were both on turk/prolific or both in-person (rare, but happens a few times)
+  select(replicated_report_code,log_p,log_sample, ratio_ss, change_platform, academic_year, d_calc_target)
+
+summary(d_stats)
+```
+
+## closeness
+
+```{r}
+
+# could do with mutate across, but clearer this way?
+
+d_close <- d_es |> 
+  mutate(open_data=ifelse(open_data=="yes", 1,0),
+         open_mat=ifelse(open_materials=="yes", 1,0),
+         stanford=ifelse(stanford_internal=="yes", 1,0)) |> 
+  select(open_data, open_mat, stanford, replicated_report_code,
+         academic_year)
+
+summary(d_close)
+```
+
+## design
+
+will need to recode mixed designs so they can be binarized
+
+```{r}
+d_design <- d_es |> 
+  mutate(is_within=case_when(
+    within_between=="within" ~ 1,
+    within_between=="between" ~ 0),
+    log_trials=log(repeated_measure),
+    log_sample=log(target_N))|> 
+  select(is_within, single_vignette,log_trials, log_sample, replicated_report_code, academic_year)
+
+summary(d_design)
+```

### 2022-11-15 code/process.Rmd
fix vars, count NAs

@@
 # TODOs
- - will need count of studies excluded for 
- reproducibility / non-exp / missing
  - Fill in ES conversion for non d/SMD/partial eta (and check for correct conversion of those)
- - check & fill on_turk columns
 
@@
 d <- readxl::read_xlsx("raw_data.xlsx", sheet="aligned data", skip=2) |> 
-  select(target_lastauthor_year, status, academic_year, subfield, stanford_internal, 
+  select(target_lastauthor_year, status, academic_year, subfield, target_year, stanford_internal, 
          open_data, open_materials, target_on_turk, replication_on_turk, 
@@
 
+# Exclusions
+
+```{r}
+d |> group_by(status) |> tally()
+```
+
+# How much missing data?
+
+```{r, message=T}
+message("total rows")
+d |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> nrow()
+
+message("number of NAs per column")
+
+d |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> summarize(                                                      across(everything(),~sum(is.na(.)))) |>
+pivot_longer(everything()) |> 
+  arrange(desc(value)) |> 
+  filter(value!=0)
+
+```
+
 # Correlation between replication scores
@@
 ```{r, message=T}
-d_corr <- d |> filter(!status %in% c("missing", "non-experiment")) |> 
+d_corr <- d |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> 
   mutate(replicated_instructor_code=as.numeric(replicated_instructor_code)) |> #forcibly convert the ?s to NAs
@@
 
-d_es <-  d |> filter(!status %in% c("missing", "non-experiment")) |> 
+d_es <-  d |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> 
   rowwise() |> 
@@
 
-need to code publication year
+```{r}
+d_demo <- d_es |> 
+  ungroup() |> 
+  mutate(pub_year= target_year-mean(target_year)) |> 
+  select(target_year, pub_year, subfield, replicated_report_code, academic_year)
 
-```{r}
-# needs publication year
-d_demo <- d_es 
+summary(d_demo)
+d_demo |> group_by(subfield) |> tally()
 ```
@@
 
-will need to recode mixed designs so they can be binarized
-
 ```{r}
@@
     within_between=="within" ~ 1,
+    within_between=="mixed" ~ 1,
     within_between=="between" ~ 0),

### 2022-11-17 code/process.Rmd
add pred interval

@@
 library(viridis)
+library(Replicate)
 theme_set(theme_bw())
@@
 
+est_SE <- function(p,d){
+  z <- -.862+sqrt(abs(.743-2.404*log(p)))
+  SE <- abs(d/z)
+  return(SE)
+}
+
 d_es <-  d |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> 
   rowwise() |> 
-  mutate(d_calc_target=fill_es(target_ES_type, target_ES_value, target_N)) |> 
-  mutate(d_calc_rep=fill_es(replication_ES_type, replication_ES_value, replication_N))
+  mutate(d_calc_target=fill_es(target_ES_type, target_ES_value, target_N),
+         se_calc_target=est_SE(target_pvalue,d_calc_target),
+         d_calc_rep=fill_es(replication_ES_type, replication_ES_value, replication_N),
+         se_calc_rep=est_SE(replication_pvalue,d_calc_rep))
 
+```
+
+```{r}
+
+d_es_try <- d_es |> filter(!is.na(d_calc_target)) |> 
+  filter(!is.na(d_calc_rep)) |> 
+  mutate(
+         predInt=Replicate::pred_int(d_calc_target,se_calc_target**2, d_calc_rep, se_calc_rep**2)$rep.inside,
+         p_orig=Replicate::p_orig(d_calc_target,se_calc_target**2, d_calc_rep, t2=0, se_calc_rep**2))
+
+```
+
+# PredInt and P_orig
+
+```{r}
+
+d_es_try |> ggplot(aes(x=d_calc_target, y=d_calc_rep, color=p_orig))+
+  geom_point()+
+  coord_cartesian(xlim=c(0,2), ylim=c(-1,3))+
+  geom_abline(slope=1, intercept=0)+
+  geom_hline(yintercept=0)+
+  scale_color_viridis(discrete=F, direction=-1)+
+  labs(color="p_orig", x="Original SMD", y="Replication SMD")
+
+d_es_try |> mutate(p_sig=p_orig<.05) |> ggplot(aes(x=d_calc_target, y=d_calc_rep, color=p_sig))+
+  geom_point()+
+  coord_cartesian(xlim=c(0,2), ylim=c(-1,3))+
+  geom_abline(slope=1, intercept=0)+
+  geom_hline(yintercept=0)+
+  scale_color_viridis(discrete=T, direction=-1)+
+  labs(color="P_orig<.05", x="Original SMD", y="Replication SMD")
+
+d_es_try |> ggplot(aes(x=d_calc_target, y=d_calc_rep, color=predInt))+
+  geom_point()+
+  coord_cartesian(xlim=c(0,2), ylim=c(-1,3))+
+  geom_abline(slope=1, intercept=0)+
+  geom_hline(yintercept=0)+
+  scale_color_viridis(discrete=T, direction=-1)+
+  labs(color="rep in predInt", x="Original SMD", y="Replication SMD")
+
+d_es_try |> ggplot(aes(x=replicated_report_code, y=p_orig))+geom_jitter(height=0, alpha=.5)+
+  #scale_y_log10()+
+  geom_hline(yintercept=.05)
+
+d_es_try |> ggplot(aes(x=replicated_report_code, y=predInt))+geom_jitter(alpha=.5)
 ```

### 2022-11-20 code/process.Rmd
work to auto get pvals

@@
 ---
-title: "Preliminary stuff"
-output: html_document
-date: "2022-10-03"
+title: "251 MA"
+output:
+  html_document: 
+    toc: true
 ---
@@
 library(Replicate)
+library(metafor)
 theme_set(theme_bw())
@@
 # TODOs
- - Fill in ES conversion for non d/SMD/partial eta (and check for correct conversion of those)
+- get ES from t test, from F test (using compute es) < -- what does within_one and within_two mean??
+- validate df against num people?
+- what about for other test statistics
 
@@
          within_between, single_vignette, repeated_measure,
-         target_N, target_test, target_pvalue, target_ES_type, target_ES_value,
-         replication_N, replication_test, replication_pvalue, replication_ES_type, replication_ES_value,
+         target_N, target_test, target_raw_stat, target_pvalue, target_ES_type, target_ES_value,
+         replication_N, replication_test, replication_raw_stat, replication_pvalue, replication_ES_type, replication_ES_value,
          replicated_instructor_code, replicated_report_code)
@@
 d |> group_by(status) |> tally()
+```
+# Validation
+
+```{r}
+d_val <- d |> filter(!status %in% c("missing", "non-experiment", "reproduction"))
+
+d_val$academic_year |> unique()
+
+d_val |> filter(!subfield %in% c("social","cognitive","non-psych","other-psych"))
+
+d_val |> filter(!stanford_internal %in% c("no","yes"))
+
+d_val |> filter(!open_data %in% c("no","yes"))
+
+d_val |> filter(!open_materials %in% c("no","yes"))
+
+d_val |> filter(!target_on_turk %in% c("no","yes"))
+
+d_val |> filter(!replication_on_turk %in% c("no","yes"))
+
+d_val |> filter(!within_between %in% c("within","between","mixed"))
+
+d_val |> filter(!single_vignette %in% c(0,1))
+
+```
+# Parsing
+```{r}
+test <- "t(42)=2.41"
+ftest <- "F(1,12)=45.43"
+parse_t <- function(tval) {
+  df=str_extract(tval, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
+  val=str_extract(tval, "=.*") |> str_sub(2,-1) |> as.numeric() |> abs()
+  return(data.frame("df_2"=df,"tstat"=val))
+}
+
+parse_f <- function(fval){
+  df_1 =str_extract(fval, "\\(.*,") |> str_sub(2,-2) |> as.numeric()
+  df_2 =str_extract(fval, ",.*\\)") |> str_sub(2,-2) |> as.numeric()
+  val=str_extract(fval, "=.*") |> str_sub(2,-1) |> as.numeric() |> abs()
+  return(data.frame("df_1"=df_1,"df_2"=df_2,"fstat"=val))
+}
+
+p_from_t <- function(d) {
+  pt(q=d$tstat, df=d$df_2, lower.tail=FALSE)*2 # two tailed
+}
+
+p_from_f <- function(d) {
+  pf(q=d$fstat, df1=d$df_1, df2=d$df_2, lower.tail=FALSE)
+}
+
+parse_t(test) |> p_from_t()
+parse_f(ftest) |> p_from_f()
+
+```
+
+```{r}
+test <-  d_val |> 
+  mutate(target_p_calc=case_when(
+    str_sub(target_raw_stat,1,1)=="t" ~ parse_t(target_raw_stat) |> p_from_t(),
+    str_sub(target_raw_stat,1,1)=="F" ~ parse_f(target_raw_stat) |> p_from_f()),
+    rep_p_calc=case_when(
+    str_sub(replication_raw_stat,1,1)=="t" ~parse_t(replication_raw_stat) %>% p_from_t(),
+    str_sub(replication_raw_stat,1,1)=="F" ~parse_f(replication_raw_stat) |> p_from_f()))
+
+ggplot(test, aes(x=target_pvalue, y=target_p_calc))+geom_point()+geom_abline(slope=1,intercept=0)+
+  scale_x_log10()+scale_y_log10()
+
+ggplot(test, aes(x=replication_pvalue, y=rep_p_calc))+geom_point()+geom_abline(slope=1,intercept=0)+scale_x_log10()+scale_y_log10()
+
 ```

### 2022-11-28 code/process.Rmd
work on computing pvals and ES

--- 2022-11-15 code/process.Rmd
@@
 library(viridis)
+library(Replicate)
+library(metafor)
+library
 theme_set(theme_bw())
@@
 # TODOs
- - Fill in ES conversion for non d/SMD/partial eta (and check for correct conversion of those)
+- why are some ES's  about 2 times bigger than they should be?
+- get ES from t test, from F test (using compute es) < -- what does within_one and within_two mean??
+- validate df against num people?
+- what about for other test statistics (r)
 
@@
 ```{r}
-d <- readxl::read_xlsx("raw_data.xlsx", sheet="aligned data", skip=2) |> 
+d <- readxl::read_xlsx("raw_data.xlsx", sheet="aligned data", skip=1) |>
+
   select(target_lastauthor_year, status, academic_year, subfield, target_year, stanford_internal, 
@@
 d |> group_by(status) |> tally()
+
+d |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> tally()
+```
+# Validation
+
+```{r}
+d_val <- d |> filter(!status %in% c("missing", "non-experiment", "reproduction"))
+
+# d_val$academic_year |> unique()
+# 
+# d_val |> filter(!subfield %in% c("social","cognitive","non-psych","other-psych"))
+# 
+# d_val |> filter(!stanford_internal %in% c("no","yes"))
+# 
+# d_val |> filter(!open_data %in% c("no","yes"))
+# 
+# d_val |> filter(!open_materials %in% c("no","yes"))
+# 
+# d_val |> filter(!target_on_turk %in% c("no","yes"))
+# 
+# d_val |> filter(!replication_on_turk %in% c("no","yes"))
+# 
+# d_val |> filter(!within_between %in% c("within","between","mixed"))
+# 
+# d_val |> filter(!single_vignette %in% c(0,1))
+
+```
+
+# Parsing
+
+We parse out values from (for now) t tests and F tests (other tests to be added later).
+
+```{r}
+# considered using the effectsize package but afaik we don't care about estimating CI's here and there were optim problems with that
+
+parse_t <- function(tval, within_between) {
+  df=str_extract(tval, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
+  val=str_extract(tval, "=.*") |> str_sub(2,-1) |> as.numeric() |> abs()
+  pval=pt(q=val, df=df, lower.tail=FALSE)*2
+  d_calc=NA
+  if(within_between=="between"){
+    d_calc=2*val/(sqrt(df))  # note this uses the 2t/sqrt(df) approximation df+2 might be more appropriate? 
+  }
+  else{d_calc=val/sqrt(df)}
+  return(data.frame("df_1"=NA, "df_2"=df,"tstat"=val, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc))
+}
+
+parse_f <- function(fval, within_between){
+  df_1 =str_extract(fval, "\\(.*,") |> str_sub(2,-2) |> as.numeric()
+  df_2 =str_extract(fval, ",.*\\)") |> str_sub(2,-2) |> as.numeric()
+  val=str_extract(fval, "=.*") |> str_sub(2,-1) |> as.numeric() |> abs()
+  pval=pf(q=val, df1=df_1, df2=df_2, lower.tail=FALSE)
+  d_calc=NA
+  if(!is.na(df_1)&&df_1==1){
+    if(within_between=="between"){
+      d_calc=2*sqrt(val)/sqrt(df_2) # if there's just two groups, then F=t**2 and we can use the t-test thingy
+    }
+    else{
+      d_calc=sqrt(val)/sqrt(df_2)
+    }
+  if(!is.na(df_1)){
+    # we go through partial eta
+    n=df_1+df_2+1 # rederive n b/c it's not always matching the n we have
+    partial_eta=(val*df_1)/(val*df_1+df_2)
+    d_calc=sqrt(n/(n-1)*(partial_eta/(1-partial_eta)))
+  }
+}
+  return(data.frame("df_1"=df_1,"df_2"=df_2,"tstat"=NA, "fstat"=val, "p_calc"=pval, "d_calc"=d_calc))
+}
+
+do_blanks <- function(){
+  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA))
+}
+do_parsing=function(raw_stat, within_between){
+  if (is.na(raw_stat)) {return (do_blanks())}
+  if (str_sub(raw_stat,1,1)=="t"){return(parse_t(raw_stat, within_between))}
+  if (str_sub(raw_stat,1,1)=="F"){return(parse_f(raw_stat, within_between))}
+  return (do_blanks())
+}
+```
+
+```{r}
+test <- d_val |> 
+  mutate(target=map2(target_raw_stat, within_between, do_parsing),
+         rep=map2(replication_raw_stat, within_between, do_parsing)) |> 
+  unnest(cols=c(target, rep), names_sep="_")
+
+```
+
+Comparing calculated p vals to provided (or hand calculated) ones.
+
+```{r}
+
+ggplot(test, aes(x=target_pvalue, y=target_p_calc))+geom_point()+geom_abline(slope=1,intercept=0)+
+  scale_x_log10()+scale_y_log10()
+
+ggplot(test, aes(x=replication_pvalue, y=rep_p_calc))+geom_point()+geom_abline(slope=1,intercept=0)+scale_x_log10()+scale_y_log10()
+
+```
+Comparing calculated ES to original (or hand calculated) ES. All converted to SMD.
+
+Note: black line is y=x, red line is y=2x. Things on y=2x probably had issues where one of the tests calculated it as (within|between) and the other did it the other way.
+
+```{r}
+fill_es <- function(type, value, n){
+  if (is.na(type)) {
+    return(NA)}
+  if (is.na(value)) {
+    return(NA)
+  }
+  if (type=="partial eta sq"){
+    d = sqrt( (n-1)/n * abs(value)/(1-abs(value)))
+    if (value < 0) {
+      return(-d)}
+    return(d)
+    }
+  if (type %in% c("d", "SMD")){
+    return(abs(value))
+  }
+  return(NA)
+}
+
+test |> rowwise() |> mutate(d_fill_target=fill_es(target_ES_type, target_ES_value, target_N))|> 
+  ggplot(aes(x=d_fill_target, y=target_d_calc))+geom_point()+geom_abline(slope=1,intercept=0)+geom_abline(slope=2,intercept=0, color="red")+coord_cartesian(xlim=c(0,5),ylim=c(0,5))
+
+test |> rowwise() |> mutate(d_fill_rep=fill_es(replication_ES_type, replication_ES_value, replication_N))|>
+  ggplot(aes(x=d_fill_rep, y=rep_d_calc))+geom_point()+geom_abline(slope=1,intercept=0)+geom_abline(slope=2,intercept=0, color="red")
+
+```
+
+# Are the ES's okay?
+
+```{r}
+library(metafor)
+
+est_SE <- function(p,d){
+  z <- -.862+sqrt(abs(.743-2.404*log(p)))
+  SE <- abs(d/z)
+  return(SE)
+}
+
+d_es <-  test |> 
+  rowwise() |> 
+  mutate(target_se_calc=est_SE(target_p_calc,target_d_calc),
+         rep_se_calc=est_SE(rep_p_calc,rep_d_calc))
+
+```
+
+```{r}
+
+d_es_try <- d_es |> filter(!is.na(target_d_calc)) |> 
+  filter(!is.na(rep_d_calc)) |> 
+  mutate(
+         predInt=Replicate::pred_int(target_d_calc,target_se_calc**2, rep_d_calc, rep_se_calc**2)$rep.inside,
+         p_orig=Replicate::p_orig(target_d_calc,target_se_calc**2, rep_d_calc, t2=0, rep_se_calc**2))
+
+```
+
+# PredInt and P_orig
+
+```{r}
+
+d_es_try |> ggplot(aes(x=target_d_calc, y=rep_d_calc, color=p_orig))+
+  geom_point()+
+  coord_cartesian(xlim=c(0,2), ylim=c(-1,3))+
+  geom_abline(slope=1, intercept=0)+
+  geom_hline(yintercept=0)+
+  scale_color_viridis(discrete=F, direction=-1)+
+  labs(color="p_orig", x="Original SMD", y="Replication SMD")
+
+d_es_try |> mutate(p_sig=p_orig<.05) |> ggplot(aes(x=target_d_calc, y=rep_d_calc, color=p_sig))+
+  geom_point()+
+  coord_cartesian(xlim=c(0,2), ylim=c(-1,3))+
+  geom_abline(slope=1, intercept=0)+
+  geom_hline(yintercept=0)+
+  scale_color_viridis(discrete=T, direction=-1)+
+  labs(color="P_orig<.05", x="Original SMD", y="Replication SMD")
+
+d_es_try |> ggplot(aes(x=target_d_calc, y=rep_d_calc, color=predInt))+
+  geom_point()+
+  coord_cartesian(xlim=c(0,2), ylim=c(-1,3))+
+  geom_abline(slope=1, intercept=0)+
+  geom_hline(yintercept=0)+
+  scale_color_viridis(discrete=T, direction=-1)+
+  labs(color="rep in predInt", x="Original SMD", y="Replication SMD")
+
+d_es_try |> ggplot(aes(x=replicated_report_code, y=p_orig))+geom_jitter(height=0, alpha=.5)+
+  #scale_y_log10()+
+  geom_hline(yintercept=.05)
+
+d_es_try |> ggplot(aes(x=replicated_report_code, y=predInt))+geom_jitter(alpha=.5)
+```
+
+# Prelim analysis -- Correlation between ES
+
+There's that one ling paper with ES of 10+...
+
+Might want to just hide that point or something instead...
+
+Could weight by precision or something
+
+```{r}
+
+d_es |> ggplot(aes(x=target_d_calc, y=rep_d_calc, color=as.factor(replicated_report_code)))+
+  geom_point()+
+  #coord_cartesian(xlim=c(0,5), ylim=c(-1,5))+
+  geom_abline(slope=1, intercept=0)+
+  scale_color_viridis(discrete=T, direction=-1)
+
+d_es |> ggplot(aes(x=target_d_calc, y=rep_d_calc, color=as.factor(replicated_report_code)))+
+  geom_point()+
+  coord_cartesian(xlim=c(0,2), ylim=c(-1,3))+
+  geom_abline(slope=1, intercept=0)+
+  geom_hline(yintercept=0)+
+  scale_color_viridis(discrete=T, direction=-1)+
+  labs(color="Replicated?", x="Original SMD", y="Replication SMD")
 ```
@@
 
-# Are the ES's okay?
-
-```{r}
-library(metafor)
-
-fill_es <- function(type, value, n){
-  if (is.na(type)) {
-    return(NA)}
-  if (is.na(value)) {
-    return(NA)
-  }
-  if (type=="partial eta sq"){
-    d = sqrt( (n-1)/n * abs(value)/(1-abs(value)))
-    if (value < 0) {
-      return(-d)}
-    return(d)
-    }
-  if (type %in% c("d", "SMD")){
-    return(value)
-  }
-  return(NA)
-}
-
-d_es <-  d |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> 
-  rowwise() |> 
-  mutate(d_calc_target=fill_es(target_ES_type, target_ES_value, target_N)) |> 
-  mutate(d_calc_rep=fill_es(replication_ES_type, replication_ES_value, replication_N))
-
-```
-
-# Prelim analysis -- Correlation between ES
-
-There's that one ling paper with ES of 10+...
-
-Might want to just hide that point or something instead...
-
-Could weight by precision or something
-
-```{r}
-
-d_es |> ggplot(aes(x=d_calc_target, y=d_calc_rep, color=as.factor(replicated_report_code)))+
-  geom_point()+
-  #coord_cartesian(xlim=c(0,5), ylim=c(-1,5))+
-  geom_abline(slope=1, intercept=0)+
-  scale_color_viridis(discrete=T, direction=-1)
-
-d_es |> ggplot(aes(x=d_calc_target, y=d_calc_rep, color=as.factor(replicated_report_code)))+
-  geom_point()+
-  coord_cartesian(xlim=c(0,2), ylim=c(-1,3))+
-  geom_abline(slope=1, intercept=0)+
-  geom_hline(yintercept=0)+
-  scale_color_viridis(discrete=T, direction=-1)+
-  labs(color="Replicated?", x="Original SMD", y="Replication SMD")
-```
-
 # code vars for models
@@
 d_stats <- d_es |> 
-  mutate(log_p =log(target_pvalue),
+  mutate(log_p =log(target_p_calc),
          log_sample =log(target_N),
@@
   # 0 if they were both on turk/prolific or both in-person (rare, but happens a few times)
-  select(replicated_report_code,log_p,log_sample, ratio_ss, change_platform, academic_year, d_calc_target)
+  select(replicated_report_code,log_p,log_sample, ratio_ss, change_platform, academic_year, target_d_calc)
 

### 2022-11-29 code/process.Rmd
more work on ES calculations

@@
 library(metafor)
-library
+library(esc)
 theme_set(theme_bw())
@@
 # TODOs
-- why are some ES's  about 2 times bigger than they should be?
-- get ES from t test, from F test (using compute es) < -- what does within_one and within_two mean??
+- why are some ES's  about 2 times bigger than they should be? (from within v between stuff)
 - validate df against num people?
-- what about for other test statistics (r)
+ - what to do for chisq, other things? for ES
 
@@
          target_N, target_test, target_raw_stat, target_pvalue, target_ES_type, target_ES_value,
+         same_dir,
          replication_N, replication_test, replication_raw_stat, replication_pvalue, replication_ES_type, replication_ES_value,
@@
 
-We parse out values from (for now) t tests and F tests (other tests to be added later).
+We parse out values from (for now) t tests, F tests, and chisq. 
+Other stats to be added later, chisq ES to be added.
 
@@
     }
-  if(!is.na(df_1)){
+  }
+  else if(!is.na(df_1)){
     # we go through partial eta
@@
   }
-}
   return(data.frame("df_1"=df_1,"df_2"=df_2,"tstat"=NA, "fstat"=val, "p_calc"=pval, "d_calc"=d_calc))
 }
+
+parse_chisq <- function(chival, within_between){
+  df=str_extract(chival, "\\(.*,") |> str_sub(2,-2) |> as.numeric()
+  n=str_extract(chival, ",N=.*\\)") |> str_sub(4,-2) |> as.numeric()
+  val=str_extract(chival, "\\)=.*") |> str_sub(3,-1) |> as.numeric() |> abs()
+  print(val)
+  pval=pchisq(val,df, lower.tail=F)
+  phi=sqrt(val/n)
+  d_calc=NA
+  if (!is.na(df)&&df==1){
+    d_calc=esc_phi(phi,pval,n, es.type="d")$es
+  }
+  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc))
+}
+
+#foo = "MCI m1=3.41[3.24,3.55], m2=3.44[3.24,3.57]"
+parse_mean_ci <- function(mci,within_between,n){
+  cond1=str_extract(mci, "m1.*\\],")
+  cond2=str_extract(mci, "m2.*\\]")
+  m1=str_extract(cond1, "m1=.*\\[") |> str_sub(4,-2) |> as.numeric()
+  m2=str_extract(cond2, "m2=.*\\[") |> str_sub(4,-2) |> as.numeric()
+  low1=str_extract(cond1, "\\[.*,.") |> str_sub(2,-3) |> as.numeric()
+  low2=str_extract(cond2, "\\[.*,") |> str_sub(2,-2) |> as.numeric()
+  high1=str_extract(cond1, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
+  high2=str_extract(cond2, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
+  se1=high1-low1/(2*1.96)
+  se2=high2-low2/(2*1.96)
+  se=(se1+se2)/2
+  tval=(m1-m2)/se |> abs()
+  if (within_between=="within"){
+  df=n-1
+  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
+  d_calc=tval/(sqrt(df)) 
+  }
+  else{
+    df=NA
+    pval=NA
+    d_calc=NA
+  }
+  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc))
+}
+
+#parse_mean_ci(foo)
 
@@
 }
-do_parsing=function(raw_stat, within_between){
+do_parsing=function(raw_stat, within_between,n){
   if (is.na(raw_stat)) {return (do_blanks())}
@@
   if (str_sub(raw_stat,1,1)=="F"){return(parse_f(raw_stat, within_between))}
+  if (str_sub(raw_stat,1,1)=="c"){return(parse_chisq(raw_stat, within_between))}
+  if (str_sub(raw_stat, 1,3)=="MCI"){return(parse_mean_ci(raw_stat, within_between,n))}
   return (do_blanks())
@@
 ```
-
-```{r}
-test <- d_val |> 
-  mutate(target=map2(target_raw_stat, within_between, do_parsing),
-         rep=map2(replication_raw_stat, within_between, do_parsing)) |> 
-  unnest(cols=c(target, rep), names_sep="_")
-
-```
-
-Comparing calculated p vals to provided (or hand calculated) ones.
-
-```{r}
-
-ggplot(test, aes(x=target_pvalue, y=target_p_calc))+geom_point()+geom_abline(slope=1,intercept=0)+
-  scale_x_log10()+scale_y_log10()
-
-ggplot(test, aes(x=replication_pvalue, y=rep_p_calc))+geom_point()+geom_abline(slope=1,intercept=0)+scale_x_log10()+scale_y_log10()
-
-```
-Comparing calculated ES to original (or hand calculated) ES. All converted to SMD.
-
-Note: black line is y=x, red line is y=2x. Things on y=2x probably had issues where one of the tests calculated it as (within|between) and the other did it the other way.
 
@@
 
-test |> rowwise() |> mutate(d_fill_target=fill_es(target_ES_type, target_ES_value, target_N))|> 
-  ggplot(aes(x=d_fill_target, y=target_d_calc))+geom_point()+geom_abline(slope=1,intercept=0)+geom_abline(slope=2,intercept=0, color="red")+coord_cartesian(xlim=c(0,5),ylim=c(0,5))
+test <- d_val |> 
+  mutate(target_raw_stat=gsub(" ","",target_raw_stat),
+         target=pmap(list(target_raw_stat, within_between,target_N), do_parsing),
+         replication_raw_stat=gsub(" ","",replication_raw_stat),
+         rep=pmap(list(replication_raw_stat, within_between,replication_N), do_parsing)) |> 
+  unnest(cols=c(target, rep), names_sep="_") |> 
+  rowwise() |> 
+  mutate(d_fill_target=fill_es(target_ES_type, target_ES_value, target_N),
+         d_fill_rep=fill_es(replication_ES_type, replication_ES_value, replication_N))
 
-test |> rowwise() |> mutate(d_fill_rep=fill_es(replication_ES_type, replication_ES_value, replication_N))|>
-  ggplot(aes(x=d_fill_rep, y=rep_d_calc))+geom_point()+geom_abline(slope=1,intercept=0)+geom_abline(slope=2,intercept=0, color="red")
+```
+
+Comparing calculated p vals to provided (or hand calculated) ones. Line is x=y.
+
+These look pretty reasonable. Lots on the line and others is places were <.001's happened.
+
+```{r}
+
+ggplot(test, aes(x=target_pvalue, y=target_p_calc))+geom_point()+geom_abline(slope=1,intercept=0)+
+  scale_x_log10()+scale_y_log10()
+
+ggplot(test, aes(x=replication_pvalue, y=rep_p_calc))+geom_point()+geom_abline(slope=1,intercept=0)+scale_x_log10()+scale_y_log10()
+
+```
+Comparing calculated ES to original (or hand calculated) ES. All converted to SMD.
+
+Note: black line is y=x, red line is y=2x. Things on y=2x probably had issues where one of the tests calculated it as (within|between) and the other did it the other way.
+
+```{r}
+
+test |> 
+  ggplot(aes(x=d_fill_target, y=target_d_calc))+geom_point()+geom_abline(slope=1,intercept=0)+geom_abline(slope=2,intercept=0, color="red")+coord_cartesian(xlim=c(0,5),ylim=c(0,5))+geom_abline(slope=.5,intercept=0, color="red")
+
+test |> 
+  ggplot(aes(x=d_fill_rep, y=rep_d_calc))+geom_point()+geom_abline(slope=1,intercept=0)+geom_abline(slope=2,intercept=0, color="red")+geom_abline(slope=.5,intercept=0, color="red")
+
+```
+
+## what to do with the weirdos
+
+Where there's a difference, I could check whether it's being compared to something *I* calculated versus something that an original paper or students paper calculated?
+Except that there's sources for errors in any of those.
+Ones where we get an off  by two error -- should I double check within-betweeness for the test?
+
+```{r}
+test |> filter(target_d_calc>1.9*d_fill_target)
+test |> filter(target_d_calc<.6*d_fill_target)
+
+test |> filter(rep_d_calc>1.9*d_fill_rep)
+test |> filter(rep_d_calc<.6*d_fill_rep)
+
+```
+
+## what didn't parse
+
+```{r}
+
+test |> filter(is.na(target_d_calc)) |> filter(!is.na(target_raw_stat)) |>  pull(target_raw_stat)
+
+test |> filter(is.na(rep_d_calc)) |> filter(!is.na(replication_raw_stat)) |> pull(replication_raw_stat)
+```
+
+# Where does df not line up?
+Note: it's not *necessarily* a problem if df's don't line up -- there could be some repeated measures or welch's test stuff going on, but nice to check.
+
+```{r}
+
+test
 
@@
   mutate(target_se_calc=est_SE(target_p_calc,target_d_calc),
+         rep_d_calc=ifelse(same_dir=="no", -rep_d_calc, rep_d_calc),
          rep_se_calc=est_SE(rep_p_calc,rep_d_calc))

### 2022-12-01 code/process.Rmd
update NA counts

@@
 ```
-# Validation
 
@@
 
-We parse out values from (for now) t tests, F tests, and chisq. 
-Other stats to be added later, chisq ES to be added.
+We parse out values from the raw stats.
 
@@
   d_calc=NA
+  N_from_df=NA
   if(within_between=="between"){
     d_calc=2*val/(sqrt(df))  # note this uses the 2t/sqrt(df) approximation df+2 might be more appropriate? 
+    N_from_df=df+2 # between so add 2
   }
-  else{d_calc=val/sqrt(df)}
-  return(data.frame("df_1"=NA, "df_2"=df,"tstat"=val, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc))
+  else{
+    d_calc=val/sqrt(df)
+    N_from_df=df+1
   }
+  return(data.frame("df_1"=NA, "df_2"=df,"tstat"=val, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df))
+}
+```
 
+```{r}
 parse_f <- function(fval, within_between){
@@
   d_calc=NA
+  N_from_df=df_1+df_2+1
   if(!is.na(df_1)&&df_1==1){
@@
   }
-  return(data.frame("df_1"=df_1,"df_2"=df_2,"tstat"=NA, "fstat"=val, "p_calc"=pval, "d_calc"=d_calc))
+  return(data.frame("df_1"=df_1,"df_2"=df_2,"tstat"=NA, "fstat"=val, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df))
 }
+```
 
+```{r}
 parse_chisq <- function(chival, within_between){
@@
   val=str_extract(chival, "\\)=.*") |> str_sub(3,-1) |> as.numeric() |> abs()
-  print(val)
   pval=pchisq(val,df, lower.tail=F)
@@
   }
-  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc))
+  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=n))
 }
 
-#foo = "MCI m1=3.41[3.24,3.55], m2=3.44[3.24,3.57]"
+```
+
+```{r}
 parse_mean_ci <- function(mci,within_between,n){
@@
   }
-  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc))
+  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA))
+}
+```
+
+```{r}
+parse_mean_sd <- function(msd,within_between,n){
+  cond1=str_extract(msd, "m1.*\\),")
+  cond2=str_extract(msd, "m2.*\\)")
+  m1=str_extract(cond1, "m1=.*\\(") |> str_sub(4,-2) |> as.numeric()
+  m2=str_extract(cond2, "m2=.*\\(") |> str_sub(4,-2) |> as.numeric()
+  sd1=str_extract(cond1, "\\(.*\\),") |> str_sub(2,-3) |> as.numeric()
+  sd2=str_extract(cond2, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
+  sd_pool=(sd1+sd2)/2
+  se=sd_pool/sqrt(n)
+  tval=(m1-m2)/se |> abs()
+  if (within_between=="within"){
+  df=n-1
+  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
+  d_calc=tval/(sqrt(df)) 
+  }
+  else if (within_between=="between"){
+    df=n-2
+    pval=pt(q=tval, df=df, lower.tail=FALSE)*2
+    d_calc=2*tval/sqrt(df)
+  }
+  else{
+    df=NA
+    pval=NA
+    d_calc=NA
+  }
+  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA))
 }
 
-#parse_mean_ci(foo)
+```
+
+```{r}
+parse_mean_se <- function(mse,within_between,n){
+  cond1=str_extract(mse, "m1.*\\),")
+  cond2=str_extract(mse, "m2.*\\)")
+  m1=str_extract(cond1, "m1=.*\\(") |> str_sub(4,-2) |> as.numeric()
+  m2=str_extract(cond2, "m2=.*\\(") |> str_sub(4,-2) |> as.numeric()
+  se1=str_extract(cond1, "\\(.*\\),") |> str_sub(2,-3) |> as.numeric()
+  se2=str_extract(cond2, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
+  se=(se1+se2)/2
+  tval=(m1-m2)/se |> abs()
+  if (within_between=="within"){
+  df=n-1
+  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
+  d_calc=tval/(sqrt(df)) 
+  }
+  else if (within_between=="between"){
+    df=n-2
+    pval=pt(q=tval, df=df, lower.tail=FALSE)*2
+    d_calc=2*tval/sqrt(df)
+  }
+  else{
+    df=NA
+    pval=NA
+    d_calc=NA
+  }
+  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA))
+}
+
+```
+
+```{r}
+parse_wilcoxon <- function(wilcox){
+  z=str_sub(wilcox,11,-1) |> as.numeric()
+  pval=pnorm(z,lower.tail=F)
+  #r=z/sqrt(n)
+  #d_calc=4*r/(sqrt(1-r**2))
+  d_calc=NA
+    return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA))
+
+}
+```
+
+```{r}
 
 do_blanks <- function(){
-  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA))
+  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA))
 }
@@
   if (str_sub(raw_stat, 1,3)=="MCI"){return(parse_mean_ci(raw_stat, within_between,n))}
+  if (str_sub(raw_stat, 1,3)=="MSD"){return(parse_mean_sd(raw_stat, within_between,n))}
+  if (str_sub(raw_stat, 1,3)=="MSE"){return(parse_mean_se(raw_stat, within_between,n))}
+  if (str_sub(raw_stat, 1,8)=="wilcoxon"){return(parse_wilcoxon(raw_stat))}
+
   return (do_blanks())
@@
     d = sqrt( (n-1)/n * abs(value)/(1-abs(value)))
-    if (value < 0) {
-      return(-d)}
     return(d)
@@
 
+## Compare pvals
+
 Comparing calculated p vals to provided (or hand calculated) ones. Line is x=y.
@@
 ```
+
+## Compare ES
+
 Comparing calculated ES to original (or hand calculated) ES. All converted to SMD.
@@
 
-## what to do with the weirdos
-
 Where there's a difference, I could check whether it's being compared to something *I* calculated versus something that an original paper or students paper calculated?
@@
 
-```{r}
-test |> filter(target_d_calc>1.9*d_fill_target)
-test |> filter(target_d_calc<.6*d_fill_target)
+## what didn't parse
 
-test |> filter(rep_d_calc>1.9*d_fill_rep)
-test |> filter(rep_d_calc<.6*d_fill_rep)
-
-```
-
-## what didn't parse
+these are ones where we did not get a non-NA effect size. Could be due to formulas being incomplete, or missing information.
 
@@
 
-# Where does df not line up?
-Note: it's not *necessarily* a problem if df's don't line up -- there could be some repeated measures or welch's test stuff going on, but nice to check.
+## how are the df's lining up with sample size?
+
+We can try to back out effective sample size from the df's.
+Note that we don't always expect them to agree (Welch's t test, repeated measures, comparisons only on a sample), but still useful to look at.
+
+There's a lot of off by 1 or 2 things, which I'm unsure what to make of. (As much as possible both sample size and test stats are taken from the papers directly)
 
 ```{r}
+ test |> filter(!is.na(target_N_calc)) |> select(target_N_calc, target_N, target_raw_stat, within_between, target_lastauthor_year) |>
+  mutate(diff=target_N_calc-target_N) |> 
+  ggplot(aes(x=target_N, y=target_N_calc, color=(target_N==target_N_calc)))+geom_point()+geom_abline(slope=1, intercept=0)+scale_y_log10()+scale_x_log10()+scale_color_manual(values=c("TRUE"="black","FALSE"="red"))
 
-test
+ test |> filter(!is.na(rep_N_calc)) |> select(rep_N_calc, replication_N, replication_raw_stat, within_between, target_lastauthor_year) |> mutate(diff=rep_N_calc-replication_N) |> 
+   ggplot(aes(x=replication_N, y=rep_N_calc, color=(replication_N==rep_N_calc)))+geom_point()+geom_abline(slope=1, intercept=0)+scale_y_log10()+scale_x_log10()+scale_color_manual(values=c("TRUE"="black","FALSE"="red"))
 
@@
 
-# Are the ES's okay?
+# PredInt and P_orig
 
@@
 ```
-
-# PredInt and P_orig
 
@@
   geom_point()+
-  coord_cartesian(xlim=c(0,2), ylim=c(-1,3))+
+  coord_cartesian(xlim=c(0,5), ylim=c(-1,4))+
   geom_abline(slope=1, intercept=0)+
@@
 
+Note, it may seem weird that we're missing d and SE for many more replications than we are p values.
+This is because we can't get d_calc if we don't have a filled in value for same direction (but we have p value and unsigned d_calc).
+
 ```{r, message=T}
 message("total rows")
-d |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> nrow()
+d_es |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> nrow()
 
@@
 
-d |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> summarize(                                                      across(everything(),~sum(is.na(.)))) |>
+d_es |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> ungroup() |> summarize(                                                      across(everything(),~sum(is.na(.)))) |>
+  select(-rep_fstat, -rep_tstat,-rep_df_1,-rep_df_2,
+         -target_fstat, -target_tstat, -target_df_1, -target_df_2,
+         -d_fill_rep, -d_fill_target, 
+         -replication_ES_type, -replication_ES_value, -replication_pvalue,
+         -target_ES_type, -target_ES_value, -target_pvalue,
+         -rep_N_calc, -target_N_calc,
+         -replication_test, -target_test) |> 
 pivot_longer(everything()) |>

### 2022-12-13 code/process.Rmd
accomodate betas

@@
 ```
+We have maybe as many as 178 at least for some analyses.
+
+Descriptions:
+
+- "great" means we have all relevant cells coded in spreadsheet
+
+- "ES_direction" is great except that we don't have the direction coded (ex. is an interaction that I can't eyeball, or a multi-way F test with no graph)
+
+- "stuck" means that I'm stuck somewhere -- we don't have everything filled in, but it may be possible to get there
+
+- "hopeless" means we don't have everything filled in, but I don't believe filling in more/all is possible
+
+- "TODO" means I'm still working on data coding (this year's projects)
 
 ```{r}
-d_val <- d |> filter(!status %in% c("missing", "non-experiment", "reproduction"))
+d_val <- d |> filter(!status %in% c("missing", "non-experiment", "reproduction", "TODO"))
 
@@
   }
-  return(data.frame("df_1"=NA, "df_2"=df,"tstat"=val, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df))
+  return(data.frame("df_1"=NA, "df_2"=df,"tstat"=val, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df, "beta"=NA, "SE"=NA))
 }
@@
   }
-  return(data.frame("df_1"=df_1,"df_2"=df_2,"tstat"=NA, "fstat"=val, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df))
+  return(data.frame("df_1"=df_1,"df_2"=df_2,"tstat"=NA, "fstat"=val, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df, "beta"=NA, "SE"=NA))
 }
@@
   }
-  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=n))
+  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=n, "beta"=NA, "SE"=NA))
 }
@@
   }
-  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA))
+  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "beta"=NA, "SE"=NA))
 }
@@
   d_calc=NA
-    return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA))
+    return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "beta"=NA, "SE"=NA))
 
@@
 
+parse_beta_se <- function(raw_stat){
+    beta=str_extract(raw_stat, "b=.*\\(") |> str_sub(3,-2) |> as.numeric()
+    se=str_extract(raw_stat, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
+    zval=beta/se
+    print(zval)
+    pval=2*pnorm(zval, lower.tail=F)
+return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=NA, "N_calc"=NA, "beta"=beta, "SE"=se))
+}
+
+```
+
+```{r}
+
 do_blanks <- function(){
-  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA))
+  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA, "beta"=NA, "SE"=NA))
 }
@@
   if (str_sub(raw_stat, 1,8)=="wilcoxon"){return(parse_wilcoxon(raw_stat))}
+  if (str_sub(raw_stat, 1,3)=="bse"){return(parse_beta_se(raw_stat))}
 
@@
 These look pretty reasonable. Lots on the line and others is places were <.001's happened.
+
+It may be worth checking points that are above the line.
 
@@
 
-d_es_try <- d_es |> filter(!is.na(target_d_calc)) |> 
-  filter(!is.na(rep_d_calc)) |> 
+d_es_try <- d_es |> filter(!is.na(target_d_calc)&!is.na(rep_d_calc)|!is.na(target_beta)&!is.na(rep_beta)) |> 
   mutate(
-         predInt=Replicate::pred_int(target_d_calc,target_se_calc**2, rep_d_calc, rep_se_calc**2)$rep.inside,
-         p_orig=Replicate::p_orig(target_d_calc,target_se_calc**2, rep_d_calc, t2=0, rep_se_calc**2))
+         predInt=ifelse(!is.na(target_d_calc),
+                        Replicate::pred_int(target_d_calc,target_se_calc**2, rep_d_calc, rep_se_calc**2)$rep.inside,
+                        Replicate::pred_int(target_beta, target_SE**2, rep_beta, rep_SE**2)$rep.inside),
+         p_orig=ifelse(!is.na(target_d_calc),
+                       Replicate::p_orig(target_d_calc,target_se_calc**2, rep_d_calc, t2=0, rep_se_calc**2),
+                       Replicate::p_orig(target_beta, target_SE**2,rep_beta, t2=0, rep_SE**2)))
 
@@
   geom_abline(slope=1, intercept=0)+
+    geom_hline(yintercept=0)+
   scale_color_viridis(discrete=T, direction=-1)
@@
 
-d_es |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> ungroup() |> summarize(                                                      across(everything(),~sum(is.na(.)))) |>
+d_check_nas <- d_es |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> ungroup() |>
     select(-rep_fstat, -rep_tstat,-rep_df_1,-rep_df_2,
@@
          -rep_N_calc, -target_N_calc,
-         -replication_test, -target_test) |> 
+         -replication_test, -target_test)
+
+d_check_nas |> summarize(                                                      across(everything(),~sum(is.na(.)))) |>
 pivot_longer(everything()) |>
@@
   filter(value!=0)
+
+message("number of complete rows")
+
+d_check_nas |> filter(across(everything(), ~!is.na(.))) |> nrow()
 

### 2022-12-13 code/process.Rmd
more coding of betas

@@
 
-# TODOs
-- why are some ES's  about 2 times bigger than they should be? (from within v between stuff)
-- validate df against num people?
- - what to do for chisq, other things? for ES
-
 # Pull data
@@
          replication_N, replication_test, replication_raw_stat, replication_pvalue, replication_ES_type, replication_ES_value,
-         replicated_instructor_code, replicated_report_code)
+         replicated_instructor_code, replicated_report_code, adjudicated_replication_code)
 
@@
 
-d |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> tally()
+d |> filter(!status %in% c("missing", "non-experiment", "reproduction", "TODO")) |> tally()
 ```
@@
 ```{r}
-d_val <- d |> filter(!status %in% c("missing", "non-experiment", "reproduction", "TODO"))
+d_val <- d |> filter(!status %in% c("missing", "non-experiment", "reproduction"))
 
@@
     zval=beta/se
-    print(zval)
+    pval=2*pnorm(zval, lower.tail=F)
+return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=NA, "N_calc"=NA, "beta"=beta, "SE"=se))
+}
+
+```
+
+```{r}
+parse_beta_ci <- function(raw_stat){
+  beta=str_extract(raw_stat, "b=.*\\[") |> str_sub(3,-2) |> as.numeric()
+  low=str_extract(raw_stat, "\\[.*,") |> str_sub(2,-2) |> as.numeric()
+  high=str_extract(raw_stat, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
+  se=high-low/(2*1.96)
+  zval=beta/se
     pval=2*pnorm(zval, lower.tail=F)
@@
   if (str_sub(raw_stat, 1,3)=="bse"){return(parse_beta_se(raw_stat))}
+  if (str_sub(raw_stat, 1,3)=="bci"){return(parse_beta_se(raw_stat))}
 
@@
 
+note that we also aren't including the betas where we know we can't get effect size, but we'll still get porig and predInt.
+
 ```{r}
 
-test |> filter(is.na(target_d_calc)) |> filter(!is.na(target_raw_stat)) |>  pull(target_raw_stat)
+test |> filter(is.na(target_d_calc)&is.na(target_beta)) |> filter(!is.na(target_raw_stat)) |>  pull(target_raw_stat)
 
-test |> filter(is.na(rep_d_calc)) |> filter(!is.na(replication_raw_stat)) |> pull(replication_raw_stat)
+test |> filter(is.na(rep_d_calc)&is.na(rep_beta)) |> filter(!is.na(replication_raw_stat)) |> pull(replication_raw_stat)
 ```
@@
 ```{r}
+do_pred_int <- function(target_d_calc, target_se_calc, rep_d_calc,rep_se_calc, target_beta, target_SE, rep_beta, rep_SE){
+  if (!is.na(target_d_calc)&!is.na(rep_d_calc)){
+    return(Replicate::pred_int(target_d_calc,target_se_calc**2, rep_d_calc, rep_se_calc**2)$rep.inside)}
+  if(!is.na(target_beta)&!is.na(rep_beta)){
+    return(Replicate::pred_int(target_beta, target_SE**2, rep_beta, rep_SE**2)$rep.inside)
+  }
+  return(NA)
+}
 
-d_es_try <- d_es |> filter(!is.na(target_d_calc)&!is.na(rep_d_calc)|!is.na(target_beta)&!is.na(rep_beta)) |> 
+do_p_orig <- function(target_d_calc, target_se_calc, rep_d_calc,rep_se_calc, target_beta, target_SE, rep_beta, rep_SE){
+  if (!is.na(target_d_calc)&!is.na(rep_d_calc)){
+    return(Replicate::p_orig(target_d_calc,target_se_calc**2, rep_d_calc, t2=0, rep_se_calc**2))}
+  if(!is.na(target_beta)&!is.na(rep_beta)){
+    return(Replicate::p_orig(target_beta, target_SE**2,rep_beta, t2=0, rep_SE**2))
+  }
+  return(NA)
+}
+
+do_subjective_rep <- function(replicated_instructor_code, replicated_report_code, adjudicated_replication_code){
+  if (is.na(replicated_instructor_code)){return(as.numeric(NA))}
+  if (is.na(replicated_report_code)){return(as.numeric(NA))}
+  if (replicated_instructor_code==replicated_report_code){ return(replicated_instructor_code)}
+  if (!is.na(adjudicated_replication_code)){return (adjudicated_replication_code)}
+  return(as.numeric(NA))
+}
+d_es_predInt <- d_es |> 
          mutate(
-         predInt=ifelse(!is.na(target_d_calc),
-                        Replicate::pred_int(target_d_calc,target_se_calc**2, rep_d_calc, rep_se_calc**2)$rep.inside,
-                        Replicate::pred_int(target_beta, target_SE**2, rep_beta, rep_SE**2)$rep.inside),
-         p_orig=ifelse(!is.na(target_d_calc),
-                       Replicate::p_orig(target_d_calc,target_se_calc**2, rep_d_calc, t2=0, rep_se_calc**2),
-                       Replicate::p_orig(target_beta, target_SE**2,rep_beta, t2=0, rep_SE**2)))
+           predInt=do_pred_int(target_d_calc, target_se_calc, rep_d_calc,rep_se_calc, target_beta, target_SE, rep_beta, rep_SE),
+           p_orig=do_p_orig(target_d_calc, target_se_calc, rep_d_calc,rep_se_calc, target_beta, target_SE, rep_beta, rep_SE),
+           sub_rep= do_subjective_rep(replicated_instructor_code, replicated_report_code, adjudicated_replication_code))
 
@@
 
-d_es_try |> ggplot(aes(x=target_d_calc, y=rep_d_calc, color=p_orig))+
+d_es_predInt |> ggplot(aes(x=target_d_calc, y=rep_d_calc, color=p_orig))+
   geom_point()+
@@
 
-d_es_try |> mutate(p_sig=p_orig<.05) |> ggplot(aes(x=target_d_calc, y=rep_d_calc, color=p_sig))+
+d_es_predInt |> mutate(p_sig=p_orig<.05) |> ggplot(aes(x=target_d_calc, y=rep_d_calc, color=p_sig))+
   geom_point()+
@@
 
-d_es_try |> ggplot(aes(x=target_d_calc, y=rep_d_calc, color=predInt))+
+d_es_predInt |> ggplot(aes(x=target_d_calc, y=rep_d_calc, color=predInt))+
   geom_point()+
@@
 
-d_es_try |> ggplot(aes(x=replicated_report_code, y=p_orig))+geom_jitter(height=0, alpha=.5)+
-  #scale_y_log10()+
-  geom_hline(yintercept=.05)
-
-d_es_try |> ggplot(aes(x=replicated_report_code, y=predInt))+geom_jitter(alpha=.5)
+# d_es_predInt |> ggplot(aes(x=replicated_report_code, y=p_orig))+geom_jitter(height=0, alpha=.5)+
+#   #scale_y_log10()+
+#   geom_hline(yintercept=.05)
+# 
+# d_es_predInt |> ggplot(aes(x=replicated_report_code, y=predInt))+geom_jitter(alpha=.5)
 ```
@@
 message("total rows")
-d_es |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> nrow()
+d_es_predInt |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> nrow()
 
@@
 
-d_check_nas <- d_es |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> ungroup() |>
-    select(-rep_fstat, -rep_tstat,-rep_df_1,-rep_df_2,
-         -target_fstat, -target_tstat, -target_df_1, -target_df_2,
-         -d_fill_rep, -d_fill_target, 
-         -replication_ES_type, -replication_ES_value, -replication_pvalue,
-         -target_ES_type, -target_ES_value, -target_pvalue,
-         -rep_N_calc, -target_N_calc,
-         -replication_test, -target_test)
+d_check_nas <- d_es_predInt |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> ungroup() |>
+    select(target_lastauthor_year, status, academic_year, subfield, target_year,
+           stanford_internal,open_data, open_materials, target_on_turk,
+           replication_on_turk, within_between, single_vignette, repeated_measure,
+           target_N, replication_N,
+           target_p_calc, target_d_calc, rep_p_calc, rep_d_calc,
+           predInt, p_orig, sub_rep)
 
-d_check_nas |> summarize(                                                      across(everything(),~sum(is.na(.)))) |>
+d_check_nas |> summarize(across(everything(),~sum(is.na(.)))) |>
 pivot_longer(everything()) |>
-  arrange(desc(value)) |>
+  arrange((value)) |>
   filter(value!=0)
 
-message("number of complete rows")
+message("number of complete rows for full analysis")
 
@@
 
-```
+message("number of rows for subjective w/ demographic/experimental")
 
-# Correlation between replication scores
+d_check_nas |> select(target_lastauthor_year, status, academic_year, subfield, target_year,
+           stanford_internal,open_data, open_materials, target_on_turk,
+           replication_on_turk, within_between, single_vignette, repeated_measure,
+           target_N, replication_N,
+           sub_rep) |> filter(across(everything(), ~!is.na(.))) |> nrow()
 
-```{r, message=T}
-d_corr <- d |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |>
-  mutate(replicated_instructor_code=as.numeric(replicated_instructor_code)) |> #forcibly convert the ?s to NAs
-  filter(!is.na(replicated_instructor_code) & !is.na(replicated_report_code))
+message("number of rows for predInt/p_orig w/ demographic/experimental")
 
-corr <- cor.test(d_corr$replicated_instructor_code, d_corr$replicated_report_code, method = 'spearman')
-
-message("Num not match")
-d_corr |> filter(replicated_instructor_code!=replicated_report_code) |> nrow()
-
-message("Num match")
-d_corr |> filter(replicated_instructor_code==replicated_report_code) |> nrow()
-
-message("distribution of non-matches")
-
-ggplot(d_corr |> filter(replicated_instructor_code!=replicated_report_code), aes(x=replicated_instructor_code, y=replicated_report_code))+geom_jitter(width=.04, height=.04)+theme_bw()
-
-d_corr |>
-  group_by(replicated_instructor_code, replicated_report_code ) |> tally() |> arrange(replicated_report_code) |>
-  pivot_wider(names_from=replicated_report_code, values_from=n, values_fill=0)
+d_check_nas |> select(target_lastauthor_year, status, academic_year, subfield, target_year,
+           stanford_internal,open_data, open_materials, target_on_turk,
+           replication_on_turk, within_between, single_vignette, repeated_measure,
+           target_N, replication_N, predInt, p_orig,
+           sub_rep) |>  filter(across(everything(), ~!is.na(.))) |> nrow()
 ```
@@
 
-NOTE: will need to replace replicated_code with the discussion agreed one!!
-
-## demographics
-
 ```{r}
-d_demo <- d_es |> 
+d_for_model <- d_es_predInt |> 
   ungroup() |> 
-  mutate(pub_year= target_year-mean(target_year)) |> 
-  select(target_year, pub_year, subfield, replicated_report_code, academic_year)
-
-summary(d_demo)
-d_demo |> group_by(subfield) |> tally()
-```
-
-## statistics
-
-? will outliers on ratio_ss cause a problem?
-
-```{r}
-d_stats <- d_es |> 
-  mutate(log_p =log(target_p_calc),
+  mutate(pub_year= target_year-mean(target_year),
+         log_p =log(target_p_calc),
          log_sample =log(target_N),
          ratio_ss = replication_N/target_N,
-         change_platform=ifelse(replication_on_turk==target_on_turk,0,1)) |> 
+         change_platform=ifelse(replication_on_turk==target_on_turk,0,1),
   #this codes 1 if the original was in person, but replication turk/prolific,
   # 0 if they were both on turk/prolific or both in-person (rare, but happens a few times)
-  select(replicated_report_code,log_p,log_sample, ratio_ss, change_platform, academic_year, target_d_calc)
-
-summary(d_stats)
-```
-
-## closeness
-
-```{r}
-
-# could do with mutate across, but clearer this way?
-
-d_close <- d_es |> 
-  mutate(open_data=ifelse(open_data=="yes", 1,0),
+        open_data=ifelse(open_data=="yes", 1,0),
          open_mat=ifelse(open_materials=="yes", 1,0),
-         stanford=ifelse(stanford_internal=="yes", 1,0)) |> 
-  select(open_data, open_mat, stanford, replicated_report_code,
-         academic_year)
-
-summary(d_close)
-```
-
-## design
-
-```{r}
-d_design <- d_es |> 
-  mutate(is_within=case_when(
+         stanford=ifelse(stanford_internal=="yes", 1,0),
+        is_within=case_when(
             within_between=="within" ~ 1,
@@
             within_between=="between" ~ 0),
-    log_trials=log(repeated_measure),
-    log_sample=log(target_N))|> 
-  select(is_within, single_vignette,log_trials, log_sample, replicated_report_code, academic_year)
+    log_trials=log(repeated_measure)) |> 
+  select(target_lastauthor_year, academic_year, subfield, 
+         pub_year, log_p, log_sample, ratio_ss, change_platform, target_d_calc,
+           stanford, open_data, open_mat, 
+         is_within, single_vignette, log_trials, 
+           predInt, p_orig, sub_rep)
 
-summary(d_design)
+summary(d_for_model)
+
 ```

### 2023-01-18 code/process.Rmd
getting closer!

@@
 
-d |> filter(!status %in% c("missing", "non-experiment", "reproduction", "TODO")) |> tally()
+d |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> tally()
 ```
-We have maybe as many as 178 at least for some analyses.
+We have maybe as many as 177 at least for some analyses.
 
@@
 
-- "great" means we have all relevant cells coded in spreadsheet
+- "complete" -- it's a full case
 
-- "ES_direction" is great except that we don't have the direction coded (ex. is an interaction that I can't eyeball, or a multi-way F test with no graph)
+- "adj" -- will be a full case once we get subjective replication and subfield coded
 
-- "stuck" means that I'm stuck somewhere -- we don't have everything filled in, but it may be possible to get there
+- "beta" -- don't have standardized ES, but have a pair that we can do predInt to
 
-- "hopeless" means we don't have everything filled in, but I don't believe filling in more/all is possible
+- "ES_direction" -- we don't have the direction coded (ex. is an interaction that I can't eyeball, or a multi-way F test with no graph)
 
-- "TODO" means I'm still working on data coding (this year's projects)
+- "ask" -- might be salvageable, but I have questions about coding
+
+- "done" -- got as far as I can, and that is that we have demographics but not stats
+
+- "unusable" -- got as far as I can, and it does not have complete descriptives
+
+- "missing" -- student didn't finish or we don't have write-up
+
+- "non-experiment" -- student replicated something that was not an experiment
+
+- "reproduction" -- student did a reproduction and not replication
 
@@
 ```{r}
+
 parse_beta_ci <- function(raw_stat){
@@
   if (str_sub(raw_stat, 1,3)=="bse"){return(parse_beta_se(raw_stat))}
-  if (str_sub(raw_stat, 1,3)=="bci"){return(parse_beta_se(raw_stat))}
+  if (str_sub(raw_stat, 1,3)=="bci"){return(parse_beta_ci(raw_stat))}
 
@@
 
-d_check_nas |> filter(across(everything(), ~!is.na(.))) |> nrow()
+d_check_nas |> select(-sub_rep, -subfield) |> filter(across(everything(), ~!is.na(.))) |> nrow()
 
@@
 
-d_check_nas |> select(target_lastauthor_year, status, academic_year, subfield, target_year,
+d_check_nas |> select(target_lastauthor_year, status, academic_year,  target_year,
            stanford_internal,open_data, open_materials, target_on_turk,
            replication_on_turk, within_between, single_vignette, repeated_measure,
-           target_N, replication_N,
-           sub_rep) |> filter(across(everything(), ~!is.na(.))) |> nrow()
+           target_N, replication_N) |> filter(across(everything(), ~!is.na(.))) |> nrow()
 
@@
 
-d_check_nas |> select(target_lastauthor_year, status, academic_year, subfield, target_year,
+d_check_nas |> select(target_lastauthor_year, status, academic_year, target_year,
            stanford_internal,open_data, open_materials, target_on_turk,
            replication_on_turk, within_between, single_vignette, repeated_measure,
-           target_N, replication_N, predInt, p_orig,
-           sub_rep) |>  filter(across(everything(), ~!is.na(.))) |> nrow()
+           target_N, replication_N, predInt, p_orig) |>  filter(across(everything(), ~!is.na(.))) |> nrow()
+```
+
+```{r}
+# papers where we don't have everything
+
+d_check_nas |> filter(if_any(everything(), ~is.na(.)))
+
+d_check_nas |> filter(across(everything(), ~!is.na(.)))
+
+d_check_nas  |> select(target_lastauthor_year, status, academic_year, target_year,
+           stanford_internal,open_data, open_materials, target_on_turk,
+           replication_on_turk, within_between, single_vignette, repeated_measure,
+           target_N, replication_N, predInt, p_orig) |>  filter(if_any(everything(), ~is.na(.)))
 ```

### 2023-02-07 code/process.Rmd
various tweaks

@@
   }
-  return(data.frame("df_1"=NA, "df_2"=df,"tstat"=val, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df, "beta"=NA, "SE"=NA))
+  return(data.frame("df_1"=NA, "df_2"=df,"tstat"=val, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df, "ES"=NA, "SE"=NA))
 }
@@
   }
-  return(data.frame("df_1"=df_1,"df_2"=df_2,"tstat"=NA, "fstat"=val, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df, "beta"=NA, "SE"=NA))
+  return(data.frame("df_1"=df_1,"df_2"=df_2,"tstat"=NA, "fstat"=val, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df, "ES"=NA, "SE"=NA))
 }
@@
 ```{r}
-parse_chisq <- function(chival, within_between){
-  df=str_extract(chival, "\\(.*,") |> str_sub(2,-2) |> as.numeric()
-  n=str_extract(chival, ",N=.*\\)") |> str_sub(4,-2) |> as.numeric()
-  val=str_extract(chival, "\\)=.*") |> str_sub(3,-1) |> as.numeric() |> abs()
-  pval=pchisq(val,df, lower.tail=F)
-  phi=sqrt(val/n)
-  d_calc=NA
-  if (!is.na(df)&&df==1){
-    d_calc=esc_phi(phi,pval,n, es.type="d")$es
+# for proportions 
+#ex <- "prob: 13 / 14 , 2 / 14"
+parse_prop <- function(propval){
+  val <- str_extract_all(propval, "[0-9]+")[[1]]
+  num1 <- val[1] |> as.numeric()
+  den1 <- val[2] |> as.numeric()
+  num2 <- val[3] |> as.numeric()
+  den2 <- val[4] |> as.numeric()
+  est1 <- num1/den1
+  est1_var <- est1*(1-est1)/den1
+  est2 <- num2/den2
+  est2_var <- est2*(1-est2)/den2
+  diff <- est1-est2
+  diff_var <- est1_var+est2_var
+  return(data.frame("df_1"=NA, "df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA, "ES"=diff, "SE"=sqrt(diff_var)))
 }
-  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=n, "beta"=NA, "SE"=NA))
-}
+#parse_prop(ex)
 
@@
   }
-  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "beta"=NA, "SE"=NA))
+  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=NA, "SE"=NA))
 }
@@
   }
-  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "beta"=NA, "SE"=NA))
+  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=NA, "SE"=NA))
 }
 
-```
-
-```{r}
-parse_wilcoxon <- function(wilcox){
-  z=str_sub(wilcox,11,-1) |> as.numeric()
-  pval=pnorm(z,lower.tail=F)
-  #r=z/sqrt(n)
-  #d_calc=4*r/(sqrt(1-r**2))
-  d_calc=NA
-    return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "beta"=NA, "SE"=NA))
-
-}
 ```
@@
     pval=2*pnorm(zval, lower.tail=F)
-return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=NA, "N_calc"=NA, "beta"=beta, "SE"=se))
+return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=NA, "N_calc"=NA, "ES"=beta, "SE"=se))
 }
@@
     pval=2*pnorm(zval, lower.tail=F)
-  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=NA, "N_calc"=NA, "beta"=beta, "SE"=se))
+  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=NA, "N_calc"=NA, "ES"=beta, "SE"=se))
 }
@@
 do_blanks <- function(){
-  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA, "beta"=NA, "SE"=NA))
+  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA, "ES"=NA, "SE"=NA))
 }
@@
   if (str_sub(raw_stat,1,1)=="F"){return(parse_f(raw_stat, within_between))}
-  if (str_sub(raw_stat,1,1)=="c"){return(parse_chisq(raw_stat, within_between))}
+  if (str_sub(raw_stat,1,4)=="prop"){return(parse_prop(raw_stat))}
   if (str_sub(raw_stat, 1,3)=="MCI"){return(parse_mean_ci(raw_stat, within_between,n))}

### 2023-02-10 code/process.Rmd
fix directionality

@@
 ```
-
+<!--
 # Exclusions
@@
 - "reproduction" -- student did a reproduction and not replication 
+-->
 
@@
 
+```{r}
+#helper function for pooling when needed
+pool_m_sd <- function(m1, sd1, n1, m2, sd2, n2){
+  m=(m1*n1+m2*n2)/(n1+n2)
+  var=(n1*(sd1**2+m1**2)+n2*(sd2**2+m2**2))/(n1+n2)-m**2
+  sd=sqrt(var)
+  return(c(m,sd))
+
+}
+
+#pool_m_sd(2.875,1.3102163,16,3.5,.8548504,14)
+#pool_m_sd(1.5, 1.6329932, 16, 2.25, 1.6583124, 12)
+#pool_m_sd(2.48,1.41,46,3.35,1.07,49)
+#pool_m_sd(1.90,1.54,49,2.22,1.46,49)
+```
 # Parsing
@@
 # considered using the effectsize package but afaik we don't care about estimating CI's here and there were optim problems with that
+
+est_SE <- function(p,d){
+  z <- -.862+sqrt(abs(.743-2.404*log(p)))
+  SE <- abs(d/z)
+  return(SE)
+}
 
@@
   }
-  return(data.frame("df_1"=NA, "df_2"=df,"tstat"=val, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df, "ES"=NA, "SE"=NA))
+  se=est_SE(pval, d_calc)
+  return(data.frame("df_1"=NA, "df_2"=df,"tstat"=val, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df, "ES"=d_calc, "SE"=se))
 }
@@
     }
+    se=est_SE(pval,d_calc)
   }
@@
     n=df_1+df_2+1 # rederive n b/c it's not always matching the n we have
-    partial_eta=(val*df_1)/(val*df_1+df_2)
-    d_calc=sqrt(n/(n-1)*(partial_eta/(1-partial_eta)))
+    #partial_eta=(val*df_1)/(val*df_1+df_2)
+    #d_calc=sqrt(n/(n-1)*(partial_eta/(1-partial_eta)))
+    d_calc=NA
+    se=NA
   }
-  return(data.frame("df_1"=df_1,"df_2"=df_2,"tstat"=NA, "fstat"=val, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df, "ES"=NA, "SE"=NA))
+
+  return(data.frame("df_1"=df_1,"df_2"=df_2,"tstat"=NA, "fstat"=val, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df, "ES"=d_calc, "SE"=se))
 }
@@
 ```{r}
-# for proportions 
+# for comparison between proportions 
 #ex <- "prob: 13 / 14 , 2 / 14"
@@
 
+```
+
+```{r}
+# for one proportion
+#ex <- "raw prop : 10 / 18"
+parse_raw_prop <- function(propval){
+  val <- str_extract_all(propval, "[0-9]+")[[1]]
+  num1 <- val[1] |> as.numeric()
+  den1 <- val[2] |> as.numeric()
+  est1 <- num1/den1
+  est1_var <- est1*(1-est1)/den1
+   return(data.frame("df_1"=NA, "df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA, "ES"=est1, "SE"=sqrt(est1_var)))
+}
+#parse_raw_prop(ex)
 ```
@@
   }
-  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=NA, "SE"=NA))
+  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=m1-m2, "SE"=se))
 }
@@
 
+#this is just to deal with yang2018 where we have d's given and bci
+#ex <- "d: 1.40 ; bci: b=1.72 [1.44, 2.00]"
+parse_dbci <- function(raw_stat){
+  bci = str_extract(raw_stat, ";.*") |> str_sub(2,-1)
+  beta=str_extract(bci, "b=.*\\[") |> str_sub(3,-2) |> as.numeric()
+  low=str_extract(bci, "\\[.*,") |> str_sub(2,-2) |> as.numeric()
+  high=str_extract(bci, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
+  se=high-low/(2*1.96)
+
+  dval = str_extract(raw_stat, ".*;") |> str_sub(3,-2) |> as.numeric()
+  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=dval, "N_calc"=NA, "ES"=beta, "SE"=se))
+}
+#parse_dbci(ex)
+
 ```
@@
   if (str_sub(raw_stat,1,4)=="prop"){return(parse_prop(raw_stat))}
+  if (str_sub(raw_stat,1,7)=="rawprop"){return(parse_raw_prop(raw_stat))}
   if (str_sub(raw_stat, 1,3)=="MCI"){return(parse_mean_ci(raw_stat, within_between,n))}
@@
   if (str_sub(raw_stat, 1,3)=="bci"){return(parse_beta_ci(raw_stat))}
+  if (str_sub(raw_stat, 1,1)=="d"){return(parse_dbci(raw_stat))}
 
@@
 ```
-
+<!--
 ## Compare pvals
@@
 Ones where we get an off  by two error -- should I double check within-betweeness for the test?
-
+-->
 ## what didn't parse
@@
 
-test |> filter(is.na(target_d_calc)&is.na(target_beta)) |> filter(!is.na(target_raw_stat)) |>  pull(target_raw_stat)
+test |> filter(is.na(target_d_calc)&is.na(target_ES)) |> filter(!is.na(target_raw_stat)) |>  pull(target_raw_stat)
 
-test |> filter(is.na(rep_d_calc)&is.na(rep_beta)) |> filter(!is.na(replication_raw_stat)) |> pull(replication_raw_stat)
+test |> filter(is.na(rep_d_calc)&is.na(rep_ES)) |> filter(!is.na(replication_raw_stat)) |> pull(replication_raw_stat)
 ```
 
+<!--
 ## how are the df's lining up with sample size?
@@
 ```
-
+-->
 # PredInt and P_orig
@@
 
-est_SE <- function(p,d){
-  z <- -.862+sqrt(abs(.743-2.404*log(p)))
-  SE <- abs(d/z)
-  return(SE)
-}
-
 d_es <-  test |> 
-  rowwise() |> 
-  mutate(target_se_calc=est_SE(target_p_calc,target_d_calc),
-         rep_d_calc=ifelse(same_dir=="no", -rep_d_calc, rep_d_calc),
-         rep_se_calc=est_SE(rep_p_calc,rep_d_calc))
+  mutate(target_d_calc=abs(target_d_calc),
+         target_ES=abs(target_ES),
+         rep_d_calc=case_when(
+           same_dir=="yes" ~ abs(rep_d_calc),
+           same_dir=="no" ~-abs(rep_d_calc),
+           T ~ as.numeric(NA)
+          ),
+         rep_ES=case_when(
+           same_dir=="yes" ~ abs(rep_ES),
+           same_dir=="no" ~-abs(rep_ES),
+           T ~ as.numeric(NA)
+         ))
 
@@
 ```{r}
-do_pred_int <- function(target_d_calc, target_se_calc, rep_d_calc,rep_se_calc, target_beta, target_SE, rep_beta, rep_SE){
-  if (!is.na(target_d_calc)&!is.na(rep_d_calc)){
-    return(Replicate::pred_int(target_d_calc,target_se_calc**2, rep_d_calc, rep_se_calc**2)$rep.inside)}
-  if(!is.na(target_beta)&!is.na(rep_beta)){
-    return(Replicate::pred_int(target_beta, target_SE**2, rep_beta, rep_SE**2)$rep.inside)
+do_pred_int <- function(target_ES, target_SE, rep_ES, rep_SE){
+  if(!is.na(target_ES)&!is.na(rep_ES)){
+    return(Replicate::pred_int(target_ES, target_SE**2, rep_ES, rep_SE**2)$rep.inside)
   }
@@
 
-do_p_orig <- function(target_d_calc, target_se_calc, rep_d_calc,rep_se_calc, target_beta, target_SE, rep_beta, rep_SE){
-  if (!is.na(target_d_calc)&!is.na(rep_d_calc)){
-    return(Replicate::p_orig(target_d_calc,target_se_calc**2, rep_d_calc, t2=0, rep_se_calc**2))}
-  if(!is.na(target_beta)&!is.na(rep_beta)){
-    return(Replicate::p_orig(target_beta, target_SE**2,rep_beta, t2=0, rep_SE**2))
+do_p_orig <- function(target_ES, target_SE, rep_ES, rep_SE){
+  if(!is.na(target_ES)&!is.na(rep_ES)){
+    return(Replicate::p_orig(target_ES, target_SE**2,rep_ES, t2=0, rep_SE**2))
   }
@@
          mutate(
-           predInt=do_pred_int(target_d_calc, target_se_calc, rep_d_calc,rep_se_calc, target_beta, target_SE, rep_beta, rep_SE),
-           p_orig=do_p_orig(target_d_calc, target_se_calc, rep_d_calc,rep_se_calc, target_beta, target_SE, rep_beta, rep_SE),
+           predInt=do_pred_int(target_ES, target_SE, rep_ES, rep_SE),
+           p_orig=do_p_orig(target_ES, target_SE, rep_ES, rep_SE),
            sub_rep= do_subjective_rep(replicated_instructor_code, replicated_report_code, adjudicated_replication_code))
@@
 
-d_check_nas |> filter(if_any(everything(), ~is.na(.)))
+#d_check_nas |> filter(if_any(everything(), ~is.na(.)))
 
-d_check_nas |> filter(across(everything(), ~!is.na(.)))
+#d_check_nas |> filter(across(everything(), ~!is.na(.)))
 
-d_check_nas  |> select(target_lastauthor_year, status, academic_year, target_year,
-           stanford_internal,open_data, open_materials, target_on_turk,
-           replication_on_turk, within_between, single_vignette, repeated_measure,
-           target_N, replication_N, predInt, p_orig) |>  filter(if_any(everything(), ~is.na(.)))
+# d_check_nas  |> select(target_lastauthor_year, status, academic_year, target_year,
+#            stanford_internal,open_data, open_materials, target_on_turk,
+#            replication_on_turk, within_between, single_vignette, repeated_measure,
+#            target_N, replication_N, predInt, p_orig) |>  filter(if_any(everything(), ~is.na(.)))
 ```
@@
 ```
+
+TODOs:
+- will need to do selection of which things have complete cases for models
+- will need to z-score things (in a recoverable way)

### 2023-02-17 code/process.Rmd
write model code

@@
 library(esc)
+library(here)
+library(brms)
 theme_set(theme_bw())
+
+model_location="code/models"
 ```
@@
     se=str_extract(raw_stat, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
-    zval=beta/se
-    pval=2*pnorm(zval, lower.tail=F)
-return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=NA, "N_calc"=NA, "ES"=beta, "SE"=se))
+    #zval=beta/se
+    #pval=2*pnorm(zval, lower.tail=F)
+return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA, "ES"=beta, "SE"=se))
 }
@@
   se=high-low/(2*1.96)
-  zval=beta/se
-    pval=2*pnorm(zval, lower.tail=F)
-  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=NA, "N_calc"=NA, "ES"=beta, "SE"=se))
+ #zval=beta/se
+    #pval=2*pnorm(zval, lower.tail=F)
+  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA, "ES"=beta, "SE"=se))
 }
@@
          log_sample =log(target_N),
-         ratio_ss = replication_N/target_N,
+         log_ratio_ss = log(replication_N/target_N),
          change_platform=ifelse(replication_on_turk==target_on_turk,0,1),
@@
             within_between=="between" ~ 0),
-    log_trials=log(repeated_measure)) |> 
+    log_trials=log(repeated_measure),
+  predInt=as.numeric(predInt)) |> 
   select(target_lastauthor_year, academic_year, subfield, 
-         pub_year, log_p, log_sample, ratio_ss, change_platform, target_d_calc,
+         pub_year, log_p, log_sample, log_ratio_ss, change_platform, target_d_calc,
            stanford, open_data, open_mat, 
@@
 
-TODOs:
-- will need to do selection of which things have complete cases for models
-- will need to z-score things (in a recoverable way)
+## z-score
+
+```{r}
+
+z_data <- d_for_model |> 
+  mutate(across(c("pub_year","log_p", "log_sample", "log_ratio_ss","target_d_calc", "log_trials"), ~scale(.)[,1], .names="z_{.col}"))
+
+back_convert <- d_for_model |> 
+  summarize(across(c("pub_year","log_p", "log_sample", "log_ratio_ss","target_d_calc", "log_trials"), ~mean(., na.rm=T), .names="mean_{.col}"),
+         across(c("pub_year","log_p", "log_sample", "log_ratio_ss","target_d_calc", "log_trials"), ~sd(.,na.rm=T), .names="sd_{.col}"))
+
+```
+
+## check z-score
+
+```{r}
+# z_data |>
+#   mutate(check_pub=pub_year - z_pub_year*back_convert$sd_pub_year+back_convert$mean_pub_year) |> 
+#   filter(check_pub > .00001)
+```
+
+## tier 1 data
+```{r}
+data_tier1 <- z_data |> select(academic_year, sub_rep, 
+                               z_pub_year, subfield, open_data, open_mat, stanford, change_platform, z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials) |> filter(across(everything(), ~!is.na(.)))
+
+```
+
+## tier 2 data
+```{r}
+data_tier2 <- z_data |> select(academic_year, sub_rep, 
+                               p_orig, predInt,
+                               z_pub_year, subfield, open_data, open_mat, stanford, change_platform, z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials) |> filter(across(everything(), ~!is.na(.)))
+```
+
+## tier 3 data
+```{r}
+data_tier3 <- z_data |> select(academic_year, sub_rep, 
+                               p_orig, predInt,
+                               z_target_d_calc, z_log_p, 
+                               z_pub_year, subfield, open_data, open_mat, stanford, change_platform, z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials) |> filter(across(everything(), ~!is.na(.)))
+```
+
+# Models
+
+```{r}
+
+priors <- c(set_prior("horseshoe(3)", class="b"),
+            set_prior("normal(0,.5)", class="sd"),
+            set_prior("lkj(1)", class="cor"))
+```
+
+```{r}
+tier1_subjective <- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
+                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
+                        family="bernoulli",
+                        data=data_tier1,
+                        file=here(model_location, "tier1_subjective"),
+                        prior=priors, 
+                        iter=100,
+                        control=list(adapt_delta=.99),
+                        backend="cmdstanr")
+```
+
+```{r, eval=F}
+tier2_predint <- brm(pred_int ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
+                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
+                        family="bernoulli",
+                        data=data_tier2,
+                        file=here(model_location, "tier2_predint"),
+                        prior=priors, 
+                        control=list(adapt_delta=.99),
+                        backend="cmdstanr")
+```
+
+```{r, eval=F}
+tier2_porig <- brm(porig ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
+                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
+                        data=data_tier2,
+                        file=here(model_location, "tier2_porig"),
+                        prior=priors, 
+                        control=list(adapt_delta=.99),
+                        backend="cmdstanr")
+```
+
+```{r, eval=F}
+tier3_subjective <- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
+                           z_target_d_calc + z_log_p+ 
+                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
+                             z_target_d_calc + z_log_p| academic_year),
+                        family="bernoulli",
+                        data=data_tier3,
+                        file=here(model_location, "tier3_subjective"),
+                        prior=priors, 
+                        control=list(adapt_delta=.99),
+                        backend="cmdstanr")
+```
+
+```{r, eval=F}
+tier3_predint <- brm(predint ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
+                           z_target_d_calc + z_log_p+ 
+                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
+                             z_target_d_calc + z_log_p| academic_year),
+                        family="bernoulli",
+                        data=data_tier3,
+                        file=here(model_location, "tier3_predint"),
+                        prior=priors, 
+                        control=list(adapt_delta=.99),
+                        backend="cmdstanr")
+```
+
+```{r, eval=F}
+tier3_porig <- brm(p_orig ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
+                           z_target_d_calc + z_log_p+ 
+                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
+                             z_target_d_calc + z_log_p| academic_year),
+                        family="bernoulli",
+                        data=data_tier3,
+                        file=here(model_location, "tier3_porig"),
+                        prior=priors, 
+                        control=list(adapt_delta=.99),
+                        backend="cmdstanr")
+```

### 2023-02-27 code/process.Rmd
work on checking inputs

@@
 library(brms)
+library(rstan)
+
+rstan_options(auto_write = TRUE)
+options(mc.cores = parallel::detectCores())
+
 theme_set(theme_bw())
@@
 ```
-<!--
-# Exclusions
 
 ```{r}
+
+d |> tally()
 d |> group_by(status) |> tally()
@@
 
-d_check_nas |> select(-sub_rep, -subfield) |> filter(across(everything(), ~!is.na(.))) |> nrow()
+d_check_nas |> filter(across(everything(), ~!is.na(.))) |> nrow()
 
@@
 d_check_nas |> select(target_lastauthor_year, status, academic_year,  target_year,
+                      sub_rep, subfield,
            stanford_internal,open_data, open_materials, target_on_turk,
            replication_on_turk, within_between, single_vignette, repeated_measure,
-           target_N, replication_N) |> filter(across(everything(), ~!is.na(.))) |> nrow()
+           target_N, replication_N) |> filter(if_any(everything(), ~is.na(.))) #|> nrow()
 
@@
 d_check_nas |> select(target_lastauthor_year, status, academic_year, target_year,
+                      sub_rep, subfield,
            stanford_internal,open_data, open_materials, target_on_turk,
@@
 
-```{r}
+```{r, eval=F}
 tier1_subjective <- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
@@
                           z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
-                        family="bernoulli",
+                        #family=gaussian(link='logit'), # runs
+                        #family="cumulative", # runs on 1-5 data
+                        # family="zero_one_inflated_beta", runs, 
+                        # beta_binomial on 0-4 data
                         data=data_tier1,
-                        file=here(model_location, "tier1_subjective"),
+                        #file=here(model_location, "tier1_subjective"),
                         prior=priors, 
@@
                         control=list(adapt_delta=.99),
-                        backend="cmdstanr")
+                        #backend="cmdstanr"
+                        )
 ```
@@
                              z_target_d_calc + z_log_p| academic_year),
-                        family="bernoulli",
+                        family=(link="logit"),
                         data=data_tier3,
@@
                         control=list(adapt_delta=.99),
-                        backend="cmdstanr")
+                        #backend="cmdstanr"
+                   )
 ```

### 2023-03-01 code/process.Rmd
final checks on stuff before running first model

@@
 
-  select(target_lastauthor_year, status, academic_year, subfield, target_year, stanford_internal, 
+  select(target_lastauthor_year, sensitivity, include,
+         status, academic_year, subfield, target_year, stanford_internal, 
          open_data, open_materials, target_on_turk, replication_on_turk, 
@@
 d |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> tally()
+
+d |> group_by(include) |> tally()
+
 ```
@@
 
-- "complete" -- it's a full case
+- "done" -- fully coded, can be used for whatever is specified in other column
 
-- "adj" -- will be a full case once we get subjective replication and subfield coded
-
-- "beta" -- don't have standardized ES, but have a pair that we can do predInt to
-
-- "ES_direction" -- we don't have the direction coded (ex. is an interaction that I can't eyeball, or a multi-way F test with no graph)
+- "ES_direction" -- we don't have the direction coded
 
 - "ask" -- might be salvageable, but I have questions about coding
-
-- "done" -- got as far as I can, and that is that we have demographics but not stats
 
@@
 - "reproduction" -- student did a reproduction and not replication
--->
 
@@
 d_val <- d |> filter(!status %in% c("missing", "non-experiment", "reproduction"))
-
-# d_val$academic_year |> unique()
-# 
-# d_val |> filter(!subfield %in% c("social","cognitive","non-psych","other-psych"))
-# 
-# d_val |> filter(!stanford_internal %in% c("no","yes"))
-# 
-# d_val |> filter(!open_data %in% c("no","yes"))
-# 
-# d_val |> filter(!open_materials %in% c("no","yes"))
-# 
-# d_val |> filter(!target_on_turk %in% c("no","yes"))
-# 
-# d_val |> filter(!replication_on_turk %in% c("no","yes"))
-# 
-# d_val |> filter(!within_between %in% c("within","between","mixed"))
-# 
-# d_val |> filter(!single_vignette %in% c(0,1))
 
@@
 }
-
-#pool_m_sd(2.875,1.3102163,16,3.5,.8548504,14)
-#pool_m_sd(1.5, 1.6329932, 16, 2.25, 1.6583124, 12)
-#pool_m_sd(2.48,1.41,46,3.35,1.07,49)
-#pool_m_sd(1.90,1.54,49,2.22,1.46,49)
 ```
@@
 
-est_SE <- function(p,d){
-  z <- -.862+sqrt(abs(.743-2.404*log(p)))
-  SE <- abs(d/z)
-  return(SE)
-}
-
 parse_t <- function(tval, within_between) {
@@
   if(within_between=="between"){
-    d_calc=2*val/(sqrt(df))  # note this uses the 2t/sqrt(df) approximation df+2 might be more appropriate? 
+    d_calc=2*val/(sqrt(df+2)) # this is a simplification for equal groups
     N_from_df=df+2 # between so add 2
@@
   else{
-    d_calc=val/sqrt(df)
+    d_calc=val/sqrt(df+1)
     N_from_df=df+1
   }
-  se=est_SE(pval, d_calc)
+  se=4/N_from_df+d_calc**2/(2*N_from_df)
   return(data.frame("df_1"=NA, "df_2"=df,"tstat"=val, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df, "ES"=d_calc, "SE"=se))
@@
     if(within_between=="between"){
-      d_calc=2*sqrt(val)/sqrt(df_2) # if there's just two groups, then F=t**2 and we can use the t-test thingy
+      d_calc=2*sqrt(val)/sqrt(N_from_df) # if there's just two groups, then F=t**2 and we can use the t-test thingy
     }
@@
     }
-    se=est_SE(pval,d_calc)
+   se=4/N_from_df+d_calc**2/(2*N_from_df)
   }
   else if(!is.na(df_1)){
-    # we go through partial eta
-    n=df_1+df_2+1 # rederive n b/c it's not always matching the n we have
-    #partial_eta=(val*df_1)/(val*df_1+df_2)
-    #d_calc=sqrt(n/(n-1)*(partial_eta/(1-partial_eta)))
     d_calc=NA
@@
 parse_mean_ci <- function(mci,within_between,n){
+  # parsing 
   cond1=str_extract(mci, "m1.*\\],")
@@
   high2=str_extract(cond2, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
+  # calculations 
   se1=high1-low1/(2*1.96)
   se2=high2-low2/(2*1.96)
-  se=(se1+se2)/2
-  tval=(m1-m2)/se |> abs()
-  if (within_between=="within"){
-  df=n-1
+  per_group_n=ifelse(within_between=="within",n, n/2)
+  sd1=se1*sqrt(per_group_n-1) # assume equal groups
+  sd2=se2*sqrt(per_group_n-1)
+  sd_pool=sqrt((sd1**2+sd2**2)/2) # assume equal groups
+  se_pool=sd_pool/sqrt(n-1)
+  d_calc=abs(m1-m2/sd_pool) # note we force all positive and then fix later 
+  tval=(m1-m2)/se_pool |> abs()
+  df=ifelse(within_between=="within", n-1, n-2)
   pval=pt(q=tval, df=df, lower.tail=FALSE)*2
-  d_calc=tval/(sqrt(df)) 
-  }
-  else{
-    df=NA
-    pval=NA
-    d_calc=NA
-  }
-  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=m1-m2, "SE"=se))
+  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=m1-m2, "SE"=se_pool))
 }
@@
   sd2=str_extract(cond2, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
-  sd_pool=(sd1+sd2)/2
-  se=sd_pool/sqrt(n)
-  tval=(m1-m2)/se |> abs()
-  if (within_between=="within"){
-  df=n-1
+  #
+  sd_pool=sqrt((sd1**2+sd2**2)/2) # assume equal groups
+  se_pool=sd_pool/sqrt(n-1)
+  d_calc=abs(m1-m2/sd_pool) # note we force all positive and then fix later 
+  tval=(m1-m2)/se_pool |> abs()
+  df=ifelse(within_between=="within", n-1, n-2)
   pval=pt(q=tval, df=df, lower.tail=FALSE)*2
-  d_calc=tval/(sqrt(df)) 
-  }
-  else if (within_between=="between"){
-    df=n-2
-    pval=pt(q=tval, df=df, lower.tail=FALSE)*2
-    d_calc=2*tval/sqrt(df)
-  }
-  else{
-    df=NA
-    pval=NA
-    d_calc=NA
-  }
-  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=m1-m2, "SE"=se))
+  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=m1-m2, "SE"=se_pool))
 }
@@
   se2=str_extract(cond2, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
-  se=(se1+se2)/2
-  tval=(m1-m2)/se |> abs()
-  if (within_between=="within"){
-  df=n-1
+
+  per_group_n=ifelse(within_between=="within",n, n/2)
+  sd1=se1*sqrt(per_group_n-1) # assume equal groups
+  sd2=se2*sqrt(per_group_n-1)
+  sd_pool=sqrt((sd1**2+sd2**2)/2) # assume equal groups
+  se_pool=sd_pool/sqrt(n-1)
+  d_calc=abs(m1-m2/sd_pool) # note we force all positive and then fix later 
+  tval=(m1-m2)/se_pool |> abs()
+  df=ifelse(within_between=="within", n-1, n-2)
   pval=pt(q=tval, df=df, lower.tail=FALSE)*2
-  d_calc=tval/(sqrt(df)) 
-  }
-  else if (within_between=="between"){
-    df=n-2
-    pval=pt(q=tval, df=df, lower.tail=FALSE)*2
-    d_calc=2*tval/sqrt(df)
-  }
-  else{
-    df=NA
-    pval=NA
-    d_calc=NA
-  }
-  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=m1-m2, "SE"=se))
+  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=m1-m2, "SE"=se_pool))
 }
@@
 ```{r}
-fill_es <- function(type, value, n){
-  if (is.na(type)) {
-    return(NA)}
-  if (is.na(value)) {
-    return(NA)
-  }
-  if (type=="partial eta sq"){
-    d = sqrt( (n-1)/n * abs(value)/(1-abs(value)))
-    return(d)
-    }
-  if (type %in% c("d", "SMD")){
-    return(abs(value))
-  }
-  return(NA)
-}
 
@@
   unnest(cols=c(target, rep), names_sep="_") |> 
-  rowwise() |> 
-  mutate(d_fill_target=fill_es(target_ES_type, target_ES_value, target_N),
-         d_fill_rep=fill_es(replication_ES_type, replication_ES_value, replication_N))
+  rowwise()
 
 ```
-<!--
-## Compare pvals
 
-Comparing calculated p vals to provided (or hand calculated) ones. Line is x=y.
+## what didn't parse
 
-These look pretty reasonable. Lots on the line and others is places were <.001's happened.
-
-It may be worth checking points that are above the line.
+Check that nothing that has a stat input and doesn't get an ES out.
 
@@
 
-ggplot(test, aes(x=target_pvalue, y=target_p_calc))+geom_point()+geom_abline(slope=1,intercept=0)+
-  scale_x_log10()+scale_y_log10()
+test |> filter(is.na(target_ES)) |> filter(!is.na(target_raw_stat)) |>  pull(target_raw_stat)
 
-ggplot(test, aes(x=replication_pvalue, y=rep_p_calc))+geom_point()+geom_abline(slope=1,intercept=0)+scale_x_log10()+scale_y_log10()
-
+test |> filter(is.na(rep_ES)) |> filter(!is.na(replication_raw_stat)) |> pull(replication_raw_stat)
 ```
 
-## Compare ES
-
-Comparing calculated ES to original (or hand calculated) ES. All converted to SMD.
-
-Note: black line is y=x, red line is y=2x. Things on y=2x probably had issues where one of the tests calculated it as (within|between) and the other did it the other way.
-
-```{r}
-
-test |> 
-  ggplot(aes(x=d_fill_target, y=target_d_calc))+geom_point()+geom_abline(slope=1,intercept=0)+geom_abline(slope=2,intercept=0, color="red")+coord_cartesian(xlim=c(0,5),ylim=c(0,5))+geom_abline(slope=.5,intercept=0, color="red")
-
-test |> 
-  ggplot(aes(x=d_fill_rep, y=rep_d_calc))+geom_point()+geom_abline(slope=1,intercept=0)+geom_abline(slope=2,intercept=0, color="red")+geom_abline(slope=.5,intercept=0, color="red")
-
-```
-
-Where there's a difference, I could check whether it's being compared to something *I* calculated versus something that an original paper or students paper calculated?
-Except that there's sources for errors in any of those.
-Ones where we get an off  by two error -- should I double check within-betweeness for the test?
--->
-## what didn't parse
-
-these are ones where we did not get a non-NA effect size. Could be due to formulas being incomplete, or missing information.
-
-note that we also aren't including the betas where we know we can't get effect size, but we'll still get porig and predInt.
-
-```{r}
-
-test |> filter(is.na(target_d_calc)&is.na(target_ES)) |> filter(!is.na(target_raw_stat)) |>  pull(target_raw_stat)
-
-test |> filter(is.na(rep_d_calc)&is.na(rep_ES)) |> filter(!is.na(replication_raw_stat)) |> pull(replication_raw_stat)
-```
-
-<!--
-## how are the df's lining up with sample size?
-
-We can try to back out effective sample size from the df's.
-Note that we don't always expect them to agree (Welch's t test, repeated measures, comparisons only on a sample), but still useful to look at.
-
-There's a lot of off by 1 or 2 things, which I'm unsure what to make of. (As much as possible both sample size and test stats are taken from the papers directly)
-
-```{r}
- test |> filter(!is.na(target_N_calc)) |> select(target_N_calc, target_N, target_raw_stat, within_between, target_lastauthor_year) |>
-  mutate(diff=target_N_calc-target_N) |> 
-  ggplot(aes(x=target_N, y=target_N_calc, color=(target_N==target_N_calc)))+geom_point()+geom_abline(slope=1, intercept=0)+scale_y_log10()+scale_x_log10()+scale_color_manual(values=c("TRUE"="black","FALSE"="red"))
-
- test |> filter(!is.na(rep_N_calc)) |> select(rep_N_calc, replication_N, replication_raw_stat, within_between, target_lastauthor_year) |> mutate(diff=rep_N_calc-replication_N) |> 
-   ggplot(aes(x=replication_N, y=rep_N_calc, color=(replication_N==rep_N_calc)))+geom_point()+geom_abline(slope=1, intercept=0)+scale_y_log10()+scale_x_log10()+scale_color_manual(values=c("TRUE"="black","FALSE"="red"))
-
-```
--->
 # PredInt and P_orig
@@
 d_es_predInt <- d_es |> 
+  rowwise() |> 
          mutate(
@@
 
+# viz SMD
 ```{r}
@@
 
-d_es_predInt |> mutate(p_sig=p_orig<.05) |> ggplot(aes(x=target_d_calc, y=rep_d_calc, color=p_sig))+
-  geom_point()+
-  coord_cartesian(xlim=c(0,2), ylim=c(-1,3))+
-  geom_abline(slope=1, intercept=0)+
-  geom_hline(yintercept=0)+
-  scale_color_viridis(discrete=T, direction=-1)+
-  labs(color="P_orig<.05", x="Original SMD", y="Replication SMD")
-
 d_es_predInt |> ggplot(aes(x=target_d_calc, y=rep_d_calc, color=predInt))+
@@
 
-# d_es_predInt |> ggplot(aes(x=replicated_report_code, y=p_orig))+geom_jitter(height=0, alpha=.5)+
-#   #scale_y_log10()+
-#   geom_hline(yintercept=.05)
-# 
-# d_es_predInt |> ggplot(aes(x=replicated_report_code, y=predInt))+geom_jitter(alpha=.5)
-```
-
-# Prelim analysis -- Correlation between ES
-
-There's that one ling paper with ES of 10+...
-
-Might want to just hide that point or something instead...
-
-Could weight by precision or something
-
-```{r}
-
-d_es |> ggplot(aes(x=target_d_calc, y=rep_d_calc, color=as.factor(replicated_report_code)))+
+d_es_predInt |> ggplot(aes(x=target_d_calc, y=rep_d_calc, color=sub_rep))+
   geom_point()+
-  #coord_cartesian(xlim=c(0,5), ylim=c(-1,5))+
+  coord_cartesian(xlim=c(0,2), ylim=c(-1,3))+
   geom_abline(slope=1, intercept=0)+
   geom_hline(yintercept=0)+
-  scale_color_viridis(discrete=T, direction=-1)
+  scale_color_viridis(discrete=F, direction=-1)+
+  labs(color="subrep", x="Original SMD", y="Replication SMD")
 
-d_es |> ggplot(aes(x=target_d_calc, y=rep_d_calc, color=as.factor(replicated_report_code)))+
+```
+# viz ES any scale 
+```{r}
+library(ggstance)
+d_es_predInt |> ggplot(aes(x=target_ES, 
+                           xmin=target_ES-target_SE*1.96,
+                           xmax=target_ES+target_SE*1.96, 
+                           y=rep_ES,
+                           ymin=rep_ES-rep_SE*1.96,
+                           ymax=rep_ES+rep_SE*1.96,
+                           color=p_orig))+
+  geom_linerange(alpha=.5)+
+  geom_linerangeh(alpha=.5)+
     geom_point()+
-  coord_cartesian(xlim=c(0,5), ylim=c(-1,4))+
+  coord_cartesian(xlim=c(-1,12), ylim=c(-1,12))+
+  geom_abline(slope=1, intercept=0)+
+  geom_hline(yintercept=0)+
+  scale_color_viridis(discrete=F, direction=-1)+
+  labs(color="p_orig", x="Original ES", y="Replication ES")
+
+d_es_predInt |> ggplot(aes(x=target_ES, 
+                           xmin=target_ES-target_SE*1.96,
+                           xmax=target_ES+target_SE*1.96, 
+                           y=rep_ES,
+                           ymin=rep_ES-rep_SE*1.96,
+                           ymax=rep_ES+rep_SE*1.96,
+                           color=p_orig))+
+  geom_linerange(alpha=.5)+
+  geom_linerangeh(alpha=.5)+
+    geom_point()+
+  coord_cartesian(xlim=c(-1,2), ylim=c(-1,2))+
+  geom_abline(slope=1, intercept=0)+
+  geom_hline(yintercept=0)+
+  scale_color_viridis(discrete=F, direction=-1)+
+  labs(color="p_orig", x="Original ES", y="Replication ES")
+
+d_es_predInt |> ggplot(aes(x=target_ES, 
+                           xmin=target_ES-target_SE*1.96,
+                           xmax=target_ES+target_SE*1.96, 
+                           y=rep_ES,
+                           ymin=rep_ES-rep_SE*1.96,
+                           ymax=rep_ES+rep_SE*1.96,
+                           color=predInt))+
+  geom_linerange(alpha=.5)+
+  geom_linerangeh(alpha=.5)+
+    geom_point()+
+  coord_cartesian(xlim=c(-1,12), ylim=c(-1,12))+
   geom_abline(slope=1, intercept=0)+
@@
   scale_color_viridis(discrete=T, direction=-1)+
-  labs(color="Replicated?", x="Original SMD", y="Replication SMD")
+  labs(color="predInt", x="Original ES", y="Replication ES")
+
+d_es_predInt |> ggplot(aes(x=target_ES, 
+                           xmin=target_ES-target_SE*1.96,
+                           xmax=target_ES+target_SE*1.96, 
+                           y=rep_ES,
+                           ymin=rep_ES-rep_SE*1.96,
+                           ymax=rep_ES+rep_SE*1.96,
+                           color=predInt))+
+  geom_linerange(alpha=.5)+
+  geom_linerangeh(alpha=.5)+
+    geom_point()+
+  coord_cartesian(xlim=c(-1,2), ylim=c(-1,2))+
+  geom_abline(slope=1, intercept=0)+
+  geom_hline(yintercept=0)+
+  scale_color_viridis(discrete=T, direction=-1)+
+  labs(color="predInt", x="Original ES", y="Replication ES")
+
+d_es_predInt |> ggplot(aes(x=target_ES, 
+                           xmin=target_ES-target_SE*1.96,
+                           xmax=target_ES+target_SE*1.96, 
+                           y=rep_ES,
+                           ymin=rep_ES-rep_SE*1.96,
+                           ymax=rep_ES+rep_SE*1.96,
+                           color=sub_rep))+
+  geom_linerange(alpha=.5)+
+  geom_linerangeh(alpha=.5)+
+    geom_point()+
+  coord_cartesian(xlim=c(-1,12), ylim=c(-1,12))+
+  geom_abline(slope=1, intercept=0)+
+  geom_hline(yintercept=0)+
+  scale_color_viridis(discrete=F, direction=-1)+
+  labs(color="sub rep", x="Original ES", y="Replication ES")
+
+d_es_predInt |> ggplot(aes(x=target_ES, 
+                           xmin=target_ES-target_SE*1.96,
+                           xmax=target_ES+target_SE*1.96, 
+                           y=rep_ES,
+                           ymin=rep_ES-rep_SE*1.96,
+                           ymax=rep_ES+rep_SE*1.96,
+                           color=sub_rep))+
+  geom_linerange(alpha=.5)+
+  geom_linerangeh(alpha=.5)+
+    geom_point()+
+  coord_cartesian(xlim=c(-1,2), ylim=c(-1,2))+
+  geom_abline(slope=1, intercept=0)+
+  geom_hline(yintercept=0)+
+  scale_color_viridis(discrete=F, direction=-1)+
+  labs(color="sub rep", x="Original ES", y="Replication ES")
 ```
@@
 
-message("number of NAs per column")
-
 d_check_nas <- d_es_predInt |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> ungroup() |>
-    select(target_lastauthor_year, status, academic_year, subfield, target_year,
+    select(include, target_lastauthor_year, status, academic_year, subfield, target_year,
            stanford_internal,open_data, open_materials, target_on_turk,
@@
 
-d_check_nas |> summarize(across(everything(),~sum(is.na(.)))) |>
-pivot_longer(everything()) |>
-  arrange((value)) |>
-  filter(value!=0)
+message("number of rows for subjective w/ demographic/experimental")
+
+message("expected")
+d_check_nas |> filter(include %in% c("stats", "pred_int", "exp")) |> nrow()
+message("actual")
+
+d_check_nas |> filter(include %in% c("stats", "pred_int", "exp")) |>
+  select(target_lastauthor_year, status, academic_year,  target_year,
+                      sub_rep, subfield,
+           stanford_internal,open_data, open_materials, target_on_turk,
+           replication_on_turk, within_between, single_vignette, repeated_measure,
+           target_N, replication_N) |> filter(across(everything(), ~!is.na(.))) |> nrow()
+
+message("number of rows for predInt/p_orig w/ demographic/experimental")
+message("expected")
+d_check_nas |> filter(include %in% c("stats", "pred_int")) |> nrow()
+message("actual")
+
+d_check_nas |> filter(include %in% c("stats", "pred_int")) |>  select(target_lastauthor_year, status, academic_year, target_year,
+                      sub_rep, subfield,
+           stanford_internal,open_data, open_materials, target_on_turk,
+           replication_on_turk, within_between, single_vignette, repeated_measure,
+           target_N, replication_N, predInt, p_orig) |> 
+ # filter(if_any(everything(), ~is.na(.)))
+  filter(across(everything(), ~!is.na(.))) |> nrow()
 
@@
 
-d_check_nas |> filter(across(everything(), ~!is.na(.))) |> nrow()
+message("expected")
+d_check_nas |> filter(include %in% c("stats")) |> nrow()
+message("actual")
 
-message("number of rows for subjective w/ demographic/experimental")
-
-d_check_nas |> select(target_lastauthor_year, status, academic_year,  target_year,
-                      sub_rep, subfield,
-           stanford_internal,open_data, open_materials, target_on_turk,
-           replication_on_turk, within_between, single_vignette, repeated_measure,
-           target_N, replication_N) |> filter(if_any(everything(), ~is.na(.))) #|> nrow()
-
-message("number of rows for predInt/p_orig w/ demographic/experimental")
-
-d_check_nas |> select(target_lastauthor_year, status, academic_year, target_year,
-                      sub_rep, subfield,
-           stanford_internal,open_data, open_materials, target_on_turk,
-           replication_on_turk, within_between, single_vignette, repeated_measure,
-           target_N, replication_N, predInt, p_orig) |>  filter(across(everything(), ~!is.na(.))) |> nrow()
-```
-
-```{r}
-# papers where we don't have everything
-
-#d_check_nas |> filter(if_any(everything(), ~is.na(.)))
-
-#d_check_nas |> filter(across(everything(), ~!is.na(.)))
-
-# d_check_nas  |> select(target_lastauthor_year, status, academic_year, target_year,
-#            stanford_internal,open_data, open_materials, target_on_turk,
-#            replication_on_turk, within_between, single_vignette, repeated_measure,
-#            target_N, replication_N, predInt, p_orig) |>  filter(if_any(everything(), ~is.na(.)))
+d_check_nas |> filter(include %in% c("stats")) |> filter(across(everything(), ~!is.na(.))) |> nrow()
 ```

### 2023-03-01 code/process.Rmd
add tier1model

@@
   predInt=as.numeric(predInt)) |> 
-  select(target_lastauthor_year, academic_year, subfield, 
+  select(include, target_lastauthor_year, academic_year, subfield, 
          pub_year, log_p, log_sample, log_ratio_ss, change_platform, target_d_calc,
@@
 ```{r}
-data_tier1 <- z_data |> select(academic_year, sub_rep, 
-                               z_pub_year, subfield, open_data, open_mat, stanford, change_platform, z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials) |> filter(across(everything(), ~!is.na(.)))
+data_tier1 <- z_data |> filter(include %in% c("stats", "exp", "pred_int")) |>
+  mutate(sub_rep=sub_rep*4+1) |>  #remap to 1-5 scale
+select(academic_year, sub_rep, 
+                               z_pub_year, subfield, open_data, open_mat, stanford, change_platform, z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials)
 
@@
 ```{r}
-data_tier2 <- z_data |> select(academic_year, sub_rep, 
+data_tier2 <- z_data |> filter(include %in% c("stats", "pred_int")) |>
+  select(academic_year, sub_rep, 
                                p_orig, predInt,
-                               z_pub_year, subfield, open_data, open_mat, stanford, change_platform, z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials) |> filter(across(everything(), ~!is.na(.)))
+                               z_pub_year, subfield, open_data, open_mat, stanford, change_platform, z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials) 
 ```
@@
 ```{r}
-data_tier3 <- z_data |> select(academic_year, sub_rep, 
+data_tier3 <- z_data |>  filter(include %in% c("stats")) |>
+  select(academic_year, sub_rep, 
                                p_orig, predInt,
                                z_target_d_calc, z_log_p, 
-                               z_pub_year, subfield, open_data, open_mat, stanford, change_platform, z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials) |> filter(across(everything(), ~!is.na(.)))
+                               z_pub_year, subfield, open_data, open_mat, stanford, change_platform, z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials) 
 ```
@@
                           z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
-                        #family=gaussian(link='logit'), # runs
-                        #family="cumulative", # runs on 1-5 data
-                        # family="zero_one_inflated_beta", runs, 
-                        # beta_binomial on 0-4 data
+                        family="cumulative", # runs on 1-5 data
                         data=data_tier1,
-                        #file=here(model_location, "tier1_subjective"),
+                        file=here(model_location, "tier1_subjective"),
                         prior=priors, 
-                        iter=100,
                         control=list(adapt_delta=.99),
-                        #backend="cmdstanr"
+                        backend="cmdstanr"
                         )

### 2023-03-02 code/process.Rmd
more exploring

@@
 
+## Exploring stuff for Tier 1
+
+```{r, eval=F}
+
+strong_priors <- c(set_prior("horseshoe(3, par_ratio=.33)", class="b"),
+            set_prior("normal(0,.5)", class="sd"),
+            set_prior("lkj(1)", class="cor"))
+tier1_subjective_strong_prior<- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
+                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
+                        family="cumulative", # runs on 1-5 data
+                        data=data_tier1,
+                        file=here(model_location, "tier1_subjective_prior"),
+                        prior=strong_priors, 
+                        control=list(adapt_delta=.99),
+                        backend="cmdstanr"
+                        )
+```
+
+```{r, eval=F}
+
+strong_priors_no_ranef <- c(set_prior("horseshoe(3, par_ratio=.33)", class="b"),
+            set_prior("normal(0,.5)", class="sd"))
+tier1_subjective_strong_prior<- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
+                          (1 | academic_year),
+                        family="cumulative", # runs on 1-5 data
+                        data=data_tier1,
+                        file=here(model_location, "tier1_subjective_prior_no_ranef"),
+                        prior=strong_priors_no_ranef, 
+                        control=list(adapt_delta=.99),
+                        backend="cmdstanr"
+                        )
+```
+
+```{r}
+
+# bad linear
+
+tier1_subjective_linear<- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
+                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
+                       # family="cumulative", # runs on 1-5 data
+                        data=data_tier1 |> mutate(sub_rep=(sub_rep-1)/4),
+                        file=here(model_location, "tier1_subjective_linear"),
+                        prior=strong_priors, 
+                        control=list(adapt_delta=.99),
+                        backend="cmdstanr"
+                        )
+
+tier1_subjective_linear2<- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
+                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
+                       # family="cumulative", # runs on 1-5 data
+                        data=data_tier1 |> mutate(sub_rep=(sub_rep-1)/4),
+                        file=here(model_location, "tier1_subjective_linear2"),
+                        prior=priors, 
+                        control=list(adapt_delta=.99),
+                        backend="cmdstanr"
+                        )
+```
+
+```{r}
+tier1_subjective_beta<- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
+                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
+                        family="beta", # runs on 1-5 data
+                        data=data_tier1 |> mutate(sub_rep=(sub_rep-1)/4*.98+.01),
+                        file=here(model_location, "tier1_subjective_beta"),
+                        prior=strong_priors, 
+                        control=list(adapt_delta=.99),
+                        backend="cmdstanr"
+                        )
+
+```
+
+### frequentism
+
+```{r}
+
+boring_logistic <- glm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials,
+                        family=binomial, 
+                        data=data_tier1 |> mutate(sub_rep=(sub_rep-1)/4),
+
+                        )
+library(glmnet)
+
+predictors <- data_tier1 |> select(z_pub_year, open_data, open_mat, stanford, change_platform, 
+                          z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials)
+
+yvals <- data_tier1 |> mutate(sub_rep=(sub_rep-1)/4) |> pull(sub_rep)
+lasso_linear <- cv.glmnet(predictors, yvals |> as.matrix(), 
+                        family="gaussian", alpha=1)
+
+lasso_linear2 <- glmnet(predictors, yvals, 
+                        family="gaussian", alpha=1)
+```
+
+## correlation
+
+```{r}
+library("lattice")
+dat <- data_tier1 |> mutate(is.cog=ifelse(subfield=="cognitive", 1,0),
+                            is.soc=ifelse(subfield=="social", 1,0),
+                            is.other=ifelse(subfield=="other-psych", 1,0),
+                            is.non=ifelse(subfield=="non-psych",1,0)) |> 
+  select(is.cog, is.soc, is.other, is.non, z_pub_year, open_data, open_mat, stanford, change_platform, 
+                          z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials)
+
+corr_mat <- round(cor(dat),2)
+
+# Install and load reshape2 package
+library(reshape2)
+
+# reduce the size of correlation matrix
+melted_corr_mat <- melt(corr_mat)
+# head(melted_corr_mat)
+
+# plotting the correlation heatmap
+library(ggplot2)
+ggplot(data = melted_corr_mat, aes(x=Var1, y=Var2,
+                                   fill=value)) + scale_fill_viridis()+
+geom_tile(alpha=.7)+theme(axis.text.x = element_text(angle = 40, vjust = 1, hjust=1))+geom_text(aes(label=value), size=3)
+
+corr_mat |> as_tibble(rownames="value2") |> pivot_longer(cols=!value2, names_to="value1", values_to = "corr") |> arrange(corr) |> filter(value2 <value1) |> View()
+
+corr_mat |> as_tibble(rownames="value2") |> pivot_longer(cols=!value2, names_to="value1", values_to = "corr") |> arrange(desc(corr)) |> filter(value2 <value1)
+
+```
+
+## Tier 2 and 3
 ```{r, eval=F}

### 2023-03-02 code/process.Rmd
minor updates

@@
 library(rstan)
+library(googledrive)
+library(glmnet)
 
@@
 
+Download
+
 ```{r, eval=F}
-library(googledrive)
-
 f <- googledrive::as_dribble("https://docs.google.com/spreadsheets/d/1UT6KLRujn6iEQ_s01_4yNfFYqc7hAWTpB-t9mdDp0O8/edit#gid=0")
-googledrive::drive_download(f, path="raw_data.xlsx", overwrite=T)
+googledrive::drive_download(f, path=here("data","raw_data.xlsx"), overwrite=T)
 
@@
 
+Read in cache.
+
 ```{r}
-d <- readxl::read_xlsx("raw_data.xlsx", sheet="aligned data", skip=1) |>
-
+d <- readxl::read_xlsx(here("data","raw_data.xlsx"), 
+                       sheet="aligned data", skip=1) |> 
   select(target_lastauthor_year, sensitivity, include,
@@
          within_between, single_vignette, repeated_measure,
-         target_N, target_test, target_raw_stat, target_pvalue, target_ES_type, target_ES_value,
-         same_dir,
-         replication_N, replication_test, replication_raw_stat, replication_pvalue, replication_ES_type, replication_ES_value,
-         replicated_instructor_code, replicated_report_code, adjudicated_replication_code)
+         target_N, target_test, target_raw_stat, target_pvalue, target_ES_type, 
+         target_ES_value, same_dir, replication_N, # replication_test
+         replication_raw_stat, replication_pvalue, replication_ES_type, 
+         replication_ES_value, replicated_instructor_code, replicated_report_code,
+         adjudicated_replication_code)
 
 ```
+
+Counts.
 
@@
 - "done" -- fully coded, can be used for whatever is specified in other column 
-
 - "ES_direction" -- we don't have the direction coded 
-
 - "ask" -- might be salvageable, but I have questions about coding
-
 - "unusable" -- got as far as I can, and it does not have complete descriptives
-
 - "missing" -- student didn't finish or we don't have write-up
-
 - "non-experiment" -- student replicated something that was not an experiment
-
 - "reproduction" -- student did a reproduction and not replication
@@
 d_val <- d |> filter(!status %in% c("missing", "non-experiment", "reproduction"))
-
 ```
 
-```{r}
-#helper function for pooling when needed
-pool_m_sd <- function(m1, sd1, n1, m2, sd2, n2){
-  m=(m1*n1+m2*n2)/(n1+n2)
-  var=(n1*(sd1**2+m1**2)+n2*(sd2**2+m2**2))/(n1+n2)-m**2
-  sd=sqrt(var)
-  return(c(m,sd))
-
-}
-```
 # Parsing
@@
 ```{r}
-# considered using the effectsize package but afaik we don't care about estimating CI's here and there were optim problems with that
-
-parse_t <- function(tval, within_between) {
-  df=str_extract(tval, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
-  val=str_extract(tval, "=.*") |> str_sub(2,-1) |> as.numeric() |> abs()
-  pval=pt(q=val, df=df, lower.tail=FALSE)*2
-  d_calc=NA
-  N_from_df=NA
-  if(within_between=="between"){
-    d_calc=2*val/(sqrt(df+2)) # this is a simplification for equal groups
-    N_from_df=df+2 # between so add 2
-  }
-  else{
-    d_calc=val/sqrt(df+1)
-    N_from_df=df+1
-  }
-  se=4/N_from_df+d_calc**2/(2*N_from_df)
-  return(data.frame("df_1"=NA, "df_2"=df,"tstat"=val, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df, "ES"=d_calc, "SE"=se))
-}
+source(here("code","helper","parse_stats.R"))
 ```
@@
 ```{r}
-parse_f <- function(fval, within_between){
-  df_1 =str_extract(fval, "\\(.*,") |> str_sub(2,-2) |> as.numeric()
-  df_2 =str_extract(fval, ",.*\\)") |> str_sub(2,-2) |> as.numeric()
-  val=str_extract(fval, "=.*") |> str_sub(2,-1) |> as.numeric() |> abs()
-  pval=pf(q=val, df1=df_1, df2=df_2, lower.tail=FALSE)
-  d_calc=NA
-  N_from_df=df_1+df_2+1
-  if(!is.na(df_1)&&df_1==1){
-    if(within_between=="between"){
-      d_calc=2*sqrt(val)/sqrt(N_from_df) # if there's just two groups, then F=t**2 and we can use the t-test thingy
-    }
-    else{
-      d_calc=sqrt(val)/sqrt(df_2)
-    }
-   se=4/N_from_df+d_calc**2/(2*N_from_df)
-  }
-  else if(!is.na(df_1)){
-    d_calc=NA
-    se=NA
-  }
-
-  return(data.frame("df_1"=df_1,"df_2"=df_2,"tstat"=NA, "fstat"=val, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df, "ES"=d_calc, "SE"=se))
-}
-```
-
-```{r}
-# for comparison between proportions 
-#ex <- "prob: 13 / 14 , 2 / 14"
-parse_prop <- function(propval){
-  val <- str_extract_all(propval, "[0-9]+")[[1]]
-  num1 <- val[1] |> as.numeric()
-  den1 <- val[2] |> as.numeric()
-  num2 <- val[3] |> as.numeric()
-  den2 <- val[4] |> as.numeric()
-  est1 <- num1/den1
-  est1_var <- est1*(1-est1)/den1
-  est2 <- num2/den2
-  est2_var <- est2*(1-est2)/den2
-  diff <- est1-est2
-  diff_var <- est1_var+est2_var
-  return(data.frame("df_1"=NA, "df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA, "ES"=diff, "SE"=sqrt(diff_var)))
-}
-#parse_prop(ex)
-
-```
-
-```{r}
-# for one proportion
-#ex <- "raw prop : 10 / 18"
-parse_raw_prop <- function(propval){
-  val <- str_extract_all(propval, "[0-9]+")[[1]]
-  num1 <- val[1] |> as.numeric()
-  den1 <- val[2] |> as.numeric()
-  est1 <- num1/den1
-  est1_var <- est1*(1-est1)/den1
-   return(data.frame("df_1"=NA, "df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA, "ES"=est1, "SE"=sqrt(est1_var)))
-}
-#parse_raw_prop(ex)
-```
-
-```{r}
-parse_mean_ci <- function(mci,within_between,n){
-  # parsing 
-  cond1=str_extract(mci, "m1.*\\],")
-  cond2=str_extract(mci, "m2.*\\]")
-  m1=str_extract(cond1, "m1=.*\\[") |> str_sub(4,-2) |> as.numeric()
-  m2=str_extract(cond2, "m2=.*\\[") |> str_sub(4,-2) |> as.numeric()
-  low1=str_extract(cond1, "\\[.*,.") |> str_sub(2,-3) |> as.numeric()
-  low2=str_extract(cond2, "\\[.*,") |> str_sub(2,-2) |> as.numeric()
-  high1=str_extract(cond1, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
-  high2=str_extract(cond2, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
-  # calculations 
-  se1=high1-low1/(2*1.96)
-  se2=high2-low2/(2*1.96)
-  per_group_n=ifelse(within_between=="within",n, n/2)
-  sd1=se1*sqrt(per_group_n-1) # assume equal groups
-  sd2=se2*sqrt(per_group_n-1)
-  sd_pool=sqrt((sd1**2+sd2**2)/2) # assume equal groups
-  se_pool=sd_pool/sqrt(n-1)
-  d_calc=abs(m1-m2/sd_pool) # note we force all positive and then fix later 
-  tval=(m1-m2)/se_pool |> abs()
-  df=ifelse(within_between=="within", n-1, n-2)
-  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
-  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=m1-m2, "SE"=se_pool))
-}
-```
-
-```{r}
-parse_mean_sd <- function(msd,within_between,n){
-  cond1=str_extract(msd, "m1.*\\),")
-  cond2=str_extract(msd, "m2.*\\)")
-  m1=str_extract(cond1, "m1=.*\\(") |> str_sub(4,-2) |> as.numeric()
-  m2=str_extract(cond2, "m2=.*\\(") |> str_sub(4,-2) |> as.numeric()
-  sd1=str_extract(cond1, "\\(.*\\),") |> str_sub(2,-3) |> as.numeric()
-  sd2=str_extract(cond2, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
-  #
-  sd_pool=sqrt((sd1**2+sd2**2)/2) # assume equal groups
-  se_pool=sd_pool/sqrt(n-1)
-  d_calc=abs(m1-m2/sd_pool) # note we force all positive and then fix later 
-  tval=(m1-m2)/se_pool |> abs()
-  df=ifelse(within_between=="within", n-1, n-2)
-  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
-  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=m1-m2, "SE"=se_pool))
-}
-
-```
-
-```{r}
-parse_mean_se <- function(mse,within_between,n){
-  cond1=str_extract(mse, "m1.*\\),")
-  cond2=str_extract(mse, "m2.*\\)")
-  m1=str_extract(cond1, "m1=.*\\(") |> str_sub(4,-2) |> as.numeric()
-  m2=str_extract(cond2, "m2=.*\\(") |> str_sub(4,-2) |> as.numeric()
-  se1=str_extract(cond1, "\\(.*\\),") |> str_sub(2,-3) |> as.numeric()
-  se2=str_extract(cond2, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
-
-  per_group_n=ifelse(within_between=="within",n, n/2)
-  sd1=se1*sqrt(per_group_n-1) # assume equal groups
-  sd2=se2*sqrt(per_group_n-1)
-  sd_pool=sqrt((sd1**2+sd2**2)/2) # assume equal groups
-  se_pool=sd_pool/sqrt(n-1)
-  d_calc=abs(m1-m2/sd_pool) # note we force all positive and then fix later 
-  tval=(m1-m2)/se_pool |> abs()
-  df=ifelse(within_between=="within", n-1, n-2)
-  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
-  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=m1-m2, "SE"=se_pool))
-}
-
-```
-
-```{r}
-
-parse_beta_se <- function(raw_stat){
-    beta=str_extract(raw_stat, "b=.*\\(") |> str_sub(3,-2) |> as.numeric()
-    se=str_extract(raw_stat, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
-    #zval=beta/se
-    #pval=2*pnorm(zval, lower.tail=F)
-return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA, "ES"=beta, "SE"=se))
-}
-
-```
-
-```{r}
-
-parse_beta_ci <- function(raw_stat){
-  beta=str_extract(raw_stat, "b=.*\\[") |> str_sub(3,-2) |> as.numeric()
-  low=str_extract(raw_stat, "\\[.*,") |> str_sub(2,-2) |> as.numeric()
-  high=str_extract(raw_stat, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
-  se=high-low/(2*1.96)
- #zval=beta/se
-    #pval=2*pnorm(zval, lower.tail=F)
-  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA, "ES"=beta, "SE"=se))
-}
-
-#this is just to deal with yang2018 where we have d's given and bci
-#ex <- "d: 1.40 ; bci: b=1.72 [1.44, 2.00]"
-parse_dbci <- function(raw_stat){
-  bci = str_extract(raw_stat, ";.*") |> str_sub(2,-1)
-  beta=str_extract(bci, "b=.*\\[") |> str_sub(3,-2) |> as.numeric()
-  low=str_extract(bci, "\\[.*,") |> str_sub(2,-2) |> as.numeric()
-  high=str_extract(bci, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
-  se=high-low/(2*1.96)
-
-  dval = str_extract(raw_stat, ".*;") |> str_sub(3,-2) |> as.numeric()
-  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=dval, "N_calc"=NA, "ES"=beta, "SE"=se))
-}
-#parse_dbci(ex)
-
-```
-
-```{r}
-
-do_blanks <- function(){
-  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA, "ES"=NA, "SE"=NA))
-}
-do_parsing=function(raw_stat, within_between,n){
-  if (is.na(raw_stat)) {return (do_blanks())}
-  if (str_sub(raw_stat,1,1)=="t"){return(parse_t(raw_stat, within_between))}
-  if (str_sub(raw_stat,1,1)=="F"){return(parse_f(raw_stat, within_between))}
-  if (str_sub(raw_stat,1,4)=="prop"){return(parse_prop(raw_stat))}
-  if (str_sub(raw_stat,1,7)=="rawprop"){return(parse_raw_prop(raw_stat))}
-  if (str_sub(raw_stat, 1,3)=="MCI"){return(parse_mean_ci(raw_stat, within_between,n))}
-  if (str_sub(raw_stat, 1,3)=="MSD"){return(parse_mean_sd(raw_stat, within_between,n))}
-  if (str_sub(raw_stat, 1,3)=="MSE"){return(parse_mean_se(raw_stat, within_between,n))}
-  if (str_sub(raw_stat, 1,8)=="wilcoxon"){return(parse_wilcoxon(raw_stat))}
-  if (str_sub(raw_stat, 1,3)=="bse"){return(parse_beta_se(raw_stat))}
-  if (str_sub(raw_stat, 1,3)=="bci"){return(parse_beta_ci(raw_stat))}
-  if (str_sub(raw_stat, 1,1)=="d"){return(parse_dbci(raw_stat))}
-
-  return (do_blanks())
-}
-```
-
-```{r}
-
 test <- d_val |> 
@@
   rowwise()
-
 ```
@@
 ```{r}
-library(metafor)
-
-d_es <-  test |> 
-  mutate(target_d_calc=abs(target_d_calc),
-         target_ES=abs(target_ES),
-         rep_d_calc=case_when(
-           same_dir=="yes" ~ abs(rep_d_calc),
-           same_dir=="no" ~-abs(rep_d_calc),
-           T ~ as.numeric(NA)
-          ),
-         rep_ES=case_when(
-           same_dir=="yes" ~ abs(rep_ES),
-           same_dir=="no" ~-abs(rep_ES),
-           T ~ as.numeric(NA)
-         ))
-
+source(here("code","helper","stats.R"))
 ```
 
+Compute prediction intervals and p_orig.
+
 ```{r}
-do_pred_int <- function(target_ES, target_SE, rep_ES, rep_SE){
-  if(!is.na(target_ES)&!is.na(rep_ES)){
-    return(Replicate::pred_int(target_ES, target_SE**2, rep_ES, rep_SE**2)$rep.inside)
-  }
-  return(NA)
-}
-
-do_p_orig <- function(target_ES, target_SE, rep_ES, rep_SE){
-  if(!is.na(target_ES)&!is.na(rep_ES)){
-    return(Replicate::p_orig(target_ES, target_SE**2,rep_ES, t2=0, rep_SE**2))
-  }
-  return(NA)
-}
-
-do_subjective_rep <- function(replicated_instructor_code, replicated_report_code, adjudicated_replication_code){
-  if (is.na(replicated_instructor_code)){return(as.numeric(NA))}
-  if (is.na(replicated_report_code)){return(as.numeric(NA))}
-  if (replicated_instructor_code==replicated_report_code){ return(replicated_instructor_code)}
-  if (!is.na(adjudicated_replication_code)){return (adjudicated_replication_code)}
-  return(as.numeric(NA))
-}
 d_es_predInt <- d_es |> 
   rowwise() |> 
-         mutate(
-           predInt=do_pred_int(target_ES, target_SE, rep_ES, rep_SE),
-           p_orig=do_p_orig(target_ES, target_SE, rep_ES, rep_SE),
-           sub_rep= do_subjective_rep(replicated_instructor_code, replicated_report_code, adjudicated_replication_code))
-
+  mutate(predInt = do_pred_int(target_ES, target_SE, rep_ES, rep_SE),
+         p_orig = do_p_orig(target_ES, target_SE, rep_ES, rep_SE),
+         sub_rep = do_subjective_rep(replicated_instructor_code, 
+                                     replicated_report_code, 
+                                     adjudicated_replication_code))
 ```
@@
 # viz SMD
+
+First pass plots.
+
 ```{r}
-
 d_es_predInt |> ggplot(aes(x=target_d_calc, y=rep_d_calc, color=p_orig))+
@@
   labs(color="rep in predInt", x="Original SMD", y="Replication SMD")
+```
 
-d_es_predInt |> ggplot(aes(x=target_d_calc, y=rep_d_calc, color=sub_rep))+
-  geom_point()+
-  coord_cartesian(xlim=c(0,2), ylim=c(-1,3))+
-  geom_abline(slope=1, intercept=0)+
-  geom_hline(yintercept=0)+
-  scale_color_viridis(discrete=F, direction=-1)+
-  labs(color="subrep", x="Original SMD", y="Replication SMD")
+Working more on the visualization with subjective rep status.
 
+```{r}
+d_es_predInt |> 
+  filter(target_d_calc < 5, rep_d_calc < 5) |>
+  ggplot(aes(x=target_d_calc, y=rep_d_calc, color=sub_rep))+
+  geom_point() +
+  geom_abline(slope=1, intercept=0, lty = 2)+
+  geom_smooth(method = "lm") + 
+  geom_hline(yintercept = 0, lty = 2)+
+  scale_color_viridis(discrete=F, direction = -1, 
+                      name = "Subjective Replication Success")+
+  labs(color="subrep", x="Original SMD", y="Replication SMD") + 
+  theme(legend.position = "bottom")
 ```
-# viz ES any scale 
+
 ```{r}
@@
                    set_prior("lkj(1)", class="cor"))
-tier1_subjective_strong_prior<- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
-                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
+
+tier1_subjective_strong_prior <- brm(sub_rep ~ z_pub_year +
+                                       subfield + open_data +  
+                                       open_mat + stanford + change_platform + 
+                                       z_log_ratio_ss + is_within + 
+                                       single_vignette + z_log_sample + 
+                                       z_log_trials + 
                                        (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
@@
                                      prior=strong_priors, 
-                        control=list(adapt_delta=.99),
-                        backend="cmdstanr"
-                        )
-```
-
-```{r, eval=F}
-
-strong_priors_no_ranef <- c(set_prior("horseshoe(3, par_ratio=.33)", class="b"),
-            set_prior("normal(0,.5)", class="sd"))
-tier1_subjective_strong_prior<- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
-                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
-                          (1 | academic_year),
-                        family="cumulative", # runs on 1-5 data
-                        data=data_tier1,
-                        file=here(model_location, "tier1_subjective_prior_no_ranef"),
-                        prior=strong_priors_no_ranef, 
                                      control=list(adapt_delta=.99),
@@
 )
-library(glmnet)
+```
 
+regularized
+```{r}
 predictors <- data_tier1 |> select(z_pub_year, open_data, open_mat, stanford, change_platform, 
@@
 ```
+
+# Random exploratory analyses
+
+## Correlations
+
+```{r}
+sub_cor <- function(var, stat = "estimate") {
+  if (stat == "estimate") {
+    cor.test(data_tier1$sub_rep, pull(data_tier1, {{var}}))$estimate
+  } else {
+    cor.test(data_tier1$sub_rep, pull(data_tier1, {{var}}))$p.value
+  }
+}
+
+preds <- c("z_pub_year", "open_data",  "open_mat", "stanford", "change_platform", 
+           "z_log_ratio_ss", "is_within", "single_vignette", "z_log_sample", 
+           "z_log_trials")
+
+cors <- tibble(preds = preds) |>
+  mutate(r = sapply(preds, function(x) sub_cor(x, stat = "estimate")),
+         p = sapply(preds, function(x) sub_cor(x, stat = "p")))
+
+knitr::kable(cors, digits = 3)
+```
+
+## Principal components
+
+Principal components are not very interpretable.
+
+```{r}
+pcs <- select(data_tier1, 
+              z_pub_year, open_data,  open_mat, stanford, change_platform, 
+              z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials) |>
+  princomp()
+
+summary(pcs)
+pcs$loadings
+plot(pcs)
+biplot(pcs)
+```
+
+## Model exploration
+
+```{r}
+mod <- lm(sub_rep ~ z_pub_year + subfield + open_data + open_mat + 
+            stanford + change_platform + 
+            z_log_ratio_ss + is_within + 
+            single_vignette + z_log_sample + z_log_trials,
+          data = data_tier1 )
+summary(mod)
+```
+
+Repeating regularized
+
+```{r}
+predictors <- data_tier1 |> 
+  select(z_pub_year, open_data, open_mat, stanford, change_platform, 
+         z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials) |>
+  as.data.frame() |>
+  as.matrix()
+
+lasso_linear <- cv.glmnet(predictors, data_tier1$sub_rep, 
+                          family="gaussian", alpha=1)
+
+coef(lasso_linear, s = "lambda.min")
+coef(lasso_linear, s = "lambda.1se")
+```
+
+## Bayesian tinkering
+
+Let's try super strong priors, consolidating a few very highly correlated variables.
+
+```{r}
+normal_priors <- c(set_prior("horseshoe(3)", class="b"),
+                   set_prior("normal(0,.5)", class="sd"))
+
+brm(sub_rep ~ z_pub_year + subfield + open_data + open_mat + stanford + change_platform + z_log_ratio_ss + is_within + single_vignette + z_log_sample +  z_log_trials + 
+      (1 | academic_year),
+    # family = "linear", # runs on 1-5 data
+    data = data_tier1,
+    prior = normal_priors, 
+    iter = 10000, warmup = 2000,
+    control = list(adapt_delta=.99),
+    backend = "cmdstanr")
+```
+
+And let's see if it's the link
+
+```{r}
+normal_priors <- c(set_prior("horseshoe(3)", class="b"),
+                   set_prior("normal(0,.5)", class="sd"))
+
+# make it in the .005 - .995 range
+data_tier1$sub_rep01 <- ((data_tier1$sub_rep-1)/5) * .99 + .005
+
+brm(sub_rep01 ~ z_pub_year + subfield + open_data + open_mat + stanford + change_platform + z_log_ratio_ss + is_within + single_vignette + z_log_sample +  z_log_trials + 
+      (1 | academic_year),
+    family = "beta", # runs on 1-5 data
+    data = data_tier1,
+    prior = normal_priors, 
+    iter = 10000, warmup = 2000,
+    control = list(adapt_delta=.99),
+    backend = "cmdstanr")
+```
+
+## Models of clusters of predictors
+
+```{r}
+mod <- lm(sub_rep ~ 
+            is_within + 
+            single_vignette +  z_log_trials,
+          data = data_tier1 )
+summary(mod)
+```

### 2023-03-02 code/helper/parse_stats.R

@@ -1,0 +1,197 @@
+# considered using the effectsize package but afaik we don't care about estimating CI's here and there were optim problems with that
+
+parse_t <- function(tval, within_between) {
+  df=str_extract(tval, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
+  val=str_extract(tval, "=.*") |> str_sub(2,-1) |> as.numeric() |> abs()
+  pval=pt(q=val, df=df, lower.tail=FALSE)*2
+  d_calc=NA
+  N_from_df=NA
+  if(within_between=="between"){
+    d_calc=2*val/(sqrt(df+2)) # this is a simplification for equal groups
+    N_from_df=df+2 # between so add 2
+  }
+  else{
+    d_calc=val/sqrt(df+1)
+    N_from_df=df+1
+  }
+  se=4/N_from_df+d_calc**2/(2*N_from_df)
+  return(data.frame("df_1"=NA, "df_2"=df,"tstat"=val, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df, "ES"=d_calc, "SE"=se))
+}
+
+parse_f <- function(fval, within_between){
+  df_1 =str_extract(fval, "\\(.*,") |> str_sub(2,-2) |> as.numeric()
+  df_2 =str_extract(fval, ",.*\\)") |> str_sub(2,-2) |> as.numeric()
+  val=str_extract(fval, "=.*") |> str_sub(2,-1) |> as.numeric() |> abs()
+  pval=pf(q=val, df1=df_1, df2=df_2, lower.tail=FALSE)
+  d_calc=NA
+  N_from_df=df_1+df_2+1
+  if(!is.na(df_1)&&df_1==1){
+    if(within_between=="between"){
+      d_calc=2*sqrt(val)/sqrt(N_from_df) # if there's just two groups, then F=t**2 and we can use the t-test thingy
+    }
+    else{
+      d_calc=sqrt(val)/sqrt(df_2)
+    }
+    se=4/N_from_df+d_calc**2/(2*N_from_df)
+  }
+  else if(!is.na(df_1)){
+    d_calc=NA
+    se=NA
+  }
+  
[…]

### 2023-03-02 code/helper/stats.R

@@ -1,0 +1,45 @@
+#helper function for pooling when needed
+pool_m_sd <- function(m1, sd1, n1, m2, sd2, n2){
+  m=(m1*n1+m2*n2)/(n1+n2)
+  var=(n1*(sd1**2+m1**2)+n2*(sd2**2+m2**2))/(n1+n2)-m**2
+  sd=sqrt(var)
+  return(c(m,sd))
+  
+}
+
+d_es <-  test |> 
+  mutate(target_d_calc=abs(target_d_calc),
+         target_ES=abs(target_ES),
+         rep_d_calc=case_when(
+           same_dir=="yes" ~ abs(rep_d_calc),
+           same_dir=="no" ~-abs(rep_d_calc),
+           T ~ as.numeric(NA)
+         ),
+         rep_ES=case_when(
+           same_dir=="yes" ~ abs(rep_ES),
+           same_dir=="no" ~-abs(rep_ES),
+           T ~ as.numeric(NA)
+         ))
+
+
+do_pred_int <- function(target_ES, target_SE, rep_ES, rep_SE){
+  if(!is.na(target_ES)&!is.na(rep_ES)){
+    return(Replicate::pred_int(target_ES, target_SE**2, rep_ES, rep_SE**2)$rep.inside)
+  }
+  return(NA)
+}
+
+do_p_orig <- function(target_ES, target_SE, rep_ES, rep_SE){
+  if(!is.na(target_ES)&!is.na(rep_ES)){
+    return(Replicate::p_orig(target_ES, target_SE**2,rep_ES, t2=0, rep_SE**2))
+  }
+  return(NA)
+}
+
+do_subjective_rep <- function(replicated_instructor_code, replicated_report_code, adjudicated_replication_code){
+  if (is.na(replicated_instructor_code)){return(as.numeric(NA))}
+  if (is.na(replicated_report_code)){return(as.numeric(NA))}
+  if (replicated_instructor_code==replicated_report_code){ return(replicated_instructor_code)}
+  if (!is.na(adjudicated_replication_code)){return (adjudicated_replication_code)}
+  return(as.numeric(NA))
+}

### 2023-03-06 code/process.Rmd
working on code

@@
          within_between, single_vignette, repeated_measure,
-         target_N, target_test, target_raw_stat, target_pvalue, target_ES_type, 
-         target_ES_value, same_dir, replication_N, # replication_test
-         replication_raw_stat, replication_pvalue, replication_ES_type, 
-         replication_ES_value, replicated_instructor_code, replicated_report_code,
+         target_N, target_raw_stat, same_dir, replication_N,
+         replication_raw_stat, replicated_instructor_code, replicated_report_code,
          adjudicated_replication_code)
@@
 
-test |> filter(is.na(target_ES)) |> filter(!is.na(target_raw_stat)) |>  pull(target_raw_stat)
+test |> filter(is.na(target_ES)) |> filter(!is.na(target_raw_stat)) |> select(target_lastauthor_year, target_raw_stat)
 
-test |> filter(is.na(rep_ES)) |> filter(!is.na(replication_raw_stat)) |> pull(replication_raw_stat)
+test |> filter(is.na(rep_ES)) |> filter(!is.na(replication_raw_stat)) |> select(target_lastauthor_year, replication_raw_stat)
+
 ```
@@
 ```{r}
+
+d_es <-  test |> 
+  mutate(target_d_calc=abs(target_d_calc),
+         target_ES=abs(target_ES),
+         rep_d_calc=case_when(
+           same_dir=="yes" ~ abs(rep_d_calc),
+           same_dir=="no" ~-abs(rep_d_calc),
+           T ~ as.numeric(NA)
+         ),
+         rep_ES=case_when(
+           same_dir=="yes" ~ abs(rep_ES),
+           same_dir=="no" ~-abs(rep_ES),
+           T ~ as.numeric(NA)
+         ))
+
 d_es_predInt <- d_es |> 
@@
   theme(legend.position = "bottom")
+
 ```
@@
 
-# Models
+# Pre-reg'd Models
 
@@
 
-```{r, eval=F}
+```{r, eval=T}
 tier1_subjective <- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
@@
 
-## Exploring stuff for Tier 1
-
-```{r, eval=F}
-
-strong_priors <- c(set_prior("horseshoe(3, par_ratio=.33)", class="b"),
-                   set_prior("normal(0,.5)", class="sd"),
-                   set_prior("lkj(1)", class="cor"))
-
-tier1_subjective_strong_prior <- brm(sub_rep ~ z_pub_year +
-                                       subfield + open_data +  
-                                       open_mat + stanford + change_platform + 
-                                       z_log_ratio_ss + is_within + 
-                                       single_vignette + z_log_sample + 
-                                       z_log_trials + 
-                                       (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
-                                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
-                                     family="cumulative", # runs on 1-5 data
-                                     data=data_tier1,
-                                     file=here(model_location, "tier1_subjective_prior"),
-                                     prior=strong_priors, 
-                                     control=list(adapt_delta=.99),
-                                     backend="cmdstanr"
-)
+```{r}
+library(tidybayes)
+tier1_subjective |> 
+gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |> 
+  ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
+  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI")+theme(axis.text=element_text(size=11))
 ```
 
-```{r}
-
-# bad linear
-
-tier1_subjective_linear<- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
-                                z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
-                                (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
-                                   z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
-                              # family="cumulative", # runs on 1-5 data
-                              data=data_tier1 |> mutate(sub_rep=(sub_rep-1)/4),
-                              file=here(model_location, "tier1_subjective_linear"),
-                              prior=strong_priors, 
-                              control=list(adapt_delta=.99),
-                              backend="cmdstanr"
-)
-
-tier1_subjective_linear2<- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
-                                 z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
-                                 (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
-                                    z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
-                               # family="cumulative", # runs on 1-5 data
-                               data=data_tier1 |> mutate(sub_rep=(sub_rep-1)/4),
-                               file=here(model_location, "tier1_subjective_linear2"),
-                               prior=priors, 
-                               control=list(adapt_delta=.99),
-                               backend="cmdstanr"
-)
-```
-
-```{r}
-tier1_subjective_beta<- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
-                              z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
-                              (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
-                                 z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
-                            family="beta", # runs on 1-5 data
-                            data=data_tier1 |> mutate(sub_rep=(sub_rep-1)/4*.98+.01),
-                            file=here(model_location, "tier1_subjective_beta"),
-                            prior=strong_priors, 
-                            control=list(adapt_delta=.99),
-                            backend="cmdstanr"
-)
-
-```
-
-### frequentism
-
-```{r}
-
-boring_logistic <- glm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
-                         z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials,
-                       family=binomial, 
-                       data=data_tier1 |> mutate(sub_rep=(sub_rep-1)/4),
-
-)
-```
-
-regularized
-```{r}
-predictors <- data_tier1 |> select(z_pub_year, open_data, open_mat, stanford, change_platform, 
-                                   z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials)
-
-yvals <- data_tier1 |> mutate(sub_rep=(sub_rep-1)/4) |> pull(sub_rep)
-lasso_linear <- cv.glmnet(predictors, yvals |> as.matrix(), 
-                          family="gaussian", alpha=1)
-
-lasso_linear2 <- glmnet(predictors, yvals, 
-                        family="gaussian", alpha=1)
-```
-
-## correlation
-
-```{r}
-library("lattice")
-dat <- data_tier1 |> mutate(is.cog=ifelse(subfield=="cognitive", 1,0),
-                            is.soc=ifelse(subfield=="social", 1,0),
-                            is.other=ifelse(subfield=="other-psych", 1,0),
-                            is.non=ifelse(subfield=="non-psych",1,0)) |> 
-  select(is.cog, is.soc, is.other, is.non, z_pub_year, open_data, open_mat, stanford, change_platform, 
-         z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials)
-
-corr_mat <- round(cor(dat),2)
-
-# Install and load reshape2 package
-library(reshape2)
-
-# reduce the size of correlation matrix
-melted_corr_mat <- melt(corr_mat)
-# head(melted_corr_mat)
-
-# plotting the correlation heatmap
-library(ggplot2)
-ggplot(data = melted_corr_mat, aes(x=Var1, y=Var2,
-                                   fill=value)) + scale_fill_viridis()+
-  geom_tile(alpha=.7)+theme(axis.text.x = element_text(angle = 40, vjust = 1, hjust=1))+geom_text(aes(label=value), size=3)
-
-corr_mat |> as_tibble(rownames="value2") |> pivot_longer(cols=!value2, names_to="value1", values_to = "corr") |> arrange(corr) |> filter(value2 <value1) |> View()
-
-corr_mat |> as_tibble(rownames="value2") |> pivot_longer(cols=!value2, names_to="value1", values_to = "corr") |> arrange(desc(corr)) |> filter(value2 <value1)
-
-```
-
-## Tier 2 and 3
 ```{r, eval=F}
@@
 
+## correlation
+
+```{r}
+library("lattice")
+dat <- data_tier1 |> mutate(is.cog=ifelse(subfield=="cognitive", 1,0),
+                            is.soc=ifelse(subfield=="social", 1,0),
+                            is.other=ifelse(subfield=="other-psych", 1,0),
+                            is.non=ifelse(subfield=="non-psych",1,0)) |> 
+  select(is.cog, is.soc, is.other, is.non,stanford, z_pub_year, open_data, open_mat,  change_platform, 
+         z_log_ratio_ss, z_log_sample, single_vignette, z_log_trials, is_within, )
+
+corr_mat <- round(cor(dat),2)
+
+# Install and load reshape2 package
+library(reshape2)
+
+# reduce the size of correlation matrix
+melted_corr_mat <-melt(corr_mat)
+# head(melted_corr_mat)
+
+# plotting the correlation heatmap
+library(ggplot2)
+ggplot(data = melted_corr_mat, aes(x=Var1, y=Var2,
+                                   fill=value)) + #scale_fill_viridis()+
+  scale_fill_gradient2(low="#440154",high="#FDE725FF")+
+  geom_tile(alpha=.7)+theme(axis.text.x = element_text(angle = 40, vjust = 1, hjust=1))+geom_text(aes(label=value), size=3)+
+  labs(x="", y="", fill="Correlation")
+
+#corr_mat |> as_tibble(rownames="value2") |> pivot_longer(cols=!value2, names_to="value1", values_to = "corr") |> arrange(corr) |> filter(value2 <value1) |> View()
+
+#corr_mat |> as_tibble(rownames="value2") |> pivot_longer(cols=!value2, names_to="value1", values_to = "corr") |> arrange(desc(corr)) |> filter(value2 <value1)
+
+```
+
+## other bayesian models
+
+```{r, eval=F}
+
+strong_priors <- c(set_prior("horseshoe(3, par_ratio=.33)", class="b"),
+                   set_prior("normal(0,.5)", class="sd"),
+                   set_prior("lkj(1)", class="cor"))
+
+tier1_subjective_strong_prior <- brm(sub_rep ~ z_pub_year +
+                                       subfield + open_data +  
+                                       open_mat + stanford + change_platform + 
+                                       z_log_ratio_ss + is_within + 
+                                       single_vignette + z_log_sample + 
+                                       z_log_trials + 
+                                       (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
+                                     family="cumulative", # runs on 1-5 data
+                                     data=data_tier1,
+                                     file=here(model_location, "tier1_subjective_prior"),
+                                     prior=strong_priors, 
+                                     control=list(adapt_delta=.99),
+                                     backend="cmdstanr"
+)
+```
+
+```{r, eval=F}
+
+# bad linear
+
+tier1_subjective_linear<- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                                z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
+                                (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                                   z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
+                              # family="cumulative", # runs on 1-5 data
+                              data=data_tier1 |> mutate(sub_rep=(sub_rep-1)/4),
+                              file=here(model_location, "tier1_subjective_linear"),
+                              prior=strong_priors, 
+                              control=list(adapt_delta=.99),
+                              backend="cmdstanr"
+)
+
+tier1_subjective_linear2<- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                                 z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
+                                 (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                                    z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
+                               # family="cumulative", # runs on 1-5 data
+                               data=data_tier1 |> mutate(sub_rep=(sub_rep-1)/4),
+                               file=here(model_location, "tier1_subjective_linear2"),
+                               prior=priors, 
+                               control=list(adapt_delta=.99),
+                               backend="cmdstanr"
+)
+```
+
+```{r, eval=F}
+tier1_subjective_beta<- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                              z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
+                              (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                                 z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
+                            family="beta", # runs on 1-5 data
+                            data=data_tier1 |> mutate(sub_rep=(sub_rep-1)/4*.98+.01),
+                            file=here(model_location, "tier1_subjective_beta"),
+                            prior=strong_priors, 
+                            control=list(adapt_delta=.99),
+                            backend="cmdstanr"
+)
+
+```
+
+## frequentism
+
+```{r}
+
+boring_logistic <- glm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                         z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials,
+                       family=binomial, 
+                       data=data_tier1 |> mutate(sub_rep=(sub_rep-1)/4),
+
+)
+```
+
+regularized
+```{r}
+predictors <- data_tier1 |> mutate(social=ifelse(subfield=="social", 1,0),other=ifelse(subfield=="other-psych",1,0), non=ifelse(subfield=="non-psych", 1,0)) |> 
+  select(z_pub_year, open_data, open_mat, stanford, change_platform, social, other, non, 
+                                   z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials) |> as.matrix()
+
+yvals <- data_tier1 |> mutate(sub_rep=(sub_rep-1)/4) |> pull(sub_rep)
+#lasso_linear <- cv.glmnet(predictors, yvals |> as.matrix(),       family="gaussian", alpha=1)
+
+lasso_linear2 <- glmnet(predictors, yvals, 
+                        family="gaussian", alpha=1)
+```
+
+```{r}
+library(ggrepel)
+library(ggthemes)
+to_plot <- lasso_linear2$beta |> as.matrix() |> as.tibble(rownames="var") |> pivot_longer(`s0`:`s71`) |> mutate(time=str_sub(name, 2,-1) |> as.numeric())
+
+ggplot(to_plot, aes(x=time, y=value, color=var, label=var))+geom_line()+geom_label_repel(data=to_plot |> filter(time==70), min.segment.length = 100, nudge_x = 10, na.rm = TRUE)+ theme(legend.position="none")+ scale_color_tableau("Classic 20")+
+  coord_cartesian(xlim=c(0,80), ylim=c(-.2, .3))+theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.ticks.x=element_blank())
+
+```
+
+regularized p_orig
+
+```{r}
+dat <- data_tier2 |> filter(!is.na(p_orig)) |>  mutate(social=ifelse(subfield=="social", 1,0),other=ifelse(subfield=="other-psych",1,0), non=ifelse(subfield=="non-psych", 1,0))
+predictors <- dat |> select(z_pub_year, open_data, open_mat, #stanford, 
+                            change_platform, social, non, other,
+                                   z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials) |> as.matrix()
+
+yvals <- dat|> pull(p_orig)
+
+lasso_linear_porig <- glmnet(predictors, yvals, 
+                        family="gaussian", alpha=1)
+
+yvals <- dat |> pull(predInt)
+
+lasso_linear_predint <- glmnet(predictors, yvals, 
+                        family="binomial", alpha=1)
+```
+
+```{r}
+to_plot <- lasso_linear_porig$beta |> as.matrix() |> as.tibble(rownames="var") |> pivot_longer(`s0`:`s72`) |> mutate(time=str_sub(name, 2,-1) |> as.numeric())
+
+ggplot(to_plot, aes(x=time, y=value, color=var, label=var))+geom_line()+geom_label_repel(data=to_plot |> filter(time==70), min.segment.length = 100, nudge_x = 10, na.rm = TRUE)+ theme(legend.position="none")+ scale_color_tableau("Classic 20")+
+  coord_cartesian(xlim=c(0,80), ylim=c(-.2, .3))+theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.ticks.x=element_blank())
+```
+
+```{r}
+to_plot <- lasso_linear_predint$beta |> as.matrix() |> as.tibble(rownames="var") |> pivot_longer(`s0`:`s58`) |> mutate(time=str_sub(name, 2,-1) |> as.numeric())
+
+ggplot(to_plot, aes(x=time, y=value, color=var, label=var))+geom_line()+geom_label_repel(data=to_plot |> filter(time==55), min.segment.length = 100, nudge_x = 10, na.rm = TRUE)+ theme(legend.position="none")+ scale_color_tableau("Classic 20")+
+  coord_cartesian(xlim=c(0,70))+theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.ticks.x=element_blank())
+
+```
+
 ## Correlations
@@
 
-```{r}
+```{r, eval=F}
 normal_priors <- c(set_prior("horseshoe(3)", class="b"),
@@
 ```
+
+## Individual predictor - outcome correlations
+
+### Sub_rep
+```{r}
+dat <- data_tier1 |> mutate(sub_rep=((sub_rep-1)/4) |> factor(levels=c("0","0.25", "0.5", "0.75", "1")))
+
+ggplot(dat, aes(x=sub_rep, fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(legend.position = "none")+labs(y="Count", x="Subjective Replication score")
+
+ggplot(dat, aes(x=subfield, fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
+
+dat |> mutate(open_mat=ifelse(open_mat, "Open materials", "No open materials"), open_data=ifelse(open_data, "Open data", "No open data")) |> ggplot( aes(x=open_data |> factor(), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+facet_wrap(.~open_mat)+theme(axis.title.x=element_blank())
+
+ ggplot(dat, aes(x=factor(stanford), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
+
+ggplot(dat, aes(x=factor(change_platform), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
+
+ggplot(dat, aes(x=ifelse(is_within, "Within", "Between"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(axis.title.x=element_blank())
+
+ggplot(dat, aes(x=ifelse(single_vignette, "1 vignette", "multiple vignettes"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(axis.title.x=element_blank())
+```
+
+```{r}
+# using d for model to get non-z-scored version
+ggplot(d_for_model, aes(x=pub_year, y=sub_rep, color=sub_rep))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()
+
+ggplot(d_for_model, aes(x=log_ratio_ss, y=log_sample, color=sub_rep))+geom_point()+scale_color_viridis()
+
+ggplot(d_for_model, aes(x=log_ratio_ss, y=sub_rep, color=sub_rep))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()
+
+ggplot(d_for_model, aes(x=log_sample, y=sub_rep, color=sub_rep))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()
+
+ggplot(d_for_model, aes(x=log_trials, y=sub_rep, color=sub_rep))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()
+
+```
+
+### Pred_int
+Note: predInt may not be reliably calculated in some cases. Dealing with numbers is hard!
+
+```{r}
+dat <- d_for_model |> filter(!is.na(predInt)) |>  mutate(predInt=predInt |> factor())
+
+ggplot(dat, aes(x=predInt, fill=predInt))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
+
+ggplot(dat, aes(x=subfield, fill=predInt))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
+
+ggplot(dat, aes(x=open_data |> factor(), fill=predInt))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+facet_wrap(.~str_c("open_mat ",open_mat))
+
+ggplot(dat, aes(x=factor(stanford), fill=predInt))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
+
+ggplot(dat, aes(x=factor(change_platform), fill=predInt))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
+
+ggplot(dat, aes(x=factor(is_within), fill=predInt))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
+
+ggplot(dat, aes(x=factor(single_vignette), fill=predInt))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
+```
+
+```{r}
+# using d for model to get non-z-scored version
+dat <- d_for_model |> filter(!is.na(predInt))
+
+ggplot(dat, aes(x=pub_year, y=predInt, color=predInt))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()
+
+ggplot(dat, aes(x=log_ratio_ss, y=log_sample, color=predInt))+geom_point()+scale_color_viridis()
+
+ggplot(dat, aes(x=log_ratio_ss, y=predInt, color=predInt))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()
+
+ggplot(dat, aes(x=log_sample, y=predInt, color=predInt))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()
+
+ggplot(dat, aes(x=log_trials, y=predInt, color=predInt))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()
+
+```
+
+### P_orig
+Note: predInt may not be reliably calculated in some cases. Dealing with numbers is hard!
+
+```{r}
+dat <- d_for_model |> filter(!is.na(p_orig)) |> mutate(p_orig_bin=ifelse(p_orig>.05, ">.05", "<.05"))
+
+ggplot(dat, aes(x=p_orig, fill=p_orig_bin))+geom_histogram()+scale_fill_viridis(discrete=T)
+
+ggplot(dat, aes(x=subfield, fill=p_orig_bin))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
+
+ggplot(dat, aes(x=open_data |> factor(), fill=p_orig_bin))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+facet_wrap(.~str_c("open_mat ",open_mat))
+
+ggplot(dat, aes(x=factor(stanford), fill=p_orig_bin))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
+
+ggplot(dat, aes(x=factor(change_platform), fill=p_orig_bin))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
+
+ggplot(dat, aes(x=factor(is_within), fill=p_orig_bin))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
+
+ggplot(dat, aes(x=factor(single_vignette), fill=p_orig_bin))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
+```
+
+```{r}
+# using d for model to get non-z-scored version
+dat <- d_for_model |> filter(!is.na(p_orig))
+
+ggplot(dat, aes(x=pub_year, y=p_orig, color=p_orig))+geom_point()+geom_smooth(method="lm")+scale_color_viridis()
+
+ggplot(dat, aes(x=log_ratio_ss, y=log_sample, color=p_orig))+geom_point()+scale_color_viridis()
+
+ggplot(dat, aes(x=log_ratio_ss, y=p_orig, color=p_orig))+geom_point()+geom_smooth(method="lm")+scale_color_viridis()
+
+ggplot(dat, aes(x=log_sample, y=p_orig, color=p_orig))+geom_point()+geom_smooth(method="lm")+scale_color_viridis()
+
+ggplot(dat, aes(x=log_trials, y=p_orig, color=p_orig))+geom_point()+geom_smooth(method="lm")+scale_color_viridis()
+
+```
+
+### TODO predictive
+
+```{r}
+# cognitive, within, foobar trials, foobar participants, etc etc
+
+back_convert
+
+fake_data <- tribble(
+   ~subfield, ~open_data, ~open_mat, ~change_platform, ~is_within, ~single_vignette, ~log_sample, ~log_trials,
+  "cognitive", 1,         1,         0,                1,          0,                log(50),    log(100),
+  "cognitive", 0,         0,         0,                1,          0,                log(50),    log(100),
+  "cognitive", 1,         1,         0,                1,          0,                log(50),    log(100),
+   "social", 0,         0,         1,                0,          1,                log(30),     log(1),
+) |> mutate(academic_year="2022-2023", pub_year=2022, stanford=0, log_ratio_ss=0,
+            z_log_sample=(log_sample-back_convert$mean_log_sample)/back_convert$sd_log_sample,
+            z_log_trials=(log_trials-back_convert$mean_log_trials)/back_convert$sd_log_trials,
+            z_pub_year=(pub_year-back_convert$mean_pub_year)/back_convert$sd_pub_year,
+            z_log_ratio_ss=(log_ratio_ss-back_convert$mean_log_ratio_ss)/back_convert$sd_log_ratio_ss, sub_rep=NA) |> 
+select(academic_year, sub_rep, 
+         z_pub_year, subfield, open_data, open_mat, stanford, change_platform, z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials)
+
+foo <- predict(tier1_subjective, newdata=fake_data)
+
+bar <- fitted(tier1_subjective,newdata=fake_data)
+```

### 2023-03-06 code/helper/parse_stats.R

@@ -74,8 +74,7 @@ parse_raw_prop <- function(propval){
 }
 #parse_raw_prop(ex)
 
-
-parse_mean_ci <- function(mci,within_between,n){
+parse_mean_ci2 <- function(mci,within_between,n){
   # parsing 
   cond1=str_extract(mci, "m1.*\\],")
   cond2=str_extract(mci, "m2.*\\]")
@@ -101,7 +100,7 @@ parse_mean_ci <- function(mci,within_between,n){
 }
 
 
-parse_mean_sd <- function(msd,within_between,n){
+parse_mean_sd2 <- function(msd,within_between,n){
   cond1=str_extract(msd, "m1.*\\),")
   cond2=str_extract(msd, "m2.*\\)")
   m1=str_extract(cond1, "m1=.*\\(") |> str_sub(4,-2) |> as.numeric()
@@ -117,6 +116,36 @@ parse_mean_sd <- function(msd,within_between,n){
   pval=pt(q=tval, df=df, lower.tail=FALSE)*2
   return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=m1-m2, "SE"=se_pool))
 }
+#foo <- "MSD4:m1=3.26(1.91),m2=5.40(1.59),m3=3.67(2.00),m4=4.67(2.06)"
+
+parse_mean_sd4 <- function(msd,within_between,n){
+  cond1=str_extract(msd, "m1.*\\),m2")
+  cond2=str_extract(msd, "m2.*\\),m3")
+  cond3=str_extract(msd, "m3.*\\),")
+  cond4=str_extract(msd, "m4.*\\)")
+  
+  m1=str_extract(cond1, "m1=.*\\(") |> str_sub(4,-2) |> as.numeric()
+  m2=str_extract(cond2, "m2=.*\\(") |> str_sub(4,-2) |> as.numeric()
+  m3=str_extract(cond3, "m3=.*\\(") |> str_sub(4,-2) |> as.numeric()
+  m4=str_extract(cond4, "m4=.*\\(") |> str_sub(4,-2) |> as.numeric()
+  
+  sd1=str_extract(cond1, "\\(.*\\),") |> str_sub(2,-3) |> as.numeric()
+  sd2=str_extract(cond2, "\\(.*\\)") |> str_sub(2,-3) |> as.numeric()
[…]

### 2023-03-06 code/process.Rmd
run rest of pre-reg models

@@
 library(glmnet)
+library(tidybayes)
+library(ggstance)
+library("lattice")
+library(reshape2)
+library(ggrepel)
+library(ggthemes)
 
@@
 ```{r}
-library(ggstance)
 d_es_predInt |> ggplot(aes(x=target_ES, 
@@
 
+Note: tier 2 and 3 models are subject to change as a few more studies might in fact have useable stats & some of the effect size extraction might be incorrect.
+
 ```{r}
@@
 ```{r}
-library(tidybayes)
 tier1_subjective |> 
@@
 
-```{r, eval=F}
-tier2_predint <- brm(pred_int ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+```{r, eval=T}
+tier2_predint <- brm(predInt ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                        z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
@@
 
-```{r, eval=F}
-tier2_porig <- brm(porig ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+```{r}
+tier2_predint |> 
+gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |> filter(Term!="Intercept") |> 
+  ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
+  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI")+theme(axis.text=element_text(size=11))
+```
+
+```{r, eval=T}
+tier2_porig <- brm(p_orig ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                      z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
@@
 
-```{r, eval=F}
+```{r}
+tier2_porig |> 
+gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |> filter(Term!="Intercept") |> 
+  ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
+  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI")+theme(axis.text=element_text(size=11))
+```
+```{r, eval=T}
 tier3_subjective <- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
@@
                              z_target_d_calc + z_log_p| academic_year),
-                        family="bernoulli",
-                        data=data_tier3,
+                        family="cumulative",
+                        data=data_tier3 |> mutate(sub_rep=sub_rep*4+1),
                         file=here(model_location, "tier3_subjective"),
@@
 
-```{r, eval=F}
-tier3_predint <- brm(predint ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+```{r}
+tier3_subjective |> 
+gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |> 
+  ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
+  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI")+theme(axis.text=element_text(size=11))
+```
+
+```{r, eval=T}
+tier3_predint <- brm(predInt ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                        z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
@@
 
+```{r}
+tier3_predint |> 
+gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |> filter(Term!="Intercept") |> 
+  ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
+  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI")+theme(axis.text=element_text(size=11))
+```
+
 ```{r, eval=F}
@@
                         z_target_d_calc + z_log_p| academic_year),
-                   family=(link="logit"),
                    data=data_tier3,
@@
                    control=list(adapt_delta=.99),
-                   #backend="cmdstanr"
+                   backend="cmdstanr"
 )
 ```
+
+```{r}
+tier3_porig |> 
+gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |> filter(Term!="Intercept") |> 
+  ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
+  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI")+theme(axis.text=element_text(size=11))
+```
+
+## Sensitivity analysis TODO
 
@@
 ```{r}
-library("lattice")
 dat <- data_tier1 |> mutate(is.cog=ifelse(subfield=="cognitive", 1,0),
@@
 # Install and load reshape2 package
-library(reshape2)
 
@@
 # plotting the correlation heatmap
-library(ggplot2)
 ggplot(data = melted_corr_mat, aes(x=Var1, y=Var2,
@@
 ```{r}
-library(ggrepel)
-library(ggthemes)
+
 to_plot <- lasso_linear2$beta |> as.matrix() |> as.tibble(rownames="var") |> pivot_longer(`s0`:`s71`) |> mutate(time=str_sub(name, 2,-1) |> as.numeric())
@@
 
-### TODO predictive
+## TODO predictive
 

### 2023-03-06 code/process.Rmd
add new lassoes

@@
 
-```{r, eval=F}
+```{r, eval=T}
 tier3_porig <- brm(p_orig ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
@@
 
-# Random exploratory analyses
+# Exploratory working
 
@@
 
+```
+
+including tier 3 predictors
+
+```{r}
+dat <- data_tier3 |> mutate(is.cog=ifelse(subfield=="cognitive", 1,0),
+                            is.soc=ifelse(subfield=="social", 1,0),
+                            is.other=ifelse(subfield=="other-psych", 1,0),
+                            is.non=ifelse(subfield=="non-psych",1,0)) |> 
+  select(is.cog, is.soc, is.other, is.non,stanford, z_pub_year, open_data, open_mat,  change_platform, 
+         z_log_ratio_ss, z_log_sample, single_vignette, z_log_trials, is_within, z_log_p, z_target_d_calc)
+
+corr_mat <- round(cor(dat),2)
+
+# Install and load reshape2 package
+
+# reduce the size of correlation matrix
+melted_corr_mat <-melt(corr_mat)
+# head(melted_corr_mat)
+
+# plotting the correlation heatmap
+ggplot(data = melted_corr_mat, aes(x=Var1, y=Var2,
+                                   fill=value)) + #scale_fill_viridis()+
+  scale_fill_gradient2(low="#440154",high="#FDE725FF")+
+  geom_tile(alpha=.7)+theme(axis.text.x = element_text(angle = 40, vjust = 1, hjust=1))+geom_text(aes(label=value), size=3)+
+  labs(x="", y="", fill="Correlation")
+
+#corr_mat |> as_tibble(rownames="value2") |> pivot_longer(cols=!value2, names_to="value1", values_to = "corr") |> arrange(corr) |> filter(value2 <value1) |> View()
+
+#corr_mat |> as_tibble(rownames="value2") |> pivot_longer(cols=!value2, names_to="value1", values_to = "corr") |> arrange(desc(corr)) |> filter(value2 <value1)
+
+```
+
+## Frequentist Lassoes
+
+```{r}
+
+boring_logistic <- glm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                         z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials,
+                       family=binomial, 
+                       data=data_tier1 |> mutate(sub_rep=(sub_rep-1)/4),
+
+)
+```
+
+regularized tier 1 sub
+```{r}
+predictors <- data_tier1 |> mutate(social=ifelse(subfield=="social", 1,0),other_psych=ifelse(subfield=="other-psych",1,0), non_psych=ifelse(subfield=="non-psych", 1,0)) |> 
+  select(z_pub_year, open_data, open_mat, stanford, change_platform, social, other_psych, non_psych, 
+                                   z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials) |> as.matrix()
+
+yvals <- data_tier1 |> mutate(sub_rep=(sub_rep-1)/4) |> pull(sub_rep)
+#lasso_linear <- cv.glmnet(predictors, yvals |> as.matrix(),       family="gaussian", alpha=1)
+
+lasso_linear2 <- glmnet(predictors, yvals, 
+                        family="gaussian", alpha=1)
+```
+
+```{r}
+
+to_plot <- lasso_linear2$beta |> as.matrix() |> as.tibble(rownames="var") |> pivot_longer(!var) |> mutate(time=str_sub(name, 2,-1) |> as.numeric())
+
+ggplot(to_plot, aes(x=time, y=value, color=var, label=var))+geom_line()+geom_label_repel(data=to_plot |> filter(time==70), min.segment.length = 100, nudge_x = 15, na.rm = TRUE)+ theme(legend.position="none")+ scale_color_tableau("Classic 20")+
+  coord_cartesian(xlim=c(0,90), ylim=c(-.2, .3))+theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.ticks.x=element_blank())
+
+```
+
+regularized p_orig
+
+```{r}
+dat <- data_tier2 |> filter(!is.na(p_orig)) |>  mutate(social=ifelse(subfield=="social", 1,0),other_psych=ifelse(subfield=="other-psych",1,0), non_psych=ifelse(subfield=="non-psych", 1,0))
+predictors <- dat |> select(z_pub_year, open_data, open_mat, stanford, 
+                            change_platform, social, non_psych, other_psych,
+                                   z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials) |> as.matrix()
+
+yvals <- dat|> pull(p_orig)
+
+lasso_linear_porig <- glmnet(predictors, yvals, 
+                        family="gaussian", alpha=1)
+
+yvals <- dat |> pull(predInt)
+
+lasso_linear_predint <- glmnet(predictors, yvals, 
+                        family="binomial", alpha=1)
+```
+
+```{r}
+to_plot <- lasso_linear_porig$beta |> as.matrix() |> as.tibble(rownames="var") |> pivot_longer(!var) |> mutate(time=str_sub(name, 2,-1) |> as.numeric())
+
+ggplot(to_plot, aes(x=time, y=value, color=var, label=var))+geom_line()+geom_label_repel(data=to_plot |> filter(time==70), min.segment.length = 100, nudge_x = 15, na.rm = TRUE)+ theme(legend.position="none")+ scale_color_tableau("Classic 20")+
+  coord_cartesian(xlim=c(0,90), ylim=c(-.2, .3))+theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.ticks.x=element_blank())
+```
+
+```{r}
+to_plot <- lasso_linear_predint$beta |> as.matrix() |> as.tibble(rownames="var") |> pivot_longer(!var) |> mutate(time=str_sub(name, 2,-1) |> as.numeric())
+
+ggplot(to_plot, aes(x=time, y=value, color=var, label=var))+geom_line()+geom_label_repel(data=to_plot |> filter(time==55), min.segment.length = 100, nudge_x = 15, na.rm = TRUE)+ theme(legend.position="none")+ scale_color_tableau("Classic 20")+
+  coord_cartesian(xlim=c(0,80))+theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.ticks.x=element_blank())
+
+```
+
+Tier 3
+
+```{r}
+dat <- data_tier3 |> filter(!is.na(p_orig)) |>  mutate(social=ifelse(subfield=="social", 1,0),other_psych=ifelse(subfield=="other-psych",1,0), non_psych=ifelse(subfield=="non-psych", 1,0))
+predictors <- dat |> select(z_pub_year, open_data, open_mat, stanford, 
+                            change_platform, social, non_psych, other_psych,
+                                   z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials, z_target_d_calc, z_log_p) |> as.matrix()
+
+yvals <- dat |> pull(sub_rep)
+lasso_3sub <- glmnet(predictors, yvals, 
+                        family="gaussian", alpha=1)
+yvals <- dat|> pull(p_orig)
+
+lasso_3porig <- glmnet(predictors, yvals, 
+                        family="gaussian", alpha=1)
+
+yvals <- dat |> pull(predInt)
+
+lasso_3predint <- glmnet(predictors, yvals, 
+                        family="binomial", alpha=1)
+```
+
+```{r}
+to_plot <- lasso_3sub$beta |> as.matrix() |> as.tibble(rownames="var") |> pivot_longer(!var) |> mutate(time=str_sub(name, 2,-1) |> as.numeric())
+
+ggplot(to_plot, aes(x=time, y=value, color=var, label=var))+geom_line()+geom_label_repel(data=to_plot |> filter(time==69), min.segment.length = 100, nudge_x = 15, na.rm = TRUE)+ theme(legend.position="none")+ scale_color_tableau("Classic 20")+
+  coord_cartesian(xlim=c(0,90))+theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.ticks.x=element_blank())
+
+```
+
+```{r}
+to_plot <- lasso_3predint$beta |> as.matrix() |> as.tibble(rownames="var") |> pivot_longer(!var) |> mutate(time=str_sub(name, 2,-1) |> as.numeric())
+
+ggplot(to_plot, aes(x=time, y=value, color=var, label=var))+geom_line()+geom_label_repel(data=to_plot |> filter(time==60), min.segment.length = 100, nudge_x = 15, na.rm = TRUE)+ theme(legend.position="none")+ scale_color_tableau("Classic 20")+
+  coord_cartesian(xlim=c(0,90))+theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.ticks.x=element_blank())
+
+```
+
+```{r}
+to_plot <- lasso_3porig$beta |> as.matrix() |> as.tibble(rownames="var") |> pivot_longer(!var) |> mutate(time=str_sub(name, 2,-1) |> as.numeric())
+
+ggplot(to_plot, aes(x=time, y=value, color=var, label=var))+geom_line()+geom_label_repel(data=to_plot |> filter(time==71), min.segment.length = 100, nudge_x = 15, na.rm = TRUE)+ theme(legend.position="none")+ scale_color_tableau("Classic 20")+
+  coord_cartesian(xlim=c(0,90))+theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.ticks.x=element_blank())
+
+```
+
+## Correlations
+
+```{r}
+sub_cor <- function(var, stat = "estimate") {
+  if (stat == "estimate") {
+    cor.test(data_tier1$sub_rep, pull(data_tier1, {{var}}))$estimate
+  } else {
+    cor.test(data_tier1$sub_rep, pull(data_tier1, {{var}}))$p.value
+  }
+}
+
+preds <- c("z_pub_year", "open_data",  "open_mat", "stanford", "change_platform", 
+           "z_log_ratio_ss", "is_within", "single_vignette", "z_log_sample", 
+           "z_log_trials")
+
+cors <- tibble(preds = preds) |>
+  mutate(r = sapply(preds, function(x) sub_cor(x, stat = "estimate")),
+         p = sapply(preds, function(x) sub_cor(x, stat = "p")))
+
+knitr::kable(cors, digits = 3)
+```
+
+## Individual predictor - outcome correlations
+
+### Sub_rep
+```{r}
+dat <- data_tier1 |> mutate(sub_rep=((sub_rep-1)/4) |> factor(levels=c("0","0.25", "0.5", "0.75", "1")))
+
+ggplot(dat, aes(x=sub_rep, fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(legend.position = "none")+labs(y="Count", x="Subjective Replication score")
+
+ggplot(dat, aes(x=subfield, fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
+
+dat |> mutate(open_mat=ifelse(open_mat, "Open materials", "No open materials"), open_data=ifelse(open_data, "Open data", "No open data")) |> ggplot( aes(x=open_data |> factor(), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+facet_wrap(.~open_mat)+theme(axis.title.x=element_blank())
+
+ ggplot(dat, aes(x=factor(stanford), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
+
+ggplot(dat, aes(x=factor(change_platform), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
+
+ggplot(dat, aes(x=ifelse(is_within, "Within", "Between"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(axis.title.x=element_blank())
+
+ggplot(dat, aes(x=ifelse(single_vignette, "1 vignette", "multiple vignettes"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(axis.title.x=element_blank())
+```
+
+```{r}
+# using d for model to get non-z-scored version
+ggplot(d_for_model, aes(x=pub_year, y=sub_rep, color=sub_rep))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()
+
+ggplot(d_for_model, aes(x=log_ratio_ss, y=log_sample, color=sub_rep))+geom_point()+scale_color_viridis()
+
+ggplot(d_for_model, aes(x=log_ratio_ss, y=sub_rep, color=sub_rep))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()
+
+ggplot(d_for_model, aes(x=log_sample, y=sub_rep, color=sub_rep))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()
+
+ggplot(d_for_model, aes(x=log_trials, y=sub_rep, color=sub_rep))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()
+
+```
+
+### Pred_int
+Note: predInt may not be reliably calculated in some cases. Dealing with numbers is hard!
+
+```{r}
+dat <- d_for_model |> filter(!is.na(predInt)) |>  mutate(predInt=predInt |> factor())
+
+ggplot(dat, aes(x=predInt, fill=predInt))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
+
+ggplot(dat, aes(x=subfield, fill=predInt))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
+
+ggplot(dat, aes(x=open_data |> factor(), fill=predInt))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+facet_wrap(.~str_c("open_mat ",open_mat))
+
+ggplot(dat, aes(x=factor(stanford), fill=predInt))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
+
+ggplot(dat, aes(x=factor(change_platform), fill=predInt))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
+
+ggplot(dat, aes(x=factor(is_within), fill=predInt))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
+
+ggplot(dat, aes(x=factor(single_vignette), fill=predInt))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
+```
+
+```{r}
+# using d for model to get non-z-scored version
+dat <- d_for_model |> filter(!is.na(predInt))
+
+ggplot(dat, aes(x=pub_year, y=predInt, color=predInt))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()
+
+ggplot(dat, aes(x=log_ratio_ss, y=log_sample, color=predInt))+geom_point()+scale_color_viridis()
+
+ggplot(dat, aes(x=log_ratio_ss, y=predInt, color=predInt))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()
+
+ggplot(dat, aes(x=log_sample, y=predInt, color=predInt))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()
+
+ggplot(dat, aes(x=log_trials, y=predInt, color=predInt))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()
+
+```
+
+### P_orig
+Note: predInt may not be reliably calculated in some cases. Dealing with numbers is hard!
+
+```{r}
+dat <- d_for_model |> filter(!is.na(p_orig)) |> mutate(p_orig_bin=ifelse(p_orig>.05, ">.05", "<.05"))
+
+ggplot(dat, aes(x=p_orig, fill=p_orig_bin))+geom_histogram()+scale_fill_viridis(discrete=T)
+
+ggplot(dat, aes(x=subfield, fill=p_orig_bin))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
+
+ggplot(dat, aes(x=open_data |> factor(), fill=p_orig_bin))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+facet_wrap(.~str_c("open_mat ",open_mat))
+
+ggplot(dat, aes(x=factor(stanford), fill=p_orig_bin))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
+
+ggplot(dat, aes(x=factor(change_platform), fill=p_orig_bin))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
+
+ggplot(dat, aes(x=factor(is_within), fill=p_orig_bin))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
+
+ggplot(dat, aes(x=factor(single_vignette), fill=p_orig_bin))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
+```
+
+```{r}
+# using d for model to get non-z-scored version
+dat <- d_for_model |> filter(!is.na(p_orig))
+
+ggplot(dat, aes(x=pub_year, y=p_orig, color=p_orig))+geom_point()+geom_smooth(method="lm")+scale_color_viridis()
+
+ggplot(dat, aes(x=log_ratio_ss, y=log_sample, color=p_orig))+geom_point()+scale_color_viridis()
+
+ggplot(dat, aes(x=log_ratio_ss, y=p_orig, color=p_orig))+geom_point()+geom_smooth(method="lm")+scale_color_viridis()
+
+ggplot(dat, aes(x=log_sample, y=p_orig, color=p_orig))+geom_point()+geom_smooth(method="lm")+scale_color_viridis()
+
+ggplot(dat, aes(x=log_trials, y=p_orig, color=p_orig))+geom_point()+geom_smooth(method="lm")+scale_color_viridis()
+
+```
+# Exploratory even randomer
+
+## Model exploration
+
+```{r}
+mod <- lm(sub_rep ~ z_pub_year + subfield + open_data + open_mat + 
+            stanford + change_platform + 
+            z_log_ratio_ss + is_within + 
+            single_vignette + z_log_sample + z_log_trials,
+          data = data_tier1 )
+summary(mod)
+```
+
+Repeating regularized
+
+```{r}
+predictors <- data_tier1 |> 
+  select(z_pub_year, open_data, open_mat, stanford, change_platform, 
+         z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials) |>
+  as.data.frame() |>
+  as.matrix()
+
+lasso_linear <- cv.glmnet(predictors, data_tier1$sub_rep, 
+                          family="gaussian", alpha=1)
+
+coef(lasso_linear, s = "lambda.min")
+coef(lasso_linear, s = "lambda.1se")
+```
+
+## Principal components
+
+Principal components are not very interpretable.
+
+```{r}
+pcs <- select(data_tier1, 
+              z_pub_year, open_data,  open_mat, stanford, change_platform, 
+              z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials) |>
+  princomp()
+
+summary(pcs)
+pcs$loadings
+plot(pcs)
+biplot(pcs)
+```
+
+## Bayesian tinkering
+
+Let's try super strong priors, consolidating a few very highly correlated variables.
+
+```{r, eval=F}
+normal_priors <- c(set_prior("horseshoe(3)", class="b"),
+                   set_prior("normal(0,.5)", class="sd"))
+
+brm(sub_rep ~ z_pub_year + subfield + open_data + open_mat + stanford + change_platform + z_log_ratio_ss + is_within + single_vignette + z_log_sample +  z_log_trials + 
+      (1 | academic_year),
+    # family = "linear", # runs on 1-5 data
+    data = data_tier1,
+    prior = normal_priors, 
+    iter = 10000, warmup = 2000,
+    control = list(adapt_delta=.99),
+    backend = "cmdstanr")
+```
+
+And let's see if it's the link
+
+```{r, eval=F}
+normal_priors <- c(set_prior("horseshoe(3)", class="b"),
+                   set_prior("normal(0,.5)", class="sd"))
+
+# make it in the .005 - .995 range
+data_tier1$sub_rep01 <- ((data_tier1$sub_rep-1)/5) * .99 + .005
+
+brm(sub_rep01 ~ z_pub_year + subfield + open_data + open_mat + stanford + change_platform + z_log_ratio_ss + is_within + single_vignette + z_log_sample +  z_log_trials + 
+      (1 | academic_year),
+    family = "beta", # runs on 1-5 data
+    data = data_tier1,
+    prior = normal_priors, 
+    iter = 10000, warmup = 2000,
+    control = list(adapt_delta=.99),
+    backend = "cmdstanr")
+```
+
+## Models of clusters of predictors
+
+```{r}
+mod <- lm(sub_rep ~ 
+            is_within + 
+            single_vignette +  z_log_trials,
+          data = data_tier1 )
+summary(mod)
 ```
@@
 
-## frequentism
-
-```{r}
-
-boring_logistic <- glm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
-                         z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials,
-                       family=binomial, 
-                       data=data_tier1 |> mutate(sub_rep=(sub_rep-1)/4),
-
-)
-```
-
-regularized
-```{r}
-predictors <- data_tier1 |> mutate(social=ifelse(subfield=="social", 1,0),other=ifelse(subfield=="other-psych",1,0), non=ifelse(subfield=="non-psych", 1,0)) |> 
-  select(z_pub_year, open_data, open_mat, stanford, change_platform, social, other, non, 
-                                   z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials) |> as.matrix()
-
-yvals <- data_tier1 |> mutate(sub_rep=(sub_rep-1)/4) |> pull(sub_rep)
-#lasso_linear <- cv.glmnet(predictors, yvals |> as.matrix(),       family="gaussian", alpha=1)
-
-lasso_linear2 <- glmnet(predictors, yvals, 
-                        family="gaussian", alpha=1)
-```
-
-```{r}
-
-to_plot <- lasso_linear2$beta |> as.matrix() |> as.tibble(rownames="var") |> pivot_longer(`s0`:`s71`) |> mutate(time=str_sub(name, 2,-1) |> as.numeric())
-
-ggplot(to_plot, aes(x=time, y=value, color=var, label=var))+geom_line()+geom_label_repel(data=to_plot |> filter(time==70), min.segment.length = 100, nudge_x = 10, na.rm = TRUE)+ theme(legend.position="none")+ scale_color_tableau("Classic 20")+
-  coord_cartesian(xlim=c(0,80), ylim=c(-.2, .3))+theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.ticks.x=element_blank())
-
-```
-
-regularized p_orig
-
-```{r}
-dat <- data_tier2 |> filter(!is.na(p_orig)) |>  mutate(social=ifelse(subfield=="social", 1,0),other=ifelse(subfield=="other-psych",1,0), non=ifelse(subfield=="non-psych", 1,0))
-predictors <- dat |> select(z_pub_year, open_data, open_mat, #stanford, 
-                            change_platform, social, non, other,
-                                   z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials) |> as.matrix()
-
-yvals <- dat|> pull(p_orig)
-
-lasso_linear_porig <- glmnet(predictors, yvals, 
-                        family="gaussian", alpha=1)
-
-yvals <- dat |> pull(predInt)
-
-lasso_linear_predint <- glmnet(predictors, yvals, 
-                        family="binomial", alpha=1)
-```
-
-```{r}
-to_plot <- lasso_linear_porig$beta |> as.matrix() |> as.tibble(rownames="var") |> pivot_longer(`s0`:`s72`) |> mutate(time=str_sub(name, 2,-1) |> as.numeric())
-
-ggplot(to_plot, aes(x=time, y=value, color=var, label=var))+geom_line()+geom_label_repel(data=to_plot |> filter(time==70), min.segment.length = 100, nudge_x = 10, na.rm = TRUE)+ theme(legend.position="none")+ scale_color_tableau("Classic 20")+
-  coord_cartesian(xlim=c(0,80), ylim=c(-.2, .3))+theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.ticks.x=element_blank())
-```
-
-```{r}
-to_plot <- lasso_linear_predint$beta |> as.matrix() |> as.tibble(rownames="var") |> pivot_longer(`s0`:`s58`) |> mutate(time=str_sub(name, 2,-1) |> as.numeric())
-
-ggplot(to_plot, aes(x=time, y=value, color=var, label=var))+geom_line()+geom_label_repel(data=to_plot |> filter(time==55), min.segment.length = 100, nudge_x = 10, na.rm = TRUE)+ theme(legend.position="none")+ scale_color_tableau("Classic 20")+
-  coord_cartesian(xlim=c(0,70))+theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.ticks.x=element_blank())
-
-```
-
-## Correlations
-
-```{r}
-sub_cor <- function(var, stat = "estimate") {
-  if (stat == "estimate") {
-    cor.test(data_tier1$sub_rep, pull(data_tier1, {{var}}))$estimate
-  } else {
-    cor.test(data_tier1$sub_rep, pull(data_tier1, {{var}}))$p.value
-  }
-}
-
-preds <- c("z_pub_year", "open_data",  "open_mat", "stanford", "change_platform", 
-           "z_log_ratio_ss", "is_within", "single_vignette", "z_log_sample", 
-           "z_log_trials")
-
-cors <- tibble(preds = preds) |>
-  mutate(r = sapply(preds, function(x) sub_cor(x, stat = "estimate")),
-         p = sapply(preds, function(x) sub_cor(x, stat = "p")))
-
-knitr::kable(cors, digits = 3)
-```
-
-## Principal components
-
-Principal components are not very interpretable.
-
-```{r}
-pcs <- select(data_tier1, 
-              z_pub_year, open_data,  open_mat, stanford, change_platform, 
-              z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials) |>
-  princomp()
-
-summary(pcs)
-pcs$loadings
-plot(pcs)
-biplot(pcs)
-```
-
-## Model exploration
-
-```{r}
-mod <- lm(sub_rep ~ z_pub_year + subfield + open_data + open_mat + 
-            stanford + change_platform + 
-            z_log_ratio_ss + is_within + 
-            single_vignette + z_log_sample + z_log_trials,
-          data = data_tier1 )
-summary(mod)
-```
-
-Repeating regularized
-
-```{r}
-predictors <- data_tier1 |> 
-  select(z_pub_year, open_data, open_mat, stanford, change_platform, 
-         z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials) |>
-  as.data.frame() |>
-  as.matrix()
-
-lasso_linear <- cv.glmnet(predictors, data_tier1$sub_rep, 
-                          family="gaussian", alpha=1)
-
-coef(lasso_linear, s = "lambda.min")
-coef(lasso_linear, s = "lambda.1se")
-```
-
-## Bayesian tinkering
-
-Let's try super strong priors, consolidating a few very highly correlated variables.
-
-```{r, eval=F}
-normal_priors <- c(set_prior("horseshoe(3)", class="b"),
-                   set_prior("normal(0,.5)", class="sd"))
-
-brm(sub_rep ~ z_pub_year + subfield + open_data + open_mat + stanford + change_platform + z_log_ratio_ss + is_within + single_vignette + z_log_sample +  z_log_trials + 
-      (1 | academic_year),
-    # family = "linear", # runs on 1-5 data
-    data = data_tier1,
-    prior = normal_priors, 
-    iter = 10000, warmup = 2000,
-    control = list(adapt_delta=.99),
-    backend = "cmdstanr")
-```
-
-And let's see if it's the link
-
-```{r, eval=F}
-normal_priors <- c(set_prior("horseshoe(3)", class="b"),
-                   set_prior("normal(0,.5)", class="sd"))
-
-# make it in the .005 - .995 range
-data_tier1$sub_rep01 <- ((data_tier1$sub_rep-1)/5) * .99 + .005
-
-brm(sub_rep01 ~ z_pub_year + subfield + open_data + open_mat + stanford + change_platform + z_log_ratio_ss + is_within + single_vignette + z_log_sample +  z_log_trials + 
-      (1 | academic_year),
-    family = "beta", # runs on 1-5 data
-    data = data_tier1,
-    prior = normal_priors, 
-    iter = 10000, warmup = 2000,
-    control = list(adapt_delta=.99),
-    backend = "cmdstanr")
-```
-
-## Models of clusters of predictors
-
-```{r}
-mod <- lm(sub_rep ~ 
-            is_within + 
-            single_vignette +  z_log_trials,
-          data = data_tier1 )
-summary(mod)
-```
-
-## Individual predictor - outcome correlations
-
-### Sub_rep
-```{r}
-dat <- data_tier1 |> mutate(sub_rep=((sub_rep-1)/4) |> factor(levels=c("0","0.25", "0.5", "0.75", "1")))
-
-ggplot(dat, aes(x=sub_rep, fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(legend.position = "none")+labs(y="Count", x="Subjective Replication score")
-
-ggplot(dat, aes(x=subfield, fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
-
-dat |> mutate(open_mat=ifelse(open_mat, "Open materials", "No open materials"), open_data=ifelse(open_data, "Open data", "No open data")) |> ggplot( aes(x=open_data |> factor(), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+facet_wrap(.~open_mat)+theme(axis.title.x=element_blank())
-
- ggplot(dat, aes(x=factor(stanford), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
-
-ggplot(dat, aes(x=factor(change_platform), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
-
-ggplot(dat, aes(x=ifelse(is_within, "Within", "Between"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(axis.title.x=element_blank())
-
-ggplot(dat, aes(x=ifelse(single_vignette, "1 vignette", "multiple vignettes"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(axis.title.x=element_blank())
-```
-
-```{r}
-# using d for model to get non-z-scored version
-ggplot(d_for_model, aes(x=pub_year, y=sub_rep, color=sub_rep))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()
-
-ggplot(d_for_model, aes(x=log_ratio_ss, y=log_sample, color=sub_rep))+geom_point()+scale_color_viridis()
-
-ggplot(d_for_model, aes(x=log_ratio_ss, y=sub_rep, color=sub_rep))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()
-
-ggplot(d_for_model, aes(x=log_sample, y=sub_rep, color=sub_rep))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()
-
-ggplot(d_for_model, aes(x=log_trials, y=sub_rep, color=sub_rep))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()
-
-```
-
-### Pred_int
-Note: predInt may not be reliably calculated in some cases. Dealing with numbers is hard!
-
-```{r}
-dat <- d_for_model |> filter(!is.na(predInt)) |>  mutate(predInt=predInt |> factor())
-
-ggplot(dat, aes(x=predInt, fill=predInt))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
-
-ggplot(dat, aes(x=subfield, fill=predInt))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
-
-ggplot(dat, aes(x=open_data |> factor(), fill=predInt))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+facet_wrap(.~str_c("open_mat ",open_mat))
-
-ggplot(dat, aes(x=factor(stanford), fill=predInt))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
-
-ggplot(dat, aes(x=factor(change_platform), fill=predInt))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
-
-ggplot(dat, aes(x=factor(is_within), fill=predInt))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
-
-ggplot(dat, aes(x=factor(single_vignette), fill=predInt))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
-```
-
-```{r}
-# using d for model to get non-z-scored version
-dat <- d_for_model |> filter(!is.na(predInt))
-
-ggplot(dat, aes(x=pub_year, y=predInt, color=predInt))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()
-
-ggplot(dat, aes(x=log_ratio_ss, y=log_sample, color=predInt))+geom_point()+scale_color_viridis()
-
-ggplot(dat, aes(x=log_ratio_ss, y=predInt, color=predInt))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()
-
-ggplot(dat, aes(x=log_sample, y=predInt, color=predInt))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()
-
-ggplot(dat, aes(x=log_trials, y=predInt, color=predInt))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()
-
-```
-
-### P_orig
-Note: predInt may not be reliably calculated in some cases. Dealing with numbers is hard!
-
-```{r}
-dat <- d_for_model |> filter(!is.na(p_orig)) |> mutate(p_orig_bin=ifelse(p_orig>.05, ">.05", "<.05"))
-
-ggplot(dat, aes(x=p_orig, fill=p_orig_bin))+geom_histogram()+scale_fill_viridis(discrete=T)
-
-ggplot(dat, aes(x=subfield, fill=p_orig_bin))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
-
-ggplot(dat, aes(x=open_data |> factor(), fill=p_orig_bin))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+facet_wrap(.~str_c("open_mat ",open_mat))
-
-ggplot(dat, aes(x=factor(stanford), fill=p_orig_bin))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
-
-ggplot(dat, aes(x=factor(change_platform), fill=p_orig_bin))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
-
-ggplot(dat, aes(x=factor(is_within), fill=p_orig_bin))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
-
-ggplot(dat, aes(x=factor(single_vignette), fill=p_orig_bin))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
-```
-
-```{r}
-# using d for model to get non-z-scored version
-dat <- d_for_model |> filter(!is.na(p_orig))
-
-ggplot(dat, aes(x=pub_year, y=p_orig, color=p_orig))+geom_point()+geom_smooth(method="lm")+scale_color_viridis()
-
-ggplot(dat, aes(x=log_ratio_ss, y=log_sample, color=p_orig))+geom_point()+scale_color_viridis()
-
-ggplot(dat, aes(x=log_ratio_ss, y=p_orig, color=p_orig))+geom_point()+geom_smooth(method="lm")+scale_color_viridis()
-
-ggplot(dat, aes(x=log_sample, y=p_orig, color=p_orig))+geom_point()+geom_smooth(method="lm")+scale_color_viridis()
-
-ggplot(dat, aes(x=log_trials, y=p_orig, color=p_orig))+geom_point()+geom_smooth(method="lm")+scale_color_viridis()
-
-```
-
 ## TODO predictive
@@
 
-bar <- fitted(tier1_subjective,newdata=fake_data)
-```
+bar <- fitted(tier1_subjective, newdata=fake_data)
+```

### 2023-03-07 code/helper/parse_stats.R
work on stats

@@ -74,6 +74,38 @@ parse_raw_prop <- function(propval){
 }
 #parse_raw_prop(ex)
 
+#foo = "MSD1:m1=49.9(11),comp=50"
+parse_mean_sd1 <- function(msd,within_between,n){
+  cond1=str_extract(msd, "m1.*\\),")
+  comp=str_extract(msd, "comp.*")|> str_sub(6,-1) |> as.numeric()
+  m1=str_extract(cond1, "m1=.*\\(") |> str_sub(4,-2) |> as.numeric()
+  sd1=str_extract(cond1, "\\(.*\\),") |> str_sub(2,-3) |> as.numeric()
+  #
+  se=sd1/sqrt(n-1)
+  d_calc=abs(m1-comp)/sd1 # note we force all positive and then fix later 
+  tval=(m1-comp)/se |> abs()
+  df=n-1
+  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
+  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=m1-comp, "SE"=se))
+}
+
+#parse_mean_sd1(foo, "within", 5)
+
+
+parse_mean_se1 <- function(mse,within_between,n){
+  cond1=str_extract(mse, "m1.*\\),")
+  comp=str_extract(mse, "comp.*")|> str_sub(6,-1) |> as.numeric()
+  m1=str_extract(cond1, "m1=.*\\(") |> str_sub(4,-2) |> as.numeric()
+  se1=str_extract(cond1, "\\(.*\\),") |> str_sub(2,-3) |> as.numeric()
+  #
+  sd1=se1*sqrt(n-1)
+  d_calc=abs(m1-comp)/sd1 # note we force all positive and then fix later 
+  tval=(m1-comp)/se1 |> abs()
+  df=n-1
+  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
+  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=m1-comp, "SE"=se1))
+}
+
 parse_mean_ci2 <- function(mci,within_between,n){
   # parsing 
   cond1=str_extract(mci, "m1.*\\],")
@@ -85,19 +117,21 @@ parse_mean_ci2 <- function(mci,within_between,n){
[…]

### 2023-03-07 code/process.Rmd
rerun models

@@
   geom_hline(yintercept=0)+
-  scale_color_viridis(discrete=F, direction=-1)+
+  scale_color_viridis(discrete=F, direction=1)+
   labs(color="p_orig", x="Original SMD", y="Replication SMD")
@@
   geom_hline(yintercept = 0, lty = 2)+
-  scale_color_viridis(discrete=F, direction = -1, 
+  scale_color_viridis(discrete=F, direction = 1, 
                       name = "Subjective Replication Success")+
@@
   ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
-  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI")+theme(axis.text=element_text(size=11))
+  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI predicting subjective replication score")+theme(axis.text=element_text(size=11))
 ```
@@
   ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
-  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI")+theme(axis.text=element_text(size=11))
+  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI predicting replication in predictive interval")+theme(axis.text=element_text(size=11))
 ```
@@
   ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
-  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI")+theme(axis.text=element_text(size=11))
+  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI predicting p_original")+theme(axis.text=element_text(size=11))
 ```
@@
   ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
-  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI")+theme(axis.text=element_text(size=11))
+  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI predicting subjective replication with stats predictors")+theme(axis.text=element_text(size=11))
 ```
@@
   ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
-  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI")+theme(axis.text=element_text(size=11))
+  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI predicting predictive interval with stats predictors")+theme(axis.text=element_text(size=11))
 ```
@@
   ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
-  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI")+theme(axis.text=element_text(size=11))
+  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI predicting p_original with stats predictors")+theme(axis.text=element_text(size=11))
 ```
@@
 yvals <- data_tier1 |> mutate(sub_rep=(sub_rep-1)/4) |> pull(sub_rep)
-#lasso_linear <- cv.glmnet(predictors, yvals |> as.matrix(),       family="gaussian", alpha=1)
+lasso_linear_1 <- cv.glmnet(predictors, yvals |> as.matrix(),       family="gaussian", alpha=1)
 
@@
 
-ggplot(to_plot, aes(x=time, y=value, color=var, label=var))+geom_line()+geom_label_repel(data=to_plot |> filter(time==70), min.segment.length = 100, nudge_x = 15, na.rm = TRUE)+ theme(legend.position="none")+ scale_color_tableau("Classic 20")+
-  coord_cartesian(xlim=c(0,90), ylim=c(-.2, .3))+theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.ticks.x=element_blank())
+ggplot(to_plot, aes(x=time, y=value, color=var, label=var))+geom_line()+geom_label_repel(data=to_plot |> filter(time==70), min.segment.length = 100, nudge_x = 15, na.rm = TRUE)+
+  annotate("text", x=40, y=.3,label="Predicting subjective replication", color="black", size=5, hjust=1)+scale_color_tableau("Classic 20")+
+  coord_cartesian(xlim=c(0,90), ylim=c(-.2, .3))+theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.ticks.x=element_blank(), legend.position="none")
 
@@
 
-ggplot(to_plot, aes(x=time, y=value, color=var, label=var))+geom_line()+geom_label_repel(data=to_plot |> filter(time==70), min.segment.length = 100, nudge_x = 15, na.rm = TRUE)+ theme(legend.position="none")+ scale_color_tableau("Classic 20")+
-  coord_cartesian(xlim=c(0,90), ylim=c(-.2, .3))+theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.ticks.x=element_blank())
+ggplot(to_plot, aes(x=time, y=value, color=var, label=var))+geom_line()+geom_label_repel(data=to_plot |> filter(time==60), min.segment.length = 100, nudge_x = 20, na.rm = TRUE)+
+    annotate("text", x=30, y=.15,label="Predicting p-original", color="black", size=5, hjust=1)+
+theme(legend.position="none")+ scale_color_tableau("Classic 20")+
+  coord_cartesian(xlim=c(0,90))+theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.ticks.x=element_blank(), legend.position="none")
 ```
@@
 
-ggplot(to_plot, aes(x=time, y=value, color=var, label=var))+geom_line()+geom_label_repel(data=to_plot |> filter(time==55), min.segment.length = 100, nudge_x = 15, na.rm = TRUE)+ theme(legend.position="none")+ scale_color_tableau("Classic 20")+
+ggplot(to_plot, aes(x=time, y=value, color=var, label=var))+geom_line()+geom_label_repel(data=to_plot |> filter(time==55), min.segment.length = 100, nudge_x = 15, na.rm = TRUE)+
+      annotate("text", x=30, y=1.3,label="Predicting predictive interval", color="black", size=5, hjust=1)+ 
+theme(legend.position="none")+ scale_color_tableau("Classic 20")+
   coord_cartesian(xlim=c(0,80))+theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.ticks.x=element_blank())
@@
 
-ggplot(to_plot, aes(x=time, y=value, color=var, label=var))+geom_line()+geom_label_repel(data=to_plot |> filter(time==69), min.segment.length = 100, nudge_x = 15, na.rm = TRUE)+ theme(legend.position="none")+ scale_color_tableau("Classic 20")+
+ggplot(to_plot, aes(x=time, y=value, color=var, label=var))+geom_line()+geom_label_repel(data=to_plot |> filter(time==69), min.segment.length = 100, nudge_x = 15, na.rm = TRUE)+
+      annotate("text", x=40, y=.25,label="Predicting subjective replication", color="black", size=5, hjust=1)+
+theme(legend.position="none")+ scale_color_tableau("Classic 20")+
   coord_cartesian(xlim=c(0,90))+theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.ticks.x=element_blank())
@@
 ggplot(to_plot, aes(x=time, y=value, color=var, label=var))+geom_line()+geom_label_repel(data=to_plot |> filter(time==60), min.segment.length = 100, nudge_x = 15, na.rm = TRUE)+ theme(legend.position="none")+ scale_color_tableau("Classic 20")+
+      annotate("text", x=40, y=.25,label="Predicting predictive interval", color="black", size=5, hjust=1)+
+
   coord_cartesian(xlim=c(0,90))+theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.ticks.x=element_blank())
@@
 
-ggplot(to_plot, aes(x=time, y=value, color=var, label=var))+geom_line()+geom_label_repel(data=to_plot |> filter(time==71), min.segment.length = 100, nudge_x = 15, na.rm = TRUE)+ theme(legend.position="none")+ scale_color_tableau("Classic 20")+
+ggplot(to_plot, aes(x=time, y=value, color=var, label=var))+geom_line()+geom_label_repel(data=to_plot |> filter(time==61), min.segment.length = 100, nudge_x = 20, na.rm = TRUE)+
+        annotate("text", x=30, y=.15,label="Predicting p-original", color="black", size=5, hjust=1)+
+
+  theme(legend.position="none")+ scale_color_tableau("Classic 20")+
   coord_cartesian(xlim=c(0,90))+theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.ticks.x=element_blank())
@@
 
-ggplot(dat, aes(x=sub_rep, fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(legend.position = "none")+labs(y="Count", x="Subjective Replication score")
-
-ggplot(dat, aes(x=subfield, fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
-
-dat |> mutate(open_mat=ifelse(open_mat, "Open materials", "No open materials"), open_data=ifelse(open_data, "Open data", "No open data")) |> ggplot( aes(x=open_data |> factor(), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+facet_wrap(.~open_mat)+theme(axis.title.x=element_blank())
-
- ggplot(dat, aes(x=factor(stanford), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
-
-ggplot(dat, aes(x=factor(change_platform), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
-
-ggplot(dat, aes(x=ifelse(is_within, "Within", "Between"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(axis.title.x=element_blank())
-
-ggplot(dat, aes(x=ifelse(single_vignette, "1 vignette", "multiple vignettes"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(axis.title.x=element_blank())
+ggplot(dat, aes(x=sub_rep, fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(legend.position = "none", axis.text=element_text(size=11))+labs(y="Count", x="Subjective Replication score")
+
+ggplot(dat, aes(x=subfield, fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme( axis.text=element_text(size=11), axis.title.x=element_blank())
+
+dat |> mutate(open_mat=ifelse(open_mat, "Open materials", "No open materials"), open_data=ifelse(open_data, "Open data", "No open data")) |> ggplot( aes(x=open_data |> factor(), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+facet_wrap(.~open_mat)+theme(axis.title.x=element_blank())+theme( axis.text=element_text(size=11))
+
+ ggplot(dat, aes(x=ifelse(stanford, "Stanford affiliation", "No Stanford affiliation"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme( axis.text=element_text(size=11), axis.title.x=element_blank())
+
+ggplot(dat, aes(x=ifelse(change_platform,"Switch to online","Same modality"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme( axis.text=element_text(size=11), axis.title.x=element_blank())
+
+ggplot(dat, aes(x=ifelse(is_within, "Within", "Between"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(axis.title.x=element_blank())+theme( axis.text=element_text(size=11))
+
+ggplot(dat, aes(x=ifelse(single_vignette, "1 vignette", "multiple vignettes"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(axis.title.x=element_blank())+theme( axis.text=element_text(size=11))
 ```
@@
 # using d for model to get non-z-scored version
-ggplot(d_for_model, aes(x=pub_year, y=sub_rep, color=sub_rep))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()
-
-ggplot(d_for_model, aes(x=log_ratio_ss, y=log_sample, color=sub_rep))+geom_point()+scale_color_viridis()
-
-ggplot(d_for_model, aes(x=log_ratio_ss, y=sub_rep, color=sub_rep))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()
-
-ggplot(d_for_model, aes(x=log_sample, y=sub_rep, color=sub_rep))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()
-
-ggplot(d_for_model, aes(x=log_trials, y=sub_rep, color=sub_rep))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()
+ggplot(d_for_model, aes(x=pub_year, y=sub_rep, color=sub_rep))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()+theme( axis.text=element_text(size=11))
+
+ggplot(d_for_model, aes(x=log_ratio_ss, y=log_sample, color=sub_rep))+geom_point()+scale_color_viridis()+theme( axis.text=element_text(size=11))
+
+ggplot(d_for_model, aes(x=log_ratio_ss, y=sub_rep, color=sub_rep))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()+theme( axis.text=element_text(size=11))
+
+ggplot(d_for_model, aes(x=log_sample, y=sub_rep, color=sub_rep))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()+theme( axis.text=element_text(size=11))
+
+ggplot(d_for_model, aes(x=log_trials, y=sub_rep, color=sub_rep))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()+theme( axis.text=element_text(size=11))
 
@@
             z_pub_year=(pub_year-back_convert$mean_pub_year)/back_convert$sd_pub_year,
-            z_log_ratio_ss=(log_ratio_ss-back_convert$mean_log_ratio_ss)/back_convert$sd_log_ratio_ss, sub_rep=NA) |> 
-select(academic_year, sub_rep, 
-         z_pub_year, subfield, open_data, open_mat, stanford, change_platform, z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials)
-
-foo <- predict(tier1_subjective, newdata=fake_data)
-
-bar <- fitted(tier1_subjective, newdata=fake_data)
-```
+            z_log_ratio_ss=(log_ratio_ss-back_convert$mean_log_ratio_ss)/back_convert$sd_log_ratio_ss, sub_rep=NA) |> mutate(social=ifelse(subfield=="social", 1,0),other_psych=ifelse(subfield=="other-psych",1,0), non_psych=ifelse(subfield=="non-psych", 1,0)) |>
+select(z_pub_year, open_data, open_mat, stanford, change_platform, social, other_psych, non_psych, 
+                                   z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials) |> as.matrix()
+blah <- predict(lasso_linear_1, fake_data)           
+#foo <- predict(tier1_subjective, newdata=fake_data)
+
+#bar <- fitted(tier1_subjective, newdata=fake_data)
+```

### 2023-03-07 code/helper/parse_stats.R

@@ -131,8 +131,25 @@ parse_mean_ci2 <- function(mci,within_between,n){
   return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=m1-m2, "SE"=se_pool))
 }
 
-
-
+parse_mean_se2 <- function(mse,within_between,n){
+  cond1=str_extract(mse, "m1.*\\),")
+  cond2=str_extract(mse, "m2.*\\)")
+  m1=str_extract(cond1, "m1=.*\\(") |> str_sub(4,-2) |> as.numeric()
+  m2=str_extract(cond2, "m2=.*\\(") |> str_sub(4,-2) |> as.numeric()
+  se1=str_extract(cond1, "\\(.*\\),") |> str_sub(2,-3) |> as.numeric()
+  se2=str_extract(cond2, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
+  
+  per_group_n=ifelse(within_between=="within",n, n/2)
+  sd1=se1*sqrt(per_group_n-1) # assume equal groups
+  sd2=se2*sqrt(per_group_n-1)
+  sd_pool=sqrt((sd1**2+sd2**2)/2) # assume equal groups
+  se_pool=sd_pool/sqrt(n-1)
+  d_calc=abs(m1-m2)/sd_pool # note we force all positive and then fix later 
+  tval=(m1-m2)/se_pool |> abs()
+  df=ifelse(within_between=="within", n-1, n-2)
+  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
+  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=m1-m2, "SE"=se_pool))
+}
 
 parse_mean_sd2 <- function(msd,within_between,n){
   cond1=str_extract(msd, "m1.*\\),")
@@ -181,6 +198,7 @@ parse_mean_sd4 <- function(msd,within_between,n){
 
 #parse_mean_sd4(foo, "between", 10)
 
+#foo="MSE4:m1=4.8(.6),m2=5.5(.6),m3=3.8(.5),m4=3.7(.5)"
 parse_mean_se4 <- function(msd,within_between,n){
   cond1=str_extract(msd, "m1.*\\),m2")
[…]

### 2023-03-07 code/helper/stats.R

@@ -23,7 +23,7 @@ d_es <-  test |>
 
 
 do_pred_int <- function(target_ES, target_SE, rep_ES, rep_SE){
-  if(!is.na(target_ES)&!is.na(rep_ES)){
+  if(!is.na(target_ES)&!is.na(rep_ES)&!is.na(target_SE)&!is.na(rep_SE)){
     return(Replicate::pred_int(target_ES, target_SE**2, rep_ES, rep_SE**2)$rep.inside)
   }
   return(NA)

### 2023-03-07 code/process.Rmd
making images

@@
   scale_color_viridis(discrete=F, direction = 1, 
-                      name = "Subjective Replication Success")+
+                      name = "Subjective\nReplication\nSuccess\n")+
   labs(color="subrep", x="Original SMD", y="Replication SMD") + 
-  theme(legend.position = "bottom")
+  theme(legend.position = "right")
+
+ggsave(here("plots/smd.pdf"))
 
@@
   stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI predicting subjective replication score")+theme(axis.text=element_text(size=11))
+
+ggsave(here("plots/tier1.pdf"))
+
 ```
@@
   ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
-  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI predicting replication in predictive interval")+theme(axis.text=element_text(size=11))
+  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI predicting replication in prediction interval")+theme(axis.text=element_text(size=11))
+
+ggsave(here("plots/tier2_pred.pdf"))
+
 ```
@@
   stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI predicting p_original")+theme(axis.text=element_text(size=11))
+
+ggsave(here("plots/porig.pdf"))
+
 ```
@@
   stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI predicting subjective replication with stats predictors")+theme(axis.text=element_text(size=11))
+
+ggsave(here("plots/tier3sub.pdf"))
 ```
@@
   ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
-  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI predicting predictive interval with stats predictors")+theme(axis.text=element_text(size=11))
+  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI predicting prediction interval with stats predictors")+theme(axis.text=element_text(size=11))
+
+ggsave(here("plots/tier3pred.pdf"))
+
 ```
@@
   stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI predicting p_original with stats predictors")+theme(axis.text=element_text(size=11))
+
+ggsave(here("plots/tier3porig.pdf"))
+
 ```
@@
 
+ggsave(here("plots/corr.pdf"))
+
 #corr_mat |> as_tibble(rownames="value2") |> pivot_longer(cols=!value2, names_to="value1", values_to = "corr") |> arrange(corr) |> filter(value2 <value1) |> View()
@@
 #corr_mat |> as_tibble(rownames="value2") |> pivot_longer(cols=!value2, names_to="value1", values_to = "corr") |> arrange(desc(corr)) |> filter(value2 <value1)
+ggsave(here("plots/corr_all.pdf"))
 
@@
 
+ggsave(here("plots/tier1_lasso.pdf"))
+
 ```
@@
   coord_cartesian(xlim=c(0,90))+theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.ticks.x=element_blank(), legend.position="none")
+
+ggsave(here("plots/tier2_lasso_porig.pdf"))
+
 ```
@@
 ggplot(to_plot, aes(x=time, y=value, color=var, label=var))+geom_line()+geom_label_repel(data=to_plot |> filter(time==55), min.segment.length = 100, nudge_x = 15, na.rm = TRUE)+
-      annotate("text", x=30, y=1.3,label="Predicting predictive interval", color="black", size=5, hjust=1)+ 
+      annotate("text", x=30, y=1.3,label="Predicting prediction interval", color="black", size=5, hjust=1)+ 
 theme(legend.position="none")+ scale_color_tableau("Classic 20")+
   coord_cartesian(xlim=c(0,80))+theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.ticks.x=element_blank())
+
+ggsave(here("plots/tier2_lasso_pred.pdf"))
 
@@
 
+ggsave(here("plots/tier3_lasso_sub.pdf"))
+
 ```
@@
 ggplot(to_plot, aes(x=time, y=value, color=var, label=var))+geom_line()+geom_label_repel(data=to_plot |> filter(time==60), min.segment.length = 100, nudge_x = 15, na.rm = TRUE)+ theme(legend.position="none")+ scale_color_tableau("Classic 20")+
-      annotate("text", x=40, y=.25,label="Predicting predictive interval", color="black", size=5, hjust=1)+
+      annotate("text", x=40, y=1.5,label="Predicting prediction interval", color="black", size=5, hjust=1)+
 
   coord_cartesian(xlim=c(0,90))+theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.ticks.x=element_blank())
+
+ggsave(here("plots/tier3_lasso_pred.pdf"))
 
@@
   coord_cartesian(xlim=c(0,90))+theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.ticks.x=element_blank())
+
+ggsave(here("plots/tier3_lasso_porig.pdf"))
 
@@
 
+ggsave(here("plots/score_all.pdf"))
+
 ggplot(dat, aes(x=subfield, fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme( axis.text=element_text(size=11), axis.title.x=element_blank())
 
+ggsave(here("plots/subfield.pdf"))
+
 dat |> mutate(open_mat=ifelse(open_mat, "Open materials", "No open materials"), open_data=ifelse(open_data, "Open data", "No open data")) |> ggplot( aes(x=open_data |> factor(), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+facet_wrap(.~open_mat)+theme(axis.title.x=element_blank())+theme( axis.text=element_text(size=11))
 
+ggsave(here("plots/openness.pdf"))
+
  ggplot(dat, aes(x=ifelse(stanford, "Stanford affiliation", "No Stanford affiliation"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme( axis.text=element_text(size=11), axis.title.x=element_blank())
 
+ ggsave(here("plots/stanford.pdf"))
+
 ggplot(dat, aes(x=ifelse(change_platform,"Switch to online","Same modality"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme( axis.text=element_text(size=11), axis.title.x=element_blank())
 
+ggsave(here("plots/modality.pdf"))
+
 ggplot(dat, aes(x=ifelse(is_within, "Within", "Between"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(axis.title.x=element_blank())+theme( axis.text=element_text(size=11))
 
+ggsave(here("plots/within.pdf"))
+
 ggplot(dat, aes(x=ifelse(single_vignette, "1 vignette", "multiple vignettes"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(axis.title.x=element_blank())+theme( axis.text=element_text(size=11))
+
+ggsave(here("plots/vignette.pdf"))
+
 ```
@@
 
+ggsave(here("plots/pubyear.pdf"))
+
 ggplot(d_for_model, aes(x=log_ratio_ss, y=log_sample, color=sub_rep))+geom_point()+scale_color_viridis()+theme( axis.text=element_text(size=11))
 
+ggsave(here("plots/ss_v_sample.pdf"))
+
 ggplot(d_for_model, aes(x=log_ratio_ss, y=sub_rep, color=sub_rep))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()+theme( axis.text=element_text(size=11))
 
+ggsave(here("plots/ss_ratio.pdf"))
+
+ggplot(d_for_model, aes(x=log_trials, y=log_sample, color=sub_rep))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()+theme( axis.text=element_text(size=11))
+
+ggsave(here("plots/sample_v_trials.pdf"))
+
+ggplot(d_for_model, aes(x=log_trials+log_sample, y=sub_rep, color=sub_rep))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()+theme( axis.text=element_text(size=11))+labs(x="Trials * Subjects (log scale)")
+
+ggsave(here("plots/trial_sample.pdf"))
+
 ggplot(d_for_model, aes(x=log_sample, y=sub_rep, color=sub_rep))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()+theme( axis.text=element_text(size=11))
 
+ggsave(here("plots/log_sample.pdf"))
+
 ggplot(d_for_model, aes(x=log_trials, y=sub_rep, color=sub_rep))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()+theme( axis.text=element_text(size=11))
+
+ggsave(here("plots/log_trials.pdf"))
 

### 2023-03-08 code/process.Rmd
fussing

@@
   ggplot(aes(x=target_d_calc, y=rep_d_calc, color=sub_rep))+
-  geom_point() +
+
   geom_abline(slope=1, intercept=0, lty = 2)+
   geom_smooth(method = "lm") + 
+   geom_point(size=2.5) +
   geom_hline(yintercept = 0, lty = 2)+
@@
 ```{r}
+for_cor <- data_tier1 |> mutate(social=ifelse(subfield=="social", 1,0),other_psych=ifelse(subfield=="other-psych",1,0), non_psych=ifelse(subfield=="non-psych", 1,0)) 
 sub_cor <- function(var, stat = "estimate") {
   if (stat == "estimate") {
-    cor.test(data_tier1$sub_rep, pull(data_tier1, {{var}}))$estimate
+    cor.test(for_cor$sub_rep, pull(for_cor, {{var}}))$estimate
   } else {
-    cor.test(data_tier1$sub_rep, pull(data_tier1, {{var}}))$p.value
+    cor.test(for_cor$sub_rep, pull(for_cor, {{var}}))$p.value
   }
@@
            "z_log_ratio_ss", "is_within", "single_vignette", "z_log_sample", 
-           "z_log_trials")
+           "z_log_trials", "social", "other_psych", "non_psych")
 
@@
   mutate(r = sapply(preds, function(x) sub_cor(x, stat = "estimate")),
-         p = sapply(preds, function(x) sub_cor(x, stat = "p")))
-
-knitr::kable(cors, digits = 3)
+         p = sapply(preds, function(x) sub_cor(x, stat = "p"))) |> 
+  mutate(Predictors=factor(preds, levels=c("social", "other_psych", "non_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "z_pub_year", "z_log_trials", "z_log_sample", "z_log_ratio_ss"), labels=c("Social", "Other psych", "Non psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rep/orig sample"))) |> arrange(Predictors) |> select(Predictors, r, p)
+
+library(kableExtra)
+knitr::kable(cors, digits = 3, align='rcc') |> kable_styling(full_width=F, htmltable_class = "lightable-classic-2", font_size=40) 
 ```
@@
 
-ggplot(dat, aes(x=sub_rep, fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(legend.position = "none", axis.text=element_text(size=11))+labs(y="Count", x="Subjective Replication score")
+ggplot(dat, aes(x=sub_rep, fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(legend.position = "none", axis.text=element_text(size=14), axis.title=element_text(size=14))+labs(y="Count", x="Subjective Replication score")
 
@@
 
-ggplot(dat, aes(x=subfield, fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme( axis.text=element_text(size=11), axis.title.x=element_blank())
+dat |> mutate(subfield=factor(subfield, levels=c("cognitive", "social", "other-psych", "non-psych"), labels=c("Cognitive\npsychology", "Social\npsychology", "Other\npsychology", "Not\npsychology"))) |> ggplot(aes(x=subfield, fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(axis.text=element_text(size=14), axis.title=element_text(size=14), axis.title.x=element_blank())+labs(y="Count")
 
@@
 
-dat |> mutate(open_mat=ifelse(open_mat, "Open materials", "No open materials"), open_data=ifelse(open_data, "Open data", "No open data")) |> ggplot( aes(x=open_data |> factor(), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+facet_wrap(.~open_mat)+theme(axis.title.x=element_blank())+theme( axis.text=element_text(size=11))
+dat |> mutate(open_mat=ifelse(open_mat, "Open materials", "No open materials"), open_data=ifelse(open_data, "Open data", "No open data")) |> ggplot( aes(x=open_data |> factor(), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+facet_wrap(.~open_mat)+theme(axis.text=element_text(size=14), axis.title=element_text(size=14), axis.title.x=element_blank(), strip.text = element_text(size=14))+labs(y="Count")
 
@@
 
- ggplot(dat, aes(x=ifelse(stanford, "Stanford affiliation", "No Stanford affiliation"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme( axis.text=element_text(size=11), axis.title.x=element_blank())
-
- ggsave(here("plots/stanford.pdf"))
-
-ggplot(dat, aes(x=ifelse(change_platform,"Switch to online","Same modality"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme( axis.text=element_text(size=11), axis.title.x=element_blank())
+ # ggplot(dat, aes(x=ifelse(stanford, "Stanford affiliation", "No Stanford affiliation"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme( axis.text=element_text(size=11), axis.title.x=element_blank())
+ # ggsave(here("plots/stanford.pdf"))
+
+ggplot(dat, aes(x=ifelse(change_platform,"Switch to online","Same modality"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(axis.text=element_text(size=14), axis.title=element_text(size=14), axis.title.x=element_blank())+labs(y="Count")
 
@@
 
-ggplot(dat, aes(x=ifelse(is_within, "Within", "Between"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(axis.title.x=element_blank())+theme( axis.text=element_text(size=11))
+ggplot(dat, aes(x=ifelse(is_within, "Within", "Between"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(axis.text=element_text(size=14), axis.title=element_text(size=14), axis.title.x=element_blank())+labs(y="Count")
 
@@
 
-ggplot(dat, aes(x=ifelse(single_vignette, "1 vignette", "multiple vignettes"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(axis.title.x=element_blank())+theme( axis.text=element_text(size=11))
+ggplot(dat, aes(x=ifelse(single_vignette, "Single vignette", "Multiple vignettes"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(axis.text=element_text(size=14), axis.title=element_text(size=14), axis.title.x=element_blank())+labs(y="Count")
 
@@
 dat <- d_for_model |> filter(!is.na(predInt)) |>  mutate(predInt=predInt |> factor())
+
+# d_for_model |> filter(!is.na(predInt)) |>  mutate(porig.num=ifelse(p_orig>.05, 1,0))|> summarize(pred=mean(predInt), por=mean(p_orig), pornum=mean(porig.num))
 

### 2023-03-15 paper/manuscript.Rmd
start manuscript

---
title: PUT YOUR TITLE HERE
author:
  - name: Veronica Boyce
    affiliation: Stanford
    footnote:
      - corresp
  - name: Maya Mathur
    affiliation: Stanford
  - name: Michael C. Frank
    affiliation: Stanford
address:
  - code: Stanford
    address: Stanford University
footnote:
  - code: corresp
    text: "Corresponding author. Email: vboyce@stanford.edu"
bibliography: ["mybibfile.bib"] # Replace with one or more of your own bibtex files. Better BibTeX for Zotero is your friend
csl: dmk-format.csl # Use any CSL style. See https://www.zotero.org/styles for a good list. Ignored if citation_package: natbib
link-citations: TRUE
output:
  bookdown::pdf_document2:
    toc: FALSE
    keep_tex: TRUE
    template: generic_article_template.tex
    #md_extensions: "-autolink_bare_uris"
    number_sections: TRUE
    citation_package: default # Can also be "natbib"
lang: en # Main document language in BCP47 format
geometry: "margin=25mm"
papersize: a4
#linestretch: 2 # for double spacing
endfloat: FALSE # Set to TRUE to turn on latex endfloat package to place figures and tables at end of document
# endfloatoption: # See endfloat documentation for more possibilities
#   - tablesfirst # Default
#   - nomarkers # Default
numberlines: FALSE
authblk: TRUE # FALSE = author affiliations in footnotes; TRUE = author affiliations in a block below author names
footnotehyper: FALSE # TRUE will give you enhanced table footnote capabilities. Set to FALSE to be able to use French blocks. Needed due to what appears to be a latex bug.
urlcolor: blue
linkcolor: blue
citecolor: blue
graphics: TRUE # Needed to be able to include images
tables: TRUE # Needed to be able to include tables
# fancyhdr:
#   first:
#     #headleft: "REPORT-NO-XXXX"
#     headright: "Kaplan et al. (2021)"
#     headrulewidth: 0pt
#     #footleft: A left foot
#     footrulewidth: 0pt
#   subsequent:
#     #headleft: "NEXT-PAGE-HEADER-LEFT"
#     headright: "Kaplan et al. (2021)"
#     headrulewidth: 1pt
#     footrulewidth: 0pt

header-includes:
 - \usepackage{setspace}\singlespacing
 - \renewcommand{\textfraction}{0.00}
 - \renewcommand{\topfraction}{1}
 - \renewcommand{\bottomfraction}{1}
 - \renewcommand{\floatpagefraction}{1}
 - \setcounter{topnumber}{3}
 - \setcounter{bottomnumber}{3}
 - \setcounter{totalnumber}{4}

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE) # By default, hide code; set to TRUE to see code
#knitr::opts_chunk$set(fig.pos = 'th') # Places figures at top or here
knitr::opts_chunk$set(out.width = '100%', dpi=300,
                      fig.width=8, fig.width=8) # Figure resolution and size
knitr::opts_chunk$set(fig.env="figure") # Latex figure environment

options(knitr.table.format="latex") # For kable tables to work without setting format option

knitr::opts_chunk$set(echo=F, warning=F, message=F)#dev = "png", dev.args = list(type = "cairo-png")
 library("papaja")
library("bookdown")
library("rticles")
 library(here)
 library(tidyverse)
library(patchwork)
 library(brms)
 library(lme4)
 library(tidybayes)
 library(mgcv)
 library(cowplot)
 library(gridExtra)
library(broom.mixed)
library(tidymv)
library(mgcViz)
library(kableExtra)
#r_refs("r-references.bib", append=F)
theme_set(theme_bw())
options(knitr.table.format = "pdf")

model_location="code/models"
```

<!---------------------- Abstract --------------------->

::: {.abstract data-latex="" lang=en}
TODO abstract
:::

<!-- Use class keywords to format keywords section -->
::: {.keywords data-latex="" lang=en}
One keyword; Yet another keyword
:::

<!------------ Main text -------------------->

```{r, eval=F}
f <- googledrive::as_dribble("https://docs.google.com/spreadsheets/d/1UT6KLRujn6iEQ_s01_4yNfFYqc7hAWTpB-t9mdDp0O8/edit#gid=0")
googledrive::drive_download(f, path=here("data","raw_data.xlsx"), overwrite=T)

```

# TODO list
- need to do supplement with the stuff we preregistered (sensitivity analysis, all models)
- somewhere need discussion of how nobody is estimating p(true), but we're just more honest about it 
- meanings and codings of predictors (perhaps copied from pre-reg) should go in methods
- how to introduce coding methods
# introduction

[replication: it's a hot issue and concerns around replication have done a lot, see crisis/revolution] Replication is a hot topic. Some argue that it is a cornerstone of a cumulative science, and findings of low replication rates are a problem.

[ there is controversy here, but to even discuss it, we need empirics] Even those who argue that replication is not so essential still rely on data from replications to make their cases that replication rates are not as low as they seem and that these replication rates are acceptable.

[ there's ... not a lot of empirics] However, due to the arduous nature of collecting samples of replications, there have not been many large-scale replication efforts, so all of the argumentation around predictors of replications and field-wide replication rates is fit to a small number of data points.

Many replications of individual effects have been performed, but these are less useful as pattern analysis because the varied sampling and reporting, and the fact they aren't all in one place. Also pub bias.

We are aware of three large-scale replication efforts replicating experimental results in the existing psychology literature. The first is RP:P, which sampled roughly 100 studies from top psychology journals in 2008. They found an overall replication rate around 40%, which provided evidence to support growing concerns about the non-reliability of the literature. [idk, maybe worth framing that this was a big deal study when it came out]. TODO some discussion of how many papers have reanalysed this cutting the data different ways.

The ManyLabs series of studies have also done large-scale replications of effects from psychology. Due to their primary goal of investigating different forms of hetereogeneity, their sampling has been non-representive, focussing on short studies with only two conditions. Across Many labs 1-3 foo bar replicated. Many labs 5 was a re-replicaiton attempt on 10 of RP:P and rescued 2/10.

Camerer replicated the 21 behaviors studies published in Nature and Science from 2010-2015 that did not require special populations or special equipment. They found a roughly 60% replication rate.

In addition to determining estimated overall replicaiton rates for fields and journals, there's also merit in knowing what features of experiments (and replication attempts) are predictive of replication success. Blah blah stakeholders and resources. There's some signal here, as people are able to predict replication success at above chance CITATIONS. RP:P looked at how replication rates varied across subsamples of their studies. They found that cognitive psychology studies replicated at higher, but still low rates (50% v 25%) compared to social psychology. They also found that larger effect sizes and smaller p-values of original studies were predictive of replicating. TODO do we talk about any other correlates. There are reasons to believe that experimental factors such as number of items or between and within subject designs may also be predictive (cite our old paper), and could pontentially be some of the reason for subfield differences.

Here we introduce a new dataset of replications in the behavioral sciences, primarily psychology. Over the years 2011-2022, students in a graduate-level experimental methods class have conducted online replications as individual course projects. From this, we have 176 experimental replications that were codeable. This approximately doubles the set of experiments in the large-scale replication literature. We investigate predictors of replicability in this new dataset.

## quick methods
Class, taught by last author, is aimed at first-year graduate students, but taken by ... Since around 2015, it has been required for incoming PhD students in the Psychology Department. Over the course of a quarter long class, students work through their individual replication projects, from choosing a study, to reimplementing it, to creating analysis code, piloting the study, pre-registering it, and finally running a full data collection and writing up their results. Students are free to choose studies related to their interests, although recent articles from Psychological Science are the recommended path under uncertainty (leading to a high proportion of Psych science articles in this replication sample). While the sampling procedure is non-random, it is generally representative of studies that are of interest to and doable by first year grad students.

Studies vary along a number of dimensions, including statistical properties, subfield, and experimental properties. We leverage this naturally occurring variation to see if these properties predict replication success.

# results

As our primary outcome measure, we use a subjective measure of replication success. At the end of the class, the instruction team coded each project on a 0-1 scale indicating whether or not it replicated. This allows for nuance around marginal effects, covers studies with a broad range of statistical outcomes (including those that do not lend themselves to NHST), and includes studies with multiple important outcome measures. For robustness, first author independently coded all projects on the same scale off of the final write-ups. Disagreements (which occured foobar % of the time) were resolved by discussion between first and third authors.

Over the years, there have been a number of student projects, of these we are able to include foobar (see PRISMA). Because of variance in the experimental designs and reporting practices, we have variable statistical information. To address this, we conducted a series of models, balancing between including as many data points as possible, and including potentially relevant outcome and predictor variables. Here we focus on one set of models, the prediction of subjective replication outcome on the basis of the whole dataset without the statistical predictors. Other model results, including those from a sensitivity analysis, are avaiable in the supplement.

# Acknowledgements {-}

Acknowledge people here. `{-}` useful to not number this section.

# References {-}

<!-- Use this magic to place references here. -->
<div id="refs"></div>

# (APPENDIX) Appendices {-}

<!-- The above header does not appear in output. Not exactly sure why. -->

# Appendix A {-}

Some appendix text.

# Appendix B {-}

More appendix text.

### 2023-03-16 paper/manuscript.Rmd
text text text

@@
 - meanings and codings of predictors (perhaps copied from pre-reg) should go in methods
-- how to introduce coding methods
+- how to introduce coding methods (outcome measures)
+- add key figs and tables (max 8)
+- many citations everywhere
+- link to open stuffs
+
 # introduction
@@
 Here we focus on one set of models, the prediction of subjective replication outcome on the basis of the whole dataset without the statistical predictors.
-Other model results, including those from a sensitivity analysis, are avaiable in the supplement.
+Other model results, including those from a sensitivity analysis, are available in the supplement.
+
+# discussion
+
+[who knows where this paragraph should go] Replications are one way of approximating whether an effect in the target paper is true, and how likely results are to replicate in some sort of platonic ideal world.
+There is no one answer here; replication projects measure something else that could be treated as an approximation.
+However, what a replication is really measuring is how likely it to get that effect given some conditions.
+Which the right conditions are is a potential point of contention (see discussion around closeness and sample size, power etc).
+Here, we are explicit in what sample of replicators and replication conditions were are sampling, and thus what we can generalize to.
+We are estimating how likely replication is when done online by a graduate student, under constraints that are typical for graduate students (limited time, limited budget).
+As much of scientific process is in fact performed by graduate students, we think this in itself is an interesting question.
+It contrasts with questions like how likely something is to replicate when performed by an expert with a large budget (perhaps this is the right framing on Camerer) or when performed with extensive feedback from the original authors, etc.
+
+We do not interpret our results as saying that all non-replications were false positives (presumably some are replicable under other circumstances and others are not).
+Some of the factors we look at are more easily interpreted as being about the original study than others.
+We do not assign causal explanation to the predictors because there are multiple plausible interpretations: they could be correlates of QRPs in the original, they could be correlates of harder-to-detect or more fragile effects, they could be correlates of less-close replications, they could even be correlates of another stronger predictor.
+
+# methods
+Our pre-registration, code, and coded data is available at TODO OSF.
+
+## outcome measures
+Our primary outcome of interest is experimenter and instructor rated replication success (0-1).
+We chose this outcome because A) it had been recorded for the majority of class replications at the time they were conducted, and B) it avoids some of the complex statistical issues associated with evaluating whether a replication is successful (e.g., is the p-value on the replication significant, do the confidence intervals not overlap, etc.).
+As a complement, we will also use the following statistical outcomes as additional measures of replication success.
+These will be evaluated on one “key” statistical test per paper (typically identified by the student at the time of replication, but occasionally selected by our team if the student reported several key tests; see below).
+P_orig : what is the p value on the hypothesis that both results come from the same population
+PredInt: is the replication effect size within the prediction interval of the original effect size
+These measures are computed based on the replication project in Cancer Biology (RP:CB, Errington et al 2021).
+
+## coding procedure
+In order to code the measured variables, we relied primarily on student replication reports.
+These were supplemented with spreadsheets for the class created at the time of the class and the original papers when student’s replications did not provide enough information or were unclear.
+
+### replication success
+The replication success was coded for many projects by the teaching staff in the year it was conducted.
+Replication success was independently coded by VB based on student’s replication reports -- this often but not always aligned with students’ assessments of whether the replication succeeded.
+Projects that were not given numeric codes by the teaching staff were coded for replication by MCF on the basis of the replication reports.
+Where VB’s coding disagreed with the staff/MCF’s code, the difference was resolved by discussion between VB and MCF.
+These were coded on a [0, .25, .5, .75, 1] scale.
+
+### Demographic properties
+We coded the subfield of the original study as a 4 way factor: cognitive psychology, social psychology, other psychology, and non-psychology.
+For each paper, we coded its year of publication, whether it had open materials, whether it had open data, and whether it had been conducted using an online, crowd-sourced platform (i.e.
+MTurk or Prolific)
+
+### Experimental design properties
+
+Properties of the original experiment design were coded from the student’s replication reports which often included excerpts of the methods of the original.
+If this was insufficient, the original paper was referenced for clarification.
+To assess the role of repeated measures, we coded the number of trials seen per participant.
+We included filler trials and trials in all conditions, but excluded training or practice trials.
+We coded whether the manipulation in the study was instantiated in a single instance (“single vignette”).
+Studies with one induction or prime used per condition across participants were coded as having a single vignette.
+Studies with multiple instances of the manipulation (even if each participant only saw one) were coded as not being single vignette.
+While most studies with a signe vignette only had one trial and vice versa, there were studies with a single induction per condition, but multiple test trials, and studies with multiple scenarios instantiating the manipulation, only one scenario and 1 trial shown per participant.
+
+We coded the number of subjects, post-exclusions. We coded whether a study had a between-subjects, within-subjects, or mixed design; for analyses mixed studies were counted as within-subjects designs.
+
+### Properties of replication
+For the replication, we coded whether the replication was conducted on a crowd-sourced platform.
+Nearly all replications were, but a handful were done in person.
+For models, we coded whether the recruitment platfrom was changed between original and replication.
+This groups the few inperson replications in with the studies that were originally online and stayed online in a "no change" condition, in contrast with the studies that were originally in-person with online replications.
+
+We coded the replication sample size (after exclusions). In our models, this was transformed to the log ratio of replication to original sample size.
+
+As a control variable, we included whether the original authors were faculty at Stanford at the time of the replication.
+This is to account for potential non-independence of the replication (ex.
+if replicating an advisor's work, students may have access to extra information about methods).
+
+We made note of studies that should be excluded from some of the sensitivity analyses, due to not quite aligned statistics, extremely small or unbalanced sample sizes, or key effects that were not key in the original.
+
+### Determination and coding of key statistical measure
+For each paper, we used one “key measure of interest” for which we calculated the predictor variables of p-value and effect size and the statistical outcome measures p_orig and predInt. 
+If the student specified a key measure of interest and this was a measure that was reported in both the original paper and replication, we used that measure.
+When the student specified a single key measure, we used that; if a student specified multiple, equally important key measures, we used the first one.
+When students were not explicit about a key measure, we used other parts of their report (including introduction and power analysis) to determine what effect and therefore what result they considered key.
+In a few cases, we went back to the original paper to find what effect was considered the crucial one by the original authors.
+In a few cases, the measures reported by the student did not cleanly match their explicit or implicitly stated key measure; in these cases we picked the most important (or first) of the measures that were reported in both the original and replication.
+These decisions can be somewhat subjective but importantly they were made without reference to replication outcomes.
+
+Whenever possible, we used per-condition means and standard deviations, or the test statistic of the key measure and its corresponding degrees of freedom (ex.
+T test, F test).
+We took the original statistic from the replication report if it quoted the relevant analysis or from the original paper if not.
+We took the replication statistics from the replication report.
+
+We then calculated p values, ES, p_orig, and predInt.
+In cases where the test statistic was not sufficiently reported, but p-values and/or effect sizes were, we will use the reported p-value and or effect size.
+
+We choose to recalculate p values and effect sizes from the means or test statistic rather than use reported measures when possible because we think this approach is more reliable: The test statistic is more likely to have been outputted programmatically and copied directly into the text.
+In contrast, p-values are often reported as <.001 rather than as a point value, and effect size derivations may be error prone.
+By recording test statistics and using our available code to calculate other measures, we are transparent, as the test statistics are more likely to be unique and thus easy to search for in the papers, and all processing is documented in code.
+
+In some cases, p-values and or effect sizes were not calculable either due to insufficient reporting (ex.
+reporting a p-value but no other statistics from a test) or key measures where p-values and effect sizes did not apply (ex.
+PCA as measure of interest).
+In some other cases, both original and replication reported beta estimates for a coefficient along with the beta’s standard error or confidence interval.
+In these cases, we did not have the information to calculate standardized effect sizes, but we used the beta values to calculate p_orig and predInt.
+
+The direction of the effect of the replication was always coded consistently with the original study’s coding, so a positive effect was in the same direction as the original and a negative effect in the opposite direction.
+We separately coded whether the two effects were in the same direction, off of raw means or graphs.
+This is more reliable because F-tests don't include the direction of effect and also some students may have flipped the direction in coding for betas or t-tests.
+
+## modelling
+
+Due to the monotonic missingness of the data (see missingness discussion above), we have more predictor variables and outcome variables for some original-replication pairs than others.
+To take full advantage of the data, we will run a series of models, with some models having fewer predictors, but more data, and others having more predictors, but more limited data.
+
+In brief, these models are:
+
+On all data:
+Subjective replication score ~ demographic & experimental predictors
+On subset of data with p_orig and pred_int:
+P_orig ~ demographic & experimental predictors
+In_pred_int ~ demographic & experimental predictors
+On subset of data with standardized effect size: 
+Subjective replication score ~ demographic & experimental & statistical predictors
+P_orig ~ demographic & experimental & statistical predictors
+In_pred_int ~ demographic & experimental & statistical predictors
+
+Modelling approach
+
+The subjective replication scores were coded on [0, .25, .5, .75, 1], we will remap these to 1-5 and run an ordinal regression predicting replicate score.
+We will run logistic regressions predicting in_pred_int and linear regressions predicting P_orig.
+
+All models will use a horseshoe prior in brms.
+All models will include random slopes for predictors nested within years of the class (year) to control for variation between cohorts of students.
+We do not include any interaction terms in the models.
+All numeric predictor variables will be z-scored after other transforms (e.g., logs) to ensure comparable regularization effects from the horseshoe prior.
+
+Predictors:
+General Demographics
+Publication year 
+Field (coded as a 4-way factor: cognitive v social v other-psych v not-psych)
+Replication Closeness
+Open data (binary variable)
+Open materials (binary variable)
+Stanford affiliation of original study (binary variable)
+Change in platform as a binary scale (when both original and replication were on turk/prolific, or more rarely both were off turk/prolific are no-change; when original was off-turk/prolific but replication was on-turk/prolific are change)
+Ratio of Replication sample size to original sample size: log (replication / original )
+
+“Experimental” predictors
+Predictors
+Between versus within will be analyzed as a binary variable - for mixed designs, we will code these as within-participants if one component of the key analysis is within-participants.
+Our rationale is that there is some increase in precision of estimates based on having multiple observations per participant.
+Single vignette is a binary variable
+Number of trials per participant (coded on log scale)
+Original sample size (coded on log scale)
+
+“Statistical” Predictors
+Predictors
+Original p-value (coded on log scale)
+Original effect size (coded on normal scale)
+
+Sensitivity Analysis
+As a secondary sensitivity analysis, we will examine the subset of the data where the statistical tests have the same specification, the result is of primary importance in the original paper (i.e.
+not a manipulation check), and there were no big issues with the replication.
+In other words, we will do an analysis where we exclude studies where something was “borderline”.
+
+Results of more models in supplement.
 

### 2023-03-16 code/process.Rmd
add fake prisma

@@
 d_check_nas |> filter(include %in% c("stats")) |> filter(across(everything(), ~!is.na(.))) |> nrow()
+```
+
+# how close subrep
+
+```{r}
+
+ d_es_predInt |> filter(include %in% c("stats", "pred_int", "exp")) |> mutate(match=replicated_instructor_code==replicated_report_code) |> ungroup() |>  mutate(abs_dif=abs(replicated_instructor_code-replicated_report_code)) |> summarize(foo=mean(abs_dif))
+
 ```
@@
 )
+boring_logistic$coefficients |> as.tibble(rownames="coeff") |> mutate(odds=exp(value)) |> select(-value) |> filter(coeff!="(Intercept)") |> kable()
+
+fun <- glm(sub_rep ~  open_data *  open_mat,
+                       family=binomial, 
+                       data=data_tier1 |> mutate(sub_rep=(sub_rep-1)/4),
+
+)
 ```
@@
 ggplot(to_plot, aes(x=time, y=value, color=var, label=var))+geom_line()+geom_label_repel(data=to_plot |> filter(time==70), min.segment.length = 100, nudge_x = 15, na.rm = TRUE)+
-  annotate("text", x=40, y=.3,label="Predicting subjective replication", color="black", size=5, hjust=1)+scale_color_tableau("Classic 20")+
-  coord_cartesian(xlim=c(0,90), ylim=c(-.2, .3))+theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.ticks.x=element_blank(), legend.position="none")
+  scale_color_tableau("Classic 20")+
+  labs(y="Coefficient", x="more regularized <-       Degree of regularization       -> less regularized        \nfew predictors <-                                                    -> many predictors   \n worse fit to data <-                                                    -> better fit to data        ")+
+  coord_cartesian(xlim=c(0,90), ylim=c(-.2, .3))+theme(axis.text.x=element_blank(), axis.title=element_text(size=14), axis.ticks.x=element_blank(), legend.position="none")
 

### 2023-03-16 code/process.Rmd
work on floats

@@
 
+raw <- readxl::read_xlsx(here("data","raw_data.xlsx"), 
+                       sheet="aligned data", skip=1) |> select(target_lastauthor_year, sensitivity, include,
+         status, status_explanation,  academic_year, journal, target_cite, article_link, study_number,  subfield, target_year, stanford_internal, 
+         open_data, open_materials, target_on_turk, replication_on_turk, 
+         within_between, single_vignette, repeated_measure,
+         target_N, target_raw_stat, effect_description, same_dir, replication_N,
+         replication_raw_stat, replicated_instructor_code, replicated_report_code,
+         adjudicated_replication_code) |> write_csv(here("data","raw_data.csv"))
 ```
@@
 ```{r}
-d <- readxl::read_xlsx(here("data","raw_data.xlsx"), 
-                       sheet="aligned data", skip=1) |> 
+d <- read_csv(here("data", "raw_data.csv")) |> 
   select(target_lastauthor_year, sensitivity, include,
@@
 ```
-We have maybe as many as 177 at least for some analyses.
-
 Descriptions:
@@
 - "done" -- fully coded, can be used for whatever is specified in other column 
-- "ES_direction" -- we don't have the direction coded 
-- "ask" -- might be salvageable, but I have questions about coding
+- "cannot tell direction" -- have stats for an effect, but can't tell which direction it is in
 - "unusable" -- got as far as I can, and it does not have complete descriptives
@@
 
-Compute prediction intervals and p_orig.
+Compute prediction intervals and p_orig, write processed data to file.
 
@@
                                      replicated_report_code, 
-                                     adjudicated_replication_code))
+                                     adjudicated_replication_code)) |> write_csv(here("data","processed_data.csv"))
 ```
@@
          is_within, single_vignette, log_trials, 
-         predInt, p_orig, sub_rep)
+         predInt, p_orig, sub_rep) |> write_csv(here("data","for_model.csv"))
 

### 2023-03-16 paper/manuscript.Rmd
work on floats

@@
 header-includes:
+ - \usepackage{tikz}
+ - \usetikzlibrary{positioning,chains}
  - \usepackage{setspace}\singlespacing
@@
  library(tidyverse)
-library(patchwork)
  library(brms)
- library(lme4)
 library(tidybayes)
- library(mgcv)
- library(cowplot)
- library(gridExtra)
-library(broom.mixed)
-library(tidymv)
-library(mgcViz)
 library(kableExtra)
+library(viridis)
 #r_refs("r-references.bib", append=F)
@@
 model_location="code/models"
+
+d <- read_csv(here("data", "processed_data.csv"))
 ```
@@
 <!------------ Main text -------------------->
-
-```{r, eval=F}
-f <- googledrive::as_dribble("https://docs.google.com/spreadsheets/d/1UT6KLRujn6iEQ_s01_4yNfFYqc7hAWTpB-t9mdDp0O8/edit#gid=0")
-googledrive::drive_download(f, path=here("data","raw_data.xlsx"), overwrite=T)
-
-```
 
@@
 
+```{=latex}
+\definecolor{bad}{HTML}{FFCCCB}
+		\definecolor{meh}{HTML}{efefef}
+			\definecolor{good}{HTML}{abcdff}
+	\tikzset{
+		mynode/.style={
+			draw, rectangle, align=center, text width=4.5cm, scale=1, font=\small, inner sep=.5ex},
+		arrow/.style={
+		 very thick,->,>=stealth}
+	}
+
+\begin{figure}[ht]
+
+	\begin{tikzpicture}[
+		node distance=.8cm,
+		start chain=1 going below,
+		every join/.style=arrow,
+		]
+		\coordinate[on chain=1] (tc);
+		\node[mynode, on chain=1, fill=meh] (n2)
+		{\textbf{210} projects from 2011-2022};
+		\node[mynode, join, on chain=1, fill=meh] (n3)
+		{\textbf{189} original - replication pairs};
+		\node[mynode, join, on chain=1, fill=meh] (n4)
+		{\textbf{177} experimental pairs};
+		\node[mynode, join, on chain=1, fill=good] (n5)
+		{\textbf{176} pairs included};
+		\node[mynode, join, on chain=1, fill=good] (n6)
+		{\textbf{131} pairs with ES};
+		\node[mynode, join, on chain=1, fill=good] (n7)
+		{\textbf{107} pairs with SMD};
+
+		\begin{scope}[start chain=going right]
+			\chainin (n2);
+			\node[mynode, join, on chain, fill=bad]
+			{ \textbf{2} missing projects \\ \textbf{19} reproducibility projects};
+			\chainin (n3);
+			\node[mynode, join, on chain, fill=bad]
+			{\textbf{12} non-experimental pairs};
+			\chainin (n4);
+			\node[mynode, join, on chain, fill=bad]
+			{\textbf{1} pair missing sample size};
+		\end{scope}
+	\end{tikzpicture}
+\caption{Which studies were excluded for what reasons, and how many original-replication pairs are left.}\label{fig:prisma}
+\end{figure}
+
+```
+
+```{r smd, out.height="25%", fig.width=5, fig.height=3, fig.pos="ht", fig.cap="TODO caption here"}
+d |> 
+  filter(target_d_calc < 5, rep_d_calc < 5) |>
+  ggplot(aes(x=target_d_calc, y=rep_d_calc, color=sub_rep))+
+
+  geom_abline(slope=1, intercept=0, lty = 2)+
+  geom_smooth(method = "lm") + 
+   geom_point(size=2.5) +
+  geom_hline(yintercept = 0, lty = 2)+
+  scale_color_viridis(discrete=F, direction = 1, 
+                      name = "Subjective\nReplication\nSuccess\n")+
+  labs(color="subrep", x="Original SMD", y="Replication SMD") + 
+  theme(legend.position = "right")
+
+```
+
+```{r mod-results, out.height="25%", fig.width=5, fig.height=3, fig.pos="ht", fig.cap="TODO caption here"}
+tier1_subjective <- read_rds(here(model_location, "tier1_subjective.rds"))
+tier1_subjective |> 
+gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |> mutate(Term=factor(Term, levels=c("subfieldsocial", "subfieldother_psych", "subfieldnon_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "z_pub_year", "z_log_trials", "z_log_sample", "z_log_ratio_ss"), labels=c("Social", "Other psych", "Non psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rep/orig sample"))) |>
+  ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
+  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI predicting subjective replication score")+theme(axis.text=element_text(size=11))
+
+```
+
+```{r}
+
+for_cor <- read_csv(here("data","for_model.csv")) |> filter(include %in% c("stats", "exp", "pred_int")) |>
+  select(sub_rep, 
+         pub_year, subfield, open_data, open_mat, stanford, change_platform, log_ratio_ss, is_within, single_vignette, log_sample, log_trials) |> mutate(social=ifelse(subfield=="social", 1,0),other_psych=ifelse(subfield=="other-psych",1,0), non_psych=ifelse(subfield=="non-psych", 1,0))
+sub_cor <- function(var, stat = "estimate") {
+  if (stat == "estimate") {
+    cor.test(for_cor$sub_rep, pull(for_cor, {{var}}))$estimate
+  } else {
+    cor.test(for_cor$sub_rep, pull(for_cor, {{var}}))$p.value
+  }
+}
+
+preds <- c("pub_year", "open_data",  "open_mat", "stanford", "change_platform", 
+           "log_ratio_ss", "is_within", "single_vignette", "log_sample", 
+           "log_trials", "social", "other_psych", "non_psych")
+
+cors <- tibble(preds = preds) |>
+  mutate(r = sapply(preds, function(x) sub_cor(x, stat = "estimate")),
+         p = sapply(preds, function(x) sub_cor(x, stat = "p"))) |> 
+  mutate(Predictors=factor(preds, levels=c("social", "other_psych", "non_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "pub_year", "log_trials", "log_sample", "log_ratio_ss"), labels=c("Social", "Other psych", "Non psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rep/orig sample"))) |> arrange(r) |> select(Predictors, r, p)
+
+library(kableExtra)
+knitr::kable(cors, digits = 3, align='rcc',format="latex", position="!h", caption="TODO the correlation of individual predictors with subjective replication outcomes.
+For subfield, cognitive psychology is treated as the baseline condition.") |> kable_styling(full_width=F, font_size=10)
+
+```
+
+```{r}
+dat <- read_csv(here("data","for_model.csv")) |> filter(include %in% c("stats", "exp", "pred_int")) |> mutate(sub_rep=as.factor(sub_rep))
+
+sub_with_leg <- dat |> mutate(subfield=factor(subfield, levels=c("cognitive", "social", "other-psych", "non-psych"), 
+                                              labels=c("Cognitive\npsychology", "Social\npsychology", "Other\npsychology", "Not\npsychology"))) |>
+  ggplot(aes(x=subfield, fill=sub_rep))+
+  geom_bar(stat="count", position="dodge")+
+  scale_fill_viridis(discrete=T)+
+  theme(axis.text=element_text(size=14), axis.title=element_text(size=14), axis.title.x=element_blank())+
+  labs(y="Count", fill="Subjective \n replication \n score")
+
+leg <- get_legend(sub_with_leg)
+
+subfield <- sub_with_leg+theme(legend.position="none")
+
+open <- dat |> mutate(openness=case_when(
+  open_mat==1& open_data==1 ~ "Open materials \n Open data",
+  open_mat==1 ~ "Open materials \n No open data",
+  open_data==1 ~ "No open materials \n Open data",
+  T ~ "No open materials \n No open data")) |> 
+  ggplot( aes(x=openness |> factor(), fill=sub_rep))+
+  geom_bar(stat="count", position="dodge")+
+  scale_fill_viridis(discrete=T)+
+  theme(axis.text=element_text(size=14), axis.title=element_text(size=14), axis.title.x=element_blank(), legend.position="none")+
+  labs(y="Count")
+
+modal <- ggplot(dat, aes(x=ifelse(change_platform,"Switch to online","Same modality"), fill=sub_rep))+
+  geom_bar(stat="count", position="dodge")+
+  scale_fill_viridis(discrete=T)+
+  theme(axis.text=element_text(size=14), axis.title=element_text(size=14), axis.title.x=element_blank(), legend.position="none")+
+  labs(y="Count")
+
+within <- ggplot(dat, aes(x=ifelse(is_within, "Within", "Between"), fill=sub_rep))+
+  geom_bar(stat="count", position="dodge")+
+  scale_fill_viridis(discrete=T)+
+  theme(axis.text=element_text(size=14), axis.title=element_text(size=14), axis.title.x=element_blank(), legend.position="none")+
+  labs(y="Count")
+
+vignette <- ggplot(dat, aes(x=ifelse(single_vignette, "Single vignette", "Multiple vignettes"), fill=sub_rep))+
+  geom_bar(stat="count", position="dodge")+
+  scale_fill_viridis(discrete=T)+
+  theme(axis.text=element_text(size=14), axis.title=element_text(size=14), axis.title.x=element_blank(), legend.position="none")+
+  labs(y="Count")
+
+top_row <- plot_grid(subfield, modal, leg, rel_widths=c(1,.5,.5), nrow=1)
+mid_row <- plot_grid(open, within, vignette, rel_widths=c(1,.5,.5), nrow=1)
+plot_grid (top_row, mid_row, nrow=2)
+```
+
 As our primary outcome measure, we use a subjective measure of replication success.
@@
 
-Over the years, there have been a number of student projects, of these we are able to include foobar (see PRISMA).
+Over the years, there have been a number of student projects, of these we are able to include foobar (see Figure \ref{fig:prisma}).
 Because of variance in the experimental designs and reporting practices, we have variable statistical information.

### 2023-03-16 paper/manuscript.Rmd
work on figs

@@
 library(viridis)
+library(cowplot)
 #r_refs("r-references.bib", append=F)
@@
 
-```{r}
+```{r predictors-graph, out.width="100%", fig.width=8, fig.height=4, fig.pos="ht", fig.cap="y-axes are counts of studies in each category, with each subjective replication score. TODO caption here"}
 dat <- read_csv(here("data","for_model.csv")) |> filter(include %in% c("stats", "exp", "pred_int")) |> mutate(sub_rep=as.factor(sub_rep))
@@
   scale_fill_viridis(discrete=T)+
-  theme(axis.text=element_text(size=14), axis.title=element_text(size=14), axis.title.x=element_blank())+
-  labs(y="Count", fill="Subjective \n replication \n score")
+    coord_cartesian(ylim=c(0,55), expand=F)+
+  theme(axis.title.x=element_blank(), axis.title.y=element_blank())+
+  labs(fill="Subjective\nreplication\nscore")
 
@@
   scale_fill_viridis(discrete=T)+
-  theme(axis.text=element_text(size=14), axis.title=element_text(size=14), axis.title.x=element_blank(), legend.position="none")+
-  labs(y="Count")
+    coord_cartesian(ylim=c(0,55), expand=F)+
+  theme(axis.title.x=element_blank(), axis.title.y=element_blank(), legend.position="none")
 
-modal <- ggplot(dat, aes(x=ifelse(change_platform,"Switch to online","Same modality"), fill=sub_rep))+
+modal <- ggplot(dat, aes(x=ifelse(change_platform,"Switch to online\n","Same modality\n"), fill=sub_rep))+
   geom_bar(stat="count", position="dodge")+
   scale_fill_viridis(discrete=T)+
-  theme(axis.text=element_text(size=14), axis.title=element_text(size=14), axis.title.x=element_blank(), legend.position="none")+
-  labs(y="Count")
+    coord_cartesian(ylim=c(0,55), expand=F)+
+  theme(axis.title.y=element_blank(), axis.title.x=element_blank(), legend.position="none")
 
-within <- ggplot(dat, aes(x=ifelse(is_within, "Within", "Between"), fill=sub_rep))+
+within <- ggplot(dat, aes(x=ifelse(is_within, "Within \nsubjects", "Between\nsubjects"), fill=sub_rep))+
   geom_bar(stat="count", position="dodge")+
   scale_fill_viridis(discrete=T)+
-  theme(axis.text=element_text(size=14), axis.title=element_text(size=14), axis.title.x=element_blank(), legend.position="none")+
-  labs(y="Count")
+  coord_cartesian(ylim=c(0,55), expand=F)+
+  theme(axis.title.y=element_blank(), axis.title.x=element_blank(), legend.position="none")
 
-vignette <- ggplot(dat, aes(x=ifelse(single_vignette, "Single vignette", "Multiple vignettes"), fill=sub_rep))+
+vignette <- ggplot(dat, aes(x=ifelse(single_vignette, "Single \nvignette", "Multiple \nvignettes"), fill=sub_rep))+
   geom_bar(stat="count", position="dodge")+
   scale_fill_viridis(discrete=T)+
-  theme(axis.text=element_text(size=14), axis.title=element_text(size=14), axis.title.x=element_blank(), legend.position="none")+
-  labs(y="Count")
+    coord_cartesian(ylim=c(0,55), expand=F)+
+  theme(axis.title.y=element_blank(), axis.title.x=element_blank(), legend.position="none")
 
-top_row <- plot_grid(subfield, modal, leg, rel_widths=c(1,.5,.5), nrow=1)
-mid_row <- plot_grid(open, within, vignette, rel_widths=c(1,.5,.5), nrow=1)
+top_row <- plot_grid(subfield, within, vignette, rel_widths=c(1, .6, .6), nrow=1)
+mid_row <- plot_grid(open,  modal, leg, rel_widths=c(1.2, .6, .25), nrow=1)
 plot_grid (top_row, mid_row, nrow=2)

### 2023-03-17 paper/manuscript.Rmd
more writing words

@@
 # TODO list
+- title
+- abstract
 - need to do supplement with the stuff we preregistered (sensitivity analysis, all models)
-- somewhere need discussion of how nobody is estimating p(true), but we're just more honest about it 
-- meanings and codings of predictors (perhaps copied from pre-reg) should go in methods
 - how to introduce coding methods (outcome measures)
-- add key figs and tables (max 8)
 - many citations everywhere
+- long list of things to gesture at in intro
 - link to open stuffs
+- ** verify code for ES ** with someone
 
@@
 Some argue that it is a cornerstone of a cumulative science, and findings of low replication rates are a problem.
-
-[ there is controversy here, but to even discuss it, we need empirics] Even those who argue that replication is not so essential still rely on data from replications to make their cases that replication rates are not as low as they seem and that these replication rates are acceptable.
+Concerns about replication rates have become a large point of discussion in psychology and other fields.
 
 [ there's ...
-not a lot of empirics] However, due to the arduous nature of collecting samples of replications, there have not been many large-scale replication efforts, so all of the argumentation around predictors of replications and field-wide replication rates is fit to a small number of data points.
+not a lot of empirics]To quantify and understand this problem, we need empirical data about replication attempts.
+However, due to the arduous nature of collecting samples of replications, there have not been many large-scale replication efforts, so all of the argumentation around predictors of replications and field-wide replication rates is fit to a small number of data points.
 
@@
 The ManyLabs series of studies have also done large-scale replications of effects from psychology.
-Due to their primary goal of investigating different forms of hetereogeneity, their sampling has been non-representive, focussing on short studies with only two conditions.
+Due to their primary goal of investigating different forms of hetereogeneity, their sampling has been non-representive, focusing on short studies with only two conditions.
 Across Many labs 1-3 foo bar replicated.
-Many labs 5 was a re-replicaiton attempt on 10 of RP:P and rescued 2/10.
+Many labs 5 was a re-replication attempt on 10 of RP:P and rescued 2/10.
+TODO look up details
 
@@
 
+[could possibly frame with a bit of some=MCF have advocated teaching replication cite whatever, describe class, then thing? ]
 Here we introduce a new dataset of replications in the behavioral sciences, primarily psychology.
@@
 ## quick methods
-Class, taught by last author, is aimed at first-year graduate students, but taken by ...
+[some of this should actually just go in methods methods] Class, taught by last author, is an experimental methods class aimed at first-year graduate students, but taken by ...
 Since around 2015, it has been required for incoming PhD students in the Psychology Department.
@@
 
-# results
+# Results
+
+[again unclear the intro/ methods/results split]
+Over the years, there have been a number of student projects, of these we are able to include 176 (see Figure \ref{fig:prisma} for exclusions).
+Because of variance in the experimental designs and reporting practices, we have variable statistical information.
+To address this, we conducted a series of models, balancing between including as many data points as possible, and including potentially relevant outcome and predictor variables.
+Here we focus on one set of models, the prediction of subjective replication outcome on the basis of the whole dataset without the statistical predictors.
+Other model results, including those from a sensitivity analysis, are available in the supplement.
+
+As our primary outcome measure, we use a subjective measure of replication success.
+At the end of the class, the instruction team coded each project on a 0-1 scale indicating whether or not it replicated.
+This allows for nuance around marginal effects, covers studies with a broad range of statistical outcomes (including those that do not lend themselves to NHST), and includes studies with multiple important outcome measures.
+For robustness, first author independently coded all projects on the same scale off of the final write-ups.
+Disagreements (which occured foobar % of the time) were resolved by discussion between first and third authors.
+
+## Overall replication rate
+
+TODO write me! see Figure 2
+
+## Single predictors
+We drew a set of predictor variables from the correlational results of RP:P and our own intuitions about experimental factors that might impact replication success as well as some co-variates related to how close the replication would be.
+Many of these predictors individually correlate with subjective replication success (Figure \ref{tab:cor}.
+In particular, within-subjects designs, higher numbers of trials, and open data were predictive of replication.
+Single vignetted studies, social psychology studies, and original-replication pairs where the replication switched to online were less likely to replicate.
+Distributions of study outcomes across some of these properties are shown in Figure TODO.
+
+Both social and cognitive psychology studies were well represented, and the cognitive psychology studies replicated at a FOOBAR higher rate.
+Within and between subjects designs were both common, and within replicated at YY more.
+Similarly, studies with multiple vignettes replicated FOOBAR more.
+However, there are strong correlations between these experimental features and between experimental features and subfield.
+
+TODO say somthing about openness
+
+The study sample is split between studies that kept the same modality as the original (generally meaning that the original study used an online crowd-sourced sample) and those that switched.
+While TODO cite online studies are respectable, this does decrease the closeness of the replication, and some studies done in person may not have been well adapted (ex.
+inductions may be weaker or attention checks inadequate to the new sample).
+
+## Regression model
+We were interested in determining what the strongest predictors were, which ones are most meaningful, so we threw it all into a big ol regularlized regression model.
+Despite this, wide uncertainty due to parameterization and stuff.
+The coefficients see Figure 3 ...
+TODO
 
@@
 
-```{r smd, out.height="25%", fig.width=5, fig.height=3, fig.pos="ht", fig.cap="TODO caption here"}
+```{r smd, out.height="25%", fig.width=6, fig.height=3, fig.pos="ht", fig.cap="Relationship between SMD of the original study, SMD of the replication study, and subjective replication success rating, for those studies where SMD was applicable."}
 d |> 
@@
 
-```{r mod-results, out.height="25%", fig.width=5, fig.height=3, fig.pos="ht", fig.cap="TODO caption here"}
+```{r mod-results, out.height="25%", fig.width=8, fig.height=3, fig.pos="ht", fig.cap="Coefficient estimates and uncertainty from a model predicting subjective replication scores from the full dataset."}
 tier1_subjective <- read_rds(here(model_location, "tier1_subjective.rds"))
@@
 
-```{r}
+```{r cor}
 
@@
          p = sapply(preds, function(x) sub_cor(x, stat = "p"))) |> 
-  mutate(Predictors=factor(preds, levels=c("social", "other_psych", "non_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "pub_year", "log_trials", "log_sample", "log_ratio_ss"), labels=c("Social", "Other psych", "Non psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rep/orig sample"))) |> arrange(r) |> select(Predictors, r, p)
+  mutate(Predictors=factor(preds, levels=c("social", "other_psych", "non_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "pub_year", "log_trials", "log_sample", "log_ratio_ss"), labels=c("Social", "Other psych", "Non psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rep/orig sample"))) |> arrange(desc(r)) |> select(Predictors, r, p)
 
 library(kableExtra)
-knitr::kable(cors, digits = 3, align='rcc',format="latex", position="!h", caption="TODO the correlation of individual predictors with subjective replication outcomes.
+knitr::kable(cors, digits = 3, align='rcc',format="latex", position="!h", caption="The correlation of individual predictors with subjective replication outcomes.
 For subfield, cognitive psychology is treated as the baseline condition.") |> kable_styling(full_width=F, font_size=10)
@@
 
-```{r predictors-graph, out.width="100%", fig.width=8, fig.height=4, fig.pos="ht", fig.cap="y-axes are counts of studies in each category, with each subjective replication score. TODO caption here"}
+```{r predictors-graph, out.width="100%", fig.width=8, fig.height=4, fig.pos="ht", fig.cap="Distribution of subjective replication scores within categories. Bar heights are counts of studies."}
 dat <- read_csv(here("data","for_model.csv")) |> filter(include %in% c("stats", "exp", "pred_int")) |> mutate(sub_rep=as.factor(sub_rep))
@@
 
-As our primary outcome measure, we use a subjective measure of replication success.
-At the end of the class, the instruction team coded each project on a 0-1 scale indicating whether or not it replicated.
-This allows for nuance around marginal effects, covers studies with a broad range of statistical outcomes (including those that do not lend themselves to NHST), and includes studies with multiple important outcome measures.
-For robustness, first author independently coded all projects on the same scale off of the final write-ups.
-Disagreements (which occured foobar % of the time) were resolved by discussion between first and third authors.
-
-Over the years, there have been a number of student projects, of these we are able to include foobar (see Figure \ref{fig:prisma}).
-Because of variance in the experimental designs and reporting practices, we have variable statistical information.
-To address this, we conducted a series of models, balancing between including as many data points as possible, and including potentially relevant outcome and predictor variables.
-Here we focus on one set of models, the prediction of subjective replication outcome on the basis of the whole dataset without the statistical predictors.
-Other model results, including those from a sensitivity analysis, are available in the supplement.
-
 # discussion
@@
 
-# methods
-Our pre-registration, code, and coded data is available at TODO OSF.
+[ there is controversy here, but to even discuss it, we need empirics] Even those who argue that replication is not so essential still rely on data from replications to make their cases that replication rates are not as low as they seem and that these replication rates are acceptable.
 
-## outcome measures
-Our primary outcome of interest is experimenter and instructor rated replication success (0-1).
-We chose this outcome because A) it had been recorded for the majority of class replications at the time they were conducted, and B) it avoids some of the complex statistical issues associated with evaluating whether a replication is successful (e.g., is the p-value on the replication significant, do the confidence intervals not overlap, etc.).
-As a complement, we will also use the following statistical outcomes as additional measures of replication success.
-These will be evaluated on one “key” statistical test per paper (typically identified by the student at the time of replication, but occasionally selected by our team if the student reported several key tests; see below).
-P_orig : what is the p value on the hypothesis that both results come from the same population
-PredInt: is the replication effect size within the prediction interval of the original effect size
-These measures are computed based on the replication project in Cancer Biology (RP:CB, Errington et al 2021).
+# Methods
+Our pre-registration, code, and coded data are available at TODO OSF REPO.
 
-## coding procedure
-In order to code the measured variables, we relied primarily on student replication reports.
-These were supplemented with spreadsheets for the class created at the time of the class and the original papers when student’s replications did not provide enough information or were unclear.
+## Dataset
+The dataset of replication projects comes from class projects conducted in PSYCH 251 (earlier called PSYCH 24) a graduate-level experimental methods class taught by MCF from 2011 to 2022.
+Each student chose a study to replicate, implemented the study, wrote analysis code, pre-registered their replication, ran the study, and turned in a structured final report including methods, analytic plan, changes from the original study, confirmatory and exploratory analyses, and discussion of outcomes.
+Students were encouraged to do experimental replications, but some students chose to replicate correlational outcomes or do computational reproducibility projects instead.
+We cannot include the full student reports for confidentiality reasons, but we include an example as well as the template given to students in the repo.
+TODO example and template
 
-### replication success
-The replication success was coded for many projects by the teaching staff in the year it was conducted.
-Replication success was independently coded by VB based on student’s replication reports -- this often but not always aligned with students’ assessments of whether the replication succeeded.
-Projects that were not given numeric codes by the teaching staff were coded for replication by MCF on the basis of the replication reports.
+## Coding procedure
+We relied primarily on student reports to code the measured variables for the replications.
+We supplemented this with spreadsheets of information about projects from the time of the class and the original papers.
+
+### Measures of replication success
+Our primary replication outcome is experimenter and instructor rated replication success (0-1).
+The subjective replication success was recorded by the teaching staff for the majority of class replications at the time they were conducted.
+Where the values were missing they were filled in by MCF on the basis of the reports.
+For all studies, replication success was independently coded by VB on the basis of the reports.
 Where VB’s coding disagreed with the staff/MCF’s code, the difference was resolved by discussion between VB and MCF.
 These were coded on a [0, .25, .5, .75, 1] scale.
+
+This subjective replication outcome was chosen because it already existed, could be applied to all projects (regardless of type and detail of statistical reporting), and did not rely solely on one statistical measure.
+As a complement, we also identified a "key" statistical test for each paper (see below for details), and if possible, computed p_original and prediction interval at this statistic (following CITE RPCB).
+p_original was a continuous measure of the p-value on the hypothesis that the original and replication samples come from the same distribution.
+Prediction interval was a binary measure of whether the replication outcome fell within the prediction interval of the original outcome measure.
 
@@
 For each paper, we coded its year of publication, whether it had open materials, whether it had open data, and whether it had been conducted using an online, crowd-sourced platform (i.e.
-MTurk or Prolific)
+MTurk or Prolific).
 
 ### Experimental design properties
+We coded experimental design on the basis of student reports, which often quoted from the original methods, and if that did not suffice, the original paper itself.
+To assess the role of repeated measures, we coded the number of trials seen per participant, including filler trials and trials in all conditions, but excluding training or practice trials.
 
-Properties of the original experiment design were coded from the student’s replication reports which often included excerpts of the methods of the original.
-If this was insufficient, the original paper was referenced for clarification.
-To assess the role of repeated measures, we coded the number of trials seen per participant.
-We included filler trials and trials in all conditions, but excluded training or practice trials.
 We coded whether the manipulation in the study was instantiated in a single instance (“single vignette”).
@@
 Studies with multiple instances of the manipulation (even if each participant only saw one) were coded as not being single vignette.
-While most studies with a signe vignette only had one trial and vice versa, there were studies with a single induction per condition, but multiple test trials, and studies with multiple scenarios instantiating the manipulation, only one scenario and 1 trial shown per participant.
+While most studies with a single vignette only had one trial and vice versa, there were studies with a single induction and multiple test trials, and other studies with multiple scenarios instantiating the manipulation, but only one shown per participant.
 
-We coded the number of subjects, post-exclusions. We coded whether a study had a between-subjects, within-subjects, or mixed design; for analyses mixed studies were counted as within-subjects designs.
+We coded the number of subjects, post-exclusions.
+We coded whether a study had a between-subjects, within-subjects, or mixed design; for analyses mixed studies were counted as within-subjects designs.
+In the analysis, we used a log-scale for number of subjects and numbers of trials.
 
 ### Properties of replication
-For the replication, we coded whether the replication was conducted on a crowd-sourced platform.
-Nearly all replications were, but a handful were done in person.
-For models, we coded whether the recruitment platfrom was changed between original and replication.
-This groups the few inperson replications in with the studies that were originally online and stayed online in a "no change" condition, in contrast with the studies that were originally in-person with online replications.
+We coded whether the replication was conducted on a crowd-sourced platform; this was the norm for the class projects, but a few were done in person.
+As the predictor variable, we used whether the recruitment platform was changed between original and replication.
+This groups the few in-person replications in with the studies that were originally online and stayed online in a "no change" condition, in contrast with the studies that were originally in-person with online replications.
 
-We coded the replication sample size (after exclusions). In our models, this was transformed to the log ratio of replication to original sample size.
+We coded the replication sample size (after exclusions). This was transformed to the predictor variable log ratio of replication to original sample size.
 
@@
 This is to account for potential non-independence of the replication (ex.
-if replicating an advisor's work, students may have access to extra information about methods).
+if replicating their advisor's work, students may have access to extra information about methods).
 
-We made note of studies that should be excluded from some of the sensitivity analyses, due to not quite aligned statistics, extremely small or unbalanced sample sizes, or key effects that were not key in the original.
+We made note of studies to exclude from some of the sensitivity analyses, due to not quite aligned statistics, extremely small or unbalanced sample sizes, or where the key statistical measure the student chose was not of central importance to the original study.
 
 ### Determination and coding of key statistical measure
-For each paper, we used one “key measure of interest” for which we calculated the predictor variables of p-value and effect size and the statistical outcome measures p_orig and predInt. 
-If the student specified a key measure of interest and this was a measure that was reported in both the original paper and replication, we used that measure.
-When the student specified a single key measure, we used that; if a student specified multiple, equally important key measures, we used the first one.
+For each study pair, we used one key measure of interest for which we calculated the predictor variables of p-value and effect size and the statistical outcome measures p_original and prediction interval.
+If the student specified a single key measure of interest and this was a measure that was reported in both the original paper and replication, we used that measure.
+If a student specified multiple, equally important, key measures, we used the first one.
 When students were not explicit about a key measure, we used other parts of their report (including introduction and power analysis) to determine what effect and therefore what result they considered key.
-In a few cases, we went back to the original paper to find what effect was considered the crucial one by the original authors.
-In a few cases, the measures reported by the student did not cleanly match their explicit or implicitly stated key measure; in these cases we picked the most important (or first) of the measures that were reported in both the original and replication.
-These decisions can be somewhat subjective but importantly they were made without reference to replication outcomes.
+In a few cases, we went back to the original paper to find what effect was considered crucial by the original authors.
+When the measures reported by the student did not cleanly match their explicit or implicitly stated key measure, we picked the most important (or first) of the measures that were reported in both the original and replication.
+These decisions could be somewhat subjective but importantly they were made without reference to replication outcomes.
 
@@
 We then calculated p values, ES, p_orig, and predInt.
-In cases where the test statistic was not sufficiently reported, but p-values and/or effect sizes were, we will use the reported p-value and or effect size.
-
-We choose to recalculate p values and effect sizes from the means or test statistic rather than use reported measures when possible because we think this approach is more reliable: The test statistic is more likely to have been outputted programmatically and copied directly into the text.
+We choose to recalculate p values and effect sizes from the means or test statistic rather than use reported measures when possible because we thought this would be more reliable and transparent.
+The means and test statistics are more likely to have been outputted programmatically and copied directly into the text.
 In contrast, p-values are often reported as <.001 rather than as a point value, and effect size derivations may be error prone.
-By recording test statistics and using our available code to calculate other measures, we are transparent, as the test statistics are more likely to be unique and thus easy to search for in the papers, and all processing is documented in code.
+By recording the raw statistics we used and using our available code to calculate other measures, we are transparent, as the test statistics can be searched for in the papers, and all processing is documented in code.
 
@@
 PCA as measure of interest).
-In some other cases, both original and replication reported beta estimates for a coefficient along with the beta’s standard error or confidence interval.
-In these cases, we did not have the information to calculate standardized effect sizes, but we used the beta values to calculate p_orig and predInt.
+Where studies reported beta estimates and standard errors or proportions, SMD isn't an applicable measure, but we were still able to calculate p_original and prediction interval.
 
-The direction of the effect of the replication was always coded consistently with the original study’s coding, so a positive effect was in the same direction as the original and a negative effect in the opposite direction.
-We separately coded whether the two effects were in the same direction, off of raw means or graphs.
-This is more reliable because F-tests don't include the direction of effect and also some students may have flipped the direction in coding for betas or t-tests.
+We separately coded whether the original and replication effects were in the same direction, using raw means and graphs.
+This is more reliable than the statistics because F-tests don't include the direction of effect, and some students may have flipped the direction in coding for betas or t-tests.
+In the processed data, the direction of the effect of the replication was always coded consistently with the original study’s coding, so a positive effect was in the same direction as the original and a negative effect in the opposite direction.
 
-## modelling
+In regressions, we used SMD and log p-value as predictors.
 
-Due to the monotonic missingness of the data (see missingness discussion above), we have more predictor variables and outcome variables for some original-replication pairs than others.
-To take full advantage of the data, we will run a series of models, with some models having fewer predictors, but more data, and others having more predictors, but more limited data.
+## Modelling
 
-In brief, these models are:
+Due to the monotonic missingness of the data, we had more predictor variables and outcome variables for some original-replication pairs than others.
+To take full advantage of the data, we ran a series of models, with some models having fewer predictors, but more data, and others having more predictors, but more limited data.
 
-On all data:
-Subjective replication score ~ demographic & experimental predictors
-On subset of data with p_orig and pred_int:
-P_orig ~ demographic & experimental predictors
-In_pred_int ~ demographic & experimental predictors
-On subset of data with standardized effect size: 
-Subjective replication score ~ demographic & experimental & statistical predictors
-P_orig ~ demographic & experimental & statistical predictors
-In_pred_int ~ demographic & experimental & statistical predictors
+We ran a model predicting the subjective replication score on the basis of demographic and experimental predictors on the entire dataset; we ran two models predicting p_original and prediction interval from demographic and experimental predictors on the subset of data where we had p_original and prediction intervals.
+Then, on the smaller subset of the data where we had SMD and p-values, we re-ran these three models with those as additional predictor variables.
 
-Modelling approach
+The subjective replication scores were coded on [0, .25, .5, .75, 1], and we ramapped these to 1-5 to run an ordinal regression predicting replication score.
+We ran logistic regressions predicting prediction interval and linear regressions predicting p_original.
 
-The subjective replication scores were coded on [0, .25, .5, .75, 1], we will remap these to 1-5 and run an ordinal regression predicting replicate score.
-We will run logistic regressions predicting in_pred_int and linear regressions predicting P_orig.
+All models used a horseshoe prior in brms.
+All models will include random slopes for predictors nested within years of the class (year) to control for variation between cohorts of students.
+We did not include any interaction terms in the models.
+All numeric predictor variables were z-scored after other transforms (e.g., logs) to ensure comparable regularization effects from the horseshoe prior.
 
-All models will use a horseshoe prior in brms.
-All models will include random slopes for predictors nested within years of the class (year) to control for variation between cohorts of students.
-We do not include any interaction terms in the models.
-All numeric predictor variables will be z-scored after other transforms (e.g., logs) to ensure comparable regularization effects from the horseshoe prior.
+As a secondary sensitivity analysis, we examined the subset of the data where the statistical tests had the same specification, the result was of primary importance in the original paper (i.e.
+not a manipulation check), and there were no big issues with the replication.
 
-Predictors:
-General Demographics
-Publication year 
-Field (coded as a 4-way factor: cognitive v social v other-psych v not-psych)
-Replication Closeness
-Open data (binary variable)
-Open materials (binary variable)
-Stanford affiliation of original study (binary variable)
-Change in platform as a binary scale (when both original and replication were on turk/prolific, or more rarely both were off turk/prolific are no-change; when original was off-turk/prolific but replication was on-turk/prolific are change)
-Ratio of Replication sample size to original sample size: log (replication / original )
-
-“Experimental” predictors
-Predictors
-Between versus within will be analyzed as a binary variable - for mixed designs, we will code these as within-participants if one component of the key analysis is within-participants.
-Our rationale is that there is some increase in precision of estimates based on having multiple observations per participant.
-Single vignette is a binary variable
-Number of trials per participant (coded on log scale)
-Original sample size (coded on log scale)
-
-“Statistical” Predictors
-Predictors
-Original p-value (coded on log scale)
-Original effect size (coded on normal scale)
-
-Sensitivity Analysis
-As a secondary sensitivity analysis, we will examine the subset of the data where the statistical tests have the same specification, the result is of primary importance in the original paper (i.e.
-not a manipulation check), and there were no big issues with the replication.
-In other words, we will do an analysis where we exclude studies where something was “borderline”.
-
-Results of more models in supplement.
+Results of more models in supplement. TODO
 

### 2023-03-17 paper/manuscript.Rmd
throw in some cites

@@
     text: "Corresponding author. Email: vboyce@stanford.edu"
-bibliography: ["mybibfile.bib"] # Replace with one or more of your own bibtex files. Better BibTeX for Zotero is your friend
+bibliography: ["251MA.bib"] # Replace with one or more of your own bibtex files. Better BibTeX for Zotero is your friend
 csl: dmk-format.csl # Use any CSL style. See https://www.zotero.org/styles for a good list. Ignored if citation_package: natbib
@@
 We are aware of three large-scale replication efforts replicating experimental results in the existing psychology literature.
-The first is RP:P, which sampled roughly 100 studies from top psychology journals in 2008.
+RP:P sampled roughly 100 studies from top psychology journals in 2008 [@openscienceconsortium2015].
 They found an overall replication rate around 40%, which provided evidence to support growing concerns about the non-reliability of the literature.
@@
 Due to their primary goal of investigating different forms of hetereogeneity, their sampling has been non-representive, focusing on short studies with only two conditions.
-Across Many labs 1-3 foo bar replicated.
-Many labs 5 was a re-replication attempt on 10 of RP:P and rescued 2/10.
+Across Many labs 1-3 foo bar replicated [@klein2014; @klein2018; @ebersole2016].
+Many labs 5 was a re-replication attempt on 10 of RP:P and rescued 2/10 [@ebersole2020].
 TODO look up details
 
-Camerer replicated the 21 behaviors studies published in Nature and Science from 2010-2015 that did not require special populations or special equipment. They found a roughly 60% replication rate.
+@camerer2018 replicated the 21 behaviors studies published in Nature and Science from 2010-2015 that did not require special populations or special equipment.
+They found a roughly 60% replication rate.
 
@@
 Blah blah stakeholders and resources.
-There's some signal here, as people are able to predict replication success at above chance CITATIONS.
+There's some signal here, as people are able to predict replication success at above chance CITATIONS @hoogeveen2019.
 RP:P looked at how replication rates varied across subsamples of their studies.
@@
 
-[could possibly frame with a bit of some=MCF have advocated teaching replication cite whatever, describe class, then thing? ]
+[could possibly frame with a bit of some=MCF have advocated teaching replication cite whatever, describe class, then thing? @frank2012; @hawkins]
 Here we introduce a new dataset of replications in the behavioral sciences, primarily psychology.
@@
 
+As secondary outcomes, we also calculated prediction intervals following @errington2021 on the key measure of interest from each study.
+Because of variable statistics and reporting, this was calculable on FOOBAR studies.
+
 ## Overall replication rate
 
-TODO write me! see Figure 2
+Across the 176 studies, the overall replication rate was 49% TODO derive in code.
+FOOBAR % of the studies had replication outcomes within the prediction interval of the original outcome.
+The average p_original value (median?) was TODO.
+
+For the FOOBAR studies with SMD, we see cite FIGURE.
 
@@
 [ there is controversy here, but to even discuss it, we need empirics] Even those who argue that replication is not so essential still rely on data from replications to make their cases that replication rates are not as low as they seem and that these replication rates are acceptable.
+@lewandowsky2020
 
@@
 This subjective replication outcome was chosen because it already existed, could be applied to all projects (regardless of type and detail of statistical reporting), and did not rely solely on one statistical measure.
-As a complement, we also identified a "key" statistical test for each paper (see below for details), and if possible, computed p_original and prediction interval at this statistic (following CITE RPCB).
+As a complement, we also identified a "key" statistical test for each paper (see below for details), and if possible, computed p_original and prediction interval at this statistic, following @errington2021.
 p_original was a continuous measure of the p-value on the hypothesis that the original and replication samples come from the same distribution.

### 2023-03-17 paper/manuscript.tex
throw in some cites

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  english,
  a4paper,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={PUT YOUR TITLE HERE},
  pdflang={en},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={blue},
  urlcolor={blue},
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=25mm]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\usepackage{footnote} % For some unknown reason, footnotehyper clashes with French
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% dont indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

%%%%%%%% START HEADER PARTIAL %%%%%%%%%%%%

% Formatting of tables & knitr::kable and kableExtra functionality
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}

% Line numbering

% endfloat stuff

% fancyhdr pagestyle

% Environment for keywords
\makeatletter
\newcommand\keywordsname{Keywords}
\newenvironment*{keywords}[1][\keywordsname]{\if@twocolumn \else \small \quotation \fi \begin{center} \textbf{\textit{#1} \\}}{\end{center}\if@twocolumn \else \small \endquotation \fi}
\newenvironment*{keywordsinline}[1][\keywordsname]{\if@twocolumn \else \small \quotation \fi \begin{center} \textbf{\textit{#1}: }}{\end{center}\if@twocolumn \else \small \endquotation \fi}
\makeatother

% Environment for abstract that takes new abstract name
\newenvironment{renameableabstract}[1][\abstractname]{\let\oldabstractname\abstractname \renewcommand{\abstractname}{#1} \begin{abstract}}{\end{abstract} \renewcommand{\abstractname}{\oldabstractname}}

%%%%%%%% END HEADER PARTIAL %%%%%%%%%%%%

\usepackage{tikz}
\usetikzlibrary{positioning,chains}
\usepackage{setspace}\singlespacing
\renewcommand{\textfraction}{0.00}
\renewcommand{\topfraction}{1}
\renewcommand{\bottomfraction}{1}
\renewcommand{\floatpagefraction}{1}
\setcounter{topnumber}{3}
\setcounter{bottomnumber}{3}
\setcounter{totalnumber}{4}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifXeTeX
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{}
\else
  \usepackage[english,main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{PUT YOUR TITLE HERE}

%%%%%%% START AUTHOR PARTIAL %%%%%%%%%%%%%%%

%%%%% Authors, affiliations and author notes stuff %%%%%

% Macros for creating and referencing stored reference
\makeatletter
\def\MyNewLabel#1#2#3{\expandafter\gdef\csname #1@#2\endcsname{#3}}

\def\MyRef#1#2{\@ifundefined{#1@#2}{???}{\csname #1@#2\endcsname}}

\newcommand*\ifcounter[1]{%
  \ifcsname c@#1\endcsname
    \expandafter\@firstoftwo
  \else
    \expandafter\@secondoftwo
  \fi
}
\makeatother

% Create labels for Addresses if the are given by code
\MyNewLabel{ADDRTXT}{Stanford}{Stanford University}

% Create labels for Footnotes if they are given by code
\MyNewLabel{ANOTETXT}{corresp}{Corresponding author. Email: \href{mailto:vboyce@stanford.edu}{\nolinkurl{vboyce@stanford.edu}}}

%%% Special footnotes for addresses and author footnotes
\usepackage{bigfoot}
\DeclareNewFootnote{Addr}[arabic] % Only used for NOT authblk
\DeclareNewFootnote{ANote}[fnsymbol]

%%% Address and author notes as a function of format %%%
 % Use authblk for affiliations %%%%%%%%%%%
\usepackage{authblk}

% Always separate by commas
\renewcommand\Authsep{, }
\renewcommand\Authand{, }
\renewcommand\Authands{, }

% Counter for addresses and footnotes
\newcounter{addrcnt}

% thanks definition that doesnt produce superscript marks
\makeatletter
\newcommand*\createaddrlblbycode[1]{%
  \ifcounter{ADDRLBL@#1}
    {}
    {\refstepcounter{addrcnt}\newcounter{ADDRLBL@#1}\setcounter{ADDRLBL@#1}{\value{addrcnt}}}%
}

\newcommand*\addrlblbycode[1]{\arabic{ADDRLBL@#1}}

\newcommand*\addrbycode[1]{%
  \ifcounter{ADDR@#1}
    {}
    {\newcounter{ADDR@#1}%
     \affil[\addrlblbycode{#1}]{\MyRef{ADDRTXT}{#1}}}%
}

\newcommand*\createanotelblbycode[1]{%
  \ifcounter{ANOTELBL@#1}
    {}
    {\refstepcounter{footnoteANote}\newcounter{ANOTELBL@#1}\setcounter{ANOTELBL@#1}{\value{footnoteANote}}}%
}

\newcommand*\anotelblbycode[1]{\fnsymbol{ANOTELBL@#1}}

\newcommand*\anotebycode[1]{%
  \ifcounter{ANOTE@#1}
    {}
    {\newcounter{ANOTE@#1}%
     \footnotetextANote[\value{ANOTELBL@#1}]{\MyRef{ANOTETXT}{#1}}}%
}
\makeatother

\createaddrlblbycode{Stanford}

\createanotelblbycode{corresp}

\author[%
\addrlblbycode{Stanford}%
,%
$\anotelblbycode{corresp}$%
]{Veronica Boyce}

\addrbycode{Stanford}

\createaddrlblbycode{Stanford}

\author[%
\addrlblbycode{Stanford}%
]{Maya Mathur}

\addrbycode{Stanford}

\createaddrlblbycode{Stanford}

\author[%
\addrlblbycode{Stanford}%
]{Michael C. Frank}

\addrbycode{Stanford}

%endif(authblk)

%%%%%%%%% END AUTHOR PARTIAL %%%%%%%%

\date{}

\begin{document}
\maketitle

%%%%%%%%%% START AFTER TITLE PARTIAL %%%%%%%%%%%%%
\anotebycode{corresp}

%%%%%%%%%% END AFTER TITLE PARTIAL %%%%%%%%%%%%%

\begin{otherlanguage}{english}

\begin{abstract}
TODO abstract

\end{abstract}

\end{otherlanguage}

\begin{otherlanguage}{english}

\begin{keywords}
One keyword; Yet another keyword

\end{keywords}

\end{otherlanguage}

\hypertarget{todo-list}{%
\section{TODO list}\label{todo-list}}

\begin{itemize}
\tightlist
\item
  title
\item
  abstract
\item
  need to do supplement with the stuff we preregistered (sensitivity analysis, all models)
\item
  how to introduce coding methods (outcome measures)
\item
  many citations everywhere
\item
  long list of things to gesture at in intro
\item
  link to open stuffs
\item
  ** verify code for ES ** with someone
\end{itemize}

\hypertarget{introduction}{%
\section{introduction}\label{introduction}}

{[}replication: it's a hot issue and concerns around replication have done a lot, see crisis/revolution{]} Replication is a hot topic. Some argue that it is a cornerstone of a cumulative science, and findings of low replication rates are a problem. Concerns about replication rates have become a large point of discussion in psychology and other fields.

{[} there's \ldots{} not a lot of empirics{]}To quantify and understand this problem, we need empirical data about replication attempts. However, due to the arduous nature of collecting samples of replications, there have not been many large-scale replication efforts, so all of the argumentation around predictors of replications and field-wide replication rates is fit to a small number of data points.

Many replications of individual effects have been performed, but these are less useful as pattern analysis because the varied sampling and reporting, and the fact they aren't all in one place. Also pub bias.

We are aware of three large-scale replication efforts replicating experimental results in the existing psychology literature. RP:P sampled roughly 100 studies from top psychology journals in 2008 (\protect\hyperlink{ref-openscienceconsortium2015}{Consortium 2015}). They found an overall replication rate around 40\%, which provided evidence to support growing concerns about the non-reliability of the literature. {[}idk, maybe worth framing that this was a big deal study when it came out{]}. TODO some discussion of how many papers have reanalysed this cutting the data different ways.

The ManyLabs series of studies have also done large-scale replications of effects from psychology. Due to their primary goal of investigating different forms of hetereogeneity, their sampling has been non-representive, focusing on short studies with only two conditions. Across Many labs 1-3 foo bar replicated (\protect\hyperlink{ref-klein2014}{Klein et al. 2014}, \protect\hyperlink{ref-ebersole2016}{Ebersole et al. 2016}, \protect\hyperlink{ref-klein2018}{Klein et al. 2018}). Many labs 5 was a re-replication attempt on 10 of RP:P and rescued 2/10 (\protect\hyperlink{ref-ebersole2020}{Ebersole et al. 2020}). TODO look up details

Camerer et al. (\protect\hyperlink{ref-camerer2018}{2018}) replicated the 21 behaviors studies published in Nature and Science from 2010-2015 that did not require special populations or special equipment. They found a roughly 60\% replication rate.

In addition to determining estimated overall replicaiton rates for fields and journals, there's also merit in knowing what features of experiments (and replication attempts) are predictive of replication success. Blah blah stakeholders and resources. There's some signal here, as people are able to predict replication success at above chance CITATIONS Hoogeveen et al. (\protect\hyperlink{ref-hoogeveen2019}{2019}). RP:P looked at how replication rates varied across subsamples of their studies. They found that cognitive psychology studies replicated at higher, but still low rates (50\% v 25\%) compared to social psychology. They also found that larger effect sizes and smaller p-values of original studies were predictive of replicating. TODO do we talk about any other correlates. There are reasons to believe that experimental factors such as number of items or between and within subject designs may also be predictive (cite our old paper), and could pontentially be some of the reason for subfield differences.

(could possibly frame with a bit of some=MCF have advocated teaching replication cite whatever, describe class, then thing? \protect\hyperlink{ref-frank2012}{Frank \& Saxe 2012}, \protect\hyperlink{ref-hawkins}{Hawkins et al. n.d.})
Here we introduce a new dataset of replications in the behavioral sciences, primarily psychology. Over the years 2011-2022, students in a graduate-level experimental methods class have conducted online replications as individual course projects. From this, we have 176 experimental replications that were codeable. This approximately doubles the set of experiments in the large-scale replication literature. We investigate predictors of replicability in this new dataset.

\hypertarget{quick-methods}{%
\subsection{quick methods}\label{quick-methods}}

{[}some of this should actually just go in methods methods{]} Class, taught by last author, is an experimental methods class aimed at first-year graduate students, but taken by \ldots{} Since around 2015, it has been required for incoming PhD students in the Psychology Department. Over the course of a quarter long class, students work through their individual replication projects, from choosing a study, to reimplementing it, to creating analysis code, piloting the study, pre-registering it, and finally running a full data collection and writing up their results. Students are free to choose studies related to their interests, although recent articles from Psychological Science are the recommended path under uncertainty (leading to a high proportion of Psych science articles in this replication sample). While the sampling procedure is non-random, it is generally representative of studies that are of interest to and doable by first year grad students.

Studies vary along a number of dimensions, including statistical properties, subfield, and experimental properties. We leverage this naturally occurring variation to see if these properties predict replication success.

\hypertarget{results}{%
\section{Results}\label{results}}

{[}again unclear the intro/ methods/results split{]}
Over the years, there have been a number of student projects, of these we are able to include 176 (see Figure \ref{fig:prisma} for exclusions). Because of variance in the experimental designs and reporting practices, we have variable statistical information. To address this, we conducted a series of models, balancing between including as many data points as possible, and including potentially relevant outcome and predictor variables. Here we focus on one set of models, the prediction of subjective replication outcome on the basis of the whole dataset without the statistical predictors. Other model results, including those from a sensitivity analysis, are available in the supplement.

As our primary outcome measure, we use a subjective measure of replication success. At the end of the class, the instruction team coded each project on a 0-1 scale indicating whether or not it replicated. This allows for nuance around marginal effects, covers studies with a broad range of statistical outcomes (including those that do not lend themselves to NHST), and includes studies with multiple important outcome measures. For robustness, first author independently coded all projects on the same scale off of the final write-ups. Disagreements (which occured foobar \% of the time) were resolved by discussion between first and third authors.

As secondary outcomes, we also calculated prediction intervals following Errington et al. (\protect\hyperlink{ref-errington2021}{2021}) on the key measure of interest from each study. Because of variable statistics and reporting, this was calculable on FOOBAR studies.

\hypertarget{overall-replication-rate}{%
\subsection{Overall replication rate}\label{overall-replication-rate}}

Across the 176 studies, the overall replication rate was 49\% TODO derive in code. FOOBAR \% of the studies had replication outcomes within the prediction interval of the original outcome. The average p\_original value (median?) was TODO.

For the FOOBAR studies with SMD, we see cite FIGURE.

\hypertarget{single-predictors}{%
\subsection{Single predictors}\label{single-predictors}}

We drew a set of predictor variables from the correlational results of RP:P and our own intuitions about experimental factors that might impact replication success as well as some co-variates related to how close the replication would be. Many of these predictors individually correlate with subjective replication success (Figure \ref{tab:cor}. In particular, within-subjects designs, higher numbers of trials, and open data were predictive of replication. Single vignetted studies, social psychology studies, and original-replication pairs where the replication switched to online were less likely to replicate. Distributions of study outcomes across some of these properties are shown in Figure TODO.

Both social and cognitive psychology studies were well represented, and the cognitive psychology studies replicated at a FOOBAR higher rate. Within and between subjects designs were both common, and within replicated at YY more. Similarly, studies with multiple vignettes replicated FOOBAR more. However, there are strong correlations between these experimental features and between experimental features and subfield.

TODO say somthing about openness

The study sample is split between studies that kept the same modality as the original (generally meaning that the original study used an online crowd-sourced sample) and those that switched. While TODO cite online studies are respectable, this does decrease the closeness of the replication, and some studies done in person may not have been well adapted (ex. inductions may be weaker or attention checks inadequate to the new sample).

\hypertarget{regression-model}{%
\subsection{Regression model}\label{regression-model}}

We were interested in determining what the strongest predictors were, which ones are most meaningful, so we threw it all into a big ol regularlized regression model. Despite this, wide uncertainty due to parameterization and stuff. The coefficients see Figure 3 \ldots{} TODO

\definecolor{bad}{HTML}{FFCCCB}
        \definecolor{meh}{HTML}{efefef}
            \definecolor{good}{HTML}{abcdff}
    \tikzset{
        mynode/.style={
            draw, rectangle, align=center, text width=4.5cm, scale=1, font=\small, inner sep=.5ex},
        arrow/.style={
         very thick,->,>=stealth}
    }

\begin{figure}[ht]

    \begin{tikzpicture}[
        node distance=.8cm,
        start chain=1 going below,
        every join/.style=arrow,
        ]
        \coordinate[on chain=1] (tc);
        \node[mynode, on chain=1, fill=meh] (n2)
        {\textbf{210} projects from 2011-2022};
        \node[mynode, join, on chain=1, fill=meh] (n3)
        {\textbf{189} original - replication pairs};
        \node[mynode, join, on chain=1, fill=meh] (n4)
        {\textbf{177} experimental pairs};
        \node[mynode, join, on chain=1, fill=good] (n5)
        {\textbf{176} pairs included};
        \node[mynode, join, on chain=1, fill=good] (n6)
        {\textbf{131} pairs with ES};
        \node[mynode, join, on chain=1, fill=good] (n7)
        {\textbf{107} pairs with SMD};

        \begin{scope}[start chain=going right]
            \chainin (n2);
            \node[mynode, join, on chain, fill=bad]
            { \textbf{2} missing projects \\ \textbf{19} reproducibility projects};
            \chainin (n3);
            \node[mynode, join, on chain, fill=bad]
            {\textbf{12} non-experimental pairs};
            \chainin (n4);
            \node[mynode, join, on chain, fill=bad]
            {\textbf{1} pair missing sample size};
        \end{scope}
    \end{tikzpicture}
\caption{Which studies were excluded for what reasons, and how many original-replication pairs are left.}\label{fig:prisma}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=1\linewidth,height=0.25\textheight]{manuscript_files/figure-latex/smd-1} \caption{Relationship between SMD of the original study, SMD of the replication study, and subjective replication success rating, for those studies where SMD was applicable.}\label{fig:smd}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=1\linewidth,height=0.25\textheight]{manuscript_files/figure-latex/mod-results-1} \caption{Coefficient estimates and uncertainty from a model predicting subjective replication scores from the full dataset.}\label{fig:mod-results}
\end{figure}

\begin{table}[!h]

\caption{\label{tab:cor}The correlation of individual predictors with subjective replication outcomes. For subfield, cognitive psychology is treated as the baseline condition.}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{r|c|c}
\hline
Predictors & r & p\\
\hline
Within subjects & 0.333 & 0.000\\
\hline
Log trials & 0.182 & 0.015\\
\hline
Open data & 0.150 & 0.047\\
\hline
Non psych & 0.080 & 0.294\\
\hline
Other psych & 0.075 & 0.322\\
\hline
Publication year & 0.064 & 0.399\\
\hline
Open materials & 0.002 & 0.979\\
\hline
Stanford & -0.027 & 0.725\\
\hline
Log rep/orig sample & -0.047 & 0.536\\
\hline
Log original sample size & -0.108 & 0.155\\
\hline
Switch to online & -0.158 & 0.037\\
\hline
Social & -0.246 & 0.001\\
\hline
Single vignette & -0.267 & 0.000\\
\hline
\end{tabular}
\end{table}

\begin{figure}[ht]
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/predictors-graph-1} \caption{Distribution of subjective replication scores within categories. Bar heights are counts of studies.}\label{fig:predictors-graph}
\end{figure}

\hypertarget{discussion}{%
\section{discussion}\label{discussion}}

{[}who knows where this paragraph should go{]} Replications are one way of approximating whether an effect in the target paper is true, and how likely results are to replicate in some sort of platonic ideal world. There is no one answer here; replication projects measure something else that could be treated as an approximation. However, what a replication is really measuring is how likely it to get that effect given some conditions. Which the right conditions are is a potential point of contention (see discussion around closeness and sample size, power etc). Here, we are explicit in what sample of replicators and replication conditions were are sampling, and thus what we can generalize to. We are estimating how likely replication is when done online by a graduate student, under constraints that are typical for graduate students (limited time, limited budget). As much of scientific process is in fact performed by graduate students, we think this in itself is an interesting question. It contrasts with questions like how likely something is to replicate when performed by an expert with a large budget (perhaps this is the right framing on Camerer) or when performed with extensive feedback from the original authors, etc.

We do not interpret our results as saying that all non-replications were false positives (presumably some are replicable under other circumstances and others are not). Some of the factors we look at are more easily interpreted as being about the original study than others. We do not assign causal explanation to the predictors because there are multiple plausible interpretations: they could be correlates of QRPs in the original, they could be correlates of harder-to-detect or more fragile effects, they could be correlates of less-close replications, they could even be correlates of another stronger predictor.

{[} there is controversy here, but to even discuss it, we need empirics{]} Even those who argue that replication is not so essential still rely on data from replications to make their cases that replication rates are not as low as they seem and that these replication rates are acceptable. Lewandowsky \& Oberauer (\protect\hyperlink{ref-lewandowsky2020}{2020})

\hypertarget{methods}{%
\section{Methods}\label{methods}}

Our pre-registration, code, and coded data are available at TODO OSF REPO.

\hypertarget{dataset}{%
\subsection{Dataset}\label{dataset}}

The dataset of replication projects comes from class projects conducted in PSYCH 251 (earlier called PSYCH 24) a graduate-level experimental methods class taught by MCF from 2011 to 2022. Each student chose a study to replicate, implemented the study, wrote analysis code, pre-registered their replication, ran the study, and turned in a structured final report including methods, analytic plan, changes from the original study, confirmatory and exploratory analyses, and discussion of outcomes. Students were encouraged to do experimental replications, but some students chose to replicate correlational outcomes or do computational reproducibility projects instead. We cannot include the full student reports for confidentiality reasons, but we include an example as well as the template given to students in the repo. TODO example and template

\hypertarget{coding-procedure}{%
\subsection{Coding procedure}\label{coding-procedure}}

We relied primarily on student reports to code the measured variables for the replications. We supplemented this with spreadsheets of information about projects from the time of the class and the original papers.

\hypertarget{measures-of-replication-success}{%
\subsubsection{Measures of replication success}\label{measures-of-replication-success}}

Our primary replication outcome is experimenter and instructor rated replication success (0-1). The subjective replication success was recorded by the teaching staff for the majority of class replications at the time they were conducted. Where the values were missing they were filled in by MCF on the basis of the reports. For all studies, replication success was independently coded by VB on the basis of the reports. Where VB's coding disagreed with the staff/MCF's code, the difference was resolved by discussion between VB and MCF. These were coded on a {[}0, .25, .5, .75, 1{]} scale.

This subjective replication outcome was chosen because it already existed, could be applied to all projects (regardless of type and detail of statistical reporting), and did not rely solely on one statistical measure. As a complement, we also identified a ``key'' statistical test for each paper (see below for details), and if possible, computed p\_original and prediction interval at this statistic, following Errington et al. (\protect\hyperlink{ref-errington2021}{2021}). p\_original was a continuous measure of the p-value on the hypothesis that the original and replication samples come from the same distribution. Prediction interval was a binary measure of whether the replication outcome fell within the prediction interval of the original outcome measure.

\hypertarget{demographic-properties}{%
\subsubsection{Demographic properties}\label{demographic-properties}}

We coded the subfield of the original study as a 4 way factor: cognitive psychology, social psychology, other psychology, and non-psychology. For each paper, we coded its year of publication, whether it had open materials, whether it had open data, and whether it had been conducted using an online, crowd-sourced platform (i.e.~MTurk or Prolific).

\hypertarget{experimental-design-properties}{%
\subsubsection{Experimental design properties}\label{experimental-design-properties}}

We coded experimental design on the basis of student reports, which often quoted from the original methods, and if that did not suffice, the original paper itself. To assess the role of repeated measures, we coded the number of trials seen per participant, including filler trials and trials in all conditions, but excluding training or practice trials.

We coded whether the manipulation in the study was instantiated in a single instance (``single vignette''). Studies with one induction or prime used per condition across participants were coded as having a single vignette. Studies with multiple instances of the manipulation (even if each participant only saw one) were coded as not being single vignette. While most studies with a single vignette only had one trial and vice versa, there were studies with a single induction and multiple test trials, and other studies with multiple scenarios instantiating the manipulation, but only one shown per participant.

We coded the number of subjects, post-exclusions. We coded whether a study had a between-subjects, within-subjects, or mixed design; for analyses mixed studies were counted as within-subjects designs. In the analysis, we used a log-scale for number of subjects and numbers of trials.

\hypertarget{properties-of-replication}{%
\subsubsection{Properties of replication}\label{properties-of-replication}}

We coded whether the replication was conducted on a crowd-sourced platform; this was the norm for the class projects, but a few were done in person. As the predictor variable, we used whether the recruitment platform was changed between original and replication. This groups the few in-person replications in with the studies that were originally online and stayed online in a ``no change'' condition, in contrast with the studies that were originally in-person with online replications.

We coded the replication sample size (after exclusions). This was transformed to the predictor variable log ratio of replication to original sample size.

As a control variable, we included whether the original authors were faculty at Stanford at the time of the replication. This is to account for potential non-independence of the replication (ex. if replicating their advisor's work, students may have access to extra information about methods).

We made note of studies to exclude from some of the sensitivity analyses, due to not quite aligned statistics, extremely small or unbalanced sample sizes, or where the key statistical measure the student chose was not of central importance to the original study.

\hypertarget{determination-and-coding-of-key-statistical-measure}{%
\subsubsection{Determination and coding of key statistical measure}\label{determination-and-coding-of-key-statistical-measure}}

For each study pair, we used one key measure of interest for which we calculated the predictor variables of p-value and effect size and the statistical outcome measures p\_original and prediction interval.
If the student specified a single key measure of interest and this was a measure that was reported in both the original paper and replication, we used that measure. If a student specified multiple, equally important, key measures, we used the first one. When students were not explicit about a key measure, we used other parts of their report (including introduction and power analysis) to determine what effect and therefore what result they considered key. In a few cases, we went back to the original paper to find what effect was considered crucial by the original authors. When the measures reported by the student did not cleanly match their explicit or implicitly stated key measure, we picked the most important (or first) of the measures that were reported in both the original and replication. These decisions could be somewhat subjective but importantly they were made without reference to replication outcomes.

Whenever possible, we used per-condition means and standard deviations, or the test statistic of the key measure and its corresponding degrees of freedom (ex. T test, F test). We took the original statistic from the replication report if it quoted the relevant analysis or from the original paper if not. We took the replication statistics from the replication report.

We then calculated p values, ES, p\_orig, and predInt. We choose to recalculate p values and effect sizes from the means or test statistic rather than use reported measures when possible because we thought this would be more reliable and transparent. The means and test statistics are more likely to have been outputted programmatically and copied directly into the text. In contrast, p-values are often reported as \textless.001 rather than as a point value, and effect size derivations may be error prone. By recording the raw statistics we used and using our available code to calculate other measures, we are transparent, as the test statistics can be searched for in the papers, and all processing is documented in code.

In some cases, p-values and or effect sizes were not calculable either due to insufficient reporting (ex. reporting a p-value but no other statistics from a test) or key measures where p-values and effect sizes did not apply (ex. PCA as measure of interest). Where studies reported beta estimates and standard errors or proportions, SMD isn't an applicable measure, but we were still able to calculate p\_original and prediction interval.

We separately coded whether the original and replication effects were in the same direction, using raw means and graphs. This is more reliable than the statistics because F-tests don't include the direction of effect, and some students may have flipped the direction in coding for betas or t-tests. In the processed data, the direction of the effect of the replication was always coded consistently with the original study's coding, so a positive effect was in the same direction as the original and a negative effect in the opposite direction.

In regressions, we used SMD and log p-value as predictors.

\hypertarget{modelling}{%
\subsection{Modelling}\label{modelling}}

Due to the monotonic missingness of the data, we had more predictor variables and outcome variables for some original-replication pairs than others. To take full advantage of the data, we ran a series of models, with some models having fewer predictors, but more data, and others having more predictors, but more limited data.

We ran a model predicting the subjective replication score on the basis of demographic and experimental predictors on the entire dataset; we ran two models predicting p\_original and prediction interval from demographic and experimental predictors on the subset of data where we had p\_original and prediction intervals. Then, on the smaller subset of the data where we had SMD and p-values, we re-ran these three models with those as additional predictor variables.

The subjective replication scores were coded on {[}0, .25, .5, .75, 1{]}, and we ramapped these to 1-5 to run an ordinal regression predicting replication score. We ran logistic regressions predicting prediction interval and linear regressions predicting p\_original.

All models used a horseshoe prior in brms. All models will include random slopes for predictors nested within years of the class (year) to control for variation between cohorts of students. We did not include any interaction terms in the models. All numeric predictor variables were z-scored after other transforms (e.g., logs) to ensure comparable regularization effects from the horseshoe prior.

As a secondary sensitivity analysis, we examined the subset of the data where the statistical tests had the same specification, the result was of primary importance in the original paper (i.e.~not a manipulation check), and there were no big issues with the replication.

Results of more models in supplement. TODO

\hypertarget{acknowledgements}{%
\section*{Acknowledgements}\label{acknowledgements}}
\addcontentsline{toc}{section}{Acknowledgements}

Acknowledge people here. \texttt{\{-\}} useful to not number this section.

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-camerer2018}{}}%
Camerer CF, Dreber A, Holzmeister F, Ho T-H, Huber J, Johannesson M, Kirchler M, Nave G, Nosek BA, Pfeiffer T, Altmejd A, Buttrick N, Chan T, Chen Y, Forsell E, Gampa A, Heikensten E, Hummer L, Imai T, Isaksson S, Manfredi D, Rose J, Wagenmakers E-J, Wu H (2018) Evaluating the replicability of social science experiments in {Nature} and {Science} between 2010 and 2015. \emph{Nat Hum Behav} \textbf{2}:637--644. doi:\href{https://doi.org/10.1038/s41562-018-0399-z}{10.1038/s41562-018-0399-z}

\leavevmode\vadjust pre{\hypertarget{ref-openscienceconsortium2015}{}}%
Consortium OS (2015) \href{https://www.science.org/doi/full/10.1126/science.aac4716?casa_token=IJ35TwwlcjsAAAAA\%3AqiP68QbVAHleIg9zD3WugKWuV6Oa5rswS0VQnDsCq5I14ME4WIQabNGVD_T6SBSuAt6voVHNnWc0sw}{Estimating the reproducibility of psychological science}. \emph{Science}

\leavevmode\vadjust pre{\hypertarget{ref-ebersole2016}{}}%
Ebersole CR, Atherton OE, Belanger AL, Skulborstad HM, Allen JM, Banks JB, Baranski E, Bernstein MJ, Bonfiglio DBV, Boucher L, Brown ER, Budiman NI, Cairo AH, Capaldi CA, Chartier CR, Chung JM, Cicero DC, Coleman JA, Conway JG, Davis WE, Devos T, Fletcher MM, German K, Grahe JE, Hermann AD, Hicks JA, Honeycutt N, Humphrey B, Janus M, Johnson DJ, Joy-Gaba JA, Juzeler H, Keres A, Kinney D, Kirshenbaum J, Klein RA, Lucas RE, Lustgraaf CJN, Martin D, Menon M, Metzger M, Moloney JM, Morse PJ, Prislin R, Razza T, Re DE, Rule NO, Sacco DF, Sauerberger K, Shrider E, Shultz M, Siemsen C, Sobocko K, Weylin Sternglanz R, Summerville A, Tskhay KO, Allen Z van, Vaughn LA, Walker RJ, Weinberg A, Wilson JP, Wirth JH, Wortman J, Nosek BA (2016) Many {Labs} 3: {Evaluating} participant pool quality across the academic semester via replication. \emph{Journal of Experimental Social Psychology} \textbf{67}:68--82. doi:\href{https://doi.org/10.1016/j.jesp.2015.10.012}{10.1016/j.jesp.2015.10.012}

\leavevmode\vadjust pre{\hypertarget{ref-ebersole2020}{}}%
Ebersole CR, Mathur MB, Baranski E, Bart-Plange D-J, Buttrick NR, Chartier CR, Corker KS, Corley M, Hartshorne JK, IJzerman H, Lazarević LB, Rabagliati H, Ropovik I, Aczel B, Aeschbach LF, Andrighetto L, Arnal JD, Arrow H, Babincak P, Bakos BE, Baník G, Baskin E, Belopavlović R, Bernstein MH, Białek M, Bloxsom NG, Bodroža B, Bonfiglio DBV, Boucher L, Brühlmann F, Brumbaugh CC, Casini E, Chen Y, Chiorri C, Chopik WJ, Christ O, Ciunci AM, Claypool HM, Coary S, Čolić MV, Collins WM, Curran PG, Day CR, Dering B, Dreber A, Edlund JE, Falcão F, Fedor A, Feinberg L, Ferguson IR, Ford M, Frank MC, Fryberger E, Garinther A, Gawryluk K, Ashbaugh K, Giacomantonio M, Giessner SR, Grahe JE, Guadagno RE, Hałasa E, Hancock PJB, Hilliard RA, Hüffmeier J, Hughes S, Idzikowska K, Inzlicht M, Jern A, Jiménez-Leal W, Johannesson M, Joy-Gaba JA, Kauff M, Kellier DJ, Kessinger G, Kidwell MC, Kimbrough AM, King JPJ, Kolb VS, Kołodziej S, Kovacs M, Krasuska K, Kraus S, Krueger LE, Kuchno K, Lage CA, Langford EV, Levitan CA, Lima TJS de, Lin H, Lins S, Loy JE, Manfredi D, Markiewicz Ł, Menon M, Mercier B, Metzger M, Meyet V, Millen AE, Miller JK, Montealegre A, Moore DA, Muda R, Nave G, Nichols AL, Novak SA, Nunnally C, Orlić A, Palinkas A, Panno A, Parks KP, Pedović I, Pękala E, Penner MR, Pessers S, Petrović B, Pfeiffer T, Pieńkosz D, Preti E, Purić D, Ramos T, Ravid J, Razza TS, Rentzsch K, Richetin J, Rife SC, Rosa AD, Rudy KH, Salamon J, Saunders B, Sawicki P, Schmidt K, Schuepfer K, Schultze T, Schulz-Hardt S, Schütz A, Shabazian AN, Shubella RL, Siegel A, Silva R, Sioma B, Skorb L, Souza LEC de, Steegen S, Stein LAR, Sternglanz RW, Stojilović D, Storage D, Sullivan GB, Szaszi B, Szecsi P, Szöke O, Szuts A, Thomae M, Tidwell ND, Tocco C, Torka A-K, Tuerlinckx F, Vanpaemel W, Vaughn LA, Vianello M, Viganola D, Vlachou M, Walker RJ, Weissgerber SC, Wichman AL, Wiggins BJ, Wolf D, Wood MJ, Zealley D, Žeželj I, Zrubka M, Nosek BA (2020) Many {Labs} 5: {Testing Pre-Data-Collection Peer Review} as an {Intervention} to {Increase Replicability}. \emph{Adv Methods Pract Psychol Sci} \textbf{3}:309--331. doi:\href{https://doi.org/10.1177/2515245920958687}{10.1177/2515245920958687}

\leavevmode\vadjust pre{\hypertarget{ref-errington2021}{}}%
Errington TM, Mathur M, Soderberg CK, Denis A, Perfito N, Iorns E, Nosek BA (2021) Investigating the replicability of preclinical cancer biology (R Pasqualini and E Franco, Eds.). \emph{eLife} \textbf{10}:e71601. doi:\href{https://doi.org/10.7554/eLife.71601}{10.7554/eLife.71601}

\leavevmode\vadjust pre{\hypertarget{ref-frank2012}{}}%
Frank MC, Saxe R (2012) Teaching {Replication}: \emph{Perspect Psychol Sci}. doi:\href{https://doi.org/10.1177/1745691612460686}{10.1177/1745691612460686}

\leavevmode\vadjust pre{\hypertarget{ref-hawkins}{}}%
Hawkins RXD, Smith EN, Au C, Arias JM, Hermann E, Keil M, Lampinen A, Raposo S, Salehi S, Salloum J, Tan J, Frank MC Improving the {Replicability} of {Psychological Science Through Pedagogy}. :41

\leavevmode\vadjust pre{\hypertarget{ref-hoogeveen2019}{}}%
Hoogeveen S, Sarafoglou A, Wagenmakers E-J (2019) Laypeople {Can Predict Which Social Science Studies Replicate}. preprint. {PsyArXiv}. Available from: \url{https://osf.io/egw9d} {[}Last accessed 30 September 2019{]}. doi:\href{https://doi.org/10.31234/osf.io/egw9d}{10.31234/osf.io/egw9d}

\leavevmode\vadjust pre{\hypertarget{ref-klein2014}{}}%
Klein RA, Ratliff KA, Vianello M, Adams RB, Bahník Š, Bernstein MJ, Bocian K, Brandt MJ, Brooks B, Brumbaugh CC, Cemalcilar Z, Chandler J, Cheong W, Davis WE, Devos T, Eisner M, Frankowska N, Furrow D, Galliani EM, Hasselman F, Hicks JA, Hovermale JF, Hunt SJ, Huntsinger JR, IJzerman H, John M-S, Joy-Gaba JA, Barry Kappes H, Krueger LE, Kurtz J, Levitan CA, Mallett RK, Morris WL, Nelson AJ, Nier JA, Packard G, Pilati R, Rutchick AM, Schmidt K, Skorinko JL, Smith R, Steiner TG, Storbeck J, Van Swol LM, Thompson D, Veer AE van `t, Ann Vaughn L, Vranka M, Wichman AL, Woodzicka JA, Nosek BA (2014) Investigating {Variation} in {Replicability}: {A} {``{Many Labs}''} {Replication Project}. \emph{Social Psychology} \textbf{45}:142--152. doi:\href{https://doi.org/10.1027/1864-9335/a000178}{10.1027/1864-9335/a000178}

\leavevmode\vadjust pre{\hypertarget{ref-klein2018}{}}%
Klein RA, Vianello M, Hasselman F, Adams BG, Adams RB, Alper S, Aveyard M, Axt JR, Babalola MT, Bahník Š, Batra R, Berkics M, Bernstein MJ, Berry DR, Bialobrzeska O, Binan ED, Bocian K, Brandt MJ, Busching R, Rédei AC, Cai H, Cambier F, Cantarero K, Carmichael CL, Ceric F, Chandler J, Chang J-H, Chatard A, Chen EE, Cheong W, Cicero DC, Coen S, Coleman JA, Collisson B, Conway MA, Corker KS, Curran PG, Cushman F, Dagona ZK, Dalgar I, Dalla Rosa A, Davis WE, Bruijn M de, De Schutter L, Devos T, Vries M de, Doğulu C, Dozo N, Dukes KN, Dunham Y, Durrheim K, Ebersole CR, Edlund JE, Eller A, English AS, Finck C, Frankowska N, Freyre M-Á, Friedman M, Galliani EM, Gandi JC, Ghoshal T, Giessner SR, Gill T, Gnambs T, Gómez Á, González R, Graham J, Grahe JE, Grahek I, Green EGT, Hai K, Haigh M, Haines EL, Hall MP, Heffernan ME, Hicks JA, Houdek P, Huntsinger JR, Huynh HP, IJzerman H, Inbar Y, Innes-Ker ÅH, Jiménez-Leal W, John M-S, Joy-Gaba JA, Kamiloğlu RG, Kappes HB, Karabati S, Karick H, Keller VN, Kende A, Kervyn N, Knežević G, Kovacs C, Krueger LE, Kurapov G, Kurtz J, Lakens D, Lazarević LB, Levitan CA, Lewis NA, Lins S, Lipsey NP, Losee JE, Maassen E, Maitner AT, Malingumu W, Mallett RK, Marotta SA, Međedović J, Mena-Pacheco F, Milfont TL, Morris WL, Murphy SC, Myachykov A, Neave N, Neijenhuijs K, Nelson AJ, Neto F, Lee Nichols A, Ocampo A, O'Donnell SL, Oikawa H, Oikawa M, Ong E, Orosz G, Osowiecka M, Packard G, Pérez-Sánchez R, Petrović B, Pilati R, Pinter B, Podesta L, Pogge G, Pollmann MMH, Rutchick AM, Saavedra P, Saeri AK, Salomon E, Schmidt K, Schönbrodt FD, Sekerdej MB, Sirlopú D, Skorinko JLM, Smith MA, Smith-Castro V, Smolders KCHJ, Sobkow A, Sowden W, Spachtholz P, Srivastava M, Steiner TG, Stouten J, Street CNH, Sundfelt OK, Szeto S, Szumowska E, Tang ACW, Tanzer N, Tear MJ, Theriault J, Thomae M, Torres D, Traczyk J, Tybur JM, Ujhelyi A, Aert RCM van, Assen MALM van, Hulst M van der, Lange PAM van, Veer AE van 't, Vásquez- Echeverría A, Ann Vaughn L, Vázquez A, Vega LD, Verniers C, Verschoor M, Voermans IPJ, Vranka MA, Welch C, Wichman AL, Williams LA, Wood M, Woodzicka JA, Wronska MK, Young L, Zelenski JM, Zhijia Z, Nosek BA (2018) Many {Labs} 2: {Investigating Variation} in {Replicability Across Samples} and {Settings}. \emph{Adv Methods Pract Psychol Sci} \textbf{1}:443--490. doi:\href{https://doi.org/10.1177/2515245918810225}{10.1177/2515245918810225}

\leavevmode\vadjust pre{\hypertarget{ref-lewandowsky2020}{}}%
Lewandowsky S, Oberauer K (2020) Low replicability can support robust and efficient science. \emph{Nat Commun} \textbf{11}:1--12. doi:\href{https://doi.org/10.1038/s41467-019-14203-0}{10.1038/s41467-019-14203-0}

\end{CSLReferences}

\hypertarget{appendix-appendices}{%
\appendix}

\hypertarget{appendix-a}{%
\section*{Appendix A}\label{appendix-a}}
\addcontentsline{toc}{section}{Appendix A}

Some appendix text.

\hypertarget{appendix-b}{%
\section*{Appendix B}\label{appendix-b}}
\addcontentsline{toc}{section}{Appendix B}

More appendix text.

\end{document}

### 2023-03-17 code/helper/parse_stats.R
look at cochrane for checking stats

@@ -1,4 +1,5 @@
 # considered using the effectsize package but afaik we don't care about estimating CI's here and there were optim problems with that
+# https://training.cochrane.org/handbook/current/chapter-06 may be relevant
 
 parse_t <- function(tval, within_between) {
   df=str_extract(tval, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()

### 2023-03-17 paper/manuscript.Rmd
looking for cites and reading

@@
 
+# Citation slush pile
+
+predict w/ ML @altmejd2019
+prediction with humans @dreber2015; @forsell2019
+
+econ also has replications and issues @camerer2016
+
+RPP has been reanalysed and complained about a lot @etz2016;@gilbert2016;@patil2016
+
+moving goal posts around replication / interpreting results @nosek2020 (also this is worth reading!)
+
+some sort of modeling of replications @pawel2020 (worth reading!)
+
+note to self: got to S in going through the cites of the review paper
 # introduction

### 2023-03-17 paper/manuscript.Rmd
stuff

--- 2023-03-17 paper/manuscript.Rmd
@@
 
-d <- read_csv(here("data", "processed_data.csv"))
+d <- read_csv(here("data", "processed_data.csv")) |> filter(status!="unusable")
 ```
@@
 - ** verify code for ES ** with someone
+- note that 4ish of these papers were previously reported in RP:P
+
+# Citation slush pile
+
+predict w/ ML @altmejd2019
+prediction with humans @dreber2015; @forsell2019
+
+econ also has replications and issues @camerer2016
+
+moving goal posts around replication / interpreting results @nosek2020
+
+some sort of modeling of replications @pawel2020
 
@@
 
-[replication: it's a hot issue and concerns around replication have done a lot, see crisis/revolution] Replication is a hot topic.
+[replication: it's a hot issue and concerns around replication have done a lot, see crisis/revolution] Concerns around the practices of science.
+Replication is a hot topic.
 Some argue that it is a cornerstone of a cumulative science, and findings of low replication rates are a problem.
-Concerns about replication rates have become a large point of discussion in psychology and other fields.
+Concerns about replication rates have become a large point of discussion in psychology and other fields, with large scale replications spurring these discussions and providing the empirical data analyzed by all sides.
 
@@
 They found an overall replication rate around 40%, which provided evidence to support growing concerns about the non-reliability of the literature.
-[idk, maybe worth framing that this was a big deal study when it came out].
+The RP:P dataset was itself much discussed and reanalyzed [@etz2016;@gilbert2016;@patil2016] [idk, maybe worth framing that this was a big deal study when it came out].
 TODO some discussion of how many papers have reanalysed this cutting the data different ways.
@@
 Blah blah stakeholders and resources.
-There's some signal here, as people are able to predict replication success at above chance CITATIONS @hoogeveen2019.
-RP:P looked at how replication rates varied across subsamples of their studies.
+There's some signal here, as people are able to predict replication success at above chance CITATIONS [@hoogeveen2019;@dreber2015; @forsell2019;@camerer2018]
+
+RP:P looked at how replication rates varied across subsamples of their studies [@openscienceconsortium2015].
 They found that cognitive psychology studies replicated at higher, but still low rates (50% v 25%) compared to social psychology.
@@
 TODO do we talk about any other correlates.
+
 There are reasons to believe that experimental factors such as number of items or between and within subject designs may also be predictive (cite our old paper), and could pontentially be some of the reason for subfield differences.
+TODO maybe foreshadow that there are reasons to believe there are correlations!
 
-[could possibly frame with a bit of some=MCF have advocated teaching replication cite whatever, describe class, then thing? @frank2012; @hawkins]
-Here we introduce a new dataset of replications in the behavioral sciences, primarily psychology.
-Over the years 2011-2022, students in a graduate-level experimental methods class have conducted online replications as individual course projects.
-From this, we have 176 experimental replications that were codeable.
+While many replications of individual studies are conducted, these may have been selected for non-representative reasons, such as a high prior on replicating (e.g.
+as a demonstration), or a low or uncertain prior (e.g.
+for a high-value study).
+When sampling is likely related to replicability, the studies are less good for estimating base rates and predictors of replicability in the literature as a whole.
+
+Prior literature, such as @frank2012 and @hawkins have advocated using research methods classes to conduct replications, both for the education and scientific value.
+
+Here we introduce a new dataset of 176 replications of experimental studies from the social sciences, primarily psychology.
+These replications were conducted by students in graduate-level experimental methods class between 2011 and 2022 as individual course projects.
 This approximately doubles the set of experiments in the large-scale replication literature.
 We investigate predictors of replicability in this new dataset.
-
-## quick methods
-[some of this should actually just go in methods methods] Class, taught by last author, is an experimental methods class aimed at first-year graduate students, but taken by ...
-Since around 2015, it has been required for incoming PhD students in the Psychology Department.
-Over the course of a quarter long class, students work through their individual replication projects, from choosing a study, to reimplementing it, to creating analysis code, piloting the study, pre-registering it, and finally running a full data collection and writing up their results.
-Students are free to choose studies related to their interests, although recent articles from Psychological Science are the recommended path under uncertainty (leading to a high proportion of Psych science articles in this replication sample).
-While the sampling procedure is non-random, it is generally representative of studies that are of interest to and doable by first year grad students.
-
-Studies vary along a number of dimensions, including statistical properties, subfield, and experimental properties.
-We leverage this naturally occurring variation to see if these properties predict replication success.
-
-# Results
-
-[again unclear the intro/ methods/results split]
-Over the years, there have been a number of student projects, of these we are able to include 176 (see Figure \ref{fig:prisma} for exclusions).
-Because of variance in the experimental designs and reporting practices, we have variable statistical information.
-To address this, we conducted a series of models, balancing between including as many data points as possible, and including potentially relevant outcome and predictor variables.
-Here we focus on one set of models, the prediction of subjective replication outcome on the basis of the whole dataset without the statistical predictors.
-Other model results, including those from a sensitivity analysis, are available in the supplement.
-
-As our primary outcome measure, we use a subjective measure of replication success.
-At the end of the class, the instruction team coded each project on a 0-1 scale indicating whether or not it replicated.
-This allows for nuance around marginal effects, covers studies with a broad range of statistical outcomes (including those that do not lend themselves to NHST), and includes studies with multiple important outcome measures.
-For robustness, first author independently coded all projects on the same scale off of the final write-ups.
-Disagreements (which occured foobar % of the time) were resolved by discussion between first and third authors.
-
-As secondary outcomes, we also calculated prediction intervals following @errington2021 on the key measure of interest from each study.
-Because of variable statistics and reporting, this was calculable on FOOBAR studies.
-
-## Overall replication rate
-
-Across the 176 studies, the overall replication rate was 49% TODO derive in code.
-FOOBAR % of the studies had replication outcomes within the prediction interval of the original outcome.
-The average p_original value (median?) was TODO.
-
-For the FOOBAR studies with SMD, we see cite FIGURE.
-
-## Single predictors
-We drew a set of predictor variables from the correlational results of RP:P and our own intuitions about experimental factors that might impact replication success as well as some co-variates related to how close the replication would be.
-Many of these predictors individually correlate with subjective replication success (Figure \ref{tab:cor}.
-In particular, within-subjects designs, higher numbers of trials, and open data were predictive of replication.
-Single vignetted studies, social psychology studies, and original-replication pairs where the replication switched to online were less likely to replicate.
-Distributions of study outcomes across some of these properties are shown in Figure TODO.
-
-Both social and cognitive psychology studies were well represented, and the cognitive psychology studies replicated at a FOOBAR higher rate.
-Within and between subjects designs were both common, and within replicated at YY more.
-Similarly, studies with multiple vignettes replicated FOOBAR more.
-However, there are strong correlations between these experimental features and between experimental features and subfield.
-
-TODO say somthing about openness
-
-The study sample is split between studies that kept the same modality as the original (generally meaning that the original study used an online crowd-sourced sample) and those that switched.
-While TODO cite online studies are respectable, this does decrease the closeness of the replication, and some studies done in person may not have been well adapted (ex.
-inductions may be weaker or attention checks inadequate to the new sample).
-
-## Regression model
-We were interested in determining what the strongest predictors were, which ones are most meaningful, so we threw it all into a big ol regularlized regression model.
-Despite this, wide uncertainty due to parameterization and stuff.
-The coefficients see Figure 3 ...
-TODO
 
@@
 
+# Results
+
+PSYCH 251 is Stanford Psychology's graduate-level experimental methods class taught by MCF.
+Over the course of 10 weeks, students choose a published finding to replicate, re-implement the study, write analysis code, pre-register their study, collect data using an online platform, and write up a structured replication report.
+Students are free to choose studies related to their research interests, with the default recommendation being an article from a recent year of Psychological Science.
+While this choice results in a non-random sampling of studies, the sample is representative of studies that are of interest to and doable by first year graduate students.
+
+The sample of replicated studies reflects the variability of the literature, including studies from different subfields, using different experimental methods and statistical outcomes.
+We leverage the naturally occuraing variability in this sample of replications to examine how different demographic, experimental design, and statistical properties predict replication success.
+
+We used a subjective rating of replication success as our primary outcome measure.
+The instruction team had coded a holistic measure of replication success for each project when they were turned in at the end of the course.
+For reliability, we had a separate rater (VB) independently code the replication success from the replication reports; discrepancies were resolved by discussion between MCF and VB.
+We focussed on this measure because it was applicable across the range of statistical measures and reporting practices and accommodated studies where there were multiple important outcome measures.
+
+As a complement, we also used two statistical measure of replication on the subset of the data where they were computable (NUMBER, see Figure \ref{fig:prisma}).
+We measured p-original, the p-value on the null hypothesis that the original and replication statistics are from the same distribution, as a continuous variable, and we also determined whether the replication statistic fell within the prediction interval of the original statistic [@errington2021].
+
 ```{r smd, out.height="25%", fig.width=6, fig.height=3, fig.pos="ht", fig.cap="Relationship between SMD of the original study, SMD of the replication study, and subjective replication success rating, for those studies where SMD was applicable."}
@@
 
-```{r mod-results, out.height="25%", fig.width=8, fig.height=3, fig.pos="ht", fig.cap="Coefficient estimates and uncertainty from a model predicting subjective replication scores from the full dataset."}
-tier1_subjective <- read_rds(here(model_location, "tier1_subjective.rds"))
-tier1_subjective |> 
-gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |> mutate(Term=factor(Term, levels=c("subfieldsocial", "subfieldother_psych", "subfieldnon_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "z_pub_year", "z_log_trials", "z_log_sample", "z_log_ratio_ss"), labels=c("Social", "Other psych", "Non psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rep/orig sample"))) |>
-  ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
-  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI predicting subjective replication score")+theme(axis.text=element_text(size=11))
+## Overall replication rate
 
+```{r}
+sub_rep_rate <- d |> summarize(m=mean(sub_rep)*100)
+
+pred_int_rate <- d |> filter(!is.na(predInt)) |> summarize(m=mean(as.numeric(predInt))*100)
+porig_rate <- d |> filter(!is.na(p_orig)) |> summarize(m=median(p_orig)*100)
 ```
+Across the 176 studies, the overall subjective replication rate was `r round(pluck(sub_rep_rate,1))`%.
+`r round(pluck(pred_int_rate,1))`% of the studies had replication outcomes within the prediction interval of the original outcome.
+The median p_original value was `r round(pluck(porig_rate, 1))`%.
+Figure \ref{fig:smd} shows the relationship between original SMD, replication SMD, and subjective replication score.
+Roughly speaking, there's a cluster of studies that replicate with similar effect sizes to the original and another cluster that fail to replicate with replication effect sizes near zero.
+On average, there is a diminution of effect sizes from original to replication.
 
@@
 ```
+
+## Single predictors
+Properties of both the original study and the replication can influence whether or not the replication is a success.
+We chose a set of predictor variables from the correlational results of RP:P and our own intuitions about experimental factors that might impact replication success as well as some covariates related to how close the replication would be.
+A full description of these features is given in methods.
+
+Many of these predictors individually correlate with subjective replication success (Table \ref{tab:cor}).
+Predictors of higher replicability included within-subjects designs, higher numbers of trials, and open data.
+Predictors of lower replicability included Single vignetted studies, social psychology studies, and original-replication pairs where the replication switched to online.
+
+Distributions of study outcomes across some of these properties are shown in Figure \ref{fig:predictors-graph}.
+Both social and cognitive psychology studies were well represented, and the cognitive psychology studies replicated at twice the rate of social psychology studies.
+Within and between subjects designs were both common, and within replicated four times as much.
+Similarly, studies with multiple vignettes replicated 1.5 times more than single vignetted studies.
+However, there were strong correlations among these experimental features and between these experimental features and subfield.
+
+Studies with open data, which almost always also had open materials, tended to replicate more than studies without open data, although this may be linked to temporal trends.
+
+Nearly all replications studies were conducted online, but original studies were split between using in-person and online recruitment.
+Replications that switched to online were less likely to replicate than those that had the same modality as the original (generally both online, in a few cases both in-person).
+While online studies in general show comparable results to studies conducted in person TODO CITATIONS, switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well adapted (ex.
+inductions may be weaker or attention checks inadequate to the new sample).
 
@@
 
+## Regression model
+While a number of the predictors show individual correlations with the subjective replication score, many of the predictors are also correlated with one another.
+In order to determine which predictors were the strongest, we ran a pre-registered regularized regression model (see Methods for details).
+The coefficient estimates are shown in Figure \ref{fig:mod-results}.
+Due to a large number of predictors coupled with a small and noisy dataset, even with strong regularization, there is much uncertainty around the coefficients.
+The general directions of coefficients are consistent with the effects of the predictors in isolation.
+Within-subjects designs seem an especially strong indicator of replicability TODO include estimate and range in text!
+
+```{r mod-results, out.height="25%", fig.width=8, fig.height=3, fig.pos="ht", fig.cap="Coefficient estimates and uncertainty from a model predicting subjective replication scores from the full dataset."}
+tier1_subjective <- read_rds(here(model_location, "tier1_subjective.rds"))
+tier1_subjective |> 
+gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |> mutate(Term=factor(Term, levels=c("subfieldsocial", "subfieldother_psych", "subfieldnon_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "z_pub_year", "z_log_trials", "z_log_sample", "z_log_ratio_ss"), labels=c("Social", "Other psych", "Non psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rep/orig sample"))) |>
+  ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
+  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI predicting subjective replication score")+theme(axis.text=element_text(size=11))
+
+```
+
+Results from other models can be found in the supplement. TODO make this a true statement
+
 # discussion
+
+blah blah we did a thing and it generally aligns with prior results.
+Overall replication rate is consistent with prior work, and we find cog greater than soc.
+However, by looking at a greater range of pr
 
@@
 
+circle back to the idea that student replications (either as class or before extension into their own work) would be valuable
+
 # Methods
@@
 TODO example and template
+
+[some of this should actually just go in methods methods] Class, taught by last author, is an experimental methods class aimed at first-year graduate students, but taken by ...
+Since around 2015, it has been required for incoming PhD students in the Psychology Department.Students are free to choose studies related to their interests, although recent articles from Psychological Science are the recommended path under uncertainty (leading to a high proportion of Psych science articles in this replication sample).
+While the sampling procedure is non-random, it is generally representative of studies that are of interest to and doable by first year grad students.
 
@@
 These were coded on a [0, .25, .5, .75, 1] scale.
+TODO rate of coding discrepancy
 

### 2023-03-17 paper/manuscript.tex
stuff

@@
   ** verify code for ES ** with someone
+\item
+  note that 4ish of these papers were previously reported in RP:P
 \end{itemize}
+
+\hypertarget{citation-slush-pile}{%
+\section{Citation slush pile}\label{citation-slush-pile}}
+
+predict w/ ML Altmejd et al. (\protect\hyperlink{ref-altmejd2019}{2019})
+prediction with humans Dreber et al. (\protect\hyperlink{ref-dreber2015}{2015}); Forsell et al. (\protect\hyperlink{ref-forsell2019}{2019})
+
+econ also has replications and issues Camerer et al. (\protect\hyperlink{ref-camerer2016}{2016})
+
+moving goal posts around replication / interpreting results Nosek \& Errington (\protect\hyperlink{ref-nosek2020}{2020})
+
+some sort of modeling of replications Pawel \& Held (\protect\hyperlink{ref-pawel2020}{2020})
 
@@
 
-{[}replication: it's a hot issue and concerns around replication have done a lot, see crisis/revolution{]} Replication is a hot topic.
+{[}replication: it's a hot issue and concerns around replication have done a lot, see crisis/revolution{]} Concerns around the practices of science.
+Replication is a hot topic.
 Some argue that it is a cornerstone of a cumulative science, and findings of low replication rates are a problem.
-Concerns about replication rates have become a large point of discussion in psychology and other fields.
+Concerns about replication rates have become a large point of discussion in psychology and other fields, with large scale replications spurring these discussions and providing the empirical data analyzed by all sides.
 
@@
 They found an overall replication rate around 40\%, which provided evidence to support growing concerns about the non-reliability of the literature.
-{[}idk, maybe worth framing that this was a big deal study when it came out{]}.
+The RP:P dataset was itself much discussed and reanalyzed (\protect\hyperlink{ref-etz2016}{Etz \& Vandekerckhove 2016}, \protect\hyperlink{ref-gilbert2016}{Gilbert et al.
+2016}, \protect\hyperlink{ref-patil2016}{Patil et al.
+2016}) {[}idk, maybe worth framing that this was a big deal study when it came out{]}.
 TODO some discussion of how many papers have reanalysed this cutting the data different ways.
@@
 Blah blah stakeholders and resources.
-There's some signal here, as people are able to predict replication success at above chance CITATIONS Hoogeveen et al.
-(\protect\hyperlink{ref-hoogeveen2019}{2019}).
-RP:P looked at how replication rates varied across subsamples of their studies.
+There's some signal here, as people are able to predict replication success at above chance CITATIONS (\protect\hyperlink{ref-dreber2015}{Dreber et al.
+2015}, \protect\hyperlink{ref-camerer2018}{Camerer et al.
+2018}, \protect\hyperlink{ref-forsell2019}{Forsell et al.
+2019}, \protect\hyperlink{ref-hoogeveen2019}{Hoogeveen et al.
+2019})
+
+RP:P looked at how replication rates varied across subsamples of their studies (\protect\hyperlink{ref-openscienceconsortium2015}{Consortium 2015}).
 They found that cognitive psychology studies replicated at higher, but still low rates (50\% v 25\%) compared to social psychology.
@@
 TODO do we talk about any other correlates.
+
 There are reasons to believe that experimental factors such as number of items or between and within subject designs may also be predictive (cite our old paper), and could pontentially be some of the reason for subfield differences.
+TODO maybe foreshadow that there are reasons to believe there are correlations!
 
-(could possibly frame with a bit of some=MCF have advocated teaching replication cite whatever, describe class, then thing?
-\protect\hyperlink{ref-frank2012}{Frank \& Saxe 2012}, \protect\hyperlink{ref-hawkins}{Hawkins et al.
-n.d.})
-Here we introduce a new dataset of replications in the behavioral sciences, primarily psychology.
-Over the years 2011-2022, students in a graduate-level experimental methods class have conducted online replications as individual course projects.
-From this, we have 176 experimental replications that were codeable.
+While many replications of individual studies are conducted, these may have been selected for non-representative reasons, such as a high prior on replicating (e.g.~as a demonstration), or a low or uncertain prior (e.g.~for a high-value study).
+When sampling is likely related to replicability, the studies are less good for estimating base rates and predictors of replicability in the literature as a whole.
+
+Prior literature, such as Frank \& Saxe (\protect\hyperlink{ref-frank2012}{2012}) and Hawkins et al.
+(\protect\hyperlink{ref-hawkins}{n.d.}) have advocated using research methods classes to conduct replications, both for the education and scientific value.
+
+Here we introduce a new dataset of 176 replications of experimental studies from the social sciences, primarily psychology.
+These replications were conducted by students in graduate-level experimental methods class between 2011 and 2022 as individual course projects.
 This approximately doubles the set of experiments in the large-scale replication literature.
 We investigate predictors of replicability in this new dataset.
-
-\hypertarget{quick-methods}{%
-\subsection{quick methods}\label{quick-methods}}
-
-{[}some of this should actually just go in methods methods{]} Class, taught by last author, is an experimental methods class aimed at first-year graduate students, but taken by \ldots{} Since around 2015, it has been required for incoming PhD students in the Psychology Department.
-Over the course of a quarter long class, students work through their individual replication projects, from choosing a study, to reimplementing it, to creating analysis code, piloting the study, pre-registering it, and finally running a full data collection and writing up their results.
-Students are free to choose studies related to their interests, although recent articles from Psychological Science are the recommended path under uncertainty (leading to a high proportion of Psych science articles in this replication sample).
-While the sampling procedure is non-random, it is generally representative of studies that are of interest to and doable by first year grad students.
-
-Studies vary along a number of dimensions, including statistical properties, subfield, and experimental properties.
-We leverage this naturally occurring variation to see if these properties predict replication success.
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-{[}again unclear the intro/ methods/results split{]}
-Over the years, there have been a number of student projects, of these we are able to include 176 (see Figure \ref{fig:prisma} for exclusions).
-Because of variance in the experimental designs and reporting practices, we have variable statistical information.
-To address this, we conducted a series of models, balancing between including as many data points as possible, and including potentially relevant outcome and predictor variables.
-Here we focus on one set of models, the prediction of subjective replication outcome on the basis of the whole dataset without the statistical predictors.
-Other model results, including those from a sensitivity analysis, are available in the supplement.
-
-As our primary outcome measure, we use a subjective measure of replication success.
-At the end of the class, the instruction team coded each project on a 0-1 scale indicating whether or not it replicated.
-This allows for nuance around marginal effects, covers studies with a broad range of statistical outcomes (including those that do not lend themselves to NHST), and includes studies with multiple important outcome measures.
-For robustness, first author independently coded all projects on the same scale off of the final write-ups.
-Disagreements (which occured foobar \% of the time) were resolved by discussion between first and third authors.
-
-As secondary outcomes, we also calculated prediction intervals following Errington et al.
-(\protect\hyperlink{ref-errington2021}{2021}) on the key measure of interest from each study.
-Because of variable statistics and reporting, this was calculable on FOOBAR studies.
-
-\hypertarget{overall-replication-rate}{%
-\subsection{Overall replication rate}\label{overall-replication-rate}}
-
-Across the 176 studies, the overall replication rate was 49\% TODO derive in code.
-FOOBAR \% of the studies had replication outcomes within the prediction interval of the original outcome.
-The average p\_original value (median?) was TODO.
-
-For the FOOBAR studies with SMD, we see cite FIGURE.
-
-\hypertarget{single-predictors}{%
-\subsection{Single predictors}\label{single-predictors}}
-
-We drew a set of predictor variables from the correlational results of RP:P and our own intuitions about experimental factors that might impact replication success as well as some co-variates related to how close the replication would be.
-Many of these predictors individually correlate with subjective replication success (Figure \ref{tab:cor}.
-In particular, within-subjects designs, higher numbers of trials, and open data were predictive of replication.
-Single vignetted studies, social psychology studies, and original-replication pairs where the replication switched to online were less likely to replicate.
-Distributions of study outcomes across some of these properties are shown in Figure TODO.
-
-Both social and cognitive psychology studies were well represented, and the cognitive psychology studies replicated at a FOOBAR higher rate.
-Within and between subjects designs were both common, and within replicated at YY more.
-Similarly, studies with multiple vignettes replicated FOOBAR more.
-However, there are strong correlations between these experimental features and between experimental features and subfield.
-
-TODO say somthing about openness
-
-The study sample is split between studies that kept the same modality as the original (generally meaning that the original study used an online crowd-sourced sample) and those that switched.
-While TODO cite online studies are respectable, this does decrease the closeness of the replication, and some studies done in person may not have been well adapted (ex.
-inductions may be weaker or attention checks inadequate to the new sample).
-
-\hypertarget{regression-model}{%
-\subsection{Regression model}\label{regression-model}}
-
-We were interested in determining what the strongest predictors were, which ones are most meaningful, so we threw it all into a big ol regularlized regression model.
-Despite this, wide uncertainty due to parameterization and stuff.
-The coefficients see Figure 3 \ldots{} TODO
 
@@
 
+\hypertarget{results}{%
+\section{Results}\label{results}}
+
+PSYCH 251 is Stanford Psychology's graduate-level experimental methods class taught by MCF.
+Over the course of 10 weeks, students choose a published finding to replicate, re-implement the study, write analysis code, pre-register their study, collect data using an online platform, and write up a structured replication report.
+Students are free to choose studies related to their research interests, with the default recommendation being an article from a recent year of Psychological Science.
+While this choice results in a non-random sampling of studies, the sample is representative of studies that are of interest to and doable by first year graduate students.
+
+The sample of replicated studies reflects the variability of the literature, including studies from different subfields, using different experimental methods and statistical outcomes.
+We leverage the naturally occuraing variability in this sample of replications to examine how different demographic, experimental design, and statistical properties predict replication success.
+
+We used a subjective rating of replication success as our primary outcome measure.
+The instruction team had coded a holistic measure of replication success for each project when they were turned in at the end of the course.
+For reliability, we had a separate rater (VB) independently code the replication success from the replication reports; discrepancies were resolved by discussion between MCF and VB.
+We focussed on this measure because it was applicable across the range of statistical measures and reporting practices and accommodated studies where there were multiple important outcome measures.
+
+As a complement, we also used two statistical measure of replication on the subset of the data where they were computable (NUMBER, see Figure \ref{fig:prisma}).
+We measured p-original, the p-value on the null hypothesis that the original and replication statistics are from the same distribution, as a continuous variable, and we also determined whether the replication statistic fell within the prediction interval of the original statistic (\protect\hyperlink{ref-errington2021}{Errington et al.
+2021}).
+
 \begin{figure}[ht]
@@
 
-\begin{figure}[ht]
-\includegraphics[width=1\linewidth,height=0.25\textheight]{manuscript_files/figure-latex/mod-results-1} \caption{Coefficient estimates and uncertainty from a model predicting subjective replication scores from the full dataset.}\label{fig:mod-results}
-\end{figure}
+\hypertarget{overall-replication-rate}{%
+\subsection{Overall replication rate}\label{overall-replication-rate}}
+
+Across the 176 studies, the overall subjective replication rate was 49\%.
+46\% of the studies had replication outcomes within the prediction interval of the original outcome.
+The median p\_original value was 3\%.
+Figure \ref{fig:smd} shows the relationship between original SMD, replication SMD, and subjective replication score.
+Roughly speaking, there's a cluster of studies that replicate with similar effect sizes to the original and another cluster that fail to replicate with replication effect sizes near zero.
+On average, there is a diminution of effect sizes from original to replication.
 
@@
 
+\hypertarget{single-predictors}{%
+\subsection{Single predictors}\label{single-predictors}}
+
+Properties of both the original study and the replication can influence whether or not the replication is a success.
+We chose a set of predictor variables from the correlational results of RP:P and our own intuitions about experimental factors that might impact replication success as well as some covariates related to how close the replication would be.
+A full description of these features is given in methods.
+
+Many of these predictors individually correlate with subjective replication success (Table \ref{tab:cor}).
+Predictors of higher replicability included within-subjects designs, higher numbers of trials, and open data.
+Predictors of lower replicability included Single vignetted studies, social psychology studies, and original-replication pairs where the replication switched to online.
+
+Distributions of study outcomes across some of these properties are shown in Figure \ref{fig:predictors-graph}.
+Both social and cognitive psychology studies were well represented, and the cognitive psychology studies replicated at twice the rate of social psychology studies.
+Within and between subjects designs were both common, and within replicated four times as much.
+Similarly, studies with multiple vignettes replicated 1.5 times more than single vignetted studies.
+However, there were strong correlations among these experimental features and between these experimental features and subfield.
+
+Studies with open data, which almost always also had open materials, tended to replicate more than studies without open data, although this may be linked to temporal trends.
+
+Nearly all replications studies were conducted online, but original studies were split between using in-person and online recruitment.
+Replications that switched to online were less likely to replicate than those that had the same modality as the original (generally both online, in a few cases both in-person).
+While online studies in general show comparable results to studies conducted in person TODO CITATIONS, switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well adapted (ex.
+inductions may be weaker or attention checks inadequate to the new sample).
+
 \begin{figure}[ht]
@@
 
+\hypertarget{regression-model}{%
+\subsection{Regression model}\label{regression-model}}
+
+While a number of the predictors show individual correlations with the subjective replication score, many of the predictors are also correlated with one another.
+In order to determine which predictors were the strongest, we ran a pre-registered regularized regression model (see Methods for details).
+The coefficient estimates are shown in Figure \ref{fig:mod-results}.
+Due to a large number of predictors coupled with a small and noisy dataset, even with strong regularization, there is much uncertainty around the coefficients.
+The general directions of coefficients are consistent with the effects of the predictors in isolation.
+Within-subjects designs seem an especially strong indicator of replicability TODO include estimate and range in text!
+
+\begin{figure}[ht]
+\includegraphics[width=1\linewidth,height=0.25\textheight]{manuscript_files/figure-latex/mod-results-1} \caption{Coefficient estimates and uncertainty from a model predicting subjective replication scores from the full dataset.}\label{fig:mod-results}
+\end{figure}
+
+Results from other models can be found in the supplement. TODO make this a true statement
+
 \hypertarget{discussion}{%
 \section{discussion}\label{discussion}}
+
+blah blah we did a thing and it generally aligns with prior results.
+Overall replication rate is consistent with prior work, and we find cog greater than soc.
+However, by looking at a greater range of pr
 
@@
 
+circle back to the idea that student replications (either as class or before extension into their own work) would be valuable
+
 \hypertarget{methods}{%
@@
 TODO example and template
+
+{[}some of this should actually just go in methods methods{]} Class, taught by last author, is an experimental methods class aimed at first-year graduate students, but taken by \ldots{} Since around 2015, it has been required for incoming PhD students in the Psychology Department.Students are free to choose studies related to their interests, although recent articles from Psychological Science are the recommended path under uncertainty (leading to a high proportion of Psych science articles in this replication sample).
+While the sampling procedure is non-random, it is generally representative of studies that are of interest to and doable by first year grad students.
 
@@
 These were coded on a {[}0, .25, .5, .75, 1{]} scale.
+TODO rate of coding discrepancy
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-altmejd2019}{}}%
+Altmejd A, Dreber A, Forsell E, Huber J, Imai T, Johannesson M, Kirchler M, Nave G, Camerer C (2019) Predicting the replicability of social science lab experiments.
+\emph{PLOS ONE} \textbf{14}:e0225826.
+doi:\href{https://doi.org/10.1371/journal.pone.0225826}{10.1371/journal.pone.0225826}
+
+\leavevmode\vadjust pre{\hypertarget{ref-camerer2016}{}}%
+Camerer CF, Dreber A, Forsell E, Ho T-H, Huber J, Johannesson M, Kirchler M, Almenberg J, Altmejd A, Chan T, Heikensten E, Holzmeister F, Imai T, Isaksson S, Nave G, Pfeiffer T, Razen M, Wu H (2016) Evaluating replicability of laboratory experiments in economics.
+\emph{Science} \textbf{351}:1433--1436.
+doi:\href{https://doi.org/10.1126/science.aaf0918}{10.1126/science.aaf0918}
+
 \leavevmode\vadjust pre{\hypertarget{ref-camerer2018}{}}%
@@
 \emph{Science}
+
+\leavevmode\vadjust pre{\hypertarget{ref-dreber2015}{}}%
+Dreber A, Pfeiffer T, Almenberg J, Isaksson S, Wilson B, Chen Y, Nosek BA, Johannesson M (2015) Using prediction markets to estimate the reproducibility of scientific research.
+\emph{Proc Natl Acad Sci} \textbf{112}:15343--15347.
+doi:\href{https://doi.org/10.1073/pnas.1516179112}{10.1073/pnas.1516179112}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-etz2016}{}}%
+Etz A, Vandekerckhove J (2016) A {Bayesian Perspective} on the {Reproducibility Project}: {Psychology}.
+\emph{PLOS ONE} \textbf{11}:e0149794.
+doi:\href{https://doi.org/10.1371/journal.pone.0149794}{10.1371/journal.pone.0149794}
+
+\leavevmode\vadjust pre{\hypertarget{ref-forsell2019}{}}%
+Forsell E, Viganola D, Pfeiffer T, Almenberg J, Wilson B, Chen Y, Nosek BA, Johannesson M, Dreber A (2019) Predicting replication outcomes in the {Many Labs} 2 study.
+\emph{Journal of Economic Psychology} \textbf{75}:102117.
+doi:\href{https://doi.org/10.1016/j.joep.2018.10.009}{10.1016/j.joep.2018.10.009}
+
 \leavevmode\vadjust pre{\hypertarget{ref-frank2012}{}}%
 Frank MC, Saxe R (2012) Teaching {Replication}: \emph{Perspect Psychol Sci}. doi:\href{https://doi.org/10.1177/1745691612460686}{10.1177/1745691612460686}
+
+\leavevmode\vadjust pre{\hypertarget{ref-gilbert2016}{}}%
+Gilbert DT, King G, Pettigrew S, Wilson TD (2016) Comment on {``{Estimating} the reproducibility of psychological science.''} \emph{Science} \textbf{351}:1037--1037.
+doi:\href{https://doi.org/10.1126/science.aad7243}{10.1126/science.aad7243}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-nosek2020}{}}%
+Nosek BA, Errington TM (2020) The best time to argue about what a replication means?
+{Before} you do it.
+\emph{Nature} \textbf{583}:518--520.
+doi:\href{https://doi.org/10.1038/d41586-020-02142-6}{10.1038/d41586-020-02142-6}
+
+\leavevmode\vadjust pre{\hypertarget{ref-patil2016}{}}%
+Patil P, Peng RD, Leek JT (2016) What {Should Researchers Expect When They Replicate Studies}?
+{A Statistical View} of {Replicability} in {Psychological Science}.
+\emph{Perspect Psychol Sci} \textbf{11}:539--544.
+doi:\href{https://doi.org/10.1177/1745691616646366}{10.1177/1745691616646366}
+
+\leavevmode\vadjust pre{\hypertarget{ref-pawel2020}{}}%
+Pawel S, Held L (2020) Probabilistic forecasting of replication studies. \emph{PLOS ONE} \textbf{15}:e0231416. doi:\href{https://doi.org/10.1371/journal.pone.0231416}{10.1371/journal.pone.0231416}
+
 \end{CSLReferences}

### 2023-03-22 paper/manuscript.Rmd
tweaks

@@
 
-[replication: it's a hot issue and concerns around replication have done a lot, see crisis/revolution] Concerns around the practices of science.
+[structure w/i intro?]
+
+[replication: it's a hot issue and concerns around replication have done a lot, see crisis/revolution] Psychology is in the middle of some heated debate around the fields practices and many reform efforts.
+Many of these issues concern the truthworthiness or not of the published literature, with transparency, openness efforts.
+A lot of this centers around issues of reproducibility and replicability.
+Concerns around the practices of science.
 Replication is a hot topic.
@@
 [ there's ...
-not a lot of empirics]To quantify and understand this problem, we need empirical data about replication attempts.
+not a lot of empirics] One of the concerns is that published literature may not replicate as much as previously thought or as desired.
+To quantify and understand this problem, we need empirical data about replication attempts.
 However, due to the arduous nature of collecting samples of replications, there have not been many large-scale replication efforts, so all of the argumentation around predictors of replications and field-wide replication rates is fit to a small number of data points.
 
+[do we discuss reasons for replications and why many, while valuable in specific phenomena, help less with this question?]
 Many replications of individual effects have been performed, but these are less useful as pattern analysis because the varied sampling and reporting, and the fact they aren't all in one place.
@@
 
+## prior literature
 We are aware of three large-scale replication efforts replicating experimental results in the existing psychology literature.
@@
 
+## predictors
 In addition to determining estimated overall replicaiton rates for fields and journals, there's also merit in knowing what features of experiments (and replication attempts) are predictive of replication success.
 Blah blah stakeholders and resources.
+Scientists may want to build their work on studies that are likely to replicate, so that they can replicate and build on work without wasting resources.
+Similarly investing in interventions may want to start with things that are more likely to replicate.
 There's some signal here, as people are able to predict replication success at above chance CITATIONS [@hoogeveen2019;@dreber2015; @forsell2019;@camerer2018]
@@
 
+## current work
 Prior literature, such as @frank2012 and @hawkins have advocated using research methods classes to conduct replications, both for the education and scientific value.
@@
 PSYCH 251 is Stanford Psychology's graduate-level experimental methods class taught by MCF.
-Over the course of 10 weeks, students choose a published finding to replicate, re-implement the study, write analysis code, pre-register their study, collect data using an online platform, and write up a structured replication report.
+During the 10 week class, students replicate a published finding.
+They individually re-implement the study, write analysis code, pre-register their study, collect data using an online platform, and write up a structured replication report.
 Students are free to choose studies related to their research interests, with the default recommendation being an article from a recent year of Psychological Science.
-While this choice results in a non-random sampling of studies, the sample is representative of studies that are of interest to and doable by first year graduate students.
+While this choice results in a non-random sample from the literature, the sample is representative of studies that are of interest to and doable by first year graduate students.
 
 The sample of replicated studies reflects the variability of the literature, including studies from different subfields, using different experimental methods and statistical outcomes.
-We leverage the naturally occuraing variability in this sample of replications to examine how different demographic, experimental design, and statistical properties predict replication success.
+We leverage the naturally occurring variability in this sample of replications to examine how different demographic, experimental design, and statistical properties predict replication success.
 
@@
 The instruction team had coded a holistic measure of replication success for each project when they were turned in at the end of the course.
-For reliability, we had a separate rater (VB) independently code the replication success from the replication reports; discrepancies were resolved by discussion between MCF and VB.
-We focussed on this measure because it was applicable across the range of statistical measures and reporting practices and accommodated studies where there were multiple important outcome measures.
+For reliability, VB independently code the replication success from the replication reports; discrepancies were resolved by discussion between MCF and VB (ToDO foobar % of cases).
+This measure was applicable across the range of statistical measures and reporting practices and accommodated studies where there were multiple important outcome measures.
 
@@
 pred_int_rate <- d |> filter(!is.na(predInt)) |> summarize(m=mean(as.numeric(predInt))*100)
-porig_rate <- d |> filter(!is.na(p_orig)) |> summarize(m=median(p_orig)*100)
+porig_rate <- d |> filter(!is.na(p_orig)) |> summarize(m=median(p_orig))
 ```
+
 Across the 176 studies, the overall subjective replication rate was `r round(pluck(sub_rep_rate,1))`%.
 `r round(pluck(pred_int_rate,1))`% of the studies had replication outcomes within the prediction interval of the original outcome.
-The median p_original value was `r round(pluck(porig_rate, 1))`%.
+The median p_original value was `r round(pluck(porig_rate, 1),2)`.
 Figure \ref{fig:smd} shows the relationship between original SMD, replication SMD, and subjective replication score.
@@
 ## Dataset
-The dataset of replication projects comes from class projects conducted in PSYCH 251 (earlier called PSYCH 24) a graduate-level experimental methods class taught by MCF from 2011 to 2022.
+The dataset of replication projects comes from class projects conducted in PSYCH 251 (earlier called PSYCH 254) a graduate-level experimental methods class taught by MCF from 2011 to 2022.
+This class is commonly taken by first year graduate students in psychology and related disciplines, and it has been a requirement of the Psychology PhD since around 2015.
 Each student chose a study to replicate, implemented the study, wrote analysis code, pre-registered their replication, ran the study, and turned in a structured final report including methods, analytic plan, changes from the original study, confirmatory and exploratory analyses, and discussion of outcomes.
@@
 
-[some of this should actually just go in methods methods] Class, taught by last author, is an experimental methods class aimed at first-year graduate students, but taken by ...
-Since around 2015, it has been required for incoming PhD students in the Psychology Department.Students are free to choose studies related to their interests, although recent articles from Psychological Science are the recommended path under uncertainty (leading to a high proportion of Psych science articles in this replication sample).
-While the sampling procedure is non-random, it is generally representative of studies that are of interest to and doable by first year grad students.
+Students were free to choose what study they replicated; the recommended path for students who did not have their own ideas was to pick an interesting study from a recent year of Psychological Science (this led to a high fraction of Psych Science articles in the replication sample FOOBAR %).
 

### 2023-03-22 paper/manuscript.tex
tweaks

@@
 
-{[}replication: it's a hot issue and concerns around replication have done a lot, see crisis/revolution{]} Concerns around the practices of science.
+{[}structure w/i intro?{]}
+
+{[}replication: it's a hot issue and concerns around replication have done a lot, see crisis/revolution{]} Psychology is in the middle of some heated debate around the fields practices and many reform efforts.
+Many of these issues concern the truthworthiness or not of the published literature, with transparency, openness efforts.
+A lot of this centers around issues of reproducibility and replicability.
+Concerns around the practices of science.
 Replication is a hot topic.
@@
 
-{[} there's \ldots{} not a lot of empirics{]}To quantify and understand this problem, we need empirical data about replication attempts.
+{[} there's \ldots{} not a lot of empirics{]} One of the concerns is that published literature may not replicate as much as previously thought or as desired.
+To quantify and understand this problem, we need empirical data about replication attempts.
 However, due to the arduous nature of collecting samples of replications, there have not been many large-scale replication efforts, so all of the argumentation around predictors of replications and field-wide replication rates is fit to a small number of data points.
 
+{[}do we discuss reasons for replications and why many, while valuable in specific phenomena, help less with this question?{]}
 Many replications of individual effects have been performed, but these are less useful as pattern analysis because the varied sampling and reporting, and the fact they aren't all in one place.
 Also pub bias.
+
+\hypertarget{prior-literature}{%
+\subsection{prior literature}\label{prior-literature}}
 
@@
 
+\hypertarget{predictors}{%
+\subsection{predictors}\label{predictors}}
+
 In addition to determining estimated overall replicaiton rates for fields and journals, there's also merit in knowing what features of experiments (and replication attempts) are predictive of replication success.
 Blah blah stakeholders and resources.
+Scientists may want to build their work on studies that are likely to replicate, so that they can replicate and build on work without wasting resources.
+Similarly investing in interventions may want to start with things that are more likely to replicate.
 There's some signal here, as people are able to predict replication success at above chance CITATIONS (\protect\hyperlink{ref-dreber2015}{Dreber et al.
@@
 When sampling is likely related to replicability, the studies are less good for estimating base rates and predictors of replicability in the literature as a whole.
+
+\hypertarget{current-work}{%
+\subsection{current work}\label{current-work}}
 
@@
 The instruction team had coded a holistic measure of replication success for each project when they were turned in at the end of the course.
-For reliability, we had a separate rater (VB) independently code the replication success from the replication reports; discrepancies were resolved by discussion between MCF and VB.
-We focussed on this measure because it was applicable across the range of statistical measures and reporting practices and accommodated studies where there were multiple important outcome measures.
+For reliability, VB independently code the replication success from the replication reports; discrepancies were resolved by discussion between MCF and VB (ToDO foobar \% of cases).
+This measure was applicable across the range of statistical measures and reporting practices and accommodated studies where there were multiple important outcome measures.
 
@@
 46\% of the studies had replication outcomes within the prediction interval of the original outcome.
-The median p\_original value was 3\%.
+The median p\_original value was 0.03.
 Figure \ref{fig:smd} shows the relationship between original SMD, replication SMD, and subjective replication score.
@@
 
-The dataset of replication projects comes from class projects conducted in PSYCH 251 (earlier called PSYCH 24) a graduate-level experimental methods class taught by MCF from 2011 to 2022.
+The dataset of replication projects comes from class projects conducted in PSYCH 251 (earlier called PSYCH 254) a graduate-level experimental methods class taught by MCF from 2011 to 2022.
+This class is commonly taken by first year graduate students in psychology and related disciplines, and it has been a requirement of the Psychology PhD since around 2015.
 Each student chose a study to replicate, implemented the study, wrote analysis code, pre-registered their replication, ran the study, and turned in a structured final report including methods, analytic plan, changes from the original study, confirmatory and exploratory analyses, and discussion of outcomes.
@@
 
-{[}some of this should actually just go in methods methods{]} Class, taught by last author, is an experimental methods class aimed at first-year graduate students, but taken by \ldots{} Since around 2015, it has been required for incoming PhD students in the Psychology Department.Students are free to choose studies related to their interests, although recent articles from Psychological Science are the recommended path under uncertainty (leading to a high proportion of Psych science articles in this replication sample).
-While the sampling procedure is non-random, it is generally representative of studies that are of interest to and doable by first year grad students.
+Students were free to choose what study they replicated; the recommended path for students who did not have their own ideas was to pick an interesting study from a recent year of Psychological Science (this led to a high fraction of Psych Science articles in the replication sample FOOBAR \%).
 

### 2023-03-23 paper/manuscript.Rmd
work on intro

@@
 ---
-title: PUT YOUR TITLE HERE
+title: "Correlates of replicability: evidence from student replication projects"
 author:
@@
 ::: {.abstract data-latex="" lang=en}
-TODO abstract
+
+A cumulative science relies on knowing how much to trust published findings.
+Large-scale replication studies provide a measure of how reliable the published literature in a field is by determining what fraction of studies replicate.
+Because of the effort involved in conducting a large number of replications, few large-scale replications are available.
+We add 176 replication projects conducted by students of experimental studies primarily in psychology.
+Roughly half the studies were replicated successfully, and we report how features of the studies and the replications influenced the replication outcome.
+
 :::
@@
 <!-- Use class keywords to format keywords section -->
-::: {.keywords data-latex="" lang=en}
+<!--::: {.keywords data-latex="" lang=en}
 One keyword; Yet another keyword
-:::
+:::-->
 
@@
 # TODO list
-- title
-- abstract
-- need to do supplement with the stuff we preregistered (sensitivity analysis, all models)
-- how to introduce coding methods (outcome measures)
+- BETTER title
+- BETTER abstract
+- need to do supplement with the stuff we preregistered (sensitivity analysis, all models) -- waiting on finalized stats predictors
 - many citations everywhere
@@
 - ** verify code for ES ** with someone
-- note that 4ish of these papers were previously reported in RP:P
 
@@
 predict w/ ML @altmejd2019
-prediction with humans @dreber2015; @forsell2019
 
@@
 
-[structure w/i intro?]
-
-[replication: it's a hot issue and concerns around replication have done a lot, see crisis/revolution] Psychology is in the middle of some heated debate around the fields practices and many reform efforts.
-Many of these issues concern the truthworthiness or not of the published literature, with transparency, openness efforts.
-A lot of this centers around issues of reproducibility and replicability.
-Concerns around the practices of science.
-Replication is a hot topic.
-Some argue that it is a cornerstone of a cumulative science, and findings of low replication rates are a problem.
+Psychology is in the middle of heated debate over its research practices and the subject of many reform efforts.
+Many of these issues concern how trustworth the published literature is (or isn't), how it got to be this way, and what measures can be taken to improve the quality of findings for the future.
+These issues center around issues of reproducibility  and replicability.
 Concerns about replication rates have become a large point of discussion in psychology and other fields, with large scale replications spurring these discussions and providing the empirical data analyzed by all sides.
 
-[ there's ...
-not a lot of empirics] One of the concerns is that published literature may not replicate as much as previously thought or as desired.
-To quantify and understand this problem, we need empirical data about replication attempts.
-However, due to the arduous nature of collecting samples of replications, there have not been many large-scale replication efforts, so all of the argumentation around predictors of replications and field-wide replication rates is fit to a small number of data points.
+ A major concern is that published literature may not replicate as much as previously thought or as desired.
+This has been illustrated by prominent findings/theories not replicating at all (ego depletion/ TMT?).
+To understand how replicable the literature as a whole is, we need empirical data about replication attempts across a wide range of studies.
+Most replications are targeted replications of individual results of interest to the researcher, but these are not sampled randomly from the literature, are performed in inconsistent ways, and may be selectively published depending on the results.
+Thus, they are not ideal for estimating the overall replicability of the field.
 
-[do we discuss reasons for replications and why many, while valuable in specific phenomena, help less with this question?]
-Many replications of individual effects have been performed, but these are less useful as pattern analysis because the varied sampling and reporting, and the fact they aren't all in one place.
-Also pub bias.
+There have been a limited number of large-scale replication efforts, which sample studies from a discipline to estimate overall replicability.
+Due to the arduous process of replicating many studies, there have not been many large-scale replication efforts.
+Thus, all of the argumentation around predictors of replications and field-wide replication rates is fit to a small number of data points.
 
@@
 
+```{r}
+matching <- d |> filter(status!="unusable") |> mutate(match=ifelse(replicated_instructor_code==replicated_report_code,1,0)) |> group_by(match) |> tally()
+
+pred_int_avail <- d |> filter(!is.na(predInt)&!is.na(p_orig)) |> tally()
+
+```
+
 PSYCH 251 is Stanford Psychology's graduate-level experimental methods class taught by MCF.
@@
 The instruction team had coded a holistic measure of replication success for each project when they were turned in at the end of the course.
-For reliability, VB independently code the replication success from the replication reports; discrepancies were resolved by discussion between MCF and VB (ToDO foobar % of cases).
+For reliability, VB independently code the replication success from the replication reports; discrepancies were resolved by discussion between MCF and VB (`r pluck(matching,2,1)/176*100 |> round()` % of cases).
 This measure was applicable across the range of statistical measures and reporting practices and accommodated studies where there were multiple important outcome measures.
 
-As a complement, we also used two statistical measure of replication on the subset of the data where they were computable (NUMBER, see Figure \ref{fig:prisma}).
+As a complement, we also used two statistical measure of replication on the subset of the data where they were computable (`r pluck(pred_int_avail,1)` cases, see Figure \ref{fig:prisma}).
 We measured p-original, the p-value on the null hypothesis that the original and replication statistics are from the same distribution, as a continuous variable, and we also determined whether the replication statistic fell within the prediction interval of the original statistic [@errington2021].
@@
 knitr::kable(cors, digits = 3, align='rcc',format="latex", position="!h", caption="The correlation of individual predictors with subjective replication outcomes.
-For subfield, cognitive psychology is treated as the baseline condition.") |> kable_styling(full_width=F, font_size=10)
+For subfield, cognitive psychology is treated as the baseline condition.
+See Methods for how these variables were coded.") |> kable_styling(full_width=F, font_size=10)
 
@@
 
-Students were free to choose what study they replicated; the recommended path for students who did not have their own ideas was to pick an interesting study from a recent year of Psychological Science (this led to a high fraction of Psych Science articles in the replication sample FOOBAR %).
+Students were free to choose what study they replicated; the recommended path for students who did not have their own ideas was to pick an interesting study from a recent year of Psychological Science (this led to a high fraction of Psych Science articles in the replication sample TODO FOOBAR %).
+
+We note that 4 (TODO check) of the replication projects were included in RP:P, and FOOBAR of them were previously reported in @hawkins.
 
@@
 For all studies, replication success was independently coded by VB on the basis of the reports.
-Where VB’s coding disagreed with the staff/MCF’s code, the difference was resolved by discussion between VB and MCF.
+Where VB’s coding disagreed with the staff/MCF’s code, the difference was resolved by discussion between VB and MCF (`r pluck(matching,2,1)/176*100 |> round()`% of studies).
 These were coded on a [0, .25, .5, .75, 1] scale.
-TODO rate of coding discrepancy
 

### 2023-03-23 paper/manuscript.tex
work on intro

@@
 \hypersetup{
-  pdftitle={PUT YOUR TITLE HERE},
+  pdftitle={Correlates of replicability: evidence from student replication projects},
   pdflang={en},
@@
 
-\title{PUT YOUR TITLE HERE}
+\title{Correlates of replicability: evidence from student replication projects}
 
@@
 \begin{abstract}
-TODO abstract
+A cumulative science relies on knowing how much to trust published findings.
+Large-scale replication studies provide a measure of how reliable the published literature in a field is by determining what fraction of studies replicate.
+Because of the effort involved in conducting a large number of replications, few large-scale replications are available.
+We add 176 replication projects conducted by students of experimental studies primarily in psychology.
+Roughly half the studies were replicated successfully, and we report how features of the studies and the replications influenced the replication outcome.
 
 \end{abstract}
-
-\end{otherlanguage}
-
-\begin{otherlanguage}{english}
-
-\begin{keywords}
-One keyword; Yet another keyword
-
-\end{keywords}
 
@@
 \item
-  title
+  BETTER title
 \item
-  abstract
+  BETTER abstract
 \item
-  need to do supplement with the stuff we preregistered (sensitivity analysis, all models)
-\item
-  how to introduce coding methods (outcome measures)
+  need to do supplement with the stuff we preregistered (sensitivity analysis, all models) -- waiting on finalized stats predictors
 \item
@@
   ** verify code for ES ** with someone
-\item
-  note that 4ish of these papers were previously reported in RP:P
 \end{itemize}
@@
 predict w/ ML Altmejd et al. (\protect\hyperlink{ref-altmejd2019}{2019})
-prediction with humans Dreber et al. (\protect\hyperlink{ref-dreber2015}{2015}); Forsell et al. (\protect\hyperlink{ref-forsell2019}{2019})
 
@@
 
-{[}structure w/i intro?{]}
-
-{[}replication: it's a hot issue and concerns around replication have done a lot, see crisis/revolution{]} Psychology is in the middle of some heated debate around the fields practices and many reform efforts.
-Many of these issues concern the truthworthiness or not of the published literature, with transparency, openness efforts.
-A lot of this centers around issues of reproducibility and replicability.
-Concerns around the practices of science.
-Replication is a hot topic.
-Some argue that it is a cornerstone of a cumulative science, and findings of low replication rates are a problem.
+Psychology is in the middle of heated debate over its research practices and the subject of many reform efforts.
+Many of these issues concern how trustworth the published literature is (or isn't), how it got to be this way, and what measures can be taken to improve the quality of findings for the future.
+These issues center around issues of reproducibility and replicability.
 Concerns about replication rates have become a large point of discussion in psychology and other fields, with large scale replications spurring these discussions and providing the empirical data analyzed by all sides.
 
-{[} there's \ldots{} not a lot of empirics{]} One of the concerns is that published literature may not replicate as much as previously thought or as desired.
-To quantify and understand this problem, we need empirical data about replication attempts.
-However, due to the arduous nature of collecting samples of replications, there have not been many large-scale replication efforts, so all of the argumentation around predictors of replications and field-wide replication rates is fit to a small number of data points.
+A major concern is that published literature may not replicate as much as previously thought or as desired.
+This has been illustrated by prominent findings/theories not replicating at all (ego depletion/ TMT?).
+To understand how replicable the literature as a whole is, we need empirical data about replication attempts across a wide range of studies.
+Most replications are targeted replications of individual results of interest to the researcher, but these are not sampled randomly from the literature, are performed in inconsistent ways, and may be selectively published depending on the results.
+Thus, they are not ideal for estimating the overall replicability of the field.
 
-{[}do we discuss reasons for replications and why many, while valuable in specific phenomena, help less with this question?{]}
-Many replications of individual effects have been performed, but these are less useful as pattern analysis because the varied sampling and reporting, and the fact they aren't all in one place.
-Also pub bias.
+There have been a limited number of large-scale replication efforts, which sample studies from a discipline to estimate overall replicability.
+Due to the arduous process of replicating many studies, there have not been many large-scale replication efforts.
+Thus, all of the argumentation around predictors of replications and field-wide replication rates is fit to a small number of data points.
 
@@
 The instruction team had coded a holistic measure of replication success for each project when they were turned in at the end of the course.
-For reliability, VB independently code the replication success from the replication reports; discrepancies were resolved by discussion between MCF and VB (ToDO foobar \% of cases).
+For reliability, VB independently code the replication success from the replication reports; discrepancies were resolved by discussion between MCF and VB (25.5681818 \% of cases).
 This measure was applicable across the range of statistical measures and reporting practices and accommodated studies where there were multiple important outcome measures.
 
-As a complement, we also used two statistical measure of replication on the subset of the data where they were computable (NUMBER, see Figure \ref{fig:prisma}).
+As a complement, we also used two statistical measure of replication on the subset of the data where they were computable (134 cases, see Figure \ref{fig:prisma}).
 We measured p-original, the p-value on the null hypothesis that the original and replication statistics are from the same distribution, as a continuous variable, and we also determined whether the replication statistic fell within the prediction interval of the original statistic (\protect\hyperlink{ref-errington2021}{Errington et al.
@@
 
-\caption{\label{tab:cor}The correlation of individual predictors with subjective replication outcomes. For subfield, cognitive psychology is treated as the baseline condition.}
+\caption{\label{tab:cor}The correlation of individual predictors with subjective replication outcomes.
+For subfield, cognitive psychology is treated as the baseline condition.
+See Methods for how these variables were coded.}
 \centering
@@
 
-Students were free to choose what study they replicated; the recommended path for students who did not have their own ideas was to pick an interesting study from a recent year of Psychological Science (this led to a high fraction of Psych Science articles in the replication sample FOOBAR \%).
+Students were free to choose what study they replicated; the recommended path for students who did not have their own ideas was to pick an interesting study from a recent year of Psychological Science (this led to a high fraction of Psych Science articles in the replication sample TODO FOOBAR \%).
+
+We note that 4 (TODO check) of the replication projects were included in RP:P, and FOOBAR of them were previously reported in Hawkins et al. (\protect\hyperlink{ref-hawkins}{n.d.}).
 
@@
 For all studies, replication success was independently coded by VB on the basis of the reports.
-Where VB's coding disagreed with the staff/MCF's code, the difference was resolved by discussion between VB and MCF.
+Where VB's coding disagreed with the staff/MCF's code, the difference was resolved by discussion between VB and MCF (25.5681818\% of studies).
 These were coded on a {[}0, .25, .5, .75, 1{]} scale.
-TODO rate of coding discrepancy
 

### 2023-03-28 code/process.Rmd
redo models with correct data

@@
 library(ggthemes)
-
+library(knitr)
 rstan_options(auto_write = TRUE)
@@
 
-d |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> tally()
+d |> filter(!status %in% c("missing", "non-experiment", "reproduction", "unusable")) |> tally()
 
@@
 ```{r}
-d_val <- d |> filter(!status %in% c("missing", "non-experiment", "reproduction"))
+d_val <- d |> filter(!status %in% c("missing", "non-experiment", "reproduction", "unusable"))
 ```
@@
   mutate(pub_year= target_year-mean(target_year),
-         log_p =log(target_p_calc),
+         log_p =ifelse(target_p_calc==0,-300, log(target_p_calc)), #prevent any -Inf problems!
          log_sample =log(target_N),
@@
          predInt=as.numeric(predInt)) |> 
-  select(include, target_lastauthor_year, academic_year, subfield, 
+  select(sensitivity, include, target_lastauthor_year, academic_year, subfield, 
          pub_year, log_p, log_sample, log_ratio_ss, change_platform, target_d_calc,
@@
 
-## Sensitivity analysis TODO
+## Sensitivity analysis
+
+### data
+
+```{r}
+data_sens <- z_data |> mutate(sensitivity=ifelse(is.na(sensitivity), include, sensitivity))
+
+data_sens1 <- data_sens |> filter(sensitivity %in% c("stats", "exp", "pred_int")) |>
+  mutate(sub_rep=sub_rep*4+1) |>  #remap to 1-5 scale
+  select(academic_year, sub_rep, 
+         z_pub_year, subfield, open_data, open_mat, stanford, change_platform, z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials)
+
+data_sens2 <- data_sens |> filter(sensitivity %in% c("stats", "pred_int")) |>
+  select(academic_year, sub_rep, 
+         p_orig, predInt,
+         z_pub_year, subfield, open_data, open_mat, stanford, change_platform, z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials)
+
+data_sens3 <- data_sens |>  filter(sensitivity %in% c("stats")) |>
+  select(academic_year, sub_rep, 
+         p_orig, predInt,
+         z_target_d_calc, z_log_p, 
+         z_pub_year, subfield, open_data, open_mat, stanford, change_platform, z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials) 
+```
+
+### models
+
+```{r, eval=T}
+sens_tier1_subjective <- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
+                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                             z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
+                        family="cumulative", # runs on 1-5 data
+                        data=data_sens1,
+                        file=here(model_location, "sens_tier1_subjective"),
+                        prior=priors, 
+                        control=list(adapt_delta=.99),
+                        backend="cmdstanr"
+)
+```
+
+```{r, eval=T}
+sens_tier2_predint <- brm(predInt ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                       z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
+                       (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
+                     family="bernoulli",
+                     data=data_sens2,
+                     file=here(model_location, "sens_tier2_predint"),
+                     prior=priors, 
+                     control=list(adapt_delta=.99),
+                     backend="cmdstanr")
+```
+
+```{r, eval=T}
+sens_tier2_porig <- brm(p_orig ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                     z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
+                     (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                        z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
+                   data=data_sens2,
+                   file=here(model_location, "sens_tier2_porig"),
+                   prior=priors, 
+                   control=list(adapt_delta=.99),
+                   backend="cmdstanr")
+```
+
+```{r, eval=T}
+sens_tier3_subjective <- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
+                          z_target_d_calc + z_log_p+ 
+                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                             z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
+                             z_target_d_calc + z_log_p| academic_year),
+                        family="cumulative",
+                        data=data_sens3 |> mutate(sub_rep=sub_rep*4+1),
+                        file=here(model_location, "sens_tier3_subjective"),
+                        prior=priors, 
+                        control=list(adapt_delta=.99),
+                        backend="cmdstanr")
+```
+
+```{r, eval=T}
+sens_tier3_predint <- brm(predInt ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                       z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
+                       z_target_d_calc + z_log_p+ 
+                       (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
+                          z_target_d_calc + z_log_p| academic_year),
+                     family="bernoulli",
+                     data=data_sens3,
+                     file=here(model_location, "sens_tier3_predint"),
+                     prior=priors, 
+                     control=list(adapt_delta=.99),
+                     backend="cmdstanr")
+```
+
+```{r, eval=T}
+sens_tier3_porig <- brm(p_orig ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                     z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
+                     z_target_d_calc + z_log_p+ 
+                     (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
+                        z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
+                        z_target_d_calc + z_log_p| academic_year),
+                   data=data_sens3,
+                   file=here(model_location, "sens_tier3_porig"),
+                   prior=priors, 
+                   control=list(adapt_delta=.99),
+                   backend="cmdstanr"
+)
+```
 
@@
 ```
-# Exploratory even randomer
+
+<!--# Exploratory even randomer
 
@@
 ```
+
+-->

### 2023-03-28 paper/manuscript.Rmd
redo models with correct data

@@
 		\node[mynode, join, on chain=1, fill=good] (n6)
-		{\textbf{131} pairs with ES};
+		{\textbf{136} pairs with ES};
 		\node[mynode, join, on chain=1, fill=good] (n7)
-		{\textbf{107} pairs with SMD};
+		{\textbf{112} pairs with SMD};
 

### 2023-03-28 code/helper/parse_stats.R

@@ -258,17 +258,33 @@ parse_beta_ci <- function(raw_stat){
 
 #this is just to deal with yang2018 where we have d's given and bci
 #ex <- "d: 1.40 ; bci: b=1.72 [1.44, 2.00]"
-parse_dbci <- function(raw_stat){
+parse_dbci <- function(raw_stat,n){
   bci = str_extract(raw_stat, ";.*") |> str_sub(2,-1)
   beta=str_extract(bci, "b=.*\\[") |> str_sub(3,-2) |> as.numeric()
   low=str_extract(bci, "\\[.*,") |> str_sub(2,-2) |> as.numeric()
   high=str_extract(bci, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
   se=(high-low)/(2*1.96)
-  
+  t=beta/se
+  df=n*2-1 # there are two trials / kid, so I think this makes sense? 
+  pval=pt(q=t, df=df, lower.tail=FALSE)*2
   dval = str_extract(raw_stat, ".*;") |> str_sub(3,-2) |> as.numeric()
-  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=dval, "N_calc"=NA, "ES"=beta, "SE"=se))
+  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=dval, "N_calc"=NA, "ES"=beta, "SE"=se))
 }
 #parse_dbci(ex)
+
+foo <- "pear: r=.75, n=45"
+parse_pearson <- function(raw_stat){
+  r=str_extract(raw_stat, "r=.*,") |> str_sub(3,-2) |> as.numeric()
+  n=str_extract(raw_stat, "n=.*") |> str_sub(3,-1) |> as.numeric()
+  d=2*r/sqrt(1-r**2) # using an approximation
+  se=4/n+d**2/(2*n)
+  t=d*sqrt(n)/2
+  pval=pt(q=t, df=n-2, lower.tail=FALSE)*2
+return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=d, "N_calc"=NA, "ES"=d, "SE"=se))
+  
+}
+
+parse_pearson(foo)
 
 
 do_blanks <- function(){
[…]

### 2023-03-28 paper/supplement.Rmd
work on supplement

---
title: "Supplement"
output: pdf_document
date: "2023-03-28"

header-includes:
 - \usepackage{tikz}
 - \usetikzlibrary{positioning,arrows.meta, quotes, shapes}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE) # By default, hide code; set to TRUE to see code
#knitr::opts_chunk$set(fig.pos = 'th') # Places figures at top or here
knitr::opts_chunk$set(out.width = '100%', dpi=300,
                      fig.width=8, fig.width=8) # Figure resolution and size
knitr::opts_chunk$set(fig.env="figure") # Latex figure environment

options(knitr.table.format="latex") # For kable tables to work without setting format option

knitr::opts_chunk$set(echo=F, warning=F, message=F)#dev = "png", dev.args = list(type = "cairo-png")
 library("papaja")
library("bookdown")
library("rticles")
 library(here)
 library(tidyverse)
 library(brms)
library(tidybayes)
library(kableExtra)
library(viridis)
library(cowplot)
library(ggthemes)
#r_refs("r-references.bib", append=F)
theme_set(theme_bw())
options(knitr.table.format = "pdf")

model_location="code/models"

```

# Additional model results

Per our pre-registration, we ran a set of 6 models crossing 3 outcome measures (subjective replication score, whether the replication result was within the prediction interval of the original, and p-original on the hypothesis that both came from the same distribution) with 2 sets of predictors (with or without statistical predictors). These 6 models required 3 tiers of data: the subjective replication score without statistical predictors applies to all the data; the p_original and prediction interval models apply to the subset of data with numeric outcomes that can be compared; and the statistical predictor models need the smaller subset of data with p-values and original SMD in particular.

Due to low sample sizes and large numbers of predictors, even with regularizing priors, the coefficient estimates generally have a lot of uncertainty.

## Sensitivity Analysis

As a check on whether our results were sensitive to the inclusion of pairs that were marginal in some way, we repeated the 6 models including only studies that were not marginal.

```{=latex}
\definecolor{bad}{HTML}{FFCCCB}
		\definecolor{meh}{HTML}{efefef}
			\definecolor{good}{HTML}{abcdff}
	\tikzset{
		mynode/.style={
			draw, rectangle, align=center, text width=4.5cm, scale=1, font=\small, inner sep=.5ex},
		arrow/.style={
		 very thick,->,>=stealth}
	}

\begin{figure}
	\begin{tikzpicture}[auto,
		node distance = 6mm and 30mm,
		every edge quotes/.append style = {font=\footnotesize, text=black, text centered}
		]
		\node (n1) [mynode, fill=good] {\textbf{112} pairs with statistical predictors};
		\node (n2) [mynode, below=of n1, fill=good]       {\textbf{24} additional pairs for p-original and prediction interval};
		\node (n3) [mynode,below=of n2, fill=good]    {\textbf{40} additional pairs for subjective replication};

		\node (n4) [mynode, fill=meh, right=of n1] {\textbf{82} pairs with statistical predictors};
		\node (n5) [mynode, below=of n4, fill=meh]       {\textbf{18} additional pairs for p-original and prediction interval};
		\node (n6) [mynode,below=of n5, fill=meh]    {\textbf{67} additional pairs for subjective replication only};
		\node (n7) [mynode,below=of n6, fill=bad]    {\textbf{9} pairs excluded};

		\begin{scope}[line width=1 pt, >=Stealth]
			\draw [->]   (n1.east) edge [pos=.8, "82"] (n4.west);
			\draw [->]   (n1.east) edge [pos=.8,"25", sloped] (n6.west);
			\draw [->]   (n1.east) edge [pos=.85,"5", sloped] (n7.west);

			\draw [->]   (n2.east) edge [pos=.8,"18"] (n5.west);
			\draw [->]   (n2.east) edge [pos=.6,"4", sloped] (n6.west);
			\draw [->]   (n2.east) edge [pos=.45,"2", sloped] (n7.west);

			\draw [->]   (n3.east) edge [pos=.2,"38"] (n6.west);
			\draw [->]   (n3.east) edge [pos=.5,"2", sloped] (n7.west);

		\end{scope}
	\end{tikzpicture}
	\caption{Diagram of what studies were downgraded or excluded for the sensitivity analysis.}
	\end{figure}

```

```{r}
do_draws <- function(model){
  draws <- model |> gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> 
    mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |>  filter(Term!="Intercept") |> 
    mutate(Term=factor(Term, levels=c("subfieldsocial", "subfieldother_psych", "subfieldnon_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "z_pub_year", "z_log_trials", "z_log_sample", "z_log_ratio_ss","z_log_p","z_target_d_calc"), labels=c("Social", "Other psych", "Non psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rep/orig sample", "P-value", "SMD"))) 
}

tier1_subjective <- read_rds(here(model_location, "tier1_subjective.rds")) |> do_draws() |> mutate(type="Without stats predictors") |> mutate(sens="All data")
tier2_porig <- read_rds(here(model_location, "tier2_porig.rds"))|> do_draws() |>  mutate(type="Without stats predictors") |> mutate(sens="All data")
tier2_predint <- read_rds(here(model_location, "tier2_predint.rds"))|> do_draws() |>  mutate(type="Without stats predictors") |> mutate(sens="All data")
tier3_subjective <- read_rds(here(model_location, "tier3_subjective.rds"))|> do_draws() |> mutate(type="Stats predictors") |> mutate(sens="All data")
tier3_porig <- read_rds(here(model_location, "tier3_porig.rds"))|> do_draws() |>  mutate(type="Stats predictors") |> mutate(sens="All data")
tier3_predint <- read_rds(here(model_location, "tier3_predint.rds"))|> do_draws() |>  mutate(type="Stats predictors") |> mutate(sens="All data")

sens1_subjective <- read_rds(here(model_location, "sens_tier1_subjective.rds"))|> do_draws() |> mutate(type="Without stats predictors") |> mutate(sens="Sensitivity test")
sens2_porig <- read_rds(here(model_location, "sens_tier2_porig.rds"))|> do_draws() |> mutate(type="Without stats predictors")|> mutate(sens="Sensitivity test")
sens2_predint <- read_rds(here(model_location, "sens_tier2_predint.rds"))|> do_draws() |> mutate(type="Without stats predictors")|> mutate(sens="Sensitivity test")
sens3_subjective <- read_rds(here(model_location, "sens_tier3_subjective.rds"))|> do_draws()|> mutate(type="Stats predictors")|> mutate(sens="Sensitivity test")
sens3_porig <- read_rds(here(model_location, "sens_tier3_porig.rds"))|> do_draws()|> mutate(type="Stats predictors")|> mutate(sens="Sensitivity test")
sens3_predint <- read_rds(here(model_location, "sens_tier3_predint.rds"))|> do_draws()|> mutate(type="Stats predictors")|> mutate(sens="Sensitivity test")

subjective <- tier1_subjective |> union(tier3_subjective) |> union(sens1_subjective) |> union(sens3_subjective)
porig <- tier2_porig |> union(tier3_porig) |> union(sens2_porig) |> union(sens3_porig)
predint <- tier2_predint |> union(tier3_predint) |> union(sens2_predint) |> union(sens3_predint)
```

```{r sub-results, out.height="75%", fig.width=8, fig.height=8, fig.pos="ht", fig.cap="Coefficient estimates and uncertainty from ordinal models predicting subjective replication scores. Solid lines correspond to models run on as much of the data as possible; dashed lines are on the subset of the data for sensitivity analysis. Red is run on all relevant data with experimental predictors only; blue is on relevant data where there are statistical predictors."}

  subjective |> ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate, color=type, linetype=sens, shape=sens)) + geom_vline(xintercept=0)+
    scale_shape_manual(values = c(19,21))+
  scale_color_solarized()+
  stat_pointinterval(position=position_dodge(width=.7))+labs(y="", x="Estimate, 66%, 95% CrI predicting subjective replication score", color="", linetype="", shape="")+theme(axis.text=element_text(size=11),legend.position="bottom")

```

```{r predint-results, out.height="75%", fig.width=8, fig.height=8, fig.pos="ht", fig.cap="Coefficient estimates and uncertainty from logistic models predicting prediction intervals. Solid lines correspond to models run on as much of the data as possible; dashed lines are on the subset of the data for sensitivity analysis. Red is run on all relevant data with experimental predictors only; blue is on relevant data where there are statistical predictors."}

  predint |> ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate, color=type, linetype=sens, shape=sens)) + geom_vline(xintercept=0)+
    scale_shape_manual(values = c(19,21))+
  scale_color_solarized()+
  stat_pointinterval(position=position_dodge(width=.7))+labs(y="", x="Estimate, 66%, 95% CrI predicting prediction interval", color="", linetype="", shape="")+theme(axis.text=element_text(size=11),legend.position="bottom")

```

```{r porig-results, out.height="75%", fig.width=8, fig.height=8, fig.pos="ht", fig.cap="Coefficient estimates and uncertainty from linear models predicting p-original values. Solid lines correspond to models run on as much of the data as possible; dashed lines are on the subset of the data for sensitivity analysis. Red is run on all relevant data with experimental predictors only; blue is on relevant data where there are statistical predictors."}

  porig |> ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate, color=type, linetype=sens, shape=sens)) + geom_vline(xintercept=0)+
    scale_shape_manual(values = c(19,21))+
  scale_color_solarized()+
  stat_pointinterval(position=position_dodge(width=.7))+labs(y="", x="Estimate, 66%, 95% CrI predicting p-original values", color="", linetype="", shape="")+theme(axis.text=element_text(size=11),legend.position="bottom")

```

### 2023-03-30 paper/manuscript.Rmd
work on discussion

@@
 ---
-title: "Correlates of replicability: evidence from student replication projects"
+title: "Eleven years of student replication projects provide evidence on the correlates of replicability in psychology"
 author:
@@
 # TODO list
-- BETTER title
 - BETTER abstract
-- need to do supplement with the stuff we preregistered (sensitivity analysis, all models) -- waiting on finalized stats predictors
 - many citations everywhere
@@
 - ** verify code for ES ** with someone
+- redo intro
+- redo results
+- redo discussion
+- fill in todos
 
+# Text slush pile 
+[who knows where this paragraph should go] Replications are one way of approximating whether an effect in the target paper is true, and how likely results are to replicate in some sort of platonic ideal world.
+There is no one answer here; replication projects measure something else that could be treated as an approximation.
+However, what a replication is really measuring is how likely it to get that effect given some conditions.
+Which the right conditions are is a potential point of contention (see discussion around closeness and sample size, power etc).
+Here, we are explicit in what sample of replicators and replication conditions were are sampling, and thus what we can generalize to.
+We are estimating how likely replication is when done online by a graduate student, under constraints that are typical for graduate students (limited time, limited budget).
+As much of scientific process is in fact performed by graduate students, we think this in itself is an interesting question.
+
+We do not interpret our results as saying that all non-replications were false positives (presumably some are replicable under other circumstances and others are not).
+Some of the factors we look at are more easily interpreted as being about the original study than others.
+We do not assign causal explanation to the predictors because there are multiple plausible interpretations: they could be correlates of QRPs in the original, they could be correlates of harder-to-detect or more fragile effects, they could be correlates of less-close replications, they could even be correlates of another stronger predictor.
+
+[ there is controversy here, but to even discuss it, we need empirics] Even those who argue that replication is not so essential still rely on data from replications to make their cases that replication rates are not as low as they seem and that these replication rates are acceptable.
+@lewandowsky2020
+
+circle back to the idea that student replications (either as class or before extension into their own work) would be valuable 
 # Citation slush pile
@@
 
+Anderson, C., Bahnik, S., Barnett-Cowan, M., Bosco, F., Chandler, J., Chartier, C., & otherss.
+(2016).
+Response to comment on “estimating the reproducibility of psychological science.” Science, 351(6277), 1037–1037.
+
+Gilbert, D. T., King, G., Pettigrew, S., & Wilson, T. D. (2016). Comment on “estimating the reproducibility of psychological science.” Science, 351(6277), 1037–1037.
+
+Schmidt, S. (2009). Shall we really do it again? The powerful concept of replication is neglected in the social sciences. Review of General Psychology, 13, 90–100.
+
+Simonsohn, U. (2015). Small telescopes: Detectability and the evaluation of replication results. Psychol. Sci., 26(5), 559–569.
+
+Gelman, A. (2018). Don’t characterize replications as successes or failures. Behavioral and Brain Sciences, 41.
+
+Mathur, M. B., & VanderWeele, T. J. (2020a). New statistical metrics for multisite replication projects. J. R. Stat. Soc. Ser. A Stat. Soc., 183(3), 1145–1166.
+
+pedagogy for replication in intro: frank & saxe, hawkins et al., quintana nature paper, scarcity PNAS pedagogy paper,
+
+Collaborative replications and education project (CREP)
+JE Grahe, MJ Brandt, H IJzerman, N Legate, J Wagge, YJ Weisberg, BJ Wiggins, Retrieved from osf. io/wfc6u, 2016 - Cited by 29
+
+https://psycnet.apa.org/record/2022-15361-001
+https://journals.sagepub.com/doi/pdf/10.1177/1475725719868149
+https://content.iospress.com/articles/education-for-information/efi190308
+
+https://psycnet.apa.org/fulltext/2018-11647-005.html
+
 # introduction
+
+replication is important (but not everything) - good starting place
+ * prereq of theory building that the results of interest "can be observed consistently" 
+ * but not everything (can still have other problems)
+
+replication rates are low in psychology (see studies)
+
+big open question: why
+
+experimental and correlational approaches to answering it
+
+experimental is hard - protzko, ML5 etc. but they are expensive and you can’t do them for many research questions
+
+correlational has been pursued extensively, but is overfit to small data (prediction markets / ML models / regression of all types)
+
+our contribution: provide more data!
+using pedagogical replications, which are good because they’re p(build on)
+slightly different estimand but maybe a better one?
 
@@
 ## current work
+
+one strategy for the pedagogical bit at end of intro: stress “this is what people want to do, that is, pick up a project that they care about (not a random sample of the literature) and see if they can ‘get it to work’” - and “subjective replication success is our primary measure for the same reason….”
+
+can even cite the “science is not a signal detection problem” paper on not randomly sampling from the literature.
+
+Prior approaches to replicability have focused on a potentially problematic estimand: the probability of a finding in the literature being somehow truly replicable.
+Critics have pointed out that "true" replicability may not be possible to estimate outside of a specific sample (van bavel etc.) or even time period (ramscar).
+
+Further, the methods for estimating this quantity have been theoretically problematic.
+Sampling schemes for prior work typically does not reflect a random sample from the literature -- and even if they did, arguably a literature will succeed if useful discoveries come out of it, not if random findings are true ("Science is not signal detection" ref).
+
+In contrast, we have pursued a different estimand: the probability that a researcher, on selecting a finding of interest from the literature, can successfully achieve a result satisfactorily close enough to the original that they feel that they can build on it in their own work, with all the necessary compromises to the methods and sample of the original that may be required by the constraints of the situation.
+SPELL OUT SAMPLING DIFFERENCE AND SUCCESS DIFFERENCE.
+
+We estimate this quantity in the context of a particular pedagogical situation: that of a graduate student entering a doctoral program in psychology...
+
 Prior literature, such as @frank2012 and @hawkins have advocated using research methods classes to conduct replications, both for the education and scientific value.
@@
 
+TODO discuss more about why this one and what other measure we don't choose are
+
 We used a subjective rating of replication success as our primary outcome measure.
@@
 Across the 176 studies, the overall subjective replication rate was `r round(pluck(sub_rep_rate,1))`%.
-`r round(pluck(pred_int_rate,1))`% of the studies had replication outcomes within the prediction interval of the original outcome.
+`r round(pluck(pred_int_rate,1))`% (N=FOOBAR) of the studies had replication outcomes within the prediction interval of the original outcome.
 The median p_original value was `r round(pluck(porig_rate, 1),2)`.
@@
 
-# discussion
+# Discussion
 
-blah blah we did a thing and it generally aligns with prior results.
-Overall replication rate is consistent with prior work, and we find cog greater than soc.
-However, by looking at a greater range of pr
+The replication rate in psychology is to the best estimates, somewhere around 50%, which is quite low.
+Many reasons for this low replication rate have been hypothesized, but studying it either experimentally or correlationally requires doing a number of replication experiments, which can be a lot of work.
+Here we took advantage of 11 years of graduate student replication projects to look at correlational predictors of replication in a previously-unused dataset.
 
-[who knows where this paragraph should go] Replications are one way of approximating whether an effect in the target paper is true, and how likely results are to replicate in some sort of platonic ideal world.
-There is no one answer here; replication projects measure something else that could be treated as an approximation.
-However, what a replication is really measuring is how likely it to get that effect given some conditions.
-Which the right conditions are is a potential point of contention (see discussion around closeness and sample size, power etc).
-Here, we are explicit in what sample of replicators and replication conditions were are sampling, and thus what we can generalize to.
-We are estimating how likely replication is when done online by a graduate student, under constraints that are typical for graduate students (limited time, limited budget).
-As much of scientific process is in fact performed by graduate students, we think this in itself is an interesting question.
-It contrasts with questions like how likely something is to replicate when performed by an expert with a large budget (perhaps this is the right framing on Camerer) or when performed with extensive feedback from the original authors, etc.
+In line with previous replications, we found a FOOBAR replication rate, with some studies showing effect sizes similar to the original and others much smaller.
+Some individual correlates of replicability that stood out included within-subjects designs, work in the subfield of cognitive psychology, and the original and replication both using online samples.
+TODO other possible things
 
-We do not interpret our results as saying that all non-replications were false positives (presumably some are replicable under other circumstances and others are not).
-Some of the factors we look at are more easily interpreted as being about the original study than others.
-We do not assign causal explanation to the predictors because there are multiple plausible interpretations: they could be correlates of QRPs in the original, they could be correlates of harder-to-detect or more fragile effects, they could be correlates of less-close replications, they could even be correlates of another stronger predictor.
+Many of these correlates interrelate with one another, and we are still limited in our sample, so models with multiple predictors have a lot of uncertainty around the effects of each predictor.
 
-[ there is controversy here, but to even discuss it, we need empirics] Even those who argue that replication is not so essential still rely on data from replications to make their cases that replication rates are not as low as they seem and that these replication rates are acceptable.
-@lewandowsky2020
+We are explicit in our goal of estimating how likely it is that a first-year graduate student, attempting to replicate a study of interest to them, gets replication results which are consistent enough with the original results that the student could build on the study in their own work.
+We can't estimate some platonic probability of truth for a study and neither can any replication study.
+Instead, we can estimate how likely studies are to get results of different levels of closeness in different circumstances.
+Much of the discussion around whether things should count as replication successes, or failures, or not replications at all is really about what the right thresholds are for closeness of results, and what the right circumstances are for a replication.
+Rather than try to find the one right answer to whether a direct replication was done in a certain right way, we think it's useful to explicitly label what the estimand really was: how likely it is to get the same results (under whatever metric) given circumstances like those used for the replication.
 
-circle back to the idea that student replications (either as class or before extension into their own work) would be valuable
+In our case, our estimand is about how well first-year graduate students will do at the replication, which takes into account the limited time, limited budget, and limited experience.
+We think this is an important estimand, as much of the work of psychology is done by trainees, in circumstances like these.
+Thus, if some studies have delicate results that require large samples and very exact methods to achieve, they may not replicate under normal resources.
+
+Other replication projects have other estimands: @camerer2018 seems to ask something closer to how likely studies are to replicate when preformed by an expert with a large budget, and @ML5 TODOCITE asks how likely certain studies are to replicate when performed with extensive feedback from the original authors.
+
+We do not interpret our results as saying that all non-replications were false positives (presumably some would be replicable under different implementations and budgets and others would not).
+There are many possible reasons for the non-replications in this sample.
+In some cases, it seemed that the problem may have been with the replication: for instance, if there were too few participants, or if there were high levels of wrong answers on attention checks, or participants speeding through without attention checks.
+For these cases, there was a clear next attempt that a student could make if they wanted to get the replication to work.
+In other cases, there might have been a priori reasons to distrust the original study results, such as exclusion criteria that seemed to be post-hoc, or a three-way interaction effect on a small sample (CITE THAT THIS IS SKETCH).
+In yet other cases, it's unclear why the results failed to replicate.
+
+[somehow transition here] Pedagogy is important for open science.
+It's one thing to require or incentivize scientists to use open science practices and conduct replicable and reproducible research, but using the right tools and workflows to do open science is something that has to be learned.
+Teaching it in the classroom addresses the knowing how point at the beginning and shows students how to have open science practices integrated in to their science at the beginning, before other habits can ossify.
+Doing replications give students the motivation to care about open science, as they see how much easier it is to implement the study with open materials versus the study where they have to make guesses about the study instructions from the methods section.
+In presenting work with classmates, students see that there is variation in how well studies replicate, with some replicating very cleanly and others not at all.
+This sort of first hand experience teaches that not everything they read in the literature may just work if done again.
+
+Our results are limited by the number and quality of the studies we included. These studies are not necessarily representative of the literature as a whole. TODO what are the limitations we want?
+
+TODO quick wrap up
 

### 2023-03-30 paper/manuscript.tex
work on discussion

@@
 \hypersetup{
-  pdftitle={Correlates of replicability: evidence from student replication projects},
+  pdftitle={Eleven years of student replication projects provide evidence on the correlates of replicability in psychology},
   pdflang={en},
@@
 
-\title{Correlates of replicability: evidence from student replication projects}
+\title{Eleven years of student replication projects provide evidence on the correlates of replicability in psychology}
 
@@
 \item
-  BETTER title
-\item
   BETTER abstract
-\item
-  need to do supplement with the stuff we preregistered (sensitivity analysis, all models) -- waiting on finalized stats predictors
 \item
@@
   ** verify code for ES ** with someone
+\item
+  redo intro
+\item
+  redo results
+\item
+  redo discussion
+\item
+  fill in todos
 \end{itemize}
 
-\hypertarget{citation-slush-pile}{%
-\section{Citation slush pile}\label{citation-slush-pile}}
+\hypertarget{text-slush-pile}{%
+\section{Text slush pile}\label{text-slush-pile}}
+
+{[}who knows where this paragraph should go{]} Replications are one way of approximating whether an effect in the target paper is true, and how likely results are to replicate in some sort of platonic ideal world.
+There is no one answer here; replication projects measure something else that could be treated as an approximation.
+However, what a replication is really measuring is how likely it to get that effect given some conditions.
+Which the right conditions are is a potential point of contention (see discussion around closeness and sample size, power etc).
+Here, we are explicit in what sample of replicators and replication conditions were are sampling, and thus what we can generalize to.
+We are estimating how likely replication is when done online by a graduate student, under constraints that are typical for graduate students (limited time, limited budget).
+As much of scientific process is in fact performed by graduate students, we think this in itself is an interesting question.
+
+We do not interpret our results as saying that all non-replications were false positives (presumably some are replicable under other circumstances and others are not).
+Some of the factors we look at are more easily interpreted as being about the original study than others.
+We do not assign causal explanation to the predictors because there are multiple plausible interpretations: they could be correlates of QRPs in the original, they could be correlates of harder-to-detect or more fragile effects, they could be correlates of less-close replications, they could even be correlates of another stronger predictor.
+
+{[} there is controversy here, but to even discuss it, we need empirics{]} Even those who argue that replication is not so essential still rely on data from replications to make their cases that replication rates are not as low as they seem and that these replication rates are acceptable.
+Lewandowsky \& Oberauer (\protect\hyperlink{ref-lewandowsky2020}{2020})
+
+circle back to the idea that student replications (either as class or before extension into their own work) would be valuable
+\# Citation slush pile
 
@@
 
+Anderson, C., Bahnik, S., Barnett-Cowan, M., Bosco, F., Chandler, J., Chartier, C., \& otherss.
+(2016).
+Response to comment on ``estimating the reproducibility of psychological science.'' Science, 351(6277), 1037--1037.
+
+Gilbert, D. T., King, G., Pettigrew, S., \& Wilson, T. D. (2016). Comment on ``estimating the reproducibility of psychological science.'' Science, 351(6277), 1037--1037.
+
+Schmidt, S. (2009). Shall we really do it again? The powerful concept of replication is neglected in the social sciences. Review of General Psychology, 13, 90--100.
+
+Simonsohn, U. (2015). Small telescopes: Detectability and the evaluation of replication results. Psychol. Sci., 26(5), 559--569.
+
+Gelman, A. (2018). Don't characterize replications as successes or failures. Behavioral and Brain Sciences, 41.
+
+Mathur, M. B., \& VanderWeele, T. J. (2020a). New statistical metrics for multisite replication projects. J. R. Stat. Soc. Ser. A Stat. Soc., 183(3), 1145--1166.
+
+pedagogy for replication in intro: frank \& saxe, hawkins et al., quintana nature paper, scarcity PNAS pedagogy paper,
+
+Collaborative replications and education project (CREP)
+JE Grahe, MJ Brandt, H IJzerman, N Legate, J Wagge, YJ Weisberg, BJ Wiggins, Retrieved from osf. io/wfc6u, 2016 - Cited by 29
+
+\url{https://psycnet.apa.org/record/2022-15361-001}
+\url{https://journals.sagepub.com/doi/pdf/10.1177/1475725719868149}
+\url{https://content.iospress.com/articles/education-for-information/efi190308}
+
+\url{https://psycnet.apa.org/fulltext/2018-11647-005.html}
+
 \hypertarget{introduction}{%
 \section{introduction}\label{introduction}}
+
+replication is important (but not everything) - good starting place
+* prereq of theory building that the results of interest ``can be observed consistently''
+* but not everything (can still have other problems)
+
+replication rates are low in psychology (see studies)
+
+big open question: why
+
+experimental and correlational approaches to answering it
+
+experimental is hard - protzko, ML5 etc. but they are expensive and you can't do them for many research questions
+
+correlational has been pursued extensively, but is overfit to small data (prediction markets / ML models / regression of all types)
+
+our contribution: provide more data!
+using pedagogical replications, which are good because they're p(build on)
+slightly different estimand but maybe a better one?
 
@@
 
+one strategy for the pedagogical bit at end of intro: stress ``this is what people want to do, that is, pick up a project that they care about (not a random sample of the literature) and see if they can `get it to work'\,'' - and ``subjective replication success is our primary measure for the same reason\ldots.''
+
+can even cite the ``science is not a signal detection problem'' paper on not randomly sampling from the literature.
+
+Prior approaches to replicability have focused on a potentially problematic estimand: the probability of a finding in the literature being somehow truly replicable.
+Critics have pointed out that ``true'' replicability may not be possible to estimate outside of a specific sample (van bavel etc.) or even time period (ramscar).
+
+Further, the methods for estimating this quantity have been theoretically problematic.
+Sampling schemes for prior work typically does not reflect a random sample from the literature -- and even if they did, arguably a literature will succeed if useful discoveries come out of it, not if random findings are true (``Science is not signal detection'' ref).
+
+In contrast, we have pursued a different estimand: the probability that a researcher, on selecting a finding of interest from the literature, can successfully achieve a result satisfactorily close enough to the original that they feel that they can build on it in their own work, with all the necessary compromises to the methods and sample of the original that may be required by the constraints of the situation.
+SPELL OUT SAMPLING DIFFERENCE AND SUCCESS DIFFERENCE.
+
+We estimate this quantity in the context of a particular pedagogical situation: that of a graduate student entering a doctoral program in psychology\ldots{}
+
 Prior literature, such as Frank \& Saxe (\protect\hyperlink{ref-frank2012}{2012}) and Hawkins et al.
@@
         \node[mynode, join, on chain=1, fill=good] (n6)
-        {\textbf{131} pairs with ES};
+        {\textbf{136} pairs with ES};
         \node[mynode, join, on chain=1, fill=good] (n7)
-        {\textbf{107} pairs with SMD};
+        {\textbf{112} pairs with SMD};
 
@@
 
-As a complement, we also used two statistical measure of replication on the subset of the data where they were computable (134 cases, see Figure \ref{fig:prisma}).
+As a complement, we also used two statistical measure of replication on the subset of the data where they were computable (138 cases, see Figure \ref{fig:prisma}).
 We measured p-original, the p-value on the null hypothesis that the original and replication statistics are from the same distribution, as a continuous variable, and we also determined whether the replication statistic fell within the prediction interval of the original statistic (\protect\hyperlink{ref-errington2021}{Errington et al.
@@
 Across the 176 studies, the overall subjective replication rate was 49\%.
-46\% of the studies had replication outcomes within the prediction interval of the original outcome.
+45\% (N=FOOBAR) of the studies had replication outcomes within the prediction interval of the original outcome.
 The median p\_original value was 0.03.
@@
 \hypertarget{discussion}{%
-\section{discussion}\label{discussion}}
+\section{Discussion}\label{discussion}}
 
-blah blah we did a thing and it generally aligns with prior results.
-Overall replication rate is consistent with prior work, and we find cog greater than soc.
-However, by looking at a greater range of pr
+The replication rate in psychology is to the best estimates, somewhere around 50\%, which is quite low.
+Many reasons for this low replication rate have been hypothesized, but studying it either experimentally or correlationally requires doing a number of replication experiments, which can be a lot of work.
+Here we took advantage of 11 years of graduate student replication projects to look at correlational predictors of replication in a previously-unused dataset.
 
-{[}who knows where this paragraph should go{]} Replications are one way of approximating whether an effect in the target paper is true, and how likely results are to replicate in some sort of platonic ideal world.
-There is no one answer here; replication projects measure something else that could be treated as an approximation.
-However, what a replication is really measuring is how likely it to get that effect given some conditions.
-Which the right conditions are is a potential point of contention (see discussion around closeness and sample size, power etc).
-Here, we are explicit in what sample of replicators and replication conditions were are sampling, and thus what we can generalize to.
-We are estimating how likely replication is when done online by a graduate student, under constraints that are typical for graduate students (limited time, limited budget).
-As much of scientific process is in fact performed by graduate students, we think this in itself is an interesting question.
-It contrasts with questions like how likely something is to replicate when performed by an expert with a large budget (perhaps this is the right framing on Camerer) or when performed with extensive feedback from the original authors, etc.
+In line with previous replications, we found a FOOBAR replication rate, with some studies showing effect sizes similar to the original and others much smaller.
+Some individual correlates of replicability that stood out included within-subjects designs, work in the subfield of cognitive psychology, and the original and replication both using online samples.
+TODO other possible things
 
-We do not interpret our results as saying that all non-replications were false positives (presumably some are replicable under other circumstances and others are not).
-Some of the factors we look at are more easily interpreted as being about the original study than others.
-We do not assign causal explanation to the predictors because there are multiple plausible interpretations: they could be correlates of QRPs in the original, they could be correlates of harder-to-detect or more fragile effects, they could be correlates of less-close replications, they could even be correlates of another stronger predictor.
+Many of these correlates interrelate with one another, and we are still limited in our sample, so models with multiple predictors have a lot of uncertainty around the effects of each predictor.
 
-{[} there is controversy here, but to even discuss it, we need empirics{]} Even those who argue that replication is not so essential still rely on data from replications to make their cases that replication rates are not as low as they seem and that these replication rates are acceptable.
-Lewandowsky \& Oberauer (\protect\hyperlink{ref-lewandowsky2020}{2020})
+We are explicit in our goal of estimating how likely it is that a first-year graduate student, attempting to replicate a study of interest to them, gets replication results which are consistent enough with the original results that the student could build on the study in their own work.
+We can't estimate some platonic probability of truth for a study and neither can any replication study.
+Instead, we can estimate how likely studies are to get results of different levels of closeness in different circumstances.
+Much of the discussion around whether things should count as replication successes, or failures, or not replications at all is really about what the right thresholds are for closeness of results, and what the right circumstances are for a replication.
+Rather than try to find the one right answer to whether a direct replication was done in a certain right way, we think it's useful to explicitly label what the estimand really was: how likely it is to get the same results (under whatever metric) given circumstances like those used for the replication.
 
-circle back to the idea that student replications (either as class or before extension into their own work) would be valuable
+In our case, our estimand is about how well first-year graduate students will do at the replication, which takes into account the limited time, limited budget, and limited experience.
+We think this is an important estimand, as much of the work of psychology is done by trainees, in circumstances like these.
+Thus, if some studies have delicate results that require large samples and very exact methods to achieve, they may not replicate under normal resources.
+
+Other replication projects have other estimands: Camerer et al.
+(\protect\hyperlink{ref-camerer2018}{2018}) seems to ask something closer to how likely studies are to replicate when preformed by an expert with a large budget, and (\protect\hyperlink{ref-ML5}{\textbf{ML5?}}) TODOCITE asks how likely certain studies are to replicate when performed with extensive feedback from the original authors.
+
+We do not interpret our results as saying that all non-replications were false positives (presumably some would be replicable under different implementations and budgets and others would not).
+There are many possible reasons for the non-replications in this sample.
+In some cases, it seemed that the problem may have been with the replication: for instance, if there were too few participants, or if there were high levels of wrong answers on attention checks, or participants speeding through without attention checks.
+For these cases, there was a clear next attempt that a student could make if they wanted to get the replication to work.
+In other cases, there might have been a priori reasons to distrust the original study results, such as exclusion criteria that seemed to be post-hoc, or a three-way interaction effect on a small sample (CITE THAT THIS IS SKETCH).
+In yet other cases, it's unclear why the results failed to replicate.
+
+{[}somehow transition here{]} Pedagogy is important for open science.
+It's one thing to require or incentivize scientists to use open science practices and conduct replicable and reproducible research, but using the right tools and workflows to do open science is something that has to be learned.
+Teaching it in the classroom addresses the knowing how point at the beginning and shows students how to have open science practices integrated in to their science at the beginning, before other habits can ossify.
+Doing replications give students the motivation to care about open science, as they see how much easier it is to implement the study with open materials versus the study where they have to make guesses about the study instructions from the methods section.
+In presenting work with classmates, students see that there is variation in how well studies replicate, with some replicating very cleanly and others not at all.
+This sort of first hand experience teaches that not everything they read in the literature may just work if done again.
+
+Our results are limited by the number and quality of the studies we included. These studies are not necessarily representative of the literature as a whole. TODO what are the limitations we want?
+
+TODO quick wrap up
 

### 2023-04-04 paper/manuscript.Rmd
update cite list

@@
 circle back to the idea that student replications (either as class or before extension into their own work) would be valuable
+
 # Citation slush pile
@@
 
-Anderson, C., Bahnik, S., Barnett-Cowan, M., Bosco, F., Chandler, J., Chartier, C., & otherss.
-(2016).
-Response to comment on “estimating the reproducibility of psychological science.” Science, 351(6277), 1037–1037.
+@gilbert2016 @anderson2016 people argue a lot about how to interpret RPP
 
-Gilbert, D. T., King, G., Pettigrew, S., & Wilson, T. D. (2016). Comment on “estimating the reproducibility of psychological science.” Science, 351(6277), 1037–1037.
+@schmidt2009 early theory of replication as part of advancing knowledge
 
-Schmidt, S. (2009). Shall we really do it again? The powerful concept of replication is neglected in the social sciences. Review of General Psychology, 13, 90–100.
+@simonsohn2015 small telescopes
 
-Simonsohn, U. (2015). Small telescopes: Detectability and the evaluation of replication results. Psychol. Sci., 26(5), 559–569.
+@gelman2018 Don’t characterize replications as successes or failures.
 
-Gelman, A. (2018). Don’t characterize replications as successes or failures. Behavioral and Brain Sciences, 41.
+@mathur2020 other metrics of replicability
 
-Mathur, M. B., & VanderWeele, T. J. (2020a). New statistical metrics for multisite replication projects. J. R. Stat. Soc. Ser. A Stat. Soc., 183(3), 1145–1166.
+pedagogy for replication in intro:
 
-pedagogy for replication in intro: frank & saxe, hawkins et al., quintana nature paper, scarcity PNAS pedagogy paper,
+@frank2012
+@hawkins
 
-Collaborative replications and education project (CREP)
-JE Grahe, MJ Brandt, H IJzerman, N Legate, J Wagge, YJ Weisberg, BJ Wiggins, Retrieved from osf. io/wfc6u, 2016 - Cited by 29
+@odonnell2021 reps of some set of related things
 
-https://psycnet.apa.org/record/2022-15361-001
-https://journals.sagepub.com/doi/pdf/10.1177/1475725719868149
-https://content.iospress.com/articles/education-for-information/efi190308
+@wagge2019 get UGs to do replications for
 
-https://psycnet.apa.org/fulltext/2018-11647-005.html
+@quintana2021 do reps as honors thesis
+@pownall2021 sips 2021 on teaching openness
+@jekel2020 teach open science w/ replication 
+@jern2018 in one study didn't show critical thinking benefits for students to make them do replications
 
 # introduction
+Replicability is a desirable feature for any study that we build theory or future experiments off of.
+It's a pre-requisite for building theories that we have phenomena for these studies to explain, but results that cannot be observed consistently aren't results to build theories around.
+However, to be a load-bearing empirical result, a study needs to do much more than just replicate, it also needs to be interesting, have a believable theoretical interpretation, generalize appropriately, and have reliable constructs.
 
@@
 
+The replication rates in psychology are low, and 
 replication rates are low in psychology (see studies)
@@
 All models used a horseshoe prior in brms.
-All models will include random slopes for predictors nested within years of the class (year) to control for variation between cohorts of students.
+All models included random slopes for predictors nested within year the class occurred to control for variation between cohorts of students.
 We did not include any interaction terms in the models.
@@
 
-Results of more models in supplement. TODO
+Results from these models not reported in the main paper are reported in the supplement.
 
@@
 <div id="refs"></div>
-
-# (APPENDIX) Appendices {-}
-
-<!-- The above header does not appear in output. Not exactly sure why. -->
-
-# Appendix A {-}
-
-Some appendix text.
-
-# Appendix B {-}
-
-More appendix text.

### 2023-04-04 paper/manuscript.Rmd
more intro rambling

@@
 
+To understand how replicable the literature as a whole is, we need empirical data about replication attempts across a wide range of studies.
+Most replications are targeted replications of individual results of interest to the researcher, but these are not sampled randomly from the literature, are performed in inconsistent ways, and may be selectively published depending on the results.
+Thus, they are not ideal for estimating the overall replicability of the field.
+
+There have been a limited number of large-scale replication efforts, which sample studies from a discipline to estimate overall replicability.
+Due to the arduous process of replicating many studies, there have not been many large-scale replication efforts.
+Thus, all of the argumentation around predictors of replications and field-wide replication rates is fit to a small number of data points.
+Psychology is in the middle of heated debate over its research practices and the subject of many reform efforts.
+Many of these issues concern how trustworth the published literature is (or isn't), how it got to be this way, and what measures can be taken to improve the quality of findings for the future.
+These issues center around issues of reproducibility  and replicability.
+Concerns about replication rates have become a large point of discussion in psychology and other fields, with large scale replications spurring these discussions and providing the empirical data analyzed by all sides.
+
+  [idk, maybe worth framing that this was a big deal study when it came out]. TODO some discussion of how many papers have reanalysed this cutting the data different ways.
+
+ Many labs 5 was a re-replication attempt on 10 of RP:P and rescued 2/10 [@ebersole2020]. TODO look up details
+
 # Citation slush pile
@@
 some sort of modeling of replications @pawel2020
-
-@gilbert2016 @anderson2016 people argue a lot about how to interpret RPP
 
@@
 
-replication is important (but not everything) - good starting place
- * prereq of theory building that the results of interest "can be observed consistently" 
- * but not everything (can still have other problems)
+The replication rates in psychology are low, with estimates of replicability of experimental findings hovering somewhere around 50%.
+A major concern is that published literature may not replicate as much as previously thought or as desired.
+This has been illustrated by prominent findings/theories not replicating at all (ego depletion/ TMT?
+CITATIONS).
+Some prominent non-replications and concerns about research practices that might impact replication rates led to a few large-scale replication projects, aiming to quantify replication rates across swaths of the literature.
 
-The replication rates in psychology are low, and 
-replication rates are low in psychology (see studies)
+We are aware of three large-scale replication efforts replicating experimental results in the existing psychology literature.
+RP:P sampled roughly 100 studies from top psychology journals in 2008 [@openscienceconsortium2015].
+They found an overall replication rate around 40%, which provided evidence to support growing concerns about the non-reliability of the literature.The ManyLabs series of studies have also done large-scale replications of effects from psychology.
+Due to their primary goal of investigating different forms of hetereogeneity, their sampling has been non-representive, focusing on short studies with only two conditions.
+Across Many labs 1-3 foo bar replicated [@klein2014; @klein2018; @ebersole2016].
+@camerer2018 replicated the 21 behaviors studies published in Nature and Science from 2010-2015 that did not require special populations or special equipment.
+They found a roughly 60% replication rate.
 
-big open question: why
+These replication studies, and similar ones in other fields, open up big questions about why the replication rates are so low.
+There are many different theories both about causes and motivations for non-replications (relating to the incentives and research practices of science) and about what studies are most affected by these.
+There have been both experimental and correlational approaches to understanding the replication rates.
 
-experimental and correlational approaches to answering it
+A couple studies have attempted to intervene on the low replication rate, but seeing if certain factors can affect whether studies replicate.
+For instance, @protzko was a prospective replication study, showing that with a slew of best practices and large samples size (TODO look up details), the replications of FOOBAR novel whatevers had similar effect sizes to the original.
+Many Labs 5 examined how adding expert advice to a replication process might intervene to improve the replicate rate, and found that it mostly didn't, at least on the 10 studies they looked at TODO CITE.
+These types of experiments are valuable, but they aren't very scalable because they are expensive and some potential influences on non-replication are not experimentally manipulable.
+Instead, many studies have pursued correlational results about what predicts replication success, whether via regression models, prediction markets and elicitations, or machine learning techniques.
+However, all of these approaches depend on data from replications.
+While many replications have been conducted, most were not randomly sampled and are not pooled together, so these studies instead rely on the small number of data points, pulling heavily from RP:P in particular.
+The RP:P dataset was itself much discussed and reanalyzed [@etz2016;@gilbert2016;@patil2016;@anderson2016].
 
-experimental is hard - protzko, ML5 etc. but they are expensive and you can’t do them for many research questions
-
-correlational has been pursued extensively, but is overfit to small data (prediction markets / ML models / regression of all types)
+Our contribution to this literature is to provide a collection of 176 replication projects, done by students for a class.
+This is a sizeable number of projects, compared to the existing amount of data.
 
@@
 slightly different estimand but maybe a better one?
-
-Psychology is in the middle of heated debate over its research practices and the subject of many reform efforts.
-Many of these issues concern how trustworth the published literature is (or isn't), how it got to be this way, and what measures can be taken to improve the quality of findings for the future.
-These issues center around issues of reproducibility  and replicability.
-Concerns about replication rates have become a large point of discussion in psychology and other fields, with large scale replications spurring these discussions and providing the empirical data analyzed by all sides.
-
- A major concern is that published literature may not replicate as much as previously thought or as desired.
-This has been illustrated by prominent findings/theories not replicating at all (ego depletion/ TMT?).
-To understand how replicable the literature as a whole is, we need empirical data about replication attempts across a wide range of studies.
-Most replications are targeted replications of individual results of interest to the researcher, but these are not sampled randomly from the literature, are performed in inconsistent ways, and may be selectively published depending on the results.
-Thus, they are not ideal for estimating the overall replicability of the field.
-
-There have been a limited number of large-scale replication efforts, which sample studies from a discipline to estimate overall replicability.
-Due to the arduous process of replicating many studies, there have not been many large-scale replication efforts.
-Thus, all of the argumentation around predictors of replications and field-wide replication rates is fit to a small number of data points.
-
-## prior literature
-We are aware of three large-scale replication efforts replicating experimental results in the existing psychology literature.
-RP:P sampled roughly 100 studies from top psychology journals in 2008 [@openscienceconsortium2015].
-They found an overall replication rate around 40%, which provided evidence to support growing concerns about the non-reliability of the literature.
-The RP:P dataset was itself much discussed and reanalyzed [@etz2016;@gilbert2016;@patil2016] [idk, maybe worth framing that this was a big deal study when it came out].
-TODO some discussion of how many papers have reanalysed this cutting the data different ways.
-
-The ManyLabs series of studies have also done large-scale replications of effects from psychology.
-Due to their primary goal of investigating different forms of hetereogeneity, their sampling has been non-representive, focusing on short studies with only two conditions.
-Across Many labs 1-3 foo bar replicated [@klein2014; @klein2018; @ebersole2016].
-Many labs 5 was a re-replication attempt on 10 of RP:P and rescued 2/10 [@ebersole2020].
-TODO look up details
-
-@camerer2018 replicated the 21 behaviors studies published in Nature and Science from 2010-2015 that did not require special populations or special equipment.
-They found a roughly 60% replication rate.
 
@@
 
-can even cite the “science is not a signal detection problem” paper on not randomly sampling from the literature.
-
 Prior approaches to replicability have focused on a potentially problematic estimand: the probability of a finding in the literature being somehow truly replicable.
-Critics have pointed out that "true" replicability may not be possible to estimate outside of a specific sample (van bavel etc.) or even time period (ramscar).
+Critics have pointed out that "true" replicability may not be possible to estimate outside of a specific sample (CITE van bavel etc.) or even time period (CITE ramscar).
 
@@
 In contrast, we have pursued a different estimand: the probability that a researcher, on selecting a finding of interest from the literature, can successfully achieve a result satisfactorily close enough to the original that they feel that they can build on it in their own work, with all the necessary compromises to the methods and sample of the original that may be required by the constraints of the situation.
+
+There's different approaches one could take to sampling, we take the versimilitude approach.
+Our sample is not a random sample of the literature, or of a given journal, or some weighting, but it does represent studies that people are interested in replicating.
+
+Quantifying when an effect is a replication is hard, and many statistical metrics have been proposed, often with tradeoffs (TODO citations).
+We instead focus on a subjective score representing a more functionally oriented outcome: studies replicate if the results match the original enough that researchers would feel comfortable building on the study.
+This matches the motivation for many replications (often in replicate and extend paradigms).
 SPELL OUT SAMPLING DIFFERENCE AND SUCCESS DIFFERENCE.
+
+There's a "can I trust this finding" question, but a key part of it is, "if I did this, would I get the same pattern of results" -- and that's what we're measuring.
 

### 2023-04-04 paper/manuscript.tex
more intro rambling

@@
 circle back to the idea that student replications (either as class or before extension into their own work) would be valuable
-\# Citation slush pile
+
+\hypertarget{citation-slush-pile}{%
+\section{Citation slush pile}\label{citation-slush-pile}}
 
@@
 
-Anderson, C., Bahnik, S., Barnett-Cowan, M., Bosco, F., Chandler, J., Chartier, C., \& otherss.
-(2016).
-Response to comment on ``estimating the reproducibility of psychological science.'' Science, 351(6277), 1037--1037.
+Gilbert et al. (\protect\hyperlink{ref-gilbert2016}{2016}) Anderson et al. (\protect\hyperlink{ref-anderson2016}{2016}) people argue a lot about how to interpret RPP
 
-Gilbert, D. T., King, G., Pettigrew, S., \& Wilson, T. D. (2016). Comment on ``estimating the reproducibility of psychological science.'' Science, 351(6277), 1037--1037.
+Schmidt (\protect\hyperlink{ref-schmidt2009}{2009}) early theory of replication as part of advancing knowledge
 
-Schmidt, S. (2009). Shall we really do it again? The powerful concept of replication is neglected in the social sciences. Review of General Psychology, 13, 90--100.
+Simonsohn (\protect\hyperlink{ref-simonsohn2015}{2015}) small telescopes
 
-Simonsohn, U. (2015). Small telescopes: Detectability and the evaluation of replication results. Psychol. Sci., 26(5), 559--569.
+Gelman (\protect\hyperlink{ref-gelman2018}{2018/ed}) Don't characterize replications as successes or failures.
 
-Gelman, A. (2018). Don't characterize replications as successes or failures. Behavioral and Brain Sciences, 41.
+Mathur \& VanderWeele (\protect\hyperlink{ref-mathur2020}{2020}) other metrics of replicability
 
-Mathur, M. B., \& VanderWeele, T. J. (2020a). New statistical metrics for multisite replication projects. J. R. Stat. Soc. Ser. A Stat. Soc., 183(3), 1145--1166.
+pedagogy for replication in intro:
 
-pedagogy for replication in intro: frank \& saxe, hawkins et al., quintana nature paper, scarcity PNAS pedagogy paper,
+Frank \& Saxe (\protect\hyperlink{ref-frank2012}{2012})
+Hawkins et al. (\protect\hyperlink{ref-hawkins}{n.d.})
 
-Collaborative replications and education project (CREP)
-JE Grahe, MJ Brandt, H IJzerman, N Legate, J Wagge, YJ Weisberg, BJ Wiggins, Retrieved from osf. io/wfc6u, 2016 - Cited by 29
+O'Donnell et al. (\protect\hyperlink{ref-odonnell2021}{2021}) reps of some set of related things
 
-\url{https://psycnet.apa.org/record/2022-15361-001}
-\url{https://journals.sagepub.com/doi/pdf/10.1177/1475725719868149}
-\url{https://content.iospress.com/articles/education-for-information/efi190308}
+Wagge et al. (\protect\hyperlink{ref-wagge2019}{2019}) get UGs to do replications for
 
-\url{https://psycnet.apa.org/fulltext/2018-11647-005.html}
+Quintana (\protect\hyperlink{ref-quintana2021}{2021}) do reps as honors thesis
+Pownall et al. (\protect\hyperlink{ref-pownall2021}{2021}) sips 2021 on teaching openness
+Jekel et al. (\protect\hyperlink{ref-jekel2020}{2020}) teach open science w/ replication
+Jern (\protect\hyperlink{ref-jern2018}{2018}) in one study didn't show critical thinking benefits for students to make them do replications
 
@@
 \section{introduction}\label{introduction}}
+
+Replicability is a desirable feature for any study that we build theory or future experiments off of.
+It's a pre-requisite for building theories that we have phenomena for these studies to explain, but results that cannot be observed consistently aren't results to build theories around.
+However, to be a load-bearing empirical result, a study needs to do much more than just replicate, it also needs to be interesting, have a believable theoretical interpretation, generalize appropriately, and have reliable constructs.
 
@@
 
+The replication rates in psychology are low, and
 replication rates are low in psychology (see studies)
@@
 doi:\href{https://doi.org/10.1371/journal.pone.0225826}{10.1371/journal.pone.0225826}
+
+\leavevmode\vadjust pre{\hypertarget{ref-anderson2016}{}}%
+Anderson CJ, Bahník Š, Barnett-Cowan M, Bosco FA, Chandler J, Chartier CR, Cheung F, Christopherson CD, Cordes A, Cremata EJ, Della Penna N, Estel V, Fedor A, Fitneva SA, Frank MC, Grange JA, Hartshorne JK, Hasselman F, Henninger F, Hulst M van der, Jonas KJ, Lai CK, Levitan CA, Miller JK, Moore KS, Meixner JM, Munafò MR, Neijenhuijs KI, Nilsonne G, Nosek BA, Plessow F, Prenoveau JM, Ricker AA, Schmidt K, Spies JR, Stieger S, Strohminger N, Sullivan GB, Aert RCM van, Assen MALM van, Vanpaemel W, Vianello M, Voracek M, Zuni K (2016) Response to {Comment} on {``{Estimating} the reproducibility of psychological science.''} \emph{Science} \textbf{351}:1037--1037.
+doi:\href{https://doi.org/10.1126/science.aad9163}{10.1126/science.aad9163}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-gelman2018}{}}%
+Gelman A (2018/ed) Don't characterize replications as successes or failures. \emph{Behav Brain Sci} \textbf{41}:e128. doi:\href{https://doi.org/10.1017/S0140525X18000638}{10.1017/S0140525X18000638}
+
 \leavevmode\vadjust pre{\hypertarget{ref-gilbert2016}{}}%
@@
 doi:\href{https://doi.org/10.31234/osf.io/egw9d}{10.31234/osf.io/egw9d}
+
+\leavevmode\vadjust pre{\hypertarget{ref-jekel2020}{}}%
+Jekel M, Fiedler S, Allstadt Torras R, Mischkowski D, Dorrough AR, Glöckner A (2020) How to {Teach Open Science Principles} in the {Undergraduate Curriculum}---{The Hagen Cumulative Science Project}.
+\emph{Psychol Learn Teach} \textbf{19}:91--106.
+doi:\href{https://doi.org/10.1177/1475725719868149}{10.1177/1475725719868149}
+
+\leavevmode\vadjust pre{\hypertarget{ref-jern2018}{}}%
+Jern A (2018) A preliminary study of the educational benefits of conducting replications in the classroom.
+\emph{Scholarsh Teach Learn Psychol} \textbf{4}:64--68.
+doi:\href{https://doi.org/10.1037/stl0000104}{10.1037/stl0000104}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-mathur2020}{}}%
+Mathur MB, VanderWeele TJ (2020) New statistical metrics for multisite replication projects.
+\emph{J R Stat Soc Ser A Stat Soc} \textbf{183}:1145--1166.
+doi:\href{https://doi.org/10.1111/rssa.12572}{10.1111/rssa.12572}
+
 \leavevmode\vadjust pre{\hypertarget{ref-nosek2020}{}}%
@@
 doi:\href{https://doi.org/10.1038/d41586-020-02142-6}{10.1038/d41586-020-02142-6}
+
+\leavevmode\vadjust pre{\hypertarget{ref-odonnell2021}{}}%
+O'Donnell M, Dev AS, Antonoplis S, Baum SM, Benedetti AH, Brown ND, Carrillo B, Choi AL, Connor P, Donnelly K, Ellwood-Lowe ME, Foushee R, Jansen R, Jarvis SN, Lundell-Creagh R, Ocampo JM, Okafor GN, Azad ZR, Rosenblum M, Schatz D, Stein DH, Wang Y, Moore DA, Nelson LD (2021) Empirical audit and review and an assessment of evidentiary value in research on the psychological consequences of scarcity.
+\emph{Proc Natl Acad Sci USA} \textbf{118}:e2103313118.
+doi:\href{https://doi.org/10.1073/pnas.2103313118}{10.1073/pnas.2103313118}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-pownall2021}{}}%
+Pownall M, Azevedo F, Aldoh A, Elsherif M, Vasilev M, Pennington CR, Robertson O, Tromp MV, Liu M, Makel MC, Tonge N, Moreau D, Horry R, Shaw J, Tzavella L, McGarrigle R, Talbot C, Parsons S (2021) Embedding open and reproducible science into teaching: {A} bank of lesson plans and resources.
+\emph{Scholarsh Teach Learn Psychol}:No Pagination Specified--No Pagination Specified.
+doi:\href{https://doi.org/10.1037/stl0000307}{10.1037/stl0000307}
+
+\leavevmode\vadjust pre{\hypertarget{ref-quintana2021}{}}%
+Quintana DS (2021) Replication studies for undergraduate theses to improve science and education.
+\emph{Nat Hum Behav} \textbf{5}:1117--1118.
+doi:\href{https://doi.org/10.1038/s41562-021-01192-8}{10.1038/s41562-021-01192-8}
+
+\leavevmode\vadjust pre{\hypertarget{ref-schmidt2009}{}}%
+Schmidt S (2009) Shall we {Really} do it {Again}?
+{The Powerful Concept} of {Replication} is {Neglected} in the {Social Sciences}.
+\emph{Rev Gen Psychol} \textbf{13}:90--100.
+doi:\href{https://doi.org/10.1037/a0015108}{10.1037/a0015108}
+
+\leavevmode\vadjust pre{\hypertarget{ref-simonsohn2015}{}}%
+Simonsohn U (2015) Small {Telescopes}: {Detectability} and the {Evaluation} of {Replication Results}.
+\emph{Psychol Sci} \textbf{26}:559--569.
+doi:\href{https://doi.org/10.1177/0956797614567341}{10.1177/0956797614567341}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wagge2019}{}}%
+Wagge JR, Brandt MJ, Lazarevic LB, Legate N, Christopherson C, Wiggins B, Grahe JE (2019) \href{https://www.frontiersin.org/articles/10.3389/fpsyg.2019.00247}{Publishing {Research With Undergraduate Students} via {Replication Work}: {The Collaborative Replications} and {Education Project}}.
+\emph{Front Psychol} \textbf{10}
+
 \end{CSLReferences}
 
-\hypertarget{appendix-appendices}{%
-\appendix}
-
-\hypertarget{appendix-a}{%
-\section*{Appendix A}\label{appendix-a}}
-\addcontentsline{toc}{section}{Appendix A}
-
-Some appendix text.
-
-\hypertarget{appendix-b}{%
-\section*{Appendix B}\label{appendix-b}}
-\addcontentsline{toc}{section}{Appendix B}
-
-More appendix text.
-
 \end{document}

### 2023-04-05 paper/manuscript.Rmd
trying to make an intro that makes sense

@@
 
+ as validity, interestingness, and generalizability, can also be important
+Cumulative science and theory-building rely on empirical results that Replicability is a desirable feature for any study that we build theory or future experiments off of.
+It's a pre-requisite for building theories that we have phenomena for these studies to explain, but results that cannot be observed consistently aren't results to build theories around.
+However, to be a load-bearing empirical result, a study needs to do much more than just replicate, it also needs to be interesting, have a believable theoretical interpretation, generalize appropriately, and have reliable constructs.
+
 # Citation slush pile
@@
 # introduction
-Replicability is a desirable feature for any study that we build theory or future experiments off of.
-It's a pre-requisite for building theories that we have phenomena for these studies to explain, but results that cannot be observed consistently aren't results to build theories around.
-However, to be a load-bearing empirical result, a study needs to do much more than just replicate, it also needs to be interesting, have a believable theoretical interpretation, generalize appropriately, and have reliable constructs.
+[wacky metaphor, maybe drop] When building a stone wall, it's important that the components be stones that will retain their shape and not clots of dirt and sand that might fall apart and bring the rest of the wall falling down.
+Building a cumulative body of scientific theories similarly requires that the empirical results, especially the more foundational empirical results, be sturdy.
+Results that cannot be observed consistently are like dirt clots, they don't hold their shape and thus are not a strong foundation for the theories and studies built on top of them.
+Replications and the theory of replicability can be thought of as a way of testing whether the empirical results are sturdy.
+Replicating is a necessary feature for load-bearing empirical results.
+We note that replicability is not the only desirable feature of a study, and that replicating does not mean that a study is valid, or generalizable, or interesting.
 
-The replication rates in psychology are low, with estimates of replicability of experimental findings hovering somewhere around 50%.
-A major concern is that published literature may not replicate as much as previously thought or as desired.
-This has been illustrated by prominent findings/theories not replicating at all (ego depletion/ TMT?
-CITATIONS).
-Some prominent non-replications and concerns about research practices that might impact replication rates led to a few large-scale replication projects, aiming to quantify replication rates across swaths of the literature.
+A major concern in psychology, as in other fields, is that the published literature may not replicate as well as had previously been assumed.
+This is illustrated both by a few prominent findings that turn out to not replicate at all (CITE ex ego depletion, TMT), and by large-scale replication projects such as RP:P which found a replication rate around 40% for a sample of the psychology literature [@openscienceconsortium2015].
+This low replication rates seems undesirable and seems to run counter to the idea of a cumulative science.
 
-We are aware of three large-scale replication efforts replicating experimental results in the existing psychology literature.
-RP:P sampled roughly 100 studies from top psychology journals in 2008 [@openscienceconsortium2015].
-They found an overall replication rate around 40%, which provided evidence to support growing concerns about the non-reliability of the literature.The ManyLabs series of studies have also done large-scale replications of effects from psychology.
-Due to their primary goal of investigating different forms of hetereogeneity, their sampling has been non-representive, focusing on short studies with only two conditions.
-Across Many labs 1-3 foo bar replicated [@klein2014; @klein2018; @ebersole2016].
-@camerer2018 replicated the 21 behaviors studies published in Nature and Science from 2010-2015 that did not require special populations or special equipment.
-They found a roughly 60% replication rate.
-
-These replication studies, and similar ones in other fields, open up big questions about why the replication rates are so low.
-There are many different theories both about causes and motivations for non-replications (relating to the incentives and research practices of science) and about what studies are most affected by these.
-There have been both experimental and correlational approaches to understanding the replication rates.
+A big open question is why the replication rates in psychology are so low.
+There are theoretical approaches modelling how questionable research practices (which many psychologists admit to) and a bias towards positive results would lead to a high rate of (non-replicable) false positives in the literature (CITE).
+There's some disconnect between these theoretically causal factors and empirical results about what causes or correlates with replicability.
 
 A couple studies have attempted to intervene on the low replication rate, but seeing if certain factors can affect whether studies replicate.
-For instance, @protzko was a prospective replication study, showing that with a slew of best practices and large samples size (TODO look up details), the replications of FOOBAR novel whatevers had similar effect sizes to the original.
-Many Labs 5 examined how adding expert advice to a replication process might intervene to improve the replicate rate, and found that it mostly didn't, at least on the 10 studies they looked at TODO CITE.
+For instance, across 16 studies, @protzko2020 showed that better methodological practices, such as transparency, large sample sizes, and confirmatory tests, led to replication rates  that matched theoretical expectations based on the effect sizes and sample sizes, and replication effect sizes comparable with the original.
+Many Labs 5 examined how adding expert advice to a replication process might intervene to improve the replicate rate, and found that it mostly didn't, at least on the 10 studies they looked at [@ebersole2020].
 These types of experiments are valuable, but they aren't very scalable because they are expensive and some potential influences on non-replication are not experimentally manipulable.
-Instead, many studies have pursued correlational results about what predicts replication success, whether via regression models, prediction markets and elicitations, or machine learning techniques.
+
+As an alternative, much of the work looking at predictors of replicability has been correlation: whether using regression models, prediction markets, or machine learning techniques to build predictions about what will replicate.
 However, all of these approaches depend on data from replications.
-While many replications have been conducted, most were not randomly sampled and are not pooled together, so these studies instead rely on the small number of data points, pulling heavily from RP:P in particular.
-The RP:P dataset was itself much discussed and reanalyzed [@etz2016;@gilbert2016;@patil2016;@anderson2016].
+While many replications have been conducted, most were not randomly sampled and are not pooled together, so these studies instead rely on the small number of data points from large-scale replication projects.
+The RP:P dataset itself is much discussed and reanalyzed [@etz2016;@gilbert2016;@patil2016;@anderson2016].
 
-Our contribution to this literature is to provide a collection of 176 replication projects, done by students for a class.
-This is a sizeable number of projects, compared to the existing amount of data.
+This reliance on the same small set of data is problematic, as much of what we think we know about replicability is overfit to this small sample.
+However, given the time-consuming nature of running a large number of replications, there is a limited amount of large-scale replication data to draw on.
+We are aware of three large-scale replication efforts replicating experimental results in the existing psychology literature.
+RP:P sampled roughly 100 studies from articles published in three top psychology journals in 2008 and found a overall replication rate of around 40% [@openscienceconsortium2015].
+The ManyLabs series of replications investigating heterogeneity has sampled target studies that are short and compare only two conditions, which is not representative of the psychology literature as a whole.
+Across Many Labs 1-3, 29 of 51 target effects (57%) were found to replicate [@klein2014; @klein2018; @ebersole2016].
+@camerer2018 found a roughly 60% replication rate when they replicated all 21 behaviors studies published in Nature and Science from 2010-2015 that did not require special populations or special equipment.
+Those are all the large-scale replication projects of experimental psychology results available at this time.
+These roughly 170 results are heavily represented in the work predicting what effects will replicate.
+
+Our main contribution is to add a collection of 176 student replication projects to the available pool. We use these studies to examine the correlates of replicability.
 

### 2023-04-05 paper/manuscript.tex
trying to make an intro that makes sense

@@
 
+To understand how replicable the literature as a whole is, we need empirical data about replication attempts across a wide range of studies.
+Most replications are targeted replications of individual results of interest to the researcher, but these are not sampled randomly from the literature, are performed in inconsistent ways, and may be selectively published depending on the results.
+Thus, they are not ideal for estimating the overall replicability of the field.
+
+There have been a limited number of large-scale replication efforts, which sample studies from a discipline to estimate overall replicability.
+Due to the arduous process of replicating many studies, there have not been many large-scale replication efforts.
+Thus, all of the argumentation around predictors of replications and field-wide replication rates is fit to a small number of data points.
+Psychology is in the middle of heated debate over its research practices and the subject of many reform efforts.
+Many of these issues concern how trustworth the published literature is (or isn't), how it got to be this way, and what measures can be taken to improve the quality of findings for the future.
+These issues center around issues of reproducibility and replicability.
+Concerns about replication rates have become a large point of discussion in psychology and other fields, with large scale replications spurring these discussions and providing the empirical data analyzed by all sides.
+
+{[}idk, maybe worth framing that this was a big deal study when it came out{]}. TODO some discussion of how many papers have reanalysed this cutting the data different ways.
+
+Many labs 5 was a re-replication attempt on 10 of RP:P and rescued 2/10 (\protect\hyperlink{ref-ebersole2020}{Ebersole et al. 2020}). TODO look up details
+
 \hypertarget{citation-slush-pile}{%
@@
 some sort of modeling of replications Pawel \& Held (\protect\hyperlink{ref-pawel2020}{2020})
-
-Gilbert et al. (\protect\hyperlink{ref-gilbert2016}{2016}) Anderson et al. (\protect\hyperlink{ref-anderson2016}{2016}) people argue a lot about how to interpret RPP
 
@@
 
-replication is important (but not everything) - good starting place
-* prereq of theory building that the results of interest ``can be observed consistently''
-* but not everything (can still have other problems)
-
-The replication rates in psychology are low, and
-replication rates are low in psychology (see studies)
-
-big open question: why
-
-experimental and correlational approaches to answering it
-
-experimental is hard - protzko, ML5 etc. but they are expensive and you can't do them for many research questions
-
-correlational has been pursued extensively, but is overfit to small data (prediction markets / ML models / regression of all types)
-
-our contribution: provide more data!
-using pedagogical replications, which are good because they're p(build on)
-slightly different estimand but maybe a better one?
-
-Psychology is in the middle of heated debate over its research practices and the subject of many reform efforts.
-Many of these issues concern how trustworth the published literature is (or isn't), how it got to be this way, and what measures can be taken to improve the quality of findings for the future.
-These issues center around issues of reproducibility and replicability.
-Concerns about replication rates have become a large point of discussion in psychology and other fields, with large scale replications spurring these discussions and providing the empirical data analyzed by all sides.
-
+The replication rates in psychology are low, with estimates of replicability of experimental findings hovering somewhere around 50\%.
 A major concern is that published literature may not replicate as much as previously thought or as desired.
-This has been illustrated by prominent findings/theories not replicating at all (ego depletion/ TMT?).
-To understand how replicable the literature as a whole is, we need empirical data about replication attempts across a wide range of studies.
-Most replications are targeted replications of individual results of interest to the researcher, but these are not sampled randomly from the literature, are performed in inconsistent ways, and may be selectively published depending on the results.
-Thus, they are not ideal for estimating the overall replicability of the field.
-
-There have been a limited number of large-scale replication efforts, which sample studies from a discipline to estimate overall replicability.
-Due to the arduous process of replicating many studies, there have not been many large-scale replication efforts.
-Thus, all of the argumentation around predictors of replications and field-wide replication rates is fit to a small number of data points.
-
-\hypertarget{prior-literature}{%
-\subsection{prior literature}\label{prior-literature}}
+This has been illustrated by prominent findings/theories not replicating at all (ego depletion/ TMT?
+CITATIONS).
+Some prominent non-replications and concerns about research practices that might impact replication rates led to a few large-scale replication projects, aiming to quantify replication rates across swaths of the literature.
 
@@
 RP:P sampled roughly 100 studies from top psychology journals in 2008 (\protect\hyperlink{ref-openscienceconsortium2015}{Consortium 2015}).
-They found an overall replication rate around 40\%, which provided evidence to support growing concerns about the non-reliability of the literature.
-The RP:P dataset was itself much discussed and reanalyzed (\protect\hyperlink{ref-etz2016}{Etz \& Vandekerckhove 2016}, \protect\hyperlink{ref-gilbert2016}{Gilbert et al.
-2016}, \protect\hyperlink{ref-patil2016}{Patil et al.
-2016}) {[}idk, maybe worth framing that this was a big deal study when it came out{]}.
-TODO some discussion of how many papers have reanalysed this cutting the data different ways.
-
-The ManyLabs series of studies have also done large-scale replications of effects from psychology.
+They found an overall replication rate around 40\%, which provided evidence to support growing concerns about the non-reliability of the literature.The ManyLabs series of studies have also done large-scale replications of effects from psychology.
 Due to their primary goal of investigating different forms of hetereogeneity, their sampling has been non-representive, focusing on short studies with only two conditions.
@@
 2018}).
-Many labs 5 was a re-replication attempt on 10 of RP:P and rescued 2/10 (\protect\hyperlink{ref-ebersole2020}{Ebersole et al.
-2020}).
-TODO look up details
-
 Camerer et al.
@@
 They found a roughly 60\% replication rate.
+
+These replication studies, and similar ones in other fields, open up big questions about why the replication rates are so low.
+There are many different theories both about causes and motivations for non-replications (relating to the incentives and research practices of science) and about what studies are most affected by these.
+There have been both experimental and correlational approaches to understanding the replication rates.
+
+A couple studies have attempted to intervene on the low replication rate, but seeing if certain factors can affect whether studies replicate.
+For instance, (\protect\hyperlink{ref-protzko}{\textbf{protzko?}}) was a prospective replication study, showing that with a slew of best practices and large samples size (TODO look up details), the replications of FOOBAR novel whatevers had similar effect sizes to the original.
+Many Labs 5 examined how adding expert advice to a replication process might intervene to improve the replicate rate, and found that it mostly didn't, at least on the 10 studies they looked at TODO CITE.
+These types of experiments are valuable, but they aren't very scalable because they are expensive and some potential influences on non-replication are not experimentally manipulable.
+Instead, many studies have pursued correlational results about what predicts replication success, whether via regression models, prediction markets and elicitations, or machine learning techniques.
+However, all of these approaches depend on data from replications.
+While many replications have been conducted, most were not randomly sampled and are not pooled together, so these studies instead rely on the small number of data points, pulling heavily from RP:P in particular.
+The RP:P dataset was itself much discussed and reanalyzed (\protect\hyperlink{ref-anderson2016}{Anderson et al.
+2016}, \protect\hyperlink{ref-etz2016}{Etz \& Vandekerckhove 2016}, \protect\hyperlink{ref-gilbert2016}{Gilbert et al.
+2016}, \protect\hyperlink{ref-patil2016}{Patil et al.
+2016}).
+
+Our contribution to this literature is to provide a collection of 176 replication projects, done by students for a class.
+This is a sizeable number of projects, compared to the existing amount of data.
+
+our contribution: provide more data!
+using pedagogical replications, which are good because they're p(build on)
+slightly different estimand but maybe a better one?
 
@@
 
-can even cite the ``science is not a signal detection problem'' paper on not randomly sampling from the literature.
-
 Prior approaches to replicability have focused on a potentially problematic estimand: the probability of a finding in the literature being somehow truly replicable.
-Critics have pointed out that ``true'' replicability may not be possible to estimate outside of a specific sample (van bavel etc.) or even time period (ramscar).
+Critics have pointed out that ``true'' replicability may not be possible to estimate outside of a specific sample (CITE van bavel etc.) or even time period (CITE ramscar).
 
@@
 In contrast, we have pursued a different estimand: the probability that a researcher, on selecting a finding of interest from the literature, can successfully achieve a result satisfactorily close enough to the original that they feel that they can build on it in their own work, with all the necessary compromises to the methods and sample of the original that may be required by the constraints of the situation.
+
+There's different approaches one could take to sampling, we take the versimilitude approach.
+Our sample is not a random sample of the literature, or of a given journal, or some weighting, but it does represent studies that people are interested in replicating.
+
+Quantifying when an effect is a replication is hard, and many statistical metrics have been proposed, often with tradeoffs (TODO citations).
+We instead focus on a subjective score representing a more functionally oriented outcome: studies replicate if the results match the original enough that researchers would feel comfortable building on the study.
+This matches the motivation for many replications (often in replicate and extend paradigms).
 SPELL OUT SAMPLING DIFFERENCE AND SUCCESS DIFFERENCE.
+
+There's a ``can I trust this finding'' question, but a key part of it is, ``if I did this, would I get the same pattern of results'' -- and that's what we're measuring.
 

### 2023-04-05 paper/manuscript.Rmd
more intro

@@
 
+<!--
 # TODO list
@@
 
+## predictors
+In addition to determining estimated overall replicaiton rates for fields and journals, there's also merit in knowing what features of experiments (and replication attempts) are predictive of replication success.
+Blah blah stakeholders and resources.
+Scientists may want to build their work on studies that are likely to replicate, so that they can replicate and build on work without wasting resources.
+Similarly investing in interventions may want to start with things that are more likely to replicate.
+There's some signal here, as people are able to predict replication success at above chance CITATIONS
+
+RP:P looked at how replication rates varied across subsamples of their studies [@openscienceconsortium2015].
+
+There are reasons to believe that experimental factors such as number of items or between and within subject designs may also be predictive (cite our old paper), and could pontentially be some of the reason for subfield differences.
+TODO maybe foreshadow that there are reasons to believe there are correlations!
+
+While many replications of individual studies are conducted, these may have been selected for non-representative reasons, such as a high prior on replicating (e.g.
+as a demonstration), or a low or uncertain prior (e.g.
+for a high-value study).
+When sampling is likely related to replicability, the studies are less good for estimating base rates and predictors of replicability in the literature as a whole.
+
+using pedagogical replications, which are good because they’re p(build on)
+slightly different estimand but maybe a better one?
+One key part of the question of whether a study is replicable or trustworthy is the idea of "if I did this, would I get the same pattern of results?".
+
+one strategy for the pedagogical bit at end of intro: stress “this is what people want to do, that is, pick up a project that they care about (not a random sample of the literature) and see if they can ‘get it to work’” - and “subjective replication success is our primary measure for the same reason….”
+
+Quantifying when an effect is a replication is hard, and many statistical metrics have been proposed, often with tradeoffs (TODO citations).
+We instead focus on a subjective score representing a more functionally oriented outcome: studies replicate if the results match the original enough that researchers would feel comfortable building on the study.
+This matches the motivation for many replications (often in replicate and extend paradigms).
+SPELL OUT SAMPLING DIFFERENCE AND SUCCESS DIFFERENCE.
+
+There's a "can I trust this finding" question, but a key part of it is, "if I did this, would I get the same pattern of results" -- and that's what we're measuring.
+
+We estimate this quantity in the context of a particular pedagogical situation: that of a graduate student entering a doctoral program in psychology...
+
+Prior literature, such as @frank2012 and @hawkins have advocated using research methods classes to conduct replications, both for the education and scientific value.
+
 # Citation slush pile
@@
 
-@wagge2019 get UGs to do replications for
-
-@quintana2021 do reps as honors thesis
 @pownall2021 sips 2021 on teaching openness
@@
 @jern2018 in one study didn't show critical thinking benefits for students to make them do replications
-
+-->
 # introduction
-[wacky metaphor, maybe drop] When building a stone wall, it's important that the components be stones that will retain their shape and not clots of dirt and sand that might fall apart and bring the rest of the wall falling down.
+When building a stone wall, it's important that the components be stones that will retain their shape and not clots of dirt and sand that might fall apart and bring the rest of the wall falling down.
 Building a cumulative body of scientific theories similarly requires that the empirical results, especially the more foundational empirical results, be sturdy.
@@
 The RP:P dataset itself is much discussed and reanalyzed [@etz2016;@gilbert2016;@patil2016;@anderson2016].
+These correlational approaches have established that people can predict what studies will replicate above chance [@hoogeveen2019;@dreber2015; @forsell2019;@camerer2018], but have not identified that many concrete predictors that differentiate replications from non-replications.
+In the RP:P sample, studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate.
 
@@
 
-Our main contribution is to add a collection of 176 student replication projects to the available pool. We use these studies to examine the correlates of replicability.
+The perceived need for more replications in tension with the lack of publishing incentives for doing replications led several to suggest that pedagogical replications could fill this gap.
+Doing replications is a way for students to learn to do experiments in a scaffolded way and leads to more useful results than what students could design from scratch on the same timescale [@quintana2021; @wagge2019;@frank2012; @hawkins].
+[TODO needs transition]
 
-our contribution: provide more data!
-using pedagogical replications, which are good because they’re p(build on)
-slightly different estimand but maybe a better one?
+Our main contribution is a new dataset of 176 replications of experimental studies from the social sciences, primarily psychology.
+These replications were conducted by students in graduate-level experimental methods class between 2011 and 2022 as individual course projects.
+This approximately doubles the set of experiments in the large-scale replication literature.
+We investigate predictors of replicability in this new dataset.
 
-## predictors
-In addition to determining estimated overall replicaiton rates for fields and journals, there's also merit in knowing what features of experiments (and replication attempts) are predictive of replication success.
-Blah blah stakeholders and resources.
-Scientists may want to build their work on studies that are likely to replicate, so that they can replicate and build on work without wasting resources.
-Similarly investing in interventions may want to start with things that are more likely to replicate.
-There's some signal here, as people are able to predict replication success at above chance CITATIONS [@hoogeveen2019;@dreber2015; @forsell2019;@camerer2018]
-
-RP:P looked at how replication rates varied across subsamples of their studies [@openscienceconsortium2015].
-They found that cognitive psychology studies replicated at higher, but still low rates (50% v 25%) compared to social psychology.
-They also found that larger effect sizes and smaller p-values of original studies were predictive of replicating.
-TODO do we talk about any other correlates.
-
-There are reasons to believe that experimental factors such as number of items or between and within subject designs may also be predictive (cite our old paper), and could pontentially be some of the reason for subfield differences.
-TODO maybe foreshadow that there are reasons to believe there are correlations!
-
-While many replications of individual studies are conducted, these may have been selected for non-representative reasons, such as a high prior on replicating (e.g.
-as a demonstration), or a low or uncertain prior (e.g.
-for a high-value study).
-When sampling is likely related to replicability, the studies are less good for estimating base rates and predictors of replicability in the literature as a whole.
-
-## current work
-
-one strategy for the pedagogical bit at end of intro: stress “this is what people want to do, that is, pick up a project that they care about (not a random sample of the literature) and see if they can ‘get it to work’” - and “subjective replication success is our primary measure for the same reason….”
-
-Prior approaches to replicability have focused on a potentially problematic estimand: the probability of a finding in the literature being somehow truly replicable.
+Prior approaches to replicability have focused on interpreting results in terms of a potentially problematic estimand: the probability of a finding in the literature being somehow truly replicable.
 Critics have pointed out that "true" replicability may not be possible to estimate outside of a specific sample (CITE van bavel etc.) or even time period (CITE ramscar).
@@
 Further, the methods for estimating this quantity have been theoretically problematic.
-Sampling schemes for prior work typically does not reflect a random sample from the literature -- and even if they did, arguably a literature will succeed if useful discoveries come out of it, not if random findings are true ("Science is not signal detection" ref).
+Sampling schemes for prior work typically do not reflect an entirely random sample from the literature; instead they sample from specific journals where results may be of more interest and adjust the sample for feasibility concerns.
+These are reasonable sampling choices, but they undermine the claim that the estimand is the level of "truth" in the literature as a whole.
+Sampling truely at random from the literature may not even be desirable, as  arguably a literature will succeed if useful discoveries come out of it, not if random findings are true (CITE "Science is not signal detection" ref).
+How much we care about whether a study is "trustworthy" is not uniformly distributed across the literature.
 
-In contrast, we have pursued a different estimand: the probability that a researcher, on selecting a finding of interest from the literature, can successfully achieve a result satisfactorily close enough to the original that they feel that they can build on it in their own work, with all the necessary compromises to the methods and sample of the original that may be required by the constraints of the situation.
+In contrast, we have explicitly pursued a different estimand: the probability that a researcher, on selecting a finding of interest from the literature, can successfully achieve a result satisfactorily close enough to the original that they can build on it in their own work, with all the necessary compromises to the methods and sample of the original that may be required by the constraints of the situation.
 
-There's different approaches one could take to sampling, we take the versimilitude approach.
-Our sample is not a random sample of the literature, or of a given journal, or some weighting, but it does represent studies that people are interested in replicating.
+The sampling for our replications is based on what studies students were interested in and wanted to replicate, with some constraints of feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable within their ability and budgetary constraints.
+Our primary criteria for replication success is a subjective measure of whether the study replicated for the same reason, that we believe this is usually what researchers care about: is it close enough that you think you're getting at the same effect and could confidently build on it.
+The quality of the replications also reflects this: unlike some prior work like @camerer2018, which explicitly aimed for high-powered replications, the power in these studies was limited by budgetary reasons in some cases, which is reflective of the types of resources often available to trainee scientists.
 
-Quantifying when an effect is a replication is hard, and many statistical metrics have been proposed, often with tradeoffs (TODO citations).
-We instead focus on a subjective score representing a more functionally oriented outcome: studies replicate if the results match the original enough that researchers would feel comfortable building on the study.
-This matches the motivation for many replications (often in replicate and extend paradigms).
-SPELL OUT SAMPLING DIFFERENCE AND SUCCESS DIFFERENCE.
-
-There's a "can I trust this finding" question, but a key part of it is, "if I did this, would I get the same pattern of results" -- and that's what we're measuring.
-
-We estimate this quantity in the context of a particular pedagogical situation: that of a graduate student entering a doctoral program in psychology...
-
-Prior literature, such as @frank2012 and @hawkins have advocated using research methods classes to conduct replications, both for the education and scientific value.
-
-Here we introduce a new dataset of 176 replications of experimental studies from the social sciences, primarily psychology.
-These replications were conducted by students in graduate-level experimental methods class between 2011 and 2022 as individual course projects.
-This approximately doubles the set of experiments in the large-scale replication literature.
-We investigate predictors of replicability in this new dataset.
+We think this is a valuable estimand because it's estimating what people actually care about: is this result of interest sturdy enough to support cumulative science?
 
@@
 
-TODO discuss more about why this one and what other measure we don't choose are
-
-We used a subjective rating of replication success as our primary outcome measure.
-The instruction team had coded a holistic measure of replication success for each project when they were turned in at the end of the course.
+Many different measures can be used to define replication success of an individual statistical result, and there is much discussion over what each measure represents and which make sense [@simonsohn2015; @gelman2018; @mathur2020].
+Because we operationalized replicability as whether a study could be built upon, we used a subjective rating of replication success as our primary outcome measure.
+This measure has the benefit that it was applicable across the diverse range of statistical measures and reporting practices present in the sample.
+It, unlike statistical measures of replication, could easily accommodate studies where there were multiple important outcome measures that together defined the pattern of interest.
+A holistic measure of replication success had been coded for each project when it was turned in at the end of the class.
 For reliability, VB independently code the replication success from the replication reports; discrepancies were resolved by discussion between MCF and VB (`r pluck(matching,2,1)/176*100 |> round()` % of cases).
-This measure was applicable across the range of statistical measures and reporting practices and accommodated studies where there were multiple important outcome measures.
 
@@
 We measured p-original, the p-value on the null hypothesis that the original and replication statistics are from the same distribution, as a continuous variable, and we also determined whether the replication statistic fell within the prediction interval of the original statistic [@errington2021].
+These both measure how similar the estimates from the two sets of data are.
 
@@
 However, there were strong correlations among these experimental features and between these experimental features and subfield.
+TODO actual numbers here!
 
@@
 
-Results from other models can be found in the supplement. TODO make this a true statement
+Results from other models can be found in the supplement.
 
@@
 Some individual correlates of replicability that stood out included within-subjects designs, work in the subfield of cognitive psychology, and the original and replication both using online samples.
-TODO other possible things
-
 Many of these correlates interrelate with one another, and we are still limited in our sample, so models with multiple predictors have a lot of uncertainty around the effects of each predictor.

### 2023-04-05 paper/manuscript.tex
more intro

--- 2023-04-04 paper/manuscript.tex
@@
 
-\hypertarget{todo-list}{%
-\section{TODO list}\label{todo-list}}
-
-\begin{itemize}
-\tightlist
-\item
-  BETTER abstract
-\item
-  many citations everywhere
-\item
-  long list of things to gesture at in intro
-\item
-  link to open stuffs
-\item
-  ** verify code for ES ** with someone
-\item
-  redo intro
-\item
-  redo results
-\item
-  redo discussion
-\item
-  fill in todos
-\end{itemize}
-
-\hypertarget{text-slush-pile}{%
-\section{Text slush pile}\label{text-slush-pile}}
-
-{[}who knows where this paragraph should go{]} Replications are one way of approximating whether an effect in the target paper is true, and how likely results are to replicate in some sort of platonic ideal world.
-There is no one answer here; replication projects measure something else that could be treated as an approximation.
-However, what a replication is really measuring is how likely it to get that effect given some conditions.
-Which the right conditions are is a potential point of contention (see discussion around closeness and sample size, power etc).
-Here, we are explicit in what sample of replicators and replication conditions were are sampling, and thus what we can generalize to.
-We are estimating how likely replication is when done online by a graduate student, under constraints that are typical for graduate students (limited time, limited budget).
-As much of scientific process is in fact performed by graduate students, we think this in itself is an interesting question.
-
-We do not interpret our results as saying that all non-replications were false positives (presumably some are replicable under other circumstances and others are not).
-Some of the factors we look at are more easily interpreted as being about the original study than others.
-We do not assign causal explanation to the predictors because there are multiple plausible interpretations: they could be correlates of QRPs in the original, they could be correlates of harder-to-detect or more fragile effects, they could be correlates of less-close replications, they could even be correlates of another stronger predictor.
-
-{[} there is controversy here, but to even discuss it, we need empirics{]} Even those who argue that replication is not so essential still rely on data from replications to make their cases that replication rates are not as low as they seem and that these replication rates are acceptable.
-Lewandowsky \& Oberauer (\protect\hyperlink{ref-lewandowsky2020}{2020})
-
-circle back to the idea that student replications (either as class or before extension into their own work) would be valuable
-
-\hypertarget{citation-slush-pile}{%
-\section{Citation slush pile}\label{citation-slush-pile}}
-
-predict w/ ML Altmejd et al. (\protect\hyperlink{ref-altmejd2019}{2019})
-
-econ also has replications and issues Camerer et al. (\protect\hyperlink{ref-camerer2016}{2016})
-
-moving goal posts around replication / interpreting results Nosek \& Errington (\protect\hyperlink{ref-nosek2020}{2020})
-
-some sort of modeling of replications Pawel \& Held (\protect\hyperlink{ref-pawel2020}{2020})
-
-Gilbert et al. (\protect\hyperlink{ref-gilbert2016}{2016}) Anderson et al. (\protect\hyperlink{ref-anderson2016}{2016}) people argue a lot about how to interpret RPP
-
-Schmidt (\protect\hyperlink{ref-schmidt2009}{2009}) early theory of replication as part of advancing knowledge
-
-Simonsohn (\protect\hyperlink{ref-simonsohn2015}{2015}) small telescopes
-
-Gelman (\protect\hyperlink{ref-gelman2018}{2018/ed}) Don't characterize replications as successes or failures.
-
-Mathur \& VanderWeele (\protect\hyperlink{ref-mathur2020}{2020}) other metrics of replicability
-
-pedagogy for replication in intro:
-
-Frank \& Saxe (\protect\hyperlink{ref-frank2012}{2012})
-Hawkins et al. (\protect\hyperlink{ref-hawkins}{n.d.})
-
-O'Donnell et al. (\protect\hyperlink{ref-odonnell2021}{2021}) reps of some set of related things
-
-Wagge et al. (\protect\hyperlink{ref-wagge2019}{2019}) get UGs to do replications for
-
-Quintana (\protect\hyperlink{ref-quintana2021}{2021}) do reps as honors thesis
-Pownall et al. (\protect\hyperlink{ref-pownall2021}{2021}) sips 2021 on teaching openness
-Jekel et al. (\protect\hyperlink{ref-jekel2020}{2020}) teach open science w/ replication
-Jern (\protect\hyperlink{ref-jern2018}{2018}) in one study didn't show critical thinking benefits for students to make them do replications
-
 \hypertarget{introduction}{%
@@
 
-Replicability is a desirable feature for any study that we build theory or future experiments off of.
-It's a pre-requisite for building theories that we have phenomena for these studies to explain, but results that cannot be observed consistently aren't results to build theories around.
-However, to be a load-bearing empirical result, a study needs to do much more than just replicate, it also needs to be interesting, have a believable theoretical interpretation, generalize appropriately, and have reliable constructs.
+When building a stone wall, it's important that the components be stones that will retain their shape and not clots of dirt and sand that might fall apart and bring the rest of the wall falling down.
+Building a cumulative body of scientific theories similarly requires that the empirical results, especially the more foundational empirical results, be sturdy.
+Results that cannot be observed consistently are like dirt clots, they don't hold their shape and thus are not a strong foundation for the theories and studies built on top of them.
+Replications and the theory of replicability can be thought of as a way of testing whether the empirical results are sturdy.
+Replicating is a necessary feature for load-bearing empirical results.
+We note that replicability is not the only desirable feature of a study, and that replicating does not mean that a study is valid, or generalizable, or interesting.
 
-replication is important (but not everything) - good starting place
-* prereq of theory building that the results of interest ``can be observed consistently''
-* but not everything (can still have other problems)
+A major concern in psychology, as in other fields, is that the published literature may not replicate as well as had previously been assumed.
+This is illustrated both by a few prominent findings that turn out to not replicate at all (CITE ex ego depletion, TMT), and by large-scale replication projects such as RP:P which found a replication rate around 40\% for a sample of the psychology literature (\protect\hyperlink{ref-openscienceconsortium2015}{Consortium 2015}).
+This low replication rates seems undesirable and seems to run counter to the idea of a cumulative science.
 
-The replication rates in psychology are low, and
-replication rates are low in psychology (see studies)
+A big open question is why the replication rates in psychology are so low.
+There are theoretical approaches modelling how questionable research practices (which many psychologists admit to) and a bias towards positive results would lead to a high rate of (non-replicable) false positives in the literature (CITE).
+There's some disconnect between these theoretically causal factors and empirical results about what causes or correlates with replicability.
 
-big open question: why
+A couple studies have attempted to intervene on the low replication rate, but seeing if certain factors can affect whether studies replicate.
+For instance, across 16 studies, Protzko et al.
+(\protect\hyperlink{ref-protzko2020}{2020}) showed that better methodological practices, such as transparency, large sample sizes, and confirmatory tests, led to replication rates that matched theoretical expectations based on the effect sizes and sample sizes, and replication effect sizes comparable with the original.
+Many Labs 5 examined how adding expert advice to a replication process might intervene to improve the replicate rate, and found that it mostly didn't, at least on the 10 studies they looked at (\protect\hyperlink{ref-ebersole2020}{Ebersole et al.
+2020}).
+These types of experiments are valuable, but they aren't very scalable because they are expensive and some potential influences on non-replication are not experimentally manipulable.
 
-experimental and correlational approaches to answering it
+As an alternative, much of the work looking at predictors of replicability has been correlation: whether using regression models, prediction markets, or machine learning techniques to build predictions about what will replicate.
+However, all of these approaches depend on data from replications.
+While many replications have been conducted, most were not randomly sampled and are not pooled together, so these studies instead rely on the small number of data points from large-scale replication projects.
+The RP:P dataset itself is much discussed and reanalyzed (\protect\hyperlink{ref-anderson2016}{Anderson et al.
+2016}, \protect\hyperlink{ref-etz2016}{Etz \& Vandekerckhove 2016}, \protect\hyperlink{ref-gilbert2016}{Gilbert et al.
+2016}, \protect\hyperlink{ref-patil2016}{Patil et al.
+2016}).
+These correlational approaches have established that people can predict what studies will replicate above chance (\protect\hyperlink{ref-dreber2015}{Dreber et al.
+2015}, \protect\hyperlink{ref-camerer2018}{Camerer et al.
+2018}, \protect\hyperlink{ref-forsell2019}{Forsell et al.
+2019}, \protect\hyperlink{ref-hoogeveen2019}{Hoogeveen et al.
+2019}), but have not identified that many concrete predictors that differentiate replications from non-replications.
+In the RP:P sample, studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate.
 
-experimental is hard - protzko, ML5 etc. but they are expensive and you can't do them for many research questions
-
-correlational has been pursued extensively, but is overfit to small data (prediction markets / ML models / regression of all types)
-
-our contribution: provide more data!
-using pedagogical replications, which are good because they're p(build on)
-slightly different estimand but maybe a better one?
-
-Psychology is in the middle of heated debate over its research practices and the subject of many reform efforts.
-Many of these issues concern how trustworth the published literature is (or isn't), how it got to be this way, and what measures can be taken to improve the quality of findings for the future.
-These issues center around issues of reproducibility and replicability.
-Concerns about replication rates have become a large point of discussion in psychology and other fields, with large scale replications spurring these discussions and providing the empirical data analyzed by all sides.
-
-A major concern is that published literature may not replicate as much as previously thought or as desired.
-This has been illustrated by prominent findings/theories not replicating at all (ego depletion/ TMT?).
-To understand how replicable the literature as a whole is, we need empirical data about replication attempts across a wide range of studies.
-Most replications are targeted replications of individual results of interest to the researcher, but these are not sampled randomly from the literature, are performed in inconsistent ways, and may be selectively published depending on the results.
-Thus, they are not ideal for estimating the overall replicability of the field.
-
-There have been a limited number of large-scale replication efforts, which sample studies from a discipline to estimate overall replicability.
-Due to the arduous process of replicating many studies, there have not been many large-scale replication efforts.
-Thus, all of the argumentation around predictors of replications and field-wide replication rates is fit to a small number of data points.
-
-\hypertarget{prior-literature}{%
-\subsection{prior literature}\label{prior-literature}}
-
+This reliance on the same small set of data is problematic, as much of what we think we know about replicability is overfit to this small sample.
+However, given the time-consuming nature of running a large number of replications, there is a limited amount of large-scale replication data to draw on.
 We are aware of three large-scale replication efforts replicating experimental results in the existing psychology literature.
-RP:P sampled roughly 100 studies from top psychology journals in 2008 (\protect\hyperlink{ref-openscienceconsortium2015}{Consortium 2015}).
-They found an overall replication rate around 40\%, which provided evidence to support growing concerns about the non-reliability of the literature.
-The RP:P dataset was itself much discussed and reanalyzed (\protect\hyperlink{ref-etz2016}{Etz \& Vandekerckhove 2016}, \protect\hyperlink{ref-gilbert2016}{Gilbert et al.
-2016}, \protect\hyperlink{ref-patil2016}{Patil et al.
-2016}) {[}idk, maybe worth framing that this was a big deal study when it came out{]}.
-TODO some discussion of how many papers have reanalysed this cutting the data different ways.
-
-The ManyLabs series of studies have also done large-scale replications of effects from psychology.
-Due to their primary goal of investigating different forms of hetereogeneity, their sampling has been non-representive, focusing on short studies with only two conditions.
-Across Many labs 1-3 foo bar replicated (\protect\hyperlink{ref-klein2014}{Klein et al.
+RP:P sampled roughly 100 studies from articles published in three top psychology journals in 2008 and found a overall replication rate of around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Consortium 2015}).
+The ManyLabs series of replications investigating heterogeneity has sampled target studies that are short and compare only two conditions, which is not representative of the psychology literature as a whole.
+Across Many Labs 1-3, 29 of 51 target effects (57\%) were found to replicate (\protect\hyperlink{ref-klein2014}{Klein et al.
 2014}, \protect\hyperlink{ref-ebersole2016}{Ebersole et al.
@@
 2018}).
-Many labs 5 was a re-replication attempt on 10 of RP:P and rescued 2/10 (\protect\hyperlink{ref-ebersole2020}{Ebersole et al.
-2020}).
-TODO look up details
+Camerer et al.
+(\protect\hyperlink{ref-camerer2018}{2018}) found a roughly 60\% replication rate when they replicated all 21 behaviors studies published in Nature and Science from 2010-2015 that did not require special populations or special equipment.
+Those are all the large-scale replication projects of experimental psychology results available at this time.
+These roughly 170 results are heavily represented in the work predicting what effects will replicate.
 
-Camerer et al.
-(\protect\hyperlink{ref-camerer2018}{2018}) replicated the 21 behaviors studies published in Nature and Science from 2010-2015 that did not require special populations or special equipment.
-They found a roughly 60\% replication rate.
+The perceived need for more replications in tension with the lack of publishing incentives for doing replications led several to suggest that pedagogical replications could fill this gap.
+Doing replications is a way for students to learn to do experiments in a scaffolded way and leads to more useful results than what students could design from scratch on the same timescale (\protect\hyperlink{ref-frank2012}{Frank \& Saxe 2012}, \protect\hyperlink{ref-wagge2019}{Wagge et al.
+2019}, \protect\hyperlink{ref-quintana2021}{Quintana 2021}, \protect\hyperlink{ref-hawkins}{Hawkins et al.
+n.d.}).
+{[}TODO needs transition{]}
 
-\hypertarget{predictors}{%
-\subsection{predictors}\label{predictors}}
-
-In addition to determining estimated overall replicaiton rates for fields and journals, there's also merit in knowing what features of experiments (and replication attempts) are predictive of replication success.
-Blah blah stakeholders and resources.
-Scientists may want to build their work on studies that are likely to replicate, so that they can replicate and build on work without wasting resources.
-Similarly investing in interventions may want to start with things that are more likely to replicate.
-There's some signal here, as people are able to predict replication success at above chance CITATIONS (\protect\hyperlink{ref-dreber2015}{Dreber et al.
-2015}, \protect\hyperlink{ref-camerer2018}{Camerer et al.
-2018}, \protect\hyperlink{ref-forsell2019}{Forsell et al.
-2019}, \protect\hyperlink{ref-hoogeveen2019}{Hoogeveen et al.
-2019})
-
-RP:P looked at how replication rates varied across subsamples of their studies (\protect\hyperlink{ref-openscienceconsortium2015}{Consortium 2015}).
-They found that cognitive psychology studies replicated at higher, but still low rates (50\% v 25\%) compared to social psychology.
-They also found that larger effect sizes and smaller p-values of original studies were predictive of replicating.
-TODO do we talk about any other correlates.
-
-There are reasons to believe that experimental factors such as number of items or between and within subject designs may also be predictive (cite our old paper), and could pontentially be some of the reason for subfield differences.
-TODO maybe foreshadow that there are reasons to believe there are correlations!
-
-While many replications of individual studies are conducted, these may have been selected for non-representative reasons, such as a high prior on replicating (e.g.~as a demonstration), or a low or uncertain prior (e.g.~for a high-value study).
-When sampling is likely related to replicability, the studies are less good for estimating base rates and predictors of replicability in the literature as a whole.
-
-\hypertarget{current-work}{%
-\subsection{current work}\label{current-work}}
-
-one strategy for the pedagogical bit at end of intro: stress ``this is what people want to do, that is, pick up a project that they care about (not a random sample of the literature) and see if they can `get it to work'\,'' - and ``subjective replication success is our primary measure for the same reason\ldots.''
-
-can even cite the ``science is not a signal detection problem'' paper on not randomly sampling from the literature.
-
-Prior approaches to replicability have focused on a potentially problematic estimand: the probability of a finding in the literature being somehow truly replicable.
-Critics have pointed out that ``true'' replicability may not be possible to estimate outside of a specific sample (van bavel etc.) or even time period (ramscar).
-
-Further, the methods for estimating this quantity have been theoretically problematic.
-Sampling schemes for prior work typically does not reflect a random sample from the literature -- and even if they did, arguably a literature will succeed if useful discoveries come out of it, not if random findings are true (``Science is not signal detection'' ref).
-
-In contrast, we have pursued a different estimand: the probability that a researcher, on selecting a finding of interest from the literature, can successfully achieve a result satisfactorily close enough to the original that they feel that they can build on it in their own work, with all the necessary compromises to the methods and sample of the original that may be required by the constraints of the situation.
-SPELL OUT SAMPLING DIFFERENCE AND SUCCESS DIFFERENCE.
-
-We estimate this quantity in the context of a particular pedagogical situation: that of a graduate student entering a doctoral program in psychology\ldots{}
-
-Prior literature, such as Frank \& Saxe (\protect\hyperlink{ref-frank2012}{2012}) and Hawkins et al.
-(\protect\hyperlink{ref-hawkins}{n.d.}) have advocated using research methods classes to conduct replications, both for the education and scientific value.
-
-Here we introduce a new dataset of 176 replications of experimental studies from the social sciences, primarily psychology.
+Our main contribution is a new dataset of 176 replications of experimental studies from the social sciences, primarily psychology.
 These replications were conducted by students in graduate-level experimental methods class between 2011 and 2022 as individual course projects.
@@
 We investigate predictors of replicability in this new dataset.
+
+Prior approaches to replicability have focused on interpreting results in terms of a potentially problematic estimand: the probability of a finding in the literature being somehow truly replicable.
+Critics have pointed out that ``true'' replicability may not be possible to estimate outside of a specific sample (CITE van bavel etc.) or even time period (CITE ramscar).
+
+Further, the methods for estimating this quantity have been theoretically problematic.
+Sampling schemes for prior work typically do not reflect an entirely random sample from the literature; instead they sample from specific journals where results may be of more interest and adjust the sample for feasibility concerns.
+These are reasonable sampling choices, but they undermine the claim that the estimand is the level of ``truth'' in the literature as a whole.
+Sampling truely at random from the literature may not even be desirable, as arguably a literature will succeed if useful discoveries come out of it, not if random findings are true (CITE ``Science is not signal detection'' ref).
+How much we care about whether a study is ``trustworthy'' is not uniformly distributed across the literature.
+
+In contrast, we have explicitly pursued a different estimand: the probability that a researcher, on selecting a finding of interest from the literature, can successfully achieve a result satisfactorily close enough to the original that they can build on it in their own work, with all the necessary compromises to the methods and sample of the original that may be required by the constraints of the situation.
+
+The sampling for our replications is based on what studies students were interested in and wanted to replicate, with some constraints of feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable within their ability and budgetary constraints.
+Our primary criteria for replication success is a subjective measure of whether the study replicated for the same reason, that we believe this is usually what researchers care about: is it close enough that you think you're getting at the same effect and could confidently build on it.
+The quality of the replications also reflects this: unlike some prior work like Camerer et al.
+(\protect\hyperlink{ref-camerer2018}{2018}), which explicitly aimed for high-powered replications, the power in these studies was limited by budgetary reasons in some cases, which is reflective of the types of resources often available to trainee scientists.
+
+We think this is a valuable estimand because it's estimating what people actually care about: is this result of interest sturdy enough to support cumulative science?
 
@@
 
-TODO discuss more about why this one and what other measure we don't choose are
-
-We used a subjective rating of replication success as our primary outcome measure.
-The instruction team had coded a holistic measure of replication success for each project when they were turned in at the end of the course.
+Many different measures can be used to define replication success of an individual statistical result, and there is much discussion over what each measure represents and which make sense (\protect\hyperlink{ref-simonsohn2015}{Simonsohn 2015}, \protect\hyperlink{ref-gelman2018}{Gelman 2018/ed}, \protect\hyperlink{ref-mathur2020}{Mathur \& VanderWeele 2020}).
+Because we operationalized replicability as whether a study could be built upon, we used a subjective rating of replication success as our primary outcome measure.
+This measure has the benefit that it was applicable across the diverse range of statistical measures and reporting practices present in the sample.
+It, unlike statistical measures of replication, could easily accommodate studies where there were multiple important outcome measures that together defined the pattern of interest.
+A holistic measure of replication success had been coded for each project when it was turned in at the end of the class.
 For reliability, VB independently code the replication success from the replication reports; discrepancies were resolved by discussion between MCF and VB (25.5681818 \% of cases).
-This measure was applicable across the range of statistical measures and reporting practices and accommodated studies where there were multiple important outcome measures.
 
@@
 2021}).
+These both measure how similar the estimates from the two sets of data are.
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-altmejd2019}{}}%
-Altmejd A, Dreber A, Forsell E, Huber J, Imai T, Johannesson M, Kirchler M, Nave G, Camerer C (2019) Predicting the replicability of social science lab experiments.
-\emph{PLOS ONE} \textbf{14}:e0225826.
-doi:\href{https://doi.org/10.1371/journal.pone.0225826}{10.1371/journal.pone.0225826}
-
 \leavevmode\vadjust pre{\hypertarget{ref-anderson2016}{}}%
@@
 doi:\href{https://doi.org/10.1126/science.aad9163}{10.1126/science.aad9163}
-
-\leavevmode\vadjust pre{\hypertarget{ref-camerer2016}{}}%
-Camerer CF, Dreber A, Forsell E, Ho T-H, Huber J, Johannesson M, Kirchler M, Almenberg J, Altmejd A, Chan T, Heikensten E, Holzmeister F, Imai T, Isaksson S, Nave G, Pfeiffer T, Razen M, Wu H (2016) Evaluating replicability of laboratory experiments in economics.
-\emph{Science} \textbf{351}:1433--1436.
-doi:\href{https://doi.org/10.1126/science.aaf0918}{10.1126/science.aaf0918}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-jekel2020}{}}%
-Jekel M, Fiedler S, Allstadt Torras R, Mischkowski D, Dorrough AR, Glöckner A (2020) How to {Teach Open Science Principles} in the {Undergraduate Curriculum}---{The Hagen Cumulative Science Project}.
-\emph{Psychol Learn Teach} \textbf{19}:91--106.
-doi:\href{https://doi.org/10.1177/1475725719868149}{10.1177/1475725719868149}
-
-\leavevmode\vadjust pre{\hypertarget{ref-jern2018}{}}%
-Jern A (2018) A preliminary study of the educational benefits of conducting replications in the classroom.
-\emph{Scholarsh Teach Learn Psychol} \textbf{4}:64--68.
-doi:\href{https://doi.org/10.1037/stl0000104}{10.1037/stl0000104}
-
 \leavevmode\vadjust pre{\hypertarget{ref-klein2014}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-lewandowsky2020}{}}%
-Lewandowsky S, Oberauer K (2020) Low replicability can support robust and efficient science.
-\emph{Nat Commun} \textbf{11}:1--12.
-doi:\href{https://doi.org/10.1038/s41467-019-14203-0}{10.1038/s41467-019-14203-0}
-
 \leavevmode\vadjust pre{\hypertarget{ref-mathur2020}{}}%
@@
 doi:\href{https://doi.org/10.1111/rssa.12572}{10.1111/rssa.12572}
-
-\leavevmode\vadjust pre{\hypertarget{ref-nosek2020}{}}%
-Nosek BA, Errington TM (2020) The best time to argue about what a replication means?
-{Before} you do it.
-\emph{Nature} \textbf{583}:518--520.
-doi:\href{https://doi.org/10.1038/d41586-020-02142-6}{10.1038/d41586-020-02142-6}
-
-\leavevmode\vadjust pre{\hypertarget{ref-odonnell2021}{}}%
-O'Donnell M, Dev AS, Antonoplis S, Baum SM, Benedetti AH, Brown ND, Carrillo B, Choi AL, Connor P, Donnelly K, Ellwood-Lowe ME, Foushee R, Jansen R, Jarvis SN, Lundell-Creagh R, Ocampo JM, Okafor GN, Azad ZR, Rosenblum M, Schatz D, Stein DH, Wang Y, Moore DA, Nelson LD (2021) Empirical audit and review and an assessment of evidentiary value in research on the psychological consequences of scarcity.
-\emph{Proc Natl Acad Sci USA} \textbf{118}:e2103313118.
-doi:\href{https://doi.org/10.1073/pnas.2103313118}{10.1073/pnas.2103313118}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-pawel2020}{}}%
-Pawel S, Held L (2020) Probabilistic forecasting of replication studies. \emph{PLOS ONE} \textbf{15}:e0231416. doi:\href{https://doi.org/10.1371/journal.pone.0231416}{10.1371/journal.pone.0231416}
-
-\leavevmode\vadjust pre{\hypertarget{ref-pownall2021}{}}%
-Pownall M, Azevedo F, Aldoh A, Elsherif M, Vasilev M, Pennington CR, Robertson O, Tromp MV, Liu M, Makel MC, Tonge N, Moreau D, Horry R, Shaw J, Tzavella L, McGarrigle R, Talbot C, Parsons S (2021) Embedding open and reproducible science into teaching: {A} bank of lesson plans and resources.
-\emph{Scholarsh Teach Learn Psychol}:No Pagination Specified--No Pagination Specified.
-doi:\href{https://doi.org/10.1037/stl0000307}{10.1037/stl0000307}
+\leavevmode\vadjust pre{\hypertarget{ref-protzko2020}{}}%
+Protzko J, Krosnick J, Nelson LD, Nosek BA, Axt J, Berent M, Buttrick N, DeBell M, Ebersole CR, Lundmark S, MacInnis B, O'Donnell M, Perfecto H, Pustejovsky JE, Roeder SS, Walleczek J, Schooler J (2020) High {Replicability} of {Newly-Discovered Social-behavioral Findings} is {Achievable}.
+preprint.
+{PsyArXiv}.
+Available from: \url{https://osf.io/n2a9x} {[}Last accessed 5 April 2023{]}.
+doi:\href{https://doi.org/10.31234/osf.io/n2a9x}{10.31234/osf.io/n2a9x}
 
@@
 doi:\href{https://doi.org/10.1038/s41562-021-01192-8}{10.1038/s41562-021-01192-8}
-
-\leavevmode\vadjust pre{\hypertarget{ref-schmidt2009}{}}%
-Schmidt S (2009) Shall we {Really} do it {Again}?
-{The Powerful Concept} of {Replication} is {Neglected} in the {Social Sciences}.
-\emph{Rev Gen Psychol} \textbf{13}:90--100.
-doi:\href{https://doi.org/10.1037/a0015108}{10.1037/a0015108}
 

### 2023-04-05 paper/manuscript.Rmd
fix some citations and todos

@@
 A major concern in psychology, as in other fields, is that the published literature may not replicate as well as had previously been assumed.
-This is illustrated both by a few prominent findings that turn out to not replicate at all (CITE ex ego depletion, TMT), and by large-scale replication projects such as RP:P which found a replication rate around 40% for a sample of the psychology literature [@openscienceconsortium2015].
+This is illustrated both by a few prominent findings that turn out to not replicate at all [ex.
+terror management theory; @klein2022], and by large-scale replication projects such as RP:P which found a replication rate around 40% for a sample of the psychology literature [@openscienceconsortium2015].
 This low replication rates seems undesirable and seems to run counter to the idea of a cumulative science.
@@
 Prior approaches to replicability have focused on interpreting results in terms of a potentially problematic estimand: the probability of a finding in the literature being somehow truly replicable.
-Critics have pointed out that "true" replicability may not be possible to estimate outside of a specific sample (CITE van bavel etc.) or even time period (CITE ramscar).
+Critics have pointed out that "true" replicability may not be possible to estimate outside of a specific sample [@vanbavel2016] or even time period [@ramscar].
 
@@
 These are reasonable sampling choices, but they undermine the claim that the estimand is the level of "truth" in the literature as a whole.
-Sampling truely at random from the literature may not even be desirable, as  arguably a literature will succeed if useful discoveries come out of it, not if random findings are true (CITE "Science is not signal detection" ref).
+Sampling truely at random from the literature may not even be desirable, as  arguably a literature will succeed if useful discoveries come out of it, not if random findings are true [@wilson2020].
 How much we care about whether a study is "trustworthy" is not uniformly distributed across the literature.
@@
 
+```{r}
+
+ within <- glm(sub_rep ~ is_within, data=for_cor, family=binomial)$coefficient[2] |> exp() 
+ vignette <- glm(sub_rep ~ single_vignette, data=for_cor, family=binomial)$coefficient[2] |> exp()
+
+  subfield <- glm(sub_rep ~ subfield, data=for_cor |> filter(subfield %in% c("social", "cognitive")), family=binomial)$coefficient[2] |> exp()
+
+```
 ## Single predictors
@@
 Predictors of higher replicability included within-subjects designs, higher numbers of trials, and open data.
-Predictors of lower replicability included Single vignetted studies, social psychology studies, and original-replication pairs where the replication switched to online.
+Predictors of lower replicability included single vignetted studies, social psychology studies, and original-replication pairs where the replication switched to online.
 
 Distributions of study outcomes across some of these properties are shown in Figure \ref{fig:predictors-graph}.
-Both social and cognitive psychology studies were well represented, and the cognitive psychology studies replicated at twice the rate of social psychology studies.
-Within and between subjects designs were both common, and within replicated four times as much.
-Similarly, studies with multiple vignettes replicated 1.5 times more than single vignetted studies.
+Both social and cognitive psychology studies were well represented, and the cognitive psychology studies replicated at `r 1/subfield |> round(2)` times the rate of social psychology studies.
+Within and between subjects designs were both common, and within replicated `r within |> round(2)` times as much.
+Similarly, studies with multiple vignettes replicated `r 1/vignette |> round(2)` times more than single vignetted studies.
 However, there were strong correlations among these experimental features and between these experimental features and subfield.
-TODO actual numbers here!
 
@@
 Replications that switched to online were less likely to replicate than those that had the same modality as the original (generally both online, in a few cases both in-person).
-While online studies in general show comparable results to studies conducted in person TODO CITATIONS, switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well adapted (ex.
+While online studies in general show comparable results to studies conducted in person [@crump2013]TODO MORE CITATIONS, switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well adapted (ex.
 inductions may be weaker or attention checks inadequate to the new sample).
@@
 
+```{r}
+tier1_subjective <- read_rds(here(model_location, "tier1_subjective.rds"))
+
+summary(tier1_subjective)$fixed |> as_tibble(rownames="var") |> filter(var=="is_within")|> mutate(text=str_c(round(Est.Error,2), "[", round(`l-95% CI`,2),",", round(`u-95% CI`,2),"]")) |> pull(text) ->within_range
+```
+
 ## Regression model
@@
 The general directions of coefficients are consistent with the effects of the predictors in isolation.
-Within-subjects designs seem an especially strong indicator of replicability TODO include estimate and range in text!
+Within-subjects designs seem an especially strong indicator of replicability (`r within_range`).
 
@@
 
-Other replication projects have other estimands: @camerer2018 seems to ask something closer to how likely studies are to replicate when preformed by an expert with a large budget, and @ML5 TODOCITE asks how likely certain studies are to replicate when performed with extensive feedback from the original authors.
+Other replication projects have other estimands: @camerer2018 seems to ask something closer to how likely studies are to replicate when preformed by an expert with a large budget, and @ebersole2020 asks how likely certain studies are to replicate when performed with extensive feedback from the original authors.
 
@@
 
-Our results are limited by the number and quality of the studies we included. These studies are not necessarily representative of the literature as a whole. TODO what are the limitations we want?
+Our results are limited by the number and quality of the studies we included.
+These studies are not necessarily representative of the studies of interest to psychologists as a whole.
+The replication studies were not designed from the start with this analysis in mind, so analysis is limited by the choices and reporting used at the time of replications.
+TODO what are the limitations we want?
 
@@
 ## Dataset
+
+```{r}
+all <- read_csv(here("data", "raw_data.csv")) |> filter(include %in% c("stats", "pred_int", "exp"))
+
+ps <- all|> mutate(journal=str_to_lower(journal)) |>filter(journal=="psych sci")
+
+```
 The dataset of replication projects comes from class projects conducted in PSYCH 251 (earlier called PSYCH 254) a graduate-level experimental methods class taught by MCF from 2011 to 2022.
@@
 
-Students were free to choose what study they replicated; the recommended path for students who did not have their own ideas was to pick an interesting study from a recent year of Psychological Science (this led to a high fraction of Psych Science articles in the replication sample TODO FOOBAR %).
+Students were free to choose what study they replicated; the recommended path for students who did not have their own ideas was to pick an interesting study from a recent year of Psychological Science (this led to a high fraction of Psych Science articles in the replication sample, `r nrow(ps)`, `r nrow(ps)/nrow(all)*100 |> round()`% of studies).
 
-We note that 4 (TODO check) of the replication projects were included in RP:P, and FOOBAR of them were previously reported in @hawkins.
+We note that 4 (TODO check) of the replication projects were included in RP:P, and 10 of them were previously reported in @hawkins.
 

### 2023-04-05 paper/manuscript.tex
fix some citations and todos

@@
 A major concern in psychology, as in other fields, is that the published literature may not replicate as well as had previously been assumed.
-This is illustrated both by a few prominent findings that turn out to not replicate at all (CITE ex ego depletion, TMT), and by large-scale replication projects such as RP:P which found a replication rate around 40\% for a sample of the psychology literature (\protect\hyperlink{ref-openscienceconsortium2015}{Consortium 2015}).
+This is illustrated both by a few prominent findings that turn out to not replicate at all {[}ex.
+terror management theory; Klein et al.
+(\protect\hyperlink{ref-klein2022}{2022}){]}, and by large-scale replication projects such as RP:P which found a replication rate around 40\% for a sample of the psychology literature (\protect\hyperlink{ref-openscienceconsortium2015}{Consortium 2015}).
 This low replication rates seems undesirable and seems to run counter to the idea of a cumulative science.
@@
 Prior approaches to replicability have focused on interpreting results in terms of a potentially problematic estimand: the probability of a finding in the literature being somehow truly replicable.
-Critics have pointed out that ``true'' replicability may not be possible to estimate outside of a specific sample (CITE van bavel etc.) or even time period (CITE ramscar).
+Critics have pointed out that ``true'' replicability may not be possible to estimate outside of a specific sample (\protect\hyperlink{ref-vanbavel2016}{Van Bavel et al.
+2016}) or even time period (\protect\hyperlink{ref-ramscar}{Ramscar et al.
+n.d.}).
 
@@
 These are reasonable sampling choices, but they undermine the claim that the estimand is the level of ``truth'' in the literature as a whole.
-Sampling truely at random from the literature may not even be desirable, as arguably a literature will succeed if useful discoveries come out of it, not if random findings are true (CITE ``Science is not signal detection'' ref).
+Sampling truely at random from the literature may not even be desirable, as arguably a literature will succeed if useful discoveries come out of it, not if random findings are true (\protect\hyperlink{ref-wilson2020}{Wilson et al.
+2020}).
 How much we care about whether a study is ``trustworthy'' is not uniformly distributed across the literature.
@@
 Predictors of higher replicability included within-subjects designs, higher numbers of trials, and open data.
-Predictors of lower replicability included Single vignetted studies, social psychology studies, and original-replication pairs where the replication switched to online.
+Predictors of lower replicability included single vignetted studies, social psychology studies, and original-replication pairs where the replication switched to online.
 
 Distributions of study outcomes across some of these properties are shown in Figure \ref{fig:predictors-graph}.
-Both social and cognitive psychology studies were well represented, and the cognitive psychology studies replicated at twice the rate of social psychology studies.
-Within and between subjects designs were both common, and within replicated four times as much.
-Similarly, studies with multiple vignettes replicated 1.5 times more than single vignetted studies.
+Both social and cognitive psychology studies were well represented, and the cognitive psychology studies replicated at 2.4390244 times the rate of social psychology studies.
+Within and between subjects designs were both common, and within replicated 3.35 times as much.
+Similarly, studies with multiple vignettes replicated 2.6315789 times more than single vignetted studies.
 However, there were strong correlations among these experimental features and between these experimental features and subfield.
-TODO actual numbers here!
 
@@
 Replications that switched to online were less likely to replicate than those that had the same modality as the original (generally both online, in a few cases both in-person).
-While online studies in general show comparable results to studies conducted in person TODO CITATIONS, switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well adapted (ex.
+While online studies in general show comparable results to studies conducted in person (\protect\hyperlink{ref-crump2013}{Crump et al.
+2013})TODO MORE CITATIONS, switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well adapted (ex.
 inductions may be weaker or attention checks inadequate to the new sample).
@@
 The general directions of coefficients are consistent with the effects of the predictors in isolation.
-Within-subjects designs seem an especially strong indicator of replicability TODO include estimate and range in text!
+Within-subjects designs seem an especially strong indicator of replicability (0.55{[}-0.01,2{]}).
 
@@
 Other replication projects have other estimands: Camerer et al.
-(\protect\hyperlink{ref-camerer2018}{2018}) seems to ask something closer to how likely studies are to replicate when preformed by an expert with a large budget, and (\protect\hyperlink{ref-ML5}{\textbf{ML5?}}) TODOCITE asks how likely certain studies are to replicate when performed with extensive feedback from the original authors.
+(\protect\hyperlink{ref-camerer2018}{2018}) seems to ask something closer to how likely studies are to replicate when preformed by an expert with a large budget, and Ebersole et al.
+(\protect\hyperlink{ref-ebersole2020}{2020}) asks how likely certain studies are to replicate when performed with extensive feedback from the original authors.
 
@@
 
-Students were free to choose what study they replicated; the recommended path for students who did not have their own ideas was to pick an interesting study from a recent year of Psychological Science (this led to a high fraction of Psych Science articles in the replication sample TODO FOOBAR \%).
+Students were free to choose what study they replicated; the recommended path for students who did not have their own ideas was to pick an interesting study from a recent year of Psychological Science (this led to a high fraction of Psych Science articles in the replication sample, 80, 45.4545455\% of studies).
 
-We note that 4 (TODO check) of the replication projects were included in RP:P, and FOOBAR of them were previously reported in Hawkins et al. (\protect\hyperlink{ref-hawkins}{n.d.}).
+We note that 4 (TODO check) of the replication projects were included in RP:P, and 10 of them were previously reported in Hawkins et al. (\protect\hyperlink{ref-hawkins}{n.d.}).
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-crump2013}{}}%
+Crump MJC, McDonnell JV, Gureckis TM (2013) Evaluating {Amazon}'s {Mechanical Turk} as a {Tool} for {Experimental Behavioral Research} (S Gilbert, Ed.).
+\emph{PLoS ONE} \textbf{8}:e57410.
+doi:\href{https://doi.org/10.1371/journal.pone.0057410}{10.1371/journal.pone.0057410}
+
 \leavevmode\vadjust pre{\hypertarget{ref-dreber2015}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-klein2022}{}}%
+Klein RA, Cook CL, Ebersole CR, Vitiello C, Nosek BA, Hilgard J, Ahn PH, Brady AJ, Chartier CR, Christopherson CD, Clay S, Collisson B, Crawford JT, Cromar R, Gardiner G, Gosnell CL, Grahe J, Hall C, Howard I, Joy-Gaba JA, Kolb M, Legg AM, Levitan CA, Mancini AD, Manfredi D, Miller J, Nave G, Redford L, Schlitz I, Schmidt K, Skorinko JLM, Storage D, Swanson T, Van Swol LM, Vaughn LA, Vidamuerte D, Wiggins B, Ratliff KA (2022) Many {Labs} 4: {Failure} to {Replicate Mortality Salience Effect With} and {Without Original Author Involvement}.
+\emph{Collabra: Psychology} \textbf{8}:35271.
+doi:\href{https://doi.org/10.1525/collabra.35271}{10.1525/collabra.35271}
+
 \leavevmode\vadjust pre{\hypertarget{ref-mathur2020}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-ramscar}{}}%
+Ramscar M, Shaoul C, Baayen RH Why many priming results don't (and won't) replicate: {A} quantitative analysis.
+
 \leavevmode\vadjust pre{\hypertarget{ref-simonsohn2015}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-vanbavel2016}{}}%
+Van Bavel JJ, Mende-Siedlecki P, Brady WJ, Reinero DA (2016) Contextual sensitivity in scientific reproducibility.
+\emph{Proc Natl Acad Sci} \textbf{113}:6454--6459.
+doi:\href{https://doi.org/10.1073/pnas.1521897113}{10.1073/pnas.1521897113}
+
 \leavevmode\vadjust pre{\hypertarget{ref-wagge2019}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-wilson2020}{}}%
+Wilson BM, Harris CR, Wixted JT (2020) Science is not a signal detection problem.
+\emph{Proc Natl Acad Sci USA} \textbf{117}:5559--5567.
+doi:\href{https://doi.org/10.1073/pnas.1914237117}{10.1073/pnas.1914237117}
+
 \end{CSLReferences}

### 2023-04-24 paper/manuscript.Rmd
try to re outline intro

@@
 -->
+
+introduction outline:
+
+Things don't replicate that well and it feels like a problem for cumulative science 
+* For a cumulative science, we want (many) of the load-bearing empirical results that form the bases of theories to hold up. 
+* People were acting as if publication of results meant they were true/reliable, trying to build on things; caused crises when some prominent results failed to replicate.
+Called into question reliability of literature as a whole -- lead to a few measurements.
+* Large scale replications of chunks of the literature, but aren't many (list and explain)
+* These rates feel lower than we want
+
+Why? Many approaches, no definitive answers.
+* Why are rates what they are. Both want to know to fix but also to watch out / calibrate caution. Can be approached from theoretical, interventional, and correlational dimensions.
+* Theoretical -- we know people do bad practices and can model how this leads to lower replicability. Requires things we already have ideas about
+* Interventional -- try things they think will make it better (like not doing bad practices), see what happens. Not everything is intervention prone, need to have strong belief first. Expensive!
+* Correlational -- markets/etc say there is some predictive value to be had, but don't say if it's transparent and explainable. RP:P. 
+   - Note that it's correlational, so can't do causality, but still useful for prediction, and as fodder for theory & intervention. (Interplay between them)
+
+* There's been a lot of discussion aroun replicabilty and it's role and yadda yadda (much overfocused on RP:P results because that's what's available).
+Growing sophistication and valid points, but we think it misses the mark about what practicing scientists are concerned about.
+* Don't want to build on something and fail a bunch trying to get your variant to work and then realize it just doesn't work.
+Replicability (as we mean it here) A useful framing is "ability to do cumulative science" -- close to what people mean, may disagree with many things
+* How this approach differs and what it gets us
+    * (built in feasibility under reasonable / small resource constraints)
+    * interest based sampling 
+* gives clear interpretation -- no mention of truth (may even be reliable in a different environment, but would be)
+
+* Previous work, especially RP:P has been overfit &
+also include somewhere:
+* pedagogy
+* overfit to small sample 
+*
+
 # introduction

### 2023-04-26 paper/manuscript.Rmd
work on intro and figure 2

@@
 library(cowplot)
+library(ggthemes)
 #r_refs("r-references.bib", append=F)
@@
 
-<!-- Use class keywords to format keywords section -->
-<!--::: {.keywords data-latex="" lang=en}
-One keyword; Yet another keyword
-:::-->
-
 <!------------ Main text -------------------->
 
+introduction outline:
+
+Things don't replicate that well and it feels like a problem for cumulative science 
+* For a cumulative science, we want (many) of the load-bearing empirical results that form the bases of theories to hold up. 
+* People were acting as if publication of results meant they were true/reliable, trying to build on things; caused crises when some prominent results failed to replicate.
+Called into question reliability of literature as a whole -- lead to a few measurements.
+* Large scale replications of chunks of the literature, but aren't many (list and explain)
+* These rates feel lower than we want
+
+Why? Many approaches, no definitive answers.
+* Why are rates what they are. Both want to know to fix but also to watch out / calibrate caution. Can be approached from theoretical, interventional, and correlational dimensions.
+* Theoretical -- we know people do bad practices and can model how this leads to lower replicability. Requires things we already have ideas about
+* Interventional -- try things they think will make it better (like not doing bad practices), see what happens. Not everything is intervention prone, need to have strong belief first. Expensive!
+* Correlational -- markets/etc say there is some predictive value to be had, but don't say if it's transparent and explainable. RP:P. 
+   - Note that it's correlational, so can't do causality, but still useful for prediction, and as fodder for theory & intervention. (Interplay between them)
+
+What's missing from the conversation and why our approach is good. 
+* There's been a lot of discussion around replicabilty and it's role and yadda yadda (much overfocused on RP:P results because that's what's available).
+Growing sophistication and valid points, but we think it misses the mark about what practicing scientists are concerned about.
+* Don't want to build on something and fail a bunch trying to get your variant to work and then realize it just doesn't work.
+Replicability (as we mean it here) A useful framing is "ability to do cumulative science" -- close to what people mean, may disagree with many things
+* How this approach differs and what it gets us
+    * (built in feasibility under reasonable / small resource constraints)
+    * interest based sampling 
+    * functional approach sidesteps issues of "truth" (may even be reliable in a different environment, but would be)
+
+Teaser:
+* We do x,y,z, and find that larger effect sizes and within subjects designs are the two strongest correlates of replicability in this sample.
+
 <!--
-# TODO list
-- BETTER abstract
-- many citations everywhere
-- long list of things to gesture at in intro
-- link to open stuffs
-- ** verify code for ES ** with someone
-- redo intro
-- redo results
-- redo discussion
-- fill in todos
 
 # Text slush pile
+
+The perceived need for more replications in tension with the lack of publishing incentives for doing replications led several to suggest that pedagogical replications could fill this gap.
+Doing replications is a way for students to learn to do experiments in a scaffolded way and leads to more useful results than what students could design from scratch on the same timescale [@quintana2021; @wagge2019;@frank2012; @hawkins].
+[TODO needs transition]
+
+ * Don't want to build on something and fail a bunch trying to get your variant to work and then realize it just doesn't work.
+Replicability (as we mean it here) A useful framing is "ability to do cumulative science" -- close to what people mean, may disagree with many things
+We think this is a valuable estimand because it's estimating what people actually care about: is this result of interest sturdy enough to support cumulative science?
+
 [who knows where this paragraph should go] Replications are one way of approximating whether an effect in the target paper is true, and how likely results are to replicate in some sort of platonic ideal world.
@@
 
-# Citation slush pile
-
-predict w/ ML @altmejd2019
-
-econ also has replications and issues @camerer2016
-
-moving goal posts around replication / interpreting results @nosek2020
-
-some sort of modeling of replications @pawel2020
-
-@schmidt2009 early theory of replication as part of advancing knowledge
-
-@simonsohn2015 small telescopes
-
-@gelman2018 Don’t characterize replications as successes or failures.
-
-@mathur2020 other metrics of replicability
-
-pedagogy for replication in intro:
-
-@frank2012
-@hawkins
-
-@odonnell2021 reps of some set of related things
-
-@pownall2021 sips 2021 on teaching openness
-@jekel2020 teach open science w/ replication 
-@jern2018 in one study didn't show critical thinking benefits for students to make them do replications
--->
-
-introduction outline:
-
-Things don't replicate that well and it feels like a problem for cumulative science 
-* For a cumulative science, we want (many) of the load-bearing empirical results that form the bases of theories to hold up. 
-* People were acting as if publication of results meant they were true/reliable, trying to build on things; caused crises when some prominent results failed to replicate.
-Called into question reliability of literature as a whole -- lead to a few measurements.
-* Large scale replications of chunks of the literature, but aren't many (list and explain)
-* These rates feel lower than we want
-
-Why? Many approaches, no definitive answers.
-* Why are rates what they are. Both want to know to fix but also to watch out / calibrate caution. Can be approached from theoretical, interventional, and correlational dimensions.
-* Theoretical -- we know people do bad practices and can model how this leads to lower replicability. Requires things we already have ideas about
-* Interventional -- try things they think will make it better (like not doing bad practices), see what happens. Not everything is intervention prone, need to have strong belief first. Expensive!
-* Correlational -- markets/etc say there is some predictive value to be had, but don't say if it's transparent and explainable. RP:P. 
-   - Note that it's correlational, so can't do causality, but still useful for prediction, and as fodder for theory & intervention. (Interplay between them)
-
-* There's been a lot of discussion aroun replicabilty and it's role and yadda yadda (much overfocused on RP:P results because that's what's available).
-Growing sophistication and valid points, but we think it misses the mark about what practicing scientists are concerned about.
-* Don't want to build on something and fail a bunch trying to get your variant to work and then realize it just doesn't work.
-Replicability (as we mean it here) A useful framing is "ability to do cumulative science" -- close to what people mean, may disagree with many things
-* How this approach differs and what it gets us
-    * (built in feasibility under reasonable / small resource constraints)
-    * interest based sampling 
-* gives clear interpretation -- no mention of truth (may even be reliable in a different environment, but would be)
-
-* Previous work, especially RP:P has been overfit &
-also include somewhere:
-* pedagogy
-* overfit to small sample 
-*
-
 # introduction
-When building a stone wall, it's important that the components be stones that will retain their shape and not clots of dirt and sand that might fall apart and bring the rest of the wall falling down.
+.
 Building a cumulative body of scientific theories similarly requires that the empirical results, especially the more foundational empirical results, be sturdy.
@@
 
-A major concern in psychology, as in other fields, is that the published literature may not replicate as well as had previously been assumed.
-This is illustrated both by a few prominent findings that turn out to not replicate at all [ex.
-terror management theory; @klein2022], and by large-scale replication projects such as RP:P which found a replication rate around 40% for a sample of the psychology literature [@openscienceconsortium2015].
-This low replication rates seems undesirable and seems to run counter to the idea of a cumulative science.
+Knowing what predicts and drives non-replications would let us potentially increase the replication rate, and also calibrate our levels of caution and skepticism toward results.
+Theoretical, interventional and correlational approaches do not yet provide comprehensive answers.
 
-A big open question is why the replication rates in psychology are so low.
-There are theoretical approaches modelling how questionable research practices (which many psychologists admit to) and a bias towards positive results would lead to a high rate of (non-replicable) false positives in the literature (CITE).
-There's some disconnect between these theoretically causal factors and empirical results about what causes or correlates with replicability.
+-->
 
-A couple studies have attempted to intervene on the low replication rate, but seeing if certain factors can affect whether studies replicate.
-For instance, across 16 studies, @protzko2020 showed that better methodological practices, such as transparency, large sample sizes, and confirmatory tests, led to replication rates  that matched theoretical expectations based on the effect sizes and sample sizes, and replication effect sizes comparable with the original.
+Questions:
+- mention primary outcome in intro? 
+- do we want to use the term p(cumulative)?
+
+TODO fill in cites
+flesh out theoretical approaches section
+
+introduction outline:
+
+Things don't replicate that well and it feels like a problem for cumulative science 
+A cumulative science requires foundational empirical results that can be build upon in theories and future experiments.
+These load-bearing results need to be reliable; when they are not robust, attempts to build on them waste resources, trying to find explanations and effects where there may be none.
+
+Scientists, policymakers, and the public often treat publication as a signal that a result is (likely to be) true.
+This trust in published findings leads scientists to attempt to build on them, but failures to build on them are explained away and rarely published, leaving the original results uncontested in the literature, while failures accumulate in private.
+
+Publicized failures to replicate called into question the tacit assumption that most of the literature was robust and would replicate.
+Certain prominent findings turned out to not replicate at all [ex.
+terror management theory; @klein2022], and a large scale replication project pegged the replication rate for findings in top-tier psychology journals at around 40% [@openscienceconsortium2015].
+
+Few large scale replications have been conducted in psychology, due to the resources required to run large numbers of replication studies.
+We are aware of three.
+RP:P sampled roughly 100 studies from articles published in three top psychology journals in 2008 and found a overall replication rate of around 40% [@openscienceconsortium2015].
+ManyLabs investigated heterogeneity using short target studies that compared between two conditions each, but these studies are not representative of the psychology literature as a whole.
+Across Many Labs 1-3, 29 of 51 target effects (57%) replicated [@klein2014; @klein2018; @ebersole2016].
+@camerer2018 replicated all 21 behavioral social science studies from Nature and Science from 2010-2015 that were feasible; the replication rate was around 60%.
+These roughly 170 replications of psychology studies are the primary empirical results on which discussions of replication rates in psychology are based.
+
+A replication rate around 50% runs counter to the prior assumption that most findings in the literature was robust enough to support cumulative science, and raises the question: What makes the replication rates in psychology so low?
+
+* Theoretical -- we know people do bad practices and can model how this leads to lower replicability. Requires things we already have ideas about
+
+Theoretical approaches to understanding the replication rate have modeled how flexible research practices, selective reporting, and a bias toward positive results could lead to a high rate of (non-replicable) false positives (CITE).
+However, while scientists admit to engaging in these practices, we don't yet know what proportion of non-replications are driven by these factors or how to identify these studies in the literature.
+
+Experimental approaches attempt to intervene on the low replication rate, by seeing if changing certain factors affects whether studies replicate.
+@protzko2020 showed, across 16 studies, that better methodological practices, such as transparency, large sample sizes, and confirmatory tests, led to replication rates that matched theoretical expectations based on the effect sizes and sample sizes, with replication effect sizes comparable with the original.
 Many Labs 5 examined how adding expert advice to a replication process might intervene to improve the replicate rate, and found that it mostly didn't, at least on the 10 studies they looked at [@ebersole2020].
-These types of experiments are valuable, but they aren't very scalable because they are expensive and some potential influences on non-replication are not experimentally manipulable.
+These types of experiments are valuable for testing potential causes of non-replication, but they don't scale well do to expense.
+Additionally, not all potential influences on non-replication are experimentally manipulable.
 
-As an alternative, much of the work looking at predictors of replicability has been correlation: whether using regression models, prediction markets, or machine learning techniques to build predictions about what will replicate.
-However, all of these approaches depend on data from replications.
-While many replications have been conducted, most were not randomly sampled and are not pooled together, so these studies instead rely on the small number of data points from large-scale replication projects.
-The RP:P dataset itself is much discussed and reanalyzed [@etz2016;@gilbert2016;@patil2016;@anderson2016].
-These correlational approaches have established that people can predict what studies will replicate above chance [@hoogeveen2019;@dreber2015; @forsell2019;@camerer2018], but have not identified that many concrete predictors that differentiate replications from non-replications.
-In the RP:P sample, studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate.
+Correlational approaches looking for predictors of replicability are the most popular.
+Prediction markets and elicitations have established that people can predict what studies will replicate above chance [@hoogeveen2019;@dreber2015; @forsell2019;@camerer2018], but have not identified many concrete predictors that differentiate replications from non-replications.
+Machine learning approaches CITE similarly show predictive signal, but do not provide explainable predictor variables.
+@opensicenceconsortium2015 looked for simple correlates of replicability in the RP:P sample and found that studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate.
+Correlations approaches depend on data from replications, generally drawing heavily from the same small set of data points.
+In particular, the RP:P dataset itself is much discussed and reanalyzed [@etz2016;@gilbert2016;@patil2016;@anderson2016] to the point that much of what we think we know about replicability may be overfit to the 100 studies included in in RP:P.
 
-This reliance on the same small set of data is problematic, as much of what we think we know about replicability is overfit to this small sample.
-However, given the time-consuming nature of running a large number of replications, there is a limited amount of large-scale replication data to draw on.
-We are aware of three large-scale replication efforts replicating experimental results in the existing psychology literature.
-RP:P sampled roughly 100 studies from articles published in three top psychology journals in 2008 and found a overall replication rate of around 40% [@openscienceconsortium2015].
-The ManyLabs series of replications investigating heterogeneity has sampled target studies that are short and compare only two conditions, which is not representative of the psychology literature as a whole.
-Across Many Labs 1-3, 29 of 51 target effects (57%) were found to replicate [@klein2014; @klein2018; @ebersole2016].
-@camerer2018 found a roughly 60% replication rate when they replicated all 21 behaviors studies published in Nature and Science from 2010-2015 that did not require special populations or special equipment.
-Those are all the large-scale replication projects of experimental psychology results available at this time.
-These roughly 170 results are heavily represented in the work predicting what effects will replicate.
+What's missing from the conversation and why our approach is good. 
+* There's been a lot of discussion around replicabilty and it's role and yadda yadda (much overfocused on RP:P results because that's what's available).
+Growing sophistication and valid points, but we think it misses the mark about what practicing scientists are concerned about.
 
-The perceived need for more replications in tension with the lack of publishing incentives for doing replications led several to suggest that pedagogical replications could fill this gap.
-Doing replications is a way for students to learn to do experiments in a scaffolded way and leads to more useful results than what students could design from scratch on the same timescale [@quintana2021; @wagge2019;@frank2012; @hawkins].
-[TODO needs transition]
-
-Our main contribution is a new dataset of 176 replications of experimental studies from the social sciences, primarily psychology.
-These replications were conducted by students in graduate-level experimental methods class between 2011 and 2022 as individual course projects.
-This approximately doubles the set of experiments in the large-scale replication literature.
-We investigate predictors of replicability in this new dataset.
-
+What does replicability mean?
 Prior approaches to replicability have focused on interpreting results in terms of a potentially problematic estimand: the probability of a finding in the literature being somehow truly replicable.
@@
 
+<!-- good below here -->
+
 In contrast, we have explicitly pursued a different estimand: the probability that a researcher, on selecting a finding of interest from the literature, can successfully achieve a result satisfactorily close enough to the original that they can build on it in their own work, with all the necessary compromises to the methods and sample of the original that may be required by the constraints of the situation.
 
-The sampling for our replications is based on what studies students were interested in and wanted to replicate, with some constraints of feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable within their ability and budgetary constraints.
-Our primary criteria for replication success is a subjective measure of whether the study replicated for the same reason, that we believe this is usually what researchers care about: is it close enough that you think you're getting at the same effect and could confidently build on it.
-The quality of the replications also reflects this: unlike some prior work like @camerer2018, which explicitly aimed for high-powered replications, the power in these studies was limited by budgetary reasons in some cases, which is reflective of the types of resources often available to trainee scientists.
+This framing of replicability matches our methodology.
 
-We think this is a valuable estimand because it's estimating what people actually care about: is this result of interest sturdy enough to support cumulative science?
+Rather than sampling at random from some parts of the literature; our sample of studies is selected based on what studies students were interested in and wanting to replicate, with some filtering for feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable given methodological and budgetary constraints.
+
+We use a subjective replication score as our primary metric.
+Whether one feels confident in the results of a study given a replication is not always dependent on only one outcome measure (ex.
+interaction term) and particularly not dependent on only one statistical comparison between the two studies (ex.
+replication is p<.05 same direction as original).
+This avoids bright line distinctions and accomodates the range of outcome measures in our diverse set of studies.
+
+All our replications were conducted under short time scales and relatively small budgets, which mimics the constraints many scientists are under when starting new projects.
+From the point of view of cumulative science, researchers want to know if they can get paradigms to work under their real-world constraints.
+The same issue that may cause a study not to replicate under constrained circumstances (despite hypothetically replicating under more favorable circumstances such as expert administration or larger budgets) will also plague attempts to build off those studies in constrained circumstances.
+Thus, we believe it is relevant to estimate replicability as done by a graduate student with limited resources.
+
+Overall, we take a functional approach to assessing replicability, by framing both our methods and interpretation around the idea of whether work can be repeated or built on by an early-career scientist.
+
+Our contribution is a new dataset of 176 replications of experimental studies from the social sciences, primarily psychology.
+These replications were conducted by students in graduate-level experimental methods class between 2011 and 2022 as individual course projects.
+We investigated predictors of replicability in this dataset and found that within-subjects designs and studies with large standardized effect sizes were positively correlated with replication success.
 
@@
 A holistic measure of replication success had been coded for each project when it was turned in at the end of the class.
-For reliability, VB independently code the replication success from the replication reports; discrepancies were resolved by discussion between MCF and VB (`r pluck(matching,2,1)/176*100 |> round()` % of cases).
+For reliability, VB independently code the replication success from the replication reports; discrepancies were resolved by discussion between MCF and VB (`r round(pluck(matching,2,1)/176*100)`% of cases).
 
@@
          pub_year, subfield, open_data, open_mat, stanford, change_platform, log_ratio_ss, is_within, single_vignette, log_sample, log_trials) |> mutate(social=ifelse(subfield=="social", 1,0),other_psych=ifelse(subfield=="other-psych",1,0), non_psych=ifelse(subfield=="non-psych", 1,0))
+
 sub_cor <- function(var, stat = "estimate") {
@@
 ```
+
 ## Single predictors
@@
 Distributions of study outcomes across some of these properties are shown in Figure \ref{fig:predictors-graph}.
-Both social and cognitive psychology studies were well represented, and the cognitive psychology studies replicated at `r 1/subfield |> round(2)` times the rate of social psychology studies.
+Both social and cognitive psychology studies were well represented, and the cognitive psychology studies replicated at `r round(1/subfield, 2)` times the rate of social psychology studies.
 Within and between subjects designs were both common, and within replicated `r within |> round(2)` times as much.
-Similarly, studies with multiple vignettes replicated `r 1/vignette |> round(2)` times more than single vignetted studies.
+Similarly, studies with multiple vignettes replicated `r round(1/vignette, 2)` times more than single vignetted studies.
 However, there were strong correlations among these experimental features and between these experimental features and subfield.
@@
 ```{r}
+do_estimates <- function(model, variable){
+  summary(model)$fixed |> as_tibble(rownames="var") |> filter(var==variable)|> mutate(text=str_c(round(Est.Error,2), ", CrI= [", round(`l-95% CI`,2),", ", round(`u-95% CI`,2),"]")) |> pull(text)
+}
+
 tier1_subjective <- read_rds(here(model_location, "tier1_subjective.rds"))
 
-summary(tier1_subjective)$fixed |> as_tibble(rownames="var") |> filter(var=="is_within")|> mutate(text=str_c(round(Est.Error,2), "[", round(`l-95% CI`,2),",", round(`u-95% CI`,2),"]")) |> pull(text) ->within_range
+within_1 <- do_estimates(tier1_subjective, "is_within")
+
+tier3_subjective <- read_rds(here(model_location, "tier3_subjective.rds"))
+
+within_3 <- do_estimates(tier3_subjective, "is_within")
+
+smd_3 <- do_estimates(tier3_subjective, "z_target_d_calc")
+
+sens_3 <- read_rds(here(model_location, "sens_tier3_subjective.rds"))
+
+within_sens <- do_estimates(sens_3, "is_within")
+
+smd_sens <- do_estimates(sens_3, "z_target_d_calc")
+
+pred_int <- read_rds(here(model_location, "tier3_predint.rds"))
+
+within_2 <- do_estimates(pred_int, "is_within")
+
+smd_2 <- do_estimates(pred_int, "z_target_d_calc")
 ```
@@
 While a number of the predictors show individual correlations with the subjective replication score, many of the predictors are also correlated with one another.
-In order to determine which predictors were the strongest, we ran a pre-registered regularized regression model (see Methods for details).
-The coefficient estimates are shown in Figure \ref{fig:mod-results}.
+In order to determine which predictors were the strongest, we ran a series of pre-registered regularized regression models (see Methods for details; see Supplement for all estimates from all models).
+The coefficient estimates of the primary model, predicting the subjective replication scores based on all the data, are shown in Figure \ref{fig:mod-results}.
 Due to a large number of predictors coupled with a small and noisy dataset, even with strong regularization, there is much uncertainty around the coefficients.
 The general directions of coefficients are consistent with the effects of the predictors in isolation.
-Within-subjects designs seem an especially strong indicator of replicability (`r within_range`).
 
-```{r mod-results, out.height="25%", fig.width=8, fig.height=3, fig.pos="ht", fig.cap="Coefficient estimates and uncertainty from a model predicting subjective replication scores from the full dataset."}
-tier1_subjective <- read_rds(here(model_location, "tier1_subjective.rds"))
-tier1_subjective |> 
-gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |> mutate(Term=factor(Term, levels=c("subfieldsocial", "subfieldother_psych", "subfieldnon_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "z_pub_year", "z_log_trials", "z_log_sample", "z_log_ratio_ss"), labels=c("Social", "Other psych", "Non psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rep/orig sample"))) |>
-  ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
-  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI predicting subjective replication score")+theme(axis.text=element_text(size=11))
+Within-subjects designs stand out as the strongest indicator of replicability in the model without statistical predictors (`r within_1`).
+When statistical predictors are added to the model, within-subjects designs remain predictive (`r within_3`).
+Standardized effect size is another strong predictor of subjective replication score (`r smd_3`).
+Both effects are robust to a sensitivity analysis including only studies with close replications and matching statistical tests (within-subjects `r within_sens`; effect size `r smd_sens`).
+
+We also ran models predicting whether the replication effect was within the prediction interval as the original effect and what the p-original was between the replication and original.
+Both these models had even more uncertain estimates.
+While the credible intervals are wide, the general patterns of predictors are similar to the subjective replication models.
+The strongest predictors are still within-subjects designs (`r within_2`) and studies with larger effect sizes (`r smd_2`).
+
+```{r mod-results, out.width="90%", fig.width=8, fig.height=5, fig.pos="ht", fig.cap="Coefficient estimates and uncertainty from a model predicting subjective replication scores from the full dataset."}
+
+do_draws <- function(model){
+  draws <- model |> gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> 
+    mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |>  filter(Term!="Intercept") |> 
+    mutate(Term=factor(Term, levels=c("subfieldsocial", "subfieldother_psych", "subfieldnon_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "z_pub_year", "z_log_trials", "z_log_sample", "z_log_ratio_ss","z_log_p","z_target_d_calc"), labels=c("Social", "Other psych", "Non psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rep/orig sample", "P-value", "Original effect size")))
+}
+
+tier1_subjective <- read_rds(here(model_location, "tier1_subjective.rds")) |> do_draws() |> mutate(type="Without stats predictors") |> mutate(sens="All data")
+tier3_subjective <- read_rds(here(model_location, "tier3_subjective.rds"))|> do_draws() |> mutate(type="With stats predictors") |> mutate(sens="All data")
+
+tier1_subjective |> union(tier3_subjective) |> ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate, color=type)) + geom_vline(xintercept=0)+
+  scale_color_solarized()+
+  stat_pointinterval(position=position_dodge(width=.7))+labs(y="", x="Estimate, 66%, 95% CrI predicting subjective replication score", color="", linetype="", shape="")+theme(axis.text=element_text(size=11),legend.position="bottom")
 
 ```
-
-Results from other models can be found in the supplement.
 

### 2023-04-26 paper/manuscript.tex
work on intro and figure 2

@@
 
-\hypertarget{introduction}{%
-\section{introduction}\label{introduction}}
+introduction outline:
 
-When building a stone wall, it's important that the components be stones that will retain their shape and not clots of dirt and sand that might fall apart and bring the rest of the wall falling down.
-Building a cumulative body of scientific theories similarly requires that the empirical results, especially the more foundational empirical results, be sturdy.
-Results that cannot be observed consistently are like dirt clots, they don't hold their shape and thus are not a strong foundation for the theories and studies built on top of them.
-Replications and the theory of replicability can be thought of as a way of testing whether the empirical results are sturdy.
-Replicating is a necessary feature for load-bearing empirical results.
-We note that replicability is not the only desirable feature of a study, and that replicating does not mean that a study is valid, or generalizable, or interesting.
+Things don't replicate that well and it feels like a problem for cumulative science
+* For a cumulative science, we want (many) of the load-bearing empirical results that form the bases of theories to hold up.
+* People were acting as if publication of results meant they were true/reliable, trying to build on things; caused crises when some prominent results failed to replicate.
+Called into question reliability of literature as a whole -- lead to a few measurements.
+* Large scale replications of chunks of the literature, but aren't many (list and explain)
+* These rates feel lower than we want
 
+Why? Many approaches, no definitive answers.
+* Why are rates what they are. Both want to know to fix but also to watch out / calibrate caution. Can be approached from theoretical, interventional, and correlational dimensions.
+* Theoretical -- we know people do bad practices and can model how this leads to lower replicability. Requires things we already have ideas about
+* Interventional -- try things they think will make it better (like not doing bad practices), see what happens. Not everything is intervention prone, need to have strong belief first. Expensive!
+* Correlational -- markets/etc say there is some predictive value to be had, but don't say if it's transparent and explainable. RP:P.
+- Note that it's correlational, so can't do causality, but still useful for prediction, and as fodder for theory \& intervention. (Interplay between them)
+
+What's missing from the conversation and why our approach is good.
+* There's been a lot of discussion around replicabilty and it's role and yadda yadda (much overfocused on RP:P results because that's what's available).
+Growing sophistication and valid points, but we think it misses the mark about what practicing scientists are concerned about.
+* Don't want to build on something and fail a bunch trying to get your variant to work and then realize it just doesn't work.
+Replicability (as we mean it here) A useful framing is ``ability to do cumulative science'' -- close to what people mean, may disagree with many things
+* How this approach differs and what it gets us
+* (built in feasibility under reasonable / small resource constraints)
+* interest based sampling
+* functional approach sidesteps issues of ``truth'' (may even be reliable in a different environment, but would be)
+
+Teaser:
+* We do x,y,z, and find that larger effect sizes and within subjects designs are the two strongest correlates of replicability in this sample.
+
+Questions:
+- mention primary outcome in intro?
+- switch out fig 4 for supp fig 2?
+- do we want to use the term p(cumulative)?
+
+TODO fill in cites
+flesh out theoretical approaches section
+
+introduction outline:
+
+Things don't replicate that well and it feels like a problem for cumulative science
+* For a cumulative science, we want (many) of the load-bearing empirical results that form the bases of theories to hold up.
+For a cumulative science, the empirical results that form the bases for theories and
+* People were acting as if publication of results meant they were true/reliable, trying to build on things; caused crises when some prominent results failed to replicate.
+Called into question reliability of literature as a whole -- lead to a few measurements.
 A major concern in psychology, as in other fields, is that the published literature may not replicate as well as had previously been assumed.
@@
 
-A big open question is why the replication rates in psychology are so low.
-There are theoretical approaches modelling how questionable research practices (which many psychologists admit to) and a bias towards positive results would lead to a high rate of (non-replicable) false positives in the literature (CITE).
-There's some disconnect between these theoretically causal factors and empirical results about what causes or correlates with replicability.
-
-A couple studies have attempted to intervene on the low replication rate, but seeing if certain factors can affect whether studies replicate.
-For instance, across 16 studies, Protzko et al.
-(\protect\hyperlink{ref-protzko2020}{2020}) showed that better methodological practices, such as transparency, large sample sizes, and confirmatory tests, led to replication rates that matched theoretical expectations based on the effect sizes and sample sizes, and replication effect sizes comparable with the original.
-Many Labs 5 examined how adding expert advice to a replication process might intervene to improve the replicate rate, and found that it mostly didn't, at least on the 10 studies they looked at (\protect\hyperlink{ref-ebersole2020}{Ebersole et al.
-2020}).
-These types of experiments are valuable, but they aren't very scalable because they are expensive and some potential influences on non-replication are not experimentally manipulable.
-
-As an alternative, much of the work looking at predictors of replicability has been correlation: whether using regression models, prediction markets, or machine learning techniques to build predictions about what will replicate.
-However, all of these approaches depend on data from replications.
-While many replications have been conducted, most were not randomly sampled and are not pooled together, so these studies instead rely on the small number of data points from large-scale replication projects.
-The RP:P dataset itself is much discussed and reanalyzed (\protect\hyperlink{ref-anderson2016}{Anderson et al.
-2016}, \protect\hyperlink{ref-etz2016}{Etz \& Vandekerckhove 2016}, \protect\hyperlink{ref-gilbert2016}{Gilbert et al.
-2016}, \protect\hyperlink{ref-patil2016}{Patil et al.
-2016}).
-These correlational approaches have established that people can predict what studies will replicate above chance (\protect\hyperlink{ref-dreber2015}{Dreber et al.
-2015}, \protect\hyperlink{ref-camerer2018}{Camerer et al.
-2018}, \protect\hyperlink{ref-forsell2019}{Forsell et al.
-2019}, \protect\hyperlink{ref-hoogeveen2019}{Hoogeveen et al.
-2019}), but have not identified that many concrete predictors that differentiate replications from non-replications.
-In the RP:P sample, studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate.
-
-This reliance on the same small set of data is problematic, as much of what we think we know about replicability is overfit to this small sample.
-However, given the time-consuming nature of running a large number of replications, there is a limited amount of large-scale replication data to draw on.
+\begin{itemize}
+\tightlist
+\item
+  Large scale replications of chunks of the literature, but aren't many (list and explain)
   We are aware of three large-scale replication efforts replicating experimental results in the existing psychology literature.
@@
 Those are all the large-scale replication projects of experimental psychology results available at this time.
-These roughly 170 results are heavily represented in the work predicting what effects will replicate.
+These roughly 170 results are the primary empirical results discussions of replication in pschology have to rely are.
+\item
+  These rates feel lower than we want
+\end{itemize}
 
-The perceived need for more replications in tension with the lack of publishing incentives for doing replications led several to suggest that pedagogical replications could fill this gap.
-Doing replications is a way for students to learn to do experiments in a scaffolded way and leads to more useful results than what students could design from scratch on the same timescale (\protect\hyperlink{ref-frank2012}{Frank \& Saxe 2012}, \protect\hyperlink{ref-wagge2019}{Wagge et al.
-2019}, \protect\hyperlink{ref-quintana2021}{Quintana 2021}, \protect\hyperlink{ref-hawkins}{Hawkins et al.
-n.d.}).
-{[}TODO needs transition{]}
+Why? Many approaches, no definitive answers.
+What makes the replication rates in psychology so low?
+Knowing what predicts and drives non-replications would let us potentially increase the replication rate, and also calibrate our levels of caution and skepticism toward results.
+Theoretical, interventional and correlational approaches do not yet provide comprehensive answers.
 
-Our main contribution is a new dataset of 176 replications of experimental studies from the social sciences, primarily psychology.
-These replications were conducted by students in graduate-level experimental methods class between 2011 and 2022 as individual course projects.
-This approximately doubles the set of experiments in the large-scale replication literature.
-We investigate predictors of replicability in this new dataset.
+\begin{itemize}
+\tightlist
+\item
+  Theoretical -- we know people do bad practices and can model how this leads to lower replicability. Requires things we already have ideas about
+\end{itemize}
 
+Theoretical approaches modelling how questionable research practices (which many psychologists admit to) and a bias towards positive results would lead to a high rate of (non-replicable) false positives in the literature (CITE).
+There's some disconnect between these theoretically causal factors and empirical results about what causes or correlates with replicability.
+
+\begin{itemize}
+\item
+  Interventional -- try things they think will make it better (like not doing bad practices), see what happens. Not everything is intervention prone, need to have strong belief first. Expensive!
+  A couple studies have attempted to intervene on the low replication rate, but seeing if certain factors can affect whether studies replicate.
+For instance, across 16 studies, Protzko et al.
+(\protect\hyperlink{ref-protzko2020}{2020}) showed that better methodological practices, such as transparency, large sample sizes, and confirmatory tests, led to replication rates that matched theoretical expectations based on the effect sizes and sample sizes, and replication effect sizes comparable with the original.
+Many Labs 5 examined how adding expert advice to a replication process might intervene to improve the replicate rate, and found that it mostly didn't, at least on the 10 studies they looked at (\protect\hyperlink{ref-ebersole2020}{Ebersole et al.
+2020}).
+These types of experiments are valuable, but they aren't very scalable because they are expensive and some potential influences on non-replication are not experimentally manipulable.
+\item
+  Correlational -- markets/etc say there is some predictive value to be had, but don't say if it's transparent and explainable. RP:P.
+  Much of the work looking at predictors of replicability has been correlational.
+Prediction markets and elicitations have established that people can predict what studies will replicate above chance (\protect\hyperlink{ref-dreber2015}{Dreber et al.
+2015}, \protect\hyperlink{ref-camerer2018}{Camerer et al.
+2018}, \protect\hyperlink{ref-forsell2019}{Forsell et al.
+2019}, \protect\hyperlink{ref-hoogeveen2019}{Hoogeveen et al.
+2019}), but have not identified many concrete predictors that differentiate replications from non-replications.
+Machine learning approaches CITE similarly show predictive signal, but do not provide explainable predictor variables.
+In the RP:P sample, studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate CITE .
+All of these correlational approaches depend on data from replications, generally drawing heavily from the same small set of large-scale replication data points.
+In particular, the RP:P dataset itself is much discussed and reanalyzed (\protect\hyperlink{ref-anderson2016}{Anderson et al.
+2016}, \protect\hyperlink{ref-etz2016}{Etz \& Vandekerckhove 2016}, \protect\hyperlink{ref-gilbert2016}{Gilbert et al.
+2016}, \protect\hyperlink{ref-patil2016}{Patil et al.
+2016}), so much of what we think we know about replicability may be overfit to the 100 studies included in in RP:P.
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Note that it's correlational, so can't do causality, but still useful for prediction, and as fodder for theory \& intervention. (Interplay between them)
+  \end{itemize}
+\end{itemize}
+
+What's missing from the conversation and why our approach is good.
+* There's been a lot of discussion around replicabilty and it's role and yadda yadda (much overfocused on RP:P results because that's what's available).
+Growing sophistication and valid points, but we think it misses the mark about what practicing scientists are concerned about.
+
+What does replicability mean?
 Prior approaches to replicability have focused on interpreting results in terms of a potentially problematic estimand: the probability of a finding in the literature being somehow truly replicable.
@@
 
-The sampling for our replications is based on what studies students were interested in and wanted to replicate, with some constraints of feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable within their ability and budgetary constraints.
-Our primary criteria for replication success is a subjective measure of whether the study replicated for the same reason, that we believe this is usually what researchers care about: is it close enough that you think you're getting at the same effect and could confidently build on it.
-The quality of the replications also reflects this: unlike some prior work like Camerer et al.
-(\protect\hyperlink{ref-camerer2018}{2018}), which explicitly aimed for high-powered replications, the power in these studies was limited by budgetary reasons in some cases, which is reflective of the types of resources often available to trainee scientists.
+This framing of replicability matches our methodology.
 
-We think this is a valuable estimand because it's estimating what people actually care about: is this result of interest sturdy enough to support cumulative science?
+Rather than sampling at random from some parts of the literature; our sample of studies is selected based on what studies students were interested in and wanting to replicate, with some filtering for feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable given methodological and budgetary constraints.
+
+We use a subjective replication score as our primary metric.
+Whether one feels confident in the results of a study given a replication is not always dependent on only one outcome measure (ex.
+interaction term) and particularly not dependent on only one statistical comparison between the two studies (ex.
+replication is p\textless.05 same direction as original).
+This avoids bright line distinctions and accomodates the range of outcome measures in our diverse set of studies.
+
+All our replications were conducted under short time scales and relatively small budgets, which mimics the constraints many scientists are under when starting new projects.
+From the point of view of cumulative science, researchers want to know if they can get paradigms to work under their real-world constraints.
+The same issue that may cause a study not to replicate under constrained circumstances (despite hypothetically replicating under more favorable circumstances such as expert administration or larger budgets) will also plague attempts to build off those studies in constrained circumstances.
+Thus, we believe it is relevant to estimate replicability as done by a graduate student with limited resources.
+
+Overall, we take a functional approach to assessing replicability, by framing both our methods and interpretation around the idea of whether work can be repeated or built on by an early-career scientist.
+
+Our contribution is a new dataset of 176 replications of experimental studies from the social sciences, primarily psychology.
+These replications were conducted by students in graduate-level experimental methods class between 2011 and 2022 as individual course projects.
+We investigated predictors of replicability in this dataset and found that within-subjects designs and studies with large standardized effect sizes were positively correlated with replication success.
 
@@
 A holistic measure of replication success had been coded for each project when it was turned in at the end of the class.
-For reliability, VB independently code the replication success from the replication reports; discrepancies were resolved by discussion between MCF and VB (25.5681818 \% of cases).
+For reliability, VB independently code the replication success from the replication reports; discrepancies were resolved by discussion between MCF and VB (26\% of cases).
 
@@
 Distributions of study outcomes across some of these properties are shown in Figure \ref{fig:predictors-graph}.
-Both social and cognitive psychology studies were well represented, and the cognitive psychology studies replicated at 2.4390244 times the rate of social psychology studies.
+Both social and cognitive psychology studies were well represented, and the cognitive psychology studies replicated at 2.45 times the rate of social psychology studies.
 Within and between subjects designs were both common, and within replicated 3.35 times as much.
-Similarly, studies with multiple vignettes replicated 2.6315789 times more than single vignetted studies.
+Similarly, studies with multiple vignettes replicated 2.62 times more than single vignetted studies.
 However, there were strong correlations among these experimental features and between these experimental features and subfield.
@@
 Replications that switched to online were less likely to replicate than those that had the same modality as the original (generally both online, in a few cases both in-person).
-While online studies in general show comparable results to studies conducted in person (\protect\hyperlink{ref-crump2013}{Crump et al.
-2013})TODO MORE CITATIONS, switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well adapted (ex.
+While online studies in general show comparable results to studies conducted in person (\protect\hyperlink{ref-crump2013}{\textbf{crump2013?}})TODO MORE CITATIONS, switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well adapted (ex.
 inductions may be weaker or attention checks inadequate to the new sample).
@@
 While a number of the predictors show individual correlations with the subjective replication score, many of the predictors are also correlated with one another.
-In order to determine which predictors were the strongest, we ran a pre-registered regularized regression model (see Methods for details).
-The coefficient estimates are shown in Figure \ref{fig:mod-results}.
+In order to determine which predictors were the strongest, we ran a series of pre-registered regularized regression models (see Methods for details; see Supplement for all estimates from all models).
+The coefficient estimates of the primary model, predicting the subjective replication scores based on all the data, are shown in Figure \ref{fig:mod-results}.
 Due to a large number of predictors coupled with a small and noisy dataset, even with strong regularization, there is much uncertainty around the coefficients.
 The general directions of coefficients are consistent with the effects of the predictors in isolation.
-Within-subjects designs seem an especially strong indicator of replicability (0.55{[}-0.01,2{]}).
+
+Within-subjects designs stand out as the strongest indicator of replicability in the model without statistical predictors (0.55, CrI= {[}-0.01, 2{]}).
+When statistical predictors are added to the model, within-subjects designs remain predictive (0.64, CrI= {[}-0.03, 2.38{]}).
+Standardized effect size is another strong predictor of subjective replication score (0.59, CrI= {[}0.31, 2.58{]}).
+Both effects are robust to a sensitivity analysis including only studies with close replications and matching statistical tests (within-subjects 0.87, CrI= {[}-0.01, 3.34{]}; effect size 0.97, CrI= {[}0.76, 4.59{]}).
+
+We also ran models predicting whether the replication effect was within the prediction interval as the original effect and what the p-original was between the replication and original.
+Both these models had even more uncertain estimates.
+While the credible intervals are wide, the general patterns of predictors are similar to the subjective replication models.
+The strongest predictors are still within-subjects designs (0.71, CrI= {[}-0.12, 2.38{]}) and studies with larger effect sizes (0.3, CrI= {[}-0.31, 0.89{]}).
 
@@
 \end{figure}
-
-Results from other models can be found in the supplement.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-crump2013}{}}%
-Crump MJC, McDonnell JV, Gureckis TM (2013) Evaluating {Amazon}'s {Mechanical Turk} as a {Tool} for {Experimental Behavioral Research} (S Gilbert, Ed.).
-\emph{PLoS ONE} \textbf{8}:e57410.
-doi:\href{https://doi.org/10.1371/journal.pone.0057410}{10.1371/journal.pone.0057410}
-
 \leavevmode\vadjust pre{\hypertarget{ref-dreber2015}{}}%
@@
 doi:\href{https://doi.org/10.1016/j.joep.2018.10.009}{10.1016/j.joep.2018.10.009}
-
-\leavevmode\vadjust pre{\hypertarget{ref-frank2012}{}}%
-Frank MC, Saxe R (2012) Teaching {Replication}: \emph{Perspect Psychol Sci}. doi:\href{https://doi.org/10.1177/1745691612460686}{10.1177/1745691612460686}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-quintana2021}{}}%
-Quintana DS (2021) Replication studies for undergraduate theses to improve science and education.
-\emph{Nat Hum Behav} \textbf{5}:1117--1118.
-doi:\href{https://doi.org/10.1038/s41562-021-01192-8}{10.1038/s41562-021-01192-8}
-
 \leavevmode\vadjust pre{\hypertarget{ref-ramscar}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-wagge2019}{}}%
-Wagge JR, Brandt MJ, Lazarevic LB, Legate N, Christopherson C, Wiggins B, Grahe JE (2019) \href{https://www.frontiersin.org/articles/10.3389/fpsyg.2019.00247}{Publishing {Research With Undergraduate Students} via {Replication Work}: {The Collaborative Replications} and {Education Project}}.
-\emph{Front Psychol} \textbf{10}
-
 \leavevmode\vadjust pre{\hypertarget{ref-wilson2020}{}}%

### 2023-04-26 paper/supplement.Rmd
work on intro and figure 2

@@
 Per our pre-registration, we ran a set of 6 models crossing 3 outcome measures (subjective replication score, whether the replication result was within the prediction interval of the original, and p-original on the hypothesis that both came from the same distribution) with 2 sets of predictors (with or without statistical predictors).
-These 6 models required 3 tiers of data: the subjective replication score without statistical predictors applies to all the data; the p_original and prediction interval models apply to the subset of data with numeric outcomes that can be compared; and the statistical predictor models need the smaller subset of data with p-values and original SMD in particular.
+These 6 models required 3 tiers of data: the subjective replication score without statistical predictors applies to all the data; the p_original and prediction interval models apply to the subset of data with numeric outcomes that can be compared; and the statistical predictor models need the smaller subset of data with p-values and original standardized effect size in particular.
 
@@
     mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |>  filter(Term!="Intercept") |> 
-    mutate(Term=factor(Term, levels=c("subfieldsocial", "subfieldother_psych", "subfieldnon_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "z_pub_year", "z_log_trials", "z_log_sample", "z_log_ratio_ss","z_log_p","z_target_d_calc"), labels=c("Social", "Other psych", "Non psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rep/orig sample", "P-value", "SMD")))
+    mutate(Term=factor(Term, levels=c("subfieldsocial", "subfieldother_psych", "subfieldnon_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "z_pub_year", "z_log_trials", "z_log_sample", "z_log_ratio_ss","z_log_p","z_target_d_calc"), labels=c("Social", "Other psych", "Non psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rep/orig sample", "P-value", "Original effect size")))
 }

### 2023-04-26 paper/manuscript.Rmd
work on intro

@@
 
-introduction outline:
+<!--introduction outline:
 
@@
 * Correlational -- markets/etc say there is some predictive value to be had, but don't say if it's transparent and explainable. RP:P.
-   - Note that it's correlational, so can't do causality, but still useful for prediction, and as fodder for theory & intervention. (Interplay between them)
 
@@
 
+-->
 <!--
@@
 
-Questions:
-- mention primary outcome in intro? 
-- do we want to use the term p(cumulative)?
+# Introduction
 
-TODO fill in cites
-flesh out theoretical approaches section
-
-introduction outline:
-
-Things don't replicate that well and it feels like a problem for cumulative science 
 A cumulative science requires foundational empirical results that can be build upon in theories and future experiments.
@@
 
-* Theoretical -- we know people do bad practices and can model how this leads to lower replicability. Requires things we already have ideas about
-
 Theoretical approaches to understanding the replication rate have modeled how flexible research practices, selective reporting, and a bias toward positive results could lead to a high rate of (non-replicable) false positives (CITE).
@@
 
-What's missing from the conversation and why our approach is good. 
-* There's been a lot of discussion around replicabilty and it's role and yadda yadda (much overfocused on RP:P results because that's what's available).
-Growing sophistication and valid points, but we think it misses the mark about what practicing scientists are concerned about.
+Many of the discussions and reanalyses have raised questions about what the right metrics for measuring replicability are and what standards are reasonable to expect.
+Some of this contention is based around notions that failed replications are referenda on the truth of the original finding.
 
-What does replicability mean?
 Prior approaches to replicability have focused on interpreting results in terms of a potentially problematic estimand: the probability of a finding in the literature being somehow truly replicable.
@@
 How much we care about whether a study is "trustworthy" is not uniformly distributed across the literature.
-
-<!-- good below here -->
 

### 2023-04-26 paper/manuscript.tex
work on intro

@@
 
-introduction outline:
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
-Things don't replicate that well and it feels like a problem for cumulative science
-* For a cumulative science, we want (many) of the load-bearing empirical results that form the bases of theories to hold up.
-* People were acting as if publication of results meant they were true/reliable, trying to build on things; caused crises when some prominent results failed to replicate.
-Called into question reliability of literature as a whole -- lead to a few measurements.
-* Large scale replications of chunks of the literature, but aren't many (list and explain)
-* These rates feel lower than we want
+A cumulative science requires foundational empirical results that can be build upon in theories and future experiments.
+These load-bearing results need to be reliable; when they are not robust, attempts to build on them waste resources, trying to find explanations and effects where there may be none.
 
-Why? Many approaches, no definitive answers.
-* Why are rates what they are. Both want to know to fix but also to watch out / calibrate caution. Can be approached from theoretical, interventional, and correlational dimensions.
-* Theoretical -- we know people do bad practices and can model how this leads to lower replicability. Requires things we already have ideas about
-* Interventional -- try things they think will make it better (like not doing bad practices), see what happens. Not everything is intervention prone, need to have strong belief first. Expensive!
-* Correlational -- markets/etc say there is some predictive value to be had, but don't say if it's transparent and explainable. RP:P.
-- Note that it's correlational, so can't do causality, but still useful for prediction, and as fodder for theory \& intervention. (Interplay between them)
+Scientists, policymakers, and the public often treat publication as a signal that a result is (likely to be) true.
+This trust in published findings leads scientists to attempt to build on them, but failures to build on them are explained away and rarely published, leaving the original results uncontested in the literature, while failures accumulate in private.
 
-What's missing from the conversation and why our approach is good.
-* There's been a lot of discussion around replicabilty and it's role and yadda yadda (much overfocused on RP:P results because that's what's available).
-Growing sophistication and valid points, but we think it misses the mark about what practicing scientists are concerned about.
-* Don't want to build on something and fail a bunch trying to get your variant to work and then realize it just doesn't work.
-Replicability (as we mean it here) A useful framing is ``ability to do cumulative science'' -- close to what people mean, may disagree with many things
-* How this approach differs and what it gets us
-* (built in feasibility under reasonable / small resource constraints)
-* interest based sampling
-* functional approach sidesteps issues of ``truth'' (may even be reliable in a different environment, but would be)
+Publicized failures to replicate called into question the tacit assumption that most of the literature was robust and would replicate.
+Certain prominent findings turned out to not replicate at all {[}ex.
+terror management theory; Klein et al.
+(\protect\hyperlink{ref-klein2022}{2022}){]}, and a large scale replication project pegged the replication rate for findings in top-tier psychology journals at around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Consortium 2015}).
 
-Teaser:
-* We do x,y,z, and find that larger effect sizes and within subjects designs are the two strongest correlates of replicability in this sample.
-
-Questions:
-- mention primary outcome in intro?
-- switch out fig 4 for supp fig 2?
-- do we want to use the term p(cumulative)?
-
-TODO fill in cites
-flesh out theoretical approaches section
-
-introduction outline:
-
-Things don't replicate that well and it feels like a problem for cumulative science
-* For a cumulative science, we want (many) of the load-bearing empirical results that form the bases of theories to hold up.
-For a cumulative science, the empirical results that form the bases for theories and
-* People were acting as if publication of results meant they were true/reliable, trying to build on things; caused crises when some prominent results failed to replicate.
-Called into question reliability of literature as a whole -- lead to a few measurements.
-A major concern in psychology, as in other fields, is that the published literature may not replicate as well as had previously been assumed.
-This is illustrated both by a few prominent findings that turn out to not replicate at all {[}ex.
-terror management theory; Klein et al.
-(\protect\hyperlink{ref-klein2022}{2022}){]}, and by large-scale replication projects such as RP:P which found a replication rate around 40\% for a sample of the psychology literature (\protect\hyperlink{ref-openscienceconsortium2015}{Consortium 2015}).
-This low replication rates seems undesirable and seems to run counter to the idea of a cumulative science.
-
-\begin{itemize}
-\tightlist
-\item
-  Large scale replications of chunks of the literature, but aren't many (list and explain)
-  We are aware of three large-scale replication efforts replicating experimental results in the existing psychology literature.
+Few large scale replications have been conducted in psychology, due to the resources required to run large numbers of replication studies.
+We are aware of three.
 RP:P sampled roughly 100 studies from articles published in three top psychology journals in 2008 and found a overall replication rate of around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Consortium 2015}).
-The ManyLabs series of replications investigating heterogeneity has sampled target studies that are short and compare only two conditions, which is not representative of the psychology literature as a whole.
-Across Many Labs 1-3, 29 of 51 target effects (57\%) were found to replicate (\protect\hyperlink{ref-klein2014}{Klein et al.
+ManyLabs investigated heterogeneity using short target studies that compared between two conditions each, but these studies are not representative of the psychology literature as a whole.
+Across Many Labs 1-3, 29 of 51 target effects (57\%) replicated (\protect\hyperlink{ref-klein2014}{Klein et al.
 2014}, \protect\hyperlink{ref-ebersole2016}{Ebersole et al.
@@
 Camerer et al.
-(\protect\hyperlink{ref-camerer2018}{2018}) found a roughly 60\% replication rate when they replicated all 21 behaviors studies published in Nature and Science from 2010-2015 that did not require special populations or special equipment.
-Those are all the large-scale replication projects of experimental psychology results available at this time.
-These roughly 170 results are the primary empirical results discussions of replication in pschology have to rely are.
-\item
-  These rates feel lower than we want
-\end{itemize}
+(\protect\hyperlink{ref-camerer2018}{2018}) replicated all 21 behavioral social science studies from Nature and Science from 2010-2015 that were feasible; the replication rate was around 60\%.
+These roughly 170 replications of psychology studies are the primary empirical results on which discussions of replication rates in psychology are based.
 
-Why? Many approaches, no definitive answers.
-What makes the replication rates in psychology so low?
-Knowing what predicts and drives non-replications would let us potentially increase the replication rate, and also calibrate our levels of caution and skepticism toward results.
-Theoretical, interventional and correlational approaches do not yet provide comprehensive answers.
+A replication rate around 50\% runs counter to the prior assumption that most findings in the literature was robust enough to support cumulative science, and raises the question: What makes the replication rates in psychology so low?
 
-\begin{itemize}
-\tightlist
-\item
-  Theoretical -- we know people do bad practices and can model how this leads to lower replicability. Requires things we already have ideas about
-\end{itemize}
+Theoretical approaches to understanding the replication rate have modeled how flexible research practices, selective reporting, and a bias toward positive results could lead to a high rate of (non-replicable) false positives (CITE).
+However, while scientists admit to engaging in these practices, we don't yet know what proportion of non-replications are driven by these factors or how to identify these studies in the literature.
 
-Theoretical approaches modelling how questionable research practices (which many psychologists admit to) and a bias towards positive results would lead to a high rate of (non-replicable) false positives in the literature (CITE).
-There's some disconnect between these theoretically causal factors and empirical results about what causes or correlates with replicability.
-
-\begin{itemize}
-\item
-  Interventional -- try things they think will make it better (like not doing bad practices), see what happens. Not everything is intervention prone, need to have strong belief first. Expensive!
-  A couple studies have attempted to intervene on the low replication rate, but seeing if certain factors can affect whether studies replicate.
-For instance, across 16 studies, Protzko et al.
-(\protect\hyperlink{ref-protzko2020}{2020}) showed that better methodological practices, such as transparency, large sample sizes, and confirmatory tests, led to replication rates that matched theoretical expectations based on the effect sizes and sample sizes, and replication effect sizes comparable with the original.
+Experimental approaches attempt to intervene on the low replication rate, by seeing if changing certain factors affects whether studies replicate.
+Protzko et al.
+(\protect\hyperlink{ref-protzko2020}{2020}) showed, across 16 studies, that better methodological practices, such as transparency, large sample sizes, and confirmatory tests, led to replication rates that matched theoretical expectations based on the effect sizes and sample sizes, with replication effect sizes comparable with the original.
 Many Labs 5 examined how adding expert advice to a replication process might intervene to improve the replicate rate, and found that it mostly didn't, at least on the 10 studies they looked at (\protect\hyperlink{ref-ebersole2020}{Ebersole et al.
 2020}).
-These types of experiments are valuable, but they aren't very scalable because they are expensive and some potential influences on non-replication are not experimentally manipulable.
-\item
-  Correlational -- markets/etc say there is some predictive value to be had, but don't say if it's transparent and explainable. RP:P.
-  Much of the work looking at predictors of replicability has been correlational.
+These types of experiments are valuable for testing potential causes of non-replication, but they don't scale well do to expense.
+Additionally, not all potential influences on non-replication are experimentally manipulable.
+
+Correlational approaches looking for predictors of replicability are the most popular.
 Prediction markets and elicitations have established that people can predict what studies will replicate above chance (\protect\hyperlink{ref-dreber2015}{Dreber et al.
@@
 Machine learning approaches CITE similarly show predictive signal, but do not provide explainable predictor variables.
-In the RP:P sample, studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate CITE .
-All of these correlational approaches depend on data from replications, generally drawing heavily from the same small set of large-scale replication data points.
+(\protect\hyperlink{ref-opensicenceconsortium2015}{\textbf{opensicenceconsortium2015?}}) looked for simple correlates of replicability in the RP:P sample and found that studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate.
+Correlations approaches depend on data from replications, generally drawing heavily from the same small set of data points.
 In particular, the RP:P dataset itself is much discussed and reanalyzed (\protect\hyperlink{ref-anderson2016}{Anderson et al.
@@
 2016}, \protect\hyperlink{ref-patil2016}{Patil et al.
-2016}), so much of what we think we know about replicability may be overfit to the 100 studies included in in RP:P.
+2016}) to the point that much of what we think we know about replicability may be overfit to the 100 studies included in in RP:P.
 
-  \begin{itemize}
-  \tightlist
-  \item
-    Note that it's correlational, so can't do causality, but still useful for prediction, and as fodder for theory \& intervention. (Interplay between them)
-  \end{itemize}
-\end{itemize}
+Many of the discussions and reanalyses have raised questions about what the right metrics for measuring replicability are and what standards are reasonable to expect.
+Some of this contention is based around notions that failed replications are referenda on the truth of the original finding.
 
-What's missing from the conversation and why our approach is good.
-* There's been a lot of discussion around replicabilty and it's role and yadda yadda (much overfocused on RP:P results because that's what's available).
-Growing sophistication and valid points, but we think it misses the mark about what practicing scientists are concerned about.
-
-What does replicability mean?
 Prior approaches to replicability have focused on interpreting results in terms of a potentially problematic estimand: the probability of a finding in the literature being somehow truly replicable.
@@
 \begin{figure}[ht]
-\includegraphics[width=1\linewidth,height=0.25\textheight]{manuscript_files/figure-latex/mod-results-1} \caption{Coefficient estimates and uncertainty from a model predicting subjective replication scores from the full dataset.}\label{fig:mod-results}
+\includegraphics[width=0.9\linewidth]{manuscript_files/figure-latex/mod-results-1} \caption{Coefficient estimates and uncertainty from a model predicting subjective replication scores from the full dataset.}\label{fig:mod-results}
 \end{figure}

### 2023-04-27 paper/manuscript.Rmd
work on abstract and intro

@@
 ::: {.abstract data-latex="" lang=en}
-
-A cumulative science relies on knowing how much to trust published findings.
-Large-scale replication studies provide a measure of how reliable the published literature in a field is by determining what fraction of studies replicate.
-Because of the effort involved in conducting a large number of replications, few large-scale replications are available.
-We add 176 replication projects conducted by students of experimental studies primarily in psychology.
-Roughly half the studies were replicated successfully, and we report how features of the studies and the replications influenced the replication outcome.
+A cumulative science requires foundational empirical results that are robust enough to support  theories and future experiments.
+Prominent failed replications of well-known published findings cast doubt on the psychological literature, and large scale replication projects suggested that the overall replication rate in psychology might be between 40-60%.
+Large-scale replications are arduous, and only around 170 replications have been conducted as part of a large-scale replication project.
+This dearth of data points limits estimations of replicability and analyses of potential correlates of replicability.
+Using a new sample of 176 replications conducted as part of a course, we estimate replicability of these studies that were of interest to graduate students.
+We look at statistical and experimental-design features of studies as potential predictors of replication.
+We find that within-study designs and large original effect sizes positively correlate with replicability.
 
@@
 
-A cumulative science requires foundational empirical results that can be build upon in theories and future experiments.
-These load-bearing results need to be reliable; when they are not robust, attempts to build on them waste resources, trying to find explanations and effects where there may be none.
+A cumulative science requires foundational empirical results that are robust enough to support  theories and future experiments.
+If scientists attempt to build cumulative science on top of results that are unreliable and cannot be achieved consistently, they waste resources looking for results where there may be none.
+This is frustrating for individual scientists, but also damaging to the enterprise of science overall.
 
-Scientists, policymakers, and the public often treat publication as a signal that a result is (likely to be) true.
-This trust in published findings leads scientists to attempt to build on them, but failures to build on them are explained away and rarely published, leaving the original results uncontested in the literature, while failures accumulate in private.
+Scientists, policymakers, and the public often treat publication in a scientific journal as a signal that a result is (likely to be) true.
+This trust in published findings has led scientists to build on findings without verifying them first, but failures were often explained away and rarely published, leaving the original results uncontested in the literature, while failures to achieve the same outcomes accumulated in private.
 
-Publicized failures to replicate called into question the tacit assumption that most of the literature was robust and would replicate.
-Certain prominent findings turned out to not replicate at all [ex.
-terror management theory; @klein2022], and a large scale replication project pegged the replication rate for findings in top-tier psychology journals at around 40% [@openscienceconsortium2015].
+During the replication crisis, publicized failures to replicate published findings called into question the tacit assumption that most of the literature was robust and would replicate.
+Certain prominent findings failed to replicate in multi-site replication attempts [ex.
+terror management theory, @klein2022; ego-depletion, @hagger2016], and a large-scale replication project pegged the replication rate for findings in top-tier psychology journals at around 40% [@openscienceconsortium2015].
 
+How replicable is psychology as a whole?
 Few large scale replications have been conducted in psychology, due to the resources required to run large numbers of replication studies.
@@
 
-A replication rate around 50% runs counter to the prior assumption that most findings in the literature was robust enough to support cumulative science, and raises the question: What makes the replication rates in psychology so low?
+A replication rate around 50% runs counter to the prior assumption that most findings in the literature were robust enough to support cumulative science, and it raises the question: What makes the replication rates in psychology so low?
 
@@
 
-Experimental approaches attempt to intervene on the low replication rate, by seeing if changing certain factors affects whether studies replicate.
+Experimental approaches attempt to intervene on the low replication rate, by changing certain factors that may affect whether studies replicate.
 @protzko2020 showed, across 16 studies, that better methodological practices, such as transparency, large sample sizes, and confirmatory tests, led to replication rates that matched theoretical expectations based on the effect sizes and sample sizes, with replication effect sizes comparable with the original.
-Many Labs 5 examined how adding expert advice to a replication process might intervene to improve the replicate rate, and found that it mostly didn't, at least on the 10 studies they looked at [@ebersole2020].
-These types of experiments are valuable for testing potential causes of non-replication, but they don't scale well do to expense.
+Many Labs 5 examined how adding expert advice to a replication process might increase the replication rate, and found that it mainly did not for the 10 studies they looked at [@ebersole2020].
+These types of experiments are valuable for testing potential causes of non-replication, but they don't scale well due to expense.
 Additionally, not all potential influences on non-replication are experimentally manipulable.
@@
 Correlational approaches looking for predictors of replicability are the most popular.
-Prediction markets and elicitations have established that people can predict what studies will replicate above chance [@hoogeveen2019;@dreber2015; @forsell2019;@camerer2018], but have not identified many concrete predictors that differentiate replications from non-replications.
-Machine learning approaches CITE similarly show predictive signal, but do not provide explainable predictor variables.
-@opensicenceconsortium2015 looked for simple correlates of replicability in the RP:P sample and found that studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate.
-Correlations approaches depend on data from replications, generally drawing heavily from the same small set of data points.
+Prediction markets and elicitations have established that people can predict what studies will replicate above chance [@hoogeveen2019;@dreber2015; @forsell2019;@camerer2018], but have not identified concrete predictors that differentiate replications from non-replications.
+Using machine learning approaches, @altmejd2019 found that sample size, effect size, and simple effects were predictive of replication.
+@openscienceconsortium2015 looked at simple correlates of replicability in the RP:P sample and found that studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate.
+Correlational approaches depend on data from replications, generally drawing heavily from the same small set of data points.
 In particular, the RP:P dataset itself is much discussed and reanalyzed [@etz2016;@gilbert2016;@patil2016;@anderson2016] to the point that much of what we think we know about replicability may be overfit to the 100 studies included in in RP:P.
@@
 These are reasonable sampling choices, but they undermine the claim that the estimand is the level of "truth" in the literature as a whole.
-Sampling truely at random from the literature may not even be desirable, as  arguably a literature will succeed if useful discoveries come out of it, not if random findings are true [@wilson2020].
-How much we care about whether a study is "trustworthy" is not uniformly distributed across the literature.
+Sampling truly at random from the literature may not even be desirable, as arguably a literature will succeed if useful discoveries come out of it, not if random findings are true [@wilson2020].
+The importance of a study being replicable is not uniformly distributed across the literature.
 
-In contrast, we have explicitly pursued a different estimand: the probability that a researcher, on selecting a finding of interest from the literature, can successfully achieve a result satisfactorily close enough to the original that they can build on it in their own work, with all the necessary compromises to the methods and sample of the original that may be required by the constraints of the situation.
+In contrast to prior approaches, we have explicitly pursued a different estimand: the probability that a researcher, on selecting a finding of interest from the literature, can successfully achieve a result satisfactorily close enough to the original that they can build on it in their own work, with all the necessary compromises to the methods and sample of the original that may be required by the constraints of the situation.
 
-This framing of replicability matches our methodology.
-
+Our methodology is reflective of this framing of replicability as being the probability of a studying being able to support cumulative science.
 Rather than sampling at random from some parts of the literature; our sample of studies is selected based on what studies students were interested in and wanting to replicate, with some filtering for feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable given methodological and budgetary constraints.
@@
 replication is p<.05 same direction as original).
-This avoids bright line distinctions and accomodates the range of outcome measures in our diverse set of studies.
+This metric avoids bright line distinctions and accommodates the range of outcome measures in our diverse set of studies.
 
@@
 The same issue that may cause a study not to replicate under constrained circumstances (despite hypothetically replicating under more favorable circumstances such as expert administration or larger budgets) will also plague attempts to build off those studies in constrained circumstances.
-Thus, we believe it is relevant to estimate replicability as done by a graduate student with limited resources.
+Thus, we believe it is relevant to estimate replicability under the limitations of real world resource and expertise constraints.
 
@@
 These replications were conducted by students in graduate-level experimental methods class between 2011 and 2022 as individual course projects.
-We investigated predictors of replicability in this dataset and found that within-subjects designs and studies with large standardized effect sizes were positively correlated with replication success.
+We investigated statistical and experimental-design predictors of replicability in this dataset and found that within-subjects designs and studies with large standardized effect sizes were positively correlated with replication success.
 
@@
 Replications that switched to online were less likely to replicate than those that had the same modality as the original (generally both online, in a few cases both in-person).
-While online studies in general show comparable results to studies conducted in person [@crump2013]TODO MORE CITATIONS, switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well adapted (ex.
+While online studies in general show comparable results to studies conducted in person [@crump2013], switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well adapted (ex.
 inductions may be weaker or attention checks inadequate to the new sample).
@@
 
-```{r mod-results, out.width="90%", fig.width=8, fig.height=5, fig.pos="ht", fig.cap="Coefficient estimates and uncertainty from a model predicting subjective replication scores from the full dataset."}
+```{r mod-results, out.width="90%", fig.width=8, fig.height=5, fig.pos="ht", fig.cap="Coefficients and uncertaintly estimates from a model of all predictors (N=112, shown in blue) and non-statistical predictors (N=176, shown in red) predicting subjective replication scores as the dependent variable.
+"}
 
@@
 
-tier1_subjective <- read_rds(here(model_location, "tier1_subjective.rds")) |> do_draws() |> mutate(type="Without stats predictors") |> mutate(sens="All data")
-tier3_subjective <- read_rds(here(model_location, "tier3_subjective.rds"))|> do_draws() |> mutate(type="With stats predictors") |> mutate(sens="All data")
+tier1_subjective <- read_rds(here(model_location, "tier1_subjective.rds")) |> do_draws() |> mutate(type="Non-statistical predictors only") |> mutate(sens="All data")
+tier3_subjective <- read_rds(here(model_location, "tier3_subjective.rds"))|> do_draws() |> mutate(type="All predictors") |> mutate(sens="All data")
 
@@
   scale_color_solarized()+
-  stat_pointinterval(position=position_dodge(width=.7))+labs(y="", x="Estimate, 66%, 95% CrI predicting subjective replication score", color="", linetype="", shape="")+theme(axis.text=element_text(size=11),legend.position="bottom")
+  stat_pointinterval(position=position_dodge(width=.7))+labs(y="", x="Estimate, 66%, 95% CrI predicting subjective replication score", color="", linetype="", shape="")+theme(axis.text=element_text(size=11),legend.position="none")
 
@@
 
-The replication rate in psychology is to the best estimates, somewhere around 50%, which is quite low.
+The replication rate in psychology is, to the best estimates, somewhere around 50%, which is quite low.
 Many reasons for this low replication rate have been hypothesized, but studying it either experimentally or correlationally requires doing a number of replication experiments, which can be a lot of work.
@@
 The replication studies were not designed from the start with this analysis in mind, so analysis is limited by the choices and reporting used at the time of replications.
-TODO what are the limitations we want?
+We reiterate that given our sample, we are able to estimate the correlates of studies replicating when the replications are conducted online, by graduate students with limited time and budget.
+This estimand is not the same as whether they would replicate when done by large labs with access to more money and experts.
+This estimand does not represent whether or not the original study was "true".
 
-TODO quick wrap up
+TODO conclusion
 

### 2023-04-27 paper/manuscript.tex
work on abstract and intro

@@
 \begin{abstract}
-A cumulative science relies on knowing how much to trust published findings.
-Large-scale replication studies provide a measure of how reliable the published literature in a field is by determining what fraction of studies replicate.
-Because of the effort involved in conducting a large number of replications, few large-scale replications are available.
-We add 176 replication projects conducted by students of experimental studies primarily in psychology.
-Roughly half the studies were replicated successfully, and we report how features of the studies and the replications influenced the replication outcome.
+A cumulative science requires foundational empirical results that are robust enough to support theories and future experiments.
+Prominent failed replications of well-known published findings cast doubt on the psychological literature, and large scale replication projects suggested that the overall replication rate in psychology might be between 40-60\%.
+Large-scale replications are arduous, and only around 170 replications have been conducted as part of a large-scale replication project.
+This dearth of data points limits estimations of replicability and analyses of potential correlates of replicability.
+Using a new sample of 176 replications conducted as part of a course, we estimate replicability of these studies that were of interest to graduate students.
+We look at statistical and experimental-design features of studies as potential predictors of replication.
+We find that within-study designs and large original effect sizes positively correlate with replicability.
 
@@
 
-A cumulative science requires foundational empirical results that can be build upon in theories and future experiments.
-These load-bearing results need to be reliable; when they are not robust, attempts to build on them waste resources, trying to find explanations and effects where there may be none.
+A cumulative science requires foundational empirical results that are robust enough to support theories and future experiments.
+If scientists attempt to build cumulative science on top of results that are unreliable and cannot be achieved consistently, they waste resources looking for results where there may be none.
+This is frustrating for individual scientists, but also damaging to the enterprise of science overall.
 
-Scientists, policymakers, and the public often treat publication as a signal that a result is (likely to be) true.
-This trust in published findings leads scientists to attempt to build on them, but failures to build on them are explained away and rarely published, leaving the original results uncontested in the literature, while failures accumulate in private.
+Scientists, policymakers, and the public often treat publication in a scientific journal as a signal that a result is (likely to be) true.
+This trust in published findings has led scientists to build on findings without verifying them first, but failures were often explained away and rarely published, leaving the original results uncontested in the literature, while failures to achieve the same outcomes accumulated in private.
 
-Publicized failures to replicate called into question the tacit assumption that most of the literature was robust and would replicate.
-Certain prominent findings turned out to not replicate at all {[}ex.
-terror management theory; Klein et al.
-(\protect\hyperlink{ref-klein2022}{2022}){]}, and a large scale replication project pegged the replication rate for findings in top-tier psychology journals at around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Consortium 2015}).
+During the replication crisis, publicized failures to replicate published findings called into question the tacit assumption that most of the literature was robust and would replicate.
+Certain prominent findings failed to replicate in multi-site replication attempts (ex.
+terror management theory, \protect\hyperlink{ref-klein2022}{Klein et al.
+2022}, ego-depletion, \protect\hyperlink{ref-hagger2016}{Hagger et al.
+2016}), and a large-scale replication project pegged the replication rate for findings in top-tier psychology journals at around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}).
 
+How replicable is psychology as a whole?
 Few large scale replications have been conducted in psychology, due to the resources required to run large numbers of replication studies.
 We are aware of three.
-RP:P sampled roughly 100 studies from articles published in three top psychology journals in 2008 and found a overall replication rate of around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Consortium 2015}).
+RP:P sampled roughly 100 studies from articles published in three top psychology journals in 2008 and found a overall replication rate of around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}).
 ManyLabs investigated heterogeneity using short target studies that compared between two conditions each, but these studies are not representative of the psychology literature as a whole.
@@
 
-A replication rate around 50\% runs counter to the prior assumption that most findings in the literature was robust enough to support cumulative science, and raises the question: What makes the replication rates in psychology so low?
+A replication rate around 50\% runs counter to the prior assumption that most findings in the literature were robust enough to support cumulative science, and it raises the question: What makes the replication rates in psychology so low?
 
@@
 
-Experimental approaches attempt to intervene on the low replication rate, by seeing if changing certain factors affects whether studies replicate.
+Experimental approaches attempt to intervene on the low replication rate, by changing certain factors that may affect whether studies replicate.
 Protzko et al.
 (\protect\hyperlink{ref-protzko2020}{2020}) showed, across 16 studies, that better methodological practices, such as transparency, large sample sizes, and confirmatory tests, led to replication rates that matched theoretical expectations based on the effect sizes and sample sizes, with replication effect sizes comparable with the original.
-Many Labs 5 examined how adding expert advice to a replication process might intervene to improve the replicate rate, and found that it mostly didn't, at least on the 10 studies they looked at (\protect\hyperlink{ref-ebersole2020}{Ebersole et al.
+Many Labs 5 examined how adding expert advice to a replication process might increase the replication rate, and found that it mainly did not for the 10 studies they looked at (\protect\hyperlink{ref-ebersole2020}{Ebersole et al.
 2020}).
-These types of experiments are valuable for testing potential causes of non-replication, but they don't scale well do to expense.
+These types of experiments are valuable for testing potential causes of non-replication, but they don't scale well due to expense.
 Additionally, not all potential influences on non-replication are experimentally manipulable.
@@
 2019}, \protect\hyperlink{ref-hoogeveen2019}{Hoogeveen et al.
-2019}), but have not identified many concrete predictors that differentiate replications from non-replications.
-Machine learning approaches CITE similarly show predictive signal, but do not provide explainable predictor variables.
-(\protect\hyperlink{ref-opensicenceconsortium2015}{\textbf{opensicenceconsortium2015?}}) looked for simple correlates of replicability in the RP:P sample and found that studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate.
-Correlations approaches depend on data from replications, generally drawing heavily from the same small set of data points.
+2019}), but have not identified concrete predictors that differentiate replications from non-replications.
+Using machine learning approaches, Altmejd et al.
+(\protect\hyperlink{ref-altmejd2019}{2019}) found that sample size, effect size, and simple effects were predictive of replication.
+Open Science Consortium (\protect\hyperlink{ref-openscienceconsortium2015}{2015}) looked at simple correlates of replicability in the RP:P sample and found that studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate.
+Correlational approaches depend on data from replications, generally drawing heavily from the same small set of data points.
 In particular, the RP:P dataset itself is much discussed and reanalyzed (\protect\hyperlink{ref-anderson2016}{Anderson et al.
@@
 These are reasonable sampling choices, but they undermine the claim that the estimand is the level of ``truth'' in the literature as a whole.
-Sampling truely at random from the literature may not even be desirable, as arguably a literature will succeed if useful discoveries come out of it, not if random findings are true (\protect\hyperlink{ref-wilson2020}{Wilson et al.
+Sampling truly at random from the literature may not even be desirable, as arguably a literature will succeed if useful discoveries come out of it, not if random findings are true (\protect\hyperlink{ref-wilson2020}{Wilson et al.
 2020}).
-How much we care about whether a study is ``trustworthy'' is not uniformly distributed across the literature.
+The importance of a study being replicable is not uniformly distributed across the literature.
 
-In contrast, we have explicitly pursued a different estimand: the probability that a researcher, on selecting a finding of interest from the literature, can successfully achieve a result satisfactorily close enough to the original that they can build on it in their own work, with all the necessary compromises to the methods and sample of the original that may be required by the constraints of the situation.
+In contrast to prior approaches, we have explicitly pursued a different estimand: the probability that a researcher, on selecting a finding of interest from the literature, can successfully achieve a result satisfactorily close enough to the original that they can build on it in their own work, with all the necessary compromises to the methods and sample of the original that may be required by the constraints of the situation.
 
-This framing of replicability matches our methodology.
-
+Our methodology is reflective of this framing of replicability as being the probability of a studying being able to support cumulative science.
 Rather than sampling at random from some parts of the literature; our sample of studies is selected based on what studies students were interested in and wanting to replicate, with some filtering for feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable given methodological and budgetary constraints.
@@
 replication is p\textless.05 same direction as original).
-This avoids bright line distinctions and accomodates the range of outcome measures in our diverse set of studies.
+This metric avoids bright line distinctions and accommodates the range of outcome measures in our diverse set of studies.
 
@@
 Replications that switched to online were less likely to replicate than those that had the same modality as the original (generally both online, in a few cases both in-person).
-While online studies in general show comparable results to studies conducted in person (\protect\hyperlink{ref-crump2013}{\textbf{crump2013?}})TODO MORE CITATIONS, switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well adapted (ex.
+While online studies in general show comparable results to studies conducted in person (\protect\hyperlink{ref-crump2013}{Crump et al.
+2013}), switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well adapted (ex.
 inductions may be weaker or attention checks inadequate to the new sample).
@@
 \begin{figure}[ht]
-\includegraphics[width=0.9\linewidth]{manuscript_files/figure-latex/mod-results-1} \caption{Coefficient estimates and uncertainty from a model predicting subjective replication scores from the full dataset.}\label{fig:mod-results}
+\includegraphics[width=0.9\linewidth]{manuscript_files/figure-latex/mod-results-1} \caption{Coefficients and uncertaintly estimates from a model of all predictors (N=112, shown in blue) and non-statistical predictors (N=176, shown in red) predicting subjective replication scores as the dependent variable.
+}\label{fig:mod-results}
 \end{figure}
@@
 
-The replication rate in psychology is to the best estimates, somewhere around 50\%, which is quite low.
+The replication rate in psychology is, to the best estimates, somewhere around 50\%, which is quite low.
 Many reasons for this low replication rate have been hypothesized, but studying it either experimentally or correlationally requires doing a number of replication experiments, which can be a lot of work.
@@
 The replication studies were not designed from the start with this analysis in mind, so analysis is limited by the choices and reporting used at the time of replications.
-TODO what are the limitations we want?
+We reiterate that given our sample, we are able to estimate the correlates of studies replicating when the replications are conducted online, by graduate students with limited time and budget.
+This estimand is not the same as whether they would replicate when done by large labs with access to more money and experts.
+This estimand does not represent whether or not the original study was ``true''.
 
-TODO quick wrap up
+TODO conclusion
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-altmejd2019}{}}%
+Altmejd A, Dreber A, Forsell E, Huber J, Imai T, Johannesson M, Kirchler M, Nave G, Camerer C (2019) Predicting the replicability of social science lab experiments.
+\emph{PLOS ONE} \textbf{14}:e0225826.
+doi:\href{https://doi.org/10.1371/journal.pone.0225826}{10.1371/journal.pone.0225826}
+
 \leavevmode\vadjust pre{\hypertarget{ref-anderson2016}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-openscienceconsortium2015}{}}%
-Consortium OS (2015) \href{https://www.science.org/doi/full/10.1126/science.aac4716?casa_token=IJ35TwwlcjsAAAAA\%3AqiP68QbVAHleIg9zD3WugKWuV6Oa5rswS0VQnDsCq5I14ME4WIQabNGVD_T6SBSuAt6voVHNnWc0sw}{Estimating the reproducibility of psychological science}.
-\emph{Science}
+\leavevmode\vadjust pre{\hypertarget{ref-crump2013}{}}%
+Crump MJC, McDonnell JV, Gureckis TM (2013) Evaluating amazon's mechanical turk as a tool for experimental behavioral research.
+\emph{{PLOS} {ONE}} \textbf{8}:e57410.
+doi:\href{https://doi.org/10.1371/journal.pone.0057410}{10.1371/journal.pone.0057410}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-hagger2016}{}}%
+Hagger MS, Chatzisarantis NLD, Alberts H, Anggono CO, Batailler C, Birt AR, Brand R, Brandt MJ, Brewer G, Bruyneel S, Calvillo DP, Campbell WK, Cannon PR, Carlucci M, Carruth NP, Cheung T, Crowell A, De Ridder DTD, Dewitte S, Elson M, Evans JR, Fay BA, Fennis BM, Finley A, Francis Z, Heise E, Hoemann H, Inzlicht M, Koole SL, Koppel L, Kroese F, Lange F, Lau K, Lynch BP, Martijn C, Merckelbach H, Mills NV, Michirev A, Miyake A, Mosser AE, Muise M, Muller D, Muzi M, Nalis D, Nurwanti R, Otgaar H, Philipp MC, Primoceri P, Rentzsch K, Ringos L, Schlinkert C, Schmeichel BJ, Schoch SF, Schrama M, Schütz A, Stamos A, Tinghög G, Ullrich J, vanDellen M, Wimbarti S, Wolff W, Yusainy C, Zerhouni O, Zwienenberg M (2016) A multilab preregistered replication of the ego-depletion effect.
+\emph{Perspect Psychol Sci} \textbf{11}:546--573.
+doi:\href{https://doi.org/10.1177/1745691616652873}{10.1177/1745691616652873}
+
 \leavevmode\vadjust pre{\hypertarget{ref-hawkins}{}}%
@@
 doi:\href{https://doi.org/10.1111/rssa.12572}{10.1111/rssa.12572}
+
+\leavevmode\vadjust pre{\hypertarget{ref-openscienceconsortium2015}{}}%
+Open Science Consortium (2015) \href{https://www.science.org/doi/full/10.1126/science.aac4716?casa_token=IJ35TwwlcjsAAAAA\%3AqiP68QbVAHleIg9zD3WugKWuV6Oa5rswS0VQnDsCq5I14ME4WIQabNGVD_T6SBSuAt6voVHNnWc0sw}{Estimating the reproducibility of psychological science}.
+\emph{Science}
 

### 2023-04-27 paper/manuscript.Rmd
tweaks to paper

@@
 PSYCH 251 is Stanford Psychology's graduate-level experimental methods class taught by MCF.
-During the 10 week class, students replicate a published finding.
-They individually re-implement the study, write analysis code, pre-register their study, collect data using an online platform, and write up a structured replication report.
-Students are free to choose studies related to their research interests, with the default recommendation being an article from a recent year of Psychological Science.
-While this choice results in a non-random sample from the literature, the sample is representative of studies that are of interest to and doable by first year graduate students.
+During the 10 week class, students replicated a published finding.
+They individually re-implemented the study, wrote analysis code, pre-registered their study, collected data using an online platform, and wrote up a structured replication report.
+Students were free to choose studies related to their research interests, with the default recommendation being an article from a recent year of Psychological Science.
+The resultant sample of studies is not a random sample from the literature but is representative of studies that are of interest to and doable by first year graduate students.
 
-The sample of replicated studies reflects the variability of the literature, including studies from different subfields, using different experimental methods and statistical outcomes.
-We leverage the naturally occurring variability in this sample of replications to examine how different demographic, experimental design, and statistical properties predict replication success.
+The sample of replicated studies reflect the variability of the literature, including studies from different subfields, using different experimental methods and statistical outcomes.
+We leveraged the naturally occurring variability in this sample of replications to examine how different demographic, experimental design, and statistical properties predict replication success.
 
-Many different measures can be used to define replication success of an individual statistical result, and there is much discussion over what each measure represents and which make sense [@simonsohn2015; @gelman2018; @mathur2020].
+Many different measures can be used to define replication success of an individual statistical result [@simonsohn2015; @gelman2018; @mathur2020].
 Because we operationalized replicability as whether a study could be built upon, we used a subjective rating of replication success as our primary outcome measure.
-This measure has the benefit that it was applicable across the diverse range of statistical measures and reporting practices present in the sample.
+This measure was applicable across the diverse range of statistical measures and reporting practices present in the sample.
 It, unlike statistical measures of replication, could easily accommodate studies where there were multiple important outcome measures that together defined the pattern of interest.
@@
 We measured p-original, the p-value on the null hypothesis that the original and replication statistics are from the same distribution, as a continuous variable, and we also determined whether the replication statistic fell within the prediction interval of the original statistic [@errington2021].
-These both measure how similar the estimates from the two sets of data are.
+These both measure how similar the outcome estimates from the two sets of data are.
 
@@
 porig_rate <- d |> filter(!is.na(p_orig)) |> summarize(m=median(p_orig))
+
+d |> filter(!is.na(predInt)) |> filter(predInt) |> nrow() -> predIntcount
+d |> filter(!is.na(predInt)) |> nrow() -> predInttotal
+
 ```
@@
 Across the 176 studies, the overall subjective replication rate was `r round(pluck(sub_rep_rate,1))`%.
-`r round(pluck(pred_int_rate,1))`% (N=FOOBAR) of the studies had replication outcomes within the prediction interval of the original outcome.
+`r round(pluck(pred_int_rate,1))`% (`r predIntcount`/`r predInttotal`) of the studies had replication outcomes within the prediction interval of the original outcome.
 The median p_original value was `r round(pluck(porig_rate, 1),2)`.
-Figure \ref{fig:smd} shows the relationship between original SMD, replication SMD, and subjective replication score.
+Figure \ref{fig:smd} shows the relationship between original standardized effect size, replication effect size, and subjective replication score.
 Roughly speaking, there's a cluster of studies that replicate with similar effect sizes to the original and another cluster that fail to replicate with replication effect sizes near zero.
@@
 Properties of both the original study and the replication can influence whether or not the replication is a success.
-We chose a set of predictor variables from the correlational results of RP:P and our own intuitions about experimental factors that might impact replication success as well as some covariates related to how close the replication would be.
-A full description of these features is given in methods.
+We chose a set of predictor variables from the correlational results of RP:P and our own intuitions about experimental factors that might impact replication success as well as some covariates related to how close the replication was.
+A full description of these features is given in Methods.
 
-Many of these predictors individually correlate with subjective replication success (Table \ref{tab:cor}).
-Predictors of higher replicability included within-subjects designs, higher numbers of trials, and open data.
-Predictors of lower replicability included single vignetted studies, social psychology studies, and original-replication pairs where the replication switched to online.
+Many predictors individually correlate with subjective replication success (Table \ref{tab:cor}).
+Predictors of higher replicability included within-subjects designs, higher numbers of trials, and the original study having open data.
+Predictors of lower replicability included single vignetted studies, social psychology studies, and original-replication pairs where the original study was in-person and replication switched to online.
 
@@
 Both social and cognitive psychology studies were well represented, and the cognitive psychology studies replicated at `r round(1/subfield, 2)` times the rate of social psychology studies.
-Within and between subjects designs were both common, and within replicated `r within |> round(2)` times as much.
+Within and between subjects designs were both common, and within-subjects designs replicated `r within |> round(2)` times as much.
 Similarly, studies with multiple vignettes replicated `r round(1/vignette, 2)` times more than single vignetted studies.
 However, there were strong correlations among these experimental features and between these experimental features and subfield.
-
 Studies with open data, which almost always also had open materials, tended to replicate more than studies without open data, although this may be linked to temporal trends.
@@
 Replications that switched to online were less likely to replicate than those that had the same modality as the original (generally both online, in a few cases both in-person).
-While online studies in general show comparable results to studies conducted in person [@crump2013], switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well adapted (ex.
+While online studies in general show comparable results to studies conducted in person [@crump2013], switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well-adapted (ex.
 inductions may be weaker or attention checks inadequate to the new sample).
@@
 ## Regression model
-While a number of the predictors show individual correlations with the subjective replication score, many of the predictors are also correlated with one another.
+While a number of predictors show individual correlations with the subjective replication score, many of the predictors also correlate with one another.
 In order to determine which predictors were the strongest, we ran a series of pre-registered regularized regression models (see Methods for details; see Supplement for all estimates from all models).
-The coefficient estimates of the primary model, predicting the subjective replication scores based on all the data, are shown in Figure \ref{fig:mod-results}.
+We ran models both using all the data, but without statistical predictors (that were uncodable for some studies) and models including statistical predictors, but limiting to the subset of data where all predictors were available.
+The coefficient estimates from two models predicting the subjective replication scores are shown in Figure \ref{fig:mod-results}.
 Due to a large number of predictors coupled with a small and noisy dataset, even with strong regularization, there is much uncertainty around the coefficients.
@@
 
-We also ran models predicting whether the replication effect was within the prediction interval as the original effect and what the p-original was between the replication and original.
+We also ran models predicting our secondary outcome measures: whether the replication effect was within the prediction interval as the original effect and what the p-original was between the replication and original.
 Both these models had even more uncertain estimates.
-While the credible intervals are wide, the general patterns of predictors are similar to the subjective replication models.
-The strongest predictors are still within-subjects designs (`r within_2`) and studies with larger effect sizes (`r smd_2`).
+While the credible intervals were wide, the general patterns of predictor direction and relative strength were similar to the subjective replication models.
+The strongest predictors were still within-subjects designs (`r within_2`) and studies with larger effect sizes (`r smd_2`).
 
@@
 # Discussion
+Prior large scale replications of psychology findings have estimated the replication rate at somewhere around 50%.
+This rate feels low, raising the question of what is causing so many studies not to replicate.
+However, limited numbers of replications and limited research into specific predictors of replication failure leave this an open question.
 
-The replication rate in psychology is, to the best estimates, somewhere around 50%, which is quite low.
-Many reasons for this low replication rate have been hypothesized, but studying it either experimentally or correlationally requires doing a number of replication experiments, which can be a lot of work.
 Here we took advantage of 11 years of graduate student replication projects to look at correlational predictors of replication in a previously-unused dataset.
 
-In line with previous replications, we found a FOOBAR replication rate, with some studies showing effect sizes similar to the original and others much smaller.
-Some individual correlates of replicability that stood out included within-subjects designs, work in the subfield of cognitive psychology, and the original and replication both using online samples.
-Many of these correlates interrelate with one another, and we are still limited in our sample, so models with multiple predictors have a lot of uncertainty around the effects of each predictor.
+In line with previous results, we found a ` rround(pluck(sub_rep_rate,1))`% replication rate, with some studies showing effect sizes similar to the original and others much smaller.
+When we looked at individual correlates of replicability, within-subjects designs, work in the subfield of cognitive psychology, and the original and replication both using online samples stood out as the strongest correlates.
+As many of these predictors interrelate with one another, we ran regularized regressions with all the predictors at once.
+Due to our small sample, model estimates were uncertain, but within-subjects designs and large original effect sizes were the strongest predictors.
 
-We are explicit in our goal of estimating how likely it is that a first-year graduate student, attempting to replicate a study of interest to them, gets replication results which are consistent enough with the original results that the student could build on the study in their own work.
+<!--We are explicit in our goal of estimating how likely it is that a first-year graduate student, attempting to replicate a study of interest to them, gets replication results which are consistent enough with the original results that the student could build on the study in their own work.
 We can't estimate some platonic probability of truth for a study and neither can any replication study.
@@
 Rather than try to find the one right answer to whether a direct replication was done in a certain right way, we think it's useful to explicitly label what the estimand really was: how likely it is to get the same results (under whatever metric) given circumstances like those used for the replication.
-
+-->
 In our case, our estimand is about how well first-year graduate students will do at the replication, which takes into account the limited time, limited budget, and limited experience.
@@
 ```
-The dataset of replication projects comes from class projects conducted in PSYCH 251 (earlier called PSYCH 254) a graduate-level experimental methods class taught by MCF from 2011 to 2022.
+The dataset of replication projects comes from class projects conducted in PSYCH 251 (earlier called PSYCH 254) a graduate-level experimental methods class taught at Stanford by MCF from 2011 to 2022.
 This class is commonly taken by first year graduate students in psychology and related disciplines, and it has been a requirement of the Psychology PhD since around 2015.
@@
 Students were encouraged to do experimental replications, but some students chose to replicate correlational outcomes or do computational reproducibility projects instead.
-We cannot include the full student reports for confidentiality reasons, but we include an example as well as the template given to students in the repo.
-TODO example and template
+We cannot include the full student reports for confidentiality reasons, but we include an example as well as the template given to students at TODO example and template.
 
-Students were free to choose what study they replicated; the recommended path for students who did not have their own ideas was to pick an interesting study from a recent year of Psychological Science (this led to a high fraction of Psych Science articles in the replication sample, `r nrow(ps)`, `r nrow(ps)/nrow(all)*100 |> round()`% of studies).
+Students were free to choose what study to replicate; the recommended path for students who did not have their own ideas was to pick an interesting study from a recent year of Psychological Science (this led to a high fraction of Psych Science articles in the replication sample, `r nrow(ps)`, `r nrow(ps)/nrow(all)*100 |> round()`% of studies).
 
@@
 ### Measures of replication success
-Our primary replication outcome is experimenter and instructor rated replication success (0-1).
+Our primary replication outcome was experimenter and instructor rated replication success.
 The subjective replication success was recorded by the teaching staff for the majority of class replications at the time they were conducted.
@@
 Where VB’s coding disagreed with the staff/MCF’s code, the difference was resolved by discussion between VB and MCF (`r pluck(matching,2,1)/176*100 |> round()`% of studies).
-These were coded on a [0, .25, .5, .75, 1] scale.
+Subjective replication scores were coded on a [0, .25, .5, .75, 1] scale.
 
@@
 We coded the number of subjects, post-exclusions.
-We coded whether a study had a between-subjects, within-subjects, or mixed design; for analyses mixed studies were counted as within-subjects designs.
+We coded whether a study had a between-subjects, within-subjects, or mixed design; for the analysis, mixed studies were counted as within-subjects designs.
 In the analysis, we used a log-scale for number of subjects and numbers of trials.
@@
 ### Properties of replication
-We coded whether the replication was conducted on a crowd-sourced platform; this was the norm for the class projects, but a few were done in person.
-As the predictor variable, we used whether the recruitment platform was changed between original and replication.
-This groups the few in-person replications in with the studies that were originally online and stayed online in a "no change" condition, in contrast with the studies that were originally in-person with online replications.
+We coded whether the replication was conducted on a crowd-sourced platform; this was the norm for the class projects, but a few were done in-person.
+For analysis, we coded this into a variable indicating if the recruitment platform changed between original and replication.
+This grouped the few in-person replications in with the studies that were originally online and stayed online in a "no change" condition, in contrast with the studies that were originally in-person with online replications.
 
@@
 As a control variable, we included whether the original authors were faculty at Stanford at the time of the replication.
-This is to account for potential non-independence of the replication (ex.
+This was to account for potential non-independence of these replications (ex.
 if replicating their advisor's work, students may have access to extra information about methods).
 
-We made note of studies to exclude from some of the sensitivity analyses, due to not quite aligned statistics, extremely small or unbalanced sample sizes, or where the key statistical measure the student chose was not of central importance to the original study.
+We made note of studies to exclude for sensitivity analyses, due to not quite aligned statistics, extremely small or unbalanced sample sizes, or a student choosing a key statistical measure that was not of central importance to the original study.
 
@@
 PCA as measure of interest).
-Where studies reported beta estimates and standard errors or proportions, SMD isn't an applicable measure, but we were still able to calculate p_original and prediction interval.
+Where studies reported beta estimates and standard errors or proportions, standardized effects sizes are not an applicable measure, but we were still able to calculate p_original and prediction interval.
 
-We separately coded whether the original and replication effects were in the same direction, using raw means and graphs.
+We separately coded whether the original and replication effects were in the same direction, based on raw means and graphs.
 This is more reliable than the statistics because F-tests don't include the direction of effect, and some students may have flipped the direction in coding for betas or t-tests.
@@
 
-In regressions, we used SMD and log p-value as predictors.
+In regression analyses, we used SMD and log p-value as predictors.
 
@@
 
-Due to the monotonic missingness of the data, we had more predictor variables and outcome variables for some original-replication pairs than others.
-To take full advantage of the data, we ran a series of models, with some models having fewer predictors, but more data, and others having more predictors, but more limited data.
+Due to the monotonic missingness of the data, we had more predictor variables and outcome variables for some original-replication pairs than for others.
+To take full advantage of the data, we ran a series of models, with some models having fewer predictors, but more data, and others having more predictors, but less data.
 
-We ran a model predicting the subjective replication score on the basis of demographic and experimental predictors on the entire dataset; we ran two models predicting p_original and prediction interval from demographic and experimental predictors on the subset of data where we had p_original and prediction intervals.
-Then, on the smaller subset of the data where we had SMD and p-values, we re-ran these three models with those as additional predictor variables.
+We ran a model predicting the subjective replication score on the basis of demographic and experimental predictors on the entire dataset.
+We ran two models predicting p_original and prediction interval from demographic and experimental predictors on the subset of data where we had p_original and prediction intervals.
+Then, on the smaller subset of the data where we had effect sizes and p-values, we re-ran these three models with those as additional predictor variables.
 

### 2023-04-27 paper/manuscript.tex
tweaks to paper

@@
 PSYCH 251 is Stanford Psychology's graduate-level experimental methods class taught by MCF.
-During the 10 week class, students replicate a published finding.
-They individually re-implement the study, write analysis code, pre-register their study, collect data using an online platform, and write up a structured replication report.
-Students are free to choose studies related to their research interests, with the default recommendation being an article from a recent year of Psychological Science.
-While this choice results in a non-random sample from the literature, the sample is representative of studies that are of interest to and doable by first year graduate students.
+During the 10 week class, students replicated a published finding.
+They individually re-implemented the study, wrote analysis code, pre-registered their study, collected data using an online platform, and wrote up a structured replication report.
+Students were free to choose studies related to their research interests, with the default recommendation being an article from a recent year of Psychological Science.
+The resultant sample of studies is not a random sample from the literature but is representative of studies that are of interest to and doable by first year graduate students.
 
-The sample of replicated studies reflects the variability of the literature, including studies from different subfields, using different experimental methods and statistical outcomes.
-We leverage the naturally occurring variability in this sample of replications to examine how different demographic, experimental design, and statistical properties predict replication success.
+The sample of replicated studies reflect the variability of the literature, including studies from different subfields, using different experimental methods and statistical outcomes.
+We leveraged the naturally occurring variability in this sample of replications to examine how different demographic, experimental design, and statistical properties predict replication success.
 
-Many different measures can be used to define replication success of an individual statistical result, and there is much discussion over what each measure represents and which make sense (\protect\hyperlink{ref-simonsohn2015}{Simonsohn 2015}, \protect\hyperlink{ref-gelman2018}{Gelman 2018/ed}, \protect\hyperlink{ref-mathur2020}{Mathur \& VanderWeele 2020}).
+Many different measures can be used to define replication success of an individual statistical result (\protect\hyperlink{ref-simonsohn2015}{Simonsohn 2015}, \protect\hyperlink{ref-gelman2018}{Gelman 2018/ed}, \protect\hyperlink{ref-mathur2020}{Mathur \& VanderWeele 2020}).
 Because we operationalized replicability as whether a study could be built upon, we used a subjective rating of replication success as our primary outcome measure.
-This measure has the benefit that it was applicable across the diverse range of statistical measures and reporting practices present in the sample.
+This measure was applicable across the diverse range of statistical measures and reporting practices present in the sample.
 It, unlike statistical measures of replication, could easily accommodate studies where there were multiple important outcome measures that together defined the pattern of interest.
@@
 2021}).
-These both measure how similar the estimates from the two sets of data are.
+These both measure how similar the outcome estimates from the two sets of data are.
 
@@
 Across the 176 studies, the overall subjective replication rate was 49\%.
-45\% (N=FOOBAR) of the studies had replication outcomes within the prediction interval of the original outcome.
+45\% (62/138) of the studies had replication outcomes within the prediction interval of the original outcome.
 The median p\_original value was 0.03.
-Figure \ref{fig:smd} shows the relationship between original SMD, replication SMD, and subjective replication score.
+Figure \ref{fig:smd} shows the relationship between original standardized effect size, replication effect size, and subjective replication score.
 Roughly speaking, there's a cluster of studies that replicate with similar effect sizes to the original and another cluster that fail to replicate with replication effect sizes near zero.
@@
 Both social and cognitive psychology studies were well represented, and the cognitive psychology studies replicated at 2.45 times the rate of social psychology studies.
-Within and between subjects designs were both common, and within replicated 3.35 times as much.
+Within and between subjects designs were both common, and within-subjects designs replicated 3.35 times as much.
 Similarly, studies with multiple vignettes replicated 2.62 times more than single vignetted studies.
 However, there were strong correlations among these experimental features and between these experimental features and subfield.
-
 Studies with open data, which almost always also had open materials, tended to replicate more than studies without open data, although this may be linked to temporal trends.
@@
 While online studies in general show comparable results to studies conducted in person (\protect\hyperlink{ref-crump2013}{Crump et al.
-2013}), switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well adapted (ex.
+2013}), switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well-adapted (ex.
 inductions may be weaker or attention checks inadequate to the new sample).
@@
 
-While a number of the predictors show individual correlations with the subjective replication score, many of the predictors are also correlated with one another.
+While a number of predictors show individual correlations with the subjective replication score, many of the predictors also correlate with one another.
 In order to determine which predictors were the strongest, we ran a series of pre-registered regularized regression models (see Methods for details; see Supplement for all estimates from all models).
-The coefficient estimates of the primary model, predicting the subjective replication scores based on all the data, are shown in Figure \ref{fig:mod-results}.
+We ran models both using all the data, but without statistical predictors (that were uncodable for some studies) and models including statistical predictors, but limiting to the subset of data where all predictors were available.
+The coefficient estimates from two models predicting the subjective replication scores are shown in Figure \ref{fig:mod-results}.
 Due to a large number of predictors coupled with a small and noisy dataset, even with strong regularization, there is much uncertainty around the coefficients.
@@
 
-We also ran models predicting whether the replication effect was within the prediction interval as the original effect and what the p-original was between the replication and original.
+We also ran models predicting our secondary outcome measures: whether the replication effect was within the prediction interval as the original effect and what the p-original was between the replication and original.
 Both these models had even more uncertain estimates.
-While the credible intervals are wide, the general patterns of predictors are similar to the subjective replication models.
-The strongest predictors are still within-subjects designs (0.71, CrI= {[}-0.12, 2.38{]}) and studies with larger effect sizes (0.3, CrI= {[}-0.31, 0.89{]}).
+While the credible intervals were wide, the general patterns of predictor direction and relative strength were similar to the subjective replication models.
+The strongest predictors were still within-subjects designs (0.71, CrI= {[}-0.12, 2.38{]}) and studies with larger effect sizes (0.3, CrI= {[}-0.31, 0.89{]}).
 
@@
 
-The replication rate in psychology is, to the best estimates, somewhere around 50\%, which is quite low.
-Many reasons for this low replication rate have been hypothesized, but studying it either experimentally or correlationally requires doing a number of replication experiments, which can be a lot of work.
+Prior large scale replications of psychology findings have estimated the replication rate at somewhere around 50\%.
+This rate feels low, raising the question of what is causing so many studies not to replicate.
+However, limited numbers of replications and limited research into specific predictors of replication failure leave this an open question.
+
 Here we took advantage of 11 years of graduate student replication projects to look at correlational predictors of replication in a previously-unused dataset.
 
-In line with previous replications, we found a FOOBAR replication rate, with some studies showing effect sizes similar to the original and others much smaller.
-Some individual correlates of replicability that stood out included within-subjects designs, work in the subfield of cognitive psychology, and the original and replication both using online samples.
-Many of these correlates interrelate with one another, and we are still limited in our sample, so models with multiple predictors have a lot of uncertainty around the effects of each predictor.
-
-We are explicit in our goal of estimating how likely it is that a first-year graduate student, attempting to replicate a study of interest to them, gets replication results which are consistent enough with the original results that the student could build on the study in their own work.
-We can't estimate some platonic probability of truth for a study and neither can any replication study.
-Instead, we can estimate how likely studies are to get results of different levels of closeness in different circumstances.
-Much of the discussion around whether things should count as replication successes, or failures, or not replications at all is really about what the right thresholds are for closeness of results, and what the right circumstances are for a replication.
-Rather than try to find the one right answer to whether a direct replication was done in a certain right way, we think it's useful to explicitly label what the estimand really was: how likely it is to get the same results (under whatever metric) given circumstances like those used for the replication.
+In line with previous results, we found a \texttt{rround(pluck(sub\_rep\_rate,1))}\% replication rate, with some studies showing effect sizes similar to the original and others much smaller.
+When we looked at individual correlates of replicability, within-subjects designs, work in the subfield of cognitive psychology, and the original and replication both using online samples stood out as the strongest correlates.
+As many of these predictors interrelate with one another, we ran regularized regressions with all the predictors at once.
+Due to our small sample, model estimates were uncertain, but within-subjects designs and large original effect sizes were the strongest predictors.
 
@@
 
-The dataset of replication projects comes from class projects conducted in PSYCH 251 (earlier called PSYCH 254) a graduate-level experimental methods class taught by MCF from 2011 to 2022.
+The dataset of replication projects comes from class projects conducted in PSYCH 251 (earlier called PSYCH 254) a graduate-level experimental methods class taught at Stanford by MCF from 2011 to 2022.
 This class is commonly taken by first year graduate students in psychology and related disciplines, and it has been a requirement of the Psychology PhD since around 2015.
@@
 Students were encouraged to do experimental replications, but some students chose to replicate correlational outcomes or do computational reproducibility projects instead.
-We cannot include the full student reports for confidentiality reasons, but we include an example as well as the template given to students in the repo.
-TODO example and template
+We cannot include the full student reports for confidentiality reasons, but we include an example as well as the template given to students at TODO example and template.
 
-Students were free to choose what study they replicated; the recommended path for students who did not have their own ideas was to pick an interesting study from a recent year of Psychological Science (this led to a high fraction of Psych Science articles in the replication sample, 80, 45.4545455\% of studies).
+Students were free to choose what study to replicate; the recommended path for students who did not have their own ideas was to pick an interesting study from a recent year of Psychological Science (this led to a high fraction of Psych Science articles in the replication sample, 80, 45.4545455\% of studies).
 
@@
 
-Our primary replication outcome is experimenter and instructor rated replication success (0-1).
+Our primary replication outcome was experimenter and instructor rated replication success.
 The subjective replication success was recorded by the teaching staff for the majority of class replications at the time they were conducted.
@@
 Where VB's coding disagreed with the staff/MCF's code, the difference was resolved by discussion between VB and MCF (25.5681818\% of studies).
-These were coded on a {[}0, .25, .5, .75, 1{]} scale.
+Subjective replication scores were coded on a {[}0, .25, .5, .75, 1{]} scale.
 
@@
 
-We coded whether the replication was conducted on a crowd-sourced platform; this was the norm for the class projects, but a few were done in person.
-As the predictor variable, we used whether the recruitment platform was changed between original and replication.
-This groups the few in-person replications in with the studies that were originally online and stayed online in a ``no change'' condition, in contrast with the studies that were originally in-person with online replications.
+We coded whether the replication was conducted on a crowd-sourced platform; this was the norm for the class projects, but a few were done in-person.
+For analysis, we coded this into a variable indicating if the recruitment platform changed between original and replication.
+This grouped the few in-person replications in with the studies that were originally online and stayed online in a ``no change'' condition, in contrast with the studies that were originally in-person with online replications.
 
@@
 PCA as measure of interest).
-Where studies reported beta estimates and standard errors or proportions, SMD isn't an applicable measure, but we were still able to calculate p\_original and prediction interval.
+Where studies reported beta estimates and standard errors or proportions, standardized effects sizes are not an applicable measure, but we were still able to calculate p\_original and prediction interval.
 
-We separately coded whether the original and replication effects were in the same direction, using raw means and graphs.
+We separately coded whether the original and replication effects were in the same direction, based on raw means and graphs.
 This is more reliable than the statistics because F-tests don't include the direction of effect, and some students may have flipped the direction in coding for betas or t-tests.
@@
 
-Due to the monotonic missingness of the data, we had more predictor variables and outcome variables for some original-replication pairs than others.
-To take full advantage of the data, we ran a series of models, with some models having fewer predictors, but more data, and others having more predictors, but more limited data.
+Due to the monotonic missingness of the data, we had more predictor variables and outcome variables for some original-replication pairs than for others.
+To take full advantage of the data, we ran a series of models, with some models having fewer predictors, but more data, and others having more predictors, but less data.
 
-We ran a model predicting the subjective replication score on the basis of demographic and experimental predictors on the entire dataset; we ran two models predicting p\_original and prediction interval from demographic and experimental predictors on the subset of data where we had p\_original and prediction intervals.
-Then, on the smaller subset of the data where we had SMD and p-values, we re-ran these three models with those as additional predictor variables.
+We ran a model predicting the subjective replication score on the basis of demographic and experimental predictors on the entire dataset.
+We ran two models predicting p\_original and prediction interval from demographic and experimental predictors on the subset of data where we had p\_original and prediction intervals.
+Then, on the smaller subset of the data where we had effect sizes and p-values, we re-ran these three models with those as additional predictor variables.
 

### 2023-04-28 paper/manuscript.Rmd
work on discussion

@@
 
-<!------------ Main text -------------------->
-
 <!--introduction outline:
@@
 
--->
-<!--
-
-# Text slush pile
-
-The perceived need for more replications in tension with the lack of publishing incentives for doing replications led several to suggest that pedagogical replications could fill this gap.
-Doing replications is a way for students to learn to do experiments in a scaffolded way and leads to more useful results than what students could design from scratch on the same timescale [@quintana2021; @wagge2019;@frank2012; @hawkins].
-[TODO needs transition]
-
- * Don't want to build on something and fail a bunch trying to get your variant to work and then realize it just doesn't work.
-Replicability (as we mean it here) A useful framing is "ability to do cumulative science" -- close to what people mean, may disagree with many things
-We think this is a valuable estimand because it's estimating what people actually care about: is this result of interest sturdy enough to support cumulative science?
-
-[who knows where this paragraph should go] Replications are one way of approximating whether an effect in the target paper is true, and how likely results are to replicate in some sort of platonic ideal world.
-There is no one answer here; replication projects measure something else that could be treated as an approximation.
-However, what a replication is really measuring is how likely it to get that effect given some conditions.
-Which the right conditions are is a potential point of contention (see discussion around closeness and sample size, power etc).
-Here, we are explicit in what sample of replicators and replication conditions were are sampling, and thus what we can generalize to.
-We are estimating how likely replication is when done online by a graduate student, under constraints that are typical for graduate students (limited time, limited budget).
-As much of scientific process is in fact performed by graduate students, we think this in itself is an interesting question.
-
-We do not interpret our results as saying that all non-replications were false positives (presumably some are replicable under other circumstances and others are not).
-Some of the factors we look at are more easily interpreted as being about the original study than others.
-We do not assign causal explanation to the predictors because there are multiple plausible interpretations: they could be correlates of QRPs in the original, they could be correlates of harder-to-detect or more fragile effects, they could be correlates of less-close replications, they could even be correlates of another stronger predictor.
-
-[ there is controversy here, but to even discuss it, we need empirics] Even those who argue that replication is not so essential still rely on data from replications to make their cases that replication rates are not as low as they seem and that these replication rates are acceptable.
-@lewandowsky2020
-
-circle back to the idea that student replications (either as class or before extension into their own work) would be valuable
-
-To understand how replicable the literature as a whole is, we need empirical data about replication attempts across a wide range of studies.
-Most replications are targeted replications of individual results of interest to the researcher, but these are not sampled randomly from the literature, are performed in inconsistent ways, and may be selectively published depending on the results.
-Thus, they are not ideal for estimating the overall replicability of the field.
-
-There have been a limited number of large-scale replication efforts, which sample studies from a discipline to estimate overall replicability.
-Due to the arduous process of replicating many studies, there have not been many large-scale replication efforts.
-Thus, all of the argumentation around predictors of replications and field-wide replication rates is fit to a small number of data points.
-Psychology is in the middle of heated debate over its research practices and the subject of many reform efforts.
-Many of these issues concern how trustworth the published literature is (or isn't), how it got to be this way, and what measures can be taken to improve the quality of findings for the future.
-These issues center around issues of reproducibility  and replicability.
-Concerns about replication rates have become a large point of discussion in psychology and other fields, with large scale replications spurring these discussions and providing the empirical data analyzed by all sides.
-
-  [idk, maybe worth framing that this was a big deal study when it came out]. TODO some discussion of how many papers have reanalysed this cutting the data different ways.
-
- Many labs 5 was a re-replication attempt on 10 of RP:P and rescued 2/10 [@ebersole2020]. TODO look up details
-
- as validity, interestingness, and generalizability, can also be important
-Cumulative science and theory-building rely on empirical results that Replicability is a desirable feature for any study that we build theory or future experiments off of.
-It's a pre-requisite for building theories that we have phenomena for these studies to explain, but results that cannot be observed consistently aren't results to build theories around.
-However, to be a load-bearing empirical result, a study needs to do much more than just replicate, it also needs to be interesting, have a believable theoretical interpretation, generalize appropriately, and have reliable constructs.
-
-## predictors
-In addition to determining estimated overall replicaiton rates for fields and journals, there's also merit in knowing what features of experiments (and replication attempts) are predictive of replication success.
-Blah blah stakeholders and resources.
-Scientists may want to build their work on studies that are likely to replicate, so that they can replicate and build on work without wasting resources.
-Similarly investing in interventions may want to start with things that are more likely to replicate.
-There's some signal here, as people are able to predict replication success at above chance CITATIONS
-
-RP:P looked at how replication rates varied across subsamples of their studies [@openscienceconsortium2015].
-
-There are reasons to believe that experimental factors such as number of items or between and within subject designs may also be predictive (cite our old paper), and could pontentially be some of the reason for subfield differences.
-TODO maybe foreshadow that there are reasons to believe there are correlations!
-
-While many replications of individual studies are conducted, these may have been selected for non-representative reasons, such as a high prior on replicating (e.g.
-as a demonstration), or a low or uncertain prior (e.g.
-for a high-value study).
-When sampling is likely related to replicability, the studies are less good for estimating base rates and predictors of replicability in the literature as a whole.
-
-using pedagogical replications, which are good because they’re p(build on)
-slightly different estimand but maybe a better one?
-One key part of the question of whether a study is replicable or trustworthy is the idea of "if I did this, would I get the same pattern of results?".
-
-one strategy for the pedagogical bit at end of intro: stress “this is what people want to do, that is, pick up a project that they care about (not a random sample of the literature) and see if they can ‘get it to work’” - and “subjective replication success is our primary measure for the same reason….”
-
-Quantifying when an effect is a replication is hard, and many statistical metrics have been proposed, often with tradeoffs (TODO citations).
-We instead focus on a subjective score representing a more functionally oriented outcome: studies replicate if the results match the original enough that researchers would feel comfortable building on the study.
-This matches the motivation for many replications (often in replicate and extend paradigms).
-SPELL OUT SAMPLING DIFFERENCE AND SUCCESS DIFFERENCE.
-
-There's a "can I trust this finding" question, but a key part of it is, "if I did this, would I get the same pattern of results" -- and that's what we're measuring.
-
-We estimate this quantity in the context of a particular pedagogical situation: that of a graduate student entering a doctoral program in psychology...
-
-Prior literature, such as @frank2012 and @hawkins have advocated using research methods classes to conduct replications, both for the education and scientific value.
-
-# introduction
-.
-Building a cumulative body of scientific theories similarly requires that the empirical results, especially the more foundational empirical results, be sturdy.
-Results that cannot be observed consistently are like dirt clots, they don't hold their shape and thus are not a strong foundation for the theories and studies built on top of them.
-Replications and the theory of replicability can be thought of as a way of testing whether the empirical results are sturdy.
-Replicating is a necessary feature for load-bearing empirical results.
-We note that replicability is not the only desirable feature of a study, and that replicating does not mean that a study is valid, or generalizable, or interesting.
-
-Knowing what predicts and drives non-replications would let us potentially increase the replication rate, and also calibrate our levels of caution and skepticism toward results.
-Theoretical, interventional and correlational approaches do not yet provide comprehensive answers.
-
+potential things to add to introduction:
+* why experimental design features? 
+* pedagogy
+* cut theoretical para?
 -->
@@
 
-Theoretical approaches to understanding the replication rate have modeled how flexible research practices, selective reporting, and a bias toward positive results could lead to a high rate of (non-replicable) false positives (CITE).
+<!--Theoretical approaches to understanding the replication rate have modeled how flexible research practices, selective reporting, and a bias toward positive results could lead to a high rate of (non-replicable) false positives (CITE).
 However, while scientists admit to engaging in these practices, we don't yet know what proportion of non-replications are driven by these factors or how to identify these studies in the literature.
+-->
 
@@
 Prediction markets and elicitations have established that people can predict what studies will replicate above chance [@hoogeveen2019;@dreber2015; @forsell2019;@camerer2018], but have not identified concrete predictors that differentiate replications from non-replications.
-Using machine learning approaches, @altmejd2019 found that sample size, effect size, and simple effects were predictive of replication.
-@openscienceconsortium2015 looked at simple correlates of replicability in the RP:P sample and found that studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate.
+Using machine learning approaches, @altmejd2019 examined statistical and demographic features of studies and identified larger sample sizes, larger effect sizes, and simple effects (as opposed to interaction terms) as predictive of replication.
+@openscienceconsortium2015 looked at correlates of replicability in the RP:P sample and found that studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate.
+One potential set of correlates to replicabilty that has not been thoroughly examined are experimental design features, such as between or within subjects designs and repeated measures.
+
 Correlational approaches depend on data from replications, generally drawing heavily from the same small set of data points.
@@
 Here we took advantage of 11 years of graduate student replication projects to look at correlational predictors of replication in a previously-unused dataset.
-
-In line with previous results, we found a ` rround(pluck(sub_rep_rate,1))`% replication rate, with some studies showing effect sizes similar to the original and others much smaller.
+In line with previous results, we found a ` r round(pluck(sub_rep_rate,1))`% replication rate, with some studies showing effect sizes similar to the original and others much smaller.
 When we looked at individual correlates of replicability, within-subjects designs, work in the subfield of cognitive psychology, and the original and replication both using online samples stood out as the strongest correlates.
@@
 
-<!--We are explicit in our goal of estimating how likely it is that a first-year graduate student, attempting to replicate a study of interest to them, gets replication results which are consistent enough with the original results that the student could build on the study in their own work.
-We can't estimate some platonic probability of truth for a study and neither can any replication study.
-Instead, we can estimate how likely studies are to get results of different levels of closeness in different circumstances.
-Much of the discussion around whether things should count as replication successes, or failures, or not replications at all is really about what the right thresholds are for closeness of results, and what the right circumstances are for a replication.
-Rather than try to find the one right answer to whether a direct replication was done in a certain right way, we think it's useful to explicitly label what the estimand really was: how likely it is to get the same results (under whatever metric) given circumstances like those used for the replication.
--->
-In our case, our estimand is about how well first-year graduate students will do at the replication, which takes into account the limited time, limited budget, and limited experience.
-We think this is an important estimand, as much of the work of psychology is done by trainees, in circumstances like these.
-Thus, if some studies have delicate results that require large samples and very exact methods to achieve, they may not replicate under normal resources.
+Our metric of replicability was operationalized around the idea of whether a study could support cumulative science, so we looked at whether similar enough results could be obtained under the resource, expertise, and time constraints on early stage graduate students.
+We think this is a valuable estimand that is consistent with scientists' reasons for valuing replicability, but it is not the only estimand.
+Other replication projects have estimated replicabilty in other circumstances; for instance, @camerer2018 looks at likely studies are to replicate when performed by an expert with a large budget, and @ebersole2020 asks how likely certain studies are to replicate when performed with extensive feedback from the original authors.
 
-Other replication projects have other estimands: @camerer2018 seems to ask something closer to how likely studies are to replicate when preformed by an expert with a large budget, and @ebersole2020 asks how likely certain studies are to replicate when performed with extensive feedback from the original authors.
+Replication results should be interpreted in light of their methods and estimand.
+We do not interpret our non-replications as indicating the original studies were false positives (presumably some were and some weren't).
+There are many possible reasons for the non-replications in this sample.
+In some cases, the problem may be with the replication, such as too few participants, many exclusions for failed attention checks, or participants speeding through the study.
+When these issues are diagnosed, they suggest possible ways to "rescue" the replication by fixing power or encouraging participants to take the task seriously, without altering the underlying experiment.
+In other cases, there were a priori reasons to distrust the original study, such as exclusion criteria that seemed post-hoc or high-order interaction terms with a small sample.
+That said, not all scientists notice the same factors as potential indications of low power or questionable research practices; students conducting these replications generally expected them to succeed.
+In many non-replication cases, it was unclear why the results failed to replicate.
 
-We do not interpret our results as saying that all non-replications were false positives (presumably some would be replicable under different implementations and budgets and others would not).
-There are many possible reasons for the non-replications in this sample.
-In some cases, it seemed that the problem may have been with the replication: for instance, if there were too few participants, or if there were high levels of wrong answers on attention checks, or participants speeding through without attention checks.
-For these cases, there was a clear next attempt that a student could make if they wanted to get the replication to work.
-In other cases, there might have been a priori reasons to distrust the original study results, such as exclusion criteria that seemed to be post-hoc, or a three-way interaction effect on a small sample (CITE THAT THIS IS SKETCH).
-In yet other cases, it's unclear why the results failed to replicate.
-
-[somehow transition here] Pedagogy is important for open science.
-It's one thing to require or incentivize scientists to use open science practices and conduct replicable and reproducible research, but using the right tools and workflows to do open science is something that has to be learned.
-Teaching it in the classroom addresses the knowing how point at the beginning and shows students how to have open science practices integrated in to their science at the beginning, before other habits can ossify.
-Doing replications give students the motivation to care about open science, as they see how much easier it is to implement the study with open materials versus the study where they have to make guesses about the study instructions from the methods section.
-In presenting work with classmates, students see that there is variation in how well studies replicate, with some replicating very cleanly and others not at all.
-This sort of first hand experience teaches that not everything they read in the literature may just work if done again.
+We also caution in the interpretation of our predictor variables.
+Some of the correlates are most easily interpreted as being about the original study, and others seem to be more about the closeness of the replication to the original.
+This was a correlational design, so we cannot attribute causality to any of these factors.
+For instance, while within-subjects designs are more likely to replicate than between-subjects designs, this could be related to power, or the types of experiments that tend to be run in each design.
+Given the predictive value, slightly more skepticism and critical reading of between-subjects designs may be warranted, but this correlation, by itself, does not mean scientists should prefer to run within-subjects designs.
 
@@
 
-TODO conclusion
+Large scale replications are costly and arduous to run.
+The batch of replications presented here were pedagogical replications, done as part of a class.
+Trainee behavioral scientists need to learn experimental methods, and conducting replications as part of methods classes serve a dual purpose: they enables students to learn to do experiments in a scaffolded way, and they lead to more useful results than if students designed their own experiments from scratch on the same timescale [@quintana2021; @wagge2019;@frank2012; @hawkins].
+Pedagogy has an important role to play in open science more broadly -- it's one thing to require or incentivize certain practices, but the tools and workflows of open science have to be learned.
+Teaching these skills and giving students an opportunity to practice using open, reproducible workflows shows students how to integrate open science practices into their workflows, before other habits can ossify.
+In doing replications, students may be motivated to value transparent practices, as they either struggle to reimplement studies from vague methods or appreciate the ease of working with available materials and analysis code.
+In presenting work with classmates, students see that there is variation in how well studies replicate, with some replicating very cleanly and others not at all.
+This sort of first hand experience teaches students that not everything they read in the literature may just work if done again.
 

### 2023-04-28 paper/manuscript.tex
work on discussion

@@
 
-Theoretical approaches to understanding the replication rate have modeled how flexible research practices, selective reporting, and a bias toward positive results could lead to a high rate of (non-replicable) false positives (CITE).
-However, while scientists admit to engaging in these practices, we don't yet know what proportion of non-replications are driven by these factors or how to identify these studies in the literature.
-
 Experimental approaches attempt to intervene on the low replication rate, by changing certain factors that may affect whether studies replicate.
@@
 Using machine learning approaches, Altmejd et al.
-(\protect\hyperlink{ref-altmejd2019}{2019}) found that sample size, effect size, and simple effects were predictive of replication.
-Open Science Consortium (\protect\hyperlink{ref-openscienceconsortium2015}{2015}) looked at simple correlates of replicability in the RP:P sample and found that studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate.
+(\protect\hyperlink{ref-altmejd2019}{2019}) examined statistical and demographic features of studies and identified larger sample sizes, larger effect sizes, and simple effects (as opposed to interaction terms) as predictive of replication.
+Open Science Consortium (\protect\hyperlink{ref-openscienceconsortium2015}{2015}) looked at correlates of replicability in the RP:P sample and found that studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate.
+One potential set of correlates to replicabilty that has not been thoroughly examined are experimental design features, such as between or within subjects designs and repeated measures.
 Correlational approaches depend on data from replications, generally drawing heavily from the same small set of data points.
@@
 Here we took advantage of 11 years of graduate student replication projects to look at correlational predictors of replication in a previously-unused dataset.
-
-In line with previous results, we found a \texttt{rround(pluck(sub\_rep\_rate,1))}\% replication rate, with some studies showing effect sizes similar to the original and others much smaller.
+In line with previous results, we found a \texttt{r\ round(pluck(sub\_rep\_rate,1))}\% replication rate, with some studies showing effect sizes similar to the original and others much smaller.
 When we looked at individual correlates of replicability, within-subjects designs, work in the subfield of cognitive psychology, and the original and replication both using online samples stood out as the strongest correlates.
@@
 
-In our case, our estimand is about how well first-year graduate students will do at the replication, which takes into account the limited time, limited budget, and limited experience.
-We think this is an important estimand, as much of the work of psychology is done by trainees, in circumstances like these.
-Thus, if some studies have delicate results that require large samples and very exact methods to achieve, they may not replicate under normal resources.
-
-Other replication projects have other estimands: Camerer et al.
-(\protect\hyperlink{ref-camerer2018}{2018}) seems to ask something closer to how likely studies are to replicate when preformed by an expert with a large budget, and Ebersole et al.
+Our metric of replicability was operationalized around the idea of whether a study could support cumulative science, so we looked at whether similar enough results could be obtained under the resource, expertise, and time constraints on early stage graduate students.
+We think this is a valuable estimand that is consistent with scientists' reasons for valuing replicability, but it is not the only estimand.
+Other replication projects have estimated replicabilty in other circumstances; for instance, Camerer et al.
+(\protect\hyperlink{ref-camerer2018}{2018}) looks at likely studies are to replicate when performed by an expert with a large budget, and Ebersole et al.
 (\protect\hyperlink{ref-ebersole2020}{2020}) asks how likely certain studies are to replicate when performed with extensive feedback from the original authors.
 
-We do not interpret our results as saying that all non-replications were false positives (presumably some would be replicable under different implementations and budgets and others would not).
+Replication results should be interpreted in light of their methods and estimand.
+We do not interpret our non-replications as indicating the original studies were false positives (presumably some were and some weren't).
 There are many possible reasons for the non-replications in this sample.
-In some cases, it seemed that the problem may have been with the replication: for instance, if there were too few participants, or if there were high levels of wrong answers on attention checks, or participants speeding through without attention checks.
-For these cases, there was a clear next attempt that a student could make if they wanted to get the replication to work.
-In other cases, there might have been a priori reasons to distrust the original study results, such as exclusion criteria that seemed to be post-hoc, or a three-way interaction effect on a small sample (CITE THAT THIS IS SKETCH).
-In yet other cases, it's unclear why the results failed to replicate.
+In some cases, the problem may be with the replication, such as too few participants, many exclusions for failed attention checks, or participants speeding through the study.
+When these issues are diagnosed, they suggest possible ways to ``rescue'' the replication by fixing power or encouraging participants to take the task seriously, without altering the underlying experiment.
+In other cases, there were a priori reasons to distrust the original study, such as exclusion criteria that seemed post-hoc or high-order interaction terms with a small sample.
+That said, not all scientists notice the same factors as potential indications of low power or questionable research practices; students conducting these replications generally expected them to succeed.
+In many non-replication cases, it was unclear why the results failed to replicate.
 
-{[}somehow transition here{]} Pedagogy is important for open science.
-It's one thing to require or incentivize scientists to use open science practices and conduct replicable and reproducible research, but using the right tools and workflows to do open science is something that has to be learned.
-Teaching it in the classroom addresses the knowing how point at the beginning and shows students how to have open science practices integrated in to their science at the beginning, before other habits can ossify.
-Doing replications give students the motivation to care about open science, as they see how much easier it is to implement the study with open materials versus the study where they have to make guesses about the study instructions from the methods section.
-In presenting work with classmates, students see that there is variation in how well studies replicate, with some replicating very cleanly and others not at all.
-This sort of first hand experience teaches that not everything they read in the literature may just work if done again.
+We also caution in the interpretation of our predictor variables.
+Some of the correlates are most easily interpreted as being about the original study, and others seem to be more about the closeness of the replication to the original.
+This was a correlational design, so we cannot attribute causality to any of these factors.
+For instance, while within-subjects designs are more likely to replicate than between-subjects designs, this could be related to power, or the types of experiments that tend to be run in each design.
+Given the predictive value, slightly more skepticism and critical reading of between-subjects designs may be warranted, but this correlation, by itself, does not mean scientists should prefer to run within-subjects designs.
 
@@
 
-TODO conclusion
+Large scale replications are costly and arduous to run.
+The batch of replications presented here were pedagogical replications, done as part of a class.
+Trainee behavioral scientists need to learn experimental methods, and conducting replications as part of methods classes serve a dual purpose: they enables students to learn to do experiments in a scaffolded way, and they lead to more useful results than if students designed their own experiments from scratch on the same timescale (\protect\hyperlink{ref-frank2012}{Frank \& Saxe 2012}, \protect\hyperlink{ref-wagge2019}{Wagge et al.
+2019}, \protect\hyperlink{ref-quintana2021}{Quintana 2021}, \protect\hyperlink{ref-hawkins}{Hawkins et al.
+n.d.}).
+Pedagogy has an important role to play in open science more broadly -- it's one thing to require or incentivize certain practices, but the tools and workflows of open science have to be learned.
+Teaching these skills and giving students an opportunity to practice using open, reproducible workflows shows students how to integrate open science practices into their workflows, before other habits can ossify.
+In doing replications, students may be motivated to value transparent practices, as they either struggle to reimplement studies from vague methods or appreciate the ease of working with available materials and analysis code.
+In presenting work with classmates, students see that there is variation in how well studies replicate, with some replicating very cleanly and others not at all.
+This sort of first hand experience teaches students that not everything they read in the literature may just work if done again.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-frank2012}{}}%
+Frank MC, Saxe R (2012) Teaching {Replication}: \emph{Perspect Psychol Sci}. doi:\href{https://doi.org/10.1177/1745691612460686}{10.1177/1745691612460686}
+
 \leavevmode\vadjust pre{\hypertarget{ref-gelman2018}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-quintana2021}{}}%
+Quintana DS (2021) Replication studies for undergraduate theses to improve science and education.
+\emph{Nat Hum Behav} \textbf{5}:1117--1118.
+doi:\href{https://doi.org/10.1038/s41562-021-01192-8}{10.1038/s41562-021-01192-8}
+
 \leavevmode\vadjust pre{\hypertarget{ref-ramscar}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-wagge2019}{}}%
+Wagge JR, Brandt MJ, Lazarevic LB, Legate N, Christopherson C, Wiggins B, Grahe JE (2019) \href{https://www.frontiersin.org/articles/10.3389/fpsyg.2019.00247}{Publishing {Research With Undergraduate Students} via {Replication Work}: {The Collaborative Replications} and {Education Project}}.
+\emph{Front Psychol} \textbf{10}
+
 \leavevmode\vadjust pre{\hypertarget{ref-wilson2020}{}}%

### 2023-04-29 paper/manuscript.Rmd
work on abstract, intro, list of problems

@@
 
-d <- read_csv(here("data", "processed_data.csv")) |> filter(status!="unusable")
+d <- read_csv(here("data", "processed_data.csv")) |> filter(status!="unusable") |> filter(include!="no")
 ```
@@
 ::: {.abstract data-latex="" lang=en}
-A cumulative science requires foundational empirical results that are robust enough to support  theories and future experiments.
-Prominent failed replications of well-known published findings cast doubt on the psychological literature, and large scale replication projects suggested that the overall replication rate in psychology might be between 40-60%.
-Large-scale replications are arduous, and only around 170 replications have been conducted as part of a large-scale replication project.
-This dearth of data points limits estimations of replicability and analyses of potential correlates of replicability.
-Using a new sample of 176 replications conducted as part of a course, we estimate replicability of these studies that were of interest to graduate students.
-We look at statistical and experimental-design features of studies as potential predictors of replication.
-We find that within-study designs and large original effect sizes positively correlate with replicability.
 
+Cumulative scientific progress requires empirical results that are robust enough to support theory construction and future experimental extension.
+Yet in psychology, some prominent individual findings are have repeatedly failed to replicate, and large-scale investigations suggest that the overall replication rate is around half.
+What predicts which studies will replicate?
+The identification of features that predict replication is limited by the common dataset of only 170 studies from large-scale investigations that are repeatedly analysed.
+We introduce a new sample of 176 replications conducted by students as part of a graduate-level experimental methods course, and we examine how often students were able replicate their chosen studies' results closely enough that they would be ready to build on it in future work.
+Using this as a metric of replicability, 49% of the studies in our sample replicate, with studies with larger original effect sizes and within-participants designs being more likely to replicate.
+Consistent with prior reports, our replication results indicate that the robustness of the psychology literature is low enough to limit progress by student investigators.
 :::
@@
 
-A cumulative science requires foundational empirical results that are robust enough to support  theories and future experiments.
-If scientists attempt to build cumulative science on top of results that are unreliable and cannot be achieved consistently, they waste resources looking for results where there may be none.
-This is frustrating for individual scientists, but also damaging to the enterprise of science overall.
+Cumulative science requires foundation empirical results that are robust enough to support theory construction and future experimental extension.
+If scientists attempt to build on top of results that cannot be achieved consistently, they waste resources looking for results where there may be none.
+This is frustrating for individual scientists and damaging to the enterprise of science overall.
 
@@
 This trust in published findings has led scientists to build on findings without verifying them first, but failures were often explained away and rarely published, leaving the original results uncontested in the literature, while failures to achieve the same outcomes accumulated in private.
+FIX PRIOR SENTENCE
 
@@
 
-How replicable is psychology as a whole?
-Few large scale replications have been conducted in psychology, due to the resources required to run large numbers of replication studies.
-We are aware of three.
-RP:P sampled roughly 100 studies from articles published in three top psychology journals in 2008 and found a overall replication rate of around 40% [@openscienceconsortium2015].
+These failures to replicate raised the question: How replicable is psychology as a whole?
+Only three large-scale investigations address this question by sampling subsets of psychology findings.
+Reproducibility Project: Psychology, mentioned above, sampled roughly 100 studies from articles published in three top psychology journals in 2008 and found a overall replication rate of around 40% [@openscienceconsortium2015].
 ManyLabs investigated heterogeneity using short target studies that compared between two conditions each, but these studies are not representative of the psychology literature as a whole.
@@
 @camerer2018 replicated all 21 behavioral social science studies from Nature and Science from 2010-2015 that were feasible; the replication rate was around 60%.
-These roughly 170 replications of psychology studies are the primary empirical results on which discussions of replication rates in psychology are based.
+Conducting large numbers of studies to assess replication rates is expensive and arduous which may explain why more large-scale investigations don't exist.
+These roughly 170 replications from these three investigations are the primary empirical results on which discussions of replication rates in psychology are based.
 
-A replication rate around 50% runs counter to the prior assumption that most findings in the literature were robust enough to support cumulative science, and it raises the question: What makes the replication rates in psychology so low?
+TRANSITION A replication rate around 50% runs counter to the prior assumption that most findings in the literature were robust enough to build upon without verification, and it raises the question: What makes the replication rates in psychology so low?
 
@@
 
-Experimental approaches attempt to intervene on the low replication rate, by changing certain factors that may affect whether studies replicate.
+Experimental approaches attempt to causally intervene on the low replication rate, by changing certain factors that may affect whether studies replicate.
 @protzko2020 showed, across 16 studies, that better methodological practices, such as transparency, large sample sizes, and confirmatory tests, led to replication rates that matched theoretical expectations based on the effect sizes and sample sizes, with replication effect sizes comparable with the original.
@@
 
-Correlational approaches looking for predictors of replicability are the most popular.
+Correlational approaches looking for predictors of replicability are more popular.
 Prediction markets and elicitations have established that people can predict what studies will replicate above chance [@hoogeveen2019;@dreber2015; @forsell2019;@camerer2018], but have not identified concrete predictors that differentiate replications from non-replications.
@@
 
-Correlational approaches depend on data from replications, generally drawing heavily from the same small set of data points.
+TRANSITION / HOW TO FIT THIS PART IN Correlational approaches depend on data from replications, generally drawing heavily from the same small set of data points.
 In particular, the RP:P dataset itself is much discussed and reanalyzed [@etz2016;@gilbert2016;@patil2016;@anderson2016] to the point that much of what we think we know about replicability may be overfit to the 100 studies included in in RP:P.
 
+TRANSITION / DELETE ?
 Many of the discussions and reanalyses have raised questions about what the right metrics for measuring replicability are and what standards are reasonable to expect.
@@
 
+TRANSITION!
 Prior approaches to replicability have focused on interpreting results in terms of a potentially problematic estimand: the probability of a finding in the literature being somehow truly replicable.
@@
 
-Our methodology is reflective of this framing of replicability as being the probability of a studying being able to support cumulative science.
-Rather than sampling at random from some parts of the literature; our sample of studies is selected based on what studies students were interested in and wanting to replicate, with some filtering for feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable given methodological and budgetary constraints.
+NEED PUNCHY TRANSITION TO DETAILS Rather than sampling at random from some parts of the literature; our sample of studies is selected based on what studies students were interested in and wanting to replicate, with some filtering for feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable given methodological and budgetary constraints.
 
@@
 
-All our replications were conducted under short time scales and relatively small budgets, which mimics the constraints many scientists are under when starting new projects.
+All our replications were conducted under short time scales and relatively small budgets, which parallels the constraints many scientists are under when starting new projects.
 From the point of view of cumulative science, researchers want to know if they can get paradigms to work under their real-world constraints.
@@
 We investigated statistical and experimental-design predictors of replicability in this dataset and found that within-subjects designs and studies with large standardized effect sizes were positively correlated with replication success.
+
+# Results
 
@@
 		\node[mynode, join, on chain=1, fill=good] (n6)
-		{\textbf{136} pairs with ES};
+		{\textbf{136} pairs with some effect size};
 		\node[mynode, join, on chain=1, fill=good] (n7)
-		{\textbf{112} pairs with SMD};
+		{\textbf{112} pairs with standardized effect size};
 
@@
 			\node[mynode, join, on chain, fill=bad]
-			{\textbf{1} pair missing sample size};
+			{\textbf{1} pair missing original sample size};
 		\end{scope}
 	\end{tikzpicture}
-\caption{Which studies were excluded for what reasons, and how many original-replication pairs are left.}\label{fig:prisma}
+\caption{Of the 210 projects conducted for the class, 176 are included in our analysis, after excluding reproducibilty projects (with no new data collection), non-experimental replications, and missing projects.
+Of the 176, 136 report sufficient information to numerically compare outcome measures, and 112 report enough to use statistical predictors.
+TODO BETTER WAY TO LABEL AND TALK ABOUT THEIR 2 AND 3}\label{fig:prisma}
 \end{figure}
@@
 
-# Results
+```{r}
+matching <- d |> filter(include!="unusable") |> mutate(match=ifelse(replicated_instructor_code==replicated_report_code,1,0)) |> group_by(match) |> tally()
 
-```{r}
-matching <- d |> filter(status!="unusable") |> mutate(match=ifelse(replicated_instructor_code==replicated_report_code,1,0)) |> group_by(match) |> tally()
-
-pred_int_avail <- d |> filter(!is.na(predInt)&!is.na(p_orig)) |> tally()
+pred_int_avail <- d |> filter(include %in% c("stats", "pred_int")) |> tally()
 
@@
 
-The sample of replicated studies reflect the variability of the literature, including studies from different subfields, using different experimental methods and statistical outcomes.
+The sample of replicated studies reflects the variability of the literature, including studies from different subfields, with different experimental methods and statistical outcomes.
 We leveraged the naturally occurring variability in this sample of replications to examine how different demographic, experimental design, and statistical properties predict replication success.
@@
 Many different measures can be used to define replication success of an individual statistical result [@simonsohn2015; @gelman2018; @mathur2020].
-Because we operationalized replicability as whether a study could be built upon, we used a subjective rating of replication success as our primary outcome measure.
+Because we operationalized replicability as whether a study could support cumulative science, we used a subjective rating of replication success as our primary outcome measure.
 This measure was applicable across the diverse range of statistical measures and reporting practices present in the sample.
@@
 
-As a complement, we also used two statistical measure of replication on the subset of the data where they were computable (`r pluck(pred_int_avail,1)` cases, see Figure \ref{fig:prisma}).
+As a complement, we also used two statistical measures of replication on the subset of the data where they were computable (`r pluck(pred_int_avail,1)` cases, see Figure \ref{fig:prisma}).
 We measured p-original, the p-value on the null hypothesis that the original and replication statistics are from the same distribution, as a continuous variable, and we also determined whether the replication statistic fell within the prediction interval of the original statistic [@errington2021].
@@
 
-```{r smd, out.height="25%", fig.width=6, fig.height=3, fig.pos="ht", fig.cap="Relationship between SMD of the original study, SMD of the replication study, and subjective replication success rating, for those studies where SMD was applicable."}
+```{r smd, out.height="25%", fig.width=6, fig.height=3, fig.pos="ht", fig.cap="Relationship between effect size of the original study, effect size of the replication study, and subjective replication success rating, for those studies where effect size was applicable."}
 d |> 
   filter(target_d_calc < 5, rep_d_calc < 5) |>
-  ggplot(aes(x=target_d_calc, y=rep_d_calc, color=sub_rep))+
+  ggplot(aes(x=target_d_calc, y=rep_d_calc))+
 
@@
   geom_smooth(method = "lm") + 
-   geom_point(size=2.5) +
+   geom_point(aes(color=as.factor(sub_rep)), size=2.5) +
   geom_hline(yintercept = 0, lty = 2)+
-  scale_color_viridis(discrete=F, direction = 1, 
+  scale_color_viridis(discrete=T, direction = 1, 
                       name = "Subjective\nReplication\nSuccess\n")+
-  labs(color="subrep", x="Original SMD", y="Replication SMD") + 
+  labs(x="Original effect size", y="Replication effect size") + 
   theme(legend.position = "right")
@@
 
+<!-- VERONICA IS HERE IN GOING BACK THROUGH --> 
 ## Overall replication rate
@@
 
-pred_int_rate <- d |> filter(!is.na(predInt)) |> summarize(m=mean(as.numeric(predInt))*100)
-porig_rate <- d |> filter(!is.na(p_orig)) |> summarize(m=median(p_orig))
+pred_int_rate <- d |> filter(include %in% c("stats", "pred_int"))|> summarize(m=mean(as.numeric(predInt))*100)
+porig_rate <- d |>filter(include %in% c("stats", "pred_int"))|> summarize(m=median(p_orig))
 
-d |> filter(!is.na(predInt)) |> filter(predInt) |> nrow() -> predIntcount
-d |> filter(!is.na(predInt)) |> nrow() -> predInttotal
+d |> filter(include %in% c("stats", "pred_int"))|> filter(predInt) |> nrow() -> predIntcount
+d |> filter(include %in% c("stats", "pred_int"))|> nrow() -> predInttotal
 
@@
 Here we took advantage of 11 years of graduate student replication projects to look at correlational predictors of replication in a previously-unused dataset.
-In line with previous results, we found a ` r round(pluck(sub_rep_rate,1))`% replication rate, with some studies showing effect sizes similar to the original and others much smaller.
+In line with previous results, we found a `r round(pluck(sub_rep_rate,1))`% replication rate, with some studies showing effect sizes similar to the original and others much smaller.
 When we looked at individual correlates of replicability, within-subjects designs, work in the subfield of cognitive psychology, and the original and replication both using online samples stood out as the strongest correlates.
@@
 
-Students were free to choose what study to replicate; the recommended path for students who did not have their own ideas was to pick an interesting study from a recent year of Psychological Science (this led to a high fraction of Psych Science articles in the replication sample, `r nrow(ps)`, `r nrow(ps)/nrow(all)*100 |> round()`% of studies).
+Students were free to choose what study to replicate; the recommended path for students who did not have their own ideas was to pick an interesting study from a recent year of Psychological Science (this led to a high fraction of Psych Science articles in the replication sample, `r nrow(ps)`, `r round( nrow(ps)/nrow(all)*100)`% of studies).
 
@@
 For all studies, replication success was independently coded by VB on the basis of the reports.
-Where VB’s coding disagreed with the staff/MCF’s code, the difference was resolved by discussion between VB and MCF (`r pluck(matching,2,1)/176*100 |> round()`% of studies).
+Where VB’s coding disagreed with the staff/MCF’s code, the difference was resolved by discussion between VB and MCF (`r round(pluck(matching,2,1)/176*100)`% of studies).
 Subjective replication scores were coded on a [0, .25, .5, .75, 1] scale.

### 2023-04-29 paper/manuscript.tex
work on abstract, intro, list of problems

@@
 \begin{abstract}
-A cumulative science requires foundational empirical results that are robust enough to support theories and future experiments.
-Prominent failed replications of well-known published findings cast doubt on the psychological literature, and large scale replication projects suggested that the overall replication rate in psychology might be between 40-60\%.
-Large-scale replications are arduous, and only around 170 replications have been conducted as part of a large-scale replication project.
-This dearth of data points limits estimations of replicability and analyses of potential correlates of replicability.
-Using a new sample of 176 replications conducted as part of a course, we estimate replicability of these studies that were of interest to graduate students.
-We look at statistical and experimental-design features of studies as potential predictors of replication.
-We find that within-study designs and large original effect sizes positively correlate with replicability.
+Cumulative scientific progress requires empirical results that are robust enough to support theory construction and future experimental extension.
+Yet in psychology, some prominent individual findings are have repeatedly failed to replicate, and large-scale investigations suggest that the overall replication rate is around half.
+What predicts which studies will replicate?
+The identification of features that predict replication is limited by the common dataset of only 170 studies from large-scale investigations that are repeatedly analysed.
+We introduce a new sample of 176 replications conducted by students as part of a graduate-level experimental methods course, and we examine how often students were able replicate their chosen studies' results closely enough that they would be ready to build on it in future work.
+Using this as a metric of replicability, 49\% of the studies in our sample replicate, with studies with larger original effect sizes and within-participants designs being more likely to replicate.
+Consistent with prior reports, our replication results indicate that the robustness of the psychology literature is low enough to limit progress by student investigators.
 
@@
 
-A cumulative science requires foundational empirical results that are robust enough to support theories and future experiments.
-If scientists attempt to build cumulative science on top of results that are unreliable and cannot be achieved consistently, they waste resources looking for results where there may be none.
-This is frustrating for individual scientists, but also damaging to the enterprise of science overall.
+Cumulative science requires foundation empirical results that are robust enough to support theory construction and future experimental extension.
+If scientists attempt to build on top of results that cannot be achieved consistently, they waste resources looking for results where there may be none.
+This is frustrating for individual scientists and damaging to the enterprise of science overall.
 
@@
 
-How replicable is psychology as a whole?
-Few large scale replications have been conducted in psychology, due to the resources required to run large numbers of replication studies.
-We are aware of three.
-RP:P sampled roughly 100 studies from articles published in three top psychology journals in 2008 and found a overall replication rate of around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}).
+These failures to replicate raised the question: How replicable is psychology as a whole?
+Only three large-scale investigations address this question by sampling subsets of psychology findings.
+Reproducibility Project: Psychology, mentioned above, sampled roughly 100 studies from articles published in three top psychology journals in 2008 and found a overall replication rate of around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}).
 ManyLabs investigated heterogeneity using short target studies that compared between two conditions each, but these studies are not representative of the psychology literature as a whole.
@@
 (\protect\hyperlink{ref-camerer2018}{2018}) replicated all 21 behavioral social science studies from Nature and Science from 2010-2015 that were feasible; the replication rate was around 60\%.
-These roughly 170 replications of psychology studies are the primary empirical results on which discussions of replication rates in psychology are based.
+Conducting large numbers of studies to assess replication rates is expensive and arduous which may explain why more large-scale investigations don't exist.
+These roughly 170 replications from these three investigations are the primary empirical results on which discussions of replication rates in psychology are based.
 
-A replication rate around 50\% runs counter to the prior assumption that most findings in the literature were robust enough to support cumulative science, and it raises the question: What makes the replication rates in psychology so low?
+TRANSITION A replication rate around 50\% runs counter to the prior assumption that most findings in the literature were robust enough to build upon without verification, and it raises the question: What makes the replication rates in psychology so low?
 
-Experimental approaches attempt to intervene on the low replication rate, by changing certain factors that may affect whether studies replicate.
+Experimental approaches attempt to causally intervene on the low replication rate, by changing certain factors that may affect whether studies replicate.
 Protzko et al.
@@
 
-Correlational approaches looking for predictors of replicability are the most popular.
+Correlational approaches looking for predictors of replicability are more popular.
 Prediction markets and elicitations have established that people can predict what studies will replicate above chance (\protect\hyperlink{ref-dreber2015}{Dreber et al.
@@
 One potential set of correlates to replicabilty that has not been thoroughly examined are experimental design features, such as between or within subjects designs and repeated measures.
-Correlational approaches depend on data from replications, generally drawing heavily from the same small set of data points.
+
+TRANSITION / HOW TO FIT THIS PART IN Correlational approaches depend on data from replications, generally drawing heavily from the same small set of data points.
 In particular, the RP:P dataset itself is much discussed and reanalyzed (\protect\hyperlink{ref-anderson2016}{Anderson et al.
@@
 
+TRANSITION / DELETE ?
 Many of the discussions and reanalyses have raised questions about what the right metrics for measuring replicability are and what standards are reasonable to expect.
@@
 We investigated statistical and experimental-design predictors of replicability in this dataset and found that within-subjects designs and studies with large standardized effect sizes were positively correlated with replication success.
+
+\hypertarget{results}{%
+\section{Results}\label{results}}
 
@@
         \node[mynode, join, on chain=1, fill=good] (n6)
-        {\textbf{136} pairs with ES};
+        {\textbf{136} pairs with some effect size};
         \node[mynode, join, on chain=1, fill=good] (n7)
-        {\textbf{112} pairs with SMD};
+        {\textbf{112} pairs with standardized effect size};
 
@@
             \node[mynode, join, on chain, fill=bad]
-            {\textbf{1} pair missing sample size};
+            {\textbf{1} pair missing original sample size};
         \end{scope}
     \end{tikzpicture}
-\caption{Which studies were excluded for what reasons, and how many original-replication pairs are left.}\label{fig:prisma}
+\caption{Of the 210 projects conducted for the class, 176 are included in our analysis, after excluding reproducibilty projects (with no new data collection), non-experimental replications, and missing projects.
+Of the 176, 136 report sufficient information to numerically compare outcome measures, and 112 report enough to use statistical predictors.
+TODO BETTER WAY TO LABEL AND TALK ABOUT THEIR 2 AND 3}\label{fig:prisma}
 \end{figure}
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
 
@@
 Many different measures can be used to define replication success of an individual statistical result (\protect\hyperlink{ref-simonsohn2015}{Simonsohn 2015}, \protect\hyperlink{ref-gelman2018}{Gelman 2018/ed}, \protect\hyperlink{ref-mathur2020}{Mathur \& VanderWeele 2020}).
-Because we operationalized replicability as whether a study could be built upon, we used a subjective rating of replication success as our primary outcome measure.
+Because we operationalized replicability as whether a study could support cumulative science, we used a subjective rating of replication success as our primary outcome measure.
 This measure was applicable across the diverse range of statistical measures and reporting practices present in the sample.
@@
 
-As a complement, we also used two statistical measure of replication on the subset of the data where they were computable (138 cases, see Figure \ref{fig:prisma}).
+As a complement, we also used two statistical measures of replication on the subset of the data where they were computable (136 cases, see Figure \ref{fig:prisma}).
 We measured p-original, the p-value on the null hypothesis that the original and replication statistics are from the same distribution, as a continuous variable, and we also determined whether the replication statistic fell within the prediction interval of the original statistic (\protect\hyperlink{ref-errington2021}{Errington et al.
@@
 \begin{figure}[ht]
-\includegraphics[width=1\linewidth,height=0.25\textheight]{manuscript_files/figure-latex/smd-1} \caption{Relationship between SMD of the original study, SMD of the replication study, and subjective replication success rating, for those studies where SMD was applicable.}\label{fig:smd}
+\includegraphics[width=1\linewidth,height=0.25\textheight]{manuscript_files/figure-latex/smd-1} \caption{Relationship between effect size of the original study, effect size of the replication study, and subjective replication success rating, for those studies where effect size was applicable.}\label{fig:smd}
 \end{figure}
@@
 Across the 176 studies, the overall subjective replication rate was 49\%.
-45\% (62/138) of the studies had replication outcomes within the prediction interval of the original outcome.
+45\% (61/136) of the studies had replication outcomes within the prediction interval of the original outcome.
 The median p\_original value was 0.03.
@@
 Here we took advantage of 11 years of graduate student replication projects to look at correlational predictors of replication in a previously-unused dataset.
-In line with previous results, we found a \texttt{r\ round(pluck(sub\_rep\_rate,1))}\% replication rate, with some studies showing effect sizes similar to the original and others much smaller.
+In line with previous results, we found a 49\% replication rate, with some studies showing effect sizes similar to the original and others much smaller.
 When we looked at individual correlates of replicability, within-subjects designs, work in the subfield of cognitive psychology, and the original and replication both using online samples stood out as the strongest correlates.
@@
 
-Students were free to choose what study to replicate; the recommended path for students who did not have their own ideas was to pick an interesting study from a recent year of Psychological Science (this led to a high fraction of Psych Science articles in the replication sample, 80, 45.4545455\% of studies).
+Students were free to choose what study to replicate; the recommended path for students who did not have their own ideas was to pick an interesting study from a recent year of Psychological Science (this led to a high fraction of Psych Science articles in the replication sample, 80, 45\% of studies).
 
@@
 For all studies, replication success was independently coded by VB on the basis of the reports.
-Where VB's coding disagreed with the staff/MCF's code, the difference was resolved by discussion between VB and MCF (25.5681818\% of studies).
+Where VB's coding disagreed with the staff/MCF's code, the difference was resolved by discussion between VB and MCF (26\% of studies).
 Subjective replication scores were coded on a {[}0, .25, .5, .75, 1{]} scale.

### 2023-04-29 paper/manuscript.Rmd
smoothed out results a little

@@
 PSYCH 251 is Stanford Psychology's graduate-level experimental methods class taught by MCF.
-During the 10 week class, students replicated a published finding.
+During the 10 week class, each student replicated a published finding.
 They individually re-implemented the study, wrote analysis code, pre-registered their study, collected data using an online platform, and wrote up a structured replication report.
@@
 Many different measures can be used to define replication success of an individual statistical result [@simonsohn2015; @gelman2018; @mathur2020].
-Because we operationalized replicability as whether a study could support cumulative science, we used a subjective rating of replication success as our primary outcome measure.
-This measure was applicable across the diverse range of statistical measures and reporting practices present in the sample.
-It, unlike statistical measures of replication, could easily accommodate studies where there were multiple important outcome measures that together defined the pattern of interest.
-A holistic measure of replication success had been coded for each project when it was turned in at the end of the class.
-For reliability, VB independently code the replication success from the replication reports; discrepancies were resolved by discussion between MCF and VB (`r round(pluck(matching,2,1)/176*100)`% of cases).
+However, a single test of a single statistical result doesn't capture the sense of whether a replication is close enough that one could feel confident extending the finding, so we used a subjective rating of replication success as our primary outcome measure.
+This subjective measure, unlike statistical measures, accommodated studies with multiple important outcome measures that together defined the pattern of interest and was applicable across the diverse range of statistical measures and reporting practices present in the sample.
+Importantly, a holistic measure of replication success had already been coded for most projects when they were turned in at the end of the class.
+For reliability, VB independently code the replication success from the students' written reports; discrepancies were resolved by discussion between MCF and VB (`r round(pluck(matching,2,1)/176*100)`% of cases).
 
-As a complement, we also used two statistical measures of replication on the subset of the data where they were computable (`r pluck(pred_int_avail,1)` cases, see Figure \ref{fig:prisma}).
-We measured p-original, the p-value on the null hypothesis that the original and replication statistics are from the same distribution, as a continuous variable, and we also determined whether the replication statistic fell within the prediction interval of the original statistic [@errington2021].
+As a complement to our primary subjective outcome, we also used two statistical measures of replication on the subset of the data where they were computable for the key statistic of interest (`r pluck(pred_int_avail,1)` cases, see Figure \ref{fig:prisma}).
+We used p-original, the p-value on the null hypothesis that the original and replication statistics are from the same distribution, and prediction interval, a binary measure of whether the replication statistic fell within the prediction interval of the original statistic [@errington2021].
 These both measure how similar the outcome estimates from the two sets of data are.
@@
 
-<!-- VERONICA IS HERE IN GOING BACK THROUGH --> 
 ## Overall replication rate
@@
 Figure \ref{fig:smd} shows the relationship between original standardized effect size, replication effect size, and subjective replication score.
-Roughly speaking, there's a cluster of studies that replicate with similar effect sizes to the original and another cluster that fail to replicate with replication effect sizes near zero.
-On average, there is a diminution of effect sizes from original to replication.
+Some studies replicated withed similar size effects to the original, and others failed to replicate, with replication effect sizes near zero.
+On average, there was a diminution of effect sizes from original to replication.
 
@@
 ## Single predictors
-Properties of both the original study and the replication can influence whether or not the replication is a success.
-We chose a set of predictor variables from the correlational results of RP:P and our own intuitions about experimental factors that might impact replication success as well as some covariates related to how close the replication was.
+We investigated what features of the original study and replication were correlated with replication success, with the goal of being able to identify potential markers of replicability.
+We chose a set of predictor variables based on the correlational results of RP:P [@openscienceconsortium2015], our own intuitions of experimental design factors that might impact replication success, and some covariates related to how close the replication was.
 A full description of these features is given in Methods.
@@
 Many predictors individually correlate with subjective replication success (Table \ref{tab:cor}).
-Predictors of higher replicability included within-subjects designs, higher numbers of trials, and the original study having open data.
-Predictors of lower replicability included single vignetted studies, social psychology studies, and original-replication pairs where the original study was in-person and replication switched to online.
+Predictors of higher replicability included within-subjects designs, larger numbers of trials, and the original study having open data.
+Predictors of lower replicability included single vignetted studies with only one induction or example per condition, social psychology studies, and original-replication pairs where the original study was in-person and replication switched to online.
 
 Distributions of study outcomes across some of these properties are shown in Figure \ref{fig:predictors-graph}.
-Both social and cognitive psychology studies were well represented, and the cognitive psychology studies replicated at `r round(1/subfield, 2)` times the rate of social psychology studies.
+Both social and cognitive psychology studies were well represented in the replication sample, and the cognitive psychology studies replicated at `r round(1/subfield, 2)` times the rate of social psychology studies.
 Within and between subjects designs were both common, and within-subjects designs replicated `r within |> round(2)` times as much.
-Similarly, studies with multiple vignettes replicated `r round(1/vignette, 2)` times more than single vignetted studies.
+Studies with multiple vignettes replicated `r round(1/vignette, 2)` times more than single vignetted studies.
 However, there were strong correlations among these experimental features and between these experimental features and subfield.
-Studies with open data, which almost always also had open materials, tended to replicate more than studies without open data, although this may be linked to temporal trends.
 
+Studies with open data, which almost always also had open materials, tended to replicate more than studies without open data.
 Nearly all replications studies were conducted online, but original studies were split between using in-person and online recruitment.
@@
 inductions may be weaker or attention checks inadequate to the new sample).
+These factors of open materials, open data, and online samples in original studies are more common in more recent studies, and so these effects may partially reflect temporal trends.
 
@@
 ## Regression model
-While a number of predictors show individual correlations with the subjective replication score, many of the predictors also correlate with one another.
+
+While a number of predictors show individual correlations with the subjective replication score, many of the predictors intercorrelate with one another.
 In order to determine which predictors were the strongest, we ran a series of pre-registered regularized regression models (see Methods for details; see Supplement for all estimates from all models).
@@
 The coefficient estimates from two models predicting the subjective replication scores are shown in Figure \ref{fig:mod-results}.
-Due to a large number of predictors coupled with a small and noisy dataset, even with strong regularization, there is much uncertainty around the coefficients.
+Due to a large number of predictors coupled with a small and noisy dataset there is much uncertainty around the coefficients even with strong regularization.
 The general directions of coefficients are consistent with the effects of the predictors in isolation.
@@
 
-# Discussion
-Prior large scale replications of psychology findings have estimated the replication rate at somewhere around 50%.
-This rate feels low, raising the question of what is causing so many studies not to replicate.
-However, limited numbers of replications and limited research into specific predictors of replication failure leave this an open question.
+# Discussioni
+
+MAY NEED SMOOTHER TRANSITIONS THROUGHOUT
+Prior large scale replications of psychology findings have estimated the replication rate at somewhere around one half, which intuitively feels low.
+However, limited numbers of replications and limited research into specific predictors of replication failure mean that the reasons for non-replications are not well understood.
 
@@
 
-Our metric of replicability was operationalized around the idea of whether a study could support cumulative science, so we looked at whether similar enough results could be obtained under the resource, expertise, and time constraints on early stage graduate students.
+Our metric of replicability was operationalized around the idea of whether a study could support cumulative science, so we considered whether results similar to the original could be obtained under the resource, expertise, and time constraints on early stage graduate students.
 We think this is a valuable estimand that is consistent with scientists' reasons for valuing replicability, but it is not the only estimand.
-Other replication projects have estimated replicabilty in other circumstances; for instance, @camerer2018 looks at likely studies are to replicate when performed by an expert with a large budget, and @ebersole2020 asks how likely certain studies are to replicate when performed with extensive feedback from the original authors.
+Other replication projects have estimated replicabilty in other circumstances; for instance, @camerer2018 looks at how likely studies are to replicate when performed by an expert with a large budget, and @ebersole2020 asks how likely certain studies are to replicate when performed with extensive feedback from the original authors.
 
 Replication results should be interpreted in light of their methods and estimand.
-We do not interpret our non-replications as indicating the original studies were false positives (presumably some were and some weren't).
+We do not interpret our non-replications as indicating the original results were false positives (presumably some were and some weren't).
 There are many possible reasons for the non-replications in this sample.
 In some cases, the problem may be with the replication, such as too few participants, many exclusions for failed attention checks, or participants speeding through the study.
-When these issues are diagnosed, they suggest possible ways to "rescue" the replication by fixing power or encouraging participants to take the task seriously, without altering the underlying experiment.
+When these issues are diagnosed, they suggest possible ways to "rescue" the replication by increasing the sample or changing the interface, without altering the underlying experiment.
 In other cases, there were a priori reasons to distrust the original study, such as exclusion criteria that seemed post-hoc or high-order interaction terms with a small sample.
-That said, not all scientists notice the same factors as potential indications of low power or questionable research practices; students conducting these replications generally expected them to succeed.
+That said, not all scientists recognize the same factors as potential indications of low power or questionable research practices; students conducting these replications generally expected them to succeed.
 In many non-replication cases, it was unclear why the results failed to replicate.
 
-We also caution in the interpretation of our predictor variables.
-Some of the correlates are most easily interpreted as being about the original study, and others seem to be more about the closeness of the replication to the original.
+We also caution the interpretation of our predictor variables.
+Some of the correlates are most easily interpreted as being about the original study, and others reflect the closeness of the replication to the original.
 This was a correlational design, so we cannot attribute causality to any of these factors.

### 2023-04-29 paper/manuscript.tex
smoothed out results a little

@@
 Many different measures can be used to define replication success of an individual statistical result (\protect\hyperlink{ref-simonsohn2015}{Simonsohn 2015}, \protect\hyperlink{ref-gelman2018}{Gelman 2018/ed}, \protect\hyperlink{ref-mathur2020}{Mathur \& VanderWeele 2020}).
-Because we operationalized replicability as whether a study could support cumulative science, we used a subjective rating of replication success as our primary outcome measure.
-This measure was applicable across the diverse range of statistical measures and reporting practices present in the sample.
-It, unlike statistical measures of replication, could easily accommodate studies where there were multiple important outcome measures that together defined the pattern of interest.
-A holistic measure of replication success had been coded for each project when it was turned in at the end of the class.
-For reliability, VB independently code the replication success from the replication reports; discrepancies were resolved by discussion between MCF and VB (26\% of cases).
+However, a single test of a single statistical result doesn't capture the sense of whether a replication is close enough that one could feel confident extending the finding, so we used a subjective rating of replication success as our primary outcome measure.
+This subjective measure, unlike statistical measures, accommodated studies with multiple important outcome measures that together defined the pattern of interest and was applicable across the diverse range of statistical measures and reporting practices present in the sample.
+Importantly, a holistic measure of replication success had already been coded for most projects when they were turned in at the end of the class.
+For reliability, VB independently code the replication success from the students' written reports; discrepancies were resolved by discussion between MCF and VB (26\% of cases).
 
-As a complement, we also used two statistical measures of replication on the subset of the data where they were computable (136 cases, see Figure \ref{fig:prisma}).
-We measured p-original, the p-value on the null hypothesis that the original and replication statistics are from the same distribution, as a continuous variable, and we also determined whether the replication statistic fell within the prediction interval of the original statistic (\protect\hyperlink{ref-errington2021}{Errington et al.
+As a complement to our primary subjective outcome, we also used two statistical measures of replication on the subset of the data where they were computable for the key statistic of interest (136 cases, see Figure \ref{fig:prisma}).
+We used p-original, the p-value on the null hypothesis that the original and replication statistics are from the same distribution, and prediction interval, a binary measure of whether the replication statistic fell within the prediction interval of the original statistic (\protect\hyperlink{ref-errington2021}{Errington et al.
 2021}).
@@
 
-Properties of both the original study and the replication can influence whether or not the replication is a success.
-We chose a set of predictor variables from the correlational results of RP:P and our own intuitions about experimental factors that might impact replication success as well as some covariates related to how close the replication was.
+We investigated what features of the original study and replication were correlated with replication success, with the goal of being able to identify potential markers of replicability.
+We chose a set of predictor variables based on the correlational results of RP:P (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}), our own intuitions of experimental design factors that might impact replication success, and some covariates related to how close the replication was.
 A full description of these features is given in Methods.
@@
 Many predictors individually correlate with subjective replication success (Table \ref{tab:cor}).
-Predictors of higher replicability included within-subjects designs, higher numbers of trials, and the original study having open data.
-Predictors of lower replicability included single vignetted studies, social psychology studies, and original-replication pairs where the original study was in-person and replication switched to online.
+Predictors of higher replicability included within-subjects designs, larger numbers of trials, and the original study having open data.
+Predictors of lower replicability included single vignetted studies with only one induction or example per condition, social psychology studies, and original-replication pairs where the original study was in-person and replication switched to online.
 
 Distributions of study outcomes across some of these properties are shown in Figure \ref{fig:predictors-graph}.
-Both social and cognitive psychology studies were well represented, and the cognitive psychology studies replicated at 2.45 times the rate of social psychology studies.
+Both social and cognitive psychology studies were well represented in the replication sample, and the cognitive psychology studies replicated at 2.45 times the rate of social psychology studies.
 Within and between subjects designs were both common, and within-subjects designs replicated 3.35 times as much.
-Similarly, studies with multiple vignettes replicated 2.62 times more than single vignetted studies.
+Studies with multiple vignettes replicated 2.62 times more than single vignetted studies.
 However, there were strong correlations among these experimental features and between these experimental features and subfield.
-Studies with open data, which almost always also had open materials, tended to replicate more than studies without open data, although this may be linked to temporal trends.
 
+Studies with open data, which almost always also had open materials, tended to replicate more than studies without open data.
 Nearly all replications studies were conducted online, but original studies were split between using in-person and online recruitment.
@@
 
-While a number of predictors show individual correlations with the subjective replication score, many of the predictors also correlate with one another.
+While a number of predictors show individual correlations with the subjective replication score, many of the predictors intercorrelate with one another.
 In order to determine which predictors were the strongest, we ran a series of pre-registered regularized regression models (see Methods for details; see Supplement for all estimates from all models).
@@
 
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
+\hypertarget{discussioni}{%
+\section{Discussioni}\label{discussioni}}
 
-Prior large scale replications of psychology findings have estimated the replication rate at somewhere around 50\%.
-This rate feels low, raising the question of what is causing so many studies not to replicate.
-However, limited numbers of replications and limited research into specific predictors of replication failure leave this an open question.
+MAY NEED SMOOTHER TRANSITIONS THROUGHOUT
+Prior large scale replications of psychology findings have estimated the replication rate at somewhere around one half, which intuitively feels low.
+However, limited numbers of replications and limited research into specific predictors of replication failure mean that the reasons for non-replications are not well understood.
 
@@
 
-Our metric of replicability was operationalized around the idea of whether a study could support cumulative science, so we looked at whether similar enough results could be obtained under the resource, expertise, and time constraints on early stage graduate students.
+Our metric of replicability was operationalized around the idea of whether a study could support cumulative science, so we considered whether results similar to the original could be obtained under the resource, expertise, and time constraints on early stage graduate students.
 We think this is a valuable estimand that is consistent with scientists' reasons for valuing replicability, but it is not the only estimand.
 Other replication projects have estimated replicabilty in other circumstances; for instance, Camerer et al.
-(\protect\hyperlink{ref-camerer2018}{2018}) looks at likely studies are to replicate when performed by an expert with a large budget, and Ebersole et al.
+(\protect\hyperlink{ref-camerer2018}{2018}) looks at how likely studies are to replicate when performed by an expert with a large budget, and Ebersole et al.
 (\protect\hyperlink{ref-ebersole2020}{2020}) asks how likely certain studies are to replicate when performed with extensive feedback from the original authors.
@@
 Replication results should be interpreted in light of their methods and estimand.
-We do not interpret our non-replications as indicating the original studies were false positives (presumably some were and some weren't).
+We do not interpret our non-replications as indicating the original results were false positives (presumably some were and some weren't).
 There are many possible reasons for the non-replications in this sample.
 In some cases, the problem may be with the replication, such as too few participants, many exclusions for failed attention checks, or participants speeding through the study.
-When these issues are diagnosed, they suggest possible ways to ``rescue'' the replication by fixing power or encouraging participants to take the task seriously, without altering the underlying experiment.
+When these issues are diagnosed, they suggest possible ways to ``rescue'' the replication by increasing the sample or changing the interface, without altering the underlying experiment.
 In other cases, there were a priori reasons to distrust the original study, such as exclusion criteria that seemed post-hoc or high-order interaction terms with a small sample.
-That said, not all scientists notice the same factors as potential indications of low power or questionable research practices; students conducting these replications generally expected them to succeed.
+That said, not all scientists recognize the same factors as potential indications of low power or questionable research practices; students conducting these replications generally expected them to succeed.
 In many non-replication cases, it was unclear why the results failed to replicate.
 
-We also caution in the interpretation of our predictor variables.
-Some of the correlates are most easily interpreted as being about the original study, and others seem to be more about the closeness of the replication to the original.
+We also caution the interpretation of our predictor variables.
+Some of the correlates are most easily interpreted as being about the original study, and others reflect the closeness of the replication to the original.
 This was a correlational design, so we cannot attribute causality to any of these factors.

### 2023-05-01 paper/manuscript.Rmd
trying to reframe intro

@@
 
-Cumulative scientific progress requires empirical results that are robust enough to support theory construction and future experimental extension.
-Yet in psychology, some prominent individual findings are have repeatedly failed to replicate, and large-scale investigations suggest that the overall replication rate is around half.
+Cumulative scientific progress requires empirical results that are robust enough to support theory construction and future extensions. 
+Yet in psychology, some prominent individual findings have failed to replicate, and large-scale investigations suggest *that failures to replicate are widespread.*
 What predicts which studies will replicate? 
-The identification of features that predict replication is limited by the common dataset of only 170 studies from large-scale investigations that are repeatedly analysed.
-We introduce a new sample of 176 replications conducted by students as part of a graduate-level experimental methods course, and we examine how often students were able replicate their chosen studies' results closely enough that they would be ready to build on it in future work.
+The identification of features that predict replication success is limited by data, however: most studies use a common dataset of only ~170 studies, *which vary in how they define replication.*
+We introduce a new dataset of 176 replications conducted by students as part of a graduate-level experimental methods course. 
+We examine how often students were able replicate their chosen studies' results closely enough that they would be ready to build on it in future work. 
 Using this as a metric of replicability, 49% of the studies in our sample replicate, with studies with larger original effect sizes and within-participants designs being more likely to replicate.
@@
 :::
+
+Alternative intro outline:
+
+* Cumulative science needs robust empirical results.
+
+* People had been assuming literature was robust which led to frustration and wasted resources (esp b/c pub bias, so failures hidden)
+
+* Non-replications question these assumptions
+
+* Replication is hard to define, both in terms of results and circumstances (CITE A BUNCH); previous work varied in methods, but their stated estimand was problematic.
+
+* Better to contextualize based on what circumstances & what metric means.
+One estimand we think is important and related to (one of the reasons) why people care is ability for normal scientist to do cumulative science under normal circumstances.
+
+* That's what we're able to estimate here given the study we have.
+
+??? How and where to work in the previous work, re-labelled by what they actual are estimating?
+
+* Then talk about predictors being important? And how we don't have enough data? And that our dataset will contribute to this question???
 

### 2023-05-03 paper/manuscript.Rmd
trying on intro

--- 2023-04-29 paper/manuscript.Rmd
@@
 
-Cumulative scientific progress requires empirical results that are robust enough to support theory construction and future experimental extension.
-Yet in psychology, some prominent individual findings are have repeatedly failed to replicate, and large-scale investigations suggest that the overall replication rate is around half.
+Cumulative scientific progress requires empirical results that are robust enough to support theory construction and future extensions. 
+Yet in psychology, some prominent individual findings have failed to replicate, and large-scale investigations suggest that failures to replicate are widespread.
 What predicts which studies will replicate? 
-The identification of features that predict replication is limited by the common dataset of only 170 studies from large-scale investigations that are repeatedly analysed.
-We introduce a new sample of 176 replications conducted by students as part of a graduate-level experimental methods course, and we examine how often students were able replicate their chosen studies' results closely enough that they would be ready to build on it in future work.
+The identification of features that predict replication success is limited by data, however: most studies use a common dataset of only ~170 studies, which vary in how they define replication.
+We introduce a new dataset of 176 replications conducted by students as part of a graduate-level experimental methods course. 
+We examine how often students were able replicate their chosen studies' results closely enough that they would be ready to build on it in future work. 
 Using this as a metric of replicability, 49% of the studies in our sample replicate, with studies with larger original effect sizes and within-participants designs being more likely to replicate.
-Consistent with prior reports, our replication results indicate that the robustness of the psychology literature is low enough to limit progress by student investigators.
+Consistent with prior reports, our results indicate that the robustness of the psychology literature is low enough to limit progress by student investigators.
 :::
-
-<!--introduction outline:
-
-Things don't replicate that well and it feels like a problem for cumulative science 
-* For a cumulative science, we want (many) of the load-bearing empirical results that form the bases of theories to hold up. 
-* People were acting as if publication of results meant they were true/reliable, trying to build on things; caused crises when some prominent results failed to replicate.
-Called into question reliability of literature as a whole -- lead to a few measurements.
-* Large scale replications of chunks of the literature, but aren't many (list and explain)
-* These rates feel lower than we want
-
-Why? Many approaches, no definitive answers.
-* Why are rates what they are. Both want to know to fix but also to watch out / calibrate caution. Can be approached from theoretical, interventional, and correlational dimensions.
-* Theoretical -- we know people do bad practices and can model how this leads to lower replicability. Requires things we already have ideas about
-* Interventional -- try things they think will make it better (like not doing bad practices), see what happens. Not everything is intervention prone, need to have strong belief first. Expensive!
-* Correlational -- markets/etc say there is some predictive value to be had, but don't say if it's transparent and explainable. RP:P.
-
-What's missing from the conversation and why our approach is good. 
-* There's been a lot of discussion around replicabilty and it's role and yadda yadda (much overfocused on RP:P results because that's what's available).
-Growing sophistication and valid points, but we think it misses the mark about what practicing scientists are concerned about.
-* Don't want to build on something and fail a bunch trying to get your variant to work and then realize it just doesn't work.
-Replicability (as we mean it here) A useful framing is "ability to do cumulative science" -- close to what people mean, may disagree with many things
-* How this approach differs and what it gets us
-    * (built in feasibility under reasonable / small resource constraints)
-    * interest based sampling 
-    * functional approach sidesteps issues of "truth" (may even be reliable in a different environment, but would be)
-
-Teaser:
-* We do x,y,z, and find that larger effect sizes and within subjects designs are the two strongest correlates of replicability in this sample.
-
-potential things to add to introduction:
-* why experimental design features? 
-* pedagogy
-* cut theoretical para?
--->
 
@@
 Cumulative science requires foundation empirical results that are robust enough to support theory construction and future experimental extension.
-If scientists attempt to build on top of results that cannot be achieved consistently, they waste resources looking for results where there may be none.
-This is frustrating for individual scientists and damaging to the enterprise of science overall.
-
-Scientists, policymakers, and the public often treat publication in a scientific journal as a signal that a result is (likely to be) true.
-This trust in published findings has led scientists to build on findings without verifying them first, but failures were often explained away and rarely published, leaving the original results uncontested in the literature, while failures to achieve the same outcomes accumulated in private.
-FIX PRIOR SENTENCE
-
-During the replication crisis, publicized failures to replicate published findings called into question the tacit assumption that most of the literature was robust and would replicate.
+Scientists often treat publication in a scientific journal as a signal that a result was (likely to be) true, which leads scientists to build on findings without verifying them first.
+Failed extensions are rarely published, so results often remained uncontested in the literature, even as undermining evidence accumulated in private.
+The replication crisis called into question the tacit assumption that most of the literature was robust and would replicate.
 Certain prominent findings failed to replicate in multi-site replication attempts [ex.
@@
 
-These failures to replicate raised the question: How replicable is psychology as a whole?
-Only three large-scale investigations address this question by sampling subsets of psychology findings.
-Reproducibility Project: Psychology, mentioned above, sampled roughly 100 studies from articles published in three top psychology journals in 2008 and found a overall replication rate of around 40% [@openscienceconsortium2015].
-ManyLabs investigated heterogeneity using short target studies that compared between two conditions each, but these studies are not representative of the psychology literature as a whole.
-Across Many Labs 1-3, 29 of 51 target effects (57%) replicated [@klein2014; @klein2018; @ebersole2016].
-@camerer2018 replicated all 21 behavioral social science studies from Nature and Science from 2010-2015 that were feasible; the replication rate was around 60%.
-Conducting large numbers of studies to assess replication rates is expensive and arduous which may explain why more large-scale investigations don't exist.
-These roughly 170 replications from these three investigations are the primary empirical results on which discussions of replication rates in psychology are based.
+[STILL ROUGH] When the trust in the literature mismatches the robustness results, many scientists can waste time and resources becoming frustrated pursuing extensions to a popular, but unreliable result.
+This seems to be the current situation of the literature, which leads to question: what do we do to minimize the waste?
+From a policy perspective, we need to understand the landscape of the problem before we can have research-informed science policy interventions.
+Thus, we might want to know 1) what quantity to measure if we want to capture frustration and waste due to non-cumulative findings and 2) from a descriptive perspective, what types of studies are most at risk for this issue.
+Such measurements have been the focus of much prior work, but there is limited consensus on what is being estimated.
 
-TRANSITION A replication rate around 50% runs counter to the prior assumption that most findings in the literature were robust enough to build upon without verification, and it raises the question: What makes the replication rates in psychology so low?
-
-<!--Theoretical approaches to understanding the replication rate have modeled how flexible research practices, selective reporting, and a bias toward positive results could lead to a high rate of (non-replicable) false positives (CITE).
-However, while scientists admit to engaging in these practices, we don't yet know what proportion of non-replications are driven by these factors or how to identify these studies in the literature.
--->
-
-Experimental approaches attempt to causally intervene on the low replication rate, by changing certain factors that may affect whether studies replicate.
-@protzko2020 showed, across 16 studies, that better methodological practices, such as transparency, large sample sizes, and confirmatory tests, led to replication rates that matched theoretical expectations based on the effect sizes and sample sizes, with replication effect sizes comparable with the original.
-Many Labs 5 examined how adding expert advice to a replication process might increase the replication rate, and found that it mainly did not for the 10 studies they looked at [@ebersole2020].
-These types of experiments are valuable for testing potential causes of non-replication, but they don't scale well due to expense.
-Additionally, not all potential influences on non-replication are experimentally manipulable.
-
-Correlational approaches looking for predictors of replicability are more popular.
-Prediction markets and elicitations have established that people can predict what studies will replicate above chance [@hoogeveen2019;@dreber2015; @forsell2019;@camerer2018], but have not identified concrete predictors that differentiate replications from non-replications.
-Using machine learning approaches, @altmejd2019 examined statistical and demographic features of studies and identified larger sample sizes, larger effect sizes, and simple effects (as opposed to interaction terms) as predictive of replication.
-@openscienceconsortium2015 looked at correlates of replicability in the RP:P sample and found that studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate.
-One potential set of correlates to replicabilty that has not been thoroughly examined are experimental design features, such as between or within subjects designs and repeated measures.
-
-TRANSITION / HOW TO FIT THIS PART IN Correlational approaches depend on data from replications, generally drawing heavily from the same small set of data points.
-In particular, the RP:P dataset itself is much discussed and reanalyzed [@etz2016;@gilbert2016;@patil2016;@anderson2016] to the point that much of what we think we know about replicability may be overfit to the 100 studies included in in RP:P.
-
-TRANSITION / DELETE ?
-Many of the discussions and reanalyses have raised questions about what the right metrics for measuring replicability are and what standards are reasonable to expect.
-Some of this contention is based around notions that failed replications are referenda on the truth of the original finding.
-
-TRANSITION!
 Prior approaches to replicability have focused on interpreting results in terms of a potentially problematic estimand: the probability of a finding in the literature being somehow truly replicable.
 Critics have pointed out that "true" replicability may not be possible to estimate outside of a specific sample [@vanbavel2016] or even time period [@ramscar].
-
 Further, the methods for estimating this quantity have been theoretically problematic.
@@
 
-In contrast to prior approaches, we have explicitly pursued a different estimand: the probability that a researcher, on selecting a finding of interest from the literature, can successfully achieve a result satisfactorily close enough to the original that they can build on it in their own work, with all the necessary compromises to the methods and sample of the original that may be required by the constraints of the situation.
+Three large-scale investigations have addressed replication rates in psychology, and we can reframe them by what they actually measure.
+Reproducibility Project: Psychology, mentioned above, sampled roughly 100 studies from articles published in three top psychology journals in 2008.
+Replication teams were given guidelines including checking protocols with original authors teams, but replication teams were left much discretion.
+This mimics how normal labs might do replications, and it resulted in an overall replication rate of around 40% [@openscienceconsortium2015].
+ManyLabs investigated heterogeneity using short target studies that compared between two conditions each.
+These study designs are not representative of the psychology literature as a whole, and due to the heterogeneity goal, they had large overall samples across multiple sites.
+Across Many Labs 1-3, in these high-powered replications, only 29 of 51 target effects (57%) replicated [@klein2014; @klein2018; @ebersole2016].
+@camerer2018 replicated all 21 behavioral social science studies from Nature and Science from 2010-2015 that were feasible; they consulted original authors and had high power to detect effects smaller than those reported.
+In this well-resourced environment with expert input, the replication rate was around 60%.
+These studies all measured replication rates, but the details of their methods and outcome measures varied.
+
+In our current study, we use student success at replicating an effect as our estimand.
+Students are often the ones conducting the research, so they should also be the ones doing the replications [@frank2012].
+In contrast to prior approaches, we are explicit about our actual estimand: the probability that a researcher, on selecting a finding of interest from the literature, can successfully achieve a result satisfactorily close enough to the original that they can build on it in their own work, with all the necessary compromises to the methods and sample of the original that may be required by the constraints of the situation.
 
@@
 
-Overall, we take a functional approach to assessing replicability, by framing both our methods and interpretation around the idea of whether work can be repeated or built on by an early-career scientist.
+Although prior large-scale replication studies have varied somewhat in their frameworks and precise definition of success, there is work suggesting some consistency in the predictors of replication success.
+Knowing these predictors is important for appropriately calibrating how we read the literature and for eventually identifying targets for interventions.
+
+Correlational approaches looking for predictors of replicability are more popular.
+Prediction markets and elicitations have established that people can predict what studies will replicate above chance [@hoogeveen2019;@dreber2015; @forsell2019;@camerer2018], but have not identified concrete predictors that differentiate replications from non-replications.
+Using machine learning approaches, @altmejd2019 examined statistical and demographic features of studies and identified larger sample sizes, larger effect sizes, and simple effects (as opposed to interaction terms) as predictive of replication.
+@openscienceconsortium2015 looked at correlates of replicability in the RP:P sample and found that studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate.
+One potential set of correlates to replicabilty that has not been thoroughly examined are experimental design features, such as between or within subjects designs and repeated measures.
+
+While Experimental approaches have tested a couple potential interventions.
+@protzko2020 showed, across 16 studies, that better methodological practices, such as transparency, large sample sizes, and confirmatory tests, led to replication rates that matched theoretical expectations based on the effect sizes and sample sizes, with replication effect sizes comparable with the original.
+Many Labs 5 added expert (original author) advice to a replication process, and found that it did not substantially increase the replication rate for the 10 studies [@ebersole2020].
+These types of experiments are valuable for testing potential causes of non-replication, that could be sites for interventions, but they don't scale well due to expense, and not all influences on non-replication may be experimentally manipulable.
+
+Given this, we are left with correlational appraches as a primary source.
+TRANSITION / HOW TO FIT THIS PART IN Correlational approaches depend on data from replications, generally drawing heavily from the same small set of data points.
+In particular, the RP:P dataset itself is much discussed and reanalyzed [@etz2016;@gilbert2016;@patil2016;@anderson2016] to the point that much of what we think we know about replicability may be overfit to the 100 studies included in in RP:P.
+We need more data to find potential targets of concern and intervention.
 
@@
 
-# Discussioni
+# Discussion
+
+## question, summary, and takehomes
 
@@
 However, limited numbers of replications and limited research into specific predictors of replication failure mean that the reasons for non-replications are not well understood.
+
+Overall, we take a functional approach to assessing replicability, by framing both our methods and interpretation around the idea of whether work can be repeated or built on by an early-career scientist.
+
+<!-- restatement of question -->
 
@@
 
+<!-- contributions and takehome  -->
+
+## intepretation - replication in light of the goal
+
+Replication results should be interpreted in light of their methods and estimand.
+
 Our metric of replicability was operationalized around the idea of whether a study could support cumulative science, so we considered whether results similar to the original could be obtained under the resource, expertise, and time constraints on early stage graduate students.
@@
 
-Replication results should be interpreted in light of their methods and estimand.
 We do not interpret our non-replications as indicating the original results were false positives (presumably some were and some weren't).
@@
 In many non-replication cases, it was unclear why the results failed to replicate.
+
+## limitations
+
+Observational/correlational study.
+
+Study sample
+
+Predictor interpretation
 
@@
 This estimand does not represent whether or not the original study was "true".
+
+## conclusion
 

### 2023-05-03 paper/manuscript.Rmd
flial at intro

@@
 
-Cumulative science requires foundation empirical results that are robust enough to support theory construction and future experimental extension.
+Cumulative science requires foundational empirical results that are robust enough to support theory construction and future experimental extension.
 Scientists often treat publication in a scientific journal as a signal that a result was (likely to be) true, which leads scientists to build on findings without verifying them first.
-Failed extensions are rarely published, so results often remained uncontested in the literature, even as undermining evidence accumulated in private.
 The replication crisis called into question the tacit assumption that most of the literature was robust and would replicate.
@@
 terror management theory, @klein2022; ego-depletion, @hagger2016], and a large-scale replication project pegged the replication rate for findings in top-tier psychology journals at around 40% [@openscienceconsortium2015].
+When the trust in the literature mismatches the robustness results, many scientists can waste time and resources becoming frustrated pursuing extensions to a popular, but unreliable result.
+This seems to be the current situation of the literature, which leads to question: what do we do to minimize the waste?
 
-[STILL ROUGH] When the trust in the literature mismatches the robustness results, many scientists can waste time and resources becoming frustrated pursuing extensions to a popular, but unreliable result.
-This seems to be the current situation of the literature, which leads to question: what do we do to minimize the waste?
 From a policy perspective, we need to understand the landscape of the problem before we can have research-informed science policy interventions.
@@
 
-Prior approaches to replicability have focused on interpreting results in terms of a potentially problematic estimand: the probability of a finding in the literature being somehow truly replicable.
-Critics have pointed out that "true" replicability may not be possible to estimate outside of a specific sample [@vanbavel2016] or even time period [@ramscar].
-Further, the methods for estimating this quantity have been theoretically problematic.
-Sampling schemes for prior work typically do not reflect an entirely random sample from the literature; instead they sample from specific journals where results may be of more interest and adjust the sample for feasibility concerns.
-These are reasonable sampling choices, but they undermine the claim that the estimand is the level of "truth" in the literature as a whole.
-Sampling truly at random from the literature may not even be desirable, as arguably a literature will succeed if useful discoveries come out of it, not if random findings are true [@wilson2020].
-The importance of a study being replicable is not uniformly distributed across the literature.
-
-Three large-scale investigations have addressed replication rates in psychology, and we can reframe them by what they actually measure.
-Reproducibility Project: Psychology, mentioned above, sampled roughly 100 studies from articles published in three top psychology journals in 2008.
-Replication teams were given guidelines including checking protocols with original authors teams, but replication teams were left much discretion.
-This mimics how normal labs might do replications, and it resulted in an overall replication rate of around 40% [@openscienceconsortium2015].
+Three large-scale investigations have addressed replication rates in psychology.
+Reproducibility Project: Psychology, mentioned above, sampled roughly 100 studies from articles published in three top psychology journals in 2008 and they found an overall replication rate of around 40% [@openscienceconsortium2015].
 ManyLabs investigated heterogeneity using short target studies that compared between two conditions each.
-These study designs are not representative of the psychology literature as a whole, and due to the heterogeneity goal, they had large overall samples across multiple sites.
+These study designs were not representative of the psychology literature as a whole, and due to the heterogeneity goal, they had large overall samples across multiple sites.
 Across Many Labs 1-3, in these high-powered replications, only 29 of 51 target effects (57%) replicated [@klein2014; @klein2018; @ebersole2016].
@@
 
+While their sampling and methods varied, these previous approaches to replicability have focused on interpreting their results in terms of a potentially problematic estimand: the probability of a finding in the literature being somehow truly replicable.
+Critics have pointed out that "true" replicability may not be possible to estimate outside of a specific sample [@vanbavel2016] or even time period [@ramscar].
+Further, the methods for estimating this quantity have been theoretically problematic.
+Sampling schemes did not reflect an entirely random sample from the literature; instead replication projects sampled from specific journals where results may be of more interest and adjusted the sample for feasibility concerns.
+These are reasonable sampling choices, but they undermine the claim that the estimand is the level of "truth" in the literature as a whole.
+Sampling truly at random from the literature may not even be desirable, as arguably a literature will succeed if useful discoveries come out of it, not if random findings are true [@wilson2020].
+The importance of a study being replicable is not uniformly distributed across the literature.
+
+Rather than aim for some measure of "true" replicability, it makes more sense to contextualize replication efforts based on their methods and outcome measures.
+With this lens, we could say that RP:P is looking at how well findings in well-known journals can be replicated in typical circumstances.
+Many Labs looked at which well-known two conditions studies replicate with huge samples, and @camerer2018 was looking at what replicates when conducted in a highly-resourced environment with expert involvement.
+All of these are pontentially desirable estimands depending on what the specific circumstances and questions of interest are.
+
+From the point of view of enabling cumulative science, an estimand of interest is how well work can be replicated by students, as students conduct most scientific work [@frank2022].
 In our current study, we use student success at replicating an effect as our estimand.
-Students are often the ones conducting the research, so they should also be the ones doing the replications [@frank2012].
-In contrast to prior approaches, we are explicit about our actual estimand: the probability that a researcher, on selecting a finding of interest from the literature, can successfully achieve a result satisfactorily close enough to the original that they can build on it in their own work, with all the necessary compromises to the methods and sample of the original that may be required by the constraints of the situation.
+In particular, our estimand is the probability that a researcher, on selecting a finding of interest from the literature, can successfully achieve a result satisfactorily close enough to the original that they can build on it in their own work, with all the necessary compromises to the methods and sample of the original that may be required by the constraints of the situation.
 
-NEED PUNCHY TRANSITION TO DETAILS Rather than sampling at random from some parts of the literature; our sample of studies is selected based on what studies students were interested in and wanting to replicate, with some filtering for feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable given methodological and budgetary constraints.
+Our replication approach reflects this estimand.
+Our sample of studies is selected based on what studies students were interested in and wanting to replicate, with some filtering for feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable given methodological and budgetary constraints.
 
@@
 
-All our replications were conducted under short time scales and relatively small budgets, which parallels the constraints many scientists are under when starting new projects.
+All our replications were conducted under short time scales and relatively small budgets, paralleling the constraints many scientists are under when starting new projects.
 From the point of view of cumulative science, researchers want to know if they can get paradigms to work under their real-world constraints.
-The same issue that may cause a study not to replicate under constrained circumstances (despite hypothetically replicating under more favorable circumstances such as expert administration or larger budgets) will also plague attempts to build off those studies in constrained circumstances.
-Thus, we believe it is relevant to estimate replicability under the limitations of real world resource and expertise constraints.
 
-Although prior large-scale replication studies have varied somewhat in their frameworks and precise definition of success, there is work suggesting some consistency in the predictors of replication success.
+Despite variation in how large-scale replication studies have defined replication successes, there is work suggesting some consistency in the predictors of replication success.
 Knowing these predictors is important for appropriately calibrating how we read the literature and for eventually identifying targets for interventions.
 
-Correlational approaches looking for predictors of replicability are more popular.
 Prediction markets and elicitations have established that people can predict what studies will replicate above chance [@hoogeveen2019;@dreber2015; @forsell2019;@camerer2018], but have not identified concrete predictors that differentiate replications from non-replications.
@@
 
-While Experimental approaches have tested a couple potential interventions.
-@protzko2020 showed, across 16 studies, that better methodological practices, such as transparency, large sample sizes, and confirmatory tests, led to replication rates that matched theoretical expectations based on the effect sizes and sample sizes, with replication effect sizes comparable with the original.
+Experimental approaches can be used to test potential interventions.
+@protzko2020 showed, across 16 studies, that better methodological practices led to replication rates that matched theoretical expectations with replication effect sizes comparable with the original.
 Many Labs 5 added expert (original author) advice to a replication process, and found that it did not substantially increase the replication rate for the 10 studies [@ebersole2020].
-These types of experiments are valuable for testing potential causes of non-replication, that could be sites for interventions, but they don't scale well due to expense, and not all influences on non-replication may be experimentally manipulable.
+These types of experiments are valuable for testing potential causes of non-replication, but they don't scale well due to expense, and not all influences on non-replication may be experimentally manipulable.
 
-Given this, we are left with correlational appraches as a primary source.
-TRANSITION / HOW TO FIT THIS PART IN Correlational approaches depend on data from replications, generally drawing heavily from the same small set of data points.
+Given the limitations of experimental approaches, we have to rely on correlational approaches for now.
+Correlational approaches depend on data from replications, generally drawing heavily from the same small set of data points.
 In particular, the RP:P dataset itself is much discussed and reanalyzed [@etz2016;@gilbert2016;@patil2016;@anderson2016] to the point that much of what we think we know about replicability may be overfit to the 100 studies included in in RP:P.
@@
 
+NEED TO REDO! 
 MAY NEED SMOOTHER TRANSITIONS THROUGHOUT
@@
 <!-- contributions and takehome  -->
-
+ The same issue that may cause a study not to replicate under constrained circumstances (despite hypothetically replicating under more favorable circumstances such as expert administration or larger budgets) will also plague attempts to build off those studies in constrained circumstances.
+Thus, we believe it is relevant to estimate replicability under the limitations of real world resource and expertise constraints.
 ## intepretation - replication in light of the goal
@@
 
-Our metric of replicability was operationalized around the idea of whether a study could support cumulative science, so we considered whether results similar to the original could be obtained under the resource, expertise, and time constraints on early stage graduate students.
-We think this is a valuable estimand that is consistent with scientists' reasons for valuing replicability, but it is not the only estimand.
-Other replication projects have estimated replicabilty in other circumstances; for instance, @camerer2018 looks at how likely studies are to replicate when performed by an expert with a large budget, and @ebersole2020 asks how likely certain studies are to replicate when performed with extensive feedback from the original authors.
-
+Given our sample, we are able to estimate the correlates of studies replicating when the replications are conducted online, by graduate students with limited time and budget.
 We do not interpret our non-replications as indicating the original results were false positives (presumably some were and some weren't).
@@
 In some cases, the problem may be with the replication, such as too few participants, many exclusions for failed attention checks, or participants speeding through the study.
-When these issues are diagnosed, they suggest possible ways to "rescue" the replication by increasing the sample or changing the interface, without altering the underlying experiment.
+When these issues are diagnosed, they suggest possible ways to "rescue" the replication by increasing the sample or changing the interface, without altering the underlying experiment; thus, while the replication did not succeed, after some troubleshooting, students may still be able to extend the work in the future.
 In other cases, there were a priori reasons to distrust the original study, such as exclusion criteria that seemed post-hoc or high-order interaction terms with a small sample.
@@
 
-Observational/correlational study.
-
-Study sample
-
-Predictor interpretation
-
-We also caution the interpretation of our predictor variables.
+We conducted an observational study of replication attempts, and our results are limited by the studies we included, which are limited in number and may not be representative of the studies of interest to psychologists as a whole.
+Our predictor variables were not manipulated, so they cannot be interpreted as causing (non-) replication, but only as correlational markers.
 Some of the correlates are most easily interpreted as being about the original study, and others reflect the closeness of the replication to the original.
-This was a correlational design, so we cannot attribute causality to any of these factors.
 For instance, while within-subjects designs are more likely to replicate than between-subjects designs, this could be related to power, or the types of experiments that tend to be run in each design.
 Given the predictive value, slightly more skepticism and critical reading of between-subjects designs may be warranted, but this correlation, by itself, does not mean scientists should prefer to run within-subjects designs.
-
-Our results are limited by the number and quality of the studies we included.
-These studies are not necessarily representative of the studies of interest to psychologists as a whole.
-The replication studies were not designed from the start with this analysis in mind, so analysis is limited by the choices and reporting used at the time of replications.
-We reiterate that given our sample, we are able to estimate the correlates of studies replicating when the replications are conducted online, by graduate students with limited time and budget.
-This estimand is not the same as whether they would replicate when done by large labs with access to more money and experts.
-This estimand does not represent whether or not the original study was "true".
 

### 2023-05-03 paper/manuscript.tex
flial at intro

@@
 \begin{abstract}
-Cumulative scientific progress requires empirical results that are robust enough to support theory construction and future experimental extension.
-Yet in psychology, some prominent individual findings are have repeatedly failed to replicate, and large-scale investigations suggest that the overall replication rate is around half.
+Cumulative scientific progress requires empirical results that are robust enough to support theory construction and future extensions.
+Yet in psychology, some prominent individual findings have failed to replicate, and large-scale investigations suggest that failures to replicate are widespread.
 What predicts which studies will replicate?
-The identification of features that predict replication is limited by the common dataset of only 170 studies from large-scale investigations that are repeatedly analysed.
-We introduce a new sample of 176 replications conducted by students as part of a graduate-level experimental methods course, and we examine how often students were able replicate their chosen studies' results closely enough that they would be ready to build on it in future work.
+The identification of features that predict replication success is limited by data, however: most studies use a common dataset of only \textasciitilde170 studies, which vary in how they define replication.
+We introduce a new dataset of 176 replications conducted by students as part of a graduate-level experimental methods course.
+We examine how often students were able replicate their chosen studies' results closely enough that they would be ready to build on it in future work.
 Using this as a metric of replicability, 49\% of the studies in our sample replicate, with studies with larger original effect sizes and within-participants designs being more likely to replicate.
-Consistent with prior reports, our replication results indicate that the robustness of the psychology literature is low enough to limit progress by student investigators.
+Consistent with prior reports, our results indicate that the robustness of the psychology literature is low enough to limit progress by student investigators.
 
@@
 
-Cumulative science requires foundation empirical results that are robust enough to support theory construction and future experimental extension.
-If scientists attempt to build on top of results that cannot be achieved consistently, they waste resources looking for results where there may be none.
-This is frustrating for individual scientists and damaging to the enterprise of science overall.
-
-Scientists, policymakers, and the public often treat publication in a scientific journal as a signal that a result is (likely to be) true.
-This trust in published findings has led scientists to build on findings without verifying them first, but failures were often explained away and rarely published, leaving the original results uncontested in the literature, while failures to achieve the same outcomes accumulated in private.
-FIX PRIOR SENTENCE
-
-During the replication crisis, publicized failures to replicate published findings called into question the tacit assumption that most of the literature was robust and would replicate.
+Cumulative science requires foundational empirical results that are robust enough to support theory construction and future experimental extension.
+Scientists often treat publication in a scientific journal as a signal that a result was (likely to be) true, which leads scientists to build on findings without verifying them first.
+The replication crisis called into question the tacit assumption that most of the literature was robust and would replicate.
 Certain prominent findings failed to replicate in multi-site replication attempts (ex.
@@
 2016}), and a large-scale replication project pegged the replication rate for findings in top-tier psychology journals at around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}).
+When the trust in the literature mismatches the robustness results, many scientists can waste time and resources becoming frustrated pursuing extensions to a popular, but unreliable result.
+This seems to be the current situation of the literature, which leads to question: what do we do to minimize the waste?
 
-These failures to replicate raised the question: How replicable is psychology as a whole?
-Only three large-scale investigations address this question by sampling subsets of psychology findings.
-Reproducibility Project: Psychology, mentioned above, sampled roughly 100 studies from articles published in three top psychology journals in 2008 and found a overall replication rate of around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}).
-ManyLabs investigated heterogeneity using short target studies that compared between two conditions each, but these studies are not representative of the psychology literature as a whole.
-Across Many Labs 1-3, 29 of 51 target effects (57\%) replicated (\protect\hyperlink{ref-klein2014}{Klein et al.
+From a policy perspective, we need to understand the landscape of the problem before we can have research-informed science policy interventions.
+Thus, we might want to know 1) what quantity to measure if we want to capture frustration and waste due to non-cumulative findings and 2) from a descriptive perspective, what types of studies are most at risk for this issue.
+Such measurements have been the focus of much prior work, but there is limited consensus on what is being estimated.
+
+Three large-scale investigations have addressed replication rates in psychology.
+Reproducibility Project: Psychology, mentioned above, sampled roughly 100 studies from articles published in three top psychology journals in 2008 and they found an overall replication rate of around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}).
+ManyLabs investigated heterogeneity using short target studies that compared between two conditions each.
+These study designs were not representative of the psychology literature as a whole, and due to the heterogeneity goal, they had large overall samples across multiple sites.
+Across Many Labs 1-3, in these high-powered replications, only 29 of 51 target effects (57\%) replicated (\protect\hyperlink{ref-klein2014}{Klein et al.
 2014}, \protect\hyperlink{ref-ebersole2016}{Ebersole et al.
@@
 Camerer et al.
-(\protect\hyperlink{ref-camerer2018}{2018}) replicated all 21 behavioral social science studies from Nature and Science from 2010-2015 that were feasible; the replication rate was around 60\%.
-Conducting large numbers of studies to assess replication rates is expensive and arduous which may explain why more large-scale investigations don't exist.
-These roughly 170 replications from these three investigations are the primary empirical results on which discussions of replication rates in psychology are based.
+(\protect\hyperlink{ref-camerer2018}{2018}) replicated all 21 behavioral social science studies from Nature and Science from 2010-2015 that were feasible; they consulted original authors and had high power to detect effects smaller than those reported.
+In this well-resourced environment with expert input, the replication rate was around 60\%.
+These studies all measured replication rates, but the details of their methods and outcome measures varied.
 
-TRANSITION A replication rate around 50\% runs counter to the prior assumption that most findings in the literature were robust enough to build upon without verification, and it raises the question: What makes the replication rates in psychology so low?
+While their sampling and methods varied, these previous approaches to replicability have focused on interpreting their results in terms of a potentially problematic estimand: the probability of a finding in the literature being somehow truly replicable.
+Critics have pointed out that ``true'' replicability may not be possible to estimate outside of a specific sample (\protect\hyperlink{ref-vanbavel2016}{Van Bavel et al.
+2016}) or even time period (\protect\hyperlink{ref-ramscar}{Ramscar et al.
+n.d.}).
+Further, the methods for estimating this quantity have been theoretically problematic.
+Sampling schemes did not reflect an entirely random sample from the literature; instead replication projects sampled from specific journals where results may be of more interest and adjusted the sample for feasibility concerns.
+These are reasonable sampling choices, but they undermine the claim that the estimand is the level of ``truth'' in the literature as a whole.
+Sampling truly at random from the literature may not even be desirable, as arguably a literature will succeed if useful discoveries come out of it, not if random findings are true (\protect\hyperlink{ref-wilson2020}{Wilson et al.
+2020}).
+The importance of a study being replicable is not uniformly distributed across the literature.
 
-Experimental approaches attempt to causally intervene on the low replication rate, by changing certain factors that may affect whether studies replicate.
-Protzko et al.
-(\protect\hyperlink{ref-protzko2020}{2020}) showed, across 16 studies, that better methodological practices, such as transparency, large sample sizes, and confirmatory tests, led to replication rates that matched theoretical expectations based on the effect sizes and sample sizes, with replication effect sizes comparable with the original.
-Many Labs 5 examined how adding expert advice to a replication process might increase the replication rate, and found that it mainly did not for the 10 studies they looked at (\protect\hyperlink{ref-ebersole2020}{Ebersole et al.
-2020}).
-These types of experiments are valuable for testing potential causes of non-replication, but they don't scale well due to expense.
-Additionally, not all potential influences on non-replication are experimentally manipulable.
+Rather than aim for some measure of ``true'' replicability, it makes more sense to contextualize replication efforts based on their methods and outcome measures.
+With this lens, we could say that RP:P is looking at how well findings in well-known journals can be replicated in typical circumstances.
+Many Labs looked at which well-known two conditions studies replicate with huge samples, and Camerer et al.
+(\protect\hyperlink{ref-camerer2018}{2018}) was looking at what replicates when conducted in a highly-resourced environment with expert involvement.
+All of these are pontentially desirable estimands depending on what the specific circumstances and questions of interest are.
 
-Correlational approaches looking for predictors of replicability are more popular.
+From the point of view of enabling cumulative science, an estimand of interest is how well work can be replicated by students, as students conduct most scientific work (\protect\hyperlink{ref-frank2022}{\textbf{frank2022?}}).
+In our current study, we use student success at replicating an effect as our estimand.
+In particular, our estimand is the probability that a researcher, on selecting a finding of interest from the literature, can successfully achieve a result satisfactorily close enough to the original that they can build on it in their own work, with all the necessary compromises to the methods and sample of the original that may be required by the constraints of the situation.
+
+Our replication approach reflects this estimand.
+Our sample of studies is selected based on what studies students were interested in and wanting to replicate, with some filtering for feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable given methodological and budgetary constraints.
+
+We use a subjective replication score as our primary metric.
+Whether one feels confident in the results of a study given a replication is not always dependent on only one outcome measure (ex.
+interaction term) and particularly not dependent on only one statistical comparison between the two studies (ex.
+replication is p\textless.05 same direction as original).
+This metric avoids bright line distinctions and accommodates the range of outcome measures in our diverse set of studies.
+
+All our replications were conducted under short time scales and relatively small budgets, paralleling the constraints many scientists are under when starting new projects.
+From the point of view of cumulative science, researchers want to know if they can get paradigms to work under their real-world constraints.
+
+Despite variation in how large-scale replication studies have defined replication successes, there is work suggesting some consistency in the predictors of replication success.
+Knowing these predictors is important for appropriately calibrating how we read the literature and for eventually identifying targets for interventions.
+
 Prediction markets and elicitations have established that people can predict what studies will replicate above chance (\protect\hyperlink{ref-dreber2015}{Dreber et al.
@@
 
-TRANSITION / HOW TO FIT THIS PART IN Correlational approaches depend on data from replications, generally drawing heavily from the same small set of data points.
+Experimental approaches can be used to test potential interventions.
+Protzko et al.
+(\protect\hyperlink{ref-protzko2020}{2020}) showed, across 16 studies, that better methodological practices led to replication rates that matched theoretical expectations with replication effect sizes comparable with the original.
+Many Labs 5 added expert (original author) advice to a replication process, and found that it did not substantially increase the replication rate for the 10 studies (\protect\hyperlink{ref-ebersole2020}{Ebersole et al.
+2020}).
+These types of experiments are valuable for testing potential causes of non-replication, but they don't scale well due to expense, and not all influences on non-replication may be experimentally manipulable.
+
+Given the limitations of experimental approaches, we have to rely on correlational approaches for now.
+Correlational approaches depend on data from replications, generally drawing heavily from the same small set of data points.
 In particular, the RP:P dataset itself is much discussed and reanalyzed (\protect\hyperlink{ref-anderson2016}{Anderson et al.
@@
 2016}) to the point that much of what we think we know about replicability may be overfit to the 100 studies included in in RP:P.
-
-TRANSITION / DELETE ?
-Many of the discussions and reanalyses have raised questions about what the right metrics for measuring replicability are and what standards are reasonable to expect.
-Some of this contention is based around notions that failed replications are referenda on the truth of the original finding.
-
-TRANSITION!
-Prior approaches to replicability have focused on interpreting results in terms of a potentially problematic estimand: the probability of a finding in the literature being somehow truly replicable.
-Critics have pointed out that ``true'' replicability may not be possible to estimate outside of a specific sample (\protect\hyperlink{ref-vanbavel2016}{Van Bavel et al.
-2016}) or even time period (\protect\hyperlink{ref-ramscar}{Ramscar et al.
-n.d.}).
-
-Further, the methods for estimating this quantity have been theoretically problematic.
-Sampling schemes for prior work typically do not reflect an entirely random sample from the literature; instead they sample from specific journals where results may be of more interest and adjust the sample for feasibility concerns.
-These are reasonable sampling choices, but they undermine the claim that the estimand is the level of ``truth'' in the literature as a whole.
-Sampling truly at random from the literature may not even be desirable, as arguably a literature will succeed if useful discoveries come out of it, not if random findings are true (\protect\hyperlink{ref-wilson2020}{Wilson et al.
-2020}).
-The importance of a study being replicable is not uniformly distributed across the literature.
-
-In contrast to prior approaches, we have explicitly pursued a different estimand: the probability that a researcher, on selecting a finding of interest from the literature, can successfully achieve a result satisfactorily close enough to the original that they can build on it in their own work, with all the necessary compromises to the methods and sample of the original that may be required by the constraints of the situation.
-
-NEED PUNCHY TRANSITION TO DETAILS Rather than sampling at random from some parts of the literature; our sample of studies is selected based on what studies students were interested in and wanting to replicate, with some filtering for feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable given methodological and budgetary constraints.
-
-We use a subjective replication score as our primary metric.
-Whether one feels confident in the results of a study given a replication is not always dependent on only one outcome measure (ex.
-interaction term) and particularly not dependent on only one statistical comparison between the two studies (ex.
-replication is p\textless.05 same direction as original).
-This metric avoids bright line distinctions and accommodates the range of outcome measures in our diverse set of studies.
-
-All our replications were conducted under short time scales and relatively small budgets, which parallels the constraints many scientists are under when starting new projects.
-From the point of view of cumulative science, researchers want to know if they can get paradigms to work under their real-world constraints.
-The same issue that may cause a study not to replicate under constrained circumstances (despite hypothetically replicating under more favorable circumstances such as expert administration or larger budgets) will also plague attempts to build off those studies in constrained circumstances.
-Thus, we believe it is relevant to estimate replicability under the limitations of real world resource and expertise constraints.
-
-Overall, we take a functional approach to assessing replicability, by framing both our methods and interpretation around the idea of whether work can be repeated or built on by an early-career scientist.
+We need more data to find potential targets of concern and intervention.
 
@@
 
-\hypertarget{discussioni}{%
-\section{Discussioni}\label{discussioni}}
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
 
+\hypertarget{question-summary-and-takehomes}{%
+\subsection{question, summary, and takehomes}\label{question-summary-and-takehomes}}
+
+NEED TO REDO!
 MAY NEED SMOOTHER TRANSITIONS THROUGHOUT
@@
 However, limited numbers of replications and limited research into specific predictors of replication failure mean that the reasons for non-replications are not well understood.
+
+Overall, we take a functional approach to assessing replicability, by framing both our methods and interpretation around the idea of whether work can be repeated or built on by an early-career scientist.
 
@@
 
-Our metric of replicability was operationalized around the idea of whether a study could support cumulative science, so we considered whether results similar to the original could be obtained under the resource, expertise, and time constraints on early stage graduate students.
-We think this is a valuable estimand that is consistent with scientists' reasons for valuing replicability, but it is not the only estimand.
-Other replication projects have estimated replicabilty in other circumstances; for instance, Camerer et al.
-(\protect\hyperlink{ref-camerer2018}{2018}) looks at how likely studies are to replicate when performed by an expert with a large budget, and Ebersole et al.
-(\protect\hyperlink{ref-ebersole2020}{2020}) asks how likely certain studies are to replicate when performed with extensive feedback from the original authors.
+The same issue that may cause a study not to replicate under constrained circumstances (despite hypothetically replicating under more favorable circumstances such as expert administration or larger budgets) will also plague attempts to build off those studies in constrained circumstances.
+Thus, we believe it is relevant to estimate replicability under the limitations of real world resource and expertise constraints.
+\#\# intepretation - replication in light of the goal
 
 Replication results should be interpreted in light of their methods and estimand.
+
+Given our sample, we are able to estimate the correlates of studies replicating when the replications are conducted online, by graduate students with limited time and budget.
 We do not interpret our non-replications as indicating the original results were false positives (presumably some were and some weren't).
@@
 In some cases, the problem may be with the replication, such as too few participants, many exclusions for failed attention checks, or participants speeding through the study.
-When these issues are diagnosed, they suggest possible ways to ``rescue'' the replication by increasing the sample or changing the interface, without altering the underlying experiment.
+When these issues are diagnosed, they suggest possible ways to ``rescue'' the replication by increasing the sample or changing the interface, without altering the underlying experiment; thus, while the replication did not succeed, after some troubleshooting, students may still be able to extend the work in the future.
 In other cases, there were a priori reasons to distrust the original study, such as exclusion criteria that seemed post-hoc or high-order interaction terms with a small sample.
@@
 
-We also caution the interpretation of our predictor variables.
+\hypertarget{limitations}{%
+\subsection{limitations}\label{limitations}}
+
+We conducted an observational study of replication attempts, and our results are limited by the studies we included, which are limited in number and may not be representative of the studies of interest to psychologists as a whole.
+Our predictor variables were not manipulated, so they cannot be interpreted as causing (non-) replication, but only as correlational markers.
 Some of the correlates are most easily interpreted as being about the original study, and others reflect the closeness of the replication to the original.
-This was a correlational design, so we cannot attribute causality to any of these factors.
 For instance, while within-subjects designs are more likely to replicate than between-subjects designs, this could be related to power, or the types of experiments that tend to be run in each design.
@@
 
-Our results are limited by the number and quality of the studies we included.
-These studies are not necessarily representative of the studies of interest to psychologists as a whole.
-The replication studies were not designed from the start with this analysis in mind, so analysis is limited by the choices and reporting used at the time of replications.
-We reiterate that given our sample, we are able to estimate the correlates of studies replicating when the replications are conducted online, by graduate students with limited time and budget.
-This estimand is not the same as whether they would replicate when done by large labs with access to more money and experts.
-This estimand does not represent whether or not the original study was ``true''.
+\hypertarget{conclusion}{%
+\subsection{conclusion}\label{conclusion}}
 

### 2023-05-04 paper/manuscript.Rmd
another pass at intro and disc

@@
 
-Cumulative science requires foundational empirical results that are robust enough to support theory construction and future experimental extension.
-Scientists often treat publication in a scientific journal as a signal that a result was (likely to be) true, which leads scientists to build on findings without verifying them first.
-The replication crisis called into question the tacit assumption that most of the literature was robust and would replicate.
-Certain prominent findings failed to replicate in multi-site replication attempts [ex.
+ Cumulative scientific progress requires empirical results that are robust enough to support theory construction and future extensions.
+Yet in psychology, some prominent individual findings have failed to replicate in multi-site replication attempts [ex.
 terror management theory, @klein2022; ego-depletion, @hagger2016], and a large-scale replication project pegged the replication rate for findings in top-tier psychology journals at around 40% [@openscienceconsortium2015].
-When the trust in the literature mismatches the robustness results, many scientists can waste time and resources becoming frustrated pursuing extensions to a popular, but unreliable result.
-This seems to be the current situation of the literature, which leads to question: what do we do to minimize the waste?
+When scientists treat publication as a signal of truth and attempt to build on results without verifying them first, they can become frustrated pursuing extensions to a popular, but unreliable result.
+As each failed extension does not directly contradict the original result, many scientists may waste a lot of time and resources pursuing results where there may be none.
+This leads to a question: what do we do to minimize the waste?
+
+[This feels like we're setting up for the advice: don't try to extend anything without replicating it first, not sure how to shift to the policy issue.]
 
@@
 Thus, we might want to know 1) what quantity to measure if we want to capture frustration and waste due to non-cumulative findings and 2) from a descriptive perspective, what types of studies are most at risk for this issue.
-Such measurements have been the focus of much prior work, but there is limited consensus on what is being estimated.
+Such measurements have been the focus of much prior work around replicability, but there is limited consensus on what is being estimated.
 
-Three large-scale investigations have addressed replication rates in psychology.
-Reproducibility Project: Psychology, mentioned above, sampled roughly 100 studies from articles published in three top psychology journals in 2008 and they found an overall replication rate of around 40% [@openscienceconsortium2015].
+Three large-scale investigations have measured replication rates in samples of psychology studies.
+Reproducibility Project: Psychology sampled roughly 100 studies from articles published in three top psychology journals in 2008 and distributed the studies across participanting labs.
+They found an overall replication rate of around 40% [@openscienceconsortium2015].
 ManyLabs investigated heterogeneity using short target studies that compared between two conditions each.
@@
 Across Many Labs 1-3, in these high-powered replications, only 29 of 51 target effects (57%) replicated [@klein2014; @klein2018; @ebersole2016].
-@camerer2018 replicated all 21 behavioral social science studies from Nature and Science from 2010-2015 that were feasible; they consulted original authors and had high power to detect effects smaller than those reported.
+@camerer2018 included all 21 behavioral social science studies from Nature and Science from 2010-2015 that were feasible; they consulted original authors and had high power to detect effects smaller than those reported.
 In this well-resourced environment with expert input, the replication rate was around 60%.
-These studies all measured replication rates, but the details of their methods and outcome measures varied.
 
@@
 Rather than aim for some measure of "true" replicability, it makes more sense to contextualize replication efforts based on their methods and outcome measures.
-With this lens, we could say that RP:P is looking at how well findings in well-known journals can be replicated in typical circumstances.
-Many Labs looked at which well-known two conditions studies replicate with huge samples, and @camerer2018 was looking at what replicates when conducted in a highly-resourced environment with expert involvement.
-All of these are pontentially desirable estimands depending on what the specific circumstances and questions of interest are.
+With this lens, we could say that RP:P looked at how well findings in well-known journals can be replicated in a typical psychology lab.
+Many Labs looked at which well-known two conditions studies replicate with huge samples, and @camerer2018 looked at which prestigious journal findings replicate when conducted in a highly-resourced environment with expert involvement.
+All of these are potentially desirable estimands depending on what the specific circumstances and questions of interest are.
 
-From the point of view of enabling cumulative science, an estimand of interest is how well work can be replicated by students, as students conduct most scientific work [@frank2022].
+Most scientific work is conducted by student, so it makes sense for students to conduct replications  [@frank2022].
 In our current study, we use student success at replicating an effect as our estimand.
@@
 Our sample of studies is selected based on what studies students were interested in and wanting to replicate, with some filtering for feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable given methodological and budgetary constraints.
-
+All our replications were conducted under short time scales and relatively small budgets, paralleling the constraints many scientists are under when starting new projects.
+From the point of view of cumulative science, researchers want to know if they can get paradigms to work under their real-world constraints.
 We use a subjective replication score as our primary metric.
@@
 This metric avoids bright line distinctions and accommodates the range of outcome measures in our diverse set of studies.
-
-All our replications were conducted under short time scales and relatively small budgets, paralleling the constraints many scientists are under when starting new projects.
-From the point of view of cumulative science, researchers want to know if they can get paradigms to work under their real-world constraints.
 
@@
 
-Given the limitations of experimental approaches, we have to rely on correlational approaches for now.
+Given the limitations of experimental approaches, correlational approaches are the more popular choice for studying potential predictors of replicability.
 Correlational approaches depend on data from replications, generally drawing heavily from the same small set of data points.
 In particular, the RP:P dataset itself is much discussed and reanalyzed [@etz2016;@gilbert2016;@patil2016;@anderson2016] to the point that much of what we think we know about replicability may be overfit to the 100 studies included in in RP:P.
-We need more data to find potential targets of concern and intervention.
+More data is needed to identify markers of replicability and targets for potential future interventions.
 
 Our contribution is a new dataset of 176 replications of experimental studies from the social sciences, primarily psychology.
-These replications were conducted by students in graduate-level experimental methods class between 2011 and 2022 as individual course projects.
+These replications were conducted by students in a graduate-level experimental methods class between 2011 and 2022 as individual course projects.
 We investigated statistical and experimental-design predictors of replicability in this dataset and found that within-subjects designs and studies with large standardized effect sizes were positively correlated with replication success.
@@
 
-## question, summary, and takehomes
-
-NEED TO REDO! 
-MAY NEED SMOOTHER TRANSITIONS THROUGHOUT
-Prior large scale replications of psychology findings have estimated the replication rate at somewhere around one half, which intuitively feels low.
+Researchers use the psychological literature as a source of empirical results that they can build upon and extend as part of cumulative science.
+When these findings don't replicate, the attempts to extend them are a waste of time and resources.
+In order to eventually reduce this waste, we need to be able to identify when results can support cumulative scientific progress and what study features are predictive of this.
 However, limited numbers of replications and limited research into specific predictors of replication failure mean that the reasons for non-replications are not well understood.
 
-Overall, we take a functional approach to assessing replicability, by framing both our methods and interpretation around the idea of whether work can be repeated or built on by an early-career scientist.
-
-<!-- restatement of question -->
-
-Here we took advantage of 11 years of graduate student replication projects to look at correlational predictors of replication in a previously-unused dataset.
+Here, we take a functional approach to assessing replicability, framing both our methods and interpretation around the idea of whether work can be repeated by an early-career scientist.
+We took advantage of 11 years of graduate student replication projects to look at correlational predictors of replication in a previously-unused dataset.
 In line with previous results, we found a `r round(pluck(sub_rep_rate,1))`% replication rate, with some studies showing effect sizes similar to the original and others much smaller.
@@
 <!-- contributions and takehome  -->
- The same issue that may cause a study not to replicate under constrained circumstances (despite hypothetically replicating under more favorable circumstances such as expert administration or larger budgets) will also plague attempts to build off those studies in constrained circumstances.
-Thus, we believe it is relevant to estimate replicability under the limitations of real world resource and expertise constraints.
-## intepretation - replication in light of the goal
 
 Replication results should be interpreted in light of their methods and estimand.
-
 Given our sample, we are able to estimate the correlates of studies replicating when the replications are conducted online, by graduate students with limited time and budget.
@@
 
-## limitations
+The same issue that may cause a study not to replicate under constrained circumstances (despite hypothetically replicating under more favorable circumstances such as expert administration or larger budgets) will also plague attempts to build off those studies in constrained circumstances.
+Thus, we believe it is relevant to consider how well studies replicate under the limitations of real world resource and expertise constraints.
 
@@
 Given the predictive value, slightly more skepticism and critical reading of between-subjects designs may be warranted, but this correlation, by itself, does not mean scientists should prefer to run within-subjects designs.
-
-## conclusion
 

### 2023-05-04 paper/manuscript.tex
another pass at intro and disc

@@
 
-Cumulative science requires foundational empirical results that are robust enough to support theory construction and future experimental extension.
-Scientists often treat publication in a scientific journal as a signal that a result was (likely to be) true, which leads scientists to build on findings without verifying them first.
-The replication crisis called into question the tacit assumption that most of the literature was robust and would replicate.
-Certain prominent findings failed to replicate in multi-site replication attempts (ex.
+Cumulative scientific progress requires empirical results that are robust enough to support theory construction and future extensions.
+Yet in psychology, some prominent individual findings have failed to replicate in multi-site replication attempts (ex.
 terror management theory, \protect\hyperlink{ref-klein2022}{Klein et al.
@@
 2016}), and a large-scale replication project pegged the replication rate for findings in top-tier psychology journals at around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}).
-When the trust in the literature mismatches the robustness results, many scientists can waste time and resources becoming frustrated pursuing extensions to a popular, but unreliable result.
-This seems to be the current situation of the literature, which leads to question: what do we do to minimize the waste?
+When scientists treat publication as a signal of truth and attempt to build on results without verifying them first, they can become frustrated pursuing extensions to a popular, but unreliable result.
+As each failed extension does not directly contradict the original result, many scientists may waste a lot of time and resources pursuing results where there may be none.
+This leads to a question: what do we do to minimize the waste?
+
+{[}This feels like we're setting up for the advice: don't try to extend anything without replicating it first, not sure how to shift to the policy issue.{]}
 
@@
 Thus, we might want to know 1) what quantity to measure if we want to capture frustration and waste due to non-cumulative findings and 2) from a descriptive perspective, what types of studies are most at risk for this issue.
-Such measurements have been the focus of much prior work, but there is limited consensus on what is being estimated.
+Such measurements have been the focus of much prior work around replicability, but there is limited consensus on what is being estimated.
 
-Three large-scale investigations have addressed replication rates in psychology.
-Reproducibility Project: Psychology, mentioned above, sampled roughly 100 studies from articles published in three top psychology journals in 2008 and they found an overall replication rate of around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}).
+Three large-scale investigations have measured replication rates in samples of psychology studies.
+Reproducibility Project: Psychology sampled roughly 100 studies from articles published in three top psychology journals in 2008 and distributed the studies across participanting labs.
+They found an overall replication rate of around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}).
 ManyLabs investigated heterogeneity using short target studies that compared between two conditions each.
@@
 Camerer et al.
-(\protect\hyperlink{ref-camerer2018}{2018}) replicated all 21 behavioral social science studies from Nature and Science from 2010-2015 that were feasible; they consulted original authors and had high power to detect effects smaller than those reported.
+(\protect\hyperlink{ref-camerer2018}{2018}) included all 21 behavioral social science studies from Nature and Science from 2010-2015 that were feasible; they consulted original authors and had high power to detect effects smaller than those reported.
 In this well-resourced environment with expert input, the replication rate was around 60\%.
-These studies all measured replication rates, but the details of their methods and outcome measures varied.
 
@@
 Rather than aim for some measure of ``true'' replicability, it makes more sense to contextualize replication efforts based on their methods and outcome measures.
-With this lens, we could say that RP:P is looking at how well findings in well-known journals can be replicated in typical circumstances.
+With this lens, we could say that RP:P looked at how well findings in well-known journals can be replicated in a typical psychology lab.
 Many Labs looked at which well-known two conditions studies replicate with huge samples, and Camerer et al.
-(\protect\hyperlink{ref-camerer2018}{2018}) was looking at what replicates when conducted in a highly-resourced environment with expert involvement.
-All of these are pontentially desirable estimands depending on what the specific circumstances and questions of interest are.
+(\protect\hyperlink{ref-camerer2018}{2018}) looked at which prestigious journal findings replicate when conducted in a highly-resourced environment with expert involvement.
+All of these are potentially desirable estimands depending on what the specific circumstances and questions of interest are.
 
-From the point of view of enabling cumulative science, an estimand of interest is how well work can be replicated by students, as students conduct most scientific work (\protect\hyperlink{ref-frank2022}{\textbf{frank2022?}}).
+Most scientific work is conducted by student, so it makes sense for students to conduct replications (\protect\hyperlink{ref-frank2022}{\textbf{frank2022?}}).
 In our current study, we use student success at replicating an effect as our estimand.
@@
 
-Given the limitations of experimental approaches, we have to rely on correlational approaches for now.
+Given the limitations of experimental approaches, correlational approaches are the more popular choice for studying potential predictors of replicability.
 Correlational approaches depend on data from replications, generally drawing heavily from the same small set of data points.
@@
 2016}) to the point that much of what we think we know about replicability may be overfit to the 100 studies included in in RP:P.
-We need more data to find potential targets of concern and intervention.
+More data is needed to identify markers of replicability and targets for potential future interventions.
 
 Our contribution is a new dataset of 176 replications of experimental studies from the social sciences, primarily psychology.
-These replications were conducted by students in graduate-level experimental methods class between 2011 and 2022 as individual course projects.
+These replications were conducted by students in a graduate-level experimental methods class between 2011 and 2022 as individual course projects.
 We investigated statistical and experimental-design predictors of replicability in this dataset and found that within-subjects designs and studies with large standardized effect sizes were positively correlated with replication success.
@@
 
-\hypertarget{question-summary-and-takehomes}{%
-\subsection{question, summary, and takehomes}\label{question-summary-and-takehomes}}
-
-NEED TO REDO!
-MAY NEED SMOOTHER TRANSITIONS THROUGHOUT
-Prior large scale replications of psychology findings have estimated the replication rate at somewhere around one half, which intuitively feels low.
+Researchers use the psychological literature as a source of empirical results that they can build upon and extend as part of cumulative science.
+When these findings don't replicate, the attempts to extend them are a waste of time and resources.
+In order to eventually reduce this waste, we need to be able to identify when results can support cumulative scientific progress and what study features are predictive of this.
 However, limited numbers of replications and limited research into specific predictors of replication failure mean that the reasons for non-replications are not well understood.
 
-Overall, we take a functional approach to assessing replicability, by framing both our methods and interpretation around the idea of whether work can be repeated or built on by an early-career scientist.
-
-Here we took advantage of 11 years of graduate student replication projects to look at correlational predictors of replication in a previously-unused dataset.
+Here, we take a functional approach to assessing replicability, framing both our methods and interpretation around the idea of whether work can be repeated by an early-career scientist.
+We took advantage of 11 years of graduate student replication projects to look at correlational predictors of replication in a previously-unused dataset.
 In line with previous results, we found a 49\% replication rate, with some studies showing effect sizes similar to the original and others much smaller.
@@
 
-The same issue that may cause a study not to replicate under constrained circumstances (despite hypothetically replicating under more favorable circumstances such as expert administration or larger budgets) will also plague attempts to build off those studies in constrained circumstances.
-Thus, we believe it is relevant to estimate replicability under the limitations of real world resource and expertise constraints.
-\#\# intepretation - replication in light of the goal
-
 Replication results should be interpreted in light of their methods and estimand.
-
 Given our sample, we are able to estimate the correlates of studies replicating when the replications are conducted online, by graduate students with limited time and budget.
@@
 
-\hypertarget{limitations}{%
-\subsection{limitations}\label{limitations}}
+The same issue that may cause a study not to replicate under constrained circumstances (despite hypothetically replicating under more favorable circumstances such as expert administration or larger budgets) will also plague attempts to build off those studies in constrained circumstances.
+Thus, we believe it is relevant to consider how well studies replicate under the limitations of real world resource and expertise constraints.
 
@@
 Given the predictive value, slightly more skepticism and critical reading of between-subjects designs may be warranted, but this correlation, by itself, does not mean scientists should prefer to run within-subjects designs.
-
-\hypertarget{conclusion}{%
-\subsection{conclusion}\label{conclusion}}
 

### 2023-05-12 paper/manuscript.Rmd
feedback from Maya and edits

@@
 What predicts which studies will replicate? 
-The identification of features that predict replication success is limited by data, however: most studies use a common dataset of only ~170 studies, which vary in how they define replication.
+The identification of features that predict replication success is limited by data, however: most analyses use a common dataset of only ~170 studies, which vary in how they define replication.
+
+[Ben points out that the 170 v 176 doesn't look good -- clarify that 170 isn't per study its *total* / that we are ~doubling available]
+
 We introduce a new dataset of 176 replications conducted by students as part of a graduate-level experimental methods course. 
@@
 Using this as a metric of replicability, 49% of the studies in our sample replicate, with studies with larger original effect sizes and within-participants designs being more likely to replicate.
+
+[TODO: add quant outcomes of predictive interval and median p orig ? ]
+
 Consistent with prior reports, our results indicate that the robustness of the psychology literature is low enough to limit progress by student investigators.
@@
 As each failed extension does not directly contradict the original result, many scientists may waste a lot of time and resources pursuing results where there may be none.
-This leads to a question: what do we do to minimize the waste?
 
-[This feels like we're setting up for the advice: don't try to extend anything without replicating it first, not sure how to shift to the policy issue.]
-
-From a policy perspective, we need to understand the landscape of the problem before we can have research-informed science policy interventions.
-Thus, we might want to know 1) what quantity to measure if we want to capture frustration and waste due to non-cumulative findings and 2) from a descriptive perspective, what types of studies are most at risk for this issue.
+[ possibly move later] To better understand this problem, we might want to know 1) what quantity to measure if we want to capture frustration and waste due to non-cumulative findings and 2) from a descriptive perspective, what types of studies are most at risk for this issue.
 Such measurements have been the focus of much prior work around replicability, but there is limited consensus on what is being estimated.
 
-Three large-scale investigations have measured replication rates in samples of psychology studies.
-Reproducibility Project: Psychology sampled roughly 100 studies from articles published in three top psychology journals in 2008 and distributed the studies across participanting labs.
+[ how to count MLs] Three large-scale investigations have measured replication rates in samples of psychology studies.
+Reproducibility Project: Psychology sampled roughly 100 studies from articles published in three top psychology journals in 2008 and distributed the studies across participating labs.
 They found an overall replication rate of around 40% [@openscienceconsortium2015].
@@
 
-Most scientific work is conducted by student, so it makes sense for students to conduct replications  [@frank2022].
+[This is good but could use more build-up.
+Something like.
+In practice, most scientific work is not conducted under such ideal conditions.
+Studies are generally run by graduate students with limited budgets ...
+.
+Therefore, an important question to ask is how replicable findings in the literature are for graduate students operating under less-than-ideal conditions.]
+
+Our goal in estimating replicability is to look for markers of when findings can support cumulative science.
+Most scientific work is conducted by students, working with limited budgets, limited time, and without access to outside experts.
+Therefore, to figure out what studies graduate students could build on, it makes sense to focus on replications conducted by students [@frank2022].
 In our current study, we use student success at replicating an effect as our estimand.
@@
 
+[maybe drop last sentence and work into a longer paragraph?]
+
+[Maya says firm this up and introduce quant outcomes as well]
+
 Our replication approach reflects this estimand.
 Our sample of studies is selected based on what studies students were interested in and wanting to replicate, with some filtering for feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable given methodological and budgetary constraints.
-All our replications were conducted under short time scales and relatively small budgets, paralleling the constraints many scientists are under when starting new projects.
-From the point of view of cumulative science, researchers want to know if they can get paradigms to work under their real-world constraints.
-We use a subjective replication score as our primary metric.
+<!--All our replications were conducted under short time scales and relatively small budgets, paralleling the constraints many scientists are under when starting new projects.
+From the point of view of cumulative science, researchers want to know if they can get paradigms to work under their real-world constraints.--> We use a subjective replication score as our primary metric.
 Whether one feels confident in the results of a study given a replication is not always dependent on only one outcome measure (ex.
@@
 This metric avoids bright line distinctions and accommodates the range of outcome measures in our diverse set of studies.
+As a complement to this, we include two statistical measures of replication success, applied to the key stat TODO
 
+[Examples ??]
 Despite variation in how large-scale replication studies have defined replication successes, there is work suggesting some consistency in the predictors of replication success.
@@
 
+[ Maya possibly suggests mentioning the uzzi paper that I am dubious of]
 Prediction markets and elicitations have established that people can predict what studies will replicate above chance [@hoogeveen2019;@dreber2015; @forsell2019;@camerer2018], but have not identified concrete predictors that differentiate replications from non-replications.
@@
 
-```{r}
+```{r, include=F}
 matching <- d |> filter(include!="unusable") |> mutate(match=ifelse(replicated_instructor_code==replicated_report_code,1,0)) |> group_by(match) |> tally()
 
+d |> filter(include!="unusable")
+irr <- cor.test(d$replicated_instructor_code, d$replicated_report_code, method="spearman")$estimate
 pred_int_avail <- d |> filter(include %in% c("stats", "pred_int")) |> tally()
@@
 Importantly, a holistic measure of replication success had already been coded for most projects when they were turned in at the end of the class.
-For reliability, VB independently code the replication success from the students' written reports; discrepancies were resolved by discussion between MCF and VB (`r round(pluck(matching,2,1)/176*100)`% of cases).
+For reliability, VB independently code the replication success from the students' written reports; discrepancies were resolved by discussion between MCF and VB (inter-rater reliability, Spearman's $\rho$: `r round(irr,2)`, disagreement in `r round(pluck(matching,2,1)/176*100)`% of cases).
 
 As a complement to our primary subjective outcome, we also used two statistical measures of replication on the subset of the data where they were computable for the key statistic of interest (`r pluck(pred_int_avail,1)` cases, see Figure \ref{fig:prisma}).
-We used p-original, the p-value on the null hypothesis that the original and replication statistics are from the same distribution, and prediction interval, a binary measure of whether the replication statistic fell within the prediction interval of the original statistic [@errington2021].
-These both measure how similar the outcome estimates from the two sets of data are.
+We used p-original, the p-value on the null hypothesis that the original and replication statistics are from the same distribution, and prediction interval, a binary measure of whether the replication statistic fell within the prediction interval of the original statistic [@mathur2020].
+The prediction interval depends on the level of evidence of the original study; if the effect was marginal, the prediction interval could overlap zero; thus, a replication might fall within the predictive interval, and be consistent with the original outcome, but not provide compelling evidence for the claimed effect.
+Conversely, large original effects with precise point estimates may have prediction intervals that do not overlap a smaller replication effect.
+Thus, this metric may not always match researcher intuitions on whether the effect is replicating.
+TODO NEEDS WORK
 
@@
 
+```{r forest, out.height="50%", fig.width=5, fig.height=8, fig.pos="ht", fig.cap="TRY FOREST PLOT"}
+d |> 
+  filter(target_d_calc < 5, rep_d_calc < 5) |>
+  ggplot(aes(y=reorder(target_lastauthor_year,target_d_calc, mean), color=as.factor(sub_rep)))+
+
+  geom_point(aes(x=target_d_calc), shape=21)+
+  geom_point(aes(x=rep_d_calc), shape=19)+
+  scale_color_viridis(discrete=T, direction = 1, 
+                      name = "Subjective\nReplication\nSuccess\n")+theme_classic()+
+  labs(x="Standardized Effect Size")+
+  theme(axis.text.y=element_blank(), axis.ticks.y=element_blank(), axis.title.y=element_blank())
+
+```
+
 ## Overall replication rate
@@
 
-Across the 176 studies, the overall subjective replication rate was `r round(pluck(sub_rep_rate,1))`%.
+Across the 176 studies, the average subjective replication score was `r round(pluck(sub_rep_rate,1))`%, which we interpret as an overall subjective replication rate.
 `r round(pluck(pred_int_rate,1))`% (`r predIntcount`/`r predInttotal`) of the studies had replication outcomes within the prediction interval of the original outcome.
-The median p_original value was `r round(pluck(porig_rate, 1),2)`.
+The median p_original value was `r round(pluck(porig_rate, 1),2)` representing the median probability that a replication study's estimate would be at least as extreme as was actually observed, if in fact the replication and original were statistically consistent.
 Figure \ref{fig:smd} shows the relationship between original standardized effect size, replication effect size, and subjective replication score.
@@
          p = sapply(preds, function(x) sub_cor(x, stat = "p"))) |> 
-  mutate(Predictors=factor(preds, levels=c("social", "other_psych", "non_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "pub_year", "log_trials", "log_sample", "log_ratio_ss"), labels=c("Social", "Other psych", "Non psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rep/orig sample"))) |> arrange(desc(r)) |> select(Predictors, r, p)
+  mutate(Predictors=factor(preds, levels=c("social", "other_psych", "non_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "pub_year", "log_trials", "log_sample", "log_ratio_ss"), labels=c("Social", "Other psych", "Non psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log n trials", "Log original sample size", "Log rep/orig sample"))) |> arrange(desc(r)) |> select(Predictors, r, p)
 
 library(kableExtra)
-knitr::kable(cors, digits = 3, align='rcc',format="latex", position="!h", caption="The correlation of individual predictors with subjective replication outcomes.
+knitr::kable(cors, digits = 3, align='rcc',format="latex", position="!h", caption="The correlation between each individual predictor and the subjective replication score.
 For subfield, cognitive psychology is treated as the baseline condition.
@@
     mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |>  filter(Term!="Intercept") |> 
-    mutate(Term=factor(Term, levels=c("subfieldsocial", "subfieldother_psych", "subfieldnon_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "z_pub_year", "z_log_trials", "z_log_sample", "z_log_ratio_ss","z_log_p","z_target_d_calc"), labels=c("Social", "Other psych", "Non psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rep/orig sample", "P-value", "Original effect size")))
+    mutate(Term=factor(Term, levels=c("subfieldsocial", "subfieldother_psych", "subfieldnon_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "z_pub_year", "z_log_trials", "z_log_sample", "z_log_ratio_ss","z_log_p","z_target_d_calc"), labels=c("Social", "Other psych", "Non psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log n trials", "Log original sample size", "Log rep/orig sample", "P-value", "Original effect size")))
 }
@@
 # Discussion
-
-Researchers use the psychological literature as a source of empirical results that they can build upon and extend as part of cumulative science.
-When these findings don't replicate, the attempts to extend them are a waste of time and resources.
-In order to eventually reduce this waste, we need to be able to identify when results can support cumulative scientific progress and what study features are predictive of this.
-However, limited numbers of replications and limited research into specific predictors of replication failure mean that the reasons for non-replications are not well understood.
+Non-replications pose a problem for scientists who want to build on the empirical results in the literature, but the limited numbers of replications and limited research into specific predictors of replication failure mean that the reasons for non-replications are not well understood.
 
@@
 Pedagogy has an important role to play in open science more broadly -- it's one thing to require or incentivize certain practices, but the tools and workflows of open science have to be learned.
-Teaching these skills and giving students an opportunity to practice using open, reproducible workflows shows students how to integrate open science practices into their workflows, before other habits can ossify.
+<!--Teaching these skills and giving students an opportunity to practice using open, reproducible workflows shows students how to integrate open science practices into their workflows, before other habits can ossify.
 In doing replications, students may be motivated to value transparent practices, as they either struggle to reimplement studies from vague methods or appreciate the ease of working with available materials and analysis code.
@@
 This sort of first hand experience teaches students that not everything they read in the literature may just work if done again.
+-->
 
@@
 This subjective replication outcome was chosen because it already existed, could be applied to all projects (regardless of type and detail of statistical reporting), and did not rely solely on one statistical measure.
-As a complement, we also identified a "key" statistical test for each paper (see below for details), and if possible, computed p_original and prediction interval at this statistic, following @errington2021.
+As a complement, we also identified a "key" statistical test for each paper (see below for details), and if possible, computed p_original and prediction interval at this statistic, following @mathur2020.
 p_original was a continuous measure of the p-value on the hypothesis that the original and replication samples come from the same distribution.
@@
 All numeric predictor variables were z-scored after other transforms (e.g., logs) to ensure comparable regularization effects from the horseshoe prior.
+The priors we used were horseshoe(3) for betas, normal(0,.5) for standard deviation of random slopes, and lkj(1) for correlations between random slopes.
 

### 2023-05-12 paper/manuscript.tex
feedback from Maya and edits

@@
 What predicts which studies will replicate?
-The identification of features that predict replication success is limited by data, however: most studies use a common dataset of only \textasciitilde170 studies, which vary in how they define replication.
+The identification of features that predict replication success is limited by data, however: most analyses use a common dataset of only \textasciitilde170 studies, which vary in how they define replication.
+
+{[}Ben points out that the 170 v 176 doesn't look good -- clarify that 170 isn't per study its \emph{total} / that we are \textasciitilde doubling available{]}
+
 We introduce a new dataset of 176 replications conducted by students as part of a graduate-level experimental methods course.
@@
 Using this as a metric of replicability, 49\% of the studies in our sample replicate, with studies with larger original effect sizes and within-participants designs being more likely to replicate.
+
+{[}TODO: add quant outcomes of predictive interval and median p orig ? {]}
+
 Consistent with prior reports, our results indicate that the robustness of the psychology literature is low enough to limit progress by student investigators.
@@
 As each failed extension does not directly contradict the original result, many scientists may waste a lot of time and resources pursuing results where there may be none.
-This leads to a question: what do we do to minimize the waste?
 
-{[}This feels like we're setting up for the advice: don't try to extend anything without replicating it first, not sure how to shift to the policy issue.{]}
-
-From a policy perspective, we need to understand the landscape of the problem before we can have research-informed science policy interventions.
-Thus, we might want to know 1) what quantity to measure if we want to capture frustration and waste due to non-cumulative findings and 2) from a descriptive perspective, what types of studies are most at risk for this issue.
+{[} possibly move later{]} To better understand this problem, we might want to know 1) what quantity to measure if we want to capture frustration and waste due to non-cumulative findings and 2) from a descriptive perspective, what types of studies are most at risk for this issue.
 Such measurements have been the focus of much prior work around replicability, but there is limited consensus on what is being estimated.
 
-Three large-scale investigations have measured replication rates in samples of psychology studies.
-Reproducibility Project: Psychology sampled roughly 100 studies from articles published in three top psychology journals in 2008 and distributed the studies across participanting labs.
+{[} how to count MLs{]} Three large-scale investigations have measured replication rates in samples of psychology studies.
+Reproducibility Project: Psychology sampled roughly 100 studies from articles published in three top psychology journals in 2008 and distributed the studies across participating labs.
 They found an overall replication rate of around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}).
@@
 
-Most scientific work is conducted by student, so it makes sense for students to conduct replications (\protect\hyperlink{ref-frank2022}{\textbf{frank2022?}}).
+{[}This is good but could use more build-up.
+Something like.
+In practice, most scientific work is not conducted under such ideal conditions.
+Studies are generally run by graduate students with limited budgets \ldots{} .
+Therefore, an important question to ask is how replicable findings in the literature are for graduate students operating under less-than-ideal conditions.{]}
+
+Our goal in estimating replicability is to look for markers of when findings can support cumulative science.
+Most scientific work is conducted by students, working with limited budgets, limited time, and without access to outside experts.
+Therefore, to figure out what studies graduate students could build on, it makes sense to focus on replications conducted by students (\protect\hyperlink{ref-frank2022}{\textbf{frank2022?}}).
 In our current study, we use student success at replicating an effect as our estimand.
@@
 
+{[}maybe drop last sentence and work into a longer paragraph?{]}
+
+{[}Maya says firm this up and introduce quant outcomes as well{]}
+
 Our replication approach reflects this estimand.
 Our sample of studies is selected based on what studies students were interested in and wanting to replicate, with some filtering for feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable given methodological and budgetary constraints.
-All our replications were conducted under short time scales and relatively small budgets, paralleling the constraints many scientists are under when starting new projects.
-From the point of view of cumulative science, researchers want to know if they can get paradigms to work under their real-world constraints.
 We use a subjective replication score as our primary metric.
@@
 This metric avoids bright line distinctions and accommodates the range of outcome measures in our diverse set of studies.
+As a complement to this, we include two statistical measures of replication success, applied to the key stat TODO
 
+{[}Examples ??{]}
 Despite variation in how large-scale replication studies have defined replication successes, there is work suggesting some consistency in the predictors of replication success.
@@
 
+{[} Maya possibly suggests mentioning the uzzi paper that I am dubious of{]}
 Prediction markets and elicitations have established that people can predict what studies will replicate above chance (\protect\hyperlink{ref-dreber2015}{Dreber et al.
@@
 Importantly, a holistic measure of replication success had already been coded for most projects when they were turned in at the end of the class.
-For reliability, VB independently code the replication success from the students' written reports; discrepancies were resolved by discussion between MCF and VB (26\% of cases).
+For reliability, VB independently code the replication success from the students' written reports; discrepancies were resolved by discussion between MCF and VB (inter-rater reliability, Spearman's \(\rho\): 0.88, disagreement in 26\% of cases).
 
 As a complement to our primary subjective outcome, we also used two statistical measures of replication on the subset of the data where they were computable for the key statistic of interest (136 cases, see Figure \ref{fig:prisma}).
-We used p-original, the p-value on the null hypothesis that the original and replication statistics are from the same distribution, and prediction interval, a binary measure of whether the replication statistic fell within the prediction interval of the original statistic (\protect\hyperlink{ref-errington2021}{Errington et al.
-2021}).
-These both measure how similar the outcome estimates from the two sets of data are.
+We used p-original, the p-value on the null hypothesis that the original and replication statistics are from the same distribution, and prediction interval, a binary measure of whether the replication statistic fell within the prediction interval of the original statistic (\protect\hyperlink{ref-mathur2020}{Mathur \& VanderWeele 2020}).
+The prediction interval depends on the level of evidence of the original study; if the effect was marginal, the prediction interval could overlap zero; thus, a replication might fall within the predictive interval, and be consistent with the original outcome, but not provide compelling evidence for the claimed effect.
+Conversely, large original effects with precise point estimates may have prediction intervals that do not overlap a smaller replication effect.
+Thus, this metric may not always match researcher intuitions on whether the effect is replicating.
+TODO NEEDS WORK
 
@@
 
+\begin{figure}[ht]
+\includegraphics[width=1\linewidth,height=0.5\textheight]{manuscript_files/figure-latex/forest-1} \caption{TRY FOREST PLOT}\label{fig:forest}
+\end{figure}
+
 \hypertarget{overall-replication-rate}{%
@@
 
-Across the 176 studies, the overall subjective replication rate was 49\%.
+Across the 176 studies, the average subjective replication score was 49\%, which we interpret as an overall subjective replication rate.
 45\% (61/136) of the studies had replication outcomes within the prediction interval of the original outcome.
-The median p\_original value was 0.03.
+The median p\_original value was 0.03 representing the median probability that a replication study's estimate would be at least as extreme as was actually observed, if in fact the replication and original were statistically consistent.
 Figure \ref{fig:smd} shows the relationship between original standardized effect size, replication effect size, and subjective replication score.
@@
 
-\caption{\label{tab:cor}The correlation of individual predictors with subjective replication outcomes.
+\caption{\label{tab:cor}The correlation between each individual predictor and the subjective replication score.
 For subfield, cognitive psychology is treated as the baseline condition.
@@
 \hline
-Log trials & 0.182 & 0.015\\
+Log n trials & 0.182 & 0.015\\
 \hline
@@
 
-Researchers use the psychological literature as a source of empirical results that they can build upon and extend as part of cumulative science.
-When these findings don't replicate, the attempts to extend them are a waste of time and resources.
-In order to eventually reduce this waste, we need to be able to identify when results can support cumulative scientific progress and what study features are predictive of this.
-However, limited numbers of replications and limited research into specific predictors of replication failure mean that the reasons for non-replications are not well understood.
+Non-replications pose a problem for scientists who want to build on the empirical results in the literature, but the limited numbers of replications and limited research into specific predictors of replication failure mean that the reasons for non-replications are not well understood.
 
@@
 Pedagogy has an important role to play in open science more broadly -- it's one thing to require or incentivize certain practices, but the tools and workflows of open science have to be learned.
-Teaching these skills and giving students an opportunity to practice using open, reproducible workflows shows students how to integrate open science practices into their workflows, before other habits can ossify.
-In doing replications, students may be motivated to value transparent practices, as they either struggle to reimplement studies from vague methods or appreciate the ease of working with available materials and analysis code.
-In presenting work with classmates, students see that there is variation in how well studies replicate, with some replicating very cleanly and others not at all.
-This sort of first hand experience teaches students that not everything they read in the literature may just work if done again.
 
@@
 This subjective replication outcome was chosen because it already existed, could be applied to all projects (regardless of type and detail of statistical reporting), and did not rely solely on one statistical measure.
-As a complement, we also identified a ``key'' statistical test for each paper (see below for details), and if possible, computed p\_original and prediction interval at this statistic, following Errington et al.
-(\protect\hyperlink{ref-errington2021}{2021}).
+As a complement, we also identified a ``key'' statistical test for each paper (see below for details), and if possible, computed p\_original and prediction interval at this statistic, following Mathur \& VanderWeele (\protect\hyperlink{ref-mathur2020}{2020}).
 p\_original was a continuous measure of the p-value on the hypothesis that the original and replication samples come from the same distribution.
@@
 doi:\href{https://doi.org/10.1177/2515245920958687}{10.1177/2515245920958687}
-
-\leavevmode\vadjust pre{\hypertarget{ref-errington2021}{}}%
-Errington TM, Mathur M, Soderberg CK, Denis A, Perfito N, Iorns E, Nosek BA (2021) Investigating the replicability of preclinical cancer biology (R Pasqualini and E Franco, Eds.).
-\emph{eLife} \textbf{10}:e71601.
-doi:\href{https://doi.org/10.7554/eLife.71601}{10.7554/eLife.71601}
 

### 2023-05-13 paper/manuscript.Rmd
fix graphs

@@
 
-```{r forest, out.height="50%", fig.width=5, fig.height=8, fig.pos="ht", fig.cap="TRY FOREST PLOT"}
-d |> 
-  filter(target_d_calc < 5, rep_d_calc < 5) |>
-  ggplot(aes(y=reorder(target_lastauthor_year,target_d_calc, mean), color=as.factor(sub_rep)))+
-
-  geom_point(aes(x=target_d_calc), shape=21)+
-  geom_point(aes(x=rep_d_calc), shape=19)+
-  scale_color_viridis(discrete=T, direction = 1, 
-                      name = "Subjective\nReplication\nSuccess\n")+theme_classic()+
-  labs(x="Standardized Effect Size")+
-  theme(axis.text.y=element_blank(), axis.ticks.y=element_blank(), axis.title.y=element_blank())
-
-```
-
 ## Overall replication rate
@@
                                               labels=c("Cognitive\npsychology", "Social\npsychology", "Other\npsychology", "Not\npsychology"))) |>
-  ggplot(aes(x=subfield, fill=sub_rep))+
-  geom_bar(stat="count", position="dodge")+
+  count(subfield, sub_rep, .drop=F) |> 
+  ggplot(aes(x=subfield, fill=sub_rep, y=n))+
+  geom_bar(stat="identity", position="dodge")+
   scale_fill_viridis(discrete=T)+
@@
   open_data==1 ~ "No open materials \n Open data",
-  T ~ "No open materials \n No open data")) |> 
-  ggplot( aes(x=openness |> factor(), fill=sub_rep))+
-  geom_bar(stat="count", position="dodge")+
+  T ~ "No open materials \n No open data") |> factor()) |> 
+    count(openness, sub_rep, .drop=F) |> 
+  ggplot( aes(x=openness, y=n, fill=sub_rep))+
+  geom_bar(stat="identity", position="dodge")+
   scale_fill_viridis(discrete=T)+
@@
 
-modal <- ggplot(dat, aes(x=ifelse(change_platform,"Switch to online\n","Same modality\n"), fill=sub_rep))+
-  geom_bar(stat="count", position="dodge")+
+modal <- dat |> mutate(platform=ifelse(change_platform,"Switch to online\n","Same modality\n")) |> count(platform, sub_rep, .drop=F) |>  ggplot(aes(x=platform, y=n, fill=sub_rep))+
+  geom_bar(stat="identity", position="dodge")+
   scale_fill_viridis(discrete=T)+
@@
 
-within <- ggplot(dat, aes(x=ifelse(is_within, "Within \nsubjects", "Between\nsubjects"), fill=sub_rep))+
-  geom_bar(stat="count", position="dodge")+
+within <- dat |> mutate(is_within=ifelse(is_within, "Within \nsubjects", "Between\nsubjects")) |> 
+  count(is_within, sub_rep, .drop=F) |> ggplot(aes(x=is_within, y=n, fill=sub_rep))+
+  geom_bar(stat="identity", position="dodge")+
   scale_fill_viridis(discrete=T)+
@@
 
-vignette <- ggplot(dat, aes(x=ifelse(single_vignette, "Single \nvignette", "Multiple \nvignettes"), fill=sub_rep))+
-  geom_bar(stat="count", position="dodge")+
+vignette <- dat |> mutate(single_vignette=ifelse(single_vignette, "Single \nvignette", "Multiple \nvignettes")) |> count(single_vignette, sub_rep, .drop=F) |> ggplot(aes(x=single_vignette,y=n, fill=sub_rep))+
+  geom_bar(stat="identity", position="dodge")+
   scale_fill_viridis(discrete=T)+

### 2023-05-13 paper/supplement.Rmd
fix graphs

@@
 model_location="code/models"
+d <- read_csv(here("data", "processed_data.csv")) |> filter(status!="unusable") |> filter(include!="no")
 
+```
+
+# Forest plot
+
+```{r forest, out.height="100%", fig.width=9, fig.height=12, fig.pos="ht", fig.cap="TRY FOREST PLOT"}
+
+d |> 
+  filter(target_d_calc < 5, rep_d_calc < 5) |>
+  mutate(numpredInt=ifelse(predInt,1,0)) |> 
+  ggplot(aes(y=reorder(target_lastauthor_year,target_d_calc, mean), color=as.factor(sub_rep)))+
+    geom_vline(xintercept=0, linetype=3)+
+  geom_point(aes(x=target_d_calc, shape="original"))+
+  geom_point(aes(x=rep_d_calc, shape="replication"))+
+  scale_shape_manual(values=c("original"=21,"replication"=19), name=NULL)+
+  coord_cartesian(xlim=c(-2,4))+
+  geom_text(aes(x=-2, label=round(p_orig,3)), size=3, hjust=0, show.legend = F)+
+  scale_color_viridis(discrete=T, direction = 1, 
+                      name = "Subjective\nReplication\nSuccess\n")+theme_classic()+
+  labs(x="Standardized Effect Size")+
+  theme(axis.ticks.y=element_blank(), axis.title.y=element_blank())
 ```

### 2023-05-15 paper/manuscript.Rmd
another pass at abstract & intro

@@
 Yet in psychology, some prominent individual findings have failed to replicate, and large-scale investigations suggest that failures to replicate are widespread.
+
 What predicts which studies will replicate? 
-The identification of features that predict replication success is limited by data, however: most analyses use a common dataset of only ~170 studies, which vary in how they define replication.
+The identification of features that predict replication success is limited by data, however: most analyses draw on the same set of ~170 replications from a few replication projects that have been extensively re-analysed.
 
-[Ben points out that the 170 v 176 doesn't look good -- clarify that 170 isn't per study its *total* / that we are ~doubling available]
+We introduce a new dataset of 176 replications where we examine how often students in a graduate-level methods course were able replicate their chosen studies' results closely enough to be ready to build on it in future work.
+The replication rate under this metric was 49%, and 45% of replications with suitable numerical outcomes (N=136) were within the prediction interval of the original outcome.
+Larger original effect sizes and within-participants designs were predictive of replication.
+Consistent with prior reports, our results indicate that the robustness of the psychology literature is low enough to limit progress by student investigators.
 
-We introduce a new dataset of 176 replications conducted by students as part of a graduate-level experimental methods course. 
-We examine how often students were able replicate their chosen studies' results closely enough that they would be ready to build on it in future work. 
-Using this as a metric of replicability, 49% of the studies in our sample replicate, with studies with larger original effect sizes and within-participants designs being more likely to replicate.
-
-[TODO: add quant outcomes of predictive interval and median p orig ? ]
-
-Consistent with prior reports, our results indicate that the robustness of the psychology literature is low enough to limit progress by student investigators.
+[Still needs work -- also needs shortening -- this is 180, NHB says max 150]
 :::
@@
 
-[ possibly move later] To better understand this problem, we might want to know 1) what quantity to measure if we want to capture frustration and waste due to non-cumulative findings and 2) from a descriptive perspective, what types of studies are most at risk for this issue.
+To identify studies are risk for non-cumulative findings, we might want to know 1) what to measure in order to capture the waste and frustration due to non-cumulative failed extensions and 2) from a descriptive perspective, what features of studies are associated with being at risk for this non-replicability.
 Such measurements have been the focus of much prior work around replicability, but there is limited consensus on what is being estimated.
 
-[ how to count MLs] Three large-scale investigations have measured replication rates in samples of psychology studies.
+ [Prior paragraph may still need work]
+
+A few large-scale investigations have measured replication rates in samples of psychology studies.
 Reproducibility Project: Psychology sampled roughly 100 studies from articles published in three top psychology journals in 2008 and distributed the studies across participating labs.
 They found an overall replication rate of around 40% [@openscienceconsortium2015].
-ManyLabs investigated heterogeneity using short target studies that compared between two conditions each.
+Many Labs investigated heterogeneity using short target studies that compared between two conditions each.
 These study designs were not representative of the psychology literature as a whole, and due to the heterogeneity goal, they had large overall samples across multiple sites.
@@
 
+[Prior paragraph is a bit verbose, but it's probably fine]
+
 Rather than aim for some measure of "true" replicability, it makes more sense to contextualize replication efforts based on their methods and outcome measures.
@@
 
-[This is good but could use more build-up.
+[TODO This is good but could use more build-up.
 Something like.
@@
 
-Our goal in estimating replicability is to look for markers of when findings can support cumulative science.
-Most scientific work is conducted by students, working with limited budgets, limited time, and without access to outside experts.
-Therefore, to figure out what studies graduate students could build on, it makes sense to focus on replications conducted by students [@frank2022].
-In our current study, we use student success at replicating an effect as our estimand.
-In particular, our estimand is the probability that a researcher, on selecting a finding of interest from the literature, can successfully achieve a result satisfactorily close enough to the original that they can build on it in their own work, with all the necessary compromises to the methods and sample of the original that may be required by the constraints of the situation.
-
-[maybe drop last sentence and work into a longer paragraph?]
-
-[Maya says firm this up and introduce quant outcomes as well]
+Our goal in estimating replicability is to look for markers of when findings can (and cannot) support cumulative science.
+If a study cannot be replicated in a given set of circumstances, we believe it it unlikely that the study can be successfully built upon in those circumstances either.
+Thus, we look at what studies are replicable under the circumstances where most scientific work is conducted: by students who are working with limited budgets, limited time, and without access to outside experts [@frank2022].
+Our primary estimand is whether a student researcher, on selecting a finding of interest from the literature, can successfully achieve a result close enough to the original that they could build on it in their own work.
 
@@
 Our sample of studies is selected based on what studies students were interested in and wanting to replicate, with some filtering for feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable given methodological and budgetary constraints.
-<!--All our replications were conducted under short time scales and relatively small budgets, paralleling the constraints many scientists are under when starting new projects.
-From the point of view of cumulative science, researchers want to know if they can get paradigms to work under their real-world constraints.--> We use a subjective replication score as our primary metric.
-Whether one feels confident in the results of a study given a replication is not always dependent on only one outcome measure (ex.
-interaction term) and particularly not dependent on only one statistical comparison between the two studies (ex.
-replication is p<.05 same direction as original).
-This metric avoids bright line distinctions and accommodates the range of outcome measures in our diverse set of studies.
-As a complement to this, we include two statistical measures of replication success, applied to the key stat TODO
+In addition to this subjective measure of replicability, we also compare the effect sizes of the original and replication on one key outcome per study using prediction interval and p-original [@mathur2020].
 
-[Examples ??]
-Despite variation in how large-scale replication studies have defined replication successes, there is work suggesting some consistency in the predictors of replication success.
-Knowing these predictors is important for appropriately calibrating how we read the literature and for eventually identifying targets for interventions.
+[TODO possibly say more??]
 
-[ Maya possibly suggests mentioning the uzzi paper that I am dubious of]
+Despite variation in the methods and outcomes used by large-scale replication studies, they are often aggregated together in analyses looking at the predictablity of replication success.
 Prediction markets and elicitations have established that people can predict what studies will replicate above chance [@hoogeveen2019;@dreber2015; @forsell2019;@camerer2018], but have not identified concrete predictors that differentiate replications from non-replications.
-Using machine learning approaches, @altmejd2019 examined statistical and demographic features of studies and identified larger sample sizes, larger effect sizes, and simple effects (as opposed to interaction terms) as predictive of replication.
-@openscienceconsortium2015 looked at correlates of replicability in the RP:P sample and found that studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate.
-One potential set of correlates to replicabilty that has not been thoroughly examined are experimental design features, such as between or within subjects designs and repeated measures.
+Machine learning approaches trained on the available replications are also above chance at predicting replication success [@yang2020; @youyou2023].
+In terms of specific attributes that predict replicability, @altmejd2019 examined statistical and demographic features of studies and identified larger sample sizes, larger effect sizes, and simple effects (as opposed to interaction terms) as predictive of replication, and @openscienceconsortium2015 looked at correlates of replicability in the RP:P sample and found that studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate.
+One potential set of correlates to replicability that has not been thoroughly examined are experimental design features, such as between or within subjects designs and repeated measures.
 
-Experimental approaches can be used to test potential interventions.
+[TODO is there a citation for experimental design features being possibly relevant?]
+
+While most approaches to correlates of replicability have been correlational, experimental approaches can be used to test potential interventions.
 @protzko2020 showed, across 16 studies, that better methodological practices led to replication rates that matched theoretical expectations with replication effect sizes comparable with the original.
@@
 
-Given the limitations of experimental approaches, correlational approaches are the more popular choice for studying potential predictors of replicability.
-Correlational approaches depend on data from replications, generally drawing heavily from the same small set of data points.
+[Awkward transition]
+
+However, while they don't incur the expense of collecting new datasets, correlational approaches depend on data from replications.
+As large-scale replications are arduous and expensive to run, analyses generally draw heavily on same small set of data points.
 In particular, the RP:P dataset itself is much discussed and reanalyzed [@etz2016;@gilbert2016;@patil2016;@anderson2016] to the point that much of what we think we know about replicability may be overfit to the 100 studies included in in RP:P.
-More data is needed to identify markers of replicability and targets for potential future interventions.
+More replication data is needed to identify markers of replicability and targets for potential future experimental approaches.
 
@@
 These replications were conducted by students in a graduate-level experimental methods class between 2011 and 2022 as individual course projects.
-We investigated statistical and experimental-design predictors of replicability in this dataset and found that within-subjects designs and studies with large standardized effect sizes were positively correlated with replication success.
+We investigate statistical and experimental-design predictors of replicability in this dataset and find that within-subjects designs and studies with large standardized effect sizes are positively correlated with replication success.
 
@@
 		\node[mynode, join, on chain=1, fill=good] (n6)
-		{\textbf{136} pairs with some effect size};
+		{\textbf{136} pairs with \\ calculable prediction interval};
 		\node[mynode, join, on chain=1, fill=good] (n7)
-		{\textbf{112} pairs with standardized effect size};
+		{\textbf{112} pairs with \\ standardized effect size};
 
@@
 
+<!--, both measures of whether the two effects are likely to have come from the same distribution with all the necessary compromises to the methods and sample of the original that may be required by the constraints of the situation.
+
+[maybe drop last sentence and work into a longer paragraph?]
+
+[TODO Maya says firm this up and introduce quant outcomes as well]
+
+As a complement, we also measure how similar/consistent the original and replication effects were for the key effect of each study. TODO blah blah
+
+ <!--All our replications were conducted under short time scales and relatively small budgets, paralleling the constraints many scientists are under when starting new projects.
+From the point of view of cumulative science, researchers want to know if they can get paradigms to work under their real-world constraints.
+
+We use a subjective replication score as our primary metric.
+Whether one feels confident in the results of a study given a replication is not always dependent on only one outcome measure (ex.
+interaction term) and particularly not dependent on only one statistical comparison between the two studies (ex.
+replication is p<.05 same direction as original).
+This metric avoids bright line distinctions and accommodates the range of outcome measures in our diverse set of studies.
+As a complement to this, we include two statistical measures of replication success, applied to the key stat TODO -->
 Many different measures can be used to define replication success of an individual statistical result [@simonsohn2015; @gelman2018; @mathur2020].
@@
 
+TODO borrow from above
+
 As a complement to our primary subjective outcome, we also used two statistical measures of replication on the subset of the data where they were computable for the key statistic of interest (`r pluck(pred_int_avail,1)` cases, see Figure \ref{fig:prisma}).
@@
 The prediction interval depends on the level of evidence of the original study; if the effect was marginal, the prediction interval could overlap zero; thus, a replication might fall within the predictive interval, and be consistent with the original outcome, but not provide compelling evidence for the claimed effect.
-Conversely, large original effects with precise point estimates may have prediction intervals that do not overlap a smaller replication effect.
+Conversely, large original effects with precise point estimates may have prediction intervals that do not overlap a smaller replication effect would be interpreted as non-replications.
 Thus, this metric may not always match researcher intuitions on whether the effect is replicating.
@@
 
+TODO describe what we did to get these numbers!
 Distributions of study outcomes across some of these properties are shown in Figure \ref{fig:predictors-graph}.
@@
 While a number of predictors show individual correlations with the subjective replication score, many of the predictors intercorrelate with one another.
-In order to determine which predictors were the strongest, we ran a series of pre-registered regularized regression models (see Methods for details; see Supplement for all estimates from all models).
-We ran models both using all the data, but without statistical predictors (that were uncodable for some studies) and models including statistical predictors, but limiting to the subset of data where all predictors were available.
+In order to determine which predictors were the strongest, we ran a series of pre-registered regression models regularized using a horseshoe prior (see Methods for details; see Supplement for all estimates from all models).
+We ran models both using all the original-replication pairs, but without the predictors original effect size and original p value (that were uncodable for some studies), and models including all predictors, but limiting to the subset of data where all predictors were available.
 The coefficient estimates from two models predicting the subjective replication scores are shown in Figure \ref{fig:mod-results}.
@@
 
-Within-subjects designs stand out as the strongest indicator of replicability in the model without statistical predictors (`r within_1`).
-When statistical predictors are added to the model, within-subjects designs remain predictive (`r within_3`).
+Within-subjects designs stand out as the strongest indicator of replicability in the model with all the original-replication pairs (`r within_1`).
+In the model with all predictors, but less data, within-subjects designs remain predictive (`r within_3`).
 Standardized effect size is another strong predictor of subjective replication score (`r smd_3`).
@@
 
-```{r mod-results, out.width="90%", fig.width=8, fig.height=5, fig.pos="ht", fig.cap="Coefficients and uncertaintly estimates from a model of all predictors (N=112, shown in blue) and non-statistical predictors (N=176, shown in red) predicting subjective replication scores as the dependent variable.
+```{r mod-results, out.width="90%", fig.width=8, fig.height=5, fig.pos="ht", fig.cap="Coefficients and uncertaintly estimates from a model of all original-replication pairs (N=176, shown in red) and a model of all pairs with full statistical information (N=112, shown in blue) and predicting subjective replication scores as the dependent variable.
 "}
@@
 
+TODO citation around horseshoe prior
+
 Due to the monotonic missingness of the data, we had more predictor variables and outcome variables for some original-replication pairs than for others.

### 2023-05-15 paper/manuscript.tex
fix graphs
another pass at abstract & intro

@@
 Yet in psychology, some prominent individual findings have failed to replicate, and large-scale investigations suggest that failures to replicate are widespread.
+
 What predicts which studies will replicate?
-The identification of features that predict replication success is limited by data, however: most analyses use a common dataset of only \textasciitilde170 studies, which vary in how they define replication.
+The identification of features that predict replication success is limited by data, however: most analyses draw on the same set of \textasciitilde170 replications from a few replication projects that have been extensively re-analysed.
 
-{[}Ben points out that the 170 v 176 doesn't look good -- clarify that 170 isn't per study its \emph{total} / that we are \textasciitilde doubling available{]}
+We introduce a new dataset of 176 replications where we examine how often students in a graduate-level methods course were able replicate their chosen studies' results closely enough to be ready to build on it in future work.
+The replication rate under this metric was 49\%, and 45\% of replications with suitable numerical outcomes (N=136) were within the prediction interval of the original outcome.
+Larger original effect sizes and within-participants designs were predictive of replication.
+Consistent with prior reports, our results indicate that the robustness of the psychology literature is low enough to limit progress by student investigators.
 
-We introduce a new dataset of 176 replications conducted by students as part of a graduate-level experimental methods course.
-We examine how often students were able replicate their chosen studies' results closely enough that they would be ready to build on it in future work.
-Using this as a metric of replicability, 49\% of the studies in our sample replicate, with studies with larger original effect sizes and within-participants designs being more likely to replicate.
-
-{[}TODO: add quant outcomes of predictive interval and median p orig ? {]}
-
-Consistent with prior reports, our results indicate that the robustness of the psychology literature is low enough to limit progress by student investigators.
+{[}Still needs work -- also needs shortening -- this is 180, NHB says max 150{]}
 
@@
 
-{[} possibly move later{]} To better understand this problem, we might want to know 1) what quantity to measure if we want to capture frustration and waste due to non-cumulative findings and 2) from a descriptive perspective, what types of studies are most at risk for this issue.
+To better understand this problem, we might want to know 1) what quantity to measure if we want to capture frustration and waste due to non-cumulative findings and 2) from a descriptive perspective, what types of studies are most at risk for this issue.
 Such measurements have been the focus of much prior work around replicability, but there is limited consensus on what is being estimated.
 
-{[} how to count MLs{]} Three large-scale investigations have measured replication rates in samples of psychology studies.
+{[}Prior sentence needs work{]}
+
+A few large-scale investigations have measured replication rates in samples of psychology studies.
 Reproducibility Project: Psychology sampled roughly 100 studies from articles published in three top psychology journals in 2008 and distributed the studies across participating labs.
@@
 
-{[}This is good but could use more build-up.
+{[}TODO This is good but could use more build-up.
 Something like.
@@
 
-{[}Maya says firm this up and introduce quant outcomes as well{]}
+{[}TODO Maya says firm this up and introduce quant outcomes as well{]}
+
+As a complement, we also measure how similar/consistent the original and replication effects were for the key effect of each study. TODO blah blah
 
@@
 
-{[}Examples ??{]}
+{[}Examples ??{]} TODO redo paragraph
 Despite variation in how large-scale replication studies have defined replication successes, there is work suggesting some consistency in the predictors of replication success.
@@
 
-{[} Maya possibly suggests mentioning the uzzi paper that I am dubious of{]}
+{[}TODO Maya possibly suggests mentioning the uzzi paper that I am dubious of{]}
 Prediction markets and elicitations have established that people can predict what studies will replicate above chance (\protect\hyperlink{ref-dreber2015}{Dreber et al.
@@
 2019}), but have not identified concrete predictors that differentiate replications from non-replications.
-Using machine learning approaches, Altmejd et al.
-(\protect\hyperlink{ref-altmejd2019}{2019}) examined statistical and demographic features of studies and identified larger sample sizes, larger effect sizes, and simple effects (as opposed to interaction terms) as predictive of replication.
-Open Science Consortium (\protect\hyperlink{ref-openscienceconsortium2015}{2015}) looked at correlates of replicability in the RP:P sample and found that studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate.
-One potential set of correlates to replicabilty that has not been thoroughly examined are experimental design features, such as between or within subjects designs and repeated measures.
+Machine learning approaches also are above chance at predicting replication, but this did not identify interpretable predictors TODO CITATIONS In terms of specific attributes that predict replicability, Altmejd et al.
+(\protect\hyperlink{ref-altmejd2019}{2019}) examined statistical and demographic features of studies and identified larger sample sizes, larger effect sizes, and simple effects (as opposed to interaction terms) as predictive of replication, and Open Science Consortium (\protect\hyperlink{ref-openscienceconsortium2015}{2015}) looked at correlates of replicability in the RP:P sample and found that studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate.
+One potential set of correlates to replicability that has not been thoroughly examined are experimental design features, such as between or within subjects designs and repeated measures.
 
@@
         \node[mynode, join, on chain=1, fill=good] (n6)
-        {\textbf{136} pairs with some effect size};
+        {\textbf{136} pairs with \\ calculable prediction interval};
         \node[mynode, join, on chain=1, fill=good] (n7)
-        {\textbf{112} pairs with standardized effect size};
+        {\textbf{112} pairs with \\ standardized effect size};
 
@@
 \includegraphics[width=1\linewidth,height=0.25\textheight]{manuscript_files/figure-latex/smd-1} \caption{Relationship between effect size of the original study, effect size of the replication study, and subjective replication success rating, for those studies where effect size was applicable.}\label{fig:smd}
-\end{figure}
-
-\begin{figure}[ht]
-\includegraphics[width=1\linewidth,height=0.5\textheight]{manuscript_files/figure-latex/forest-1} \caption{TRY FOREST PLOT}\label{fig:forest}
 \end{figure}
@@
 
-Within-subjects designs stand out as the strongest indicator of replicability in the model without statistical predictors (0.55, CrI= {[}-0.01, 2{]}).
-When statistical predictors are added to the model, within-subjects designs remain predictive (0.64, CrI= {[}-0.03, 2.38{]}).
+Within-subjects designs stand out as the strongest indicator of replicability in the model with all the original-replication pairs (0.55, CrI= {[}-0.01, 2{]}).
+In the model with all predictors, but less data, within-subjects designs remain predictive (0.64, CrI= {[}-0.03, 2.38{]}).
 Standardized effect size is another strong predictor of subjective replication score (0.59, CrI= {[}0.31, 2.58{]}).
@@
 \begin{figure}[ht]
-\includegraphics[width=0.9\linewidth]{manuscript_files/figure-latex/mod-results-1} \caption{Coefficients and uncertaintly estimates from a model of all predictors (N=112, shown in blue) and non-statistical predictors (N=176, shown in red) predicting subjective replication scores as the dependent variable.
+\includegraphics[width=0.9\linewidth]{manuscript_files/figure-latex/mod-results-1} \caption{Coefficients and uncertaintly estimates from a model of all original-replication pairs (N=176, shown in red) and a model of all pairs with full statistical information (N=112, shown in blue) and predicting subjective replication scores as the dependent variable.
 }\label{fig:mod-results}
@@
 \subsection{Modelling}\label{modelling}}
+
+TODO citation around horseshoe prior
 

### 2023-05-15 paper/manuscript.Rmd
attempts were made

@@
 
+TODO figure out how to fix the fact that some of the p-orig and predInt had things on different scales b/c I screwed up ! Whether to switch all the SMD or only the ones we can't get on original!!!
+
+ALSO figure out how to talk about tau**2 and do that
+
+TODO propogate naming schemes to supplement wrt models
+
 # Introduction
@@
 If a study cannot be replicated in a given set of circumstances, we believe it it unlikely that the study can be successfully built upon in those circumstances either.
-Thus, we look at what studies are replicable under the circumstances where most scientific work is conducted: by students who are working with limited budgets, limited time, and without access to outside experts [@frank2022].
+Thus, we look at what studies are replicable under the circumstances where most scientific work is conducted: by students who are working with limited budgets, limited time, and without access to outside experts [@frank2012].
 Our primary estimand is whether a student researcher, on selecting a finding of interest from the literature, can successfully achieve a result close enough to the original that they could build on it in their own work.
@@
 \caption{Of the 210 projects conducted for the class, 176 are included in our analysis, after excluding reproducibilty projects (with no new data collection), non-experimental replications, and missing projects.
-Of the 176, 136 report sufficient information to numerically compare outcome measures, and 112 report enough to use statistical predictors.
-TODO BETTER WAY TO LABEL AND TALK ABOUT THEIR 2 AND 3}\label{fig:prisma}
+Of the 176, 136 report sufficient information to calculate prediction intervals, and 112 reported enough to calculated standardized effect sizes.
+}\label{fig:prisma}
 \end{figure}
@@
 
-<!--, both measures of whether the two effects are likely to have come from the same distribution with all the necessary compromises to the methods and sample of the original that may be required by the constraints of the situation.
+Of note, these replications were all conducted on short time scales, with constrained budgets, that in some cases limited the number of participants who could be recruited below what the original study had or what power analyses suggested.
+In nearly all cases, replications were conducted online, with recruitment from Amazon Mechanical Turk (default 2011-2020) or Prolific (default 2021-2022).
 
-[maybe drop last sentence and work into a longer paragraph?]
-
-[TODO Maya says firm this up and introduce quant outcomes as well]
-
-As a complement, we also measure how similar/consistent the original and replication effects were for the key effect of each study. TODO blah blah
-
- <!--All our replications were conducted under short time scales and relatively small budgets, paralleling the constraints many scientists are under when starting new projects.
-From the point of view of cumulative science, researchers want to know if they can get paradigms to work under their real-world constraints.
-
-We use a subjective replication score as our primary metric.
-Whether one feels confident in the results of a study given a replication is not always dependent on only one outcome measure (ex.
+Many different measures can be used to define replication success of an individual statistical result [@simonsohn2015; @gelman2018; @mathur2020].
+However, whether one feels confident in the results of a study given a replication is not always dependent on only one outcome measure (ex.
 interaction term) and particularly not dependent on only one statistical comparison between the two studies (ex.
 replication is p<.05 same direction as original).
-This metric avoids bright line distinctions and accommodates the range of outcome measures in our diverse set of studies.
-As a complement to this, we include two statistical measures of replication success, applied to the key stat TODO -->
-Many different measures can be used to define replication success of an individual statistical result [@simonsohn2015; @gelman2018; @mathur2020].
-However, a single test of a single statistical result doesn't capture the sense of whether a replication is close enough that one could feel confident extending the finding, so we used a subjective rating of replication success as our primary outcome measure.
-This subjective measure, unlike statistical measures, accommodated studies with multiple important outcome measures that together defined the pattern of interest and was applicable across the diverse range of statistical measures and reporting practices present in the sample.
+As our primary outcome, we use a subjective replication score which, unlike statistical measures, accommodated studies with multiple important outcome measures that together defined the pattern of interest and was applicable across the diverse range of statistical measures and reporting practices present in the sample.
 Importantly, a holistic measure of replication success had already been coded for most projects when they were turned in at the end of the class.
 For reliability, VB independently code the replication success from the students' written reports; discrepancies were resolved by discussion between MCF and VB (inter-rater reliability, Spearman's $\rho$: `r round(irr,2)`, disagreement in `r round(pluck(matching,2,1)/176*100)`% of cases).
-
-TODO borrow from above
 
@@
 The prediction interval depends on the level of evidence of the original study; if the effect was marginal, the prediction interval could overlap zero; thus, a replication might fall within the predictive interval, and be consistent with the original outcome, but not provide compelling evidence for the claimed effect.
-Conversely, large original effects with precise point estimates may have prediction intervals that do not overlap a smaller replication effect would be interpreted as non-replications.
-Thus, this metric may not always match researcher intuitions on whether the effect is replicating.
-TODO NEEDS WORK
+Conversely, large original effects with precise point estimates may have prediction intervals that do not overlap a smaller replication effect size, and thus would be inconsistent with the original outcome, even though researcher intuition might classify it as a success.
+Thus, the statistical metrics quantify the similarity of a key statistic, but they will not always match researcher intuitions on whether a study replicated.
 
@@
 
-Across the 176 studies, the average subjective replication score was `r round(pluck(sub_rep_rate,1))`%, which we interpret as an overall subjective replication rate.
+Across the 176 studies, the average subjective replication score was `r round(pluck(sub_rep_rate,1))`%, which we can interpret as an overall subjective replication rate.
 `r round(pluck(pred_int_rate,1))`% (`r predIntcount`/`r predInttotal`) of the studies had replication outcomes within the prediction interval of the original outcome.
@@
 On average, there was a diminution of effect sizes from original to replication.
+This pattern of results is consistent with the pattern of results found in RP:P [@openscienceconsortium2015].
 
@@
 
-Many predictors individually correlate with subjective replication success (Table \ref{tab:cor}).
-Predictors of higher replicability included within-subjects designs, larger numbers of trials, and the original study having open data.
+TODO any citations around experimental design predictors??
+
+Many predictors individually correlated with subjective replication success (Table \ref{tab:cor}).
+Predictors of higher replicability included within-subjects designs, larger numbers of trials per subject, and the original study having open data.
 Predictors of lower replicability included single vignetted studies with only one induction or example per condition, social psychology studies, and original-replication pairs where the original study was in-person and replication switched to online.
 
-TODO describe what we did to get these numbers!
 Distributions of study outcomes across some of these properties are shown in Figure \ref{fig:predictors-graph}.
-Both social and cognitive psychology studies were well represented in the replication sample, and the cognitive psychology studies replicated at `r round(1/subfield, 2)` times the rate of social psychology studies.
+To quantify the effects of these single predictors, we ran logistic models predicting the subjective replication score (on 0-1) as a function of the single predictor, and exponentiated the coefficient to get an odds ratio.
+Both social and cognitive psychology studies were well represented in the replication sample, and the cognitive psychology studies replicated `r round(1/subfield, 2)` times as often as social psychology studies.
 Within and between subjects designs were both common, and within-subjects designs replicated `r within |> round(2)` times as much.
-Studies with multiple vignettes replicated `r round(1/vignette, 2)` times more than single vignetted studies.
+Studies with multiple vignettes replicated `r round(1/vignette, 2)` times as often as single vignetted studies.
 However, there were strong correlations among these experimental features and between these experimental features and subfield.
@@
 While a number of predictors show individual correlations with the subjective replication score, many of the predictors intercorrelate with one another.
-In order to determine which predictors were the strongest, we ran a series of pre-registered regression models regularized using a horseshoe prior (see Methods for details; see Supplement for all estimates from all models).
-We ran models both using all the original-replication pairs, but without the predictors original effect size and original p value (that were uncodable for some studies), and models including all predictors, but limiting to the subset of data where all predictors were available.
-The coefficient estimates from two models predicting the subjective replication scores are shown in Figure \ref{fig:mod-results}.
+In order to determine which predictors were the strongest, we ran a series of pre-registered regression models regularized using a horseshoe shrinkage prior [@carvalho09].
+We ran both 1) models using all the original-replication pairs, but without original effect size and original p value as predictors, as they were uncodable for some pairs, and 2) models including all predictors, but on only the subset of data where all predictors were available.
+The coefficient estimates from two models predicting the subjective replication scores are shown in Figure \ref{fig:mod-results}; see Supplement for full model results.
 Due to a large number of predictors coupled with a small and noisy dataset there is much uncertainty around the coefficients even with strong regularization.
@@
 
-Within-subjects designs stand out as the strongest indicator of replicability in the model with all the original-replication pairs (`r within_1`).
-In the model with all predictors, but less data, within-subjects designs remain predictive (`r within_3`).
-Standardized effect size is another strong predictor of subjective replication score (`r smd_3`).
+Within-subjects designs stand out as the strongest indicator of replicability in the model with all the data (`r within_1`).
+In the model with all predictors, but less data, within-subjects designs remain predictive (`r within_3`), and standardized effect size is also a strong predictor of subjective replication score (`r smd_3`).
 Both effects are robust to a sensitivity analysis including only studies with close replications and matching statistical tests (within-subjects `r within_sens`; effect size `r smd_sens`).
 
-We also ran models predicting our secondary outcome measures: whether the replication effect was within the prediction interval as the original effect and what the p-original was between the replication and original.
+We also ran models predicting our secondary outcome measures: whether the replication effect was within the prediction interval of the original effect and what the p-original was between the replication and original.
 Both these models had even more uncertain estimates.
 While the credible intervals were wide, the general patterns of predictor direction and relative strength were similar to the subjective replication models.
-The strongest predictors were still within-subjects designs (`r within_2`) and studies with larger effect sizes (`r smd_2`).
+The strongest predictors for prediction interval were still within-subjects designs (`r within_2`) and studies with larger effect sizes (`r smd_2`).
 
@@
 
-tier1_subjective <- read_rds(here(model_location, "tier1_subjective.rds")) |> do_draws() |> mutate(type="Non-statistical predictors only") |> mutate(sens="All data")
-tier3_subjective <- read_rds(here(model_location, "tier3_subjective.rds"))|> do_draws() |> mutate(type="All predictors") |> mutate(sens="All data")
+tier1_subjective <- read_rds(here(model_location, "tier1_subjective.rds")) |> do_draws() |> mutate(type="All pairs") |> mutate(sens="All data")
+tier3_subjective <- read_rds(here(model_location, "tier3_subjective.rds"))|> do_draws() |> mutate(type="Pairs with full statistical information") |> mutate(sens="All data")
 
@@
 # Discussion
+
 Non-replications pose a problem for scientists who want to build on the empirical results in the literature, but the limited numbers of replications and limited research into specific predictors of replication failure mean that the reasons for non-replications are not well understood.
@@
 
-The same issue that may cause a study not to replicate under constrained circumstances (despite hypothetically replicating under more favorable circumstances such as expert administration or larger budgets) will also plague attempts to build off those studies in constrained circumstances.
-Thus, we believe it is relevant to consider how well studies replicate under the limitations of real world resource and expertise constraints.
-
 We conducted an observational study of replication attempts, and our results are limited by the studies we included, which are limited in number and may not be representative of the studies of interest to psychologists as a whole.
-Our predictor variables were not manipulated, so they cannot be interpreted as causing (non-) replication, but only as correlational markers.
+Our predictor variables were not manipulated, so they cannot be interpreted as causing (non-)replication, but only as correlational markers.
 Some of the correlates are most easily interpreted as being about the original study, and others reflect the closeness of the replication to the original.
@@
 Given the predictive value, slightly more skepticism and critical reading of between-subjects designs may be warranted, but this correlation, by itself, does not mean scientists should prefer to run within-subjects designs.
+
+[TODO should we discuss the need for more replications and pooling and coding??]
 
@@
 Pedagogy has an important role to play in open science more broadly -- it's one thing to require or incentivize certain practices, but the tools and workflows of open science have to be learned.
-<!--Teaching these skills and giving students an opportunity to practice using open, reproducible workflows shows students how to integrate open science practices into their workflows, before other habits can ossify.
-In doing replications, students may be motivated to value transparent practices, as they either struggle to reimplement studies from vague methods or appreciate the ease of working with available materials and analysis code.
-In presenting work with classmates, students see that there is variation in how well studies replicate, with some replicating very cleanly and others not at all.
-This sort of first hand experience teaches students that not everything they read in the literature may just work if done again.
--->
 
@@
 ```
+
 The dataset of replication projects comes from class projects conducted in PSYCH 251 (earlier called PSYCH 254) a graduate-level experimental methods class taught at Stanford by MCF from 2011 to 2022.
@@
 This subjective replication outcome was chosen because it already existed, could be applied to all projects (regardless of type and detail of statistical reporting), and did not rely solely on one statistical measure.
-As a complement, we also identified a "key" statistical test for each paper (see below for details), and if possible, computed p_original and prediction interval at this statistic, following @mathur2020.
-p_original was a continuous measure of the p-value on the hypothesis that the original and replication samples come from the same distribution.
+As a complement, we also identified a "key" statistical test for each paper (see below for details), and if possible, computed p-original and prediction interval at this statistic, following @mathur2020.
+p-original was a continuous measure of the p-value on the hypothesis that the original and replication samples come from the same distribution.
 Prediction interval was a binary measure of whether the replication outcome fell within the prediction interval of the original outcome measure.
@@
 
-We then calculated p values, ES, p_orig, and predInt.
+We then calculated p values, effect sizes, p-original, and prediction intervals.
 We choose to recalculate p values and effect sizes from the means or test statistic rather than use reported measures when possible because we thought this would be more reliable and transparent.
@@
 
-In some cases, p-values and or effect sizes were not calculable either due to insufficient reporting (ex.
+In some cases, p-values or effect sizes were not calculable either due to insufficient reporting (ex.
 reporting a p-value but no other statistics from a test) or key measures where p-values and effect sizes did not apply (ex.
 PCA as measure of interest).
-Where studies reported beta estimates and standard errors or proportions, standardized effects sizes are not an applicable measure, but we were still able to calculate p_original and prediction interval.
+Where studies reported beta estimates and standard errors or proportions, standardized effects sizes are not an applicable measure, but we were still able to calculate p-original and prediction interval.
 
@@
 
-In regression analyses, we used SMD and log p-value as predictors.
+In regression analyses, we used standardized mean difference and log p-value as predictors.
 
@@
 
-All models used a horseshoe prior in brms.
+We used a horseshoe shrinkage prior on the fixed effect coefficients because we had a lot of predictors compared to the amount of data [@carvalho09].
 All models included random slopes for predictors nested within year the class occurred to control for variation between cohorts of students.
@@
 The priors we used were horseshoe(3) for betas, normal(0,.5) for standard deviation of random slopes, and lkj(1) for correlations between random slopes.
+Models were run in BRMS [@brms].
 
@@
 
-Results from these models not reported in the main paper are reported in the supplement.
+Results from these models not reported in the main paper are reported in the Supplement.
 

### 2023-05-15 paper/manuscript.tex
attempts were made

@@
 
+TODO figure out how to fix the fact that some of the p-orig and predInt had things on different scales b/c I screwed up ! Whether to switch all the SMD or only the ones we can't get on original!!!
+
+ALSO figure out how to talk about tau**2 and do that
+
+TODO propogate naming schemes to supplement wrt models
+
 \hypertarget{introduction}{%
@@
 
-To better understand this problem, we might want to know 1) what quantity to measure if we want to capture frustration and waste due to non-cumulative findings and 2) from a descriptive perspective, what types of studies are most at risk for this issue.
+To identify studies are risk for non-cumulative findings, we might want to know 1) what to measure in order to capture the waste and frustration due to non-cumulative failed extensions and 2) from a descriptive perspective, what features of studies are associated with being at risk for this non-replicability.
 Such measurements have been the focus of much prior work around replicability, but there is limited consensus on what is being estimated.
 
-{[}Prior sentence needs work{]}
+{[}Prior paragraph may still need work{]}
 
@@
 They found an overall replication rate of around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}).
-ManyLabs investigated heterogeneity using short target studies that compared between two conditions each.
+Many Labs investigated heterogeneity using short target studies that compared between two conditions each.
 These study designs were not representative of the psychology literature as a whole, and due to the heterogeneity goal, they had large overall samples across multiple sites.
@@
 
+{[}Prior paragraph is a bit verbose, but it's probably fine{]}
+
 Rather than aim for some measure of ``true'' replicability, it makes more sense to contextualize replication efforts based on their methods and outcome measures.
@@
 
-Our goal in estimating replicability is to look for markers of when findings can support cumulative science.
-Most scientific work is conducted by students, working with limited budgets, limited time, and without access to outside experts.
-Therefore, to figure out what studies graduate students could build on, it makes sense to focus on replications conducted by students (\protect\hyperlink{ref-frank2022}{\textbf{frank2022?}}).
-In our current study, we use student success at replicating an effect as our estimand.
-In particular, our estimand is the probability that a researcher, on selecting a finding of interest from the literature, can successfully achieve a result satisfactorily close enough to the original that they can build on it in their own work, with all the necessary compromises to the methods and sample of the original that may be required by the constraints of the situation.
-
-{[}maybe drop last sentence and work into a longer paragraph?{]}
-
-{[}TODO Maya says firm this up and introduce quant outcomes as well{]}
-
-As a complement, we also measure how similar/consistent the original and replication effects were for the key effect of each study. TODO blah blah
+Our goal in estimating replicability is to look for markers of when findings can (and cannot) support cumulative science.
+If a study cannot be replicated in a given set of circumstances, we believe it it unlikely that the study can be successfully built upon in those circumstances either.
+Thus, we look at what studies are replicable under the circumstances where most scientific work is conducted: by students who are working with limited budgets, limited time, and without access to outside experts (\protect\hyperlink{ref-frank2012}{Frank \& Saxe 2012}).
+Our primary estimand is whether a student researcher, on selecting a finding of interest from the literature, can successfully achieve a result close enough to the original that they could build on it in their own work.
 
@@
 Our sample of studies is selected based on what studies students were interested in and wanting to replicate, with some filtering for feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable given methodological and budgetary constraints.
-We use a subjective replication score as our primary metric.
-Whether one feels confident in the results of a study given a replication is not always dependent on only one outcome measure (ex.
-interaction term) and particularly not dependent on only one statistical comparison between the two studies (ex.
-replication is p\textless.05 same direction as original).
-This metric avoids bright line distinctions and accommodates the range of outcome measures in our diverse set of studies.
-As a complement to this, we include two statistical measures of replication success, applied to the key stat TODO
+In addition to this subjective measure of replicability, we also compare the effect sizes of the original and replication on one key outcome per study using prediction interval and p-original (\protect\hyperlink{ref-mathur2020}{Mathur \& VanderWeele 2020}).
 
-{[}Examples ??{]} TODO redo paragraph
-Despite variation in how large-scale replication studies have defined replication successes, there is work suggesting some consistency in the predictors of replication success.
-Knowing these predictors is important for appropriately calibrating how we read the literature and for eventually identifying targets for interventions.
+{[}TODO possibly say more??{]}
 
-{[}TODO Maya possibly suggests mentioning the uzzi paper that I am dubious of{]}
+Despite variation in the methods and outcomes used by large-scale replication studies, they are often aggregated together in analyses looking at the predictablity of replication success.
 Prediction markets and elicitations have established that people can predict what studies will replicate above chance (\protect\hyperlink{ref-dreber2015}{Dreber et al.
@@
 2019}), but have not identified concrete predictors that differentiate replications from non-replications.
-Machine learning approaches also are above chance at predicting replication, but this did not identify interpretable predictors TODO CITATIONS In terms of specific attributes that predict replicability, Altmejd et al.
+Machine learning approaches trained on the available replications are also above chance at predicting replication success (\protect\hyperlink{ref-yang2020}{Yang et al.
+2020}, \protect\hyperlink{ref-youyou2023}{Youyou et al.
+2023}).
+In terms of specific attributes that predict replicability, Altmejd et al.
 (\protect\hyperlink{ref-altmejd2019}{2019}) examined statistical and demographic features of studies and identified larger sample sizes, larger effect sizes, and simple effects (as opposed to interaction terms) as predictive of replication, and Open Science Consortium (\protect\hyperlink{ref-openscienceconsortium2015}{2015}) looked at correlates of replicability in the RP:P sample and found that studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate.
@@
 
-Experimental approaches can be used to test potential interventions.
+{[}TODO is there a citation for experimental design features being possibly relevant?{]}
+
+While most approaches to correlates of replicability have been correlational, experimental approaches can be used to test potential interventions.
 Protzko et al.
@@
 
-Given the limitations of experimental approaches, correlational approaches are the more popular choice for studying potential predictors of replicability.
-Correlational approaches depend on data from replications, generally drawing heavily from the same small set of data points.
+{[}Awkward transition{]}
+
+However, while they don't incur the expense of collecting new datasets, correlational approaches depend on data from replications.
+As large-scale replications are arduous and expensive to run, analyses generally draw heavily on same small set of data points.
 In particular, the RP:P dataset itself is much discussed and reanalyzed (\protect\hyperlink{ref-anderson2016}{Anderson et al.
@@
 2016}) to the point that much of what we think we know about replicability may be overfit to the 100 studies included in in RP:P.
-More data is needed to identify markers of replicability and targets for potential future interventions.
+More replication data is needed to identify markers of replicability and targets for potential future experimental approaches.
 
@@
 
+Of note, these replications were all conducted on short time scales, with constrained budgets, that in some cases limited the number of participants who could be recruited below what the original study had or what power analyses suggested.
+In nearly all cases, replications were conducted online, with recruitment from Amazon Mechanical Turk (default 2011-2020) or Prolific (default 2021-2022).
+
 Many different measures can be used to define replication success of an individual statistical result (\protect\hyperlink{ref-simonsohn2015}{Simonsohn 2015}, \protect\hyperlink{ref-gelman2018}{Gelman 2018/ed}, \protect\hyperlink{ref-mathur2020}{Mathur \& VanderWeele 2020}).
-However, a single test of a single statistical result doesn't capture the sense of whether a replication is close enough that one could feel confident extending the finding, so we used a subjective rating of replication success as our primary outcome measure.
-This subjective measure, unlike statistical measures, accommodated studies with multiple important outcome measures that together defined the pattern of interest and was applicable across the diverse range of statistical measures and reporting practices present in the sample.
+However, whether one feels confident in the results of a study given a replication is not always dependent on only one outcome measure (ex.
+interaction term) and particularly not dependent on only one statistical comparison between the two studies (ex.
+replication is p\textless.05 same direction as original).
+As our primary outcome, we use a subjective replication score which, unlike statistical measures, accommodated studies with multiple important outcome measures that together defined the pattern of interest and was applicable across the diverse range of statistical measures and reporting practices present in the sample.
 Importantly, a holistic measure of replication success had already been coded for most projects when they were turned in at the end of the class.
@@
 
-Across the 176 studies, the average subjective replication score was 49\%, which we interpret as an overall subjective replication rate.
+Across the 176 studies, the average subjective replication score was 49\%, which we can interpret as an overall subjective replication rate.
 45\% (61/136) of the studies had replication outcomes within the prediction interval of the original outcome.
@@
 On average, there was a diminution of effect sizes from original to replication.
+This pattern of results is consistent with the pattern of results found in RP:P (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}).
 
@@
 
-Many predictors individually correlate with subjective replication success (Table \ref{tab:cor}).
-Predictors of higher replicability included within-subjects designs, larger numbers of trials, and the original study having open data.
+TODO any citations around experimental design predictors??
+
+Many predictors individually correlated with subjective replication success (Table \ref{tab:cor}).
+Predictors of higher replicability included within-subjects designs, larger numbers of trials per subject, and the original study having open data.
 Predictors of lower replicability included single vignetted studies with only one induction or example per condition, social psychology studies, and original-replication pairs where the original study was in-person and replication switched to online.
 
-TODO describe what we did to get these numbers!
 Distributions of study outcomes across some of these properties are shown in Figure \ref{fig:predictors-graph}.
-Both social and cognitive psychology studies were well represented in the replication sample, and the cognitive psychology studies replicated at 2.45 times the rate of social psychology studies.
+To quantify the effects of these single predictors, we ran logistic models predicting the subjective replication score (on 0-1) as a function of the single predictor, and exponentiated the coefficient to get an odds ratio.
+Both social and cognitive psychology studies were well represented in the replication sample, and the cognitive psychology studies replicated 2.45 times as often as social psychology studies.
 Within and between subjects designs were both common, and within-subjects designs replicated 3.35 times as much.
-Studies with multiple vignettes replicated 2.62 times more than single vignetted studies.
+Studies with multiple vignettes replicated 2.62 times as often as single vignetted studies.
 However, there were strong correlations among these experimental features and between these experimental features and subfield.
@@
 While a number of predictors show individual correlations with the subjective replication score, many of the predictors intercorrelate with one another.
-In order to determine which predictors were the strongest, we ran a series of pre-registered regression models regularized using a horseshoe prior (see Methods for details; see Supplement for all estimates from all models).
-We ran models both using all the original-replication pairs, but without the predictors original effect size and original p value (that were uncodable for some studies), and models including all predictors, but limiting to the subset of data where all predictors were available.
-The coefficient estimates from two models predicting the subjective replication scores are shown in Figure \ref{fig:mod-results}.
+In order to determine which predictors were the strongest, we ran a series of pre-registered regression models regularized using a horseshoe shrinkage prior (\protect\hyperlink{ref-carvalho09}{Carvalho et al.
+2009}).
+We ran both 1) models using all the original-replication pairs, but without original effect size and original p value as predictors, as they were uncodable for some pairs, and 2) models including all predictors, but on only the subset of data where all predictors were available.
+The coefficient estimates from two models predicting the subjective replication scores are shown in Figure \ref{fig:mod-results}; see Supplement for full model results.
 Due to a large number of predictors coupled with a small and noisy dataset there is much uncertainty around the coefficients even with strong regularization.
@@
 
-Within-subjects designs stand out as the strongest indicator of replicability in the model with all the original-replication pairs (0.55, CrI= {[}-0.01, 2{]}).
-In the model with all predictors, but less data, within-subjects designs remain predictive (0.64, CrI= {[}-0.03, 2.38{]}).
-Standardized effect size is another strong predictor of subjective replication score (0.59, CrI= {[}0.31, 2.58{]}).
+Within-subjects designs stand out as the strongest indicator of replicability in the model with all the data (0.55, CrI= {[}-0.01, 2{]}).
+In the model with all predictors, but less data, within-subjects designs remain predictive (0.64, CrI= {[}-0.03, 2.38{]}), and standardized effect size is also a strong predictor of subjective replication score (0.59, CrI= {[}0.31, 2.58{]}).
 Both effects are robust to a sensitivity analysis including only studies with close replications and matching statistical tests (within-subjects 0.87, CrI= {[}-0.01, 3.34{]}; effect size 0.97, CrI= {[}0.76, 4.59{]}).
 
-We also ran models predicting our secondary outcome measures: whether the replication effect was within the prediction interval as the original effect and what the p-original was between the replication and original.
+We also ran models predicting our secondary outcome measures: whether the replication effect was within the prediction interval of the original effect and what the p-original was between the replication and original.
 Both these models had even more uncertain estimates.
 While the credible intervals were wide, the general patterns of predictor direction and relative strength were similar to the subjective replication models.
-The strongest predictors were still within-subjects designs (0.71, CrI= {[}-0.12, 2.38{]}) and studies with larger effect sizes (0.3, CrI= {[}-0.31, 0.89{]}).
+The strongest predictors for prediction interval were still within-subjects designs (0.71, CrI= {[}-0.12, 2.38{]}) and studies with larger effect sizes (0.3, CrI= {[}-0.31, 0.89{]}).
 
@@
 Given the predictive value, slightly more skepticism and critical reading of between-subjects designs may be warranted, but this correlation, by itself, does not mean scientists should prefer to run within-subjects designs.
+
+{[}TODO should we discuss the need for more replications and pooling and coding??{]}
 
@@
 This subjective replication outcome was chosen because it already existed, could be applied to all projects (regardless of type and detail of statistical reporting), and did not rely solely on one statistical measure.
-As a complement, we also identified a ``key'' statistical test for each paper (see below for details), and if possible, computed p\_original and prediction interval at this statistic, following Mathur \& VanderWeele (\protect\hyperlink{ref-mathur2020}{2020}).
-p\_original was a continuous measure of the p-value on the hypothesis that the original and replication samples come from the same distribution.
+As a complement, we also identified a ``key'' statistical test for each paper (see below for details), and if possible, computed p-original and prediction interval at this statistic, following Mathur \& VanderWeele (\protect\hyperlink{ref-mathur2020}{2020}).
+p-original was a continuous measure of the p-value on the hypothesis that the original and replication samples come from the same distribution.
 Prediction interval was a binary measure of whether the replication outcome fell within the prediction interval of the original outcome measure.
@@
 
-We then calculated p values, ES, p\_orig, and predInt.
+We then calculated p values, effect sizes, p-original, and prediction intervals.
 We choose to recalculate p values and effect sizes from the means or test statistic rather than use reported measures when possible because we thought this would be more reliable and transparent.
@@
 
-In some cases, p-values and or effect sizes were not calculable either due to insufficient reporting (ex.
+In some cases, p-values or effect sizes were not calculable either due to insufficient reporting (ex.
 reporting a p-value but no other statistics from a test) or key measures where p-values and effect sizes did not apply (ex.
 PCA as measure of interest).
-Where studies reported beta estimates and standard errors or proportions, standardized effects sizes are not an applicable measure, but we were still able to calculate p\_original and prediction interval.
+Where studies reported beta estimates and standard errors or proportions, standardized effects sizes are not an applicable measure, but we were still able to calculate p-original and prediction interval.
 
@@
 
-All models used a horseshoe prior in brms.
+We used a horseshoe shrinkage prior on the fixed effect coefficients because we had a lot of predictors compared to the amount of data (\protect\hyperlink{ref-carvalho09}{Carvalho et al.
+2009}).
 All models included random slopes for predictors nested within year the class occurred to control for variation between cohorts of students.
@@
 The priors we used were horseshoe(3) for betas, normal(0,.5) for standard deviation of random slopes, and lkj(1) for correlations between random slopes.
+Models were run in BRMS (\protect\hyperlink{ref-brms}{Bürkner 2017}).
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-brms}{}}%
+Bürkner P-C (2017) {brms}: An {R} package for {Bayesian} multilevel models using {Stan}.
+\emph{Journal of Statistical Software} \textbf{80}:1--28.
+doi:\href{https://doi.org/10.18637/jss.v080.i01}{10.18637/jss.v080.i01}
+
 \leavevmode\vadjust pre{\hypertarget{ref-camerer2018}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-carvalho09}{}}%
+Carvalho CM, Polson NG, Scott JG (2009) Handling sparsity via the horseshoe.
+In: Dyk D van, Welling M (eds) \emph{Proceedings of the twelth international conference on artificial intelligence and statistics}.
+PMLR, Hilton Clearwater Beach Resort, Clearwater Beach, Florida USA, p 73--80.
+Available from: \url{https://proceedings.mlr.press/v5/carvalho09a.html}
+
 \leavevmode\vadjust pre{\hypertarget{ref-crump2013}{}}%
-Crump MJC, McDonnell JV, Gureckis TM (2013) Evaluating amazon's mechanical turk as a tool for experimental behavioral research.
-\emph{{PLOS} {ONE}} \textbf{8}:e57410.
+Crump MJC, McDonnell JV, Gureckis TM (2013) Evaluating {Amazon}'s {Mechanical Turk} as a {Tool} for {Experimental Behavioral Research}.
+\emph{PLOS ONE} \textbf{8}:e57410.
 doi:\href{https://doi.org/10.1371/journal.pone.0057410}{10.1371/journal.pone.0057410}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-hagger2016}{}}%
-Hagger MS, Chatzisarantis NLD, Alberts H, Anggono CO, Batailler C, Birt AR, Brand R, Brandt MJ, Brewer G, Bruyneel S, Calvillo DP, Campbell WK, Cannon PR, Carlucci M, Carruth NP, Cheung T, Crowell A, De Ridder DTD, Dewitte S, Elson M, Evans JR, Fay BA, Fennis BM, Finley A, Francis Z, Heise E, Hoemann H, Inzlicht M, Koole SL, Koppel L, Kroese F, Lange F, Lau K, Lynch BP, Martijn C, Merckelbach H, Mills NV, Michirev A, Miyake A, Mosser AE, Muise M, Muller D, Muzi M, Nalis D, Nurwanti R, Otgaar H, Philipp MC, Primoceri P, Rentzsch K, Ringos L, Schlinkert C, Schmeichel BJ, Schoch SF, Schrama M, Schütz A, Stamos A, Tinghög G, Ullrich J, vanDellen M, Wimbarti S, Wolff W, Yusainy C, Zerhouni O, Zwienenberg M (2016) A multilab preregistered replication of the ego-depletion effect.
+Hagger MS, Chatzisarantis NLD, Alberts H, Anggono CO, Batailler C, Birt AR, Brand R, Brandt MJ, Brewer G, Bruyneel S, Calvillo DP, Campbell WK, Cannon PR, Carlucci M, Carruth NP, Cheung T, Crowell A, De Ridder DTD, Dewitte S, Elson M, Evans JR, Fay BA, Fennis BM, Finley A, Francis Z, Heise E, Hoemann H, Inzlicht M, Koole SL, Koppel L, Kroese F, Lange F, Lau K, Lynch BP, Martijn C, Merckelbach H, Mills NV, Michirev A, Miyake A, Mosser AE, Muise M, Muller D, Muzi M, Nalis D, Nurwanti R, Otgaar H, Philipp MC, Primoceri P, Rentzsch K, Ringos L, Schlinkert C, Schmeichel BJ, Schoch SF, Schrama M, Schütz A, Stamos A, Tinghög G, Ullrich J, vanDellen M, Wimbarti S, Wolff W, Yusainy C, Zerhouni O, Zwienenberg M (2016) A {Multilab Preregistered Replication} of the {Ego-Depletion Effect}.
 \emph{Perspect Psychol Sci} \textbf{11}:546--573.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-openscienceconsortium2015}{}}%
-Open Science Consortium (2015) \href{https://www.science.org/doi/full/10.1126/science.aac4716?casa_token=IJ35TwwlcjsAAAAA\%3AqiP68QbVAHleIg9zD3WugKWuV6Oa5rswS0VQnDsCq5I14ME4WIQabNGVD_T6SBSuAt6voVHNnWc0sw}{Estimating the reproducibility of psychological science}.
-\emph{Science}
+Open Science Consortium (2015) Estimating the reproducibility of psychological science. \emph{Science}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-yang2020}{}}%
+Yang Y, Youyou W, Uzzi B (2020) Estimating the deep replicability of scientific findings using human and artificial intelligence.
+\emph{Proc Natl Acad Sci} \textbf{117}:10762--10768.
+doi:\href{https://doi.org/10.1073/pnas.1909046117}{10.1073/pnas.1909046117}
+
+\leavevmode\vadjust pre{\hypertarget{ref-youyou2023}{}}%
+Youyou W, Yang Y, Uzzi B (2023) A discipline-wide investigation of the replicability of {Psychology} papers over the past two decades.
+\emph{Proc Natl Acad Sci} \textbf{120}:e2208863120.
+doi:\href{https://doi.org/10.1073/pnas.2208863120}{10.1073/pnas.2208863120}
+
 \end{CSLReferences}

### 2023-05-15 paper/supplement.Rmd
attempts were made

--- 2023-04-26 paper/supplement.Rmd
@@
 model_location="code/models"
+d <- read_csv(here("data", "processed_data.csv")) |> filter(status!="unusable") |> filter(include!="no")
 
@@
 
+# Forest plot
+
+```{r forest, out.height="100%", fig.width=9, fig.height=12, fig.pos="ht", fig.cap="Forest plot of original and replication effect sizes.
+Original effect sizes are open dots, replication are closed dots.
+Coloring indicates subjective replication score, and p-original values are listed on the left side.
+"}
+
+d |> 
+  filter(target_d_calc < 5, rep_d_calc < 5) |>
+  mutate(numpredInt=ifelse(predInt,1,0)) |> 
+  ggplot(aes(y=reorder(target_lastauthor_year,target_d_calc, mean), color=as.factor(sub_rep)))+
+    geom_vline(xintercept=0, linetype=3)+
+  geom_point(aes(x=target_d_calc, shape="original"))+
+  geom_point(aes(x=rep_d_calc, shape="replication"))+
+  geom_segment(aes(x=target_d_calc, xend=rep_d_calc, y=target_lastauthor_year, yend=target_lastauthor_year))+
+  scale_shape_manual(values=c("original"=21,"replication"=19), name=NULL)+
+  coord_cartesian(xlim=c(-1.5,3.5))+
+  geom_text(aes(x=-1.4, label=round(p_orig,3)), color="black", size=3, hjust=0, show.legend = F)+
+  scale_color_viridis(discrete=T, direction = 1, 
+                      name = "Subjective\nReplication\nSuccess\n")+theme_classic()+
+  labs(x="Standardized Effect Size")+
+  theme(axis.ticks.y=element_blank(), axis.title.y=element_blank())
+```
+
+# Additional model results
 ```{r}
@@
 ```
+
+# tau**2  sensitivity analysis is a mess
+
+```{r, include=F, echo=F}
+# library(Replicate)
+# do_pred_int <- function(target_ES, target_SE, rep_ES, rep_SE){
+#   if(!is.na(target_ES)&!is.na(rep_ES)&!is.na(target_SE)&!is.na(rep_SE)){
+#     return(Replicate::pred_int(target_ES, target_SE**2, rep_ES, rep_SE**2)$rep.inside)
+#   }
+#   return(NA)
+# }
+# 
+# do_pred_int_sens <- function(target_ES, target_SE, rep_ES, rep_SE){
+#   if(!is.na(target_ES)&!is.na(rep_ES)&!is.na(target_SE)&!is.na(rep_SE)){
+#     yio=target_ES
+#     vio=target_SE**2
+#     yir=rep_ES
+#     vir=rep_SE**2
+#     t2=.21
+#     pooled.SE = sqrt(vio + vir + t2)
+#     PILo.sens = yio - qnorm(0.975) * pooled.SE
+#     PIHi.sens = yio + qnorm(0.975) * pooled.SE
+#     PIinside.sens = (yir > PILo.sens) & (yir < PIHi.sens)
+#     return(PIinside.sens)
+#   }
+#   return(NA)
+# }
+# do_p_orig <- function(target_ES, target_SE, rep_ES, rep_SE){
+#   if(!is.na(target_ES)&!is.na(rep_ES)){
+#     return(Replicate::p_orig(target_ES, target_SE**2,rep_ES, t2=0, rep_SE**2))
+#   }
+#   return(NA)
+# }
+# 
+# do_p_orig_sens <- function(target_ES, target_SE, rep_ES, rep_SE){
+#   if(!is.na(target_ES)&!is.na(rep_ES)){
+#     return(Replicate::p_orig(target_ES, target_SE**2,rep_ES, t2=0.21, rep_SE**2))
+#   }
+#   return(NA)
+# }
+# check_sens <- d |> filter(include=="stats") |> 
+#   mutate(sens_target_d=target_d_calc,
+#          sens_target_se=target_SE*target_d_calc/target_ES,
+#          sens_target_se2=4/target_N+target_d_calc**2/(2*target_N),
+#          sens_rep_d=rep_d_calc,
+#          sens_rep_se=rep_SE*rep_d_calc/rep_ES,
+#          sens_target_se2=4/replication_N+rep_d_calc**2/(2*replication_N)) |> 
+#   
+#   rowwise() |> 
+#   mutate(predInt2 = do_pred_int(sens_target_d, sens_target_se, sens_rep_d, sens_rep_se),
+#          p_orig2 = do_p_orig(sens_target_d, sens_target_se, sens_rep_d, sens_rep_se),
+#          predIntSens=do_pred_int_sens(sens_target_d, sens_target_se, sens_rep_d, sens_rep_se),
+#          p_origSens=do_p_orig_sens(sens_target_d, sens_target_se, sens_rep_d, sens_rep_se))
+# 
+# 
+# check_sens |> select(starts_with("sens"))
+# check_sens |> #select(predInt, predInt2, predIntSens, p_orig, p_orig2, p_origSens) |> 
+#   filter(signif(p_orig,2)!=signif(p_orig2,2)) |> View()
+# 
+# check_sens |> group_by(predIntSens) |> tally()
+# check_sens |> group_by(predInt2) |> tally()
+# check_sens |> group_by(predInt) |> tally()
+# 
+# check_sens |> ungroup() |> summarize(m=median(p_origSens))
+# check_sens |> ungroup() |> summarize(m=median(p_orig2))
+# check_sens |> ungroup() |> summarize(m=median(p_orig))
+# 
+# 
+# check_sens |> mutate(r1=sens_target_d/target_ES, r2=sens_target_se/target_SE, r3=sens_rep_d/rep_ES, r4=sens_rep_se/rep_SE) |> select(r1,r2,r3,r4)
+# 
+# d |> select(replication_raw_stat, target_raw_stat, include, sensitivity) |> View()
+```

### 2023-05-22 paper/supplement.Rmd
poking at tau squared

@@
 ```{r, include=F, echo=F}
-# library(Replicate)
-# do_pred_int <- function(target_ES, target_SE, rep_ES, rep_SE){
-#   if(!is.na(target_ES)&!is.na(rep_ES)&!is.na(target_SE)&!is.na(rep_SE)){
-#     return(Replicate::pred_int(target_ES, target_SE**2, rep_ES, rep_SE**2)$rep.inside)
-#   }
-#   return(NA)
-# }
-# 
-# do_pred_int_sens <- function(target_ES, target_SE, rep_ES, rep_SE){
-#   if(!is.na(target_ES)&!is.na(rep_ES)&!is.na(target_SE)&!is.na(rep_SE)){
-#     yio=target_ES
-#     vio=target_SE**2
-#     yir=rep_ES
-#     vir=rep_SE**2
-#     t2=.21
-#     pooled.SE = sqrt(vio + vir + t2)
-#     PILo.sens = yio - qnorm(0.975) * pooled.SE
-#     PIHi.sens = yio + qnorm(0.975) * pooled.SE
-#     PIinside.sens = (yir > PILo.sens) & (yir < PIHi.sens)
-#     return(PIinside.sens)
-#   }
-#   return(NA)
-# }
-# do_p_orig <- function(target_ES, target_SE, rep_ES, rep_SE){
-#   if(!is.na(target_ES)&!is.na(rep_ES)){
-#     return(Replicate::p_orig(target_ES, target_SE**2,rep_ES, t2=0, rep_SE**2))
-#   }
-#   return(NA)
-# }
-# 
-# do_p_orig_sens <- function(target_ES, target_SE, rep_ES, rep_SE){
-#   if(!is.na(target_ES)&!is.na(rep_ES)){
-#     return(Replicate::p_orig(target_ES, target_SE**2,rep_ES, t2=0.21, rep_SE**2))
-#   }
-#   return(NA)
-# }
-# check_sens <- d |> filter(include=="stats") |> 
-#   mutate(sens_target_d=target_d_calc,
-#          sens_target_se=target_SE*target_d_calc/target_ES,
-#          sens_target_se2=4/target_N+target_d_calc**2/(2*target_N),
-#          sens_rep_d=rep_d_calc,
-#          sens_rep_se=rep_SE*rep_d_calc/rep_ES,
-#          sens_target_se2=4/replication_N+rep_d_calc**2/(2*replication_N)) |> 
-#   
-#   rowwise() |> 
-#   mutate(predInt2 = do_pred_int(sens_target_d, sens_target_se, sens_rep_d, sens_rep_se),
-#          p_orig2 = do_p_orig(sens_target_d, sens_target_se, sens_rep_d, sens_rep_se),
-#          predIntSens=do_pred_int_sens(sens_target_d, sens_target_se, sens_rep_d, sens_rep_se),
-#          p_origSens=do_p_orig_sens(sens_target_d, sens_target_se, sens_rep_d, sens_rep_se))
-# 
-# 
-# check_sens |> select(starts_with("sens"))
-# check_sens |> #select(predInt, predInt2, predIntSens, p_orig, p_orig2, p_origSens) |> 
-#   filter(signif(p_orig,2)!=signif(p_orig2,2)) |> View()
-# 
-# check_sens |> group_by(predIntSens) |> tally()
-# check_sens |> group_by(predInt2) |> tally()
-# check_sens |> group_by(predInt) |> tally()
-# 
-# check_sens |> ungroup() |> summarize(m=median(p_origSens))
-# check_sens |> ungroup() |> summarize(m=median(p_orig2))
-# check_sens |> ungroup() |> summarize(m=median(p_orig))
-# 
-# 
-# check_sens |> mutate(r1=sens_target_d/target_ES, r2=sens_target_se/target_SE, r3=sens_rep_d/rep_ES, r4=sens_rep_se/rep_SE) |> select(r1,r2,r3,r4)
-# 
-# d |> select(replication_raw_stat, target_raw_stat, include, sensitivity) |> View()
+library(Replicate)
+do_pred_int <- function(target_ES, target_SE, rep_ES, rep_SE){
+  if(!is.na(target_ES)&!is.na(rep_ES)&!is.na(target_SE)&!is.na(rep_SE)){
+    return(Replicate::pred_int(target_ES, target_SE**2, rep_ES, rep_SE**2)$rep.inside)
+  }
+  return(NA)
+}
+
+do_pred_int_sens <- function(target_ES, target_SE, rep_ES, rep_SE){
+  if(!is.na(target_ES)&!is.na(rep_ES)&!is.na(target_SE)&!is.na(rep_SE)){
+    yio=target_ES
+    vio=target_SE**2
+    yir=rep_ES
+    vir=rep_SE**2
+    t2=.21**2
+    pooled.SE = sqrt(vio + vir + t2)
+    PILo.sens = yio - qnorm(0.975) * pooled.SE
+    PIHi.sens = yio + qnorm(0.975) * pooled.SE
+    PIinside.sens = (yir > PILo.sens) & (yir < PIHi.sens)
+    return(PIinside.sens)
+  }
+  return(NA)
+}
+do_p_orig <- function(target_ES, target_SE, rep_ES, rep_SE){
+  if(!is.na(target_ES)&!is.na(rep_ES)){
+    return(Replicate::p_orig(target_ES, target_SE**2,rep_ES, t2=0, rep_SE**2))
+  }
+  return(NA)
+}
+
+do_p_orig_sens <- function(target_ES, target_SE, rep_ES, rep_SE){
+  if(!is.na(target_ES)&!is.na(rep_ES)){
+    return(Replicate::p_orig(target_ES, target_SE**2,rep_ES, t2=0.21**2, rep_SE**2))
+  }
+  return(NA)
+}
+check_sens <- d |> filter(include=="stats") |>
+  mutate(sens_target_d=target_d_calc,
+         sens_target_se=target_SE*target_d_calc/target_ES,
+         sens_target_se2=4/target_N+target_d_calc**2/(2*target_N),
+         sens_rep_d=rep_d_calc,
+         sens_rep_se=rep_SE*rep_d_calc/rep_ES,
+         sens_target_se2=4/replication_N+rep_d_calc**2/(2*replication_N)) |>
+
+  rowwise() |>
+  mutate(predInt2 = do_pred_int(sens_target_d, sens_target_se, sens_rep_d, sens_rep_se),
+         p_orig2 = do_p_orig(sens_target_d, sens_target_se, sens_rep_d, sens_rep_se),
+         predIntSens=do_pred_int_sens(sens_target_d, sens_target_se, sens_rep_d, sens_rep_se),
+         p_origSens=do_p_orig_sens(sens_target_d, sens_target_se, sens_rep_d, sens_rep_se))
+
+check_sens |> select(starts_with("sens"))
+check_sens |> #select(predInt, predInt2, predIntSens, p_orig, p_orig2, p_origSens) |>
+  filter(signif(p_orig,2)!=signif(p_orig2,2)) |> View()
+
+check_sens |> group_by(predIntSens) |> tally()
+check_sens |> group_by(predInt2) |> tally()
+check_sens |> group_by(predInt) |> tally()
+
+check_sens |> ungroup() |> summarize(m=median(p_origSens))
+check_sens |> ungroup() |> summarize(m=median(p_orig2))
+check_sens |> ungroup() |> summarize(m=median(p_orig))
+
+check_sens |> mutate(r1=sens_target_d/target_ES, r2=sens_target_se/target_SE, r3=sens_rep_d/rep_ES, r4=sens_rep_se/rep_SE) |> select(r1,r2,r3,r4)
+
+d |> select(replication_raw_stat, target_raw_stat, include, sensitivity) |> View()
 ```

### 2023-06-30 code/process.Rmd
fixes based on meeting with Maya

@@
 ```
-Descriptions:
-
-- "done" -- fully coded, can be used for whatever is specified in other column 
-- "cannot tell direction" -- have stats for an effect, but can't tell which direction it is in
-- "unusable" -- got as far as I can, and it does not have complete descriptives
-- "missing" -- student didn't finish or we don't have write-up
-- "non-experiment" -- student replicated something that was not an experiment
-- "reproduction" -- student did a reproduction and not replication
 
@@
 
-test |> filter(is.na(target_ES)) |> filter(!is.na(target_raw_stat)) |> select(target_lastauthor_year, target_raw_stat)
-
-test |> filter(is.na(rep_ES)) |> filter(!is.na(replication_raw_stat)) |> select(target_lastauthor_year, replication_raw_stat)
+test |> filter(is.na(target_ES)&(is.na(target_d_calc))) |> filter(!is.na(target_raw_stat)) |> select(target_lastauthor_year, target_raw_stat)
+
+test |> filter(is.na(rep_ES)&(is.na(rep_d_calc))) |> filter(!is.na(replication_raw_stat)) |> select(target_lastauthor_year, replication_raw_stat)
 
@@
 
+#d_es |> filter(is.na(target_ES)!=is.na(target_SE))
+#d_es |> filter(is.na(rep_ES)!=is.na(rep_SE))
+#d_es |> filter(is.na(rep_d_calc)!=is.na(rep_d_calc_se)) #fine all of the bad ones are exp only
+#d_es |> filter(is.na(target_d_calc)!=is.na(target_d_calc_se))
+
 d_es_predInt <- d_es |> 
   rowwise() |> 
-  mutate(predInt = do_pred_int(target_ES, target_SE, rep_ES, rep_SE),
+  mutate(predInt = do_pred_int(target_ES, target_SE, rep_ES, rep_SE), # on untransformed scale
+         predInt_from_d = do_pred_int(target_d_calc, target_d_calc_se, rep_d_calc, rep_d_calc_se), #on standardized scale 
          p_orig = do_p_orig(target_ES, target_SE, rep_ES, rep_SE),
+         p_orig_from_d = do_p_orig(target_d_calc, target_d_calc_se, rep_d_calc, rep_d_calc_se),
+         predInt=ifelse(is.na(predInt), predInt_from_d, predInt), #prefer untransformed scale, but use standardized when that's the only option
+         p_orig=ifelse(is.na(p_orig), p_orig_from_d, p_orig), # prefer untrasformed when available 
+         predInt_with_tau = do_pred_int_sens(target_d_calc, target_d_calc_se, rep_d_calc, rep_d_calc_se), #on standardized scale 
+         p_orig_with_tau = do_p_orig_sens(target_d_calc, target_d_calc_se, rep_d_calc, rep_d_calc_se),
          sub_rep = do_subjective_rep(replicated_instructor_code, 
@@
                                      adjudicated_replication_code)) |> write_csv(here("data","processed_data.csv"))
-```
-
-# viz SMD
+
+#d_es_predInt |> filter(include!="exp") |> filter(is.na(predInt))
+#d_es_predInt |> filter(include!="exp") |> filter(is.na(p_orig))
+
+```
+
+<!-- # viz SMD
 
@@
 
+-->
+
 # How much missing data?
@@
 
-# how close subrep
+<!-- # how close subrep
 
@@
 ```
+-->
 
@@
 
-Note: tier 2 and 3 models are subject to change as a few more studies might in fact have useable stats & some of the effect size extraction might be incorrect.
-
 ```{r}
@@
 
+<!-- 
 ## Frequentist Lassoes
-
+Note these have not been updated since corrections to data pipeline 
 ```{r}
@@
 ### Pred_int
-Note: predInt may not be reliably calculated in some cases. Dealing with numbers is hard!
 
@@
 ### P_orig
-Note: predInt may not be reliably calculated in some cases. Dealing with numbers is hard!
 

### 2023-06-30 paper/manuscript.tex
fixes based on meeting with Maya

@@
 Across the 176 studies, the average subjective replication score was 49\%, which we can interpret as an overall subjective replication rate.
-45\% (61/136) of the studies had replication outcomes within the prediction interval of the original outcome.
+46\% (62/136) of the studies had replication outcomes within the prediction interval of the original outcome.
 The median p\_original value was 0.03 representing the median probability that a replication study's estimate would be at least as extreme as was actually observed, if in fact the replication and original were statistically consistent.
@@
 
-Within-subjects designs stand out as the strongest indicator of replicability in the model with all the data (0.55, CrI= {[}-0.01, 2{]}).
-In the model with all predictors, but less data, within-subjects designs remain predictive (0.64, CrI= {[}-0.03, 2.38{]}), and standardized effect size is also a strong predictor of subjective replication score (0.59, CrI= {[}0.31, 2.58{]}).
-Both effects are robust to a sensitivity analysis including only studies with close replications and matching statistical tests (within-subjects 0.87, CrI= {[}-0.01, 3.34{]}; effect size 0.97, CrI= {[}0.76, 4.59{]}).
+Within-subjects designs stand out as the strongest indicator of replicability in the model with all the data (0.53, CrI= {[}0, 2{]}).
+In the model with all predictors, but less data, within-subjects designs remain predictive (0.66, CrI= {[}-0.04, 2.37{]}), and standardized effect size is also a strong predictor of subjective replication score (0.65, CrI= {[}0.27, 2.81{]}).
+Both effects are robust to a sensitivity analysis including only studies with close replications and matching statistical tests (within-subjects 0.87, CrI= {[}-0.01, 3.33{]}; effect size 1.05, CrI= {[}0.76, 4.88{]}).
 
@@
 While the credible intervals were wide, the general patterns of predictor direction and relative strength were similar to the subjective replication models.
-The strongest predictors for prediction interval were still within-subjects designs (0.71, CrI= {[}-0.12, 2.38{]}) and studies with larger effect sizes (0.3, CrI= {[}-0.31, 0.89{]}).
+The strongest predictors for prediction interval were still within-subjects designs (0.62, CrI= {[}-0.18, 2.01{]}) and studies with larger effect sizes (0.3, CrI= {[}-0.29, 0.94{]}).
 

### 2023-06-30 paper/supplement.Rmd
fixes based on meeting with Maya

@@
 ```{r, include=F, echo=F}
-library(Replicate)
-do_pred_int <- function(target_ES, target_SE, rep_ES, rep_SE){
-  if(!is.na(target_ES)&!is.na(rep_ES)&!is.na(target_SE)&!is.na(rep_SE)){
-    return(Replicate::pred_int(target_ES, target_SE**2, rep_ES, rep_SE**2)$rep.inside)
-  }
-  return(NA)
-}
+d |> select(starts_with("pred") | starts_with("p_orig"))
 
-do_pred_int_sens <- function(target_ES, target_SE, rep_ES, rep_SE){
-  if(!is.na(target_ES)&!is.na(rep_ES)&!is.na(target_SE)&!is.na(rep_SE)){
-    yio=target_ES
-    vio=target_SE**2
-    yir=rep_ES
-    vir=rep_SE**2
-    t2=.21**2
-    pooled.SE = sqrt(vio + vir + t2)
-    PILo.sens = yio - qnorm(0.975) * pooled.SE
-    PIHi.sens = yio + qnorm(0.975) * pooled.SE
-    PIinside.sens = (yir > PILo.sens) & (yir < PIHi.sens)
-    return(PIinside.sens)
-  }
-  return(NA)
-}
-do_p_orig <- function(target_ES, target_SE, rep_ES, rep_SE){
-  if(!is.na(target_ES)&!is.na(rep_ES)){
-    return(Replicate::p_orig(target_ES, target_SE**2,rep_ES, t2=0, rep_SE**2))
-  }
-  return(NA)
-}
+d |> filter(!is.na(predInt)) |> count(predInt)
+#using predInt as reported 62 in interval, 72 not (45% rep)
 
-do_p_orig_sens <- function(target_ES, target_SE, rep_ES, rep_SE){
-  if(!is.na(target_ES)&!is.na(rep_ES)){
-    return(Replicate::p_orig(target_ES, target_SE**2,rep_ES, t2=0.21**2, rep_SE**2))
-  }
-  return(NA)
-}
-check_sens <- d |> filter(include=="stats") |>
-  mutate(sens_target_d=target_d_calc,
-         sens_target_se=target_SE*target_d_calc/target_ES,
-         sens_target_se2=4/target_N+target_d_calc**2/(2*target_N),
-         sens_rep_d=rep_d_calc,
-         sens_rep_se=rep_SE*rep_d_calc/rep_ES,
-         sens_target_se2=4/replication_N+rep_d_calc**2/(2*replication_N)) |>
+#of those with SMD predInts
+d |> filter(!is.na(predInt_from_d)) |> count(predInt)
+# using predInt 44 in / 70 out (38%)
+d |> filter(!is.na(predInt_from_d)) |> count(predInt_from_d)
+# 34 in /80 out (30%)
+d |> filter(!is.na(predInt_from_d)) |> count(predInt_with_tau)
+# with tau 73 in / 41 out (64%)
 
-  rowwise() |>
-  mutate(predInt2 = do_pred_int(sens_target_d, sens_target_se, sens_rep_d, sens_rep_se),
-         p_orig2 = do_p_orig(sens_target_d, sens_target_se, sens_rep_d, sens_rep_se),
-         predIntSens=do_pred_int_sens(sens_target_d, sens_target_se, sens_rep_d, sens_rep_se),
-         p_origSens=do_p_orig_sens(sens_target_d, sens_target_se, sens_rep_d, sens_rep_se))
+d |> filter(!is.na(predInt)) |> summarise(median(p_orig))
+#median .03
 
-check_sens |> select(starts_with("sens"))
-check_sens |> #select(predInt, predInt2, predIntSens, p_orig, p_orig2, p_origSens) |>
-  filter(signif(p_orig,2)!=signif(p_orig2,2)) |> View()
-
-check_sens |> group_by(predIntSens) |> tally()
-check_sens |> group_by(predInt2) |> tally()
-check_sens |> group_by(predInt) |> tally()
-
-check_sens |> ungroup() |> summarize(m=median(p_origSens))
-check_sens |> ungroup() |> summarize(m=median(p_orig2))
-check_sens |> ungroup() |> summarize(m=median(p_orig))
-
-check_sens |> mutate(r1=sens_target_d/target_ES, r2=sens_target_se/target_SE, r3=sens_rep_d/rep_ES, r4=sens_rep_se/rep_SE) |> select(r1,r2,r3,r4)
-
-d |> select(replication_raw_stat, target_raw_stat, include, sensitivity) |> View()
+#of those with SMD predInts
+d |> filter(!is.na(predInt_from_d)) |>summarise(median(p_orig))
+# median .01
+d |> filter(!is.na(predInt_from_d)) |> summarise(median(p_orig_from_d))
+# median .001
+d |> filter(!is.na(predInt_from_d)) |> summarise(median(p_orig_with_tau))
+# median .15
 ```

### 2023-06-30 code/helper/parse_stats.R

@@ -15,8 +15,10 @@ parse_t <- function(tval, within_between) {
     d_calc=val/sqrt(df+1)
     N_from_df=df+1
   }
-  se=4/N_from_df+d_calc**2/(2*N_from_df)
-  return(data.frame("df_1"=NA, "df_2"=df,"tstat"=val, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df, "ES"=d_calc, "SE"=se))
+  # note this and future instances of it are from taking the delta formula 
+  # and then assuming (two) equal groups and simplifying 
+  se=4/N_from_df+d_calc**2/(2*N_from_df) 
+  return(data.frame("df_1"=NA, "df_2"=df,"tstat"=val, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "d_calc_se"=se, "N_calc"=N_from_df, "ES"=NA, "SE"=NA))
 }
 
 parse_f <- function(fval, within_between){
@@ -40,7 +42,7 @@ parse_f <- function(fval, within_between){
     se=NA
   }
   
-  return(data.frame("df_1"=df_1,"df_2"=df_2,"tstat"=NA, "fstat"=val, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df, "ES"=d_calc, "SE"=se))
+  return(data.frame("df_1"=df_1,"df_2"=df_2,"tstat"=NA, "fstat"=val, "p_calc"=pval, "d_calc"=d_calc, "d_calc_se"=se, "N_calc"=N_from_df, "ES"=NA, "SE"=NA))
 }
 
 
@@ -58,7 +60,7 @@ parse_prop <- function(propval){
   est2_var <- est2*(1-est2)/den2
   diff <- est1-est2
   diff_var <- est1_var+est2_var
-  return(data.frame("df_1"=NA, "df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA, "ES"=diff, "SE"=sqrt(diff_var)))
+  return(data.frame("df_1"=NA, "df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "d_calc_se"=NA, "N_calc"=NA, "ES"=diff, "SE"=sqrt(diff_var)))
 }
[…]

### 2023-06-30 code/helper/stats.R

@@ -7,19 +7,7 @@ pool_m_sd <- function(m1, sd1, n1, m2, sd2, n2){
   
 }
 
-d_es <-  test |> 
-  mutate(target_d_calc=abs(target_d_calc),
-         target_ES=abs(target_ES),
-         rep_d_calc=case_when(
-           same_dir=="yes" ~ abs(rep_d_calc),
-           same_dir=="no" ~-abs(rep_d_calc),
-           T ~ as.numeric(NA)
-         ),
-         rep_ES=case_when(
-           same_dir=="yes" ~ abs(rep_ES),
-           same_dir=="no" ~-abs(rep_ES),
-           T ~ as.numeric(NA)
-         ))
+
 
 
 do_pred_int <- function(target_ES, target_SE, rep_ES, rep_SE){
@@ -29,9 +17,34 @@ do_pred_int <- function(target_ES, target_SE, rep_ES, rep_SE){
   return(NA)
 }
 
+do_pred_int_sens <- function(target_ES, target_SE, rep_ES, rep_SE){
+  if(!is.na(target_ES)&!is.na(rep_ES)&!is.na(target_SE)&!is.na(rep_SE)){
+    yio=target_ES
+    vio=target_SE**2
+    yir=rep_ES
+    vir=rep_SE**2
+    t2=.21**2
+    pooled.SE = sqrt(vio + vir + t2)
+    PILo.sens = yio - qnorm(0.975) * pooled.SE
+    PIHi.sens = yio + qnorm(0.975) * pooled.SE
+    PIinside.sens = (yir > PILo.sens) & (yir < PIHi.sens)
+    return(PIinside.sens)
+  }
+  return(NA)
+}
+
+
+
 do_p_orig <- function(target_ES, target_SE, rep_ES, rep_SE){
-  if(!is.na(target_ES)&!is.na(rep_ES)){
+  if(!is.na(target_ES)&!is.na(rep_ES)&!is.na(target_SE)&!is.na(rep_SE)){
     return(Replicate::p_orig(target_ES, target_SE**2,rep_ES, t2=0, rep_SE**2))
+  }
+  return(NA)
+}
+
+do_p_orig_sens <- function(target_ES, target_SE, rep_ES, rep_SE){
+  if(!is.na(target_ES)&!is.na(rep_ES)&!is.na(target_SE)&!is.na(rep_SE)){
+    return(Replicate::p_orig(target_ES, target_SE**2,rep_ES, t2=0.21**2, rep_SE**2))
   }
   return(NA)
 }

### 2023-07-03 paper/manuscript.Rmd
add sensitivity

@@
 Cumulative scientific progress requires empirical results that are robust enough to support theory construction and future extensions.
-Yet in psychology, some prominent individual findings have failed to replicate, and large-scale investigations suggest that failures to replicate are widespread.
-
-What predicts which studies will replicate? 
-The identification of features that predict replication success is limited by data, however: most analyses draw on the same set of ~170 replications from a few replication projects that have been extensively re-analysed.
-
-We introduce a new dataset of 176 replications where we examine how often students in a graduate-level methods course were able replicate their chosen studies' results closely enough to be ready to build on it in future work.
-The replication rate under this metric was 49%, and 45% of replications with suitable numerical outcomes (N=136) were within the prediction interval of the original outcome.
+Yet in psychology, some prominent findings have failed to replicate, and large-scale investigations suggest that failures to replicate are widespread.
+The identification of features that predict replication success is limited by data, and most analyses re-analyse the same set of ~170 replications.
+We introduce a new dataset of 176 replications from students in a graduate-level methods course.
+Replication results were close enough to original results to support student extensions in 49% of replications.
+45% of replications with suitable numerical outcomes (N=136) had point estimates within the prediction interval of the original outcome.
 Larger original effect sizes and within-participants designs were predictive of replication.
@@
 
-[Still needs work -- also needs shortening -- this is 180, NHB says max 150]
+[148 words / NHB max 150] 
 :::
-
-TODO figure out how to fix the fact that some of the p-orig and predInt had things on different scales b/c I screwed up ! Whether to switch all the SMD or only the ones we can't get on original!!!
-
-ALSO figure out how to talk about tau**2 and do that
-
-TODO propogate naming schemes to supplement wrt models
 
@@
 Across the 176 studies, the average subjective replication score was `r round(pluck(sub_rep_rate,1))`%, which we can interpret as an overall subjective replication rate.
-`r round(pluck(pred_int_rate,1))`% (`r predIntcount`/`r predInttotal`) of the studies had replication outcomes within the prediction interval of the original outcome.
-The median p_original value was `r round(pluck(porig_rate, 1),2)` representing the median probability that a replication study's estimate would be at least as extreme as was actually observed, if in fact the replication and original were statistically consistent.
+`r round(pluck(pred_int_rate,1))`% (`r predIntcount`/`r predInttotal`) of replications has outcomes with point-estimates within the prediction interval of the original outcome.
+The median p_original value on the original and replication point-estimates coming from the same distribution was `r round(pluck(porig_rate, 1),2)`, representing the median probability that a replication study's estimate would be at least as extreme as was actually observed, if in fact the replication and original were statistically consistent.
 Figure \ref{fig:smd} shows the relationship between original standardized effect size, replication effect size, and subjective replication score.
@@
 This pattern of results is consistent with the pattern of results found in RP:P [@openscienceconsortium2015].
+
+```{r }
+
+tau_predIntcount <- d |> filter(!is.na(predInt_from_d)) |> filter(predInt_with_tau) |> nrow()
+tau_predInttotal <- d |> filter(!is.na(predInt_from_d))  |> nrow()
+
+tau_pct <- tau_predIntcount/tau_predInttotal*100
+# with tau 73 in / 41 out (64%)
+
+```
+
+Some multi-site replication projects have found heterogeneity in effect sizes across replication sites [@ebersole2020; @klein2018; @olsson2020].
+We calculated how often the original and replication results were distributionally consistent.
+If we assume that the level of heterogeneity in hypothetical multi-site replications of these effects would be the same as the average level heterogeneity found in @olsson2020 (tau=.21 in SMD units), then `r round(tau_pct,1)`% (`r tau_predIntcount`/`r tau_predInttotal`) of replications are distributionally consistent with the original.
+More work on understanding heterogeneity is needed to understand what levels of heterogeneity to expect across different implementations of the same experiment, and how considerations of heterogeneity should impact interpretations of both novel results and replications.
+
+[what was I supposed to say about heterogeneity, and is this the right place for it?]
 

### 2023-07-03 paper/manuscript.tex
add sensitivity

@@
 Cumulative scientific progress requires empirical results that are robust enough to support theory construction and future extensions.
-Yet in psychology, some prominent individual findings have failed to replicate, and large-scale investigations suggest that failures to replicate are widespread.
-
-What predicts which studies will replicate?
-The identification of features that predict replication success is limited by data, however: most analyses draw on the same set of \textasciitilde170 replications from a few replication projects that have been extensively re-analysed.
-
-We introduce a new dataset of 176 replications where we examine how often students in a graduate-level methods course were able replicate their chosen studies' results closely enough to be ready to build on it in future work.
-The replication rate under this metric was 49\%, and 45\% of replications with suitable numerical outcomes (N=136) were within the prediction interval of the original outcome.
+Yet in psychology, some prominent findings have failed to replicate, and large-scale investigations suggest that failures to replicate are widespread.
+The identification of features that predict replication success is limited by data, and most analyses re-analyse the same set of \textasciitilde170 replications.
+We introduce a new dataset of 176 replications from students in a graduate-level methods course.
+Replication results were close enough to original results to support student extensions in 49\% of replications.
+45\% of replications with suitable numerical outcomes (N=136) had point estimates within the prediction interval of the original outcome.
 Larger original effect sizes and within-participants designs were predictive of replication.
@@
 
-{[}Still needs work -- also needs shortening -- this is 180, NHB says max 150{]}
+{[}148 words / NHB max 150{]}
 
@@
 \end{otherlanguage}
-
-TODO figure out how to fix the fact that some of the p-orig and predInt had things on different scales b/c I screwed up ! Whether to switch all the SMD or only the ones we can't get on original!!!
-
-ALSO figure out how to talk about tau**2 and do that
-
-TODO propogate naming schemes to supplement wrt models
 
@@
 2022}, ego-depletion, \protect\hyperlink{ref-hagger2016}{Hagger et al.
-2016}), and a large-scale replication project pegged the replication rate for findings in top-tier psychology journals at around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}).
+2016}), and a large-scale replication project pegged the replication rate for findings in top-tier psychology journals at around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Science Consortium\} n.d.}).
 When scientists treat publication as a signal of truth and attempt to build on results without verifying them first, they can become frustrated pursuing extensions to a popular, but unreliable result.
@@
 Reproducibility Project: Psychology sampled roughly 100 studies from articles published in three top psychology journals in 2008 and distributed the studies across participating labs.
-They found an overall replication rate of around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}).
+They found an overall replication rate of around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Science Consortium\} n.d.}).
 Many Labs investigated heterogeneity using short target studies that compared between two conditions each.
@@
 In terms of specific attributes that predict replicability, Altmejd et al.
-(\protect\hyperlink{ref-altmejd2019}{2019}) examined statistical and demographic features of studies and identified larger sample sizes, larger effect sizes, and simple effects (as opposed to interaction terms) as predictive of replication, and Open Science Consortium (\protect\hyperlink{ref-openscienceconsortium2015}{2015}) looked at correlates of replicability in the RP:P sample and found that studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate.
+(\protect\hyperlink{ref-altmejd2019}{2019}) examined statistical and demographic features of studies and identified larger sample sizes, larger effect sizes, and simple effects (as opposed to interaction terms) as predictive of replication, and Science Consortium\} (\protect\hyperlink{ref-openscienceconsortium2015}{n.d.}) looked at correlates of replicability in the RP:P sample and found that studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate.
 One potential set of correlates to replicability that has not been thoroughly examined are experimental design features, such as between or within subjects designs and repeated measures.
@@
 Across the 176 studies, the average subjective replication score was 49\%, which we can interpret as an overall subjective replication rate.
-46\% (62/136) of the studies had replication outcomes within the prediction interval of the original outcome.
-The median p\_original value was 0.03 representing the median probability that a replication study's estimate would be at least as extreme as was actually observed, if in fact the replication and original were statistically consistent.
+46\% (62/136) of replications has outcomes with point-estimates within the prediction interval of the original outcome.
+The median p\_original value on the original and replication point-estimates coming from the same distribution was 0.03, representing the median probability that a replication study's estimate would be at least as extreme as was actually observed, if in fact the replication and original were statistically consistent.
 Figure \ref{fig:smd} shows the relationship between original standardized effect size, replication effect size, and subjective replication score.
@@
 On average, there was a diminution of effect sizes from original to replication.
-This pattern of results is consistent with the pattern of results found in RP:P (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}).
+This pattern of results is consistent with the pattern of results found in RP:P (\protect\hyperlink{ref-openscienceconsortium2015}{Science Consortium\} n.d.}).
+
+Some multi-site replication projects have found heterogeneity in effect sizes across replication sites (\protect\hyperlink{ref-klein2018}{Klein et al.
+2018}, \protect\hyperlink{ref-ebersole2020}{Ebersole et al.
+2020}, \protect\hyperlink{ref-olsson2020}{Olsson-Collentine et al.
+2020}).
+We calculated how often the original and replication results were distributionally consistent.
+If we assume that the level of heterogeneity in hypothetical multi-site replications of these effects would be the same as the average level heterogeneity found in Olsson-Collentine et al.
+(\protect\hyperlink{ref-olsson2020}{2020}) (tau=.21 in SMD units), then 64\% (73/114) of replications are distributionally consistent with the original.
+More work on understanding heterogeneity is needed to understand what levels of heterogeneity to expect across different implementations of the same experiment, and how considerations of heterogeneity should impact interpretations of both novel results and replications.
+
+{[}what was I supposed to say about heterogeneity, and is this the right place for it?{]}
 
@@
 We investigated what features of the original study and replication were correlated with replication success, with the goal of being able to identify potential markers of replicability.
-We chose a set of predictor variables based on the correlational results of RP:P (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}), our own intuitions of experimental design factors that might impact replication success, and some covariates related to how close the replication was.
+We chose a set of predictor variables based on the correlational results of RP:P (\protect\hyperlink{ref-openscienceconsortium2015}{Science Consortium\} n.d.}), our own intuitions of experimental design factors that might impact replication success, and some covariates related to how close the replication was.
 A full description of these features is given in Methods.
@@
 While a number of predictors show individual correlations with the subjective replication score, many of the predictors intercorrelate with one another.
-In order to determine which predictors were the strongest, we ran a series of pre-registered regression models regularized using a horseshoe shrinkage prior (\protect\hyperlink{ref-carvalho09}{Carvalho et al.
-2009}).
+In order to determine which predictors were the strongest, we ran a series of pre-registered regression models regularized using a horseshoe shrinkage prior (\protect\hyperlink{ref-carvalho09}{\textbf{carvalho09?}}).
 We ran both 1) models using all the original-replication pairs, but without original effect size and original p value as predictors, as they were uncodable for some pairs, and 2) models including all predictors, but on only the subset of data where all predictors were available.
@@
 
-We used a horseshoe shrinkage prior on the fixed effect coefficients because we had a lot of predictors compared to the amount of data (\protect\hyperlink{ref-carvalho09}{Carvalho et al.
-2009}).
+We used a horseshoe shrinkage prior on the fixed effect coefficients because we had a lot of predictors compared to the amount of data (\protect\hyperlink{ref-carvalho09}{\textbf{carvalho09?}}).
 All models included random slopes for predictors nested within year the class occurred to control for variation between cohorts of students.
@@
 The priors we used were horseshoe(3) for betas, normal(0,.5) for standard deviation of random slopes, and lkj(1) for correlations between random slopes.
-Models were run in BRMS (\protect\hyperlink{ref-brms}{Bürkner 2017}).
+Models were run in BRMS (\protect\hyperlink{ref-brms}{\textbf{brms?}}).
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-brms}{}}%
-Bürkner P-C (2017) {brms}: An {R} package for {Bayesian} multilevel models using {Stan}.
-\emph{Journal of Statistical Software} \textbf{80}:1--28.
-doi:\href{https://doi.org/10.18637/jss.v080.i01}{10.18637/jss.v080.i01}
-
 \leavevmode\vadjust pre{\hypertarget{ref-camerer2018}{}}%
@@
 doi:\href{https://doi.org/10.1038/s41562-018-0399-z}{10.1038/s41562-018-0399-z}
-
-\leavevmode\vadjust pre{\hypertarget{ref-carvalho09}{}}%
-Carvalho CM, Polson NG, Scott JG (2009) Handling sparsity via the horseshoe.
-In: Dyk D van, Welling M (eds) \emph{Proceedings of the twelth international conference on artificial intelligence and statistics}.
-PMLR, Hilton Clearwater Beach Resort, Clearwater Beach, Florida USA, p 73--80.
-Available from: \url{https://proceedings.mlr.press/v5/carvalho09a.html}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-openscienceconsortium2015}{}}%
-Open Science Consortium (2015) Estimating the reproducibility of psychological science. \emph{Science}
+\leavevmode\vadjust pre{\hypertarget{ref-olsson2020}{}}%
+Olsson-Collentine A, Assen MA van, Wicherts J (2020) Heterogeneity in direct replications in psychology and its association with effect size.
 
@@
 Ramscar M, Shaoul C, Baayen RH Why many priming results don't (and won't) replicate: {A} quantitative analysis.
+
+\leavevmode\vadjust pre{\hypertarget{ref-openscienceconsortium2015}{}}%
+Science Consortium\} \{Open \href{https://www.science.org/doi/full/10.1126/science.aac4716?casa_token=IJ35TwwlcjsAAAAA\%3AqiP68QbVAHleIg9zD3WugKWuV6Oa5rswS0VQnDsCq5I14ME4WIQabNGVD_T6SBSuAt6voVHNnWc0sw}{Estimating the reproducibility of psychological science}.
+\emph{Science}
 

### 2023-07-03 paper/manuscript.Rmd
more tau and citation tweaks

@@
 
-tau_predIntcount <- d |> filter(!is.na(predInt_from_d)) |> filter(predInt_with_tau) |> nrow()
-tau_predInttotal <- d |> filter(!is.na(predInt_from_d))  |> nrow()
+tau_predIntcount <- d |> filter(include %in% c("stats")) |> filter(!is.na(predInt_from_d)) |> filter(predInt_with_tau) |> nrow()
+tau_predInttotal <- d |> filter(include %in% c("stats")) |> filter(!is.na(predInt_from_d))  |> nrow()
 
 tau_pct <- tau_predIntcount/tau_predInttotal*100
-# with tau 73 in / 41 out (64%)
 

### 2023-07-03 paper/manuscript.tex
more tau and citation tweaks

--- 2023-06-30 paper/manuscript.tex
@@
 This pattern of results is consistent with the pattern of results found in RP:P (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}).
+
+Some multi-site replication projects have found heterogeneity in effect sizes across replication sites (\protect\hyperlink{ref-klein2018}{Klein et al.
+2018}, \protect\hyperlink{ref-ebersole2020}{Ebersole et al.
+2020}, \protect\hyperlink{ref-olsson2020}{Olsson-Collentine et al.
+2020}).
+We calculated how often the original and replication results were distributionally consistent.
+If we assume that the level of heterogeneity in hypothetical multi-site replications of these effects would be the same as the average level heterogeneity found in Olsson-Collentine et al.
+(\protect\hyperlink{ref-olsson2020}{2020}) (tau=.21 in SMD units), then 64.3\% (72/112) of replications are distributionally consistent with the original.
+More work on understanding heterogeneity is needed to understand what levels of heterogeneity to expect across different implementations of the same experiment, and how considerations of heterogeneity should impact interpretations of both novel results and replications.
+
+{[}what was I supposed to say about heterogeneity, and is this the right place for it?{]}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-olsson2020}{}}%
+Olsson-Collentine A, Assen MA van, Wicherts J (2020) Heterogeneity in direct replications in psychology and its association with effect size.
+
 \leavevmode\vadjust pre{\hypertarget{ref-openscienceconsortium2015}{}}%
-Open Science Consortium (2015) Estimating the reproducibility of psychological science. \emph{Science}
+Open Science Consortium (2015) \href{https://www.science.org/doi/full/10.1126/science.aac4716?casa_token=IJ35TwwlcjsAAAAA\%3AqiP68QbVAHleIg9zD3WugKWuV6Oa5rswS0VQnDsCq5I14ME4WIQabNGVD_T6SBSuAt6voVHNnWc0sw}{Estimating the reproducibility of psychological science}.
+\emph{Science}
 

### 2023-07-03 paper/supplement.Rmd
more tau and citation tweaks

@@
 
-```{r, include=F, echo=F}
-d |> select(starts_with("pred") | starts_with("p_orig"))
+```{r, echo=F}
 
-d |> filter(!is.na(predInt)) |> count(predInt)
-#using predInt as reported 62 in interval, 72 not (45% rep)
+d |> filter(include %in% c("stats", "pred_int")) |> filter(!is.na(predInt)) |> count(predInt)
 
 #of those with SMD predInts
-d |> filter(!is.na(predInt_from_d)) |> count(predInt)
-# using predInt 44 in / 70 out (38%)
-d |> filter(!is.na(predInt_from_d)) |> count(predInt_from_d)
-# 34 in /80 out (30%)
-d |> filter(!is.na(predInt_from_d)) |> count(predInt_with_tau)
-# with tau 73 in / 41 out (64%)
+d |>filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> count(predInt)
+d |> filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> count(predInt_from_d)
+d |> filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> count(predInt_with_tau)
 
-d |> filter(!is.na(predInt)) |> summarise(median(p_orig))
+d |> filter(include %in% c("stats", "pred_int")) |> filter(!is.na(predInt)) |> summarise(median(p_orig))
 #median .03
@@
 #of those with SMD predInts
-d |> filter(!is.na(predInt_from_d)) |>summarise(median(p_orig))
-# median .01
-d |> filter(!is.na(predInt_from_d)) |> summarise(median(p_orig_from_d))
-# median .001
-d |> filter(!is.na(predInt_from_d)) |> summarise(median(p_orig_with_tau))
-# median .15
+d |> filter(include=="stats") |> filter(!is.na(predInt_from_d)) |>summarise(median(p_orig))
+d |> filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> summarise(median(p_orig_from_d))
+d |> filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> summarise(median(p_orig_with_tau))
 ```

### 2023-07-05 paper/manuscript.Rmd
work

@@
 When scientists treat publication as a signal of truth and attempt to build on results without verifying them first, they can become frustrated pursuing extensions to a popular, but unreliable result.
-As each failed extension does not directly contradict the original result, many scientists may waste a lot of time and resources pursuing results where there may be none.
+As each failed extension does not directly contradict the original result, many scientists may waste considerable time and resources pursuing results where there may be none.
 
-To identify studies are risk for non-cumulative findings, we might want to know 1) what to measure in order to capture the waste and frustration due to non-cumulative failed extensions and 2) from a descriptive perspective, what features of studies are associated with being at risk for this non-replicability.
-Such measurements have been the focus of much prior work around replicability, but there is limited consensus on what is being estimated.
-
- [Prior paragraph may still need work]
+To identify studies at risk for non-cumulative findings, we might want to know 1) what to measure in order to capture the waste and frustration due to non-cumulative failed extensions and 2) from a descriptive perspective, what features of studies are associated with being at risk for this non-replicability.
+Measuring replicability has been the focus of much prior work, but there is limited consensus on what exactly is being estimated.
 
@@
 Sampling truly at random from the literature may not even be desirable, as arguably a literature will succeed if useful discoveries come out of it, not if random findings are true [@wilson2020].
-The importance of a study being replicable is not uniformly distributed across the literature.
 
-[Prior paragraph is a bit verbose, but it's probably fine]
-
-Rather than aim for some measure of "true" replicability, it makes more sense to contextualize replication efforts based on their methods and outcome measures.
+Rather than aim for some measure of "true" replicability, it makes more sense to contextualize replication efforts based on their methodologies and outcome measures.
 With this lens, we could say that RP:P looked at how well findings in well-known journals can be replicated in a typical psychology lab.
-Many Labs looked at which well-known two conditions studies replicate with huge samples, and @camerer2018 looked at which prestigious journal findings replicate when conducted in a highly-resourced environment with expert involvement.
+Many Labs looked at which well-known two condition studies replicate with huge samples, and @camerer2018 looked at which prestigious journal findings replicate when conducted in a highly-resourced environment with expert involvement.
 All of these are potentially desirable estimands depending on what the specific circumstances and questions of interest are.
@@
 
+In practice, most scientific work is not conducted 
 Our goal in estimating replicability is to look for markers of when findings can (and cannot) support cumulative science.

### 2023-07-05 paper/supplement.Rmd
work

@@
 
+\pagebreak
+
 # Forest plot
@@
 
+\pagebreak
+
 # Additional model results
@@
 
-tier1_subjective <- read_rds(here(model_location, "tier1_subjective.rds")) |> do_draws() |> mutate(type="Without stats predictors") |> mutate(sens="All data")
-tier2_porig <- read_rds(here(model_location, "tier2_porig.rds"))|> do_draws() |>  mutate(type="Without stats predictors") |> mutate(sens="All data")
-tier2_predint <- read_rds(here(model_location, "tier2_predint.rds"))|> do_draws() |>  mutate(type="Without stats predictors") |> mutate(sens="All data")
-tier3_subjective <- read_rds(here(model_location, "tier3_subjective.rds"))|> do_draws() |> mutate(type="Stats predictors") |> mutate(sens="All data")
-tier3_porig <- read_rds(here(model_location, "tier3_porig.rds"))|> do_draws() |>  mutate(type="Stats predictors") |> mutate(sens="All data")
-tier3_predint <- read_rds(here(model_location, "tier3_predint.rds"))|> do_draws() |>  mutate(type="Stats predictors") |> mutate(sens="All data")
+tier1_subjective <- read_rds(here(model_location, "tier1_subjective.rds")) |> do_draws() |> mutate(type="All original-replication pairs") |> mutate(sens="All data")
+tier2_porig <- read_rds(here(model_location, "tier2_porig.rds"))|> do_draws() |>  mutate(type="All original-replication pairs") |> mutate(sens="All data")
+tier2_predint <- read_rds(here(model_location, "tier2_predint.rds"))|> do_draws() |>  mutate(type="All original-replication pairs") |> mutate(sens="All data")
+tier3_subjective <- read_rds(here(model_location, "tier3_subjective.rds"))|> do_draws() |> mutate(type="Only pairs with full statistical info") |> mutate(sens="All data")
+tier3_porig <- read_rds(here(model_location, "tier3_porig.rds"))|> do_draws() |>  mutate(type="Only pairs with full statistical info") |> mutate(sens="All data")
+tier3_predint <- read_rds(here(model_location, "tier3_predint.rds"))|> do_draws() |>  mutate(type="Only pairs with full statistical info") |> mutate(sens="All data")
 
-sens1_subjective <- read_rds(here(model_location, "sens_tier1_subjective.rds"))|> do_draws() |> mutate(type="Without stats predictors") |> mutate(sens="Sensitivity test")
-sens2_porig <- read_rds(here(model_location, "sens_tier2_porig.rds"))|> do_draws() |> mutate(type="Without stats predictors")|> mutate(sens="Sensitivity test")
-sens2_predint <- read_rds(here(model_location, "sens_tier2_predint.rds"))|> do_draws() |> mutate(type="Without stats predictors")|> mutate(sens="Sensitivity test")
-sens3_subjective <- read_rds(here(model_location, "sens_tier3_subjective.rds"))|> do_draws()|> mutate(type="Stats predictors")|> mutate(sens="Sensitivity test")
-sens3_porig <- read_rds(here(model_location, "sens_tier3_porig.rds"))|> do_draws()|> mutate(type="Stats predictors")|> mutate(sens="Sensitivity test")
-sens3_predint <- read_rds(here(model_location, "sens_tier3_predint.rds"))|> do_draws()|> mutate(type="Stats predictors")|> mutate(sens="Sensitivity test")
+sens1_subjective <- read_rds(here(model_location, "sens_tier1_subjective.rds"))|> do_draws() |> mutate(type="All original-replication pairs") |> mutate(sens="Sensitivity test")
+sens2_porig <- read_rds(here(model_location, "sens_tier2_porig.rds"))|> do_draws() |> mutate(type="All original-replication pairs")|> mutate(sens="Sensitivity test")
+sens2_predint <- read_rds(here(model_location, "sens_tier2_predint.rds"))|> do_draws() |> mutate(type="All original-replication pairs")|> mutate(sens="Sensitivity test")
+sens3_subjective <- read_rds(here(model_location, "sens_tier3_subjective.rds"))|> do_draws()|> mutate(type="Only pairs with full statistical info")|> mutate(sens="Sensitivity test")
+sens3_porig <- read_rds(here(model_location, "sens_tier3_porig.rds"))|> do_draws()|> mutate(type="Only pairs with full statistical info")|> mutate(sens="Sensitivity test")
+sens3_predint <- read_rds(here(model_location, "sens_tier3_predint.rds"))|> do_draws()|> mutate(type="Only pairs with full statistical info")|> mutate(sens="Sensitivity test")
 
@@
 
-# tau**2  sensitivity analysis is a mess
+\pagebreak
+
+# Heterogeneity analysis
 
@@
 
-d |> filter(include %in% c("stats", "pred_int")) |> filter(!is.na(predInt)) |> count(predInt)
+all_true <- d |> filter(include %in% c("stats", "pred_int")) |> filter(!is.na(predInt)) |> filter(predInt) |> nrow()
+
+all <- d |> filter(include %in% c("stats", "pred_int")) |> filter(!is.na(predInt)) |> nrow()
 
 #of those with SMD predInts
-d |>filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> count(predInt)
-d |> filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> count(predInt_from_d)
-d |> filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> count(predInt_with_tau)
+all_orig  <- d |>filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> nrow()
+all_orig_true <- d |>filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> filter(predInt) |> nrow()
+all_d_true <- d |> filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> filter(predInt_from_d) |> nrow()
+all_tau <- d |> filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> filter(predInt_with_tau) |> nrow()
 
-d |> filter(include %in% c("stats", "pred_int")) |> filter(!is.na(predInt)) |> summarise(median(p_orig))
-#median .03
+```
 
-#of those with SMD predInts
-d |> filter(include=="stats") |> filter(!is.na(predInt_from_d)) |>summarise(median(p_orig))
-d |> filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> summarise(median(p_orig_from_d))
-d |> filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> summarise(median(p_orig_with_tau))
-```
+The prediction interval and p-original values used for models and point estimates were done on the original scale where possible.
+However, to do heterogeneity analysis, our imputed value for tau is in SMD units, so we have to use SMD units for the original and replication values.
+This limits the number of applicable original-replication pairs.
+Prediction intervals are sensitive to whether only studies with SMD are included (different studies report differently and also vary in how close replications were) and whether the scale used was original or SMD (if the variances differed between original and replication).
+
+Of all studies where prediction intervals can be calculated, `r all_true`/`r all` (`r round(all_true/all*100)`%) of the original estimates had prediction intervals that included the replication effect size.
+For those where we have SMD, `r all_orig_true`/`r all_orig` (`r round(all_orig_true/all_orig*100)`%) of the original estimates had prediction intervals that included the replication effect size, when we use original units where possible.
+Using SMD units, `r all_d_true`/`r all_orig` (`r round(all_d_true/all_orig*100)`%) of the original estimates had prediction intervals that included the replication effect size.
+Allowing for heterogeneity, with tau=.21, `r all_tau`/`r all_orig` (`r round(all_tau/all_orig*100)`%) of the original estimates are distributionally consistent.

### 2023-07-05 paper/manuscript.Rmd
small text fixes

@@
 
+## Large-scale replication projects
+
 A few large-scale investigations have measured replication rates in samples of psychology studies.
@@
 
-[TODO This is good but could use more build-up.
-Something like.
-In practice, most scientific work is not conducted under such ideal conditions.
-Studies are generally run by graduate students with limited budgets ...
-.
-Therefore, an important question to ask is how replicable findings in the literature are for graduate students operating under less-than-ideal conditions.]
+In practice, most scientific work is conducted by graduate students with limited time, limited budgets and limited access to experts.
+Therefore, an important question is how replicable findings in the literature are for graduate students operating under these less-than-ideal conditions.
+If students cannot replicate a finding under these circumstances, it is unlikely that they will be able to successfully build upon the study in these circumstances either.
 
-In practice, most scientific work is not conducted 
-Our goal in estimating replicability is to look for markers of when findings can (and cannot) support cumulative science.
-If a study cannot be replicated in a given set of circumstances, we believe it it unlikely that the study can be successfully built upon in those circumstances either.
-Thus, we look at what studies are replicable under the circumstances where most scientific work is conducted: by students who are working with limited budgets, limited time, and without access to outside experts [@frank2012].
+Our goal in estimating replicability is to look for markers of when findings can (and cannot) support cumulative science, by looking for markers of findings that do (or do not) support replication by graduate students operating under typical real-word constraints.
+Our sample of studies is selected based on what studies students were interested in and wanting to replicate, with some filtering for feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable given methodological and budgetary constraints.
 Our primary estimand is whether a student researcher, on selecting a finding of interest from the literature, can successfully achieve a result close enough to the original that they could build on it in their own work.
-
-Our replication approach reflects this estimand.
-Our sample of studies is selected based on what studies students were interested in and wanting to replicate, with some filtering for feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable given methodological and budgetary constraints.
 In addition to this subjective measure of replicability, we also compare the effect sizes of the original and replication on one key outcome per study using prediction interval and p-original [@mathur2020].
 
-[TODO possibly say more??]
+## Predicting replication success
 
@@
 
-[TODO is there a citation for experimental design features being possibly relevant?]
-
 While most approaches to correlates of replicability have been correlational, experimental approaches can be used to test potential interventions.
@@
 
-[Awkward transition]
-
-However, while they don't incur the expense of collecting new datasets, correlational approaches depend on data from replications.
-As large-scale replications are arduous and expensive to run, analyses generally draw heavily on same small set of data points.
-In particular, the RP:P dataset itself is much discussed and reanalyzed [@etz2016;@gilbert2016;@patil2016;@anderson2016] to the point that much of what we think we know about replicability may be overfit to the 100 studies included in in RP:P.
+While they don't incur the expense of collecting new datasets, correlational approaches do depend on previously collected replication data, and their conclusions are limited by the available data.
+Large-scale replications are arduous and expensive to run, so only a few large-scale replication datasets exist, and most analyses analyses draw heavily on same small set of data points.
+In particular, the RP:P dataset is much discussed and reanalyzed [@etz2016;@gilbert2016;@patil2016;@anderson2016] to the point that much of what we think we know about replicability may be overfit to the 100 studies included in RP:P.
 More replication data is needed to identify markers of replicability and targets for potential future experimental approaches.
@@
 Some multi-site replication projects have found heterogeneity in effect sizes across replication sites [@ebersole2020; @klein2018; @olsson2020].
-We calculated how often the original and replication results were distributionally consistent.
-If we assume that the level of heterogeneity in hypothetical multi-site replications of these effects would be the same as the average level heterogeneity found in @olsson2020 (tau=.21 in SMD units), then `r round(tau_pct,1)`% (`r tau_predIntcount`/`r tau_predInttotal`) of replications are distributionally consistent with the original.
-More work on understanding heterogeneity is needed to understand what levels of heterogeneity to expect across different implementations of the same experiment, and how considerations of heterogeneity should impact interpretations of both novel results and replications.
+If we assume that the level of heterogeneity in hypothetical multi-site replications of these effects would be the same as the average level heterogeneity found in @olsson2020 (tau=.21 in SMD units), then `r round(tau_pct,1)`% (`r tau_predIntcount`/`r tau_predInttotal`) of replication effect sizes are distributionally consistent with the original effect size.
+More work on understanding heterogeneity is needed to understand what levels of heterogeneity to expect across different implementations of the same experiment, and how considerations of heterogeneity should impact interpretations of both novel results and replication results.
 
-[what was I supposed to say about heterogeneity, and is this the right place for it?]
+[Is this the right place to talk about heterogeneity / what did we want to say?]
 
@@
 
-TODO any citations around experimental design predictors??
-
 Many predictors individually correlated with subjective replication success (Table \ref{tab:cor}).
 Predictors of higher replicability included within-subjects designs, larger numbers of trials per subject, and the original study having open data.
-Predictors of lower replicability included single vignetted studies with only one induction or example per condition, social psychology studies, and original-replication pairs where the original study was in-person and replication switched to online.
+Predictors of lower replicability included single vignetted studies with only one induction or example per condition, social psychology studies, and original-replication pairs where the original study was in-person and the replication switched to online.
 
@@
 The coefficient estimates from two models predicting the subjective replication scores are shown in Figure \ref{fig:mod-results}; see Supplement for full model results.
-Due to a large number of predictors coupled with a small and noisy dataset there is much uncertainty around the coefficients even with strong regularization.
+Due to a large number of predictors coupled with a small and noisy dataset, there is much uncertainty around the coefficients even with strong regularization.
 The general directions of coefficients are consistent with the effects of the predictors in isolation.
@@
 Both these models had even more uncertain estimates.
-While the credible intervals were wide, the general patterns of predictor direction and relative strength were similar to the subjective replication models.
+While the credible intervals were wide, the general patterns of predictor direction and relative strength were similar to the subjective replication models (See Supplement for plots of coefficients for these additional models).
 The strongest predictors for prediction interval were still within-subjects designs (`r within_2`) and studies with larger effect sizes (`r smd_2`).
 
-```{r mod-results, out.width="90%", fig.width=8, fig.height=5, fig.pos="ht", fig.cap="Coefficients and uncertaintly estimates from a model of all original-replication pairs (N=176, shown in red) and a model of all pairs with full statistical information (N=112, shown in blue) and predicting subjective replication scores as the dependent variable.
+```{r mod-results, out.width="90%", fig.width=8, fig.height=5, fig.pos="ht", fig.cap="Coefficients and uncertaintly estimates from a model of all original-replication pairs (N=176, shown in blue) and a model of all pairs with full statistical information (N=112, shown in red) and predicting subjective replication scores as the dependent variable.
 "}
@@
 Given the predictive value, slightly more skepticism and critical reading of between-subjects designs may be warranted, but this correlation, by itself, does not mean scientists should prefer to run within-subjects designs.
-
-[TODO should we discuss the need for more replications and pooling and coding??]
 

### 2023-07-05 paper/manuscript.tex
small text fixes

@@
 When scientists treat publication as a signal of truth and attempt to build on results without verifying them first, they can become frustrated pursuing extensions to a popular, but unreliable result.
-As each failed extension does not directly contradict the original result, many scientists may waste a lot of time and resources pursuing results where there may be none.
+As each failed extension does not directly contradict the original result, many scientists may waste considerable time and resources pursuing results where there may be none.
 
-To identify studies are risk for non-cumulative findings, we might want to know 1) what to measure in order to capture the waste and frustration due to non-cumulative failed extensions and 2) from a descriptive perspective, what features of studies are associated with being at risk for this non-replicability.
-Such measurements have been the focus of much prior work around replicability, but there is limited consensus on what is being estimated.
+To identify studies at risk for non-cumulative findings, we might want to know 1) what to measure in order to capture the waste and frustration due to non-cumulative failed extensions and 2) from a descriptive perspective, what features of studies are associated with being at risk for this non-replicability.
+Measuring replicability has been the focus of much prior work, but there is limited consensus on what exactly is being estimated.
 
-{[}Prior paragraph may still need work{]}
+\hypertarget{large-scale-replication-projects}{%
+\subsection{Large-scale replication projects}\label{large-scale-replication-projects}}
 
@@
 2020}).
-The importance of a study being replicable is not uniformly distributed across the literature.
 
-{[}Prior paragraph is a bit verbose, but it's probably fine{]}
-
-Rather than aim for some measure of ``true'' replicability, it makes more sense to contextualize replication efforts based on their methods and outcome measures.
+Rather than aim for some measure of ``true'' replicability, it makes more sense to contextualize replication efforts based on their methodologies and outcome measures.
 With this lens, we could say that RP:P looked at how well findings in well-known journals can be replicated in a typical psychology lab.
-Many Labs looked at which well-known two conditions studies replicate with huge samples, and Camerer et al.
+Many Labs looked at which well-known two condition studies replicate with huge samples, and Camerer et al.
 (\protect\hyperlink{ref-camerer2018}{2018}) looked at which prestigious journal findings replicate when conducted in a highly-resourced environment with expert involvement.
@@
 
-{[}TODO This is good but could use more build-up.
-Something like.
-In practice, most scientific work is not conducted under such ideal conditions.
-Studies are generally run by graduate students with limited budgets \ldots{} .
-Therefore, an important question to ask is how replicable findings in the literature are for graduate students operating under less-than-ideal conditions.{]}
+In practice, most scientific work is conducted by graduate students with limited time, limited budgets and limited access to experts.
+Therefore, an important question is how replicable findings in the literature are for graduate students operating under these less-than-ideal conditions.
+If students cannot replicate a finding under these circumstances, it is unlikely that they will be able to successfully build upon the study in these circumstances either.
 
-Our goal in estimating replicability is to look for markers of when findings can (and cannot) support cumulative science.
-If a study cannot be replicated in a given set of circumstances, we believe it it unlikely that the study can be successfully built upon in those circumstances either.
-Thus, we look at what studies are replicable under the circumstances where most scientific work is conducted: by students who are working with limited budgets, limited time, and without access to outside experts (\protect\hyperlink{ref-frank2012}{Frank \& Saxe 2012}).
+Our goal in estimating replicability is to look for markers of when findings can (and cannot) support cumulative science, by looking for markers of findings that do (or do not) support replication by graduate students operating under typical real-word constraints.
+Our sample of studies is selected based on what studies students were interested in and wanting to replicate, with some filtering for feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable given methodological and budgetary constraints.
 Our primary estimand is whether a student researcher, on selecting a finding of interest from the literature, can successfully achieve a result close enough to the original that they could build on it in their own work.
-
-Our replication approach reflects this estimand.
-Our sample of studies is selected based on what studies students were interested in and wanting to replicate, with some filtering for feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable given methodological and budgetary constraints.
 In addition to this subjective measure of replicability, we also compare the effect sizes of the original and replication on one key outcome per study using prediction interval and p-original (\protect\hyperlink{ref-mathur2020}{Mathur \& VanderWeele 2020}).
 
-{[}TODO possibly say more??{]}
+\hypertarget{predicting-replication-success}{%
+\subsection{Predicting replication success}\label{predicting-replication-success}}
 
@@
 
-{[}TODO is there a citation for experimental design features being possibly relevant?{]}
-
 While most approaches to correlates of replicability have been correlational, experimental approaches can be used to test potential interventions.
@@
 
-{[}Awkward transition{]}
-
-However, while they don't incur the expense of collecting new datasets, correlational approaches depend on data from replications.
-As large-scale replications are arduous and expensive to run, analyses generally draw heavily on same small set of data points.
-In particular, the RP:P dataset itself is much discussed and reanalyzed (\protect\hyperlink{ref-anderson2016}{Anderson et al.
+While they don't incur the expense of collecting new datasets, correlational approaches do depend on previously collected replication data, and their conclusions are limited by the available data.
+Large-scale replications are arduous and expensive to run, so only a few large-scale replication datasets exist, and most analyses analyses draw heavily on same small set of data points.
+In particular, the RP:P dataset is much discussed and reanalyzed (\protect\hyperlink{ref-anderson2016}{Anderson et al.
 2016}, \protect\hyperlink{ref-etz2016}{Etz \& Vandekerckhove 2016}, \protect\hyperlink{ref-gilbert2016}{Gilbert et al.
 2016}, \protect\hyperlink{ref-patil2016}{Patil et al.
-2016}) to the point that much of what we think we know about replicability may be overfit to the 100 studies included in in RP:P.
+2016}) to the point that much of what we think we know about replicability may be overfit to the 100 studies included in RP:P.
 More replication data is needed to identify markers of replicability and targets for potential future experimental approaches.
@@
 2020}).
-We calculated how often the original and replication results were distributionally consistent.
 If we assume that the level of heterogeneity in hypothetical multi-site replications of these effects would be the same as the average level heterogeneity found in Olsson-Collentine et al.
-(\protect\hyperlink{ref-olsson2020}{2020}) (tau=.21 in SMD units), then 64.3\% (72/112) of replications are distributionally consistent with the original.
-More work on understanding heterogeneity is needed to understand what levels of heterogeneity to expect across different implementations of the same experiment, and how considerations of heterogeneity should impact interpretations of both novel results and replications.
+(\protect\hyperlink{ref-olsson2020}{2020}) (tau=.21 in SMD units), then 64.3\% (72/112) of replication effect sizes are distributionally consistent with the original effect size.
+More work on understanding heterogeneity is needed to understand what levels of heterogeneity to expect across different implementations of the same experiment, and how considerations of heterogeneity should impact interpretations of both novel results and replication results.
 
-{[}what was I supposed to say about heterogeneity, and is this the right place for it?{]}
+{[}Is this the right place to talk about heterogeneity / what did we want to say?{]}
 
@@
 Both these models had even more uncertain estimates.
-While the credible intervals were wide, the general patterns of predictor direction and relative strength were similar to the subjective replication models.
+While the credible intervals were wide, the general patterns of predictor direction and relative strength were similar to the subjective replication models (See Supplement for plots of coefficients for these additional models).
 The strongest predictors for prediction interval were still within-subjects designs (0.62, CrI= {[}-0.18, 2.01{]}) and studies with larger effect sizes (0.3, CrI= {[}-0.29, 0.94{]}).
@@
 \begin{figure}[ht]
-\includegraphics[width=0.9\linewidth]{manuscript_files/figure-latex/mod-results-1} \caption{Coefficients and uncertaintly estimates from a model of all original-replication pairs (N=176, shown in red) and a model of all pairs with full statistical information (N=112, shown in blue) and predicting subjective replication scores as the dependent variable.
+\includegraphics[width=0.9\linewidth]{manuscript_files/figure-latex/mod-results-1} \caption{Coefficients and uncertaintly estimates from a model of all original-replication pairs (N=176, shown in blue) and a model of all pairs with full statistical information (N=112, shown in red) and predicting subjective replication scores as the dependent variable.
 }\label{fig:mod-results}
@@
 Given the predictive value, slightly more skepticism and critical reading of between-subjects designs may be warranted, but this correlation, by itself, does not mean scientists should prefer to run within-subjects designs.
-
-{[}TODO should we discuss the need for more replications and pooling and coding??{]}
 

### 2023-07-05 paper/supplement.Rmd
small text fixes

@@
 
-\pagebreak
-
-# Forest plot
-
 ```{r forest, out.height="100%", fig.width=9, fig.height=12, fig.pos="ht", fig.cap="Forest plot of original and replication effect sizes.
@@
 
-# Additional model results
 ```{r}

### 2023-07-08 paper/manuscript.Rmd
mike pass

@@
 
-Cumulative scientific progress requires empirical results that are robust enough to support theory construction and future extensions.
-Yet in psychology, some prominent findings have failed to replicate, and large-scale investigations suggest that failures to replicate are widespread.
-The identification of features that predict replication success is limited by data, and most analyses re-analyse the same set of ~170 replications.
+Cumulative scientific progress requires empirical results that are robust enough to support theory construction and extension.
+Yet in psychology, some prominent findings have failed to replicate, and large-scale studies suggest replicability issues are widespread.
+The identification of predictors of replication success is limited by the difficulty of conducting large samples of indepedendent replication experiments, however: most investigations re-analyse the same set of ~170 replications.
 We introduce a new dataset of 176 replications from students in a graduate-level methods course.
-Replication results were close enough to original results to support student extensions in 49% of replications.
-45% of replications with suitable numerical outcomes (N=136) had point estimates within the prediction interval of the original outcome.
-Larger original effect sizes and within-participants designs were predictive of replication.
-Consistent with prior reports, our results indicate that the robustness of the psychology literature is low enough to limit progress by student investigators.
-
-[148 words / NHB max 150] 
+Replication results were judged to be successful in 49% of replications; of the 136 where comparable effect sizes could be computed, 45% had point estimates within the prediction interval of the original outcome.
+Larger original effect sizes and within-participants designs were especially related to replication success.
+Or results indicate that, consistent with prior reports, the robustness of the psychology literature is low enough to limit cumulative progress by student investigators.
 :::
@@
 
- Cumulative scientific progress requires empirical results that are robust enough to support theory construction and future extensions.
+Cumulative scientific progress requires empirical results that are robust enough to support both future empirical extensions and the construction of synthetic theories.
 Yet in psychology, some prominent individual findings have failed to replicate in multi-site replication attempts [ex.
-terror management theory, @klein2022; ego-depletion, @hagger2016], and a large-scale replication project pegged the replication rate for findings in top-tier psychology journals at around 40% [@openscienceconsortium2015].
-When scientists treat publication as a signal of truth and attempt to build on results without verifying them first, they can become frustrated pursuing extensions to a popular, but unreliable result.
-As each failed extension does not directly contradict the original result, many scientists may waste considerable time and resources pursuing results where there may be none.
+terror management theory, @klein2022; ego-depletion, @hagger2016].
+One early large-scale replication project pegged the replication rate for findings in top-tier psychology journals at around 40% [RP:P; @openscienceconsortium2015].
+Low replicability has negative consequences for the field as a whole: when scientists attempt to build on published results, they stand a good chance of meeting with failure.
 
-To identify studies at risk for non-cumulative findings, we might want to know 1) what to measure in order to capture the waste and frustration due to non-cumulative failed extensions and 2) from a descriptive perspective, what features of studies are associated with being at risk for this non-replicability.
-Measuring replicability has been the focus of much prior work, but there is limited consensus on what exactly is being estimated.
+<!-- et interpreting the results of replication studies is difficult:  As each failed extension does not directly contradict the original result, many scientists may waste considerable time and resources pursuing results where there may be none.
+-->
 
-## Large-scale replication projects
+Addressing this issue requires a better understanding of the scope of the problem as well as the methodological and structural issues that might lead to replication failure [@smaldino2016;@simmons20211].
+Estimating replicability in the literature is a key starting point, but, as we review below, there is limited consensus on what quantity exactly should be estimated.
+
+Our viewpoint here is that one important estimand is the probability that a graduate student can identify a finding in the literature and replicate it successfully enough that they can build on that finding in subsequent work.
+Taking this perspective, our contribution is a new dataset of 176 replications of experimental studies from the social sciences, primarily psychology.
+These replications were conducted as individual course projects by students in a graduate-level experimental methods class between 2011 and 2022.
+We then use this dataset to investigate statistical and experimental design predictors of replicability.
+
+## What are we estimating when we measure replicability?
 
 A few large-scale investigations have measured replication rates in samples of psychology studies.
-Reproducibility Project: Psychology sampled roughly 100 studies from articles published in three top psychology journals in 2008 and distributed the studies across participating labs.
-They found an overall replication rate of around 40% [@openscienceconsortium2015].
-Many Labs investigated heterogeneity using short target studies that compared between two conditions each.
-These study designs were not representative of the psychology literature as a whole, and due to the heterogeneity goal, they had large overall samples across multiple sites.
-Across Many Labs 1-3, in these high-powered replications, only 29 of 51 target effects (57%) replicated [@klein2014; @klein2018; @ebersole2016].
-@camerer2018 included all 21 behavioral social science studies from Nature and Science from 2010-2015 that were feasible; they consulted original authors and had high power to detect effects smaller than those reported.
-In this well-resourced environment with expert input, the replication rate was around 60%.
+The first of these, RP:P, sampled roughly 100 studies from articles published in three top psychology journals in 2008 and distributed the studies across participating labs, finding an overall replication rate of around 40% [@openscienceconsortium2015].
+The followup Many Labs Studies investigated heterogeneity using short target studies that each compared two conditions.
+These study designs were not representative of the psychology literature as a whole, and due to the of measuring heterogeneity, they had large overall samples across multiple sites.
+Across Many Labs 1--3, only 29 of 51 target effects (57%) replicated [@klein2014; @klein2018; @ebersole2016].
+@camerer2018 included all 21 behavioral social science studies from Nature and Science from 2010-2015 that were feasible to replicate.
+They consulted original authors and had high power to detect even small effects; under these conditions and with this sample, the replication rate was around 60%.
 
-While their sampling and methods varied, these previous approaches to replicability have focused on interpreting their results in terms of a potentially problematic estimand: the probability of a finding in the literature being somehow truly replicable.
-Critics have pointed out that "true" replicability may not be possible to estimate outside of a specific sample [@vanbavel2016] or even time period [@ramscar].
-Further, the methods for estimating this quantity have been theoretically problematic.
-Sampling schemes did not reflect an entirely random sample from the literature; instead replication projects sampled from specific journals where results may be of more interest and adjusted the sample for feasibility concerns.
-These are reasonable sampling choices, but they undermine the claim that the estimand is the level of "truth" in the literature as a whole.
-Sampling truly at random from the literature may not even be desirable, as arguably a literature will succeed if useful discoveries come out of it, not if random findings are true [@wilson2020].
+While their sampling procedure and methods varied, these previous approaches to replicability have all focused on interpreting their results in terms of a potentially problematic estimand: the probability of a finding in the literature being truly replicable.
+Critics have pointed out that "true" replicability may not be possible to estimate outside of a specific sample [@vanbavel2016] or even time period [@ramscar2015].
 
-Rather than aim for some measure of "true" replicability, it makes more sense to contextualize replication efforts based on their methodologies and outcome measures.
-With this lens, we could say that RP:P looked at how well findings in well-known journals can be replicated in a typical psychology lab.
-Many Labs looked at which well-known two condition studies replicate with huge samples, and @camerer2018 looked at which prestigious journal findings replicate when conducted in a highly-resourced environment with expert involvement.
-All of these are potentially desirable estimands depending on what the specific circumstances and questions of interest are.
+Further, the methods used in these studies are not sufficient to yield an unbiased estimate of this quantity.
+In no case were studies randomly sampled from the literature; instead replication projects sampled from specific journals and adjusted the sample for feasibility concerns.
+These reasonable decisions further undermine interpretation of the results from these studies as representing the proportion of true findings in the psychology literature as a whole.
+<!-- Sampling at random from the literature may not even be desirable, as arguably a literature will succeed if useful discoveries come out of it, not if random findings are true [@wilson2020].  -->
 
-In practice, most scientific work is conducted by graduate students with limited time, limited budgets and limited access to experts.
-Therefore, an important question is how replicable findings in the literature are for graduate students operating under these less-than-ideal conditions.
-If students cannot replicate a finding under these circumstances, it is unlikely that they will be able to successfully build upon the study in these circumstances either.
+Rather than aim for some measure of true replicability, perhaps we should contextualize the true estimand for replication efforts based on their methodologies and outcome measures.
+Through this lens, RP:P estimated the rate at which findings from relatively simple experiments published in a few well-known journals at a particular time could be replicated in a typical psychology lab.
+Many Labs estimated at which well-known, two-condition findings replicate in very large samples.
+@camerer2018 estimated which prestigious journal findings replicate when conducted in a highly-resourced environment with expert involvement.
+All of these could be potentially desirable estimands.
 
-Our goal in estimating replicability is to look for markers of when findings can (and cannot) support cumulative science, by looking for markers of findings that do (or do not) support replication by graduate students operating under typical real-word constraints.
-Our sample of studies is selected based on what studies students were interested in and wanting to replicate, with some filtering for feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable given methodological and budgetary constraints.
-Our primary estimand is whether a student researcher, on selecting a finding of interest from the literature, can successfully achieve a result close enough to the original that they could build on it in their own work.
+But in practice, most scientific work is conducted by graduate students with limited time, limited budgets and limited access to experts.
+If students cannot replicate a finding under these circumstances, they cannot build on it in their empirical or theoretical work.
+How replicable are findings in the literature for graduate students operating under these less-than-ideal conditions?
+We address this question here.
+
+Our current sample of replications is selected based on what experiments students were interested in and wanted to replicate, with some filtering for feasibility.
+This sampling is not at all random.
+It reflects how scientists generally choose which experiments to build on: those that are interesting and relatively feasible given methodological and budgetary constraints.
+
+In the current study, we estimate the probability of successful replication in this sample, with the goal of also identifying markers of when findings can (and cannot) support cumulative science.
+Our hope is to extend previous work that has attempted to find key correlates of replication success.
+
+<!-- Our primary estimand is whether a student researcher, on selecting a finding of interest from the literature, can successfully achieve a result close enough to the original that they could build on it in their own work.
 In addition to this subjective measure of replicability, we also compare the effect sizes of the original and replication on one key outcome per study using prediction interval and p-original [@mathur2020].
+-->
 
-## Predicting replication success
+## When do replications succeed?
 
-Despite variation in the methods and outcomes used by large-scale replication studies, they are often aggregated together in analyses looking at the predictablity of replication success.
+Despite variation in the methods and outcomes used by large-scale replication studies, they are often aggregated together in analyses looking at the predictability of replication success.
 Prediction markets and elicitations have established that people can predict what studies will replicate above chance [@hoogeveen2019;@dreber2015; @forsell2019;@camerer2018], but have not identified concrete predictors that differentiate replications from non-replications.
-Machine learning approaches trained on the available replications are also above chance at predicting replication success [@yang2020; @youyou2023].
-In terms of specific attributes that predict replicability, @altmejd2019 examined statistical and demographic features of studies and identified larger sample sizes, larger effect sizes, and simple effects (as opposed to interaction terms) as predictive of replication, and @openscienceconsortium2015 looked at correlates of replicability in the RP:P sample and found that studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate.
-One potential set of correlates to replicability that has not been thoroughly examined are experimental design features, such as between or within subjects designs and repeated measures.
+Machine learning approaches trained on the available replications are also above chance at predicting replication success [@yang2020; @youyou2023], though again the precise features relating to success are unclear.
 
-While most approaches to correlates of replicability have been correlational, experimental approaches can be used to test potential interventions.
-@protzko2020 showed, across 16 studies, that better methodological practices led to replication rates that matched theoretical expectations with replication effect sizes comparable with the original.
-Many Labs 5 added expert (original author) advice to a replication process, and found that it did not substantially increase the replication rate for the 10 studies [@ebersole2020].
-These types of experiments are valuable for testing potential causes of non-replication, but they don't scale well due to expense, and not all influences on non-replication may be experimentally manipulable.
+In search of such features, RP:P examined correlates of replicability in the RP:P sample and found that studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate.
+Using these same data combined with a few other smaller samples, @altmejd2019 examined statistical and demographic features of replication studies and identified larger sample sizes, larger effect sizes, and simple effects (as opposed to interaction terms) as predictive of replication.^[While most approaches to correlates of replicability have been correlational, experimental approaches can be used to test potential interventions [@protzko2020;@ebersole2020].
+Experiments can be very valuable as tests of specific causes of non-replication, but they are expensive and time-consuming to conduct, and not all factors affecting replication success can be manipulated experimentally.]
+<!-- showed, across 16 studies, that better methodological practices led to replication rates that matched theoretical expectations based on sampling error, with replication effect sizes comparable with the original.
+Many Labs 5 added expert (original author) advice to a replication process, and found that it did not substantially increase the replication rate for the 10 studies -->
 
-While they don't incur the expense of collecting new datasets, correlational approaches do depend on previously collected replication data, and their conclusions are limited by the available data.
+These approaches are fundamentally limited by the available data.
 Large-scale replications are arduous and expensive to run, so only a few large-scale replication datasets exist, and most analyses analyses draw heavily on same small set of data points.
-In particular, the RP:P dataset is much discussed and reanalyzed [@etz2016;@gilbert2016;@patil2016;@anderson2016] to the point that much of what we think we know about replicability may be overfit to the 100 studies included in RP:P.
+In particular, the RP:P dataset is much discussed and reanalyzed [@etz2016;@gilbert2016;@patil2016;@anderson2016] -- to the point that much of what we think we know about replicability may be over-fit to the 100 studies included in RP:P.
 More replication data is needed to identify markers of replicability and targets for potential future experimental approaches.
 
-Our contribution is a new dataset of 176 replications of experimental studies from the social sciences, primarily psychology.
-These replications were conducted by students in a graduate-level experimental methods class between 2011 and 2022 as individual course projects.
-We investigate statistical and experimental-design predictors of replicability in this dataset and find that within-subjects designs and studies with large standardized effect sizes are positively correlated with replication success.
+Further, none of these studies focused on features of experimental design, such as within-subjects designs or the use of repeated measures.
+There has been speculation that both of these factors should be linked to increased replicability due to their role in enabling increased statistical precision.
+Within-subjects designs lead to more precise experimental estimates by allowing the estimation of correlated person-level variation across conditions; repeated measures allow for more precise estimation by averaging out measurement error.
+Both are often recommended by methodologists as part of good measurement practices, at least when they are feasible  [@rosenthal2008;@greenwald1976; @frank2023].
+
+In sum, our current study examines the overall rate of replicability as well as the statistical and design features that predict replicability in a new sample of student replications.
+
+<!-- This study thus provides an estimate of the probability of cumulative progress by a capable student when faced with the current literature and offers some descrptive insight into which  -->
 
@@
 
-PSYCH 251 is Stanford Psychology's graduate-level experimental methods class taught by MCF.
-During the 10 week class, each student replicated a published finding.
-They individually re-implemented the study, wrote analysis code, pre-registered their study, collected data using an online platform, and wrote up a structured replication report.
-Students were free to choose studies related to their research interests, with the default recommendation being an article from a recent year of Psychological Science.
-The resultant sample of studies is not a random sample from the literature but is representative of studies that are of interest to and doable by first year graduate students.
+PSYCH 251 is a graduate-level experimental methods class in experimental psychology taught at Stanford University.
+During the 10 week class, each student replicates a published finding.
+They individually re-implement the study, write analysis code, pre-register their study, collect data (typically using an online crowd-sourcing platform), and write a structured replication report.
+Students in the course are free to choose studies related to their research interests, with the default recommendation being an article from a recent year of Psychological Science.
+<!-- The resultant sample of studies is not a random sample from the literature but is representative of studies that are of interest to and doable by first year graduate students.  -->
 
-The sample of replicated studies reflects the variability of the literature, including studies from different subfields, with different experimental methods and statistical outcomes.
-We leveraged the naturally occurring variability in this sample of replications to examine how different demographic, experimental design, and statistical properties predict replication success.
+The sample of replicated studies reflects the variability of the literature, including studies from different subfields (and occasionally fields outside of psychology), with different experimental methods and statistical outcomes.
+We leveraged naturally occurring variability in this sample of replications to examine how different demographic, experimental design, and statistical properties predict replication success.
 
-Of note, these replications were all conducted on short time scales, with constrained budgets, that in some cases limited the number of participants who could be recruited below what the original study had or what power analyses suggested.
-In nearly all cases, replications were conducted online, with recruitment from Amazon Mechanical Turk (default 2011-2020) or Prolific (default 2021-2022).
+These replications were all conducted on short time scales, within a constrained class budget.
+In some cases the budget limited the number of participants who could be recruited, occasionally below what the original study included or what power analyses suggested.
+In nearly all cases, replications were conducted online, with recruitment from Amazon Mechanical Turk (the default from 2011 to 2020) or Prolific (the default from 2021 -- 2022).
 
 Many different measures can be used to define replication success of an individual statistical result [@simonsohn2015; @gelman2018; @mathur2020].
-However, whether one feels confident in the results of a study given a replication is not always dependent on only one outcome measure (ex.
-interaction term) and particularly not dependent on only one statistical comparison between the two studies (ex.
-replication is p<.05 same direction as original).
-As our primary outcome, we use a subjective replication score which, unlike statistical measures, accommodated studies with multiple important outcome measures that together defined the pattern of interest and was applicable across the diverse range of statistical measures and reporting practices present in the sample.
-Importantly, a holistic measure of replication success had already been coded for most projects when they were turned in at the end of the class.
+However, whether a replication should be considered successful is not always dependent on only one statistical comparison between the two studies.
+Often in original papers, multiple statistical tests are cited in support of the claim that a pattern of results matches a particular theoretical expectation.
+
+As our primary outcome, we  chose to use a subjective replication score (coded by two independent raters -- one typically at the time of project completion -- with discrepancies resolved by discussion).
+Unlike statistical measures, subjective replication success accommodates studies with multiple important outcome measures that together define the pattern of interest.
+Further, this measure was applicable across the diverse range of statistical measures and reporting practices present in the sample.
+<!-- Importantly, a holistic measure of replication success had already been coded for most projects when they were turned in at the end of the class.
 For reliability, VB independently code the replication success from the students' written reports; discrepancies were resolved by discussion between MCF and VB (inter-rater reliability, Spearman's $\rho$: `r round(irr,2)`, disagreement in `r round(pluck(matching,2,1)/176*100)`% of cases).
+-->
 
 As a complement to our primary subjective outcome, we also used two statistical measures of replication on the subset of the data where they were computable for the key statistic of interest (`r pluck(pred_int_avail,1)` cases, see Figure \ref{fig:prisma}).
-We used p-original, the p-value on the null hypothesis that the original and replication statistics are from the same distribution, and prediction interval, a binary measure of whether the replication statistic fell within the prediction interval of the original statistic [@mathur2020].
+We used *p-original*, the *p*-value on the null hypothesis that the original and replication statistics are from the same distribution, and *prediction interval*, a binary measure of whether the replication statistic fell within the prediction interval of the original statistic [@mathur2020].
 The prediction interval depends on the level of evidence of the original study; if the effect was marginal, the prediction interval could overlap zero; thus, a replication might fall within the predictive interval, and be consistent with the original outcome, but not provide compelling evidence for the claimed effect.
 Conversely, large original effects with precise point estimates may have prediction intervals that do not overlap a smaller replication effect size, and thus would be inconsistent with the original outcome, even though researcher intuition might classify it as a success.
-Thus, the statistical metrics quantify the similarity of a key statistic, but they will not always match researcher intuitions on whether a study replicated.
+Thus, these two statistical metrics each quantify the similarity between a key statistic in the original study and the replication, but they will not always match researcher intuitions on whether a study replicated.
 
@@
 `r round(pluck(pred_int_rate,1))`% (`r predIntcount`/`r predInttotal`) of replications has outcomes with point-estimates within the prediction interval of the original outcome.
-The median p_original value on the original and replication point-estimates coming from the same distribution was `r round(pluck(porig_rate, 1),2)`, representing the median probability that a replication study's estimate would be at least as extreme as was actually observed, if in fact the replication and original were statistically consistent.
+The median *p*-original value on the original and replication point-estimates coming from the same distribution was `r round(pluck(porig_rate, 1),2)`, representing the median probability that a replication study's estimate would be at least as extreme as was actually observed, if in fact the replication and original were statistically consistent.
+
 Figure \ref{fig:smd} shows the relationship between original standardized effect size, replication effect size, and subjective replication score.
@@
 On average, there was a diminution of effect sizes from original to replication.
-This pattern of results is consistent with the pattern of results found in RP:P [@openscienceconsortium2015].
+This pattern of results is consistent with the results of RP:P [@openscienceconsortium2015].
 
@@
 Some multi-site replication projects have found heterogeneity in effect sizes across replication sites [@ebersole2020; @klein2018; @olsson2020].
-If we assume that the level of heterogeneity in hypothetical multi-site replications of these effects would be the same as the average level heterogeneity found in @olsson2020 (tau=.21 in SMD units), then `r round(tau_pct,1)`% (`r tau_predIntcount`/`r tau_predInttotal`) of replication effect sizes are distributionally consistent with the original effect size.
-More work on understanding heterogeneity is needed to understand what levels of heterogeneity to expect across different implementations of the same experiment, and how considerations of heterogeneity should impact interpretations of both novel results and replication results.
+If we assume that the level of heterogeneity in hypothetical multi-site replications of these effects is the same as the average level heterogeneity found in prior multi-site replications in psychology [$\tau=.21$ in units of standardized mean difference; @olsson2020], then `r round(tau_pct,1)`% (`r tau_predIntcount`/`r tau_predInttotal`) of replication effect sizes are distributionally consistent with the original effect size.
+However, more work on understanding heterogeneity is needed to understand what levels of heterogeneity to expect across different implementations of the same experiment, and how considerations of heterogeneity should impact interpretations of both novel results and replication results.
 
-[Is this the right place to talk about heterogeneity / what did we want to say?]
+<!-- [Is this the right place to talk about heterogeneity / what did we want to say?]  -->
 
@@
 
-## Single predictors
+## Independent correlates of replication success
+
 We investigated what features of the original study and replication were correlated with replication success, with the goal of being able to identify potential markers of replicability.
-We chose a set of predictor variables based on the correlational results of RP:P [@openscienceconsortium2015], our own intuitions of experimental design factors that might impact replication success, and some covariates related to how close the replication was.
-A full description of these features is given in Methods.
+We chose a set of predictor variables based on the correlational results of RP:P [@openscienceconsortium2015], our own intuitions of experimental design factors that might impact replication success, and some covariates related to how close the replication was; a full description of these features is given in the Methods.
 
 Many predictors individually correlated with subjective replication success (Table \ref{tab:cor}).
-Predictors of higher replicability included within-subjects designs, larger numbers of trials per subject, and the original study having open data.
-Predictors of lower replicability included single vignetted studies with only one induction or example per condition, social psychology studies, and original-replication pairs where the original study was in-person and the replication switched to online.
+Predictors of higher replicability included within-subjects designs, larger numbers of trials per subject, and the original study having openly accessible data.
+Predictors of lower replicability included single-vignette studies (those with only one experimental stimulus per condition), classification as social psychology, and study pairs where the original study was in-person and the replication switched to online.
 
 Distributions of study outcomes across some of these properties are shown in Figure \ref{fig:predictors-graph}.
-To quantify the effects of these single predictors, we ran logistic models predicting the subjective replication score (on 0-1) as a function of the single predictor, and exponentiated the coefficient to get an odds ratio.
+To quantify the effects of these single predictors, we ran logistic models predicting the subjective replication score (on a 0--1 scale) as a function of the single predictor, and exponentiated the coefficient to obtain an odds ratio.
 Both social and cognitive psychology studies were well represented in the replication sample, and the cognitive psychology studies replicated `r round(1/subfield, 2)` times as often as social psychology studies.
@@
 Studies with multiple vignettes replicated `r round(1/vignette, 2)` times as often as single vignetted studies.
-However, there were strong correlations among these experimental features and between these experimental features and subfield.
+However, there were strong correlations among these experimental features as well as between these experimental features and specific subfields.
 
-Studies with open data, which almost always also had open materials, tended to replicate more than studies without open data.
+Studies with open data, which almost always also had open materials as well, tended to replicate more than studies without open data.
 Nearly all replications studies were conducted online, but original studies were split between using in-person and online recruitment.
 Replications that switched to online were less likely to replicate than those that had the same modality as the original (generally both online, in a few cases both in-person).
-While online studies in general show comparable results to studies conducted in person [@crump2013], switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well-adapted (ex.
-inductions may be weaker or attention checks inadequate to the new sample).
-These factors of open materials, open data, and online samples in original studies are more common in more recent studies, and so these effects may partially reflect temporal trends.
+While online studies in general show comparable results to studies conducted in person [@crump2013], switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well-adapted (e.g., inductions might have been weaker or instructions might have been insufficient).
+These factors -- open materials, open data, and online samples -- are more common in more recent studies, and so these effects may partially reflect temporal trends.
 
@@
 
-## Regression model
+## Joint evaluation of the predictors of replicability
 
-While a number of predictors show individual correlations with the subjective replication score, many of the predictors intercorrelate with one another.
-In order to determine which predictors were the strongest, we ran a series of pre-registered regression models regularized using a horseshoe shrinkage prior [@carvalho09].
-We ran both 1) models using all the original-replication pairs, but without original effect size and original p value as predictors, as they were uncodable for some pairs, and 2) models including all predictors, but on only the subset of data where all predictors were available.
-The coefficient estimates from two models predicting the subjective replication scores are shown in Figure \ref{fig:mod-results}; see Supplement for full model results.
+While a number of features show individual correlations with the subjective replication score, many correlate with one another.
+To determine which predictors were the strongest, we ran a series of pre-registered Bayesian regression models regularized using a horseshoe shrinkage prior [@carvalho09].
+We first ran models using all of the original-replication pairs (N=176), but without original effect size and original $p$ value as predictors, as they were uncodable for some pairs.
+We next ran models including all predictors, but on only the subset of data where all predictors were available (N=136).
+
+Coefficient estimates from the two models predicting the subjective replication scores are shown in Figure \ref{fig:mod-results}; see Supplement for full model results.
 Due to a large number of predictors coupled with a small and noisy dataset, there is much uncertainty around the coefficients even with strong regularization.
@@
 
-Within-subjects designs stand out as the strongest indicator of replicability in the model with all the data (`r within_1`).
-In the model with all predictors, but less data, within-subjects designs remain predictive (`r within_3`), and standardized effect size is also a strong predictor of subjective replication score (`r smd_3`).
+Within-subjects designs stand out as the strongest correlate of replicability in the model with all the data (`r within_1`).
+In the model with all predictors, but less data, within-subjects designs remain strong (`r within_3`), and standardized effect size is also substantially related to subjective replication score (`r smd_3`).
 Both effects are robust to a sensitivity analysis including only studies with close replications and matching statistical tests (within-subjects `r within_sens`; effect size `r smd_sens`).
@@
 We also ran models predicting our secondary outcome measures: whether the replication effect was within the prediction interval of the original effect and what the p-original was between the replication and original.
-Both these models had even more uncertain estimates.
-While the credible intervals were wide, the general patterns of predictor direction and relative strength were similar to the subjective replication models (See Supplement for plots of coefficients for these additional models).
+Both these models had more uncertain estimates.
+While the credible intervals were wide, the general patterns of predictor direction and relative strength were similar to the subjective replication models (see Supplement).
 The strongest predictors for prediction interval were still within-subjects designs (`r within_2`) and studies with larger effect sizes (`r smd_2`).
@@
 Here, we take a functional approach to assessing replicability, framing both our methods and interpretation around the idea of whether work can be repeated by an early-career scientist.
-We took advantage of 11 years of graduate student replication projects to look at correlational predictors of replication in a previously-unused dataset.
+We took advantage of 11 years of graduate student replication projects to study both the overall level of replication success and the correlational predictors of replication in a previously-unused dataset.
 In line with previous results, we found a `r round(pluck(sub_rep_rate,1))`% replication rate, with some studies showing effect sizes similar to the original and others much smaller.
-When we looked at individual correlates of replicability, within-subjects designs, work in the subfield of cognitive psychology, and the original and replication both using online samples stood out as the strongest correlates.
+Within-subjects designs, work in the subfield of cognitive psychology, and the original and replication both using online samples stood out as the strongest correlates of replication success.
 As many of these predictors interrelate with one another, we ran regularized regressions with all the predictors at once.
@@
 
-<!-- contributions and takehome  -->
+<!-- Large-scale replication studies including ours should be interpreted in light of their methods and their estimand.
+Given our sample, we are able to estimate the correlates of studies replicating when the replications are conducted online, by graduate students who have limited time and budget.
+-->
 
-Replication results should be interpreted in light of their methods and estimand.
-Given our sample, we are able to estimate the correlates of studies replicating when the replications are conducted online, by graduate students with limited time and budget.
-We do not interpret our non-replications as indicating the original results were false positives (presumably some were and some weren't).
+We do not interpret our non-replications as indicating the original results were false positives: presumably some were and some were not.
 There are many possible reasons for the non-replications in this sample.
 In some cases, the problem may be with the replication, such as too few participants, many exclusions for failed attention checks, or participants speeding through the study.
-When these issues are diagnosed, they suggest possible ways to "rescue" the replication by increasing the sample or changing the interface, without altering the underlying experiment; thus, while the replication did not succeed, after some troubleshooting, students may still be able to extend the work in the future.
+When these issues are diagnosed, they can suggest possible ways to "rescue" the replication by increasing the sample or changing the interface, without altering the underlying experiment; thus, while the replication did not succeed, after some troubleshooting, students may still be able to extend the work in the future.
 In other cases, there were a priori reasons to distrust the original study, such as exclusion criteria that seemed post-hoc or high-order interaction terms with a small sample.
 That said, not all scientists recognize the same factors as potential indications of low power or questionable research practices; students conducting these replications generally expected them to succeed.
-In many non-replication cases, it was unclear why the results failed to replicate.
+In many -- perhaps most -- non-replications in our sample, it was unclear why the results failed to replicate.
 
-We conducted an observational study of replication attempts, and our results are limited by the studies we included, which are limited in number and may not be representative of the studies of interest to psychologists as a whole.
-Our predictor variables were not manipulated, so they cannot be interpreted as causing (non-)replication, but only as correlational markers.
+Our results are limited by the sample of studies we included, which are limited in number and may not be representative of the studies of interest to psychologists as a whole.
+Further, our predictor variables were not manipulated, so they cannot be interpreted as causing (non-)replication, but only as correlational markers.
 Some of the correlates are most easily interpreted as being about the original study, and others reflect the closeness of the replication to the original.
-For instance, while within-subjects designs are more likely to replicate than between-subjects designs, this could be related to power, or the types of experiments that tend to be run in each design.
-Given the predictive value, slightly more skepticism and critical reading of between-subjects designs may be warranted, but this correlation, by itself, does not mean scientists should prefer to run within-subjects designs.
+For instance, while within-subjects designs are more likely to replicate than between-subjects designs, this predictor could also be related to the types of experiments that tend to be run in each design.
+Given the strong relationship of this factor to replicability, slightly more skepticism and critical reading of between-subjects designs may be warranted, but this correlation, by itself, does not mean scientists should prefer within-subjects designs.
 
-Large scale replications are costly and arduous to run.
+Large scale replication studies are costly and arduous.
 The batch of replications presented here were pedagogical replications, done as part of a class.
-Trainee behavioral scientists need to learn experimental methods, and conducting replications as part of methods classes serve a dual purpose: they enables students to learn to do experiments in a scaffolded way, and they lead to more useful results than if students designed their own experiments from scratch on the same timescale [@quintana2021; @wagge2019;@frank2012; @hawkins].
-Pedagogy has an important role to play in open science more broadly -- it's one thing to require or incentivize certain practices, but the tools and workflows of open science have to be learned.
+Trainees must learn experimental methods, and conducting replications as part of methods classes serves several purposes: it enables students to learn to do experiments in a supportive context, it often leads to more useful results than if students designed their own experiments from scratch, and it creates a resource for studying the literature [@quintana2021; @wagge2019;@frank2012; @hawkins2018].
+We believe that this kind of pedagogy has an important role to play in improving methodological practices in psychology more broadly.
+The tools and workflows of rigorous, replicable science cannot simply be mandated: they have to be learned.
 

### 2023-07-08 paper/manuscript.Rmd
other cleanup

@@
 
-Addressing this issue requires a better understanding of the scope of the problem as well as the methodological and structural issues that might lead to replication failure [@smaldino2016;@simmons20211].
+Addressing this issue requires a better understanding of the scope of the problem as well as the methodological and structural issues that might lead to replication failure [e.g., @smaldino2016;@simmons2011].
 Estimating replicability in the literature is a key starting point, but, as we review below, there is limited consensus on what quantity exactly should be estimated.
@@
 These replications were conducted as individual course projects by students in a graduate-level experimental methods class between 2011 and 2022.
-We then use this dataset to investigate statistical and experimental design predictors of replicability.
+We use this dataset to investigate the rate of replicability for such projects as well as the correlates of replication success.
 
@@
 For subfield, cognitive psychology is treated as the baseline condition.
-See Methods for how these variables were coded.") |> kable_styling(full_width=F, font_size=10)
+See Methods for how these variables were coded.", booktabs=TRUE) |> kable_styling(full_width=F, font_size=10)
 
@@
 
-We note that 4 (TODO check) of the replication projects were included in RP:P, and 10 of them were previously reported in @hawkins.
+Four of these replication projects were included in RP:P, and 10 of them were previously reported in @hawkins2018.
 
 ## Coding procedure
+
 We relied primarily on student reports to code the measured variables for the replications.

### 2023-07-08 paper/manuscript.tex
other cleanup

@@
 \begin{abstract}
-Cumulative scientific progress requires empirical results that are robust enough to support theory construction and future extensions.
-Yet in psychology, some prominent findings have failed to replicate, and large-scale investigations suggest that failures to replicate are widespread.
-The identification of features that predict replication success is limited by data, and most analyses re-analyse the same set of \textasciitilde170 replications.
+Cumulative scientific progress requires empirical results that are robust enough to support theory construction and extension.
+Yet in psychology, some prominent findings have failed to replicate, and large-scale studies suggest replicability issues are widespread.
+The identification of predictors of replication success is limited by the difficulty of conducting large samples of indepedendent replication experiments, however: most investigations re-analyse the same set of \textasciitilde170 replications.
 We introduce a new dataset of 176 replications from students in a graduate-level methods course.
-Replication results were close enough to original results to support student extensions in 49\% of replications.
-45\% of replications with suitable numerical outcomes (N=136) had point estimates within the prediction interval of the original outcome.
-Larger original effect sizes and within-participants designs were predictive of replication.
-Consistent with prior reports, our results indicate that the robustness of the psychology literature is low enough to limit progress by student investigators.
-
-{[}148 words / NHB max 150{]}
+Replication results were judged to be successful in 49\% of replications; of the 136 where comparable effect sizes could be computed, 45\% had point estimates within the prediction interval of the original outcome.
+Larger original effect sizes and within-participants designs were especially related to replication success.
+Or results indicate that, consistent with prior reports, the robustness of the psychology literature is low enough to limit cumulative progress by student investigators.
 
@@
 
-Cumulative scientific progress requires empirical results that are robust enough to support theory construction and future extensions.
+Cumulative scientific progress requires empirical results that are robust enough to support both future empirical extensions and the construction of synthetic theories.
 Yet in psychology, some prominent individual findings have failed to replicate in multi-site replication attempts (ex.
@@
 2022}, ego-depletion, \protect\hyperlink{ref-hagger2016}{Hagger et al.
-2016}), and a large-scale replication project pegged the replication rate for findings in top-tier psychology journals at around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}).
-When scientists treat publication as a signal of truth and attempt to build on results without verifying them first, they can become frustrated pursuing extensions to a popular, but unreliable result.
-As each failed extension does not directly contradict the original result, many scientists may waste considerable time and resources pursuing results where there may be none.
+2016}).
+One early large-scale replication project pegged the replication rate for findings in top-tier psychology journals at around 40\% {[}RP:P; Open Science Consortium (\protect\hyperlink{ref-openscienceconsortium2015}{2015}){]}.
+Low replicability has negative consequences for the field as a whole: when scientists attempt to build on published results, they stand a good chance of meeting with failure.
 
-To identify studies at risk for non-cumulative findings, we might want to know 1) what to measure in order to capture the waste and frustration due to non-cumulative failed extensions and 2) from a descriptive perspective, what features of studies are associated with being at risk for this non-replicability.
-Measuring replicability has been the focus of much prior work, but there is limited consensus on what exactly is being estimated.
+Addressing this issue requires a better understanding of the scope of the problem as well as the methodological and structural issues that might lead to replication failure (\protect\hyperlink{ref-simmons2011}{Simmons et al.
+2011}, e.g., \protect\hyperlink{ref-smaldino2016}{Smaldino \& McElreath 2016}).
+Estimating replicability in the literature is a key starting point, but, as we review below, there is limited consensus on what quantity exactly should be estimated.
 
-\hypertarget{large-scale-replication-projects}{%
-\subsection{Large-scale replication projects}\label{large-scale-replication-projects}}
+Our viewpoint here is that one important estimand is the probability that a graduate student can identify a finding in the literature and replicate it successfully enough that they can build on that finding in subsequent work.
+Taking this perspective, our contribution is a new dataset of 176 replications of experimental studies from the social sciences, primarily psychology.
+These replications were conducted as individual course projects by students in a graduate-level experimental methods class between 2011 and 2022.
+We use this dataset to investigate the rate of replicability for such projects as well as the correlates of replication success.
+
+\hypertarget{what-are-we-estimating-when-we-measure-replicability}{%
+\subsection{What are we estimating when we measure replicability?}\label{what-are-we-estimating-when-we-measure-replicability}}
 
 A few large-scale investigations have measured replication rates in samples of psychology studies.
-Reproducibility Project: Psychology sampled roughly 100 studies from articles published in three top psychology journals in 2008 and distributed the studies across participating labs.
-They found an overall replication rate of around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}).
-Many Labs investigated heterogeneity using short target studies that compared between two conditions each.
-These study designs were not representative of the psychology literature as a whole, and due to the heterogeneity goal, they had large overall samples across multiple sites.
-Across Many Labs 1-3, in these high-powered replications, only 29 of 51 target effects (57\%) replicated (\protect\hyperlink{ref-klein2014}{Klein et al.
+The first of these, RP:P, sampled roughly 100 studies from articles published in three top psychology journals in 2008 and distributed the studies across participating labs, finding an overall replication rate of around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}).
+The followup Many Labs Studies investigated heterogeneity using short target studies that each compared two conditions.
+These study designs were not representative of the psychology literature as a whole, and due to the of measuring heterogeneity, they had large overall samples across multiple sites.
+Across Many Labs 1--3, only 29 of 51 target effects (57\%) replicated (\protect\hyperlink{ref-klein2014}{Klein et al.
 2014}, \protect\hyperlink{ref-ebersole2016}{Ebersole et al.
@@
 Camerer et al.
-(\protect\hyperlink{ref-camerer2018}{2018}) included all 21 behavioral social science studies from Nature and Science from 2010-2015 that were feasible; they consulted original authors and had high power to detect effects smaller than those reported.
-In this well-resourced environment with expert input, the replication rate was around 60\%.
+(\protect\hyperlink{ref-camerer2018}{2018}) included all 21 behavioral social science studies from Nature and Science from 2010-2015 that were feasible to replicate.
+They consulted original authors and had high power to detect even small effects; under these conditions and with this sample, the replication rate was around 60\%.
 
-While their sampling and methods varied, these previous approaches to replicability have focused on interpreting their results in terms of a potentially problematic estimand: the probability of a finding in the literature being somehow truly replicable.
+While their sampling procedure and methods varied, these previous approaches to replicability have all focused on interpreting their results in terms of a potentially problematic estimand: the probability of a finding in the literature being truly replicable.
 Critics have pointed out that ``true'' replicability may not be possible to estimate outside of a specific sample (\protect\hyperlink{ref-vanbavel2016}{Van Bavel et al.
-2016}) or even time period (\protect\hyperlink{ref-ramscar}{Ramscar et al.
-n.d.}).
-Further, the methods for estimating this quantity have been theoretically problematic.
-Sampling schemes did not reflect an entirely random sample from the literature; instead replication projects sampled from specific journals where results may be of more interest and adjusted the sample for feasibility concerns.
-These are reasonable sampling choices, but they undermine the claim that the estimand is the level of ``truth'' in the literature as a whole.
-Sampling truly at random from the literature may not even be desirable, as arguably a literature will succeed if useful discoveries come out of it, not if random findings are true (\protect\hyperlink{ref-wilson2020}{Wilson et al.
-2020}).
+2016}) or even time period (\protect\hyperlink{ref-ramscar2015}{Ramscar et al.
+2015}).
 
-Rather than aim for some measure of ``true'' replicability, it makes more sense to contextualize replication efforts based on their methodologies and outcome measures.
-With this lens, we could say that RP:P looked at how well findings in well-known journals can be replicated in a typical psychology lab.
-Many Labs looked at which well-known two condition studies replicate with huge samples, and Camerer et al.
-(\protect\hyperlink{ref-camerer2018}{2018}) looked at which prestigious journal findings replicate when conducted in a highly-resourced environment with expert involvement.
-All of these are potentially desirable estimands depending on what the specific circumstances and questions of interest are.
+Further, the methods used in these studies are not sufficient to yield an unbiased estimate of this quantity.
+In no case were studies randomly sampled from the literature; instead replication projects sampled from specific journals and adjusted the sample for feasibility concerns.
+These reasonable decisions further undermine interpretation of the results from these studies as representing the proportion of true findings in the psychology literature as a whole.
 
-In practice, most scientific work is conducted by graduate students with limited time, limited budgets and limited access to experts.
-Therefore, an important question is how replicable findings in the literature are for graduate students operating under these less-than-ideal conditions.
-If students cannot replicate a finding under these circumstances, it is unlikely that they will be able to successfully build upon the study in these circumstances either.
+Rather than aim for some measure of true replicability, perhaps we should contextualize the true estimand for replication efforts based on their methodologies and outcome measures.
+Through this lens, RP:P estimated the rate at which findings from relatively simple experiments published in a few well-known journals at a particular time could be replicated in a typical psychology lab.
+Many Labs estimated at which well-known, two-condition findings replicate in very large samples.
+Camerer et al.
+(\protect\hyperlink{ref-camerer2018}{2018}) estimated which prestigious journal findings replicate when conducted in a highly-resourced environment with expert involvement.
+All of these could be potentially desirable estimands.
 
-Our goal in estimating replicability is to look for markers of when findings can (and cannot) support cumulative science, by looking for markers of findings that do (or do not) support replication by graduate students operating under typical real-word constraints.
-Our sample of studies is selected based on what studies students were interested in and wanting to replicate, with some filtering for feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable given methodological and budgetary constraints.
-Our primary estimand is whether a student researcher, on selecting a finding of interest from the literature, can successfully achieve a result close enough to the original that they could build on it in their own work.
-In addition to this subjective measure of replicability, we also compare the effect sizes of the original and replication on one key outcome per study using prediction interval and p-original (\protect\hyperlink{ref-mathur2020}{Mathur \& VanderWeele 2020}).
+But in practice, most scientific work is conducted by graduate students with limited time, limited budgets and limited access to experts.
+If students cannot replicate a finding under these circumstances, they cannot build on it in their empirical or theoretical work.
+How replicable are findings in the literature for graduate students operating under these less-than-ideal conditions?
+We address this question here.
 
-\hypertarget{predicting-replication-success}{%
-\subsection{Predicting replication success}\label{predicting-replication-success}}
+Our current sample of replications is selected based on what experiments students were interested in and wanted to replicate, with some filtering for feasibility.
+This sampling is not at all random.
+It reflects how scientists generally choose which experiments to build on: those that are interesting and relatively feasible given methodological and budgetary constraints.
 
-Despite variation in the methods and outcomes used by large-scale replication studies, they are often aggregated together in analyses looking at the predictablity of replication success.
+In the current study, we estimate the probability of successful replication in this sample, with the goal of also identifying markers of when findings can (and cannot) support cumulative science.
+Our hope is to extend previous work that has attempted to find key correlates of replication success.
+
+\hypertarget{when-do-replications-succeed}{%
+\subsection{When do replications succeed?}\label{when-do-replications-succeed}}
+
+Despite variation in the methods and outcomes used by large-scale replication studies, they are often aggregated together in analyses looking at the predictability of replication success.
 Prediction markets and elicitations have established that people can predict what studies will replicate above chance (\protect\hyperlink{ref-dreber2015}{Dreber et al.
@@
 2020}, \protect\hyperlink{ref-youyou2023}{Youyou et al.
-2023}).
-In terms of specific attributes that predict replicability, Altmejd et al.
-(\protect\hyperlink{ref-altmejd2019}{2019}) examined statistical and demographic features of studies and identified larger sample sizes, larger effect sizes, and simple effects (as opposed to interaction terms) as predictive of replication, and Open Science Consortium (\protect\hyperlink{ref-openscienceconsortium2015}{2015}) looked at correlates of replicability in the RP:P sample and found that studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate.
-One potential set of correlates to replicability that has not been thoroughly examined are experimental design features, such as between or within subjects designs and repeated measures.
+2023}), though again the precise features relating to success are unclear.
 
-While most approaches to correlates of replicability have been correlational, experimental approaches can be used to test potential interventions.
-Protzko et al.
-(\protect\hyperlink{ref-protzko2020}{2020}) showed, across 16 studies, that better methodological practices led to replication rates that matched theoretical expectations with replication effect sizes comparable with the original.
-Many Labs 5 added expert (original author) advice to a replication process, and found that it did not substantially increase the replication rate for the 10 studies (\protect\hyperlink{ref-ebersole2020}{Ebersole et al.
+In search of such features, RP:P examined correlates of replicability in the RP:P sample and found that studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate.
+Using these same data combined with a few other smaller samples, Altmejd et al.
+(\protect\hyperlink{ref-altmejd2019}{2019}) examined statistical and demographic features of replication studies and identified larger sample sizes, larger effect sizes, and simple effects (as opposed to interaction terms) as predictive of replication.\footnote{While most approaches to correlates of replicability have been correlational, experimental approaches can be used to test potential interventions (\protect\hyperlink{ref-ebersole2020}{Ebersole et al.
+2020}, \protect\hyperlink{ref-protzko2020}{Protzko et al.
 2020}).
-These types of experiments are valuable for testing potential causes of non-replication, but they don't scale well due to expense, and not all influences on non-replication may be experimentally manipulable.
+Experiments can be very valuable as tests of specific causes of non-replication, but they are expensive and time-consuming to conduct, and not all factors affecting replication success can be manipulated experimentally.}
 
-While they don't incur the expense of collecting new datasets, correlational approaches do depend on previously collected replication data, and their conclusions are limited by the available data.
+These approaches are fundamentally limited by the available data.
 Large-scale replications are arduous and expensive to run, so only a few large-scale replication datasets exist, and most analyses analyses draw heavily on same small set of data points.
@@
 2016}, \protect\hyperlink{ref-patil2016}{Patil et al.
-2016}) to the point that much of what we think we know about replicability may be overfit to the 100 studies included in RP:P.
+2016}) -- to the point that much of what we think we know about replicability may be over-fit to the 100 studies included in RP:P.
 More replication data is needed to identify markers of replicability and targets for potential future experimental approaches.
 
-Our contribution is a new dataset of 176 replications of experimental studies from the social sciences, primarily psychology.
-These replications were conducted by students in a graduate-level experimental methods class between 2011 and 2022 as individual course projects.
-We investigate statistical and experimental-design predictors of replicability in this dataset and find that within-subjects designs and studies with large standardized effect sizes are positively correlated with replication success.
+Further, none of these studies focused on features of experimental design, such as within-subjects designs or the use of repeated measures.
+There has been speculation that both of these factors should be linked to increased replicability due to their role in enabling increased statistical precision.
+Within-subjects designs lead to more precise experimental estimates by allowing the estimation of correlated person-level variation across conditions; repeated measures allow for more precise estimation by averaging out measurement error.
+Both are often recommended by methodologists as part of good measurement practices, at least when they are feasible (\protect\hyperlink{ref-greenwald1976}{Greenwald 1976}, \protect\hyperlink{ref-rosenthal2008}{Rosenthal \& Rosnow 2008}, \protect\hyperlink{ref-frank2023}{Frank et al.
+2023}).
+
+In sum, our current study examines the overall rate of replicability as well as the statistical and design features that predict replicability in a new sample of student replications.
 
@@
 
-PSYCH 251 is Stanford Psychology's graduate-level experimental methods class taught by MCF.
-During the 10 week class, each student replicated a published finding.
-They individually re-implemented the study, wrote analysis code, pre-registered their study, collected data using an online platform, and wrote up a structured replication report.
-Students were free to choose studies related to their research interests, with the default recommendation being an article from a recent year of Psychological Science.
-The resultant sample of studies is not a random sample from the literature but is representative of studies that are of interest to and doable by first year graduate students.
+PSYCH 251 is a graduate-level experimental methods class in experimental psychology taught at Stanford University.
+During the 10 week class, each student replicates a published finding.
+They individually re-implement the study, write analysis code, pre-register their study, collect data (typically using an online crowd-sourcing platform), and write a structured replication report.
+Students in the course are free to choose studies related to their research interests, with the default recommendation being an article from a recent year of Psychological Science.
 
-The sample of replicated studies reflects the variability of the literature, including studies from different subfields, with different experimental methods and statistical outcomes.
-We leveraged the naturally occurring variability in this sample of replications to examine how different demographic, experimental design, and statistical properties predict replication success.
+The sample of replicated studies reflects the variability of the literature, including studies from different subfields (and occasionally fields outside of psychology), with different experimental methods and statistical outcomes.
+We leveraged naturally occurring variability in this sample of replications to examine how different demographic, experimental design, and statistical properties predict replication success.
 
-Of note, these replications were all conducted on short time scales, with constrained budgets, that in some cases limited the number of participants who could be recruited below what the original study had or what power analyses suggested.
-In nearly all cases, replications were conducted online, with recruitment from Amazon Mechanical Turk (default 2011-2020) or Prolific (default 2021-2022).
+These replications were all conducted on short time scales, within a constrained class budget.
+In some cases the budget limited the number of participants who could be recruited, occasionally below what the original study included or what power analyses suggested.
+In nearly all cases, replications were conducted online, with recruitment from Amazon Mechanical Turk (the default from 2011 to 2020) or Prolific (the default from 2021 -- 2022).
 
 Many different measures can be used to define replication success of an individual statistical result (\protect\hyperlink{ref-simonsohn2015}{Simonsohn 2015}, \protect\hyperlink{ref-gelman2018}{Gelman 2018/ed}, \protect\hyperlink{ref-mathur2020}{Mathur \& VanderWeele 2020}).
-However, whether one feels confident in the results of a study given a replication is not always dependent on only one outcome measure (ex.
-interaction term) and particularly not dependent on only one statistical comparison between the two studies (ex.
-replication is p\textless.05 same direction as original).
-As our primary outcome, we use a subjective replication score which, unlike statistical measures, accommodated studies with multiple important outcome measures that together defined the pattern of interest and was applicable across the diverse range of statistical measures and reporting practices present in the sample.
-Importantly, a holistic measure of replication success had already been coded for most projects when they were turned in at the end of the class.
-For reliability, VB independently code the replication success from the students' written reports; discrepancies were resolved by discussion between MCF and VB (inter-rater reliability, Spearman's \(\rho\): 0.88, disagreement in 26\% of cases).
+However, whether a replication should be considered successful is not always dependent on only one statistical comparison between the two studies.
+Often in original papers, multiple statistical tests are cited in support of the claim that a pattern of results matches a particular theoretical expectation.
+
+As our primary outcome, we chose to use a subjective replication score (coded by two independent raters -- one typically at the time of project completion -- with discrepancies resolved by discussion).
+Unlike statistical measures, subjective replication success accommodates studies with multiple important outcome measures that together define the pattern of interest.
+Further, this measure was applicable across the diverse range of statistical measures and reporting practices present in the sample.
 
 As a complement to our primary subjective outcome, we also used two statistical measures of replication on the subset of the data where they were computable for the key statistic of interest (136 cases, see Figure \ref{fig:prisma}).
-We used p-original, the p-value on the null hypothesis that the original and replication statistics are from the same distribution, and prediction interval, a binary measure of whether the replication statistic fell within the prediction interval of the original statistic (\protect\hyperlink{ref-mathur2020}{Mathur \& VanderWeele 2020}).
+We used \emph{p-original}, the \emph{p}-value on the null hypothesis that the original and replication statistics are from the same distribution, and \emph{prediction interval}, a binary measure of whether the replication statistic fell within the prediction interval of the original statistic (\protect\hyperlink{ref-mathur2020}{Mathur \& VanderWeele 2020}).
 The prediction interval depends on the level of evidence of the original study; if the effect was marginal, the prediction interval could overlap zero; thus, a replication might fall within the predictive interval, and be consistent with the original outcome, but not provide compelling evidence for the claimed effect.
 Conversely, large original effects with precise point estimates may have prediction intervals that do not overlap a smaller replication effect size, and thus would be inconsistent with the original outcome, even though researcher intuition might classify it as a success.
-Thus, the statistical metrics quantify the similarity of a key statistic, but they will not always match researcher intuitions on whether a study replicated.
+Thus, these two statistical metrics each quantify the similarity between a key statistic in the original study and the replication, but they will not always match researcher intuitions on whether a study replicated.
 
@@
 46\% (62/136) of replications has outcomes with point-estimates within the prediction interval of the original outcome.
-The median p\_original value on the original and replication point-estimates coming from the same distribution was 0.03, representing the median probability that a replication study's estimate would be at least as extreme as was actually observed, if in fact the replication and original were statistically consistent.
+The median \emph{p}-original value on the original and replication point-estimates coming from the same distribution was 0.03, representing the median probability that a replication study's estimate would be at least as extreme as was actually observed, if in fact the replication and original were statistically consistent.
+
 Figure \ref{fig:smd} shows the relationship between original standardized effect size, replication effect size, and subjective replication score.
@@
 On average, there was a diminution of effect sizes from original to replication.
-This pattern of results is consistent with the pattern of results found in RP:P (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}).
+This pattern of results is consistent with the results of RP:P (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}).
 
@@
 2020}).
-If we assume that the level of heterogeneity in hypothetical multi-site replications of these effects would be the same as the average level heterogeneity found in Olsson-Collentine et al.
-(\protect\hyperlink{ref-olsson2020}{2020}) (tau=.21 in SMD units), then 64.3\% (72/112) of replication effect sizes are distributionally consistent with the original effect size.
-More work on understanding heterogeneity is needed to understand what levels of heterogeneity to expect across different implementations of the same experiment, and how considerations of heterogeneity should impact interpretations of both novel results and replication results.
-
-{[}Is this the right place to talk about heterogeneity / what did we want to say?{]}
+If we assume that the level of heterogeneity in hypothetical multi-site replications of these effects is the same as the average level heterogeneity found in prior multi-site replications in psychology {[}\(\tau=.21\) in units of standardized mean difference; Olsson-Collentine et al.
+(\protect\hyperlink{ref-olsson2020}{2020}){]}, then 64.3\% (72/112) of replication effect sizes are distributionally consistent with the original effect size.
+However, more work on understanding heterogeneity is needed to understand what levels of heterogeneity to expect across different implementations of the same experiment, and how considerations of heterogeneity should impact interpretations of both novel results and replication results.
 
@@
 \fontsize{10}{12}\selectfont
-\begin{tabular}[t]{r|c|c}
-\hline
+\begin{tabular}[t]{rcc}
+\toprule
 Predictors & r & p\\
-\hline
+\midrule
 Within subjects & 0.333 & 0.000\\
-\hline
 Log n trials & 0.182 & 0.015\\
-\hline
 Open data & 0.150 & 0.047\\
-\hline
 Non psych & 0.080 & 0.294\\
-\hline
 Other psych & 0.075 & 0.322\\
-\hline
+\addlinespace
 Publication year & 0.064 & 0.399\\
-\hline
 Open materials & 0.002 & 0.979\\
-\hline
 Stanford & -0.027 & 0.725\\
-\hline
 Log rep/orig sample & -0.047 & 0.536\\
-\hline
 Log original sample size & -0.108 & 0.155\\
-\hline
+\addlinespace
 Switch to online & -0.158 & 0.037\\
-\hline
 Social & -0.246 & 0.001\\
-\hline
 Single vignette & -0.267 & 0.000\\
-\hline
+\bottomrule
 \end{tabular}
@@
 
-\hypertarget{single-predictors}{%
-\subsection{Single predictors}\label{single-predictors}}
+\hypertarget{independent-correlates-of-replication-success}{%
+\subsection{Independent correlates of replication success}\label{independent-correlates-of-replication-success}}
 
 We investigated what features of the original study and replication were correlated with replication success, with the goal of being able to identify potential markers of replicability.
-We chose a set of predictor variables based on the correlational results of RP:P (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}), our own intuitions of experimental design factors that might impact replication success, and some covariates related to how close the replication was.
-A full description of these features is given in Methods.
+We chose a set of predictor variables based on the correlational results of RP:P (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}), our own intuitions of experimental design factors that might impact replication success, and some covariates related to how close the replication was; a full description of these features is given in the Methods.
 
 Many predictors individually correlated with subjective replication success (Table \ref{tab:cor}).
-Predictors of higher replicability included within-subjects designs, larger numbers of trials per subject, and the original study having open data.
-Predictors of lower replicability included single vignetted studies with only one induction or example per condition, social psychology studies, and original-replication pairs where the original study was in-person and the replication switched to online.
+Predictors of higher replicability included within-subjects designs, larger numbers of trials per subject, and the original study having openly accessible data.
+Predictors of lower replicability included single-vignette studies (those with only one experimental stimulus per condition), classification as social psychology, and study pairs where the original study was in-person and the replication switched to online.
 
 Distributions of study outcomes across some of these properties are shown in Figure \ref{fig:predictors-graph}.
-To quantify the effects of these single predictors, we ran logistic models predicting the subjective replication score (on 0-1) as a function of the single predictor, and exponentiated the coefficient to get an odds ratio.
+To quantify the effects of these single predictors, we ran logistic models predicting the subjective replication score (on a 0--1 scale) as a function of the single predictor, and exponentiated the coefficient to obtain an odds ratio.
 Both social and cognitive psychology studies were well represented in the replication sample, and the cognitive psychology studies replicated 2.45 times as often as social psychology studies.
@@
 Studies with multiple vignettes replicated 2.62 times as often as single vignetted studies.
-However, there were strong correlations among these experimental features and between these experimental features and subfield.
+However, there were strong correlations among these experimental features as well as between these experimental features and specific subfields.
 
-Studies with open data, which almost always also had open materials, tended to replicate more than studies without open data.
+Studies with open data, which almost always also had open materials as well, tended to replicate more than studies without open data.
 Nearly all replications studies were conducted online, but original studies were split between using in-person and online recruitment.
@@
 While online studies in general show comparable results to studies conducted in person (\protect\hyperlink{ref-crump2013}{Crump et al.
-2013}), switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well-adapted (ex.
-inductions may be weaker or attention checks inadequate to the new sample).
-These factors of open materials, open data, and online samples in original studies are more common in more recent studies, and so these effects may partially reflect temporal trends.
+2013}), switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well-adapted (e.g., inductions might have been weaker or instructions might have been insufficient).
+These factors -- open materials, open data, and online samples -- are more common in more recent studies, and so these effects may partially reflect temporal trends.
 
@@
 
-\hypertarget{regression-model}{%
-\subsection{Regression model}\label{regression-model}}
+\hypertarget{joint-evaluation-of-the-predictors-of-replicability}{%
+\subsection{Joint evaluation of the predictors of replicability}\label{joint-evaluation-of-the-predictors-of-replicability}}
 
-While a number of predictors show individual correlations with the subjective replication score, many of the predictors intercorrelate with one another.
-In order to determine which predictors were the strongest, we ran a series of pre-registered regression models regularized using a horseshoe shrinkage prior (\protect\hyperlink{ref-carvalho09}{Carvalho et al.
+While a number of features show individual correlations with the subjective replication score, many correlate with one another.
+To determine which predictors were the strongest, we ran a series of pre-registered Bayesian regression models regularized using a horseshoe shrinkage prior (\protect\hyperlink{ref-carvalho09}{Carvalho et al.
 2009}).
-We ran both 1) models using all the original-replication pairs, but without original effect size and original p value as predictors, as they were uncodable for some pairs, and 2) models including all predictors, but on only the subset of data where all predictors were available.
-The coefficient estimates from two models predicting the subjective replication scores are shown in Figure \ref{fig:mod-results}; see Supplement for full model results.
+We first ran models using all of the original-replication pairs (N=176), but without original effect size and original \(p\) value as predictors, as they were uncodable for some pairs.
+We next ran models including all predictors, but on only the subset of data where all predictors were available (N=136).
+
+Coefficient estimates from the two models predicting the subjective replication scores are shown in Figure \ref{fig:mod-results}; see Supplement for full model results.
 Due to a large number of predictors coupled with a small and noisy dataset, there is much uncertainty around the coefficients even with strong regularization.
@@
 
-Within-subjects designs stand out as the strongest indicator of replicability in the model with all the data (0.53, CrI= {[}0, 2{]}).
-In the model with all predictors, but less data, within-subjects designs remain predictive (0.66, CrI= {[}-0.04, 2.37{]}), and standardized effect size is also a strong predictor of subjective replication score (0.65, CrI= {[}0.27, 2.81{]}).
+Within-subjects designs stand out as the strongest correlate of replicability in the model with all the data (0.53, CrI= {[}0, 2{]}).
+In the model with all predictors, but less data, within-subjects designs remain strong (0.66, CrI= {[}-0.04, 2.37{]}), and standardized effect size is also substantially related to subjective replication score (0.65, CrI= {[}0.27, 2.81{]}).
 Both effects are robust to a sensitivity analysis including only studies with close replications and matching statistical tests (within-subjects 0.87, CrI= {[}-0.01, 3.33{]}; effect size 1.05, CrI= {[}0.76, 4.88{]}).
@@
 We also ran models predicting our secondary outcome measures: whether the replication effect was within the prediction interval of the original effect and what the p-original was between the replication and original.
-Both these models had even more uncertain estimates.
-While the credible intervals were wide, the general patterns of predictor direction and relative strength were similar to the subjective replication models (See Supplement for plots of coefficients for these additional models).
+Both these models had more uncertain estimates.
+While the credible intervals were wide, the general patterns of predictor direction and relative strength were similar to the subjective replication models (see Supplement).
 The strongest predictors for prediction interval were still within-subjects designs (0.62, CrI= {[}-0.18, 2.01{]}) and studies with larger effect sizes (0.3, CrI= {[}-0.29, 0.94{]}).
@@
 Here, we take a functional approach to assessing replicability, framing both our methods and interpretation around the idea of whether work can be repeated by an early-career scientist.
-We took advantage of 11 years of graduate student replication projects to look at correlational predictors of replication in a previously-unused dataset.
+We took advantage of 11 years of graduate student replication projects to study both the overall level of replication success and the correlational predictors of replication in a previously-unused dataset.
 In line with previous results, we found a 49\% replication rate, with some studies showing effect sizes similar to the original and others much smaller.
-When we looked at individual correlates of replicability, within-subjects designs, work in the subfield of cognitive psychology, and the original and replication both using online samples stood out as the strongest correlates.
+Within-subjects designs, work in the subfield of cognitive psychology, and the original and replication both using online samples stood out as the strongest correlates of replication success.
 As many of these predictors interrelate with one another, we ran regularized regressions with all the predictors at once.
@@
 
-Replication results should be interpreted in light of their methods and estimand.
-Given our sample, we are able to estimate the correlates of studies replicating when the replications are conducted online, by graduate students with limited time and budget.
-We do not interpret our non-replications as indicating the original results were false positives (presumably some were and some weren't).
+We do not interpret our non-replications as indicating the original results were false positives: presumably some were and some were not.
 There are many possible reasons for the non-replications in this sample.
 In some cases, the problem may be with the replication, such as too few participants, many exclusions for failed attention checks, or participants speeding through the study.
-When these issues are diagnosed, they suggest possible ways to ``rescue'' the replication by increasing the sample or changing the interface, without altering the underlying experiment; thus, while the replication did not succeed, after some troubleshooting, students may still be able to extend the work in the future.
+When these issues are diagnosed, they can suggest possible ways to ``rescue'' the replication by increasing the sample or changing the interface, without altering the underlying experiment; thus, while the replication did not succeed, after some troubleshooting, students may still be able to extend the work in the future.
 In other cases, there were a priori reasons to distrust the original study, such as exclusion criteria that seemed post-hoc or high-order interaction terms with a small sample.
 That said, not all scientists recognize the same factors as potential indications of low power or questionable research practices; students conducting these replications generally expected them to succeed.
-In many non-replication cases, it was unclear why the results failed to replicate.
+In many -- perhaps most -- non-replications in our sample, it was unclear why the results failed to replicate.
 
-We conducted an observational study of replication attempts, and our results are limited by the studies we included, which are limited in number and may not be representative of the studies of interest to psychologists as a whole.
-Our predictor variables were not manipulated, so they cannot be interpreted as causing (non-)replication, but only as correlational markers.
+Our results are limited by the sample of studies we included, which are limited in number and may not be representative of the studies of interest to psychologists as a whole.
+Further, our predictor variables were not manipulated, so they cannot be interpreted as causing (non-)replication, but only as correlational markers.
 Some of the correlates are most easily interpreted as being about the original study, and others reflect the closeness of the replication to the original.
-For instance, while within-subjects designs are more likely to replicate than between-subjects designs, this could be related to power, or the types of experiments that tend to be run in each design.
-Given the predictive value, slightly more skepticism and critical reading of between-subjects designs may be warranted, but this correlation, by itself, does not mean scientists should prefer to run within-subjects designs.
+For instance, while within-subjects designs are more likely to replicate than between-subjects designs, this predictor could also be related to the types of experiments that tend to be run in each design.
+Given the strong relationship of this factor to replicability, slightly more skepticism and critical reading of between-subjects designs may be warranted, but this correlation, by itself, does not mean scientists should prefer within-subjects designs.
 
-Large scale replications are costly and arduous to run.
+Large scale replication studies are costly and arduous.
 The batch of replications presented here were pedagogical replications, done as part of a class.
-Trainee behavioral scientists need to learn experimental methods, and conducting replications as part of methods classes serve a dual purpose: they enables students to learn to do experiments in a scaffolded way, and they lead to more useful results than if students designed their own experiments from scratch on the same timescale (\protect\hyperlink{ref-frank2012}{Frank \& Saxe 2012}, \protect\hyperlink{ref-wagge2019}{Wagge et al.
-2019}, \protect\hyperlink{ref-quintana2021}{Quintana 2021}, \protect\hyperlink{ref-hawkins}{Hawkins et al.
-n.d.}).
-Pedagogy has an important role to play in open science more broadly -- it's one thing to require or incentivize certain practices, but the tools and workflows of open science have to be learned.
+Trainees must learn experimental methods, and conducting replications as part of methods classes serves several purposes: it enables students to learn to do experiments in a supportive context, it often leads to more useful results than if students designed their own experiments from scratch, and it creates a resource for studying the literature (\protect\hyperlink{ref-frank2012}{Frank \& Saxe 2012}, \protect\hyperlink{ref-hawkins2018}{Hawkins et al.
+2018}, \protect\hyperlink{ref-wagge2019}{Wagge et al.
+2019}, \protect\hyperlink{ref-quintana2021}{Quintana 2021}).
+We believe that this kind of pedagogy has an important role to play in improving methodological practices in psychology more broadly.
+The tools and workflows of rigorous, replicable science cannot simply be mandated: they have to be learned.
 
@@
 
-We note that 4 (TODO check) of the replication projects were included in RP:P, and 10 of them were previously reported in Hawkins et al. (\protect\hyperlink{ref-hawkins}{n.d.}).
+Four of these replication projects were included in RP:P, and 10 of them were previously reported in Hawkins et al. (\protect\hyperlink{ref-hawkins2018}{2018}).
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-anderson2016}{}}%
-Anderson CJ, Bahník Š, Barnett-Cowan M, Bosco FA, Chandler J, Chartier CR, Cheung F, Christopherson CD, Cordes A, Cremata EJ, Della Penna N, Estel V, Fedor A, Fitneva SA, Frank MC, Grange JA, Hartshorne JK, Hasselman F, Henninger F, Hulst M van der, Jonas KJ, Lai CK, Levitan CA, Miller JK, Moore KS, Meixner JM, Munafò MR, Neijenhuijs KI, Nilsonne G, Nosek BA, Plessow F, Prenoveau JM, Ricker AA, Schmidt K, Spies JR, Stieger S, Strohminger N, Sullivan GB, Aert RCM van, Assen MALM van, Vanpaemel W, Vianello M, Voracek M, Zuni K (2016) Response to {Comment} on {``{Estimating} the reproducibility of psychological science.''} \emph{Science} \textbf{351}:1037--1037.
+Anderson CJ, Bahník án, Barnett-Cowan M, Bosco FA, Chandler J, Chartier CR, Cheung F, Christopherson CD, Cordes A, Cremata EJ, Della Penna N, Estel V, Fedor A, Fitneva SA, Frank MC, Grange JA, Hartshorne JK, Hasselman F, Henninger F, Hulst M van der, Jonas KJ, Lai CK, Levitan CA, Miller JK, Moore KS, Meixner JM, Munafò MR, Neijenhuijs KI, Nilsonne G, Nosek BA, Plessow F, Prenoveau JM, Ricker AA, Schmidt K, Spies JR, Stieger S, Strohminger N, Sullivan GB, Aert RCM van, Assen MALM van, Vanpaemel W, Vianello M, Voracek M, Zuni K (2016) Response to {Comment} on {``{Estimating} the reproducibility of psychological science.''} \emph{Science} \textbf{351}:1037--1037.
 doi:\href{https://doi.org/10.1126/science.aad9163}{10.1126/science.aad9163}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ebersole2020}{}}%
-Ebersole CR, Mathur MB, Baranski E, Bart-Plange D-J, Buttrick NR, Chartier CR, Corker KS, Corley M, Hartshorne JK, IJzerman H, Lazarević LB, Rabagliati H, Ropovik I, Aczel B, Aeschbach LF, Andrighetto L, Arnal JD, Arrow H, Babincak P, Bakos BE, Baník G, Baskin E, Belopavlović R, Bernstein MH, Białek M, Bloxsom NG, Bodroža B, Bonfiglio DBV, Boucher L, Brühlmann F, Brumbaugh CC, Casini E, Chen Y, Chiorri C, Chopik WJ, Christ O, Ciunci AM, Claypool HM, Coary S, Čolić MV, Collins WM, Curran PG, Day CR, Dering B, Dreber A, Edlund JE, Falcão F, Fedor A, Feinberg L, Ferguson IR, Ford M, Frank MC, Fryberger E, Garinther A, Gawryluk K, Ashbaugh K, Giacomantonio M, Giessner SR, Grahe JE, Guadagno RE, Hałasa E, Hancock PJB, Hilliard RA, Hüffmeier J, Hughes S, Idzikowska K, Inzlicht M, Jern A, Jiménez-Leal W, Johannesson M, Joy-Gaba JA, Kauff M, Kellier DJ, Kessinger G, Kidwell MC, Kimbrough AM, King JPJ, Kolb VS, Kołodziej S, Kovacs M, Krasuska K, Kraus S, Krueger LE, Kuchno K, Lage CA, Langford EV, Levitan CA, Lima TJS de, Lin H, Lins S, Loy JE, Manfredi D, Markiewicz Ł, Menon M, Mercier B, Metzger M, Meyet V, Millen AE, Miller JK, Montealegre A, Moore DA, Muda R, Nave G, Nichols AL, Novak SA, Nunnally C, Orlić A, Palinkas A, Panno A, Parks KP, Pedović I, Pękala E, Penner MR, Pessers S, Petrović B, Pfeiffer T, Pieńkosz D, Preti E, Purić D, Ramos T, Ravid J, Razza TS, Rentzsch K, Richetin J, Rife SC, Rosa AD, Rudy KH, Salamon J, Saunders B, Sawicki P, Schmidt K, Schuepfer K, Schultze T, Schulz-Hardt S, Schütz A, Shabazian AN, Shubella RL, Siegel A, Silva R, Sioma B, Skorb L, Souza LEC de, Steegen S, Stein LAR, Sternglanz RW, Stojilović D, Storage D, Sullivan GB, Szaszi B, Szecsi P, Szöke O, Szuts A, Thomae M, Tidwell ND, Tocco C, Torka A-K, Tuerlinckx F, Vanpaemel W, Vaughn LA, Vianello M, Viganola D, Vlachou M, Walker RJ, Weissgerber SC, Wichman AL, Wiggins BJ, Wolf D, Wood MJ, Zealley D, Žeželj I, Zrubka M, Nosek BA (2020) Many {Labs} 5: {Testing Pre-Data-Collection Peer Review} as an {Intervention} to {Increase Replicability}.
+Ebersole CR, Mathur MB, Baranski E, Bart-Plange D-J, Buttrick NR, Chartier CR,..., Nosek BA (2020) Many {Labs} 5: {Testing Pre-Data-Collection Peer Review} as an {Intervention} to {Increase Replicability}.
 \emph{Adv Methods Pract Psychol Sci} \textbf{3}:309--331.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-frank2023}{}}%
+Frank MC, Braginsky M, Cachia J, Coles N, Hardwicke T, Hawkins R, Mathur MB, Williams R (2023) Experimentology: An open science approach to experimental psychology methods.
+
 \leavevmode\vadjust pre{\hypertarget{ref-gelman2018}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-greenwald1976}{}}%
+Greenwald AG (1976) Within-subjects designs: To use or not to use? \emph{Psychological Bulletin} \textbf{83}:314
+
 \leavevmode\vadjust pre{\hypertarget{ref-hagger2016}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-hawkins}{}}%
-Hawkins RXD, Smith EN, Au C, Arias JM, Hermann E, Keil M, Lampinen A, Raposo S, Salehi S, Salloum J, Tan J, Frank MC Improving the {Replicability} of {Psychological Science Through Pedagogy}. :41
+\leavevmode\vadjust pre{\hypertarget{ref-hawkins2018}{}}%
+Hawkins RD, Smith EN, Au C, Arias JM, Catapano R, Hermann E, Keil M, Lampinen A, Raposo S, Reynolds J, Salehi S, Salloum J, Tan J, Frank MC (2018) Improving the replicability of psychological science through pedagogy.
+\emph{Advances in Methods and Practices in Psychological Science} \textbf{1}:7--18
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-klein2014}{}}%
-Klein RA, Ratliff KA, Vianello M, Adams RB, Bahník Š, Bernstein MJ, Bocian K, Brandt MJ, Brooks B, Brumbaugh CC, Cemalcilar Z, Chandler J, Cheong W, Davis WE, Devos T, Eisner M, Frankowska N, Furrow D, Galliani EM, Hasselman F, Hicks JA, Hovermale JF, Hunt SJ, Huntsinger JR, IJzerman H, John M-S, Joy-Gaba JA, Barry Kappes H, Krueger LE, Kurtz J, Levitan CA, Mallett RK, Morris WL, Nelson AJ, Nier JA, Packard G, Pilati R, Rutchick AM, Schmidt K, Skorinko JL, Smith R, Steiner TG, Storbeck J, Van Swol LM, Thompson D, Veer AE van `t, Ann Vaughn L, Vranka M, Wichman AL, Woodzicka JA, Nosek BA (2014) Investigating {Variation} in {Replicability}: {A} {``{Many Labs}''} {Replication Project}.
+Klein RA, Ratliff KA, Vianello M, Adams RB, Bahník án, Bernstein MJ,..., Nosek BA (2014) Investigating {Variation} in {Replicability}: {A} {``{Many Labs}''} {Replication Project}.
 \emph{Social Psychology} \textbf{45}:142--152.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-klein2018}{}}%
-Klein RA, Vianello M, Hasselman F, Adams BG, Adams RB, Alper S, Aveyard M, Axt JR, Babalola MT, Bahník Š, Batra R, Berkics M, Bernstein MJ, Berry DR, Bialobrzeska O, Binan ED, Bocian K, Brandt MJ, Busching R, Rédei AC, Cai H, Cambier F, Cantarero K, Carmichael CL, Ceric F, Chandler J, Chang J-H, Chatard A, Chen EE, Cheong W, Cicero DC, Coen S, Coleman JA, Collisson B, Conway MA, Corker KS, Curran PG, Cushman F, Dagona ZK, Dalgar I, Dalla Rosa A, Davis WE, Bruijn M de, De Schutter L, Devos T, Vries M de, Doğulu C, Dozo N, Dukes KN, Dunham Y, Durrheim K, Ebersole CR, Edlund JE, Eller A, English AS, Finck C, Frankowska N, Freyre M-Á, Friedman M, Galliani EM, Gandi JC, Ghoshal T, Giessner SR, Gill T, Gnambs T, Gómez Á, González R, Graham J, Grahe JE, Grahek I, Green EGT, Hai K, Haigh M, Haines EL, Hall MP, Heffernan ME, Hicks JA, Houdek P, Huntsinger JR, Huynh HP, IJzerman H, Inbar Y, Innes-Ker ÅH, Jiménez-Leal W, John M-S, Joy-Gaba JA, Kamiloğlu RG, Kappes HB, Karabati S, Karick H, Keller VN, Kende A, Kervyn N, Knežević G, Kovacs C, Krueger LE, Kurapov G, Kurtz J, Lakens D, Lazarević LB, Levitan CA, Lewis NA, Lins S, Lipsey NP, Losee JE, Maassen E, Maitner AT, Malingumu W, Mallett RK, Marotta SA, Međedović J, Mena-Pacheco F, Milfont TL, Morris WL, Murphy SC, Myachykov A, Neave N, Neijenhuijs K, Nelson AJ, Neto F, Lee Nichols A, Ocampo A, O'Donnell SL, Oikawa H, Oikawa M, Ong E, Orosz G, Osowiecka M, Packard G, Pérez-Sánchez R, Petrović B, Pilati R, Pinter B, Podesta L, Pogge G, Pollmann MMH, Rutchick AM, Saavedra P, Saeri AK, Salomon E, Schmidt K, Schönbrodt FD, Sekerdej MB, Sirlopú D, Skorinko JLM, Smith MA, Smith-Castro V, Smolders KCHJ, Sobkow A, Sowden W, Spachtholz P, Srivastava M, Steiner TG, Stouten J, Street CNH, Sundfelt OK, Szeto S, Szumowska E, Tang ACW, Tanzer N, Tear MJ, Theriault J, Thomae M, Torres D, Traczyk J, Tybur JM, Ujhelyi A, Aert RCM van, Assen MALM van, Hulst M van der, Lange PAM van, Veer AE van 't, Vásquez- Echeverría A, Ann Vaughn L, Vázquez A, Vega LD, Verniers C, Verschoor M, Voermans IPJ, Vranka MA, Welch C, Wichman AL, Williams LA, Wood M, Woodzicka JA, Wronska MK, Young L, Zelenski JM, Zhijia Z, Nosek BA (2018) Many {Labs} 2: {Investigating Variation} in {Replicability Across Samples} and {Settings}.
+Klein RA, Vianello M, Hasselman F, Adams BG, Adams RB, Alper S,..., Nosek BA (2018) Many {Labs} 2: {Investigating Variation} in {Replicability Across Samples} and {Settings}.
 \emph{Adv Methods Pract Psychol Sci} \textbf{1}:443--490.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-ramscar}{}}%
-Ramscar M, Shaoul C, Baayen RH Why many priming results don't (and won't) replicate: {A} quantitative analysis.
+\leavevmode\vadjust pre{\hypertarget{ref-ramscar2015}{}}%
+Ramscar M, Shaoul C, Baayen RH (2015) Why many priming results don't (and won't) replicate: {A} quantitative analysis.
+
+\leavevmode\vadjust pre{\hypertarget{ref-rosenthal2008}{}}%
+Rosenthal R, Rosnow RL (2008) Essentials of behavioral research: Methods and data analysis.
+
+\leavevmode\vadjust pre{\hypertarget{ref-simmons2011}{}}%
+Simmons JP, Nelson LD, Simonsohn U (2011) False-positive psychology: Undisclosed flexibility in data collection and analysis allows presenting anything as significant.
+\emph{Psychological science} \textbf{22}:1359--1366
 
@@
 doi:\href{https://doi.org/10.1177/0956797614567341}{10.1177/0956797614567341}
+
+\leavevmode\vadjust pre{\hypertarget{ref-smaldino2016}{}}%
+Smaldino PE, McElreath R (2016) The natural selection of bad science. \emph{Royal Society Open Science} \textbf{3}:160384. doi:\href{https://doi.org/10.1098/rsos.160384}{10.1098/rsos.160384}
 
@@
 \emph{Front Psychol} \textbf{10}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wilson2020}{}}%
-Wilson BM, Harris CR, Wixted JT (2020) Science is not a signal detection problem.
-\emph{Proc Natl Acad Sci USA} \textbf{117}:5559--5567.
-doi:\href{https://doi.org/10.1073/pnas.1914237117}{10.1073/pnas.1914237117}
 

### 2023-07-10 paper/manuscript.Rmd
new draft

@@
 Yet in psychology, some prominent findings have failed to replicate, and large-scale studies suggest replicability issues are widespread.
-The identification of predictors of replication success is limited by the difficulty of conducting large samples of indepedendent replication experiments, however: most investigations re-analyse the same set of ~170 replications.
+The identification of predictors of replication success is limited by the difficulty of conducting large samples of independent replication experiments, however: most investigations re-analyse the same set of ~170 replications.
 We introduce a new dataset of 176 replications from students in a graduate-level methods course.
-Replication results were judged to be successful in 49% of replications; of the 136 where comparable effect sizes could be computed, 45% had point estimates within the prediction interval of the original outcome.
+Replication results were judged to be successful in 49% of replications; of the 136 where comparable effect sizes could be computed, 46% had point estimates within the prediction interval of the original outcome.
 Larger original effect sizes and within-participants designs were especially related to replication success.
-Or results indicate that, consistent with prior reports, the robustness of the psychology literature is low enough to limit cumulative progress by student investigators.
+Our results indicate that, consistent with prior reports, the robustness of the psychology literature is low enough to limit cumulative progress by student investigators.
 :::
@@
 The first of these, RP:P, sampled roughly 100 studies from articles published in three top psychology journals in 2008 and distributed the studies across participating labs, finding an overall replication rate of around 40% [@openscienceconsortium2015].
-The followup Many Labs Studies investigated heterogeneity using short target studies that each compared two conditions.
-These study designs were not representative of the psychology literature as a whole, and due to the of measuring heterogeneity, they had large overall samples across multiple sites.
+The followup Many Labs studies investigated heterogeneity using short target studies that each compared two conditions.
+These study designs were not representative of the psychology literature as a whole, and due to the goal of measuring heterogeneity, they had large overall samples across multiple sites.
 Across Many Labs 1--3, only 29 of 51 target effects (57%) replicated [@klein2014; @klein2018; @ebersole2016].
@@
 In no case were studies randomly sampled from the literature; instead replication projects sampled from specific journals and adjusted the sample for feasibility concerns.
-These reasonable decisions further undermine interpretation of the results from these studies as representing the proportion of true findings in the psychology literature as a whole.
+These reasonable decisions further undermine the interpretation of the results from these studies as representing the proportion of true findings in the psychology literature as a whole.
 <!-- Sampling at random from the literature may not even be desirable, as arguably a literature will succeed if useful discoveries come out of it, not if random findings are true [@wilson2020].  -->
@@
 Through this lens, RP:P estimated the rate at which findings from relatively simple experiments published in a few well-known journals at a particular time could be replicated in a typical psychology lab.
-Many Labs estimated at which well-known, two-condition findings replicate in very large samples.
+Many Labs estimated the rate at which well-known, two-condition findings replicate in very large samples.
 @camerer2018 estimated which prestigious journal findings replicate when conducted in a highly-resourced environment with expert involvement.
@@
 
-But in practice, most scientific work is conducted by graduate students with limited time, limited budgets and limited access to experts.
-If students cannot replicate a finding under these circumstances, they cannot build on it in their empirical or theoretical work.
+But in practice, most scientific work is conducted by graduate students with limited time, limited budgets, and limited access to experts.
+If students cannot replicate a finding under these circumstances, they cannot build on it in their own empirical or theoretical work.
 How replicable are findings in the literature for graduate students operating under these less-than-ideal conditions?
@@
 
-In search of such features, RP:P examined correlates of replicability in the RP:P sample and found that studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate.
+In search of such features, RP:P examined correlates of replicability in the RP:P sample and found that studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller $p$ values were more likely to replicate.
 Using these same data combined with a few other smaller samples, @altmejd2019 examined statistical and demographic features of replication studies and identified larger sample sizes, larger effect sizes, and simple effects (as opposed to interaction terms) as predictive of replication.^[While most approaches to correlates of replicability have been correlational, experimental approaches can be used to test potential interventions [@protzko2020;@ebersole2020].
@@
 These approaches are fundamentally limited by the available data.
-Large-scale replications are arduous and expensive to run, so only a few large-scale replication datasets exist, and most analyses analyses draw heavily on same small set of data points.
+Large-scale replications are arduous and expensive to run, so only a few large-scale replication datasets exist, and most analyses draw heavily on same small set of data points.
 In particular, the RP:P dataset is much discussed and reanalyzed [@etz2016;@gilbert2016;@patil2016;@anderson2016] -- to the point that much of what we think we know about replicability may be over-fit to the 100 studies included in RP:P.
-More replication data is needed to identify markers of replicability and targets for potential future experimental approaches.
 
-Further, none of these studies focused on features of experimental design, such as within-subjects designs or the use of repeated measures.
+Further, none of these studies focused on features of experimental design, such as within-participants designs or the use of repeated measures.
 There has been speculation that both of these factors should be linked to increased replicability due to their role in enabling increased statistical precision.
-Within-subjects designs lead to more precise experimental estimates by allowing the estimation of correlated person-level variation across conditions; repeated measures allow for more precise estimation by averaging out measurement error.
+Within-participants designs lead to more precise experimental estimates by allowing the estimation of correlated person-level variation across conditions; repeated measures allow for more precise estimation by averaging out measurement error.
 Both are often recommended by methodologists as part of good measurement practices, at least when they are feasible  [@rosenthal2008;@greenwald1976; @frank2023].
@@
 
+target_dist <- quantile(d$target_N)
+rep_dist <- quantile(d$replication_N)
+ratio_dist <- d |> mutate(ratio_N=replication_N/target_N) |> pull(ratio_N) |> quantile()
+
 ```
@@
 In some cases the budget limited the number of participants who could be recruited, occasionally below what the original study included or what power analyses suggested.
+The replications had a median post-exclusion sample size that was `r round(ratio_dist[3]*100)`% of the original sample size (interquartile range `r round(ratio_dist[2]*100)`%-`r round(ratio_dist[4]*100)`%)^[Replications had a median of `r round(rep_dist[3])` participants (interquartile range: `r round(rep_dist[2])` - `r round(rep_dist[4])`), while original studies had a median of `r round(target_dist[3])` participants (interquartile range: `r round(target_dist[2])` - `r round(target_dist[4])`).].
 In nearly all cases, replications were conducted online, with recruitment from Amazon Mechanical Turk (the default from 2011 to 2020) or Prolific (the default from 2021 -- 2022).
@@
 
-```{r smd, out.height="25%", fig.width=6, fig.height=3, fig.pos="ht", fig.cap="Relationship between effect size of the original study, effect size of the replication study, and subjective replication success rating, for those studies where effect size was applicable."}
+```{r smd, out.height="25%", fig.width=6, fig.height=3, fig.pos="ht", fig.cap="Relationship between effect size of the original study, effect size of the replication study, and subjective replication success rating, for those studies where effect size was applicable (N=112)."}
 d |> 
@@
 
+# sample size considerations
+
+# ggplot(d, aes(x=target_N, y=replication_N, color=as.factor(sub_rep)))+geom_point()+coord_trans(x="log", y="log")+geom_abline(slope=1)+ scale_color_viridis(discrete=T, direction = 1, 
+#                       name = "Subjective\nReplication\nSuccess\n")
+# d |> mutate(bigger_orig=replication_N<.9*target_N,
+#             bigger_rep=replication_N>1.1*target_N,
+#             similar=!bigger_orig & !bigger_rep) |> 
+#   group_by(bigger_orig, bigger_rep, similar) |> tally()
+
 ```
@@
 Figure \ref{fig:smd} shows the relationship between original standardized effect size, replication effect size, and subjective replication score.
-Some studies replicated withed similar size effects to the original, and others failed to replicate, with replication effect sizes near zero.
+Some studies replicated with similar size effects to the original, and others failed to replicate, with replication effect sizes near zero.
 On average, there was a diminution of effect sizes from original to replication.
@@
 Some multi-site replication projects have found heterogeneity in effect sizes across replication sites [@ebersole2020; @klein2018; @olsson2020].
-If we assume that the level of heterogeneity in hypothetical multi-site replications of these effects is the same as the average level heterogeneity found in prior multi-site replications in psychology [$\tau=.21$ in units of standardized mean difference; @olsson2020], then `r round(tau_pct,1)`% (`r tau_predIntcount`/`r tau_predInttotal`) of replication effect sizes are distributionally consistent with the original effect size.
+As a test of sensitivity to heterogeneity, we assumed that the level of heterogeneity in hypothetical multi-site replications of our sampled articles was the same as the average level heterogeneity found by @olssen2020 in prior multi-site replications in psychology ($\tau=.21$ in units of standardized mean difference).
+Under this assumption, `r round(tau_pct)`% (`r tau_predIntcount`/`r tau_predInttotal`) of replication effect sizes are distributionally consistent with the original effect size.
 However, more work on understanding heterogeneity is needed to understand what levels of heterogeneity to expect across different implementations of the same experiment, and how considerations of heterogeneity should impact interpretations of both novel results and replication results.
@@
          p = sapply(preds, function(x) sub_cor(x, stat = "p"))) |> 
-  mutate(Predictors=factor(preds, levels=c("social", "other_psych", "non_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "pub_year", "log_trials", "log_sample", "log_ratio_ss"), labels=c("Social", "Other psych", "Non psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log n trials", "Log original sample size", "Log rep/orig sample"))) |> arrange(desc(r)) |> select(Predictors, r, p)
+  mutate(Predictors=factor(preds, levels=c("social", "other_psych", "non_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "pub_year", "log_trials", "log_sample", "log_ratio_ss"), labels=c("Social", "Other psych", "Non psych", "Within participants", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log n trials", "Log original sample size", "Log rep/orig sample"))) |> arrange(desc(r)) |> select(Predictors, r, p)
 
@@
 Many predictors individually correlated with subjective replication success (Table \ref{tab:cor}).
-Predictors of higher replicability included within-subjects designs, larger numbers of trials per subject, and the original study having openly accessible data.
+Predictors of higher replicability included within-participants designs, larger numbers of trials per participant, and the original study having openly accessible data.
 Predictors of lower replicability included single-vignette studies (those with only one experimental stimulus per condition), classification as social psychology, and study pairs where the original study was in-person and the replication switched to online.
@@
 Both social and cognitive psychology studies were well represented in the replication sample, and the cognitive psychology studies replicated `r round(1/subfield, 2)` times as often as social psychology studies.
-Within and between subjects designs were both common, and within-subjects designs replicated `r within |> round(2)` times as much.
+Within and between participants designs were both common, and within-participants designs replicated `r within |> round(2)` times as much as between-participants designs.
 Studies with multiple vignettes replicated `r round(1/vignette, 2)` times as often as single vignetted studies.
@@
 Studies with open data, which almost always also had open materials as well, tended to replicate more than studies without open data.
-Nearly all replications studies were conducted online, but original studies were split between using in-person and online recruitment.
+Nearly all replication studies were conducted online, but original studies were split between using in-person and online recruitment.
 Replications that switched to online were less likely to replicate than those that had the same modality as the original (generally both online, in a few cases both in-person).
@@
 
-within <- dat |> mutate(is_within=ifelse(is_within, "Within \nsubjects", "Between\nsubjects")) |> 
+within <- dat |> mutate(is_within=ifelse(is_within, "Within \nparticipants", "Between\nparticipants")) |> 
   count(is_within, sub_rep, .drop=F) |> ggplot(aes(x=is_within, y=n, fill=sub_rep))+
@@
 We first ran models using all of the original-replication pairs (N=176), but without original effect size and original $p$ value as predictors, as they were uncodable for some pairs.
-We next ran models including all predictors, but on only the subset of data where all predictors were available (N=136).
+We next ran models including all predictors, but on only the subset of data where all predictors were available (N=112).
 
-Coefficient estimates from the two models predicting the subjective replication scores are shown in Figure \ref{fig:mod-results}; see Supplement for full model results.
+Coefficient estimates from the two models predicting the subjective replication scores are shown in Figure \ref{fig:mod-results}.
 Due to a large number of predictors coupled with a small and noisy dataset, there is much uncertainty around the coefficients even with strong regularization.
@@
 
-Within-subjects designs stand out as the strongest correlate of replicability in the model with all the data (`r within_1`).
-In the model with all predictors, but less data, within-subjects designs remain strong (`r within_3`), and standardized effect size is also substantially related to subjective replication score (`r smd_3`).
-Both effects are robust to a sensitivity analysis including only studies with close replications and matching statistical tests (within-subjects `r within_sens`; effect size `r smd_sens`).
+Within-participants designs stand out as the strongest correlate of replicability in the model with all the data (`r within_1`).
+In the model with all predictors, but less data, within-participants designs remain strong (`r within_3`), and standardized effect size is also substantially related to subjective replication score (`r smd_3`).
+Both effects are robust to a sensitivity analysis including only studies with close replications and matching statistical tests (within-participants `r within_sens`; effect size `r smd_sens`).
 
-We also ran models predicting our secondary outcome measures: whether the replication effect was within the prediction interval of the original effect and what the p-original was between the replication and original.
+We also ran models predicting our secondary outcome measures: whether the replication effect was within the prediction interval of the original effect and what the $p$-original was between the replication and original.
 Both these models had more uncertain estimates.
-While the credible intervals were wide, the general patterns of predictor direction and relative strength were similar to the subjective replication models (see Supplement).
-The strongest predictors for prediction interval were still within-subjects designs (`r within_2`) and studies with larger effect sizes (`r smd_2`).
+While the credible intervals were wide, the general patterns of predictor direction and relative strength were similar to the subjective replication models (see Supplement for coefficients from all models).
+The strongest predictors for prediction interval were still within-participants designs (`r within_2`) and studies with larger effect sizes (`r smd_2`).
 
@@
     mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |>  filter(Term!="Intercept") |> 
-    mutate(Term=factor(Term, levels=c("subfieldsocial", "subfieldother_psych", "subfieldnon_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "z_pub_year", "z_log_trials", "z_log_sample", "z_log_ratio_ss","z_log_p","z_target_d_calc"), labels=c("Social", "Other psych", "Non psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log n trials", "Log original sample size", "Log rep/orig sample", "P-value", "Original effect size")))
+    mutate(Term=factor(Term, levels=c("subfieldsocial", "subfieldother_psych", "subfieldnon_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "z_pub_year", "z_log_trials", "z_log_sample", "z_log_ratio_ss","z_log_p","z_target_d_calc"), labels=c("Social", "Other psych", "Non psych", "Within participants", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log n trials", "Log original sample size", "Log rep/orig sample", "P-value", "Original effect size")))
 }
@@
 In line with previous results, we found a `r round(pluck(sub_rep_rate,1))`% replication rate, with some studies showing effect sizes similar to the original and others much smaller.
-Within-subjects designs, work in the subfield of cognitive psychology, and the original and replication both using online samples stood out as the strongest correlates of replication success.
+Within-participants designs, work in the subfield of cognitive psychology, and the original and replication both using online samples stood out as the strongest correlates of replication success.
 As many of these predictors interrelate with one another, we ran regularized regressions with all the predictors at once.
-Due to our small sample, model estimates were uncertain, but within-subjects designs and large original effect sizes were the strongest predictors.
+Due to our small sample, model estimates were uncertain, but within-participants designs and large original effect sizes were the strongest predictors.
 
@@
 Some of the correlates are most easily interpreted as being about the original study, and others reflect the closeness of the replication to the original.
-For instance, while within-subjects designs are more likely to replicate than between-subjects designs, this predictor could also be related to the types of experiments that tend to be run in each design.
-Given the strong relationship of this factor to replicability, slightly more skepticism and critical reading of between-subjects designs may be warranted, but this correlation, by itself, does not mean scientists should prefer within-subjects designs.
+For instance, while within-participants designs are more likely to replicate than between-participants designs, this predictor could also be related to the types of experiments that tend to be run in each design.
+Given the strong relationship of this factor to replicability, slightly more skepticism and critical reading of between-participants designs may be warranted, but this correlation, by itself, does not mean scientists should prefer within-participants designs.
 
@@
 Students were encouraged to do experimental replications, but some students chose to replicate correlational outcomes or do computational reproducibility projects instead.
-We cannot include the full student reports for confidentiality reasons, but we include an example as well as the template given to students at TODO example and template.
+We cannot include the full student reports for confidentiality reasons, but we include some example reports we have permission to share and the template given to students at TOOD OSF REPO.
 
@@
 
-Four of these replication projects were included in RP:P, and 10 of them were previously reported in @hawkins2018.
+Four of the replication projects were included in RP:P, and 10 were previously reported in @hawkins2018 (which reported 11 student replications from the 2015-2016 class, one of those was excluded from the current sample for being non-experimental).
 
@@
 This subjective replication outcome was chosen because it already existed, could be applied to all projects (regardless of type and detail of statistical reporting), and did not rely solely on one statistical measure.
-As a complement, we also identified a "key" statistical test for each paper (see below for details), and if possible, computed p-original and prediction interval at this statistic, following @mathur2020.
-p-original was a continuous measure of the p-value on the hypothesis that the original and replication samples come from the same distribution.
+As a complement, we also identified a "key" statistical test for each paper (see below for details), and if possible, computed $p$-original and prediction interval at this statistic, following @mathur2020.
+$p$-original was a continuous measure of the $p$ value on the hypothesis that the original and replication samples come from the same distribution.
 Prediction interval was a binary measure of whether the replication outcome fell within the prediction interval of the original outcome measure.
@@
 
-We coded the number of subjects, post-exclusions.
-We coded whether a study had a between-subjects, within-subjects, or mixed design; for the analysis, mixed studies were counted as within-subjects designs.
-In the analysis, we used a log-scale for number of subjects and numbers of trials.
+We coded the number of participants, post-exclusions.
+We coded whether a study had a between-participants, within-participants, or mixed design; for the analysis, mixed studies were counted as within-participants designs.
+In the analysis, we used a log-scale for number of participants and numbers of trials.
 
@@
 ### Determination and coding of key statistical measure
-For each study pair, we used one key measure of interest for which we calculated the predictor variables of p-value and effect size and the statistical outcome measures p_original and prediction interval.
+For each study pair, we used one key measure of interest for which we calculated the predictor variables of $p$ value and effect size and the statistical outcome measures $p$-original and prediction interval.
 If the student specified a single key measure of interest and this was a measure that was reported in both the original paper and replication, we used that measure.
@@
 
-We then calculated p values, effect sizes, p-original, and prediction intervals.
+We then calculated $p$ values, effect sizes, $p$-original, and prediction intervals.
 We choose to recalculate p values and effect sizes from the means or test statistic rather than use reported measures when possible because we thought this would be more reliable and transparent.
 The means and test statistics are more likely to have been outputted programmatically and copied directly into the text.
-In contrast, p-values are often reported as <.001 rather than as a point value, and effect size derivations may be error prone.
+In contrast, $p$ values are often reported as <.001 rather than as a point value, and effect size derivations may be error prone.
 By recording the raw statistics we used and using our available code to calculate other measures, we are transparent, as the test statistics can be searched for in the papers, and all processing is documented in code.
 
-In some cases, p-values or effect sizes were not calculable either due to insufficient reporting (ex.
-reporting a p-value but no other statistics from a test) or key measures where p-values and effect sizes did not apply (ex.
+In some cases, $p$ values or effect sizes were not calculable either due to insufficient reporting (ex.
+reporting a $p$ value but no other statistics from a test) or key measures where $p$ values and effect sizes did not apply (ex.
 PCA as measure of interest).
-Where studies reported beta estimates and standard errors or proportions, standardized effects sizes are not an applicable measure, but we were still able to calculate p-original and prediction interval.
+Where studies reported beta estimates and standard errors or proportions, standardized effects sizes are not an applicable measure, but we were still able to calculate $p$-original and prediction interval.
 
@@
 
-In regression analyses, we used standardized mean difference and log p-value as predictors.
+In regression analyses, we used standardized mean difference and log $p$ value as predictors.
 
 ## Modelling
-
-TODO citation around horseshoe prior
 
@@
 We ran a model predicting the subjective replication score on the basis of demographic and experimental predictors on the entire dataset.
-We ran two models predicting p_original and prediction interval from demographic and experimental predictors on the subset of data where we had p_original and prediction intervals.
-Then, on the smaller subset of the data where we had effect sizes and p-values, we re-ran these three models with those as additional predictor variables.
+We ran two models predicting $p$-original and prediction interval from demographic and experimental predictors on the subset of data where we had $p$-original and prediction intervals.
+Then, on the smaller subset of the data where we had effect sizes and $p$ values, we re-ran these three models with those as additional predictor variables.
 
 The subjective replication scores were coded on [0, .25, .5, .75, 1], and we ramapped these to 1-5 to run an ordinal regression predicting replication score.
-We ran logistic regressions predicting prediction interval and linear regressions predicting p_original.
+We ran logistic regressions predicting prediction interval and linear regressions predicting $p$-original.
 
@@
 
-Acknowledge people here. `{-}` useful to not number this section.
+TODO We are grateful to the students in PSYCH 254 and PSYCH 251 for conducting the replication projects included here.
+We thank Ben Prystawski and the FriSem audience for feedback on earlier versions of this work.
+TODO GRANTS??
 

### 2023-07-10 paper/manuscript.tex
new draft

@@
 Yet in psychology, some prominent findings have failed to replicate, and large-scale studies suggest replicability issues are widespread.
-The identification of predictors of replication success is limited by the difficulty of conducting large samples of indepedendent replication experiments, however: most investigations re-analyse the same set of \textasciitilde170 replications.
+The identification of predictors of replication success is limited by the difficulty of conducting large samples of independent replication experiments, however: most investigations re-analyse the same set of \textasciitilde170 replications.
 We introduce a new dataset of 176 replications from students in a graduate-level methods course.
-Replication results were judged to be successful in 49\% of replications; of the 136 where comparable effect sizes could be computed, 45\% had point estimates within the prediction interval of the original outcome.
+Replication results were judged to be successful in 49\% of replications; of the 136 where comparable effect sizes could be computed, 46\% had point estimates within the prediction interval of the original outcome.
 Larger original effect sizes and within-participants designs were especially related to replication success.
-Or results indicate that, consistent with prior reports, the robustness of the psychology literature is low enough to limit cumulative progress by student investigators.
+Our results indicate that, consistent with prior reports, the robustness of the psychology literature is low enough to limit cumulative progress by student investigators.
 
@@
 The first of these, RP:P, sampled roughly 100 studies from articles published in three top psychology journals in 2008 and distributed the studies across participating labs, finding an overall replication rate of around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}).
-The followup Many Labs Studies investigated heterogeneity using short target studies that each compared two conditions.
-These study designs were not representative of the psychology literature as a whole, and due to the of measuring heterogeneity, they had large overall samples across multiple sites.
+The followup Many Labs studies investigated heterogeneity using short target studies that each compared two conditions.
+These study designs were not representative of the psychology literature as a whole, and due to the goal of measuring heterogeneity, they had large overall samples across multiple sites.
 Across Many Labs 1--3, only 29 of 51 target effects (57\%) replicated (\protect\hyperlink{ref-klein2014}{Klein et al.
@@
 In no case were studies randomly sampled from the literature; instead replication projects sampled from specific journals and adjusted the sample for feasibility concerns.
-These reasonable decisions further undermine interpretation of the results from these studies as representing the proportion of true findings in the psychology literature as a whole.
+These reasonable decisions further undermine the interpretation of the results from these studies as representing the proportion of true findings in the psychology literature as a whole.
 
@@
 Through this lens, RP:P estimated the rate at which findings from relatively simple experiments published in a few well-known journals at a particular time could be replicated in a typical psychology lab.
-Many Labs estimated at which well-known, two-condition findings replicate in very large samples.
+Many Labs estimated the rate at which well-known, two-condition findings replicate in very large samples.
 Camerer et al.
@@
 
-In search of such features, RP:P examined correlates of replicability in the RP:P sample and found that studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate.
+In search of such features, RP:P examined correlates of replicability in the RP:P sample and found that studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller \(p\) values were more likely to replicate.
 Using these same data combined with a few other smaller samples, Altmejd et al.
@@
 These approaches are fundamentally limited by the available data.
-Large-scale replications are arduous and expensive to run, so only a few large-scale replication datasets exist, and most analyses analyses draw heavily on same small set of data points.
+Large-scale replications are arduous and expensive to run, so only a few large-scale replication datasets exist, and most analyses draw heavily on same small set of data points.
 In particular, the RP:P dataset is much discussed and reanalyzed (\protect\hyperlink{ref-anderson2016}{Anderson et al.
@@
 2016}) -- to the point that much of what we think we know about replicability may be over-fit to the 100 studies included in RP:P.
-More replication data is needed to identify markers of replicability and targets for potential future experimental approaches.
 
-Further, none of these studies focused on features of experimental design, such as within-subjects designs or the use of repeated measures.
+Further, none of these studies focused on features of experimental design, such as within-participants designs or the use of repeated measures.
 There has been speculation that both of these factors should be linked to increased replicability due to their role in enabling increased statistical precision.
-Within-subjects designs lead to more precise experimental estimates by allowing the estimation of correlated person-level variation across conditions; repeated measures allow for more precise estimation by averaging out measurement error.
+Within-participants designs lead to more precise experimental estimates by allowing the estimation of correlated person-level variation across conditions; repeated measures allow for more precise estimation by averaging out measurement error.
 Both are often recommended by methodologists as part of good measurement practices, at least when they are feasible (\protect\hyperlink{ref-greenwald1976}{Greenwald 1976}, \protect\hyperlink{ref-rosenthal2008}{Rosenthal \& Rosnow 2008}, \protect\hyperlink{ref-frank2023}{Frank et al.
@@
 In some cases the budget limited the number of participants who could be recruited, occasionally below what the original study included or what power analyses suggested.
+The replications had a median post-exclusion sample size that was 86\% of the original sample size (interquartile range 41\%-105\%)\footnote{Replications had a median of 59 participants (interquartile range: 31 - 124), while original studies had a median of 101 participants (interquartile range: 40 - 180).}.
 In nearly all cases, replications were conducted online, with recruitment from Amazon Mechanical Turk (the default from 2011 to 2020) or Prolific (the default from 2021 -- 2022).
@@
 \begin{figure}[ht]
-\includegraphics[width=1\linewidth,height=0.25\textheight]{manuscript_files/figure-latex/smd-1} \caption{Relationship between effect size of the original study, effect size of the replication study, and subjective replication success rating, for those studies where effect size was applicable.}\label{fig:smd}
+\includegraphics[width=1\linewidth,height=0.25\textheight]{manuscript_files/figure-latex/smd-1} \caption{Relationship between effect size of the original study, effect size of the replication study, and subjective replication success rating, for those studies where effect size was applicable (N=112).}\label{fig:smd}
 \end{figure}
@@
 2020}).
-If we assume that the level of heterogeneity in hypothetical multi-site replications of these effects is the same as the average level heterogeneity found in prior multi-site replications in psychology {[}\(\tau=.21\) in units of standardized mean difference; Olsson-Collentine et al.
-(\protect\hyperlink{ref-olsson2020}{2020}){]}, then 64.3\% (72/112) of replication effect sizes are distributionally consistent with the original effect size.
+As a test of sensitivity to heterogeneity, we assumed that the level of heterogeneity in hypothetical multi-site replications of our sampled articles was the same as the average level heterogeneity found by (\protect\hyperlink{ref-olssen2020}{\textbf{olssen2020?}}) in prior multi-site replications in psychology (\(\tau=.21\) in units of standardized mean difference).
+Under this assumption, 64\% (72/112) of replication effect sizes are distributionally consistent with the original effect size.
 However, more work on understanding heterogeneity is needed to understand what levels of heterogeneity to expect across different implementations of the same experiment, and how considerations of heterogeneity should impact interpretations of both novel results and replication results.
@@
 \midrule
-Within subjects & 0.333 & 0.000\\
+Within participants & 0.333 & 0.000\\
 Log n trials & 0.182 & 0.015\\
@@
 Both social and cognitive psychology studies were well represented in the replication sample, and the cognitive psychology studies replicated 2.45 times as often as social psychology studies.
-Within and between subjects designs were both common, and within-subjects designs replicated 3.35 times as much.
+Within and between participants designs were both common, and within-participants designs replicated 3.35 times as much as between-participants designs.
 Studies with multiple vignettes replicated 2.62 times as often as single vignetted studies.
@@
 We first ran models using all of the original-replication pairs (N=176), but without original effect size and original \(p\) value as predictors, as they were uncodable for some pairs.
-We next ran models including all predictors, but on only the subset of data where all predictors were available (N=136).
+We next ran models including all predictors, but on only the subset of data where all predictors were available (N=112).
 
-Coefficient estimates from the two models predicting the subjective replication scores are shown in Figure \ref{fig:mod-results}; see Supplement for full model results.
+Coefficient estimates from the two models predicting the subjective replication scores are shown in Figure \ref{fig:mod-results}.
 Due to a large number of predictors coupled with a small and noisy dataset, there is much uncertainty around the coefficients even with strong regularization.
@@
 
-Within-subjects designs stand out as the strongest correlate of replicability in the model with all the data (0.53, CrI= {[}0, 2{]}).
-In the model with all predictors, but less data, within-subjects designs remain strong (0.66, CrI= {[}-0.04, 2.37{]}), and standardized effect size is also substantially related to subjective replication score (0.65, CrI= {[}0.27, 2.81{]}).
-Both effects are robust to a sensitivity analysis including only studies with close replications and matching statistical tests (within-subjects 0.87, CrI= {[}-0.01, 3.33{]}; effect size 1.05, CrI= {[}0.76, 4.88{]}).
+Within-participants designs stand out as the strongest correlate of replicability in the model with all the data (0.53, CrI= {[}0, 2{]}).
+In the model with all predictors, but less data, within-participants designs remain strong (0.66, CrI= {[}-0.04, 2.37{]}), and standardized effect size is also substantially related to subjective replication score (0.65, CrI= {[}0.27, 2.81{]}).
+Both effects are robust to a sensitivity analysis including only studies with close replications and matching statistical tests (within-participants 0.87, CrI= {[}-0.01, 3.33{]}; effect size 1.05, CrI= {[}0.76, 4.88{]}).
 
-We also ran models predicting our secondary outcome measures: whether the replication effect was within the prediction interval of the original effect and what the p-original was between the replication and original.
+We also ran models predicting our secondary outcome measures: whether the replication effect was within the prediction interval of the original effect and what the \(p\)-original was between the replication and original.
 Both these models had more uncertain estimates.
-While the credible intervals were wide, the general patterns of predictor direction and relative strength were similar to the subjective replication models (see Supplement).
-The strongest predictors for prediction interval were still within-subjects designs (0.62, CrI= {[}-0.18, 2.01{]}) and studies with larger effect sizes (0.3, CrI= {[}-0.29, 0.94{]}).
+While the credible intervals were wide, the general patterns of predictor direction and relative strength were similar to the subjective replication models (see Supplement for coefficients from all models).
+The strongest predictors for prediction interval were still within-participants designs (0.62, CrI= {[}-0.18, 2.01{]}) and studies with larger effect sizes (0.3, CrI= {[}-0.29, 0.94{]}).
 
@@
 In line with previous results, we found a 49\% replication rate, with some studies showing effect sizes similar to the original and others much smaller.
-Within-subjects designs, work in the subfield of cognitive psychology, and the original and replication both using online samples stood out as the strongest correlates of replication success.
+Within-participants designs, work in the subfield of cognitive psychology, and the original and replication both using online samples stood out as the strongest correlates of replication success.
 As many of these predictors interrelate with one another, we ran regularized regressions with all the predictors at once.
-Due to our small sample, model estimates were uncertain, but within-subjects designs and large original effect sizes were the strongest predictors.
+Due to our small sample, model estimates were uncertain, but within-participants designs and large original effect sizes were the strongest predictors.
 
@@
 
-Four of these replication projects were included in RP:P, and 10 of them were previously reported in Hawkins et al. (\protect\hyperlink{ref-hawkins2018}{2018}).
+Four of the replication projects were included in RP:P, and 10 were previously reported in Hawkins et al.
+(\protect\hyperlink{ref-hawkins2018}{2018}) (which reported 11 student replications from the 2015-2016 class, one of those was excluded from the current sample for being non-experimental).
 
@@
 This subjective replication outcome was chosen because it already existed, could be applied to all projects (regardless of type and detail of statistical reporting), and did not rely solely on one statistical measure.
-As a complement, we also identified a ``key'' statistical test for each paper (see below for details), and if possible, computed p-original and prediction interval at this statistic, following Mathur \& VanderWeele (\protect\hyperlink{ref-mathur2020}{2020}).
-p-original was a continuous measure of the p-value on the hypothesis that the original and replication samples come from the same distribution.
+As a complement, we also identified a ``key'' statistical test for each paper (see below for details), and if possible, computed \(p\)-original and prediction interval at this statistic, following Mathur \& VanderWeele (\protect\hyperlink{ref-mathur2020}{2020}).
+\(p\)-original was a continuous measure of the \(p\) value on the hypothesis that the original and replication samples come from the same distribution.
 Prediction interval was a binary measure of whether the replication outcome fell within the prediction interval of the original outcome measure.
@@
 
-For each study pair, we used one key measure of interest for which we calculated the predictor variables of p-value and effect size and the statistical outcome measures p\_original and prediction interval.
+For each study pair, we used one key measure of interest for which we calculated the predictor variables of \(p\) value and effect size and the statistical outcome measures \(p\)-original and prediction interval.
 If the student specified a single key measure of interest and this was a measure that was reported in both the original paper and replication, we used that measure.
@@
 
-We then calculated p values, effect sizes, p-original, and prediction intervals.
+We then calculated \(p\) values, effect sizes, \(p\)-original, and prediction intervals.
 We choose to recalculate p values and effect sizes from the means or test statistic rather than use reported measures when possible because we thought this would be more reliable and transparent.
 The means and test statistics are more likely to have been outputted programmatically and copied directly into the text.
-In contrast, p-values are often reported as \textless.001 rather than as a point value, and effect size derivations may be error prone.
+In contrast, \(p\) values are often reported as \textless.001 rather than as a point value, and effect size derivations may be error prone.
 By recording the raw statistics we used and using our available code to calculate other measures, we are transparent, as the test statistics can be searched for in the papers, and all processing is documented in code.
 
-In some cases, p-values or effect sizes were not calculable either due to insufficient reporting (ex.
-reporting a p-value but no other statistics from a test) or key measures where p-values and effect sizes did not apply (ex.
+In some cases, \(p\) values or effect sizes were not calculable either due to insufficient reporting (ex.
+reporting a \(p\) value but no other statistics from a test) or key measures where \(p\) values and effect sizes did not apply (ex.
 PCA as measure of interest).
-Where studies reported beta estimates and standard errors or proportions, standardized effects sizes are not an applicable measure, but we were still able to calculate p-original and prediction interval.
+Where studies reported beta estimates and standard errors or proportions, standardized effects sizes are not an applicable measure, but we were still able to calculate \(p\)-original and prediction interval.
 
@@
 
-In regression analyses, we used standardized mean difference and log p-value as predictors.
+In regression analyses, we used standardized mean difference and log \(p\) value as predictors.
 
@@
 \subsection{Modelling}\label{modelling}}
-
-TODO citation around horseshoe prior
 
@@
 We ran a model predicting the subjective replication score on the basis of demographic and experimental predictors on the entire dataset.
-We ran two models predicting p\_original and prediction interval from demographic and experimental predictors on the subset of data where we had p\_original and prediction intervals.
-Then, on the smaller subset of the data where we had effect sizes and p-values, we re-ran these three models with those as additional predictor variables.
+We ran two models predicting \(p\)-original and prediction interval from demographic and experimental predictors on the subset of data where we had \(p\)-original and prediction intervals.
+Then, on the smaller subset of the data where we had effect sizes and \(p\) values, we re-ran these three models with those as additional predictor variables.
 
 The subjective replication scores were coded on {[}0, .25, .5, .75, 1{]}, and we ramapped these to 1-5 to run an ordinal regression predicting replication score.
-We ran logistic regressions predicting prediction interval and linear regressions predicting p\_original.
+We ran logistic regressions predicting prediction interval and linear regressions predicting \(p\)-original.
 
@@
 
-Acknowledge people here. \texttt{\{-\}} useful to not number this section.
+TODO We are grateful to the students in PSYCH 254 and PSYCH 251 for conducting the replication projects included here.
+We thank Ben Prystawski and the FriSem audience for feedback on earlier versions of this work.
+TODO GRANTS??
 

### 2023-07-10 paper/supplement.Rmd
new draft

@@
     mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |>  filter(Term!="Intercept") |> 
-    mutate(Term=factor(Term, levels=c("subfieldsocial", "subfieldother_psych", "subfieldnon_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "z_pub_year", "z_log_trials", "z_log_sample", "z_log_ratio_ss","z_log_p","z_target_d_calc"), labels=c("Social", "Other psych", "Non psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rep/orig sample", "P-value", "Original effect size")))
+    mutate(Term=factor(Term, levels=c("subfieldsocial", "subfieldother_psych", "subfieldnon_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "z_pub_year", "z_log_trials", "z_log_sample", "z_log_ratio_ss","z_log_p","z_target_d_calc"), labels=c("Social", "Other psych", "Non psych", "Within participants", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rep/orig sample", "P-value", "Original effect size")))
 }

### 2023-07-14 paper/manuscript.Rmd
updating statistical reporting

@@
 We introduce a new dataset of 176 replications from students in a graduate-level methods course.
-Replication results were judged to be successful in 49% of replications; of the 136 where comparable effect sizes could be computed, 46% had point estimates within the prediction interval of the original outcome.
+Replication results were judged to be successful in 49% of replications; of the 136 where effect sizes could be numerically compared, 46% had point estimates within the prediction interval of the original outcome (versus the expected 95%).
 Larger original effect sizes and within-participants designs were especially related to replication success.
@@
 Despite variation in the methods and outcomes used by large-scale replication studies, they are often aggregated together in analyses looking at the predictability of replication success.
-Prediction markets and elicitations have established that people can predict what studies will replicate above chance [@hoogeveen2019;@dreber2015; @forsell2019;@camerer2018], but have not identified concrete predictors that differentiate replications from non-replications.
+Prediction markets and elicitations have established that people can predict above chance what studies will replicate [@hoogeveen2019;@dreber2015; @forsell2019;@camerer2018], but have not identified concrete predictors that differentiate replications from non-replications.
 Machine learning approaches trained on the available replications are also above chance at predicting replication success [@yang2020; @youyou2023], though again the precise features relating to success are unclear.
@@
 Some multi-site replication projects have found heterogeneity in effect sizes across replication sites [@ebersole2020; @klein2018; @olsson2020].
-As a test of sensitivity to heterogeneity, we assumed that the level of heterogeneity in hypothetical multi-site replications of our sampled articles was the same as the average level heterogeneity found by @olssen2020 in prior multi-site replications in psychology ($\tau=.21$ in units of standardized mean difference).
+As a test of sensitivity to heterogeneity, we assumed that the level of heterogeneity in hypothetical multi-site replications of our sampled articles was the same as the average level heterogeneity found by @olsson2020 in prior multi-site replications in psychology ($\tau=.21$ in units of standardized mean difference).
 Under this assumption, `r round(tau_pct)`% (`r tau_predIntcount`/`r tau_predInttotal`) of replication effect sizes are distributionally consistent with the original effect size.
@@
          p = sapply(preds, function(x) sub_cor(x, stat = "p"))) |> 
-  mutate(Predictors=factor(preds, levels=c("social", "other_psych", "non_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "pub_year", "log_trials", "log_sample", "log_ratio_ss"), labels=c("Social", "Other psych", "Non psych", "Within participants", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log n trials", "Log original sample size", "Log rep/orig sample"))) |> arrange(desc(r)) |> select(Predictors, r, p)
+  mutate(Predictors=factor(preds, levels=c("social", "other_psych", "non_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "pub_year", "log_trials", "log_sample", "log_ratio_ss"), labels=c("Social psychology (versus cognitive psych)", "Other psychology (versus cognitive psych)", "Non psychology (versus cogntive psych)", "Within participants design (versus between participants)", "Single vignette (versus multiple items/inductions per condition)", "Switch to online for replication (versus same modality for original and replication)", "Open data", "Open materials", "Stanford affiliation of original authors at time of replication", "Publication year", "Log number of  trials", "Log original sample size", "Log ratio between replication and original sample sizes"))) |> arrange(desc(r)) |> select(r, p, Predictors)
 
 library(kableExtra)
-knitr::kable(cors, digits = 3, align='rcc',format="latex", position="!h", caption="The correlation between each individual predictor and the subjective replication score.
+knitr::kable(cors, digits = 3, align='ccl',format="latex", position="!h", caption="The correlation between each individual predictor and the subjective replication score.
 For subfield, cognitive psychology is treated as the baseline condition.
-See Methods for how these variables were coded.", booktabs=TRUE) |> kable_styling(full_width=F, font_size=10)
+See Methods for how these variables were coded.", booktabs=TRUE, linesep="") |> kable_styling(full_width=F, font_size=10)
+
+```
+
+```{r, include=F}
+
+ within <- glm(sub_rep ~ is_within, data=for_cor, family=binomial)$coefficient[2] |> exp() 
+ vignette <- glm(sub_rep ~ single_vignette, data=for_cor, family=binomial)$coefficient[2] |> exp()
+
+  subfield <- glm(sub_rep ~ subfield, data=for_cor |> filter(subfield %in% c("social", "cognitive")), family=binomial)$coefficient[2] |> exp()
 
@@
 
- within <- glm(sub_rep ~ is_within, data=for_cor, family=binomial)$coefficient[2] |> exp() 
- vignette <- glm(sub_rep ~ single_vignette, data=for_cor, family=binomial)$coefficient[2] |> exp()
+within <- for_cor |> group_by(is_within) |> summarize(avg=mean(sub_rep)*100)
 
-  subfield <- glm(sub_rep ~ subfield, data=for_cor |> filter(subfield %in% c("social", "cognitive")), family=binomial)$coefficient[2] |> exp()
+cog <- for_cor |> group_by(subfield) |> summarize(avg=mean(sub_rep)*100)
+vignette <- for_cor |> group_by(single_vignette) |> summarize(avg=mean(sub_rep)*100)
 
@@
 Distributions of study outcomes across some of these properties are shown in Figure \ref{fig:predictors-graph}.
-To quantify the effects of these single predictors, we ran logistic models predicting the subjective replication score (on a 0--1 scale) as a function of the single predictor, and exponentiated the coefficient to obtain an odds ratio.
-Both social and cognitive psychology studies were well represented in the replication sample, and the cognitive psychology studies replicated `r round(1/subfield, 2)` times as often as social psychology studies.
-Within and between participants designs were both common, and within-participants designs replicated `r within |> round(2)` times as much as between-participants designs.
-Studies with multiple vignettes replicated `r round(1/vignette, 2)` times as often as single vignetted studies.
+Both social and cognitive psychology studies were well represented in the replication sample, and the cognitive psychology studies replicated more often than social psychology studies (`r pluck(cog,2,1) |> round()`% versus `r pluck(cog,2,4) |> round()`%).
+Within and between participants designs were both common, and within-participants designs replicated more often than between-participants designs (`r pluck(within,2,2) |> round()`% versus `r pluck(within,2,1) |> round()`%).
+Studies with multiple vignettes replicated more often than single vignetted studies (`r pluck(vignette,2,1) |> round()`% versus `r pluck(vignette,2,2) |> round()`%).
 However, there were strong correlations among these experimental features as well as between these experimental features and specific subfields.
@@
 do_estimates <- function(model, variable){
-  summary(model)$fixed |> as_tibble(rownames="var") |> filter(var==variable)|> mutate(text=str_c(round(Est.Error,2), ", CrI= [", round(`l-95% CI`,2),", ", round(`u-95% CI`,2),"]")) |> pull(text)
+  summary(model)$fixed |> as_tibble(rownames="var") |> filter(var==variable)|> mutate(text=str_c("$\\beta = ", round(Est.Error,2), ",  95\\% \\mathrm{CrI} = [", round(`l-95% CI`,2),", ", round(`u-95% CI`,2),"]$")) |> pull(text)
 }
@@
 While a number of features show individual correlations with the subjective replication score, many correlate with one another.
-To determine which predictors were the strongest, we ran a series of pre-registered Bayesian regression models regularized using a horseshoe shrinkage prior [@carvalho09].
+To determine which predictors were the strongest, we ran a series of pre-registered Bayesian regression models using an ordinal link function and  regularized using a horseshoe shrinkage prior [@carvalho09].
 We first ran models using all of the original-replication pairs (N=176), but without original effect size and original $p$ value as predictors, as they were uncodable for some pairs.
@@
 
-Coefficient estimates from the two models predicting the subjective replication scores are shown in Figure \ref{fig:mod-results}.
+Coefficient estimates from the two ordinal models predicting the subjective replication scores are shown in Figure \ref{fig:mod-results}.
 Due to a large number of predictors coupled with a small and noisy dataset, there is much uncertainty around the coefficients even with strong regularization.
@@
 
-We also ran models predicting our secondary outcome measures: whether the replication effect was within the prediction interval of the original effect and what the $p$-original was between the replication and original.
+We also ran models predicting our secondary outcome measures: a logistic model predicting whether the replication effect was within the prediction interval of the original effect, and a linear model predicting what the $p$-original was between the replication and original.
 Both these models had more uncertain estimates.
@@
 
-Due to the monotonic missingness of the data, we had more predictor variables and outcome variables for some original-replication pairs than for others.
+All original-replication pairs (except for one) had codable demographic and experimental features, while fewer pairs had codable effect sizes on some consistent scale, and fewer still had codable p-values and SMD effect sizes.
+Thus, we had more predictor variables and outcome variables for some original-replication pairs than for others, but which variables were codable was monotonic.
 To take full advantage of the data, we ran a series of models, with some models having fewer predictors, but more data, and others having more predictors, but less data.
@@
 We ran a model predicting the subjective replication score on the basis of demographic and experimental predictors on the entire dataset.
-We ran two models predicting $p$-original and prediction interval from demographic and experimental predictors on the subset of data where we had $p$-original and prediction intervals.
+We ran two models predicting $p$-original and predicting whether the replication was in the prediction interval from demographic and experimental predictors on the subset of data where we had $p$-original and prediction intervals.
 Then, on the smaller subset of the data where we had effect sizes and $p$ values, we re-ran these three models with those as additional predictor variables.

### 2023-07-14 paper/manuscript.tex
updating statistical reporting

@@
 We introduce a new dataset of 176 replications from students in a graduate-level methods course.
-Replication results were judged to be successful in 49\% of replications; of the 136 where comparable effect sizes could be computed, 46\% had point estimates within the prediction interval of the original outcome.
+Replication results were judged to be successful in 49\% of replications; of the 136 where effect sizes could be numerically compared, 46\% had point estimates within the prediction interval of the original outcome (versus the expected 95\%).
 Larger original effect sizes and within-participants designs were especially related to replication success.
@@
 Despite variation in the methods and outcomes used by large-scale replication studies, they are often aggregated together in analyses looking at the predictability of replication success.
-Prediction markets and elicitations have established that people can predict what studies will replicate above chance (\protect\hyperlink{ref-dreber2015}{Dreber et al.
+Prediction markets and elicitations have established that people can predict above chance what studies will replicate (\protect\hyperlink{ref-dreber2015}{Dreber et al.
 2015}, \protect\hyperlink{ref-camerer2018}{Camerer et al.
@@
 2020}).
-As a test of sensitivity to heterogeneity, we assumed that the level of heterogeneity in hypothetical multi-site replications of our sampled articles was the same as the average level heterogeneity found by (\protect\hyperlink{ref-olssen2020}{\textbf{olssen2020?}}) in prior multi-site replications in psychology (\(\tau=.21\) in units of standardized mean difference).
+As a test of sensitivity to heterogeneity, we assumed that the level of heterogeneity in hypothetical multi-site replications of our sampled articles was the same as the average level heterogeneity found by Olsson-Collentine et al.
+(\protect\hyperlink{ref-olsson2020}{2020}) in prior multi-site replications in psychology (\(\tau=.21\) in units of standardized mean difference).
 Under this assumption, 64\% (72/112) of replication effect sizes are distributionally consistent with the original effect size.
@@
 \fontsize{10}{12}\selectfont
-\begin{tabular}[t]{rcc}
+\begin{tabular}[t]{ccl}
 \toprule
-Predictors & r & p\\
+r & p & Predictors\\
 \midrule
-Within participants & 0.333 & 0.000\\
-Log n trials & 0.182 & 0.015\\
-Open data & 0.150 & 0.047\\
-Non psych & 0.080 & 0.294\\
-Other psych & 0.075 & 0.322\\
-\addlinespace
-Publication year & 0.064 & 0.399\\
-Open materials & 0.002 & 0.979\\
-Stanford & -0.027 & 0.725\\
-Log rep/orig sample & -0.047 & 0.536\\
-Log original sample size & -0.108 & 0.155\\
-\addlinespace
-Switch to online & -0.158 & 0.037\\
-Social & -0.246 & 0.001\\
-Single vignette & -0.267 & 0.000\\
+0.333 & 0.000 & Within participants design (versus between participants)\\
+0.182 & 0.015 & Log number of  trials\\
+0.150 & 0.047 & Open data\\
+0.080 & 0.294 & Non psychology (versus cogntive psych)\\
+0.075 & 0.322 & Other psychology (versus cognitive psych)\\
+0.064 & 0.399 & Publication year\\
+0.002 & 0.979 & Open materials\\
+-0.027 & 0.725 & Stanford affiliation of original authors at time of replication\\
+-0.047 & 0.536 & Log ratio between replication and original sample sizes\\
+-0.108 & 0.155 & Log original sample size\\
+-0.158 & 0.037 & Switch to online for replication (versus same modality for original and replication)\\
+-0.246 & 0.001 & Social psychology (versus cognitive psych)\\
+-0.267 & 0.000 & Single vignette (versus multiple items/inductions per condition)\\
 \bottomrule
@@
 Distributions of study outcomes across some of these properties are shown in Figure \ref{fig:predictors-graph}.
-To quantify the effects of these single predictors, we ran logistic models predicting the subjective replication score (on a 0--1 scale) as a function of the single predictor, and exponentiated the coefficient to obtain an odds ratio.
-Both social and cognitive psychology studies were well represented in the replication sample, and the cognitive psychology studies replicated 2.45 times as often as social psychology studies.
-Within and between participants designs were both common, and within-participants designs replicated 3.35 times as much as between-participants designs.
-Studies with multiple vignettes replicated 2.62 times as often as single vignetted studies.
+Both social and cognitive psychology studies were well represented in the replication sample, and the cognitive psychology studies replicated more often than social psychology studies (58\% versus 36\%).
+Within and between participants designs were both common, and within-participants designs replicated more often than between-participants designs (65\% versus 36\%).
+Studies with multiple vignettes replicated more often than single vignetted studies (59\% versus 36\%).
 However, there were strong correlations among these experimental features as well as between these experimental features and specific subfields.
@@
 While a number of features show individual correlations with the subjective replication score, many correlate with one another.
-To determine which predictors were the strongest, we ran a series of pre-registered Bayesian regression models regularized using a horseshoe shrinkage prior (\protect\hyperlink{ref-carvalho09}{Carvalho et al.
+To determine which predictors were the strongest, we ran a series of pre-registered Bayesian regression models using an ordinal link function and regularized using a horseshoe shrinkage prior (\protect\hyperlink{ref-carvalho09}{Carvalho et al.
 2009}).
@@
 
-Within-participants designs stand out as the strongest correlate of replicability in the model with all the data (0.53, CrI= {[}0, 2{]}).
-In the model with all predictors, but less data, within-participants designs remain strong (0.66, CrI= {[}-0.04, 2.37{]}), and standardized effect size is also substantially related to subjective replication score (0.65, CrI= {[}0.27, 2.81{]}).
-Both effects are robust to a sensitivity analysis including only studies with close replications and matching statistical tests (within-participants 0.87, CrI= {[}-0.01, 3.33{]}; effect size 1.05, CrI= {[}0.76, 4.88{]}).
+Within-participants designs stand out as the strongest correlate of replicability in the model with all the data (\(\beta = 0.53, 95\% \mathrm{CrI} = [0, 2]\)).
+In the model with all predictors, but less data, within-participants designs remain strong (\(\beta = 0.66, 95\% \mathrm{CrI} = [-0.04, 2.37]\)), and standardized effect size is also substantially related to subjective replication score (\(\beta = 0.65, 95\% \mathrm{CrI} = [0.27, 2.81]\)).
+Both effects are robust to a sensitivity analysis including only studies with close replications and matching statistical tests (within-participants \(\beta = 0.87, 95\% \mathrm{CrI} = [-0.01, 3.33]\); effect size \(\beta = 1.05, 95\% \mathrm{CrI} = [0.76, 4.88]\)).
 
-We also ran models predicting our secondary outcome measures: whether the replication effect was within the prediction interval of the original effect and what the \(p\)-original was between the replication and original.
+We also ran models predicting our secondary outcome measures: a logistic model predicting whether the replication effect was within the prediction interval of the original effect, and a linear model predicting what the \(p\)-original was between the replication and original.
 Both these models had more uncertain estimates.
 While the credible intervals were wide, the general patterns of predictor direction and relative strength were similar to the subjective replication models (see Supplement for coefficients from all models).
-The strongest predictors for prediction interval were still within-participants designs (0.62, CrI= {[}-0.18, 2.01{]}) and studies with larger effect sizes (0.3, CrI= {[}-0.29, 0.94{]}).
+The strongest predictors for prediction interval were still within-participants designs (\(\beta = 0.62, 95\% \mathrm{CrI} = [-0.18, 2.01]\)) and studies with larger effect sizes (\(\beta = 0.3, 95\% \mathrm{CrI} = [-0.29, 0.94]\)).
 
@@
 We ran a model predicting the subjective replication score on the basis of demographic and experimental predictors on the entire dataset.
-We ran two models predicting \(p\)-original and prediction interval from demographic and experimental predictors on the subset of data where we had \(p\)-original and prediction intervals.
+We ran two models predicting \(p\)-original and predicting whether the replication was in the prediction interval from demographic and experimental predictors on the subset of data where we had \(p\)-original and prediction intervals.
 Then, on the smaller subset of the data where we had effect sizes and \(p\) values, we re-ran these three models with those as additional predictor variables.

### 2023-07-14 reports/RPubs - Document2_files/embed.js
add raw reports where we have permission to include

@@ -1,0 +1,49 @@
+(function () {
+    'use strict';
+    var _config = window.disqus_config;
+    window.disqus_config = function () {
+        if (_config) {
+            try {
+                _config.call(this);
+            } catch(err) {
+                console.error('There was a problem with the Disqus configuration.', err);
+            }
+        }
+        this.server_side = {
+  "inthread_repeat_comment_count":"8",
+  "default_placement_url":"",
+  "inthread_placement_url":"",
+  "under_ccpa":"1",
+  "can_disable_ads":"",
+  "lazyload_viewports":"2",
+  "service":"dynamic",
+  "sourceless_iframe":"1",
+  "experiment":"prebidbidisrequired",
+  "inthread_count_children":"True",
+  "under_gdpr":"",
+  "inthread_multiple_ads":"True",
+  "bin":"embed:promoted_discovery:dynamic:prebidbidisrequired:active",
+  "bottom_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola/?position=bottom&shortname=rpubs&experiment=prebidbidisrequired&variant=active&service=dynamic",
+  "variant":"active",
+  "forum_id":"1423073",
+  "recommendations_placement_url":"",
+  "top_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola/?position=top&shortname=rpubs&experiment=prebidbidisrequired&variant=active&service=dynamic",
+  "inthread_trailing_comment_count":"0",
+  "is_private":"",
+  "skeleton_frame_enabled":"",
+  "recs_outside_embed_enabled":"1",
+  "forum":{
+    "id":1423073,
+    "disable_disqus_branding":false,
+    "recommendation_placement":"top",
+    "recommendations_feature_enabled":true
+  },
+  "sandbox_ads":"1",
+  "inthread_leading_comment_count":"1",
+  "t":"1689376730"
+};
+    };
+})();
[…]

### 2023-07-14 reports/RPubs - Final Report on Hughes et al. 2013_files/recommendations.js

@@ -1,0 +1,36 @@
+(function () {
+    'use strict';
+    var _config = window.disqus_recommendations_config;
+    window.disqus_recommendations_config = function () {
+        if (_config) {
+            try {
+                _config.call(this);
+            } catch(err) {
+                console.error('There was a problem with the Disqus configuration.', err);
+            }
+        }
+        this.server_side = {
+  "bin":"embed:promoted_discovery:dynamic:prebidbidisrequired:active",
+  "recs_outside_embed_enabled":"1",
+  "forum":{
+    "id":1423073,
+    "disable_disqus_branding":false,
+    "recommendation_placement":"top",
+    "recommendations_feature_enabled":true
+  },
+  "service":"dynamic",
+  "sourceless_iframe":"1",
+  "variant":"active",
+  "forum_id":"1423073",
+  "recommendations_placement_url":"",
+  "experiment":"prebidbidisrequired",
+  "default_placement_url":"",
+  "t":"1689376730",
+  "can_disable_ads":"",
+  "skeleton_frame_enabled":""
+};
+    };
+})();
[…]

### 2023-07-14 reports/RPubs - Replication Project Proposal_files/config.js

@@ -1,0 +1,1 @@
+define({"tos_exempt_forums_shortnames":["somememes","qrt-dev","qrt-test","qrt-prd"],"register":{"ENABLE_CAPTCHA":true},"max_post_edit_days":7,"lounge":{"follow_channel_prompt_views":1,"motd_admin_url":"https://blog.disqus.com/the-disqus-comment-section-upgraded","viglink":{"experiment_version":"v5","version":"v4"},"tracking":{"iframe_limit":4,"list":[{"url":"//referrer.disqus.com/juggler/stat.gif?event=data_tracker","forced_forums":["disqus"],"rate":0,"type":"img"}]},"font_options":[{"category":"serif","name":"Lora"},{"category":"sans-serif","name":"Montserrat"},{"category":"sans-serif","name":"Nunito"},{"category":"sans-serif","name":"Open+Sans"},{"category":"sans-serif","name":"Poppins"},{"category":"sans-serif","name":"Roboto"},{"category":"serif","name":"Roboto+Slab"},{"category":"sans-serif","name":"Source+Sans+Pro"},{"category":"serif","name":"Source+Serif+Pro"},{"category":"serif","name":"Spectral"},{"category":"sans-serif","name":"IBM+Plex+Sans"}],"cc_v2_start":"2023-04-18T17:50:00","motd_home_title":"The Disqus comment section gets a refresh!","motd_admin_title":"The Disqus comment section gets a refresh!","motd_home_url":"https://blog.disqus.com/the-disqus-comment-section-upgraded","REALTIME":{"BACKOFF_INTERVAL":4,"MAX_HANDSHAKE_FAILS":1,"XHR_ENABLED":false,"THREAD_STALE_DAYS":1},"motd_marketing_cta":"Full details here \u00bb","switches":{"customer_pulse_analytics":{"username":["orazumov_zeta","michaelyakovlev","commenting_privacy","andrei_ivanov_disqus","aivanov"]},"custom_reactions":true,"home_ads":{"channelDiscussions":true},"home_ads_prevented":{"forum":["iphoneincanada","thehill-v4","nmax","toofab","channel-discussdisqus","patdollardcom"]},"zyncOnly":{"percent":100},"spam_and_ban_moderation":{"percent":100,"forum":["taylans","disqus","rawstory","androidpolice","dogus"]},"st
[…]

### 2023-07-14 reports/RPubs - ReplicationReport_LuizaSantos_files/lounge.load.3c00c65811f2cec80a8903c739975872.js

@@ -1,0 +1,1 @@
+!function(){"use strict";var a=window.document,b={STYLES:"https://c.disquscdn.com/next/embed/styles/lounge.dbc47866f009f9d6f1556cd58214d9a3.css",RTL_STYLES:"https://c.disquscdn.com/next/embed/styles/lounge_rtl.c7a4fee6da46503e07c9e61415dfd32f.css","lounge/main":"https://c.disquscdn.com/next/embed/lounge.bundle.9252e8c30002c02fb7a36ab614c3c6ee.js","remote/config":"https://disqus.com/next/config.js","common/vendor_extensions/highlight":"https://c.disquscdn.com/next/embed/highlight.6fbf348532f299e045c254c49c4dbedf.js"};window.require={baseUrl:"https://c.disquscdn.com/next/current/embed/embed",paths:["lounge/main","remote/config","common/vendor_extensions/highlight"].reduce(function(a,c){return a[c]=b[c].slice(0,-3),a},{})};var c=a.createElement("script");c.onload=function(){require(["common/main"],function(a){a.init("lounge",b)})},c.src="https://c.disquscdn.com/next/embed/common.bundle.42272221620e218896f3973a3bb140e2.js",a.body.appendChild(c);var d=["astarostin-test","hovseptestrealm","disqus-pse-stock-v2"],e=!1;if(d.forEach(function(a){(window.location.hostname===a||window.location.search.includes(a))&&(e=!0)}),e){var f=a.createElement("script");f.src="https://c.disquscdn.com/embedv2/latest/embedv2.js",a.body.appendChild(f)}}();

### 2023-07-24 reports/RPubs - Maddux et al. (2008) Replication Report_files/embed.js
add student report

@@ -1,0 +1,49 @@
+(function () {
+    'use strict';
+    var _config = window.disqus_config;
+    window.disqus_config = function () {
+        if (_config) {
+            try {
+                _config.call(this);
+            } catch(err) {
+                console.error('There was a problem with the Disqus configuration.', err);
+            }
+        }
+        this.server_side = {
+  "inthread_repeat_comment_count":"8",
+  "default_placement_url":"",
+  "inthread_placement_url":"",
+  "under_ccpa":"1",
+  "can_disable_ads":"",
+  "lazyload_viewports":"2",
+  "service":"dynamic",
+  "sourceless_iframe":"1",
+  "experiment":"prebidbidisrequired",
+  "inthread_count_children":"True",
+  "under_gdpr":"",
+  "inthread_multiple_ads":"True",
+  "bin":"embed:promoted_discovery:dynamic:prebidbidisrequired:active",
+  "bottom_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola/?position=bottom&shortname=rpubs&experiment=prebidbidisrequired&variant=active&service=dynamic",
+  "variant":"active",
+  "forum_id":"1423073",
+  "recommendations_placement_url":"",
+  "top_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola/?position=top&shortname=rpubs&experiment=prebidbidisrequired&variant=active&service=dynamic",
+  "inthread_trailing_comment_count":"0",
+  "is_private":"",
+  "skeleton_frame_enabled":"",
+  "recs_outside_embed_enabled":"1",
+  "forum":{
+    "id":1423073,
+    "disable_disqus_branding":false,
+    "recommendation_placement":"top",
+    "recommendations_feature_enabled":true
+  },
+  "sandbox_ads":"1",
+  "inthread_leading_comment_count":"1",
+  "t":"1690236196"
+};
+    };
+})();
[…]

### 2023-07-24 reports/RPubs - Maddux et al. (2008) Replication Report_files/lounge.load.272a8103e6a3ca6530f74990fa65b6aa.js

@@ -1,0 +1,1 @@
+!function(){"use strict";var a=window.document,b={STYLES:"https://c.disquscdn.com/next/embed/styles/lounge.dbc47866f009f9d6f1556cd58214d9a3.css",RTL_STYLES:"https://c.disquscdn.com/next/embed/styles/lounge_rtl.c7a4fee6da46503e07c9e61415dfd32f.css","lounge/main":"https://c.disquscdn.com/next/embed/lounge.bundle.9252e8c30002c02fb7a36ab614c3c6ee.js","remote/config":"https://disqus.com/next/config.js","common/vendor_extensions/highlight":"https://c.disquscdn.com/next/embed/highlight.6fbf348532f299e045c254c49c4dbedf.js"};window.require={baseUrl:"https://c.disquscdn.com/next/current/embed/embed",paths:["lounge/main","remote/config","common/vendor_extensions/highlight"].reduce(function(a,c){return a[c]=b[c].slice(0,-3),a},{})};var c=a.createElement("script");c.onload=function(){require(["common/main"],function(a){a.init("lounge",b)})},c.src="https://c.disquscdn.com/next/embed/common.bundle.3202c242c010134b5e230e1eedac257a.js",a.body.appendChild(c);var d=["astarostin-test","hovseptestrealm","disqus-pse-stock-v2"],e=!1;if(d.forEach(function(a){(window.location.hostname===a||window.location.search.includes(a))&&(e=!0)}),e){var f=a.createElement("script");f.src="https://c.disquscdn.com/embedv2/latest/embedv2.js",a.body.appendChild(f)}}();

### 2023-07-24 reports/RPubs - Maddux et al. (2008) Replication Report_files/recommendations.js

@@ -1,0 +1,36 @@
+(function () {
+    'use strict';
+    var _config = window.disqus_recommendations_config;
+    window.disqus_recommendations_config = function () {
+        if (_config) {
+            try {
+                _config.call(this);
+            } catch(err) {
+                console.error('There was a problem with the Disqus configuration.', err);
+            }
+        }
+        this.server_side = {
+  "bin":"embed:promoted_discovery:dynamic:prebidbidisrequired:active",
+  "recs_outside_embed_enabled":"1",
+  "forum":{
+    "id":1423073,
+    "disable_disqus_branding":false,
+    "recommendation_placement":"top",
+    "recommendations_feature_enabled":true
+  },
+  "service":"dynamic",
+  "sourceless_iframe":"1",
+  "variant":"active",
+  "forum_id":"1423073",
+  "recommendations_placement_url":"",
+  "experiment":"prebidbidisrequired",
+  "default_placement_url":"",
+  "t":"1690236196",
+  "can_disable_ads":"",
+  "skeleton_frame_enabled":""
+};
+    };
+})();
[…]

### 2023-07-24 reports/RPubs - Maddux et al. (2008) Replication Report_files/recommendations.load.885ab6576d98e58fe91518733ccb84a2.js

@@ -1,0 +1,1 @@
+!function(){"use strict";var a=window.document,b={STYLES:"https://c.disquscdn.com/next/recommendations/styles/recommendations.10022a97346f1c6e3798931bbd8e4bb5.css",RTL_STYLES:"https://c.disquscdn.com/next/recommendations/styles/recommendations_rtl.9c3ccad48c24340222b5a85c20ea36b8.css","recommendations/main":"https://c.disquscdn.com/next/recommendations/recommendations.bundle.bb3216316047d5c61d9dafa6240fbf39.js","remote/config":"https://disqus.com/next/config.js"};window.require={baseUrl:"https://c.disquscdn.com/next/current/recommendations/recommendations",paths:["recommendations/main","remote/config"].reduce(function(a,c){var d=-3;return a[c]=b[c].slice(0,d),a},{})};var c=a.createElement("script");c.onload=function(){require(["common/main"],function(a){a.init("recommendations",b)})},c.src="https://c.disquscdn.com/next/recommendations/common.bundle.d3c61c72047a19eda535a9d1d31eba39.js",a.body.appendChild(c)}();

### 2023-07-25 code/process.Rmd
fix supplement, add student permission data

@@
 
-raw <- readxl::read_xlsx(here("data","raw_data.xlsx"), 
-                       sheet="aligned data", skip=1) |> select(target_lastauthor_year, sensitivity, include,
+raw <- readxl::read_xlsx(here("data","raw_data.xlsx"), sheet="aligned data", skip=1) |> 
+  mutate(student_name_shared=ifelse(is.na(student_name_shared), "N/A", student_name_shared),
+         replication_report_included=ifelse(is.na(replication_report_included), "no", replication_report_included)) |> 
+  select(target_lastauthor_year, student_name_shared, replication_report_included, sensitivity, include,
          status, status_explanation,  academic_year, journal, target_cite, article_link, study_number,  subfield, target_year, stanford_internal, 

### 2023-07-25 paper/manuscript.Rmd
fix supplement, add student permission data

@@
          p = sapply(preds, function(x) sub_cor(x, stat = "p"))) |> 
-  mutate(Predictors=factor(preds, levels=c("social", "other_psych", "non_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "pub_year", "log_trials", "log_sample", "log_ratio_ss"), labels=c("Social psychology (versus cognitive psych)", "Other psychology (versus cognitive psych)", "Non psychology (versus cogntive psych)", "Within participants design (versus between participants)", "Single vignette (versus multiple items/inductions per condition)", "Switch to online for replication (versus same modality for original and replication)", "Open data", "Open materials", "Stanford affiliation of original authors at time of replication", "Publication year", "Log number of  trials", "Log original sample size", "Log ratio between replication and original sample sizes"))) |> arrange(desc(r)) |> select(r, p, Predictors)
+  mutate(Predictors=factor(preds, levels=c("social", "other_psych", "non_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "pub_year", "log_trials", "log_sample", "log_ratio_ss"), labels=c("Social psychology (versus cognitive psych)", "Other psychology (versus cognitive psych)", "Non psychology (versus cognitive psych)", "Within participants design (versus between participants)", "Single vignette (versus multiple items/inductions per condition)", "Switch to online for replication (versus same modality for original and replication)", "Open data", "Open materials", "Stanford affiliation of original authors at time of replication", "Publication year", "Log number of  trials", "Log original sample size", "Log ratio between replication and original sample sizes"))) |> arrange(desc(r)) |> select(r, p, Predictors)
 
 library(kableExtra)
-knitr::kable(cors, digits = 3, align='ccl',format="latex", position="!h", caption="The correlation between each individual predictor and the subjective replication score.
-For subfield, cognitive psychology is treated as the baseline condition.
+knitr::kable(cors, digits = 3, align='ccl',format="latex", position="!h", caption="The unadjusted Pearson correlations between each individual predictor and the subjective replication score.
 See Methods for how these variables were coded.", booktabs=TRUE, linesep="") |> kable_styling(full_width=F, font_size=10)
-
-```
-
-```{r, include=F}
-
- within <- glm(sub_rep ~ is_within, data=for_cor, family=binomial)$coefficient[2] |> exp() 
- vignette <- glm(sub_rep ~ single_vignette, data=for_cor, family=binomial)$coefficient[2] |> exp()
-
-  subfield <- glm(sub_rep ~ subfield, data=for_cor |> filter(subfield %in% c("social", "cognitive")), family=binomial)$coefficient[2] |> exp()
 
@@
 
-within <- for_cor |> group_by(is_within) |> summarize(avg=mean(sub_rep)*100)
+within <- for_cor |> group_by(is_within) |> summarize(avg=mean(sub_rep))
 
-cog <- for_cor |> group_by(subfield) |> summarize(avg=mean(sub_rep)*100)
-vignette <- for_cor |> group_by(single_vignette) |> summarize(avg=mean(sub_rep)*100)
+cog <- for_cor |> group_by(subfield) |> summarize(avg=mean(sub_rep))
+vignette <- for_cor |> group_by(single_vignette) |> summarize(avg=mean(sub_rep))
 
@@
 
-## Independent correlates of replication success
+## Bivariate correlates of replication success
 
@@
 
-Many predictors individually correlated with subjective replication success (Table \ref{tab:cor}).
+Many predictors correlated with subjective replication success using unadjusted Pearson correlations(Table \ref{tab:cor}).
 Predictors of higher replicability included within-participants designs, larger numbers of trials per participant, and the original study having openly accessible data.
@@
 Distributions of study outcomes across some of these properties are shown in Figure \ref{fig:predictors-graph}.
-Both social and cognitive psychology studies were well represented in the replication sample, and the cognitive psychology studies replicated more often than social psychology studies (`r pluck(cog,2,1) |> round()`% versus `r pluck(cog,2,4) |> round()`%).
-Within and between participants designs were both common, and within-participants designs replicated more often than between-participants designs (`r pluck(within,2,2) |> round()`% versus `r pluck(within,2,1) |> round()`%).
-Studies with multiple vignettes replicated more often than single vignetted studies (`r pluck(vignette,2,1) |> round()`% versus `r pluck(vignette,2,2) |> round()`%).
+Both social and cognitive psychology studies were well represented in the replication sample, and the cognitive psychology studies replicated more often than social psychology studies (mean subjective replication scores: `r pluck(cog,2,1) |> round(2)` versus `r pluck(cog,2,4) |> round(2)`).
+Within and between participants designs were both common, and within-participants designs replicated more often than between-participants designs (mean scores: `r pluck(within,2,2) |> round(2)` versus `r pluck(within,2,1) |> round(2)`).
+Studies with multiple vignettes replicated more often than single vignetted studies (mean scores: `r pluck(vignette,2,1) |> round(2)` versus `r pluck(vignette,2,2) |> round(2)`).
 However, there were strong correlations among these experimental features as well as between these experimental features and specific subfields.
@@
 do_estimates <- function(model, variable){
-  summary(model)$fixed |> as_tibble(rownames="var") |> filter(var==variable)|> mutate(text=str_c("$\\beta = ", round(Est.Error,2), ",  95\\% \\mathrm{CrI} = [", round(`l-95% CI`,2),", ", round(`u-95% CI`,2),"]$")) |> pull(text)
+  summary(model)$fixed |> as_tibble(rownames="var") |> filter(var==variable)|> 
+    mutate(OR=exp(Estimate), lower=exp(`l-95% CI`), upper=exp(`u-95% CI`)) |> 
+    mutate(text=str_c("OR = ", round(OR,2), ",  95\\% CrI = [", round(lower,2),", ", round(upper,2),"]")) |> pull(text)
 }
@@
 Both these models had more uncertain estimates.
-While the credible intervals were wide, the general patterns of predictor direction and relative strength were similar to the subjective replication models (see Supplement for coefficients from all models).
+While the credible intervals were wide, the general patterns of predictor direction and relative strength were similar to the subjective replication models (see Supplement for results from all models).
 The strongest predictors for prediction interval were still within-participants designs (`r within_2`) and studies with larger effect sizes (`r smd_2`).
 
-```{r mod-results, out.width="90%", fig.width=8, fig.height=5, fig.pos="ht", fig.cap="Coefficients and uncertaintly estimates from a model of all original-replication pairs (N=176, shown in blue) and a model of all pairs with full statistical information (N=112, shown in red) and predicting subjective replication scores as the dependent variable.
-"}
+```{r mod-results, out.width="90%", fig.width=8, fig.height=5, fig.pos="ht", fig.cap="Odds ratios and corresponding uncertaintly estimates on the likelihood of having a higher subjective replication score as a function of the dependent variable.
+Estimates from a model of all original-replication pairs (N=176) are shown in blue, and from a model of all pairs with full statistical information (N=112) are shown in red.
+A value of 1 indicates no effect, greater than one indicates an association with higher replication scores and less than 1 an association with lower replication scores."}
 
@@
     mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |>  filter(Term!="Intercept") |> 
-    mutate(Term=factor(Term, levels=c("subfieldsocial", "subfieldother_psych", "subfieldnon_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "z_pub_year", "z_log_trials", "z_log_sample", "z_log_ratio_ss","z_log_p","z_target_d_calc"), labels=c("Social", "Other psych", "Non psych", "Within participants", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log n trials", "Log original sample size", "Log rep/orig sample", "P-value", "Original effect size")))
+    mutate(Term=factor(Term, levels=c("subfieldsocial", "subfieldother_psych", "subfieldnon_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "z_pub_year", "z_log_trials", "z_log_sample", "z_log_ratio_ss","z_log_p","z_target_d_calc"), labels=c("Social psych", "Other psych", "Non psych", "Within participants", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log n trials", "Log original sample size", "Log rep/orig sample", "P-value", "Original effect size")))
 }
 
-tier1_subjective <- read_rds(here(model_location, "tier1_subjective.rds")) |> do_draws() |> mutate(type="All pairs") |> mutate(sens="All data")
-tier3_subjective <- read_rds(here(model_location, "tier3_subjective.rds"))|> do_draws() |> mutate(type="Pairs with full statistical information") |> mutate(sens="All data")
+tier1_subjective <- read_rds(here(model_location, "tier1_subjective.rds")) |> do_draws() |> mutate(OR=exp(Estimate))|> mutate(type="All pairs") |> mutate(sens="All data")
+tier3_subjective <- read_rds(here(model_location, "tier3_subjective.rds"))|> do_draws() |>  mutate(OR=exp(Estimate)) |> mutate(type="Pairs with full statistical information") |> mutate(sens="All data")
 
-tier1_subjective |> union(tier3_subjective) |> ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate, color=type)) + geom_vline(xintercept=0)+
+tier1_subjective |> union(tier3_subjective) |> ggplot(aes(y = reorder(Term, OR, mean), x = OR, color=type)) + geom_vline(xintercept=1)+
   scale_color_solarized()+
-  stat_pointinterval(position=position_dodge(width=.7))+labs(y="", x="Estimate, 66%, 95% CrI predicting subjective replication score", color="", linetype="", shape="")+theme(axis.text=element_text(size=11),legend.position="none")
+  stat_pointinterval(position=position_dodge(width=.7))+labs(y="", x="Odds Ratios for subjective replication score (point estimate, 66% CrI, 95% CrI)", color="", linetype="", shape="")+theme(axis.text=element_text(size=11),legend.position="none")+coord_trans(x="log10")+scale_x_continuous(breaks=c(.125, .25, .5, 1, 2, 4, 8, 16), minor_breaks = NULL)
 
@@
 # Methods
-Our pre-registration, code, and coded data are available at TODO OSF REPO.
+Our pre-registration, code, and coded data are available at https://osf.io/xwn9m/. <!--TODO VIEW ONLY https://osf.io/xwn9m/?view_only=ebb6df1ae97045cfa5154d6119ec20b1-->
 
@@
 Students were encouraged to do experimental replications, but some students chose to replicate correlational outcomes or do computational reproducibility projects instead.
-We cannot include the full student reports for confidentiality reasons, but we include some example reports we have permission to share and the template given to students at TOOD OSF REPO.
+We cannot include the full student reports for confidentiality reasons, but we include over 50 reports that we received permission to share and the template given to students at https://osf.io/xwn9m/.
+<!-- TODO VIEW ONLY-->
 
@@
 
-TODO We are grateful to the students in PSYCH 254 and PSYCH 251 for conducting the replication projects included here.
+We are grateful to the students in PSYCH 254 and PSYCH 251 for conducting the replication projects included here.
 We thank Ben Prystawski and the FriSem audience for feedback on earlier versions of this work.
@@
 
+# Author Contributions {-}
+
+The authors have no conflicts of interest to declare. TODO contributor statement!
 # References {-}

### 2023-07-25 paper/manuscript.tex
fix supplement, add student permission data

@@
 
-Many different measures can be used to define replication success of an individual statistical result (\protect\hyperlink{ref-simonsohn2015}{Simonsohn 2015}, \protect\hyperlink{ref-gelman2018}{Gelman 2018/ed}, \protect\hyperlink{ref-mathur2020}{Mathur \& VanderWeele 2020}).
+Many different measures can be used to define replication success of an individual statistical result (\protect\hyperlink{ref-gelman2018}{Gelman 2018/ed}, \protect\hyperlink{ref-simonsohn2015}{Simonsohn 2015}, \protect\hyperlink{ref-mathur2020}{Mathur \& VanderWeele 2020}).
 However, whether a replication should be considered successful is not always dependent on only one statistical comparison between the two studies.
@@
 
-\caption{\label{tab:cor}The correlation between each individual predictor and the subjective replication score.
-For subfield, cognitive psychology is treated as the baseline condition.
-See Methods for how these variables were coded.}
+\caption{\label{tab:cor}The unadjusted Pearson correlations between each individual predictor and the subjective replication score. See Methods for how these variables were coded.}
 \centering
@@
 0.150 & 0.047 & Open data\\
-0.080 & 0.294 & Non psychology (versus cogntive psych)\\
+0.080 & 0.294 & Non psychology (versus cognitive psych)\\
 0.075 & 0.322 & Other psychology (versus cognitive psych)\\
@@
 
-\hypertarget{independent-correlates-of-replication-success}{%
-\subsection{Independent correlates of replication success}\label{independent-correlates-of-replication-success}}
+\hypertarget{bivariate-correlates-of-replication-success}{%
+\subsection{Bivariate correlates of replication success}\label{bivariate-correlates-of-replication-success}}
 
@@
 Distributions of study outcomes across some of these properties are shown in Figure \ref{fig:predictors-graph}.
-Both social and cognitive psychology studies were well represented in the replication sample, and the cognitive psychology studies replicated more often than social psychology studies (58\% versus 36\%).
-Within and between participants designs were both common, and within-participants designs replicated more often than between-participants designs (65\% versus 36\%).
-Studies with multiple vignettes replicated more often than single vignetted studies (59\% versus 36\%).
+Both social and cognitive psychology studies were well represented in the replication sample, and the cognitive psychology studies replicated more often than social psychology studies (mean subjective replication scores: 0.58 versus 0.36).
+Within and between participants designs were both common, and within-participants designs replicated more often than between-participants designs (mean scores: 0.65 versus 0.36).
+Studies with multiple vignettes replicated more often than single vignetted studies (mean scores: 0.59 versus 0.36).
 However, there were strong correlations among these experimental features as well as between these experimental features and specific subfields.
@@
 
-Within-participants designs stand out as the strongest correlate of replicability in the model with all the data (\(\beta = 0.53, 95\% \mathrm{CrI} = [0, 2]\)).
-In the model with all predictors, but less data, within-participants designs remain strong (\(\beta = 0.66, 95\% \mathrm{CrI} = [-0.04, 2.37]\)), and standardized effect size is also substantially related to subjective replication score (\(\beta = 0.65, 95\% \mathrm{CrI} = [0.27, 2.81]\)).
-Both effects are robust to a sensitivity analysis including only studies with close replications and matching statistical tests (within-participants \(\beta = 0.87, 95\% \mathrm{CrI} = [-0.01, 3.33]\); effect size \(\beta = 1.05, 95\% \mathrm{CrI} = [0.76, 4.88]\)).
+Within-participants designs stand out as the strongest correlate of replicability in the model with all the data (OR = 2.56, 95\% CrI = {[}1, 7.36{]}).
+In the model with all predictors, but less data, within-participants designs remain strong (OR = 2.76, 95\% CrI = {[}0.97, 10.71{]}), and standardized effect size is also substantially related to subjective replication score (OR = 4.36, 95\% CrI = {[}1.31, 16.65{]}).
+Both effects are robust to a sensitivity analysis including only studies with close replications and matching statistical tests (within-participants OR = 4.45, 95\% CrI = {[}0.99, 28.08{]}; effect size OR = 13.93, 95\% CrI = {[}2.15, 131.6{]}).
 
@@
 Both these models had more uncertain estimates.
-While the credible intervals were wide, the general patterns of predictor direction and relative strength were similar to the subjective replication models (see Supplement for coefficients from all models).
-The strongest predictors for prediction interval were still within-participants designs (\(\beta = 0.62, 95\% \mathrm{CrI} = [-0.18, 2.01]\)) and studies with larger effect sizes (\(\beta = 0.3, 95\% \mathrm{CrI} = [-0.29, 0.94]\)).
+While the credible intervals were wide, the general patterns of predictor direction and relative strength were similar to the subjective replication models (see Supplement for results from all models).
+The strongest predictors for prediction interval were still within-participants designs (OR = 1.79, 95\% CrI = {[}0.83, 7.44{]}) and studies with larger effect sizes (OR = 1.17, 95\% CrI = {[}0.75, 2.57{]}).
 
 \begin{figure}[ht]
-\includegraphics[width=0.9\linewidth]{manuscript_files/figure-latex/mod-results-1} \caption{Coefficients and uncertaintly estimates from a model of all original-replication pairs (N=176, shown in blue) and a model of all pairs with full statistical information (N=112, shown in red) and predicting subjective replication scores as the dependent variable.
-}\label{fig:mod-results}
+\includegraphics[width=0.9\linewidth]{manuscript_files/figure-latex/mod-results-1} \caption{Odds ratios and corresponding uncertaintly estimates on the likelihood of having a higher subjective replication score as a function of the dependent variable.
+Estimates from a model of all original-replication pairs (N=176) are shown in blue, and from a model of all pairs with full statistical information (N=112) are shown in red.
+A value of 1 indicates no effect, greater than one indicates an association with higher replication scores and less than 1 an association with lower replication scores.}\label{fig:mod-results}
 \end{figure}
@@
 
-Our pre-registration, code, and coded data are available at TODO OSF REPO.
+Our pre-registration, code, and coded data are available at \url{https://osf.io/xwn9m/}.
 
@@
 Students were encouraged to do experimental replications, but some students chose to replicate correlational outcomes or do computational reproducibility projects instead.
-We cannot include the full student reports for confidentiality reasons, but we include some example reports we have permission to share and the template given to students at TOOD OSF REPO.
+We cannot include the full student reports for confidentiality reasons, but we include over 50 reports that we received permission to share and the template given to students at \url{https://osf.io/xwn9m/}.
 
@@
 
-\hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
+\hypertarget{author-contributions}{%
+\section*{Author Contributions}\label{author-contributions}}
+\addcontentsline{toc}{section}{Author Contributions}
+
+The authors have no conflicts of interest to declare. TODO contributor statement!
+\# References \{-\}
 

### 2023-07-25 paper/supplement.Rmd
fix supplement, add student permission data

--- 2023-07-05 paper/supplement.Rmd
@@
 title: "Supplement"
-output: pdf_document
-date: "2023-03-28"
+output:
+  bookdown::pdf_document2:
+    toc: FALSE
+    keep_tex: TRUE
 
@@
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE) # By default, hide code; set to TRUE to see code
-#knitr::opts_chunk$set(fig.pos = 'th') # Places figures at top or here
-knitr::opts_chunk$set(out.width = '100%', dpi=300,
-                      fig.width=8, fig.width=8) # Figure resolution and size
-knitr::opts_chunk$set(fig.env="figure") # Latex figure environment
-
-options(knitr.table.format="latex") # For kable tables to work without setting format option
-
+```{r setup, include=F}
 knitr::opts_chunk$set(echo=F, warning=F, message=F)#dev = "png", dev.args = list(type = "cairo-png")
@@
 theme_set(theme_bw())
-options(knitr.table.format = "pdf")
 
@@
 ```
+# Heterogeneity analysis
+
+```{r, echo=F}
+
+all_true <- d |> filter(include %in% c("stats", "pred_int")) |> filter(!is.na(predInt)) |> filter(predInt) |> nrow()
+
+all <- d |> filter(include %in% c("stats", "pred_int")) |> filter(!is.na(predInt)) |> nrow()
+
+#of those with SMD predInts
+all_orig  <- d |>filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> nrow()
+all_orig_true <- d |>filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> filter(predInt) |> nrow()
+all_d_true <- d |> filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> filter(predInt_from_d) |> nrow()
+all_tau <- d |> filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> filter(predInt_with_tau) |> nrow()
+
+```
+
+The prediction interval and p-original values used for models and point estimates were done on the original scale where possible.
+However, to do heterogeneity analysis, our imputed value for tau is in SMD units, so we have to use SMD units for the original and replication values.
+This limits the number of applicable original-replication pairs.
+Prediction intervals are sensitive to whether only studies with SMD are included (different studies report differently and also vary in how close replications were) and whether the scale used was original or SMD (if the variances differed between original and replication).
+
+Of all studies where prediction intervals can be calculated, `r all_true`/`r all` (`r round(all_true/all*100)`%) of the original estimates had prediction intervals that included the replication effect size.
+For those where we have SMD, `r all_orig_true`/`r all_orig` (`r round(all_orig_true/all_orig*100)`%) of the original estimates had prediction intervals that included the replication effect size, when we use original units where possible.
+Using SMD units, `r all_d_true`/`r all_orig` (`r round(all_d_true/all_orig*100)`%) of the original estimates had prediction intervals that included the replication effect size.
+Allowing for heterogeneity, with tau=.21, `r all_tau`/`r all_orig` (`r round(all_tau/all_orig*100)`%) of the original estimates are distributionally consistent.
 
@@
 
-\pagebreak
-
-```{r}
+```{r, eval=F}
 do_draws <- function(model){
@@
 
-subjective <- tier1_subjective |> union(tier3_subjective) |> union(sens1_subjective) |> union(sens3_subjective)
+subjective <- tier1_subjective |> union(tier3_subjective) |> union(sens1_subjective) |> union(sens3_subjective) |> mutate(OR=exp(Estimate))
 porig <- tier2_porig |> union(tier3_porig) |> union(sens2_porig) |> union(sens3_porig)
-predint <- tier2_predint |> union(tier3_predint) |> union(sens2_predint) |> union(sens3_predint)
+predint <- tier2_predint |> union(tier3_predint) |> union(sens2_predint) |> union(sens3_predint) |> mutate(OR=exp(Estimate))
 ```
 
-```{r sub-results, out.height="75%", fig.width=8, fig.height=8, fig.pos="ht", fig.cap="Coefficient estimates and uncertainty from ordinal models predicting subjective replication scores.
-Solid lines correspond to models run on as much of the data as possible; dashed lines are on the subset of the data for sensitivity analysis.
-Red is run on all relevant data with experimental predictors only; blue is on relevant data where there are statistical predictors."}
+```{r}
+do_estimates <- function(model){
+  summary(model)$fixed |> as_tibble(rownames="var") |> select(var, Estimate, lower=`l-95% CI`, upper=`u-95% CI`) |> filter(!str_detect(var, "Intercept")) |> 
+    mutate(var=str_replace(var, "M","_"),
+           Term=factor(var, levels=c("subfieldsocial", "subfieldother_psych", "subfieldnon_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "z_pub_year", "z_log_trials", "z_log_sample", "z_log_ratio_ss","z_log_p","z_target_d_calc"), labels=c("Social psych", "Other psych", "Non psych", "Within participants", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rep/orig sample", "P-value", "Original effect size"))) |>
+        mutate(est=str_c(round(Estimate,2)), 
+               range=str_c("[", round(lower,2),", ", round(upper,2),"]")) |> 
+    select(Term, est, range)
 
-  subjective |> ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate, color=type, linetype=sens, shape=sens)) + geom_vline(xintercept=0)+
-    scale_shape_manual(values = c(19,21))+
-  scale_color_solarized()+
-  stat_pointinterval(position=position_dodge(width=.7))+labs(y="", x="Estimate, 66%, 95% CrI predicting subjective replication score", color="", linetype="", shape="")+theme(axis.text=element_text(size=11),legend.position="bottom")
+}
+do_estimates_OR <- function(model){
+  summary(model)$fixed |> as_tibble(rownames="var") |> select(var, Estimate, lower=`l-95% CI`, upper=`u-95% CI`) |> filter(!str_detect(var, "Intercept")) |> 
+    mutate(var=str_replace(var, "M","_"),
+           Term=factor(var, levels=c("subfieldsocial", "subfieldother_psych", "subfieldnon_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "z_pub_year", "z_log_trials", "z_log_sample", "z_log_ratio_ss","z_log_p","z_target_d_calc"), labels=c("Social psych", "Other psych", "Non psych", "Within participants", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rep/orig sample", "P-value", "Original effect size"))) |>
+        mutate(OR=exp(Estimate),
+               lower=exp(lower),
+               upper=exp(upper),
+               est=str_c(round(OR,2)), 
+               range=str_c("[", round(lower,2),", ", round(upper,2),"]")) |> 
+    select(Term, est, range)
+
+}
+```
+
+```{r}
+
+tier1_subjective <- read_rds(here(model_location, "tier1_subjective.rds")) |> do_estimates_OR() |> mutate(type="All pairs") 
+tier3_subjective <- read_rds(here(model_location, "tier3_subjective.rds"))|> do_estimates_OR() |> mutate(type="Full stats")
+
+sens1_subjective <- read_rds(here(model_location, "sens_tier1_subjective.rds"))|> do_estimates_OR() |> mutate(type="All pairs: Sensitivity")
+sens3_subjective <- read_rds(here(model_location, "sens_tier3_subjective.rds"))|> do_estimates_OR()|> mutate(type="Full stats: Sensitivity")
+
+subjective <- tier1_subjective |> union(tier3_subjective) |> union(sens1_subjective) |> union(sens3_subjective) |> pivot_wider(id_cols=Term, names_from=type, values_from=c(est, range), values_fill="--") |> select(Term, "est_All pairs","range_All pairs", "est_Full stats", "range_Full stats",  "est_All pairs: Sensitivity" , "range_All pairs: Sensitivity", "est_Full stats: Sensitivity", "range_Full stats: Sensitivity") |> arrange(desc(`est_Full stats`))
+```
+
+```{r}
+
+tier2_predint <- read_rds(here(model_location, "tier2_predint.rds")) |> do_estimates_OR() |> mutate(type="All pairs") 
+tier3_predint <- read_rds(here(model_location, "tier3_predint.rds"))|> do_estimates_OR() |> mutate(type="Full stats")
+
+sens2_predint <- read_rds(here(model_location, "sens_tier2_predint.rds"))|> do_estimates_OR() |> mutate(type="All pairs: Sensitivity")
+sens3_predint <- read_rds(here(model_location, "sens_tier3_predint.rds"))|> do_estimates_OR()|> mutate(type="Full stats: Sensitivity")
+
+predint <- tier2_predint |> union(tier3_predint) |> union(sens2_predint) |> union(sens3_predint) |> pivot_wider(id_cols=Term, names_from=type, values_from=c(est, range), values_fill="--") |> select(Term, "est_All pairs","range_All pairs", "est_Full stats", "range_Full stats",  "est_All pairs: Sensitivity" , "range_All pairs: Sensitivity", "est_Full stats: Sensitivity", "range_Full stats: Sensitivity") |> arrange(desc(`est_Full stats`))
+```
+
+```{r}
+
+tier2_porig <- read_rds(here(model_location, "tier2_porig.rds")) |> do_estimates() |> mutate(type="All pairs") 
+tier3_porig <- read_rds(here(model_location, "tier3_porig.rds"))|> do_estimates() |> mutate(type="Full stats")
+
+sens2_porig <- read_rds(here(model_location, "sens_tier2_porig.rds"))|> do_estimates() |> mutate(type="All pairs: Sensitivity")
+sens3_porig <- read_rds(here(model_location, "sens_tier3_porig.rds"))|> do_estimates()|> mutate(type="Full stats: Sensitivity")
+
+porig<- tier2_porig |> union(tier3_porig) |> union(sens2_porig) |> union(sens3_porig) |> pivot_wider(id_cols=Term, names_from=type, values_from=c(est, range), values_fill="--") |> select(Term, "est_All pairs","range_All pairs", "est_Full stats", "range_Full stats",  "est_All pairs: Sensitivity" , "range_All pairs: Sensitivity", "est_Full stats: Sensitivity", "range_Full stats: Sensitivity") |> arrange(desc(`est_Full stats`))
+```
+
+```{r}
+knitr::kable(subjective, col.names=NULL, align='rrlrlrlrl',position="!h", caption="Odds ratios and 95\\% CrI from ordinal models predicting subjective replication scores.
+All pairs indicates that all pairs used, regardless of whether they had full statistical information; Full stats indicates that only pairs with full statistical information was used.
+Sensitivity indicates that it was a sensitivity test.", booktabs=T, linesep="") |> kable_styling() |>
+  add_header_above(c(" " = 1, "N=176" = 2, "N=112" = 2, "N=167" = 2, "N=82"=2)) |> 
+ add_header_above(c(" " = 1, " " = 2, " " = 2, "Sensitivity" = 2, "Sensitivity"=2)) |> add_header_above(c(" " = 1, "All pairs" = 2, "Full stats" = 2, "All pairs" = 2, "Full stats"=2))
 
@@
 
-```{r predint-results, out.height="75%", fig.width=8, fig.height=8, fig.pos="ht", fig.cap="Coefficient estimates and uncertainty from logistic models predicting prediction intervals.
-Solid lines correspond to models run on as much of the data as possible; dashed lines are on the subset of the data for sensitivity analysis.
-Red is run on all relevant data with experimental predictors only; blue is on relevant data where there are statistical predictors."}
-
-  predint |> ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate, color=type, linetype=sens, shape=sens)) + geom_vline(xintercept=0)+
-    scale_shape_manual(values = c(19,21))+
-  scale_color_solarized()+
-  stat_pointinterval(position=position_dodge(width=.7))+labs(y="", x="Estimate, 66%, 95% CrI predicting prediction interval", color="", linetype="", shape="")+theme(axis.text=element_text(size=11),legend.position="bottom")
+```{r}
+knitr::kable(predint, col.names=NULL, align='rrlrlrlrl',position="!h", caption="Odds ratios and 95\\% CrI from logistic models predicting whether the prediction interval of the original effect contained the replication effect.
+All pairs indicates that all pairs with calculable prediction intervals were used, regardless of whether they had full statistical information; Full stats indicates that only data with full statistical information was used.
+Sensitivity indicates that it was a sensitivity test.", booktabs=T, linesep="") |> kable_styling() |>
+  add_header_above(c(" " = 1, "N=136" = 2, "N=112" = 2, "N=100" = 2, "N=82"=2)) |> 
+ add_header_above(c(" " = 1, " " = 2, " " = 2, "Sensitivity" = 2, "Sensitivity"=2)) |> add_header_above(c(" " = 1, "All pairs" = 2, "Full stats" = 2, "All pairs" = 2, "Full stats"=2))
 
@@
 
-```{r porig-results, out.height="75%", fig.width=8, fig.height=8, fig.pos="ht", fig.cap="Coefficient estimates and uncertainty from linear models predicting p-original values.
-Solid lines correspond to models run on as much of the data as possible; dashed lines are on the subset of the data for sensitivity analysis.
-Red is run on all relevant data with experimental predictors only; blue is on relevant data where there are statistical predictors."}
-
-  porig |> ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate, color=type, linetype=sens, shape=sens)) + geom_vline(xintercept=0)+
-    scale_shape_manual(values = c(19,21))+
-  scale_color_solarized()+
-  stat_pointinterval(position=position_dodge(width=.7))+labs(y="", x="Estimate, 66%, 95% CrI predicting p-original values", color="", linetype="", shape="")+theme(axis.text=element_text(size=11),legend.position="bottom")
+```{r}
+knitr::kable(predint, col.names=NULL, align='rrlrlrlrl',position="!h", caption="Coefficients and 95\\% CrI from linear models predictiong the p-original value between the original and replicaiton effects.
+All pairs indicates that all pairs with calculable prediction intervals were used, regardless of whether they had full statistical information; Full stats indicates that only data with full statistical information was used.
+Sensitivity indicates that it was a sensitivity test.", booktabs=T, linesep="") |> kable_styling() |>
+  add_header_above(c(" " = 1, "N=136" = 2, "N=112" = 2, "N=100" = 2, "N=82"=2)) |> 
+ add_header_above(c(" " = 1, " " = 2, " " = 2, "Sensitivity" = 2, "Sensitivity"=2)) |> add_header_above(c(" " = 1, "All pairs" = 2, "Full stats" = 2, "All pairs" = 2, "Full stats"=2))
 
 ```
-
-\pagebreak
-
-# Heterogeneity analysis
-
-```{r, echo=F}
-
-all_true <- d |> filter(include %in% c("stats", "pred_int")) |> filter(!is.na(predInt)) |> filter(predInt) |> nrow()
-
-all <- d |> filter(include %in% c("stats", "pred_int")) |> filter(!is.na(predInt)) |> nrow()
-
-#of those with SMD predInts
-all_orig  <- d |>filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> nrow()
-all_orig_true <- d |>filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> filter(predInt) |> nrow()
-all_d_true <- d |> filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> filter(predInt_from_d) |> nrow()
-all_tau <- d |> filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> filter(predInt_with_tau) |> nrow()
-
-```
-
-The prediction interval and p-original values used for models and point estimates were done on the original scale where possible.
-However, to do heterogeneity analysis, our imputed value for tau is in SMD units, so we have to use SMD units for the original and replication values.
-This limits the number of applicable original-replication pairs.
-Prediction intervals are sensitive to whether only studies with SMD are included (different studies report differently and also vary in how close replications were) and whether the scale used was original or SMD (if the variances differed between original and replication).
-
-Of all studies where prediction intervals can be calculated, `r all_true`/`r all` (`r round(all_true/all*100)`%) of the original estimates had prediction intervals that included the replication effect size.
-For those where we have SMD, `r all_orig_true`/`r all_orig` (`r round(all_orig_true/all_orig*100)`%) of the original estimates had prediction intervals that included the replication effect size, when we use original units where possible.
-Using SMD units, `r all_d_true`/`r all_orig` (`r round(all_d_true/all_orig*100)`%) of the original estimates had prediction intervals that included the replication effect size.
-Allowing for heterogeneity, with tau=.21, `r all_tau`/`r all_orig` (`r round(all_tau/all_orig*100)`%) of the original estimates are distributionally consistent.

### 2023-07-25 plots/tikz_exclusion.tex
fix supplement, add student permission data

--- 2023-07-05 paper/supplement.Rmd
@@
----
-title: "Supplement"
-output: pdf_document
-date: "2023-03-28"
+\documentclass[margin=3mm, 10pt]{article}
+\usepackage{tikz}
+\usetikzlibrary{arrows.meta, positioning, quotes, shapes}
 
-header-includes:
- - \usepackage{tikz}
- - \usetikzlibrary{positioning,arrows.meta, quotes, shapes}
----
+\begin{document}
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE) # By default, hide code; set to TRUE to see code
-#knitr::opts_chunk$set(fig.pos = 'th') # Places figures at top or here
-knitr::opts_chunk$set(out.width = '100%', dpi=300,
-                      fig.width=8, fig.width=8) # Figure resolution and size
-knitr::opts_chunk$set(fig.env="figure") # Latex figure environment
-
-options(knitr.table.format="latex") # For kable tables to work without setting format option
-
-knitr::opts_chunk$set(echo=F, warning=F, message=F)#dev = "png", dev.args = list(type = "cairo-png")
- library("papaja")
-library("bookdown")
-library("rticles")
- library(here)
- library(tidyverse)
- library(brms)
-library(tidybayes)
-library(kableExtra)
-library(viridis)
-library(cowplot)
-library(ggthemes)
-#r_refs("r-references.bib", append=F)
-theme_set(theme_bw())
-options(knitr.table.format = "pdf")
-
-model_location="code/models"
-d <- read_csv(here("data", "processed_data.csv")) |> filter(status!="unusable") |> filter(include!="no")
-
-```
-
-# Additional model results
-
-Per our pre-registration, we ran a set of 6 models crossing 3 outcome measures (subjective replication score, whether the replication result was within the prediction interval of the original, and p-original on the hypothesis that both came from the same distribution) with 2 sets of predictors (with or without statistical predictors).
-These 6 models required 3 tiers of data: the subjective replication score without statistical predictors applies to all the data; the p_original and prediction interval models apply to the subset of data with numeric outcomes that can be compared; and the statistical predictor models need the smaller subset of data with p-values and original standardized effect size in particular.
-
-Due to low sample sizes and large numbers of predictors, even with regularizing priors, the coefficient estimates generally have a lot of uncertainty.
-
-## Sensitivity Analysis
-
-As a check on whether our results were sensitive to the inclusion of pairs that were marginal in some way, we repeated the 6 models including only studies that were not marginal.
-
-```{=latex}
 	\definecolor{bad}{HTML}{FFCCCB}
-		\definecolor{meh}{HTML}{efefef}
+	\definecolor{meh}{HTML}{aaddaa}
 	\definecolor{good}{HTML}{abcdff}
@@
 			draw, rectangle, align=center, text width=4.5cm, scale=1, font=\small, inner sep=.5ex},
-		arrow/.style={
-		 very thick,->,>=stealth}
 	}
-
-\begin{figure}
 	\begin{tikzpicture}[auto,
@@
 	\end{tikzpicture}
-	\caption{Diagram of what studies were downgraded or excluded for the sensitivity analysis.}
-	\end{figure}
-
-```
-
-```{r forest, out.height="100%", fig.width=9, fig.height=12, fig.pos="ht", fig.cap="Forest plot of original and replication effect sizes.
-Original effect sizes are open dots, replication are closed dots.
-Coloring indicates subjective replication score, and p-original values are listed on the left side.
-"}
-
-d |> 
-  filter(target_d_calc < 5, rep_d_calc < 5) |>
-  mutate(numpredInt=ifelse(predInt,1,0)) |> 
-  ggplot(aes(y=reorder(target_lastauthor_year,target_d_calc, mean), color=as.factor(sub_rep)))+
-    geom_vline(xintercept=0, linetype=3)+
-  geom_point(aes(x=target_d_calc, shape="original"))+
-  geom_point(aes(x=rep_d_calc, shape="replication"))+
-  geom_segment(aes(x=target_d_calc, xend=rep_d_calc, y=target_lastauthor_year, yend=target_lastauthor_year))+
-  scale_shape_manual(values=c("original"=21,"replication"=19), name=NULL)+
-  coord_cartesian(xlim=c(-1.5,3.5))+
-  geom_text(aes(x=-1.4, label=round(p_orig,3)), color="black", size=3, hjust=0, show.legend = F)+
-  scale_color_viridis(discrete=T, direction = 1, 
-                      name = "Subjective\nReplication\nSuccess\n")+theme_classic()+
-  labs(x="Standardized Effect Size")+
-  theme(axis.ticks.y=element_blank(), axis.title.y=element_blank())
-```
-
-\pagebreak
-
-```{r}
-do_draws <- function(model){
-  draws <- model |> gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> 
-    mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |>  filter(Term!="Intercept") |> 
-    mutate(Term=factor(Term, levels=c("subfieldsocial", "subfieldother_psych", "subfieldnon_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "z_pub_year", "z_log_trials", "z_log_sample", "z_log_ratio_ss","z_log_p","z_target_d_calc"), labels=c("Social", "Other psych", "Non psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rep/orig sample", "P-value", "Original effect size")))
-}
-
-tier1_subjective <- read_rds(here(model_location, "tier1_subjective.rds")) |> do_draws() |> mutate(type="All original-replication pairs") |> mutate(sens="All data")
-tier2_porig <- read_rds(here(model_location, "tier2_porig.rds"))|> do_draws() |>  mutate(type="All original-replication pairs") |> mutate(sens="All data")
-tier2_predint <- read_rds(here(model_location, "tier2_predint.rds"))|> do_draws() |>  mutate(type="All original-replication pairs") |> mutate(sens="All data")
-tier3_subjective <- read_rds(here(model_location, "tier3_subjective.rds"))|> do_draws() |> mutate(type="Only pairs with full statistical info") |> mutate(sens="All data")
-tier3_porig <- read_rds(here(model_location, "tier3_porig.rds"))|> do_draws() |>  mutate(type="Only pairs with full statistical info") |> mutate(sens="All data")
-tier3_predint <- read_rds(here(model_location, "tier3_predint.rds"))|> do_draws() |>  mutate(type="Only pairs with full statistical info") |> mutate(sens="All data")
-
-sens1_subjective <- read_rds(here(model_location, "sens_tier1_subjective.rds"))|> do_draws() |> mutate(type="All original-replication pairs") |> mutate(sens="Sensitivity test")
-sens2_porig <- read_rds(here(model_location, "sens_tier2_porig.rds"))|> do_draws() |> mutate(type="All original-replication pairs")|> mutate(sens="Sensitivity test")
-sens2_predint <- read_rds(here(model_location, "sens_tier2_predint.rds"))|> do_draws() |> mutate(type="All original-replication pairs")|> mutate(sens="Sensitivity test")
-sens3_subjective <- read_rds(here(model_location, "sens_tier3_subjective.rds"))|> do_draws()|> mutate(type="Only pairs with full statistical info")|> mutate(sens="Sensitivity test")
-sens3_porig <- read_rds(here(model_location, "sens_tier3_porig.rds"))|> do_draws()|> mutate(type="Only pairs with full statistical info")|> mutate(sens="Sensitivity test")
-sens3_predint <- read_rds(here(model_location, "sens_tier3_predint.rds"))|> do_draws()|> mutate(type="Only pairs with full statistical info")|> mutate(sens="Sensitivity test")
-
-subjective <- tier1_subjective |> union(tier3_subjective) |> union(sens1_subjective) |> union(sens3_subjective)
-porig <- tier2_porig |> union(tier3_porig) |> union(sens2_porig) |> union(sens3_porig)
-predint <- tier2_predint |> union(tier3_predint) |> union(sens2_predint) |> union(sens3_predint)
-```
-
-```{r sub-results, out.height="75%", fig.width=8, fig.height=8, fig.pos="ht", fig.cap="Coefficient estimates and uncertainty from ordinal models predicting subjective replication scores.
-Solid lines correspond to models run on as much of the data as possible; dashed lines are on the subset of the data for sensitivity analysis.
-Red is run on all relevant data with experimental predictors only; blue is on relevant data where there are statistical predictors."}
-
-  subjective |> ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate, color=type, linetype=sens, shape=sens)) + geom_vline(xintercept=0)+
-    scale_shape_manual(values = c(19,21))+
-  scale_color_solarized()+
-  stat_pointinterval(position=position_dodge(width=.7))+labs(y="", x="Estimate, 66%, 95% CrI predicting subjective replication score", color="", linetype="", shape="")+theme(axis.text=element_text(size=11),legend.position="bottom")
-
-```
-
-```{r predint-results, out.height="75%", fig.width=8, fig.height=8, fig.pos="ht", fig.cap="Coefficient estimates and uncertainty from logistic models predicting prediction intervals.
-Solid lines correspond to models run on as much of the data as possible; dashed lines are on the subset of the data for sensitivity analysis.
-Red is run on all relevant data with experimental predictors only; blue is on relevant data where there are statistical predictors."}
-
-  predint |> ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate, color=type, linetype=sens, shape=sens)) + geom_vline(xintercept=0)+
-    scale_shape_manual(values = c(19,21))+
-  scale_color_solarized()+
-  stat_pointinterval(position=position_dodge(width=.7))+labs(y="", x="Estimate, 66%, 95% CrI predicting prediction interval", color="", linetype="", shape="")+theme(axis.text=element_text(size=11),legend.position="bottom")
-
-```
-
-```{r porig-results, out.height="75%", fig.width=8, fig.height=8, fig.pos="ht", fig.cap="Coefficient estimates and uncertainty from linear models predicting p-original values.
-Solid lines correspond to models run on as much of the data as possible; dashed lines are on the subset of the data for sensitivity analysis.
-Red is run on all relevant data with experimental predictors only; blue is on relevant data where there are statistical predictors."}
-
-  porig |> ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate, color=type, linetype=sens, shape=sens)) + geom_vline(xintercept=0)+
-    scale_shape_manual(values = c(19,21))+
-  scale_color_solarized()+
-  stat_pointinterval(position=position_dodge(width=.7))+labs(y="", x="Estimate, 66%, 95% CrI predicting p-original values", color="", linetype="", shape="")+theme(axis.text=element_text(size=11),legend.position="bottom")
-
-```
-
-\pagebreak
-
-# Heterogeneity analysis
-
-```{r, echo=F}
-
-all_true <- d |> filter(include %in% c("stats", "pred_int")) |> filter(!is.na(predInt)) |> filter(predInt) |> nrow()
-
-all <- d |> filter(include %in% c("stats", "pred_int")) |> filter(!is.na(predInt)) |> nrow()
-
-#of those with SMD predInts
-all_orig  <- d |>filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> nrow()
-all_orig_true <- d |>filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> filter(predInt) |> nrow()
-all_d_true <- d |> filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> filter(predInt_from_d) |> nrow()
-all_tau <- d |> filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> filter(predInt_with_tau) |> nrow()
-
-```
-
-The prediction interval and p-original values used for models and point estimates were done on the original scale where possible.
-However, to do heterogeneity analysis, our imputed value for tau is in SMD units, so we have to use SMD units for the original and replication values.
-This limits the number of applicable original-replication pairs.
-Prediction intervals are sensitive to whether only studies with SMD are included (different studies report differently and also vary in how close replications were) and whether the scale used was original or SMD (if the variances differed between original and replication).
-
-Of all studies where prediction intervals can be calculated, `r all_true`/`r all` (`r round(all_true/all*100)`%) of the original estimates had prediction intervals that included the replication effect size.
-For those where we have SMD, `r all_orig_true`/`r all_orig` (`r round(all_orig_true/all_orig*100)`%) of the original estimates had prediction intervals that included the replication effect size, when we use original units where possible.
-Using SMD units, `r all_d_true`/`r all_orig` (`r round(all_d_true/all_orig*100)`%) of the original estimates had prediction intervals that included the replication effect size.
-Allowing for heterogeneity, with tau=.21, `r all_tau`/`r all_orig` (`r round(all_tau/all_orig*100)`%) of the original estimates are distributionally consistent.
+\end{document}

### 2023-07-31 paper/manuscript.Rmd
tweaks
final clarifications!

@@
 
-Many predictors correlated with subjective replication success using unadjusted Pearson correlations(Table \ref{tab:cor}).
+Many predictors correlated with subjective replication success using unadjusted Pearson correlations (Table \ref{tab:cor}).
 Predictors of higher replicability included within-participants designs, larger numbers of trials per participant, and the original study having openly accessible data.
@@
 While a number of features show individual correlations with the subjective replication score, many correlate with one another.
-To determine which predictors were the strongest, we ran a series of pre-registered Bayesian regression models using an ordinal link function and  regularized using a horseshoe shrinkage prior [@carvalho09].
+To determine which predictors were the strongest, we modeled subjective replication score as an ordinal outcome using ordinal Bayesian regression models with a logit link function, regularized using a horseshoe shrinkage prior [@carvalho09].
+This model estimates odds ratios representing the association of the predictor with having a higher versus lower subjective replication score.
 We first ran models using all of the original-replication pairs (N=176), but without original effect size and original $p$ value as predictors, as they were uncodable for some pairs.
@@
 
-```{r mod-results, out.width="90%", fig.width=8, fig.height=5, fig.pos="ht", fig.cap="Odds ratios and corresponding uncertaintly estimates on the likelihood of having a higher subjective replication score as a function of the dependent variable.
+```{r mod-results, out.width="90%", fig.width=8, fig.height=5, fig.pos="ht", fig.cap="Odds ratios and corresponding 95\\% CrI on the likelihood of having a higher subjective replication score as a function of the independent variable.
 Estimates from a model of all original-replication pairs (N=176) are shown in blue, and from a model of all pairs with full statistical information (N=112) are shown in red.
-A value of 1 indicates no effect, greater than one indicates an association with higher replication scores and less than 1 an association with lower replication scores."}
+A value of 1 indicates no association, greater than one indicates an association with higher replication scores and less than 1 an association with lower replication scores."}
 
@@
 We thank Ben Prystawski and the FriSem audience for feedback on earlier versions of this work.
-TODO GRANTS??
+MM was supported by R01LM013866.
 
@@
 
-The authors have no conflicts of interest to declare. TODO contributor statement!
+VB and MCF report no conflicts of interest. MM is the Associate Director of the Stanford Center for Open and Reproducible Science.
+
+The authors made the following contributions: VB: Methodology, Data Curation, Formal Analysis, Writing - original draft; 
+MM:  Methodology, Writing - review & editing; 
+MCF: Conceptualization, Methodology, Writing - review & editing.
+
 # References {-}

### 2023-07-31 paper/manuscript.tex
tweaks
final clarifications!

@@
 While a number of features show individual correlations with the subjective replication score, many correlate with one another.
-To determine which predictors were the strongest, we ran a series of pre-registered Bayesian regression models using an ordinal link function and regularized using a horseshoe shrinkage prior (\protect\hyperlink{ref-carvalho09}{Carvalho et al.
+To determine which predictors were the strongest, we modeled subjective replication score as an ordinal outcome using ordinal Bayesian regression models with a logit link function, regularized using a horseshoe shrinkage prior (\protect\hyperlink{ref-carvalho09}{Carvalho et al.
 2009}).
+This model estimates odds ratios representing the association of the predictor with having a higher versus lower subjective replication score.
 We first ran models using all of the original-replication pairs (N=176), but without original effect size and original \(p\) value as predictors, as they were uncodable for some pairs.
@@
 \begin{figure}[ht]
-\includegraphics[width=0.9\linewidth]{manuscript_files/figure-latex/mod-results-1} \caption{Odds ratios and corresponding uncertaintly estimates on the likelihood of having a higher subjective replication score as a function of the dependent variable.
+\includegraphics[width=0.9\linewidth]{manuscript_files/figure-latex/mod-results-1} \caption{Odds ratios and corresponding 95\% CrI on the likelihood of having a higher subjective replication score as a function of the independent variable.
 Estimates from a model of all original-replication pairs (N=176) are shown in blue, and from a model of all pairs with full statistical information (N=112) are shown in red.
-A value of 1 indicates no effect, greater than one indicates an association with higher replication scores and less than 1 an association with lower replication scores.}\label{fig:mod-results}
+A value of 1 indicates no association, greater than one indicates an association with higher replication scores and less than 1 an association with lower replication scores.}\label{fig:mod-results}
 \end{figure}
@@
 
-The authors have no conflicts of interest to declare. TODO contributor statement!
-\# References \{-\}
+VB and MCF report no conflicts of interest. MM is the Associate Director of the Stanford Center for Open and Reproducible Science.
+
+The authors made the following contributions: VB: Methodology, Data Curation, Formal Analysis, Writing - original draft;
+MM: Methodology, Writing - review \& editing;
+MCF: Conceptualization, Methodology, Writing - review \& editing.
+
+\hypertarget{references}{%
+\section*{References}\label{references}}
+\addcontentsline{toc}{section}{References}
 

### 2023-07-31 paper/supplement.Rmd
final clarifications!

@@
 As a check on whether our results were sensitive to the inclusion of pairs that were marginal in some way, we repeated the 6 models including only studies that were not marginal.
+For sensitivity analyses, we completely excluded some studies where the replication analysis was not the focal analysis of the original (ex.
+student chose a manipulation check as their primary analysis).
+We also excluded studies with extremely small or lop-sided sample sizes.
+
+For some studies that were included with some statistical outcomes in the main results, we downgraded them to experimental features only for sensitivity.
+Here, we felt the replication itself didn't have major problems and we felt confident in the subjective replication score reflecting holistically on the replication.
+However, there were some mismatches in the statistical reporting that meant we were not confident enough if your numeric calculations for the paper.
+Common mismatches were  where one reported a t-test and the other reported mean and SDs, and when degrees of freedom seemed inconsistent across replication and original (suggesting different groupings or levels of analysis).
 

### 2023-08-21 paper/manuscript.Rmd
?

@@
 #   - nomarkers # Default
-numberlines: FALSE
+numberlines: TRUE
 authblk: TRUE # FALSE = author affiliations in footnotes; TRUE = author affiliations in a block below author names

### 2023-08-21 paper/coverletter/nhb1.tex
rejected

\documentclass{stanfordletter}
%\makelabels
\begin{document}
	\name{Veronica Boyce}
	\signature{Veronica Boyce \\ Maya Mathur \\ Michael C. Frank}

	\begin{letter}{Dr. Stavroula Kousta \\ Chief Editor \\ Nature Human Behavior}

          \opening{Dear Dr. Kousta,} 
          This
          submission contains the manuscript ``Eleven years of student replication projects provide evidence on
          the correlates of replicability in psychology''
          which we are submitting to Nature Human Behavior for
          publication.

          The manuscript reports on a new dataset of 176 replications of social science experiments conducted by students in a graduate-level methods course. The roughly 170 existing replications from RP:P, ManyLabs, and Camerer et al. (2018) have been heavily discussed and re-analysed. Our current dataset is an independent sample of replications that greatly increases the number of replications.  In the paper, we discuss how being able to replicate a study is a prerequisite to building cumulative science on that finding. Student replications were successful 49\% of the time, indicating that many published findings are out of reach of student investigators.    We examine correlates of replication success, including   statistical, demographic, and  experimental design features.  We find that studies with large original effect sizes and within-subjects designs were the most likely to replicate.

          We believe this paper will be of broad
          interest to psychologists.

          Researchers with relevant expertise and interest who
          therefore might be appropriate reviewers include Brian Nosek, Simine Vazire, Dani\"{e}l Lakens, and Daniel Quintana.

          This manuscript is not under review at any other
          venue. Please let us know if you need any further
          information in connection with this submission. We look
          forward to hearing from you regarding the manuscript!
          \closing{Sincerely,}

	\end{letter}

\end{document}

### 2023-09-25 paper/supplement.Rmd
add median effect sizes to supp

@@
 
-```{r forest, out.height="100%", fig.width=9, fig.height=12, fig.pos="ht", fig.cap="Forest plot of original and replication effect sizes.
+```{r}
+# relative effect size
+
+medians <- d %>% filter(include =="stats") %>% summarize(orig=quantile(target_d_calc), rep=quantile(rep_d_calc))
+
+```
+
+```{r forest, out.height="100%", fig.width=9, fig.height=12, fig.pos="ht", fig.cap="Forest plot of original and replication effect sizes (N=112).
 Original effect sizes are open dots, replication are closed dots.
 Coloring indicates subjective replication score, and p-original values are listed on the left side.
+The median original effect size was .61 and the median replication effect size was .28.
 "}

### 2023-10-03 code/helper/parse_stats.R
found p-value error in parse stats
if tval or whatever was negative, pval was in wrong range since it
takes the upper portion and then x2
now fixed with abs()

@@ -4,7 +4,7 @@
 parse_t <- function(tval, within_between) {
   df=str_extract(tval, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
   val=str_extract(tval, "=.*") |> str_sub(2,-1) |> as.numeric() |> abs()
-  pval=pt(q=val, df=df, lower.tail=FALSE)*2
+  pval=pt(q=abs(val), df=df, lower.tail=FALSE)*2
   d_calc=NA
   N_from_df=NA
   if(within_between=="between"){
@@ -88,7 +88,7 @@ parse_mean_sd1 <- function(msd,within_between,n){
   d_calc=abs(m1-comp)/sd1 # note we force all positive and then fix later 
   tval=(m1-comp)/se |> abs()
   df=n-1
-  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
+  pval=pt(q=abs(tval), df=df, lower.tail=FALSE)*2
   d_se=4/n+d_calc**2/(2*n)
   
   return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "d_calc_se"=d_se,"N_calc"=NA, "ES"=m1-comp, "SE"=se))
@@ -107,7 +107,7 @@ parse_mean_se1 <- function(mse,within_between,n){
   d_calc=abs(m1-comp)/sd1 # note we force all positive and then fix later 
   tval=(m1-comp)/se1 |> abs()
   df=n-1
-  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
+  pval=pt(q=abs(tval), df=df, lower.tail=FALSE)*2
   d_se=4/n+d_calc**2/(2*n)
   
   return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "d_calc_se"=d_se, "N_calc"=NA, "ES"=m1-comp, "SE"=se1))
@@ -136,7 +136,7 @@ parse_mean_ci2 <- function(mci,within_between,n){
   d_calc=abs(m1-m2)/sd_pool # note we force all positive and then fix later 
   tval=(m1-m2)/se_pool |> abs()
   df=ifelse(within_between=="within", n-1, n-2)
[…]

### 2023-10-04 paper/manuscript.tex
?
propagate p-value issue changes

@@
 % Line numbering
+\usepackage{lineno}
+\linenumbers
 
@@
 Within-participants designs stand out as the strongest correlate of replicability in the model with all the data (OR = 2.56, 95\% CrI = {[}1, 7.36{]}).
-In the model with all predictors, but less data, within-participants designs remain strong (OR = 2.76, 95\% CrI = {[}0.97, 10.71{]}), and standardized effect size is also substantially related to subjective replication score (OR = 4.36, 95\% CrI = {[}1.31, 16.65{]}).
-Both effects are robust to a sensitivity analysis including only studies with close replications and matching statistical tests (within-participants OR = 4.45, 95\% CrI = {[}0.99, 28.08{]}; effect size OR = 13.93, 95\% CrI = {[}2.15, 131.6{]}).
+In the model with all predictors, but less data, within-participants designs remain strong (OR = 2.84, 95\% CrI = {[}0.95, 10.9{]}), and standardized effect size is also substantially related to subjective replication score (OR = 3.32, 95\% CrI = {[}1.04, 11.99{]}).
+Both effects are robust to a sensitivity analysis including only studies with close replications and matching statistical tests (within-participants OR = 3.7, 95\% CrI = {[}0.98, 21.2{]}; effect size OR = 7.34, 95\% CrI = {[}1.25, 48.65{]}).
 
@@
 While the credible intervals were wide, the general patterns of predictor direction and relative strength were similar to the subjective replication models (see Supplement for results from all models).
-The strongest predictors for prediction interval were still within-participants designs (OR = 1.79, 95\% CrI = {[}0.83, 7.44{]}) and studies with larger effect sizes (OR = 1.17, 95\% CrI = {[}0.75, 2.57{]}).
+The strongest predictors for prediction interval were still within-participants designs (OR = 1.89, 95\% CrI = {[}0.84, 8.98{]}) and studies with larger effect sizes (OR = 1.2, 95\% CrI = {[}0.75, 2.81{]}).
 

### 2023-10-12 paper/coverletter/rsos_response.tex
work on edits in response to reviewers

\documentclass{stanfordletter}
%\makelabels
\usepackage{todonotes}
\usepackage{varioref}
\usepackage{xr}
%\externaldocument[paper-]{../revision}
\usepackage[american]{babel}
\usepackage{csquotes}
\usepackage[backend=biber,style=apa,doi=false,url=false,hyperref=true,apamaxprtauth=30,uniquename=false]{biblatex}
\DeclareLanguageMapping{american}{american-apa}
%\bibliography{../draft0}
\newcommand{\citet}[1]{\textcite{#1}}
\newcommand{\citep}[1]{\parencite{#1}}

%\makelabels
\newcommand{\theysaid}[1]{\begin{leftbar} \noindent 
		\textsl{ #1}\end{leftbar}}
\newcommand{\revised}[1]{\begin{quote}		#1 \end{quote}}

\begin{document}
	\name{Veronica Boyce}
	\signature{Veronica Boyce \\ Maya Mathur \\ Michael C. Frank}

	\begin{letter}{Dr Christina Demski \\ Associate Editor, Royal Society Open Science}

          \opening{Dear Dr Christina Demski,}

          Thank you for your speedy response to our submission. 
          To address reviewer points, we are quoting the decision letter with our point-by-point responses and revised text.

          Before we get to responses to reviewers, we should mention for transparency that we found an error in our code for calculating p-values that affected 26 rows of the data. This has been fixed and all analyses downstream of the problem have been rerun and the changes propagated to the manuscript, with no substantial changes to results or interpretation. (We were missing an absolute value function; which led to taking the wrong tail for p-values where the t-value was negative.)

          \theysaid{Both reviewers were in agreement that the manuscript is well written and describes a dataset and series of analyses that will be of interest to the readers of the journal. There were only a few minor points that they like to see addressed and responded to before it can be published. We would like to see your responses to these suggestions.}

          \theysaid{Reviewer comments to Author:

          Reviewer: 1
          Comments to the Author(s)
          I have read this manuscript with great enthusiasm. It provides an important infusion of new data into a field that is very much oversaturated with analyses of what little data there is.
        }

        \theysaid{

          I find the report to be clearly written, well-documented, of a sensible length, and appropriately cautious when discussing the generalizability and potential causal implications of the reported results. But for a single minor issue, I believe the report could be accepted as is.

          The only thing I miss in the current manuscript is some description/discussion of how close/conceptual replications in the sample tended to be. See LeBel et. al. (2018, figure 1; https://doi.org/10.1177/2515245918787489) for a taxonomy of replication closeness. It would not need to be a long section, and I am not saying the authors need to code closeness for all studies included, or anything like that. However, I recommend adding a short paragraph to give readers a sense of how closely the original procedures were followed in the replications (on average/in general). The rationale being that I would generally expect a higher replication rate the closer replication procedures are to the original. Having a sense of what mix of close/conceptual replications in this sample is thus relevant for my interpretation of the overall replicability estimate.}

          TODO our response!

          We've added TODO what we add

          We considered coding for closeness (and started to do so in a preliminary stage) but couldn't come up with a scheme that felt meaningfully uniform. We thank the reviewer for the pointer to LeBel!

          From memory, I think we have a range from exact replication to very close replication to close replication.

          For studies that were originally done online and had open materials, may have approached exact replication. (Ex. the study I did, there was javascript for running the study available and I rehosted it, so the procedure was identical).

          Many switched to online and may have had procedural differences as a result (or as a result of instruction text not being available and students recreating from what the manuscript said).

          When possible the stimuli were usually the same. In a couple cases, populations and stimuli were farther due to language changes. In some cases, stimuli weren't available, and so were recreated to match as was possible.

          Population was different in some cases due to switches from college student to crowdworker; in one case from high school to young adult crowd worker; and in some cases from "hiring manager" to crowdworker.

          This is why we're careful to frame as "how well can grad students redo" -- closeness was dependent on factors like avialable and ease, and varies by study in how much it calls into question the original study results.

          \theysaid{Reviewer: 2
          	Comments to the Author(s)
          	This is an excellent contribution, and I have only minor suggestions for the authors. I should state upfront that, unfortunately, I was more rushed than I expected to be when doing this review, and so did not access the data or code, or any supplemental materials.  I glanced at the preregistration.  I also lack the expertise to evaluate the statistical approach.
          }

          \theysaid{	1a. I believe there are some deviations from the preregistration (e.g., year of publication is mentioned as a potential predictor (with no directional hypothesis) in the preregistration but is not in the results; other variables appear in the manuscript but not in the preregistration). The authors should be clear about these deviations and also any decisions that were not constrained by the preregistration. Perhaps a disclosure table would be a good way to share this information.}

          TODO check deviations

          We did include publication year in the models (and in the not-pre-registered list of correlations).

          \theysaid{
          	1b. Even though the analyses are preregistered, I assume that the decisions made in the preregistration were not made without any knowledge of the data.  That is, the people involved in making the decisions in the preregistration presumably knew/remembered some of the outcomes of the replication studies.  Of course this is fine, but I think it makes the choices and analyses slightly data-dependent, and therefore more susceptible to inadvertently overfitting the models to this dataset. I think it would be good to point this out to readers, and calibrate claims appropriately (I think the claims are already well-calibrated, in that the authors don't make strong claims, which is appropriate for several reasons).
          }

          In fact, much of the data-coding had been done when the pre-registration was finalized, due to the need to figure out what variables were actually codeable.

          \theysaid{
          	2. There are some descriptive variables that I would have liked to see in the main text, such as the number of studies at each level of each of the predictor variables, the correlations among the predictor variables, and the correlations among the outcome variables.
          }

          \theysaid{
          	3. I was curious to know the magnitude of the difference in effect sizes between the original studies and replication studies, for: 1) all studies, and 2) just the "successful" replications.
          }

          \theysaid{
          	4. The authors are appropriately cautious in drawing conclusions, for example about the effect of within-participant designs.  I would suggest adding that it's possible one factor that contributed to this effect is that within-participant designs could be more susceptible to artifacts, such as demand characteristics, that could inflate the replicability of the result but not its accuracy.  This is also a reason to caution against simply adopting a within-participant design as a way to improve replicability in future studies, without considering the potential costs to other aspects of validity/accuracy of the results.
          }
          \theysaid{
          	5. I was curious whether the authors considered inviting the graduate students who ran the studies as co-authors/contributors on this paper. I could see good reasons for either decision, but just wanted to raise the question.
          }

          \theysaid{
          	6. Personally, I was curious about how the "date of original study publication" fared as a predictor, as well as whether being published in Psych Science was a predictor (I have a conflict of interest in asking about this, I am the incoming editor in chief of Psych Science).  Of course readers can presumably analyze these themselves, but I wonder if it would be worth including at least publication year, as that was in the preregistration (and I also thought of it before looking at the preregistration, and I expect other readers might wonder the same thing).
          }
          We do have publication year. We've added a more clear mention in the text. It is correlated with practices that have changed over time, such as open data, open materials, and online samples, which basically means it's correlated with closeness of replication.

          Psych Science makes up TODO \% of the sample, so we couldn't really use it as a predictor, since other journals are much much less represented.

          	\theysaid{
          	Minor typos:
          	section 2.1 "of replications has outcomes with" should be "had"
          	section 4.3 "ramapped" should be "remapped"
          }
          Fixed, thank you!

          \closing{Sincerely,}

	\end{letter}

\end{document}

### 2023-10-12 paper/manuscript.Rmd
work on edits in response to reviewers

--- 2023-07-31 paper/manuscript.Rmd
@@
 bibliography: ["251MA.bib"] # Replace with one or more of your own bibtex files. Better BibTeX for Zotero is your friend
-csl: dmk-format.csl # Use any CSL style. See https://www.zotero.org/styles for a good list. Ignored if citation_package: natbib
+csl: vancouver.csl # Use any CSL style. See https://www.zotero.org/styles for a good list. Ignored if citation_package: natbib
 link-citations: TRUE
@@
 library(ggthemes)
+library(reshape2)
 #r_refs("r-references.bib", append=F)
@@
 
-# sample size considerations
+# correlations between outcome measures
 
-# ggplot(d, aes(x=target_N, y=replication_N, color=as.factor(sub_rep)))+geom_point()+coord_trans(x="log", y="log")+geom_abline(slope=1)+ scale_color_viridis(discrete=T, direction = 1, 
-#                       name = "Subjective\nReplication\nSuccess\n")
-# d |> mutate(bigger_orig=replication_N<.9*target_N,
-#             bigger_rep=replication_N>1.1*target_N,
-#             similar=!bigger_orig & !bigger_rep) |> 
-#   group_by(bigger_orig, bigger_rep, similar) |> tally()
+for_cor <- d %>% filter(include %in% c("stats", "pred_int")) %>% 
+  mutate(predInt=as.numeric(predInt))
+sub_pred <- cor.test(for_cor$sub_rep, for_cor$predInt)$estimate
+sub_p <- cor.test(for_cor$sub_rep, for_cor$p_orig)$estimate
+pred_p <- cor.test(for_cor$predInt, for_cor$p_orig)$estimate
 
@@
 Across the 176 studies, the average subjective replication score was `r round(pluck(sub_rep_rate,1))`%, which we can interpret as an overall subjective replication rate.
-`r round(pluck(pred_int_rate,1))`% (`r predIntcount`/`r predInttotal`) of replications has outcomes with point-estimates within the prediction interval of the original outcome.
+`r round(pluck(pred_int_rate,1))`% (`r predIntcount`/`r predInttotal`) of replications had outcomes with point-estimates within the prediction interval of the original outcome.
 The median *p*-original value on the original and replication point-estimates coming from the same distribution was `r round(pluck(porig_rate, 1),2)`, representing the median probability that a replication study's estimate would be at least as extreme as was actually observed, if in fact the replication and original were statistically consistent.
+The subjective replication scores were moderately correlated with both prediction interval (r=`r round(sub_pred,2)`) and *p*-original (r=`r round(sub_p, 2)`) values; prediction interval and *p*-original were highly correlated with each other (r=`r round(pred_p,2)`).
+
+```{r}
+medians <- d %>% filter(include =="stats") %>%
+  mutate(difference=target_d_calc-rep_d_calc) %>% summarize(orig=quantile(target_d_calc), rep=quantile(rep_d_calc), diff=quantile(difference))
+
+original_50  <- pluck(medians, 1,3) %>% round(2)
+original_25 <- str_c(pluck(medians, 1,2) %>% round(2)," - ",pluck(medians, 1,4) %>% round(2))
+
+rep_50  <- pluck(medians, 2,3) %>% round(2)
+rep_25 <- str_c(pluck(medians, 2,2) %>% round(2)," - ",pluck(medians, 2,4) %>% round(2))
+
+diff_50 <- pluck(medians, 3,3) %>% round(2)
+diff_25 <- str_c(pluck(medians, 3,2) %>% round(2)," - ",pluck(medians, 3,4) %>% round(2))
+
+medians_successful <- d %>% filter(include =="stats") %>%
+  filter(sub_rep %in% c(1)) %>% 
+    mutate(diff=target_d_calc-rep_d_calc) %>%
+  summarize(orig=quantile(target_d_calc), rep=quantile(rep_d_calc),
+            diff=quantile(diff))
+
+original_50_succ  <- pluck(medians_successful, 1,3) %>% round(2)
+original_25_succ <- str_c(pluck(medians_successful, 1,2) %>% round(2)," - ",pluck(medians_successful, 1,4) %>% round(2))
+
+rep_50_succ <- pluck(medians_successful, 2,3) %>% round(2)
+rep_25_succ <- str_c(pluck(medians_successful, 2,2) %>% round(2)," - ", pluck(medians_successful, 2,4) %>% round(2))
+
+diff_50_succ <- pluck(medians_successful, 3,3) %>% round(2)
+diff_25_succ <- str_c(pluck(medians_successful, 3,2) %>% round(2)," - ",pluck(medians_successful, 3,4) %>% round(2))
+
+n_successful <- d %>% filter(include =="stats") %>%
+  filter(sub_rep %in% c(1)) %>% nrow()
+```
 
@@
 Some studies replicated with similar size effects to the original, and others failed to replicate, with replication effect sizes near zero.
+
 On average, there was a diminution of effect sizes from original to replication.
 This pattern of results is consistent with the results of RP:P [@openscienceconsortium2015].
+Specifically, the median original effect size (in SMD units) was `r original_50` (interquartile range: `r original_25`), and the median replication effect size was `r rep_50` (`r rep_25`), for a median difference of `r diff_50` (`r diff_25`).
+Among the pairs with a subjective replication score of 1 (N=`r n_successful` with standardized effect sizes), the median original effect size was `r original_50_succ` (interquartile range: `r original_25_succ`), and the median replication effect size was `r rep_50_succ` (`r rep_25_succ`), for a median difference of `r diff_50_succ` (`r diff_25_succ`).
+Thus, for the highest subjectively-rated replications, effect sizes for original and replication were similar in magnitude on average, with some replications having larger effects than their originals.
 
@@
 
+```{r}
+library(gtsummary)
+theme_gtsummary_language("en", big.mark = "")
+library(kableExtra)
+
+desc <- d %>% mutate(target_d_calc=ifelse(include=="stats", target_d_calc, NA),
+             target_p_calc=ifelse(include=="stats",target_p_calc, NA),
+      switch_modality=ifelse(target_on_turk!=replication_on_turk,1,0),
+         ss_ratio=replication_N/target_N)%>% 
+  select("subfield","open_data", "open_materials","switch_modality",  "stanford_internal","within_between","single_vignette","repeated_measure","target_year","target_N","replication_N", "ss_ratio", "target_d_calc", "target_p_calc") %>%
+  mutate(subfield=factor(subfield, levels=c("cognitive", "social", "other-psych", "non-psych"), labels=c("Cognitive", "Social", "Other psych", "Non-psych")),
+         within_between=ifelse(within_between=="between", 0, 1)) %>% 
+             tbl_summary(
+               label=list(
+                 subfield ~ "Subfield",
+                 stanford_internal ~ "Original authors at Stanford",
+                 target_year~ "Publication Year",
+                 single_vignette ~ "Single vignette",
+                 open_data ~ "Open data",
+                 open_materials ~ "Open materials",
+                 within_between ~ "Within subjects design",
+                 repeated_measure ~ "Number of trials",
+                 target_N ~ "Original sample size",
+                 replication_N ~ "Replication sample size",
+                 ss_ratio ~ "Ratio of replication/original sample sizes",
+                 target_d_calc ~"Original effect size (SMD)",
+                 target_p_calc ~ "Original p-value",
+                 switch_modality ~ "Switch from in-person to online"
+               ),
+               statistic = list(all_continuous() ~ "{mean} ({sd})", all_continuous() ~ "{median} ({p25}, {p75})"),
+               digits=list(target_year ~ 0, target_p_calc ~4),
+    missing="no",
+             ) %>% modify_header(label="Feature", stat_0="Summary") %>% 
+    modify_footnote(update = everything() ~ NA)
+
+as_kable_extra(desc,format="latex", position="!h", caption="Descriptive properties of the replication dataset.
+For categorical features, counts and percentages are given.
+For continuous features, the median value and interquartile range are given.
+N=176 except for original effect size and p-value where N=112.
+", booktabs=TRUE, linesep="") |> kable_styling(full_width=F, font_size=10)
+
+```
 ## Bivariate correlates of replication success
@@
 
+```{r corr-plot, out.height="40%", fig.width=8, fig.height=4.5, fig.pos="ht", fig.cap="Correlations between predictors. See TODO Table 1 or Methods for descriptions. "}
+dat <-  for_cor %>% mutate(cognitive=ifelse(subfield=="cognitive",1,0)) %>% select(-sub_rep, -subfield)
+
+corr_mat <- round(cor(dat),2)
+
+# Install and load reshape2 package
+
+# reduce the size of correlation matrix
+melted_corr_mat <-melt(corr_mat) %>% 
+  mutate(value=ifelse(Var1==Var2, NA, value),
+         value=ifelse(Var1 %in% c("cognitive", "non_psych", "other_psych", "social") &
+                        Var2 %in% c("cognitive", "non_psych", "other_psych", "social"),
+                      NA, value)) %>% 
+  mutate(Var1=factor(Var1, levels=c("social", "cognitive", "other_psych", "non_psych", "is_within", "single_vignette", "stanford", "change_platform", "open_data", "open_mat", "pub_year", "log_trials", "log_sample", "log_ratio_ss"), labels=c("Social psych", "Cognitive psych", "Other psych", "Non-psych", "Within participants design", "Single vignette ","Stanford affiliated", "Switch to online", "Open data", "Open materials", "Publication year", "Log # of trials", "Log original sample size", "Log ratio rep/original sample sizes")),
+         Var2=factor(Var2, levels=c("social", "cognitive", "other_psych", "non_psych", "is_within", "single_vignette", "stanford", "change_platform", "open_data", "open_mat", "pub_year", "log_trials", "log_sample", "log_ratio_ss"), labels=c("Social psych", "Cognitive psych", "Other psych", "Non-psych", "Within participants design", "Single vignette ","Stanford affiliated", "Switch to online", "Open data", "Open materials", "Publication year", "Log # of trials", "Log original sample size", "Log ratio rep/original sample sizes")))
+
+# plotting the correlation heatmap
+ggplot(data = melted_corr_mat, aes(x=Var1, y=Var2,
+                                   fill=value)) + #scale_fill_viridis()+
+  theme_classic()+
+  scale_fill_gradient2(low="#763386",high="#FDE725FF", na.value="grey")+
+  labs(x="", y="")+
+  geom_tile(alpha=.7)+
+  theme(axis.text.x = element_text(angle = 40, vjust = 1, hjust=1), legend.position="none")+
+  geom_text(aes(label=value), size=3)
+
+```
 Distributions of study outcomes across some of these properties are shown in Figure \ref{fig:predictors-graph}.
@@
 Studies with multiple vignettes replicated more often than single vignetted studies (mean scores: `r pluck(vignette,2,1) |> round(2)` versus `r pluck(vignette,2,2) |> round(2)`).
-However, there were strong correlations among these experimental features as well as between these experimental features and specific subfields.
+However, there were strong correlations among these experimental features as well as between these experimental features and specific subfields (Figure \ref{fig:corr-plot}).
 
@@
 While online studies in general show comparable results to studies conducted in person [@crump2013], switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well-adapted (e.g., inductions might have been weaker or instructions might have been insufficient).
-These factors -- open materials, open data, and online samples -- are more common in more recent studies, and so these effects may partially reflect temporal trends.
+These factors -- open materials, open data, and online samples -- are more common in more recent studies, and so these effects may partially reflect temporal trends (see Figure \ref{fig:corr-plot} for the correlations between these factors and publication year).
 
@@
 # Methods
-Our pre-registration, code, and coded data are available at https://osf.io/xwn9m/. <!--TODO VIEW ONLY https://osf.io/xwn9m/?view_only=ebb6df1ae97045cfa5154d6119ec20b1-->
+Our pre-registration, code, and coded data are available at https://osf.io/xwn9m/ [@osfdata]. <!--TODO VIEW ONLY https://osf.io/xwn9m/?view_only=ebb6df1ae97045cfa5154d6119ec20b1-->
 
@@
 Students were encouraged to do experimental replications, but some students chose to replicate correlational outcomes or do computational reproducibility projects instead.
-We cannot include the full student reports for confidentiality reasons, but we include over 50 reports that we received permission to share and the template given to students at https://osf.io/xwn9m/.
+We cannot include the full student reports for confidentiality reasons, but we include over 50 reports that we received permission to share and the template given to students at https://osf.io/xwn9m/ [@osfdata].
 <!-- TODO VIEW ONLY-->
@@
 
-Four of the replication projects were included in RP:P, and 10 were previously reported in @hawkins2018 (which reported 11 student replications from the 2015-2016 class, one of those was excluded from the current sample for being non-experimental).
+Four of the replication projects were included in RP:P, and 10 were previously reported in @hawkins2018 (which reported 11 student replications from the 2015-2016 class; one of those was excluded from the current sample for being non-experimental).
 
@@
 
-The subjective replication scores were coded on [0, .25, .5, .75, 1], and we ramapped these to 1-5 to run an ordinal regression predicting replication score.
+The subjective replication scores were coded on [0, .25, .5, .75, 1], and we remapped these to 1-5 to run an ordinal regression predicting replication score.
 We ran logistic regressions predicting prediction interval and linear regressions predicting $p$-original.

### 2023-10-12 paper/manuscript.tex
work on edits in response to reviewers

@@
 % Line numbering
-\usepackage{lineno}
-\linenumbers
 
@@
 Yet in psychology, some prominent individual findings have failed to replicate in multi-site replication attempts (ex.
-terror management theory, \protect\hyperlink{ref-klein2022}{Klein et al.
-2022}, ego-depletion, \protect\hyperlink{ref-hagger2016}{Hagger et al.
-2016}).
-One early large-scale replication project pegged the replication rate for findings in top-tier psychology journals at around 40\% {[}RP:P; Open Science Consortium (\protect\hyperlink{ref-openscienceconsortium2015}{2015}){]}.
+terror management theory, \protect\hyperlink{ref-klein2022}{1},ego-depletion, \protect\hyperlink{ref-hagger2016}{2}).
+One early large-scale replication project pegged the replication rate for findings in top-tier psychology journals at around 40\% {[}RP:P; (\protect\hyperlink{ref-openscienceconsortium2015}{3}){]}.
 Low replicability has negative consequences for the field as a whole: when scientists attempt to build on published results, they stand a good chance of meeting with failure.
 
-Addressing this issue requires a better understanding of the scope of the problem as well as the methodological and structural issues that might lead to replication failure (\protect\hyperlink{ref-simmons2011}{Simmons et al.
-2011}, e.g., \protect\hyperlink{ref-smaldino2016}{Smaldino \& McElreath 2016}).
+Addressing this issue requires a better understanding of the scope of the problem as well as the methodological and structural issues that might lead to replication failure (e.g., \protect\hyperlink{ref-smaldino2016}{4},\protect\hyperlink{ref-simmons2011}{5}).
 Estimating replicability in the literature is a key starting point, but, as we review below, there is limited consensus on what quantity exactly should be estimated.
@@
 A few large-scale investigations have measured replication rates in samples of psychology studies.
-The first of these, RP:P, sampled roughly 100 studies from articles published in three top psychology journals in 2008 and distributed the studies across participating labs, finding an overall replication rate of around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}).
+The first of these, RP:P, sampled roughly 100 studies from articles published in three top psychology journals in 2008 and distributed the studies across participating labs, finding an overall replication rate of around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{3}).
 The followup Many Labs studies investigated heterogeneity using short target studies that each compared two conditions.
 These study designs were not representative of the psychology literature as a whole, and due to the goal of measuring heterogeneity, they had large overall samples across multiple sites.
-Across Many Labs 1--3, only 29 of 51 target effects (57\%) replicated (\protect\hyperlink{ref-klein2014}{Klein et al.
-2014}, \protect\hyperlink{ref-ebersole2016}{Ebersole et al.
-2016}, \protect\hyperlink{ref-klein2018}{Klein et al.
-2018}).
-Camerer et al.
-(\protect\hyperlink{ref-camerer2018}{2018}) included all 21 behavioral social science studies from Nature and Science from 2010-2015 that were feasible to replicate.
+Across Many Labs 1--3, only 29 of 51 target effects (57\%) replicated (\protect\hyperlink{ref-klein2014}{6}--\protect\hyperlink{ref-ebersole2016}{8}).
+(\protect\hyperlink{ref-camerer2018}{9}) included all 21 behavioral social science studies from Nature and Science from 2010-2015 that were feasible to replicate.
 They consulted original authors and had high power to detect even small effects; under these conditions and with this sample, the replication rate was around 60\%.
@@
 While their sampling procedure and methods varied, these previous approaches to replicability have all focused on interpreting their results in terms of a potentially problematic estimand: the probability of a finding in the literature being truly replicable.
-Critics have pointed out that ``true'' replicability may not be possible to estimate outside of a specific sample (\protect\hyperlink{ref-vanbavel2016}{Van Bavel et al.
-2016}) or even time period (\protect\hyperlink{ref-ramscar2015}{Ramscar et al.
-2015}).
+Critics have pointed out that ``true'' replicability may not be possible to estimate outside of a specific sample (\protect\hyperlink{ref-vanbavel2016}{10}) or even time period (\protect\hyperlink{ref-ramscar2015}{11}).
 
@@
 Many Labs estimated the rate at which well-known, two-condition findings replicate in very large samples.
-Camerer et al.
-(\protect\hyperlink{ref-camerer2018}{2018}) estimated which prestigious journal findings replicate when conducted in a highly-resourced environment with expert involvement.
+(\protect\hyperlink{ref-camerer2018}{9}) estimated which prestigious journal findings replicate when conducted in a highly-resourced environment with expert involvement.
 All of these could be potentially desirable estimands.
@@
 Despite variation in the methods and outcomes used by large-scale replication studies, they are often aggregated together in analyses looking at the predictability of replication success.
-Prediction markets and elicitations have established that people can predict above chance what studies will replicate (\protect\hyperlink{ref-dreber2015}{Dreber et al.
-2015}, \protect\hyperlink{ref-camerer2018}{Camerer et al.
-2018}, \protect\hyperlink{ref-forsell2019}{Forsell et al.
-2019}, \protect\hyperlink{ref-hoogeveen2019}{Hoogeveen et al.
-2019}), but have not identified concrete predictors that differentiate replications from non-replications.
-Machine learning approaches trained on the available replications are also above chance at predicting replication success (\protect\hyperlink{ref-yang2020}{Yang et al.
-2020}, \protect\hyperlink{ref-youyou2023}{Youyou et al.
-2023}), though again the precise features relating to success are unclear.
+Prediction markets and elicitations have established that people can predict above chance what studies will replicate (\protect\hyperlink{ref-camerer2018}{9},\protect\hyperlink{ref-hoogeveen2019}{12}--\protect\hyperlink{ref-forsell2019}{14}), but have not identified concrete predictors that differentiate replications from non-replications.
+Machine learning approaches trained on the available replications are also above chance at predicting replication success (\protect\hyperlink{ref-yang2020}{15},\protect\hyperlink{ref-youyou2023}{16}), though again the precise features relating to success are unclear.
 
 In search of such features, RP:P examined correlates of replicability in the RP:P sample and found that studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller \(p\) values were more likely to replicate.
-Using these same data combined with a few other smaller samples, Altmejd et al.
-(\protect\hyperlink{ref-altmejd2019}{2019}) examined statistical and demographic features of replication studies and identified larger sample sizes, larger effect sizes, and simple effects (as opposed to interaction terms) as predictive of replication.\footnote{While most approaches to correlates of replicability have been correlational, experimental approaches can be used to test potential interventions (\protect\hyperlink{ref-ebersole2020}{Ebersole et al.
-2020}, \protect\hyperlink{ref-protzko2020}{Protzko et al.
-2020}).
+Using these same data combined with a few other smaller samples, (\protect\hyperlink{ref-altmejd2019}{17}) examined statistical and demographic features of replication studies and identified larger sample sizes, larger effect sizes, and simple effects (as opposed to interaction terms) as predictive of replication.\footnote{While most approaches to correlates of replicability have been correlational, experimental approaches can be used to test potential interventions (\protect\hyperlink{ref-protzko2020}{18},\protect\hyperlink{ref-ebersole2020}{19}).
 Experiments can be very valuable as tests of specific causes of non-replication, but they are expensive and time-consuming to conduct, and not all factors affecting replication success can be manipulated experimentally.}
@@
 Large-scale replications are arduous and expensive to run, so only a few large-scale replication datasets exist, and most analyses draw heavily on same small set of data points.
-In particular, the RP:P dataset is much discussed and reanalyzed (\protect\hyperlink{ref-anderson2016}{Anderson et al.
-2016}, \protect\hyperlink{ref-etz2016}{Etz \& Vandekerckhove 2016}, \protect\hyperlink{ref-gilbert2016}{Gilbert et al.
-2016}, \protect\hyperlink{ref-patil2016}{Patil et al.
-2016}) -- to the point that much of what we think we know about replicability may be over-fit to the 100 studies included in RP:P.
+In particular, the RP:P dataset is much discussed and reanalyzed (\protect\hyperlink{ref-etz2016}{20}--\protect\hyperlink{ref-anderson2016}{23}) -- to the point that much of what we think we know about replicability may be over-fit to the 100 studies included in RP:P.
 
@@
 Within-participants designs lead to more precise experimental estimates by allowing the estimation of correlated person-level variation across conditions; repeated measures allow for more precise estimation by averaging out measurement error.
-Both are often recommended by methodologists as part of good measurement practices, at least when they are feasible (\protect\hyperlink{ref-greenwald1976}{Greenwald 1976}, \protect\hyperlink{ref-rosenthal2008}{Rosenthal \& Rosnow 2008}, \protect\hyperlink{ref-frank2023}{Frank et al.
-2023}).
+Both are often recommended by methodologists as part of good measurement practices, at least when they are feasible (\protect\hyperlink{ref-rosenthal2008}{24}--\protect\hyperlink{ref-frank2023}{26}).
 
@@
 
-Many different measures can be used to define replication success of an individual statistical result (\protect\hyperlink{ref-gelman2018}{Gelman 2018/ed}, \protect\hyperlink{ref-simonsohn2015}{Simonsohn 2015}, \protect\hyperlink{ref-mathur2020}{Mathur \& VanderWeele 2020}).
+Many different measures can be used to define replication success of an individual statistical result (\protect\hyperlink{ref-simonsohn2015}{27}--\protect\hyperlink{ref-mathur2020}{29}).
 However, whether a replication should be considered successful is not always dependent on only one statistical comparison between the two studies.
@@
 As a complement to our primary subjective outcome, we also used two statistical measures of replication on the subset of the data where they were computable for the key statistic of interest (136 cases, see Figure \ref{fig:prisma}).
-We used \emph{p-original}, the \emph{p}-value on the null hypothesis that the original and replication statistics are from the same distribution, and \emph{prediction interval}, a binary measure of whether the replication statistic fell within the prediction interval of the original statistic (\protect\hyperlink{ref-mathur2020}{Mathur \& VanderWeele 2020}).
+We used \emph{p-original}, the \emph{p}-value on the null hypothesis that the original and replication statistics are from the same distribution, and \emph{prediction interval}, a binary measure of whether the replication statistic fell within the prediction interval of the original statistic (\protect\hyperlink{ref-mathur2020}{29}).
 The prediction interval depends on the level of evidence of the original study; if the effect was marginal, the prediction interval could overlap zero; thus, a replication might fall within the predictive interval, and be consistent with the original outcome, but not provide compelling evidence for the claimed effect.
@@
 Across the 176 studies, the average subjective replication score was 49\%, which we can interpret as an overall subjective replication rate.
-46\% (62/136) of replications has outcomes with point-estimates within the prediction interval of the original outcome.
+46\% (62/136) of replications had outcomes with point-estimates within the prediction interval of the original outcome.
 The median \emph{p}-original value on the original and replication point-estimates coming from the same distribution was 0.03, representing the median probability that a replication study's estimate would be at least as extreme as was actually observed, if in fact the replication and original were statistically consistent.
+The subjective replication scores were moderately correlated with both prediction interval (r=0.37) and \emph{p}-original (r=0.29) values; prediction interval and \emph{p}-original were highly correlated with each other (r=0.73).
 
@@
 Some studies replicated with similar size effects to the original, and others failed to replicate, with replication effect sizes near zero.
+
 On average, there was a diminution of effect sizes from original to replication.
-This pattern of results is consistent with the results of RP:P (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}).
-
-Some multi-site replication projects have found heterogeneity in effect sizes across replication sites (\protect\hyperlink{ref-klein2018}{Klein et al.
-2018}, \protect\hyperlink{ref-ebersole2020}{Ebersole et al.
-2020}, \protect\hyperlink{ref-olsson2020}{Olsson-Collentine et al.
-2020}).
-As a test of sensitivity to heterogeneity, we assumed that the level of heterogeneity in hypothetical multi-site replications of our sampled articles was the same as the average level heterogeneity found by Olsson-Collentine et al.
-(\protect\hyperlink{ref-olsson2020}{2020}) in prior multi-site replications in psychology (\(\tau=.21\) in units of standardized mean difference).
+This pattern of results is consistent with the results of RP:P (\protect\hyperlink{ref-openscienceconsortium2015}{3}).
+Specifically, the median original effect size (in SMD units) was 0.61 (interquartile range: 0.46 - 0.98), and the median replication effect size was 0.28 (0.09 - 0.76), for a median difference of 0.3 (0.03 - 0.64).
+Among the pairs with a subjective replication score of 1 (N=38 with standardized effect sizes), the median original effect size was 0.92 (interquartile range: 0.52 - 1.4), and the median replication effect size was 0.89 (0.57 - 1.24), for a median difference of 0.02 (-0.16 - 0.3).
+Thus, for the highest subjectively-rated replications, effect sizes for original and replication were similar in magnitude on average, with some replications having larger effects than their originals.
+
+Some multi-site replication projects have found heterogeneity in effect sizes across replication sites (\protect\hyperlink{ref-klein2018}{7},\protect\hyperlink{ref-ebersole2020}{19},\protect\hyperlink{ref-olsson2020}{30}).
+As a test of sensitivity to heterogeneity, we assumed that the level of heterogeneity in hypothetical multi-site replications of our sampled articles was the same as the average level heterogeneity found by (\protect\hyperlink{ref-olsson2020}{30}) in prior multi-site replications in psychology (\(\tau=.21\) in units of standardized mean difference).
 Under this assumption, 64\% (72/112) of replication effect sizes are distributionally consistent with the original effect size.
@@
 
+\begin{table}[!h]
+
+\caption{\label{tab:unnamed-chunk-6}Descriptive properties of the replication dataset.
+For categorical features, counts and percentages are given.
+For continuous features, the median value and interquartile range are given.
+N=176 except for original effect size and p-value where N=112.
+}
+\centering
+\fontsize{10}{12}\selectfont
+\begin{tabular}[t]{lc}
+\toprule
+Feature & Summary\\
+\midrule
+Subfield & \\
+\hspace{1em}Cognitive & 62 (35\%)\\
+\hspace{1em}Social & 70 (40\%)\\
+\hspace{1em}Other psych & 24 (14\%)\\
+\hspace{1em}Non-psych & 20 (11\%)\\
+Open data & 52 (30\%)\\
+Open materials & 83 (47\%)\\
+Switch from in-person to online & 94 (53\%)\\
+Original authors at Stanford & 16 (9.1\%)\\
+Within subjects design & 80 (45\%)\\
+Single vignette & 78 (44\%)\\
+Number of trials & 6 (1, 60)\\
+Publication Year & 2015 (2011, 2017)\\
+Original sample size & 101 (40, 181)\\
+Replication sample size & 59 (31, 125)\\
+Ratio of replication/original sample sizes & 0.86 (0.41, 1.05)\\
+Original effect size (SMD) & 0.61 (0.46, 0.98)\\
+Original p-value & 0.0001 (0.0000, 0.0069)\\
+\bottomrule
+\end{tabular}
+\end{table}
+
 \hypertarget{bivariate-correlates-of-replication-success}{%
@@
 We investigated what features of the original study and replication were correlated with replication success, with the goal of being able to identify potential markers of replicability.
-We chose a set of predictor variables based on the correlational results of RP:P (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}), our own intuitions of experimental design factors that might impact replication success, and some covariates related to how close the replication was; a full description of these features is given in the Methods.
+We chose a set of predictor variables based on the correlational results of RP:P (\protect\hyperlink{ref-openscienceconsortium2015}{3}), our own intuitions of experimental design factors that might impact replication success, and some covariates related to how close the replication was; a full description of these features is given in the Methods.
 
@@
 Predictors of lower replicability included single-vignette studies (those with only one experimental stimulus per condition), classification as social psychology, and study pairs where the original study was in-person and the replication switched to online.
+
+\begin{figure}[ht]
+\includegraphics[width=1\linewidth,height=0.4\textheight]{manuscript_files/figure-latex/corr-plot-1} \caption{Correlations between predictors.
+See TODO Table 1 or Methods for descriptions.
+}\label{fig:corr-plot}
+\end{figure}
 
@@
 Studies with multiple vignettes replicated more often than single vignetted studies (mean scores: 0.59 versus 0.36).
-However, there were strong correlations among these experimental features as well as between these experimental features and specific subfields.
+However, there were strong correlations among these experimental features as well as between these experimental features and specific subfields (Figure \ref{fig:corr-plot}).
 
@@
 Replications that switched to online were less likely to replicate than those that had the same modality as the original (generally both online, in a few cases both in-person).
-While online studies in general show comparable results to studies conducted in person (\protect\hyperlink{ref-crump2013}{Crump et al.
-2013}), switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well-adapted (e.g., inductions might have been weaker or instructions might have been insufficient).
-These factors -- open materials, open data, and online samples -- are more common in more recent studies, and so these effects may partially reflect temporal trends.
+While online studies in general show comparable results to studies conducted in person (\protect\hyperlink{ref-crump2013}{31}), switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well-adapted (e.g., inductions might have been weaker or instructions might have been insufficient).
+These factors -- open materials, open data, and online samples -- are more common in more recent studies, and so these effects may partially reflect temporal trends (see Figure \ref{fig:corr-plot} for the correlations between these factors and publication year).
 
@@
 While a number of features show individual correlations with the subjective replication score, many correlate with one another.
-To determine which predictors were the strongest, we modeled subjective replication score as an ordinal outcome using ordinal Bayesian regression models with a logit link function, regularized using a horseshoe shrinkage prior (\protect\hyperlink{ref-carvalho09}{Carvalho et al.
-2009}).
+To determine which predictors were the strongest, we modeled subjective replication score as an ordinal outcome using ordinal Bayesian regression models with a logit link function, regularized using a horseshoe shrinkage prior (\protect\hyperlink{ref-carvalho09}{32}).
 This model estimates odds ratios representing the association of the predictor with having a higher versus lower subjective replication score.
@@
 The batch of replications presented here were pedagogical replications, done as part of a class.
-Trainees must learn experimental methods, and conducting replications as part of methods classes serves several purposes: it enables students to learn to do experiments in a supportive context, it often leads to more useful results than if students designed their own experiments from scratch, and it creates a resource for studying the literature (\protect\hyperlink{ref-frank2012}{Frank \& Saxe 2012}, \protect\hyperlink{ref-hawkins2018}{Hawkins et al.
-2018}, \protect\hyperlink{ref-wagge2019}{Wagge et al.
-2019}, \protect\hyperlink{ref-quintana2021}{Quintana 2021}).
+Trainees must learn experimental methods, and conducting replications as part of methods classes serves several purposes: it enables students to learn to do experiments in a supportive context, it often leads to more useful results than if students designed their own experiments from scratch, and it creates a resource for studying the literature (\protect\hyperlink{ref-quintana2021}{33}--\protect\hyperlink{ref-hawkins2018}{36}).
 We believe that this kind of pedagogy has an important role to play in improving methodological practices in psychology more broadly.
@@
 
-Our pre-registration, code, and coded data are available at \url{https://osf.io/xwn9m/}.
+Our pre-registration, code, and coded data are available at \url{https://osf.io/xwn9m/} (\protect\hyperlink{ref-osfdata}{37}).
 
@@
 Students were encouraged to do experimental replications, but some students chose to replicate correlational outcomes or do computational reproducibility projects instead.
-We cannot include the full student reports for confidentiality reasons, but we include over 50 reports that we received permission to share and the template given to students at \url{https://osf.io/xwn9m/}.
+We cannot include the full student reports for confidentiality reasons, but we include over 50 reports that we received permission to share and the template given to students at \url{https://osf.io/xwn9m/} (\protect\hyperlink{ref-osfdata}{37}).
 
@@
 
-Four of the replication projects were included in RP:P, and 10 were previously reported in Hawkins et al.
-(\protect\hyperlink{ref-hawkins2018}{2018}) (which reported 11 student replications from the 2015-2016 class, one of those was excluded from the current sample for being non-experimental).
+Four of the replication projects were included in RP:P, and 10 were previously reported in (\protect\hyperlink{ref-hawkins2018}{36}) (which reported 11 student replications from the 2015-2016 class; one of those was excluded from the current sample for being non-experimental).
 
@@
 This subjective replication outcome was chosen because it already existed, could be applied to all projects (regardless of type and detail of statistical reporting), and did not rely solely on one statistical measure.
-As a complement, we also identified a ``key'' statistical test for each paper (see below for details), and if possible, computed \(p\)-original and prediction interval at this statistic, following Mathur \& VanderWeele (\protect\hyperlink{ref-mathur2020}{2020}).
+As a complement, we also identified a ``key'' statistical test for each paper (see below for details), and if possible, computed \(p\)-original and prediction interval at this statistic, following (\protect\hyperlink{ref-mathur2020}{29}).
 \(p\)-original was a continuous measure of the \(p\) value on the hypothesis that the original and replication samples come from the same distribution.
@@
 
-The subjective replication scores were coded on {[}0, .25, .5, .75, 1{]}, and we ramapped these to 1-5 to run an ordinal regression predicting replication score.
+The subjective replication scores were coded on {[}0, .25, .5, .75, 1{]}, and we remapped these to 1-5 to run an ordinal regression predicting replication score.
 We ran logistic regressions predicting prediction interval and linear regressions predicting \(p\)-original.
 
-We used a horseshoe shrinkage prior on the fixed effect coefficients because we had a lot of predictors compared to the amount of data (\protect\hyperlink{ref-carvalho09}{Carvalho et al.
-2009}).
+We used a horseshoe shrinkage prior on the fixed effect coefficients because we had a lot of predictors compared to the amount of data (\protect\hyperlink{ref-carvalho09}{32}).
 All models included random slopes for predictors nested within year the class occurred to control for variation between cohorts of students.
@@
 The priors we used were horseshoe(3) for betas, normal(0,.5) for standard deviation of random slopes, and lkj(1) for correlations between random slopes.
-Models were run in BRMS (\protect\hyperlink{ref-brms}{Bürkner 2017}).
+Models were run in BRMS (\protect\hyperlink{ref-brms}{38}).
 
@@
 \hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
+\begin{CSLReferences}{0}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-klein2022}{}}%
+\CSLLeftMargin{1. }%
+\CSLRightInline{Klein RA, Cook CL, Ebersole CR, Vitiello C, Nosek BA, Hilgard J, et al.
+Many {Labs} 4: {Failure} to {Replicate Mortality Salience Effect With} and {Without Original Author Involvement}.
+Collabra: Psychology {[}Internet{]}.
+2022 Apr 29 {[}cited 2023 Feb 10{]};8(1):35271.
+Available from: \url{https://doi.org/10.1525/collabra.35271}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hagger2016}{}}%
+\CSLLeftMargin{2. }%
+\CSLRightInline{Hagger MS, Chatzisarantis NLD, Alberts H, Anggono CO, Batailler C, Birt AR, et al.
+A {Multilab Preregistered Replication} of the {Ego-Depletion Effect}.
+Perspect Psychol Sci {[}Internet{]}.
+2016 Jul 1 {[}cited 2023 Apr 27{]};11(4):546--73.
+Available from: \url{https://doi.org/10.1177/1745691616652873}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-openscienceconsortium2015}{}}%
+\CSLLeftMargin{3. }%
+\CSLRightInline{Open Science Consortium.
+Estimating the reproducibility of psychological science.
+Science {[}Internet{]}.
+2015 {[}cited 2023 Mar 17{]}; Available from: \url{https://www.science.org/doi/full/10.1126/science.aac4716?casa_token=IJ35TwwlcjsAAAAA\%3AqiP68QbVAHleIg9zD3WugKWuV6Oa5rswS0VQnDsCq5I14ME4WIQabNGVD_T6SBSuAt6voVHNnWc0sw}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-smaldino2016}{}}%
+\CSLLeftMargin{4. }%
+\CSLRightInline{Smaldino PE, McElreath R.
+The natural selection of bad science.
+Royal Society Open Science {[}Internet{]}.
+2016 Sep;3(9):160384.
+Available from: \url{https://doi.org/10.1098\%2Frsos.160384}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-simmons2011}{}}%
+\CSLLeftMargin{5. }%
+\CSLRightInline{Simmons JP, Nelson LD, Simonsohn U.
+False-positive psychology: Undisclosed flexibility in data collection and analysis allows presenting anything as significant.
+Psychological science.
+2011;22(11):1359--66.
+}
+
+\leavevmode\vadjust pre{\hypertarget{ref-klein2014}{}}%
+\CSLLeftMargin{6. }%
+\CSLRightInline{Klein RA, Ratliff KA, Vianello M, Adams RB, Bahník án, Bernstein MJ, et al.
+Investigating {Variation} in {Replicability}: {A} {``{Many Labs}''} {Replication Project}.
+Social Psychology {[}Internet{]}.
+2014 May 1 {[}cited 2023 Feb 10{]};45(3):142--52.
+Available from: \url{https://econtent.hogrefe.com/doi/10.1027/1864-9335/a000178}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-klein2018}{}}%
+\CSLLeftMargin{7. }%
+\CSLRightInline{Klein RA, Vianello M, Hasselman F, Adams BG, Adams RB, Alper S, et al.
+Many {Labs} 2: {Investigating Variation} in {Replicability Across Samples} and {Settings}.
+Adv Methods Pract Psychol Sci {[}Internet{]}.
+2018 Dec 1 {[}cited 2023 Feb 10{]};1(4):443--90.
+Available from: \url{https://doi.org/10.1177/2515245918810225}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ebersole2016}{}}%
+\CSLLeftMargin{8. }%
+\CSLRightInline{Ebersole CR, Atherton OE, Belanger AL, Skulborstad HM, Allen JM, Banks JB, et al.
+Many {Labs} 3: {Evaluating} participant pool quality across the academic semester via replication.
+Journal of Experimental Social Psychology {[}Internet{]}.
+2016 Nov 1 {[}cited 2023 Feb 10{]};67:68--82.
+Available from: \url{https://www.sciencedirect.com/science/article/pii/S0022103115300123}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-camerer2018}{}}%
+\CSLLeftMargin{9. }%
+\CSLRightInline{Camerer CF, Dreber A, Holzmeister F, Ho TH, Huber J, Johannesson M, et al.
+Evaluating the replicability of social science experiments in {Nature} and {Science} between 2010 and 2015.
+Nat Hum Behav {[}Internet{]}.
+2018 Aug 27 {[}cited 2023 Feb 11{]};2(9):637--44.
+Available from: \url{https://www.nature.com/articles/s41562-018-0399-z}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-vanbavel2016}{}}%
+\CSLLeftMargin{10. }%
+\CSLRightInline{Van Bavel JJ, Mende-Siedlecki P, Brady WJ, Reinero DA.
+Contextual sensitivity in scientific reproducibility.
+Proc Natl Acad Sci {[}Internet{]}.
+2016 Jun 7 {[}cited 2023 Apr 5{]};113(23):6454--9.
+Available from: \url{https://www.pnas.org/doi/full/10.1073/pnas.1521897113}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ramscar2015}{}}%
+\CSLLeftMargin{11. }%
+\CSLRightInline{Ramscar M, Shaoul C, Baayen RH. Why many priming results don't (and won't) replicate: {A} quantitative analysis. 2015. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-hoogeveen2019}{}}%
+\CSLLeftMargin{12. }%
+\CSLRightInline{Hoogeveen S, Sarafoglou A, Wagenmakers EJ.
+Laypeople {Can Predict Which Social Science Studies Replicate} {[}Internet{]}.
+{PsyArXiv}; 2019 Sep {[}cited 2019 Sep 30{]}.
+Available from: \url{https://osf.io/egw9d}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-dreber2015}{}}%
+\CSLLeftMargin{13. }%
+\CSLRightInline{Dreber A, Pfeiffer T, Almenberg J, Isaksson S, Wilson B, Chen Y, et al.
+Using prediction markets to estimate the reproducibility of scientific research.
+Proc Natl Acad Sci {[}Internet{]}.
+2015 Dec 15 {[}cited 2023 Mar 17{]};112(50):15343--7.
+Available from: \url{https://www.pnas.org/doi/abs/10.1073/pnas.1516179112}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-forsell2019}{}}%
+\CSLLeftMargin{14. }%
+\CSLRightInline{Forsell E, Viganola D, Pfeiffer T, Almenberg J, Wilson B, Chen Y, et al.
+Predicting replication outcomes in the {Many Labs} 2 study.
+Journal of Economic Psychology {[}Internet{]}.
+2019 Dec 1 {[}cited 2023 Mar 17{]};75:102117.
+Available from: \url{https://www.sciencedirect.com/science/article/pii/S0167487018303283}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-yang2020}{}}%
+\CSLLeftMargin{15. }%
+\CSLRightInline{Yang Y, Youyou W, Uzzi B.
+Estimating the deep replicability of scientific findings using human and artificial intelligence.
+Proc Natl Acad Sci {[}Internet{]}.
+2020 May 19 {[}cited 2023 May 15{]};117(20):10762--8.
+Available from: \url{https://www.pnas.org/doi/10.1073/pnas.1909046117}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-youyou2023}{}}%
+\CSLLeftMargin{16. }%
+\CSLRightInline{Youyou W, Yang Y, Uzzi B.
+A discipline-wide investigation of the replicability of {Psychology} papers over the past two decades.
+Proc Natl Acad Sci {[}Internet{]}.
+2023 Feb 7 {[}cited 2023 Jan 31{]};120(6):e2208863120.
+Available from: \url{https://www.pnas.org/doi/10.1073/pnas.2208863120}}
+
 \leavevmode\vadjust pre{\hypertarget{ref-altmejd2019}{}}%
-Altmejd A, Dreber A, Forsell E, Huber J, Imai T, Johannesson M, Kirchler M, Nave G, Camerer C (2019) Predicting the replicability of social science lab experiments.
-\emph{PLOS ONE} \textbf{14}:e0225826.
-doi:\href{https://doi.org/10.1371/journal.pone.0225826}{10.1371/journal.pone.0225826}
+\CSLLeftMargin{17. }%
+\CSLRightInline{Altmejd A, Dreber A, Forsell E, Huber J, Imai T, Johannesson M, et al.
+Predicting the replicability of social science lab experiments.
+PLOS ONE {[}Internet{]}.
+2019 Dec 5 {[}cited 2023 Mar 17{]};14(12):e0225826.
+Available from: \url{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0225826}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-protzko2020}{}}%
+\CSLLeftMargin{18. }%
+\CSLRightInline{Protzko J, Krosnick J, Nelson LD, Nosek BA, Axt J, Berent M, et al.
+High {Replicability} of {Newly-Discovered Social-behavioral Findings} is {Achievable} {[}Internet{]}.
+{PsyArXiv}; 2020 Sep {[}cited 2023 Apr 5{]}.
+Available from: \url{https://osf.io/n2a9x}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ebersole2020}{}}%
+\CSLLeftMargin{19. }%
+\CSLRightInline{Ebersole CR, Mathur MB, Baranski E, Bart-Plange DJ, Buttrick NR, Chartier CR, et al.
+Many {Labs} 5: {Testing Pre-Data-Collection Peer Review} as an {Intervention} to {Increase Replicability}.
+Adv Methods Pract Psychol Sci {[}Internet{]}.
+2020 Sep 1 {[}cited 2023 Feb 10{]};3(3):309--31.
+Available from: \url{https://doi.org/10.1177/2515245920958687}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-etz2016}{}}%
+\CSLLeftMargin{20. }%
+\CSLRightInline{Etz A, Vandekerckhove J.
+A {Bayesian Perspective} on the {Reproducibility Project}: {Psychology}.
+PLOS ONE {[}Internet{]}.
+2016 Feb 26 {[}cited 2023 Mar 17{]};11(2):e0149794.
+Available from: \url{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0149794}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-gilbert2016}{}}%
+\CSLLeftMargin{21. }%
+\CSLRightInline{Gilbert DT, King G, Pettigrew S, Wilson TD.
+Comment on {``{Estimating} the reproducibility of psychological science.''} Science {[}Internet{]}.
+2016 Mar 4 {[}cited 2023 Mar 17{]};351(6277):1037--7.
+Available from: \url{https://www.science.org/doi/10.1126/science.aad7243}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-patil2016}{}}%
+\CSLLeftMargin{22. }%
+\CSLRightInline{Patil P, Peng RD, Leek JT.
+\href{https://doi.org/10.1177/1745691616646366}{What {Should Researchers Expect When They Replicate Studies}?
+{A Statistical View} of {Replicability} in {Psychological Science}}.
+Perspect Psychol Sci.
+2016 Jul;11(4):539--44.
+}
 
 \leavevmode\vadjust pre{\hypertarget{ref-anderson2016}{}}%
-Anderson CJ, Bahník án, Barnett-Cowan M, Bosco FA, Chandler J, Chartier CR, Cheung F, Christopherson CD, Cordes A, Cremata EJ, Della Penna N, Estel V, Fedor A, Fitneva SA, Frank MC, Grange JA, Hartshorne JK, Hasselman F, Henninger F, Hulst M van der, Jonas KJ, Lai CK, Levitan CA, Miller JK, Moore KS, Meixner JM, Munafò MR, Neijenhuijs KI, Nilsonne G, Nosek BA, Plessow F, Prenoveau JM, Ricker AA, Schmidt K, Spies JR, Stieger S, Strohminger N, Sullivan GB, Aert RCM van, Assen MALM van, Vanpaemel W, Vianello M, Voracek M, Zuni K (2016) Response to {Comment} on {``{Estimating} the reproducibility of psychological science.''} \emph{Science} \textbf{351}:1037--1037.
-doi:\href{https://doi.org/10.1126/science.aad9163}{10.1126/science.aad9163}
+\CSLLeftMargin{23. }%
+\CSLRightInline{Anderson CJ, Bahník án, Barnett-Cowan M, Bosco FA, Chandler J, Chartier CR, et al.
+Response to {Comment} on {``{Estimating} the reproducibility of psychological science.''} Science {[}Internet{]}.
+2016 Mar 4 {[}cited 2023 Apr 4{]};351(6277):1037--7.
+Available from: \url{https://www.science.org/doi/10.1126/science.aad9163}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rosenthal2008}{}}%
+\CSLLeftMargin{24. }%
+\CSLRightInline{Rosenthal R, Rosnow RL. Essentials of behavioral research: Methods and data analysis. 2008. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-greenwald1976}{}}%
+\CSLLeftMargin{25. }%
+\CSLRightInline{Greenwald AG. Within-subjects designs: To use or not to use? Psychological Bulletin. 1976;83(2):314. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-frank2023}{}}%
+\CSLLeftMargin{26. }%
+\CSLRightInline{Frank MC, Braginsky M, Cachia J, Coles N, Hardwicke T, Hawkins R, et al. Experimentology: An open science approach to experimental psychology methods. Boston, MA: MIT Press; 2023. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-simonsohn2015}{}}%
+\CSLLeftMargin{27. }%
+\CSLRightInline{Simonsohn U.
+Small {Telescopes}: {Detectability} and the {Evaluation} of {Replication Results}.
+Psychol Sci {[}Internet{]}.
+2015 May 1 {[}cited 2023 Apr 4{]};26(5):559--69.
+Available from: \url{https://doi.org/10.1177/0956797614567341}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-gelman2018}{}}%
+\CSLLeftMargin{28. }%
+\CSLRightInline{Gelman A.
+Don't characterize replications as successes or failures.
+Behav Brain Sci {[}Internet{]}.
+2018/ed {[}cited 2023 Apr 4{]};41:e128.
+Available from: \url{https://www.cambridge.org/core/journals/behavioral-and-brain-sciences/article/abs/dont-characterize-replications-as-successes-or-failures/1AB661F1E7A08E9C5870258878DBA0EA}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-mathur2020}{}}%
+\CSLLeftMargin{29. }%
+\CSLRightInline{Mathur MB, VanderWeele TJ.
+New statistical metrics for multisite replication projects.
+J R Stat Soc Ser A Stat Soc {[}Internet{]}.
+2020 {[}cited 2023 Apr 4{]};183(3):1145--66.
+Available from: \url{https://onlinelibrary.wiley.com/doi/abs/10.1111/rssa.12572}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-olsson2020}{}}%
+\CSLLeftMargin{30. }%
+\CSLRightInline{Olsson-Collentine A, Assen MA van, Wicherts J. Heterogeneity in direct replications in psychology and its association with effect size. 2020; }
+
+\leavevmode\vadjust pre{\hypertarget{ref-crump2013}{}}%
+\CSLLeftMargin{31. }%
+\CSLRightInline{Crump MJC, McDonnell JV, Gureckis TM.
+Evaluating {Amazon}'s {Mechanical Turk} as a {Tool} for {Experimental Behavioral Research}.
+PLOS ONE {[}Internet{]}.
+2013 Mar 13 {[}cited 2020 Sep 30{]};8(3):e57410.
+Available from: \url{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0057410}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-carvalho09}{}}%
+\CSLLeftMargin{32. }%
+\CSLRightInline{Carvalho CM, Polson NG, Scott JG.
+Handling sparsity via the horseshoe.
+In: Dyk D van, Welling M, editors.
+Proceedings of the twelth international conference on artificial intelligence and statistics {[}Internet{]}.
+Hilton Clearwater Beach Resort, Clearwater Beach, Florida USA: PMLR; 2009.
+p.
+73--80.
+(Proceedings of machine learning research; vol.
+5).
+Available from: \url{https://proceedings.mlr.press/v5/carvalho09a.html}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-quintana2021}{}}%
+\CSLLeftMargin{33. }%
+\CSLRightInline{Quintana DS.
+Replication studies for undergraduate theses to improve science and education.
+Nat Hum Behav {[}Internet{]}.
+2021 Sep {[}cited 2023 Apr 4{]};5(9, 9):1117--8.
+Available from: \url{https://www.nature.com/articles/s41562-021-01192-8}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wagge2019}{}}%
+\CSLLeftMargin{34. }%
+\CSLRightInline{Wagge JR, Brandt MJ, Lazarevic LB, Legate N, Christopherson C, Wiggins B, et al.
+Publishing {Research With Undergraduate Students} via {Replication Work}: {The Collaborative Replications} and {Education Project}.
+Front Psychol {[}Internet{]}.
+2019 {[}cited 2023 Apr 4{]};10.
+Available from: \url{https://www.frontiersin.org/articles/10.3389/fpsyg.2019.00247}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-frank2012}{}}%
+\CSLLeftMargin{35. }%
+\CSLRightInline{Frank MC, Saxe R.
+Teaching {Replication}: Perspect Psychol Sci {[}Internet{]}.
+2012 Nov 7 {[}cited 2020 Sep 14{]}; Available from: \url{https://journals.sagepub.com/doi/10.1177/1745691612460686}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hawkins2018}{}}%
+\CSLLeftMargin{36. }%
+\CSLRightInline{Hawkins RD, Smith EN, Au C, Arias JM, Catapano R, Hermann E, et al.
+Improving the replicability of psychological science through pedagogy.
+Advances in Methods and Practices in Psychological Science.
+2018 Mar;1(1):7--18.
+}
+
+\leavevmode\vadjust pre{\hypertarget{ref-osfdata}{}}%
+\CSLLeftMargin{37. }%
+\CSLRightInline{Boyce V. Meta analysis of class replication projects from PSYCH251 {[}Internet{]}. OSF; 2023. Available from: \href{https://osf.io/xwn9m}{osf.io/xwn9m}}
 
 \leavevmode\vadjust pre{\hypertarget{ref-brms}{}}%
-Bürkner P-C (2017) {brms}: An {R} package for {Bayesian} multilevel models using {Stan}.
-\emph{Journal of Statistical Software} \textbf{80}:1--28.
-doi:\href{https://doi.org/10.18637/jss.v080.i01}{10.18637/jss.v080.i01}
-
-\leavevmode\vadjust pre{\hypertarget{ref-camerer2018}{}}%
-Camerer CF, Dreber A, Holzmeister F, Ho T-H, Huber J, Johannesson M, Kirchler M, Nave G, Nosek BA, Pfeiffer T, Altmejd A, Buttrick N, Chan T, Chen Y, Forsell E, Gampa A, Heikensten E, Hummer L, Imai T, Isaksson S, Manfredi D, Rose J, Wagenmakers E-J, Wu H (2018) Evaluating the replicability of social science experiments in {Nature} and {Science} between 2010 and 2015.
-\emph{Nat Hum Behav} \textbf{2}:637--644.
-doi:\href{https://doi.org/10.1038/s41562-018-0399-z}{10.1038/s41562-018-0399-z}
-
-\leavevmode\vadjust pre{\hypertarget{ref-carvalho09}{}}%
-Carvalho CM, Polson NG, Scott JG (2009) Handling sparsity via the horseshoe.
-In: Dyk D van, Welling M (eds) \emph{Proceedings of the twelth international conference on artificial intelligence and statistics}.
-PMLR, Hilton Clearwater Beach Resort, Clearwater Beach, Florida USA, p 73--80.
-Available from: \url{https://proceedings.mlr.press/v5/carvalho09a.html}
-
-\leavevmode\vadjust pre{\hypertarget{ref-crump2013}{}}%
-Crump MJC, McDonnell JV, Gureckis TM (2013) Evaluating {Amazon}'s {Mechanical Turk} as a {Tool} for {Experimental Behavioral Research}.
-\emph{PLOS ONE} \textbf{8}:e57410.
-doi:\href{https://doi.org/10.1371/journal.pone.0057410}{10.1371/journal.pone.0057410}
-
-\leavevmode\vadjust pre{\hypertarget{ref-dreber2015}{}}%
-Dreber A, Pfeiffer T, Almenberg J, Isaksson S, Wilson B, Chen Y, Nosek BA, Johannesson M (2015) Using prediction markets to estimate the reproducibility of scientific research.
-\emph{Proc Natl Acad Sci} \textbf{112}:15343--15347.
-doi:\href{https://doi.org/10.1073/pnas.1516179112}{10.1073/pnas.1516179112}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ebersole2016}{}}%
-Ebersole CR, Atherton OE, Belanger AL, Skulborstad HM, Allen JM, Banks JB, Baranski E, Bernstein MJ, Bonfiglio DBV, Boucher L, Brown ER, Budiman NI, Cairo AH, Capaldi CA, Chartier CR, Chung JM, Cicero DC, Coleman JA, Conway JG, Davis WE, Devos T, Fletcher MM, German K, Grahe JE, Hermann AD, Hicks JA, Honeycutt N, Humphrey B, Janus M, Johnson DJ, Joy-Gaba JA, Juzeler H, Keres A, Kinney D, Kirshenbaum J, Klein RA, Lucas RE, Lustgraaf CJN, Martin D, Menon M, Metzger M, Moloney JM, Morse PJ, Prislin R, Razza T, Re DE, Rule NO, Sacco DF, Sauerberger K, Shrider E, Shultz M, Siemsen C, Sobocko K, Weylin Sternglanz R, Summerville A, Tskhay KO, Allen Z van, Vaughn LA, Walker RJ, Weinberg A, Wilson JP, Wirth JH, Wortman J, Nosek BA (2016) Many {Labs} 3: {Evaluating} participant pool quality across the academic semester via replication.
-\emph{Journal of Experimental Social Psychology} \textbf{67}:68--82.
-doi:\href{https://doi.org/10.1016/j.jesp.2015.10.012}{10.1016/j.jesp.2015.10.012}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ebersole2020}{}}%
-Ebersole CR, Mathur MB, Baranski E, Bart-Plange D-J, Buttrick NR, Chartier CR,..., Nosek BA (2020) Many {Labs} 5: {Testing Pre-Data-Collection Peer Review} as an {Intervention} to {Increase Replicability}.
-\emph{Adv Methods Pract Psychol Sci} \textbf{3}:309--331.
-doi:\href{https://doi.org/10.1177/2515245920958687}{10.1177/2515245920958687}
-
-\leavevmode\vadjust pre{\hypertarget{ref-etz2016}{}}%
-Etz A, Vandekerckhove J (2016) A {Bayesian Perspective} on the {Reproducibility Project}: {Psychology}.
-\emph{PLOS ONE} \textbf{11}:e0149794.
-doi:\href{https://doi.org/10.1371/journal.pone.0149794}{10.1371/journal.pone.0149794}
-
-\leavevmode\vadjust pre{\hypertarget{ref-forsell2019}{}}%
-Forsell E, Viganola D, Pfeiffer T, Almenberg J, Wilson B, Chen Y, Nosek BA, Johannesson M, Dreber A (2019) Predicting replication outcomes in the {Many Labs} 2 study.
-\emph{Journal of Economic Psychology} \textbf{75}:102117.
-doi:\href{https://doi.org/10.1016/j.joep.2018.10.009}{10.1016/j.joep.2018.10.009}
-
-\leavevmode\vadjust pre{\hypertarget{ref-frank2012}{}}%
-Frank MC, Saxe R (2012) Teaching {Replication}: \emph{Perspect Psychol Sci}. doi:\href{https://doi.org/10.1177/1745691612460686}{10.1177/1745691612460686}
-
-\leavevmode\vadjust pre{\hypertarget{ref-frank2023}{}}%
-Frank MC, Braginsky M, Cachia J, Coles N, Hardwicke T, Hawkins R, Mathur MB, Williams R (2023) Experimentology: An open science approach to experimental psychology methods.
-
-\leavevmode\vadjust pre{\hypertarget{ref-gelman2018}{}}%
-Gelman A (2018/ed) Don't characterize replications as successes or failures. \emph{Behav Brain Sci} \textbf{41}:e128. doi:\href{https://doi.org/10.1017/S0140525X18000638}{10.1017/S0140525X18000638}
-
-\leavevmode\vadjust pre{\hypertarget{ref-gilbert2016}{}}%
-Gilbert DT, King G, Pettigrew S, Wilson TD (2016) Comment on {``{Estimating} the reproducibility of psychological science.''} \emph{Science} \textbf{351}:1037--1037.
-doi:\href{https://doi.org/10.1126/science.aad7243}{10.1126/science.aad7243}
-
-\leavevmode\vadjust pre{\hypertarget{ref-greenwald1976}{}}%
-Greenwald AG (1976) Within-subjects designs: To use or not to use? \emph{Psychological Bulletin} \textbf{83}:314
-
-\leavevmode\vadjust pre{\hypertarget{ref-hagger2016}{}}%
-Hagger MS, Chatzisarantis NLD, Alberts H, Anggono CO, Batailler C, Birt AR, Brand R, Brandt MJ, Brewer G, Bruyneel S, Calvillo DP, Campbell WK, Cannon PR, Carlucci M, Carruth NP, Cheung T, Crowell A, De Ridder DTD, Dewitte S, Elson M, Evans JR, Fay BA, Fennis BM, Finley A, Francis Z, Heise E, Hoemann H, Inzlicht M, Koole SL, Koppel L, Kroese F, Lange F, Lau K, Lynch BP, Martijn C, Merckelbach H, Mills NV, Michirev A, Miyake A, Mosser AE, Muise M, Muller D, Muzi M, Nalis D, Nurwanti R, Otgaar H, Philipp MC, Primoceri P, Rentzsch K, Ringos L, Schlinkert C, Schmeichel BJ, Schoch SF, Schrama M, Schütz A, Stamos A, Tinghög G, Ullrich J, vanDellen M, Wimbarti S, Wolff W, Yusainy C, Zerhouni O, Zwienenberg M (2016) A {Multilab Preregistered Replication} of the {Ego-Depletion Effect}.
-\emph{Perspect Psychol Sci} \textbf{11}:546--573.
-doi:\href{https://doi.org/10.1177/1745691616652873}{10.1177/1745691616652873}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hawkins2018}{}}%
-Hawkins RD, Smith EN, Au C, Arias JM, Catapano R, Hermann E, Keil M, Lampinen A, Raposo S, Reynolds J, Salehi S, Salloum J, Tan J, Frank MC (2018) Improving the replicability of psychological science through pedagogy.
-\emph{Advances in Methods and Practices in Psychological Science} \textbf{1}:7--18
-
-\leavevmode\vadjust pre{\hypertarget{ref-hoogeveen2019}{}}%
-Hoogeveen S, Sarafoglou A, Wagenmakers E-J (2019) Laypeople {Can Predict Which Social Science Studies Replicate}.
-preprint.
-{PsyArXiv}.
-Available from: \url{https://osf.io/egw9d} {[}Last accessed 30 September 2019{]}.
-doi:\href{https://doi.org/10.31234/osf.io/egw9d}{10.31234/osf.io/egw9d}
-
-\leavevmode\vadjust pre{\hypertarget{ref-klein2014}{}}%
-Klein RA, Ratliff KA, Vianello M, Adams RB, Bahník án, Bernstein MJ,..., Nosek BA (2014) Investigating {Variation} in {Replicability}: {A} {``{Many Labs}''} {Replication Project}.
-\emph{Social Psychology} \textbf{45}:142--152.
-doi:\href{https://doi.org/10.1027/1864-9335/a000178}{10.1027/1864-9335/a000178}
-
-\leavevmode\vadjust pre{\hypertarget{ref-klein2018}{}}%
-Klein RA, Vianello M, Hasselman F, Adams BG, Adams RB, Alper S,..., Nosek BA (2018) Many {Labs} 2: {Investigating Variation} in {Replicability Across Samples} and {Settings}.
-\emph{Adv Methods Pract Psychol Sci} \textbf{1}:443--490.
-doi:\href{https://doi.org/10.1177/2515245918810225}{10.1177/2515245918810225}
-
-\leavevmode\vadjust pre{\hypertarget{ref-klein2022}{}}%
-Klein RA, Cook CL, Ebersole CR, Vitiello C, Nosek BA, Hilgard J, Ahn PH, Brady AJ, Chartier CR, Christopherson CD, Clay S, Collisson B, Crawford JT, Cromar R, Gardiner G, Gosnell CL, Grahe J, Hall C, Howard I, Joy-Gaba JA, Kolb M, Legg AM, Levitan CA, Mancini AD, Manfredi D, Miller J, Nave G, Redford L, Schlitz I, Schmidt K, Skorinko JLM, Storage D, Swanson T, Van Swol LM, Vaughn LA, Vidamuerte D, Wiggins B, Ratliff KA (2022) Many {Labs} 4: {Failure} to {Replicate Mortality Salience Effect With} and {Without Original Author Involvement}.
-\emph{Collabra: Psychology} \textbf{8}:35271.
-doi:\href{https://doi.org/10.1525/collabra.35271}{10.1525/collabra.35271}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mathur2020}{}}%
-Mathur MB, VanderWeele TJ (2020) New statistical metrics for multisite replication projects.
-\emph{J R Stat Soc Ser A Stat Soc} \textbf{183}:1145--1166.
-doi:\href{https://doi.org/10.1111/rssa.12572}{10.1111/rssa.12572}
-
-\leavevmode\vadjust pre{\hypertarget{ref-olsson2020}{}}%
-Olsson-Collentine A, Assen MA van, Wicherts J (2020) Heterogeneity in direct replications in psychology and its association with effect size.
-
-\leavevmode\vadjust pre{\hypertarget{ref-openscienceconsortium2015}{}}%
-Open Science Consortium (2015) \href{https://www.science.org/doi/full/10.1126/science.aac4716?casa_token=IJ35TwwlcjsAAAAA\%3AqiP68QbVAHleIg9zD3WugKWuV6Oa5rswS0VQnDsCq5I14ME4WIQabNGVD_T6SBSuAt6voVHNnWc0sw}{Estimating the reproducibility of psychological science}.
-\emph{Science}
-
-\leavevmode\vadjust pre{\hypertarget{ref-patil2016}{}}%
-Patil P, Peng RD, Leek JT (2016) What {Should Researchers Expect When They Replicate Studies}?
-{A Statistical View} of {Replicability} in {Psychological Science}.
-\emph{Perspect Psychol Sci} \textbf{11}:539--544.
-doi:\href{https://doi.org/10.1177/1745691616646366}{10.1177/1745691616646366}
-
-\leavevmode\vadjust pre{\hypertarget{ref-protzko2020}{}}%
-Protzko J, Krosnick J, Nelson LD, Nosek BA, Axt J, Berent M, Buttrick N, DeBell M, Ebersole CR, Lundmark S, MacInnis B, O'Donnell M, Perfecto H, Pustejovsky JE, Roeder SS, Walleczek J, Schooler J (2020) High {Replicability} of {Newly-Discovered Social-behavioral Findings} is {Achievable}.
-preprint.
-{PsyArXiv}.
-Available from: \url{https://osf.io/n2a9x} {[}Last accessed 5 April 2023{]}.
-doi:\href{https://doi.org/10.31234/osf.io/n2a9x}{10.31234/osf.io/n2a9x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-quintana2021}{}}%
-Quintana DS (2021) Replication studies for undergraduate theses to improve science and education.
-\emph{Nat Hum Behav} \textbf{5}:1117--1118.
-doi:\href{https://doi.org/10.1038/s41562-021-01192-8}{10.1038/s41562-021-01192-8}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ramscar2015}{}}%
-Ramscar M, Shaoul C, Baayen RH (2015) Why many priming results don't (and won't) replicate: {A} quantitative analysis.
-
-\leavevmode\vadjust pre{\hypertarget{ref-rosenthal2008}{}}%
-Rosenthal R, Rosnow RL (2008) Essentials of behavioral research: Methods and data analysis.
-
-\leavevmode\vadjust pre{\hypertarget{ref-simmons2011}{}}%
-Simmons JP, Nelson LD, Simonsohn U (2011) False-positive psychology: Undisclosed flexibility in data collection and analysis allows presenting anything as significant.
-\emph{Psychological science} \textbf{22}:1359--1366
-
-\leavevmode\vadjust pre{\hypertarget{ref-simonsohn2015}{}}%
-Simonsohn U (2015) Small {Telescopes}: {Detectability} and the {Evaluation} of {Replication Results}.
-\emph{Psychol Sci} \textbf{26}:559--569.
-doi:\href{https://doi.org/10.1177/0956797614567341}{10.1177/0956797614567341}
-
-\leavevmode\vadjust pre{\hypertarget{ref-smaldino2016}{}}%
-Smaldino PE, McElreath R (2016) The natural selection of bad science. \emph{Royal Society Open Science} \textbf{3}:160384. doi:\href{https://doi.org/10.1098/rsos.160384}{10.1098/rsos.160384}
-
-\leavevmode\vadjust pre{\hypertarget{ref-vanbavel2016}{}}%
-Van Bavel JJ, Mende-Siedlecki P, Brady WJ, Reinero DA (2016) Contextual sensitivity in scientific reproducibility.
-\emph{Proc Natl Acad Sci} \textbf{113}:6454--6459.
-doi:\href{https://doi.org/10.1073/pnas.1521897113}{10.1073/pnas.1521897113}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wagge2019}{}}%
-Wagge JR, Brandt MJ, Lazarevic LB, Legate N, Christopherson C, Wiggins B, Grahe JE (2019) \href{https://www.frontiersin.org/articles/10.3389/fpsyg.2019.00247}{Publishing {Research With Undergraduate Students} via {Replication Work}: {The Collaborative Replications} and {Education Project}}.
-\emph{Front Psychol} \textbf{10}
-
-\leavevmode\vadjust pre{\hypertarget{ref-yang2020}{}}%
-Yang Y, Youyou W, Uzzi B (2020) Estimating the deep replicability of scientific findings using human and artificial intelligence.
-\emph{Proc Natl Acad Sci} \textbf{117}:10762--10768.
-doi:\href{https://doi.org/10.1073/pnas.1909046117}{10.1073/pnas.1909046117}
-
-\leavevmode\vadjust pre{\hypertarget{ref-youyou2023}{}}%
-Youyou W, Yang Y, Uzzi B (2023) A discipline-wide investigation of the replicability of {Psychology} papers over the past two decades.
-\emph{Proc Natl Acad Sci} \textbf{120}:e2208863120.
-doi:\href{https://doi.org/10.1073/pnas.2208863120}{10.1073/pnas.2208863120}
+\CSLLeftMargin{38. }%
+\CSLRightInline{Bürkner PC. \href{https://doi.org/10.18637/jss.v080.i01}{{brms}: An {R} package for {Bayesian} multilevel models using {Stan}}. Journal of Statistical Software. 2017;80(1):1--28. }
 

### 2023-10-12 paper/manuscript.Rmd
work on edits; redo tieu

@@
 In some cases the budget limited the number of participants who could be recruited, occasionally below what the original study included or what power analyses suggested.
-The replications had a median post-exclusion sample size that was `r round(ratio_dist[3]*100)`% of the original sample size (interquartile range `r round(ratio_dist[2]*100)`%-`r round(ratio_dist[4]*100)`%)^[Replications had a median of `r round(rep_dist[3])` participants (interquartile range: `r round(rep_dist[2])` - `r round(rep_dist[4])`), while original studies had a median of `r round(target_dist[3])` participants (interquartile range: `r round(target_dist[2])` - `r round(target_dist[4])`).].
+The replications had a median post-exclusion sample size that was `r round(ratio_dist[3]*100)`% of the original sample size.
 In nearly all cases, replications were conducted online, with recruitment from Amazon Mechanical Turk (the default from 2011 to 2020) or Prolific (the default from 2021 -- 2022).
@@
 
+```{r}
+library(gtsummary)
+theme_gtsummary_language("en", big.mark = "")
+library(kableExtra)
+
+desc <- d %>% mutate(target_d_calc=ifelse(include=="stats", target_d_calc, NA),
+             target_p_calc=ifelse(include=="stats",target_p_calc, NA),
+      switch_modality=ifelse(target_on_turk!=replication_on_turk,1,0),
+         ss_ratio=replication_N/target_N)%>% 
+  select("subfield","open_data", "open_materials","switch_modality",  "stanford_internal","within_between","single_vignette","repeated_measure","target_year","target_N","replication_N", "ss_ratio", "target_d_calc", "target_p_calc") %>%
+  mutate(subfield=factor(subfield, levels=c("cognitive", "social", "other-psych", "non-psych"), labels=c("Cognitive", "Social", "Other psych", "Non-psych")),
+         within_between=ifelse(within_between=="between", 0, 1)) %>% 
+             tbl_summary(
+               label=list(
+                 subfield ~ "Subfield",
+                 stanford_internal ~ "Original authors at Stanford",
+                 target_year~ "Publication Year",
+                 single_vignette ~ "Single vignette",
+                 open_data ~ "Open data",
+                 open_materials ~ "Open materials",
+                 within_between ~ "Within subjects design",
+                 repeated_measure ~ "Number of trials",
+                 target_N ~ "Original sample size",
+                 replication_N ~ "Replication sample size",
+                 ss_ratio ~ "Ratio of replication/original sample sizes",
+                 target_d_calc ~"Original effect size (SMD)",
+                 target_p_calc ~ "Original p-value",
+                 switch_modality ~ "Switch from in-person to online"
+               ),
+               statistic = list(all_continuous() ~ "{mean} ({sd})", all_continuous() ~ "{median} ({p25}, {p75})"),
+               digits=list(target_year ~ 0, target_p_calc ~4),
+    missing="no",
+             ) %>% modify_header(label="Feature", stat_0="Summary") %>% 
+    modify_footnote(update = everything() ~ NA)
+
+as_kable_extra(desc,format="latex", position="!h", caption="Descriptive properties of the replication dataset.
+For categorical features, counts and percentages are given.
+For continuous features, the median value and interquartile range are given.
+N=176 except for original effect size and p-value where N=112.
+", booktabs=TRUE, linesep="") |> kable_styling(full_width=F, font_size=10)
+
+```
+
 ```{r }
@@
 
-```{r}
-library(gtsummary)
-theme_gtsummary_language("en", big.mark = "")
-library(kableExtra)
-
-desc <- d %>% mutate(target_d_calc=ifelse(include=="stats", target_d_calc, NA),
-             target_p_calc=ifelse(include=="stats",target_p_calc, NA),
-      switch_modality=ifelse(target_on_turk!=replication_on_turk,1,0),
-         ss_ratio=replication_N/target_N)%>% 
-  select("subfield","open_data", "open_materials","switch_modality",  "stanford_internal","within_between","single_vignette","repeated_measure","target_year","target_N","replication_N", "ss_ratio", "target_d_calc", "target_p_calc") %>%
-  mutate(subfield=factor(subfield, levels=c("cognitive", "social", "other-psych", "non-psych"), labels=c("Cognitive", "Social", "Other psych", "Non-psych")),
-         within_between=ifelse(within_between=="between", 0, 1)) %>% 
-             tbl_summary(
-               label=list(
-                 subfield ~ "Subfield",
-                 stanford_internal ~ "Original authors at Stanford",
-                 target_year~ "Publication Year",
-                 single_vignette ~ "Single vignette",
-                 open_data ~ "Open data",
-                 open_materials ~ "Open materials",
-                 within_between ~ "Within subjects design",
-                 repeated_measure ~ "Number of trials",
-                 target_N ~ "Original sample size",
-                 replication_N ~ "Replication sample size",
-                 ss_ratio ~ "Ratio of replication/original sample sizes",
-                 target_d_calc ~"Original effect size (SMD)",
-                 target_p_calc ~ "Original p-value",
-                 switch_modality ~ "Switch from in-person to online"
-               ),
-               statistic = list(all_continuous() ~ "{mean} ({sd})", all_continuous() ~ "{median} ({p25}, {p75})"),
-               digits=list(target_year ~ 0, target_p_calc ~4),
-    missing="no",
-             ) %>% modify_header(label="Feature", stat_0="Summary") %>% 
-    modify_footnote(update = everything() ~ NA)
-
-as_kable_extra(desc,format="latex", position="!h", caption="Descriptive properties of the replication dataset.
-For categorical features, counts and percentages are given.
-For continuous features, the median value and interquartile range are given.
-N=176 except for original effect size and p-value where N=112.
-", booktabs=TRUE, linesep="") |> kable_styling(full_width=F, font_size=10)
-
-```
 ## Bivariate correlates of replication success
@@
 While online studies in general show comparable results to studies conducted in person [@crump2013], switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well-adapted (e.g., inductions might have been weaker or instructions might have been insufficient).
-These factors -- open materials, open data, and online samples -- are more common in more recent studies, and so these effects may partially reflect temporal trends (see Figure \ref{fig:corr-plot} for the correlations between these factors and publication year).
+These factors -- open materials, open data, and online samples -- may have all contributed to the closeness of the replications.
+However, they are also practices that have increased over time, and so these effects may partially reflect temporal trends.
+Nonetheless, publication year only very weakly correlated with replicability, but does correlate strongly with online samples and openness (Figure \ref{fig:corr-plot}).
 
@@
 
-Students were free to choose what study to replicate; the recommended path for students who did not have their own ideas was to pick an interesting study from a recent year of Psychological Science (this led to a high fraction of Psych Science articles in the replication sample, `r nrow(ps)`, `r round( nrow(ps)/nrow(all)*100)`% of studies).
+Students were free to choose what study to replicate; the recommended path for students who did not have their own ideas was to pick an interesting study from a recent year of Psychological Science (this led to `r nrow(ps)` Psych Science articles in the replication sample, `r round( nrow(ps)/nrow(all)*100)`% of all studies).
 

### 2023-10-12 paper/manuscript.tex
work on edits; redo tieu

@@
 In some cases the budget limited the number of participants who could be recruited, occasionally below what the original study included or what power analyses suggested.
-The replications had a median post-exclusion sample size that was 86\% of the original sample size (interquartile range 41\%-105\%)\footnote{Replications had a median of 59 participants (interquartile range: 31 - 124), while original studies had a median of 101 participants (interquartile range: 40 - 180).}.
+The replications had a median post-exclusion sample size that was 86\% of the original sample size.
 In nearly all cases, replications were conducted online, with recruitment from Amazon Mechanical Turk (the default from 2011 to 2020) or Prolific (the default from 2021 -- 2022).
@@
 
-Some multi-site replication projects have found heterogeneity in effect sizes across replication sites (\protect\hyperlink{ref-klein2018}{7},\protect\hyperlink{ref-ebersole2020}{19},\protect\hyperlink{ref-olsson2020}{30}).
-As a test of sensitivity to heterogeneity, we assumed that the level of heterogeneity in hypothetical multi-site replications of our sampled articles was the same as the average level heterogeneity found by (\protect\hyperlink{ref-olsson2020}{30}) in prior multi-site replications in psychology (\(\tau=.21\) in units of standardized mean difference).
-Under this assumption, 64\% (72/112) of replication effect sizes are distributionally consistent with the original effect size.
-However, more work on understanding heterogeneity is needed to understand what levels of heterogeneity to expect across different implementations of the same experiment, and how considerations of heterogeneity should impact interpretations of both novel results and replication results.
-
 \begin{table}[!h]
 
-\caption{\label{tab:cor}The unadjusted Pearson correlations between each individual predictor and the subjective replication score. See Methods for how these variables were coded.}
-\centering
-\fontsize{10}{12}\selectfont
-\begin{tabular}[t]{ccl}
-\toprule
-r & p & Predictors\\
-\midrule
-0.333 & 0.000 & Within participants design (versus between participants)\\
-0.182 & 0.015 & Log number of  trials\\
-0.150 & 0.047 & Open data\\
-0.080 & 0.294 & Non psychology (versus cognitive psych)\\
-0.075 & 0.322 & Other psychology (versus cognitive psych)\\
-0.064 & 0.399 & Publication year\\
-0.002 & 0.979 & Open materials\\
--0.027 & 0.725 & Stanford affiliation of original authors at time of replication\\
--0.047 & 0.536 & Log ratio between replication and original sample sizes\\
--0.108 & 0.155 & Log original sample size\\
--0.158 & 0.037 & Switch to online for replication (versus same modality for original and replication)\\
--0.246 & 0.001 & Social psychology (versus cognitive psych)\\
--0.267 & 0.000 & Single vignette (versus multiple items/inductions per condition)\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\begin{table}[!h]
-
-\caption{\label{tab:unnamed-chunk-6}Descriptive properties of the replication dataset.
+\caption{\label{tab:unnamed-chunk-4}Descriptive properties of the replication dataset.
 For categorical features, counts and percentages are given.
@@
 
+Some multi-site replication projects have found heterogeneity in effect sizes across replication sites (\protect\hyperlink{ref-klein2018}{7},\protect\hyperlink{ref-ebersole2020}{19},\protect\hyperlink{ref-olsson2020}{30}).
+As a test of sensitivity to heterogeneity, we assumed that the level of heterogeneity in hypothetical multi-site replications of our sampled articles was the same as the average level heterogeneity found by (\protect\hyperlink{ref-olsson2020}{30}) in prior multi-site replications in psychology (\(\tau=.21\) in units of standardized mean difference).
+Under this assumption, 64\% (72/112) of replication effect sizes are distributionally consistent with the original effect size.
+However, more work on understanding heterogeneity is needed to understand what levels of heterogeneity to expect across different implementations of the same experiment, and how considerations of heterogeneity should impact interpretations of both novel results and replication results.
+
+\begin{table}[!h]
+
+\caption{\label{tab:cor}The unadjusted Pearson correlations between each individual predictor and the subjective replication score. See Methods for how these variables were coded.}
+\centering
+\fontsize{10}{12}\selectfont
+\begin{tabular}[t]{ccl}
+\toprule
+r & p & Predictors\\
+\midrule
+0.333 & 0.000 & Within participants design (versus between participants)\\
+0.182 & 0.015 & Log number of  trials\\
+0.150 & 0.047 & Open data\\
+0.080 & 0.294 & Non psychology (versus cognitive psych)\\
+0.075 & 0.322 & Other psychology (versus cognitive psych)\\
+0.064 & 0.399 & Publication year\\
+0.002 & 0.979 & Open materials\\
+-0.027 & 0.725 & Stanford affiliation of original authors at time of replication\\
+-0.047 & 0.536 & Log ratio between replication and original sample sizes\\
+-0.108 & 0.155 & Log original sample size\\
+-0.158 & 0.037 & Switch to online for replication (versus same modality for original and replication)\\
+-0.246 & 0.001 & Social psychology (versus cognitive psych)\\
+-0.267 & 0.000 & Single vignette (versus multiple items/inductions per condition)\\
+\bottomrule
+\end{tabular}
+\end{table}
+
 \hypertarget{bivariate-correlates-of-replication-success}{%
@@
 While online studies in general show comparable results to studies conducted in person (\protect\hyperlink{ref-crump2013}{31}), switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well-adapted (e.g., inductions might have been weaker or instructions might have been insufficient).
-These factors -- open materials, open data, and online samples -- are more common in more recent studies, and so these effects may partially reflect temporal trends (see Figure \ref{fig:corr-plot} for the correlations between these factors and publication year).
+These factors -- open materials, open data, and online samples -- may have all contributed to the closeness of the replications.
+However, they are also practices that have increased over time, and so these effects may partially reflect temporal trends.
+Nonetheless, publication year only very weakly correlated with replicability, but does correlate strongly with online samples and openness (Figure \ref{fig:corr-plot}).
 
@@
 
-Students were free to choose what study to replicate; the recommended path for students who did not have their own ideas was to pick an interesting study from a recent year of Psychological Science (this led to a high fraction of Psych Science articles in the replication sample, 80, 45\% of studies).
+Students were free to choose what study to replicate; the recommended path for students who did not have their own ideas was to pick an interesting study from a recent year of Psychological Science (this led to 80 Psych Science articles in the replication sample, 45\% of all studies).
 

### 2023-10-12 paper/supplement.Rmd
work on edits; redo tieu

@@
 ```
+
+# Sub sample of Psych Science papers
+
+```{r}
+all <- read_csv(here("data", "raw_data.csv")) |> filter(include %in% c("stats", "pred_int", "exp"))
+
+ps <- all|> mutate(journal=str_to_lower(journal)) |>filter(journal=="psych sci")
+
+```
+
+We were unable to use journal as a predictor in the models because of very uneven representation across journals.
+By far the most represented journal was Psychological Science, with `r nrow(ps)` original papers.
+Other journals had at most a few papers in the sample.
+
+Here we present bivariate analyses on the subset of the data coming from Psych Science. This is a post-hoc split of the data.
+
+Overall, this split looks similar to the overall sample. Of note, publication year is correlated with replication success in this sample, but is not substantially correlated overall.
+
+```{r}
+library(gtsummary)
+theme_gtsummary_language("en", big.mark = "")
+library(kableExtra)
+
+all_label <- all %>% select(target_lastauthor_year,journal)
+
+desc <- d %>% left_join(all_label) %>% 
+  mutate(journal=str_to_lower(journal)) |>
+  filter(journal=="psych sci") %>% 
+  mutate(target_d_calc=ifelse(include=="stats", target_d_calc, NA),
+             target_p_calc=ifelse(include=="stats",target_p_calc, NA),
+      switch_modality=ifelse(target_on_turk!=replication_on_turk,1,0),
+         ss_ratio=replication_N/target_N)%>% 
+  select("subfield","open_data", "open_materials","switch_modality",  "stanford_internal","within_between","single_vignette","repeated_measure","target_year","target_N","replication_N", "ss_ratio", "target_d_calc", "target_p_calc") %>%
+  mutate(subfield=factor(subfield, levels=c("cognitive", "social", "other-psych", "non-psych"), labels=c("Cognitive", "Social", "Other psych", "Non-psych")),
+         within_between=ifelse(within_between=="between", 0, 1)) %>% 
+             tbl_summary(
+               label=list(
+                 subfield ~ "Subfield",
+                 stanford_internal ~ "Original authors at Stanford",
+                 target_year~ "Publication Year",
+                 single_vignette ~ "Single vignette",
+                 open_data ~ "Open data",
+                 open_materials ~ "Open materials",
+                 within_between ~ "Within subjects design",
+                 repeated_measure ~ "Number of trials",
+                 target_N ~ "Original sample size",
+                 replication_N ~ "Replication sample size",
+                 ss_ratio ~ "Ratio of replication/original sample sizes",
+                 target_d_calc ~"Original effect size (SMD)",
+                 target_p_calc ~ "Original p-value",
+                 switch_modality ~ "Switch from in-person to online"
+               ),
+               statistic = list(all_continuous() ~ "{mean} ({sd})", all_continuous() ~ "{median} ({p25}, {p75})"),
+               digits=list(target_year ~ 0, target_p_calc ~4),
+    missing="no",
+             ) %>% 
+modify_header(label="Feature", stat_0="Summary") %>% 
+    modify_footnote(update = everything() ~ NA)
+
+as_kable_extra(desc,format="latex", position="!h", caption="Descriptive properties of the Psych Science portion of the replication dataset.
+For categorical features, counts and percentages are given.
+For continuous features, the median value and interquartile range are given.
+", booktabs=TRUE, linesep="") |> kable_styling(full_width=F, font_size=10)
+
+```
+
+```{r cor}
+
+for_cor <- read_csv(here("data","for_model.csv")) |> filter(include %in% c("stats", "exp", "pred_int")) |>
+  left_join(all_label) %>% 
+  mutate(journal=str_to_lower(journal)) |>
+  filter(journal=="psych sci") %>% 
+  select(sub_rep, 
+         pub_year, subfield, open_data, open_mat, stanford, change_platform, log_ratio_ss, is_within, single_vignette, log_sample, log_trials) |> mutate(social=ifelse(subfield=="social", 1,0),other_psych=ifelse(subfield=="other-psych",1,0), non_psych=ifelse(subfield=="non-psych", 1,0))
+
+sub_cor <- function(var, stat = "estimate") {
+  if (stat == "estimate") {
+    cor.test(for_cor$sub_rep, pull(for_cor, {{var}}))$estimate
+  } else {
+    cor.test(for_cor$sub_rep, pull(for_cor, {{var}}))$p.value
+  }
+}
+
+preds <- c("pub_year", "open_data",  "open_mat", "stanford", "change_platform", 
+           "log_ratio_ss", "is_within", "single_vignette", "log_sample", 
+           "log_trials", "social", "other_psych", "non_psych")
+
+cors <- tibble(preds = preds) |>
+  mutate(r = sapply(preds, function(x) sub_cor(x, stat = "estimate")),
+         p = sapply(preds, function(x) sub_cor(x, stat = "p"))) |> 
+  mutate(Predictors=factor(preds, levels=c("social", "other_psych", "non_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "pub_year", "log_trials", "log_sample", "log_ratio_ss"), labels=c("Social psychology (versus cognitive psych)", "Other psychology (versus cognitive psych)", "Non psychology (versus cognitive psych)", "Within participants design (versus between participants)", "Single vignette (versus multiple items/inductions per condition)", "Switch to online for replication (versus same modality for original and replication)", "Open data", "Open materials", "Stanford affiliation of original authors at time of replication", "Publication year", "Log number of  trials", "Log original sample size", "Log ratio between replication and original sample sizes"))) |> arrange(desc(r)) |> select(r, p, Predictors)
+
+library(kableExtra)
+knitr::kable(cors, digits = 3, align='ccl',format="latex", position="!h", caption="The unadjusted Pearson correlations between each individual predictor and the subjective replication score for the Psych Science subsample.", booktabs=TRUE, linesep="") |> kable_styling(full_width=F, font_size=10)
+
+```

### 2023-10-16 code/process.Rmd
found p-value error in parse stats
if tval or whatever was negative, pval was in wrong range since it
takes the upper portion and then x2
now fixed with abs()
rerun models; add closeness and pre-reg stuff to ms

--- 2023-06-30 code/process.Rmd
@@
 
-raw <- readxl::read_xlsx(here("data","raw_data.xlsx"), 
-                       sheet="aligned data", skip=1) |> select(target_lastauthor_year, sensitivity, include,
+raw <- readxl::read_xlsx(here("data","raw_data.xlsx"), sheet="aligned data", skip=1) |> 
+  mutate(student_name_shared=ifelse(is.na(student_name_shared), "N/A", student_name_shared),
+         replication_report_included=ifelse(is.na(replication_report_included), "no", replication_report_included)) |> 
+  select(target_lastauthor_year, student_name_shared, replication_report_included, how_close, sensitivity, include,
          status, status_explanation,  academic_year, journal, target_cite, article_link, study_number,  subfield, target_year, stanford_internal, 
@@
 d <- read_csv(here("data", "raw_data.csv")) |> 
-  select(target_lastauthor_year, sensitivity, include,
+  select(target_lastauthor_year, sensitivity, include, how_close,
          status, academic_year, subfield, target_year, stanford_internal, 
@@
 
+# Closeness
+
+```{r}
+ d |> filter(include %in% c("exp","pred_int", "stats")) |> group_by(how_close) |> tally()
+
+```
 # Parsing
@@
   rowwise()
+```
+
+```{r}
+#found error in pval calculation related to sign flips
+
+test %>% ungroup() %>% summarize(target=quantile(target_p_calc, na.rm=T), rep=quantile(rep_p_calc, na.rm=T))
 ```

### 2023-10-16 paper/coverletter/rsos_response.tex
rerun models; add closeness and pre-reg stuff to ms

@@
 \documentclass{stanfordletter}
-%\makelabels
+\makelabels
 \usepackage{todonotes}
@@
 \usepackage{xr}
-%\externaldocument[paper-]{../revision}
+\externaldocument[paper-]{../revision}
 \usepackage[american]{babel}
@@
 \usepackage[backend=biber,style=apa,doi=false,url=false,hyperref=true,apamaxprtauth=30,uniquename=false]{biblatex}
+\usepackage{framed}
 \DeclareLanguageMapping{american}{american-apa}
@@
 
-%\makelabels
+\makelabels
 \newcommand{\theysaid}[1]{\begin{leftbar} \noindent 
@@
 
+\usepackage{longtable,booktabs,array}
+\usepackage{float}
 \begin{document}
@@
 
-          \theysaid{Reviewer comments to Author:
+          \theysaid{Reviewer comments to Author:\\
+          Reviewer: 1 \\
+          Comments to the Author(s)}
 
-          Reviewer: 1
-          Comments to the Author(s)
-          I have read this manuscript with great enthusiasm. It provides an important infusion of new data into a field that is very much oversaturated with analyses of what little data there is.
-        }
+          \theysaid{I have read this manuscript with great enthusiasm.
+It provides an important infusion of new data into a field that is very much oversaturated with analyses of what little data there is.}
 
-        \theysaid{
+        \theysaid{I find the report to be clearly written, well-documented, of a sensible length, and appropriately cautious when discussing the generalizability and potential causal implications of the reported results.
+But for a single minor issue, I believe the report could be accepted as is.}
 
-          I find the report to be clearly written, well-documented, of a sensible length, and appropriately cautious when discussing the generalizability and potential causal implications of the reported results.
-But for a single minor issue, I believe the report could be accepted as is.
-
-          The only thing I miss in the current manuscript is some description/discussion of how close/conceptual replications in the sample tended to be.
+          \theysaid{The only thing I miss in the current manuscript is some description/discussion of how close/conceptual replications in the sample tended to be.
 See LeBel et.
@@
 The rationale being that I would generally expect a higher replication rate the closer replication procedures are to the original.
-Having a sense of what mix of close/conceptual replications in this sample is thus relevant for my interpretation of the overall replicability estimate.}
+Having a sense of what mix of close/conceptual replications in this sample is thus relevant for my interpretation of the overall replicability estimate.
+          }
 
@@
           We've added TODO what we add
+
+          can't always tell if close or very close b/c had to guess based on whether materials were open and whether student mentioned having received from authors.
+
+		student reports has a "differences" section -- this combined with platform and open materials and if they mentioned getting materials from authors.
+
+		not quite sure how to code in some cases
 
@@
           This is why we're careful to frame as "how well can grad students redo" -- closeness was dependent on factors like avialable and ease, and varies by study in how much it calls into question the original study results.
+
+          coded based on what is being analyzed -- sometimes there were additional measures in original or this is the behavioral portion of an fmri etc
+
+          assuming that switching from college to crowdsourced is not a difference in sample 
+          and that reducing number of trials (ex. in trade-off with number of participants) doesn't prevent "close
 
@@
 
+          Coauthors: In prior collaborations with students, we have invited students prospectively to be co-authors (Hawkins et al., 2018; Hardwicke et al., 2018).
+In those projects, we gave opportunities to engage with the research design throughout the process as well as approval over the manuscript.
+In this case, our study was based on retrospective coding of a large sample of projects.
+We had no assurance that we could contact all students for input (and had we been able to reach them, they might not have been interested).
+Further, we did not see ways that we could engage them with the research design prospectively to provide meaningful opportunities for contribution.
+Instead, we viewed this study as an archival investigation of course records - a meta-analysis of gray literature.
+(Note that we did attempt to contact all students to alert them to the project and provide them with an opportunity to include their course project in the shared materials).
+
           \theysaid{
@@
 
+          But, for your edification, we did run the descriptive summary and the bivariate correlates on the Psych Science subsample.
+
+          We were unable to use journal as a predictor in the models because of very uneven representation across journals.
+By far the most represented journal was Psychological Science, with 80 original papers.
+Other journals had at most a few papers in the sample.
+
+          Here we present bivariate analyses on the subset of the data coming from Psych Science. This is a post-hoc split of the data.
+
+          Overall, this split looks similar to the overall sample. Of note, publication year is correlated with replication success in this sample, but is not substantially correlated overall.
+
+\begin{center}
+
+          Descriptive properties of the Psych Science portion of the replication dataset.
+For categorical features, counts and percentages are given.
+For continuous features, the median value and interquartile range are given.
+
+          \fontsize{10}{12}\selectfont
+          \begin{tabular}[t]{lc}
+          	\toprule
+          	Feature & Summary\\
+          	\midrule
+          	Subfield & \\
+          	\hspace{1em}Cognitive & 23 (29\%)\\
+          	\hspace{1em}Social & 39 (49\%)\\
+          	\hspace{1em}Other psych & 15 (19\%)\\
+          	\hspace{1em}Non-psych & 3 (3.8\%)\\
+          	Open data & 35 (44\%)\\
+          	Open materials & 50 (63\%)\\
+          	Switch from in-person to online & 33 (41\%)\\
+          	Original authors at Stanford & 6 (7.5\%)\\
+          	Within subjects design & 36 (45\%)\\
+          	Single vignette & 41 (51\%)\\
+          	Number of trials & 4 (1, 59)\\
+          	Publication Year & 2016 (2014, 2017)\\
+          	Original sample size & 97 (48, 155)\\
+          	Replication sample size & 61 (30, 125)\\
+          	Ratio of replication/original sample sizes & 0.79 (0.47, 1.05)\\
+          	Original effect size (SMD) & 0.61 (0.47, 0.99)\\
+          	Original p-value & 0.0003 (0.0000, 0.0070)\\
+          	\bottomrule
+          \end{tabular}
+
+     The unadjusted Pearson correlations between each individual predictor and the subjective replication score for the Psych Science subsample.
+
+          \fontsize{10}{12}\selectfont
+          \begin{tabular}[t]{ccl}
+          	\toprule
+          	r & p & Predictors\\
+          	\midrule
+          	0.397 & 0.000 & Within participants design (versus between participants)\\
+          	0.297 & 0.007 & Publication year\\
+          	0.288 & 0.010 & Open data\\
+          	0.214 & 0.057 & Non psychology (versus cognitive psych)\\
+          	0.171 & 0.130 & Log number of  trials\\
+          	0.167 & 0.139 & Other psychology (versus cognitive psych)\\
+          	0.030 & 0.790 & Open materials\\
+          	-0.052 & 0.644 & Log original sample size\\
+          	-0.114 & 0.315 & Log ratio between replication and original sample sizes\\
+          	-0.163 & 0.149 & Stanford affiliation of original authors at time of replication\\
+          	-0.255 & 0.022 & Switch to online for replication (versus same modality for original and replication)\\
+          	-0.268 & 0.016 & Social psychology (versus cognitive psych)\\
+          	-0.311 & 0.005 & Single vignette (versus multiple items/inductions per condition)\\
+          	\bottomrule
+          \end{tabular}
+          \end{center}
+
+Notably, the Psych Science subsample is pretty similar descriptively to the overall sample.
+The biggest difference in the bi-variate correlations is the Publication Year is correlated with replication success in the Psych Science portion, but not the overall sample (possible due to more limited time frame for Psych Science, and substantial changes in how the journal was run during that time frame).
           	\theysaid{
-          	Minor typos:
-          	section 2.1 "of replications has outcomes with" should be "had"
+          	Minor typos:\\
+          	section 2.1 "of replications has outcomes with" should be "had"\\
           	section 4.3 "ramapped" should be "remapped"

### 2023-10-16 paper/manuscript.Rmd
rerun models; add closeness and pre-reg stuff to ms

@@
 ```{r, include=F}
-matching <- d |> filter(include!="unusable") |> mutate(match=ifelse(replicated_instructor_code==replicated_report_code,1,0)) |> group_by(match) |> tally()
+matching <- d |>  mutate(match=ifelse(replicated_instructor_code==replicated_report_code,1,0)) |> group_by(match) |> tally()
 
-d |> filter(include!="unusable")
 irr <- cor.test(d$replicated_instructor_code, d$replicated_report_code, method="spearman")$estimate
@@
 
+```{r}
+closeness <- d |> group_by(how_close) |> tally() |> mutate(pct=(n/sum(n)*100) |> round())
+
+```
+
 These replications were all conducted on short time scales, within a constrained class budget.
@@
 In nearly all cases, replications were conducted online, with recruitment from Amazon Mechanical Turk (the default from 2011 to 2020) or Prolific (the default from 2021 -- 2022).
+The goal was for replications to be as close as possible to the original, but budgetary constraints, inability to option original materials, and primarily using online samples meant that replications varied in their degree of closeness to the original.
+According to the schema from @lebel2018, `r pluck(closeness,3,2)`% of studies were exact replications, `r pluck(closeness,3,4)`% were very close replications, `r pluck(closeness,3,1)`% were close replications, and `r pluck(closeness,3,3)` were far replications (See Methods for more details on common deviations).
 
@@
                  open_materials ~ "Open materials",
-                 within_between ~ "Within subjects design",
+                 within_between ~ "Within participants design",
                  repeated_measure ~ "Number of trials",
@@
 ```{r corr-plot, out.height="40%", fig.width=8, fig.height=4.5, fig.pos="ht", fig.cap="Correlations between predictors. See TODO Table 1 or Methods for descriptions. "}
-dat <-  for_cor %>% mutate(cognitive=ifelse(subfield=="cognitive",1,0)) %>% select(-sub_rep, -subfield)
+dat <-  for_cor %>% mutate(cognitive=ifelse(subfield=="cognitive",1,0)) %>% select(-sub_rep, -subfield) %>% select( "social", "cognitive", "other_psych", "non_psych","is_within", "single_vignette", "stanford", "change_platform", "open_data", "open_mat", "pub_year", "log_trials", "log_sample", "log_ratio_ss", )
 
 corr_mat <- round(cor(dat),2)
+
+corr_mat[lower.tri(corr_mat)] <- NA
 
@@
                       NA, value)) %>% 
-  mutate(Var1=factor(Var1, levels=c("social", "cognitive", "other_psych", "non_psych", "is_within", "single_vignette", "stanford", "change_platform", "open_data", "open_mat", "pub_year", "log_trials", "log_sample", "log_ratio_ss"), labels=c("Social psych", "Cognitive psych", "Other psych", "Non-psych", "Within participants design", "Single vignette ","Stanford affiliated", "Switch to online", "Open data", "Open materials", "Publication year", "Log # of trials", "Log original sample size", "Log ratio rep/original sample sizes")),
-         Var2=factor(Var2, levels=c("social", "cognitive", "other_psych", "non_psych", "is_within", "single_vignette", "stanford", "change_platform", "open_data", "open_mat", "pub_year", "log_trials", "log_sample", "log_ratio_ss"), labels=c("Social psych", "Cognitive psych", "Other psych", "Non-psych", "Within participants design", "Single vignette ","Stanford affiliated", "Switch to online", "Open data", "Open materials", "Publication year", "Log # of trials", "Log original sample size", "Log ratio rep/original sample sizes")))
+    filter(Var1!="log_ratio_ss") |> 
+  mutate(Var1=factor(Var1, levels=c("social", "cognitive", "other_psych", "non_psych", "is_within", "single_vignette", "stanford", "change_platform", "open_data", "open_mat", "pub_year", "log_trials", "log_sample", "log_ratio_ss"), labels=c("Social psych", "Cognitive psych", "Other psych", "Non-psych", "Within participants design", "Single vignette ","Stanford affiliated", "Switch to online", "Open data", "Open materials", "Publication year", "Log # of trials", "Log original sample size", "Log ratio rep/original sample sizes"))) |>
+           filter(!Var2 %in% c("social", "cognitive","other_psych", "non_psych")) |> 
+         mutate(Var2=factor(Var2, levels=c("social", "cognitive", "other_psych", "non_psych", "is_within", "single_vignette", "stanford", "change_platform", "open_data", "open_mat", "pub_year", "log_trials", "log_sample", "log_ratio_ss"), labels=c("Social psych", "Cognitive psych", "Other psych", "Non-psych", "Within participants design", "Single vignette ","Stanford affiliated", "Switch to online", "Open data", "Open materials", "Publication year", "Log # of trials", "Log original sample size", "Log ratio rep/original sample sizes")))
 
@@
   theme_classic()+
+      scale_y_discrete(limits=rev)+
   scale_fill_gradient2(low="#763386",high="#FDE725FF", na.value="grey")+
@@
 Some of the correlates are most easily interpreted as being about the original study, and others reflect the closeness of the replication to the original.
+
 For instance, while within-participants designs are more likely to replicate than between-participants designs, this predictor could also be related to the types of experiments that tend to be run in each design.
-Given the strong relationship of this factor to replicability, slightly more skepticism and critical reading of between-participants designs may be warranted, but this correlation, by itself, does not mean scientists should prefer within-participants designs.
+Additionally, as @greenwald1976 notes, within-participants designs can lead to practice effects, carry-over of treatments, and critically, sensitization effects, where participants reason about the contrast between conditions and respond differently due to that reasoning.
+Sensitization effects are a threat to internal validity, and could be replicable even in the absence of the effect itself being replicable.
+Given the strong relationship of within-participants designs to replicability, slightly more skepticism and critical reading of between-participants designs may be warranted, but this correlation, by itself, does not mean scientists should prefer within-participants designs.
 
@@
 # Methods
-Our pre-registration, code, and coded data are available at https://osf.io/xwn9m/ [@osfdata]. <!--TODO VIEW ONLY https://osf.io/xwn9m/?view_only=ebb6df1ae97045cfa5154d6119ec20b1-->
+Our pre-registration, code, and coded data are available at https://osf.io/xwn9m/ [@osfdata].
+
+At the onset of this project, all authors had some familiarity with the dataset.
+MCF taught PSYCH 254/251; MM and VB had each been students in the class.
+The coding of the data primarily took place before the pre-registration was finalized; the only way for us to know what variables were actually codeable and what forms of missingness were present in the data was to code it.
+Thus, the pre-registration was a pre-registration of the analyses and a "locking-in" of the coding scheme.
+VB coded both the predictor variables and was one of the coders of outcome variables, but these were coded in separate passes through the data.
+<!--TODO VIEW ONLY https://osf.io/xwn9m/?view_only=ebb6df1ae97045cfa5154d6119ec20b1-->
+
+## Deviations from pre-registration
+The descriptive statistics and bivariate correlations between predictor and outcome variables were not pre-registered.
+
+In the pre-registration, our research questions mentioned publication journal, but due to the distribution of journals, journal was not a predictor in the pre-registered model plan (or the actual models).
+Our pre-registration stated that we could not include students names or reports in the released dataset; we ended up letting students opt-in to associating their names with their projects and having their replication report included.
+Our pre-registration stated that any errors found would be noted; errors are noted in the data spreadsheet of the materials.
 
@@
 
+Replications varied in how close they were to the original; while the goal was to replicate the original as closely as possible, some deviations were sometimes necessary.
+Student reports contained a section listing changes from the original.
+In response to a reviewer, we attempted to code studies using the classification scheme from @lebel2018.
+
+Common reasons for replications being very close instead of exact were a switch from in-person to online and lack of access to the original instructions.
+(It was not always possible to tell if students had access to original wording and presentation style of materials.) Common reason for replications being only close included recreating materials when the original materials were not available and changing materials to fit the audience (ex.
+switching from UK to US English).
+(It was not always possible to determine if students had the original materials; in some cases students mentioned trying to obtain materials but did not indicate if they had succeeded.) Less common reasons for replications being only close included changing the number of trials per participant or reducing training periods.
+
+Far replications were rare, but were primarily due to a couple deviations.
+In some cases an original study had a specific population (ex.
+high schoolers or hiring managers), and the replication was on a convenience population.
+The other main reason was changing the language of materials to English when cultural or linguistic factors were potentially relevant to the construct of interest.
+
+Other common changes (that we did not consider as decreasing the closeness) were switching which convenience population was used (i.e.
+from college students to crowdworkers or from one crowdwork platform to another), changing or reducing demographic surveys (which were used only in exploratory or secondary analyses, if at all), and removing secondary measures that were not part of the analyses being replicated.
 Four of the replication projects were included in RP:P, and 10 were previously reported in @hawkins2018 (which reported 11 student replications from the 2015-2016 class; one of those was excluded from the current sample for being non-experimental).

### 2023-10-16 paper/manuscript.tex
rerun models; add closeness and pre-reg stuff to ms

@@
 In nearly all cases, replications were conducted online, with recruitment from Amazon Mechanical Turk (the default from 2011 to 2020) or Prolific (the default from 2021 -- 2022).
-
-Many different measures can be used to define replication success of an individual statistical result (\protect\hyperlink{ref-simonsohn2015}{27}--\protect\hyperlink{ref-mathur2020}{29}).
+The goal was for replications to be as close as possible to the original, but budgetary constraints, inability to option original materials, and primarily using online samples meant that replications varied in their degree of closeness to the original.
+According to the schema from (\protect\hyperlink{ref-lebel2018}{27}), 19\% of studies were exact replications, 29\% were very close replications, 44\% were close replications, and 8 were far replications (See Methods for more details on common deviations).
+
+Many different measures can be used to define replication success of an individual statistical result (\protect\hyperlink{ref-simonsohn2015}{28}--\protect\hyperlink{ref-mathur2020}{30}).
 However, whether a replication should be considered successful is not always dependent on only one statistical comparison between the two studies.
@@
 As a complement to our primary subjective outcome, we also used two statistical measures of replication on the subset of the data where they were computable for the key statistic of interest (136 cases, see Figure \ref{fig:prisma}).
-We used \emph{p-original}, the \emph{p}-value on the null hypothesis that the original and replication statistics are from the same distribution, and \emph{prediction interval}, a binary measure of whether the replication statistic fell within the prediction interval of the original statistic (\protect\hyperlink{ref-mathur2020}{29}).
+We used \emph{p-original}, the \emph{p}-value on the null hypothesis that the original and replication statistics are from the same distribution, and \emph{prediction interval}, a binary measure of whether the replication statistic fell within the prediction interval of the original statistic (\protect\hyperlink{ref-mathur2020}{30}).
 The prediction interval depends on the level of evidence of the original study; if the effect was marginal, the prediction interval could overlap zero; thus, a replication might fall within the predictive interval, and be consistent with the original outcome, but not provide compelling evidence for the claimed effect.
@@
 Across the 176 studies, the average subjective replication score was 49\%, which we can interpret as an overall subjective replication rate.
-46\% (62/136) of replications had outcomes with point-estimates within the prediction interval of the original outcome.
+45\% (61/136) of replications had outcomes with point-estimates within the prediction interval of the original outcome.
 The median \emph{p}-original value on the original and replication point-estimates coming from the same distribution was 0.03, representing the median probability that a replication study's estimate would be at least as extreme as was actually observed, if in fact the replication and original were statistically consistent.
-The subjective replication scores were moderately correlated with both prediction interval (r=0.37) and \emph{p}-original (r=0.29) values; prediction interval and \emph{p}-original were highly correlated with each other (r=0.73).
+The subjective replication scores were moderately correlated with both prediction interval (r=0.36) and \emph{p}-original (r=0.27) values; prediction interval and \emph{p}-original were highly correlated with each other (r=0.73).
 
@@
 This pattern of results is consistent with the results of RP:P (\protect\hyperlink{ref-openscienceconsortium2015}{3}).
-Specifically, the median original effect size (in SMD units) was 0.61 (interquartile range: 0.46 - 0.98), and the median replication effect size was 0.28 (0.09 - 0.76), for a median difference of 0.3 (0.03 - 0.64).
-Among the pairs with a subjective replication score of 1 (N=38 with standardized effect sizes), the median original effect size was 0.92 (interquartile range: 0.52 - 1.4), and the median replication effect size was 0.89 (0.57 - 1.24), for a median difference of 0.02 (-0.16 - 0.3).
+Specifically, the median original effect size (in SMD units) was 0.61 (interquartile range: 0.46 - 0.98), and the median replication effect size was 0.28 (0.09 - 0.76), for a median difference of 0.31 (0.04 - 0.66).
+Among the pairs with a subjective replication score of 1 (N=38 with standardized effect sizes), the median original effect size was 0.92 (interquartile range: 0.52 - 1.4), and the median replication effect size was 0.89 (0.57 - 1.24), for a median difference of 0.03 (-0.16 - 0.33).
 Thus, for the highest subjectively-rated replications, effect sizes for original and replication were similar in magnitude on average, with some replications having larger effects than their originals.
@@
 
-\caption{\label{tab:unnamed-chunk-4}Descriptive properties of the replication dataset.
+\caption{\label{tab:unnamed-chunk-5}Descriptive properties of the replication dataset.
 For categorical features, counts and percentages are given.
@@
 Original authors at Stanford & 16 (9.1\%)\\
-Within subjects design & 80 (45\%)\\
+Within participants design & 80 (45\%)\\
 Single vignette & 78 (44\%)\\
@@
 
-Some multi-site replication projects have found heterogeneity in effect sizes across replication sites (\protect\hyperlink{ref-klein2018}{7},\protect\hyperlink{ref-ebersole2020}{19},\protect\hyperlink{ref-olsson2020}{30}).
-As a test of sensitivity to heterogeneity, we assumed that the level of heterogeneity in hypothetical multi-site replications of our sampled articles was the same as the average level heterogeneity found by (\protect\hyperlink{ref-olsson2020}{30}) in prior multi-site replications in psychology (\(\tau=.21\) in units of standardized mean difference).
-Under this assumption, 64\% (72/112) of replication effect sizes are distributionally consistent with the original effect size.
+Some multi-site replication projects have found heterogeneity in effect sizes across replication sites (\protect\hyperlink{ref-klein2018}{7},\protect\hyperlink{ref-ebersole2020}{19},\protect\hyperlink{ref-olsson2020}{31}).
+As a test of sensitivity to heterogeneity, we assumed that the level of heterogeneity in hypothetical multi-site replications of our sampled articles was the same as the average level heterogeneity found by (\protect\hyperlink{ref-olsson2020}{31}) in prior multi-site replications in psychology (\(\tau=.21\) in units of standardized mean difference).
+Under this assumption, 63\% (71/112) of replication effect sizes are distributionally consistent with the original effect size.
 However, more work on understanding heterogeneity is needed to understand what levels of heterogeneity to expect across different implementations of the same experiment, and how considerations of heterogeneity should impact interpretations of both novel results and replication results.
@@
 Replications that switched to online were less likely to replicate than those that had the same modality as the original (generally both online, in a few cases both in-person).
-While online studies in general show comparable results to studies conducted in person (\protect\hyperlink{ref-crump2013}{31}), switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well-adapted (e.g., inductions might have been weaker or instructions might have been insufficient).
+While online studies in general show comparable results to studies conducted in person (\protect\hyperlink{ref-crump2013}{32}), switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well-adapted (e.g., inductions might have been weaker or instructions might have been insufficient).
 These factors -- open materials, open data, and online samples -- may have all contributed to the closeness of the replications.
@@
 While a number of features show individual correlations with the subjective replication score, many correlate with one another.
-To determine which predictors were the strongest, we modeled subjective replication score as an ordinal outcome using ordinal Bayesian regression models with a logit link function, regularized using a horseshoe shrinkage prior (\protect\hyperlink{ref-carvalho09}{32}).
+To determine which predictors were the strongest, we modeled subjective replication score as an ordinal outcome using ordinal Bayesian regression models with a logit link function, regularized using a horseshoe shrinkage prior (\protect\hyperlink{ref-carvalho09}{33}).
 This model estimates odds ratios representing the association of the predictor with having a higher versus lower subjective replication score.
@@
 
-Within-participants designs stand out as the strongest correlate of replicability in the model with all the data (OR = 2.56, 95\% CrI = {[}1, 7.36{]}).
-In the model with all predictors, but less data, within-participants designs remain strong (OR = 2.84, 95\% CrI = {[}0.95, 10.9{]}), and standardized effect size is also substantially related to subjective replication score (OR = 3.32, 95\% CrI = {[}1.04, 11.99{]}).
-Both effects are robust to a sensitivity analysis including only studies with close replications and matching statistical tests (within-participants OR = 3.7, 95\% CrI = {[}0.98, 21.2{]}; effect size OR = 7.34, 95\% CrI = {[}1.25, 48.65{]}).
+Within-participants designs stand out as the strongest correlate of replicability in the model with all the data (OR = 2.59, 95\% CrI = {[}1, 7.3{]}).
+In the model with all predictors, but less data, within-participants designs remain strong (OR = 2.89, 95\% CrI = {[}0.96, 11.24{]}), and standardized effect size is also substantially related to subjective replication score (OR = 3.33, 95\% CrI = {[}1.11, 12.44{]}).
+Both effects are robust to a sensitivity analysis including only studies with close replications and matching statistical tests (within-participants OR = 3.58, 95\% CrI = {[}0.91, 19.57{]}; effect size OR = 7.22, 95\% CrI = {[}1.24, 47{]}).
 
@@
 While the credible intervals were wide, the general patterns of predictor direction and relative strength were similar to the subjective replication models (see Supplement for results from all models).
-The strongest predictors for prediction interval were still within-participants designs (OR = 1.89, 95\% CrI = {[}0.84, 8.98{]}) and studies with larger effect sizes (OR = 1.2, 95\% CrI = {[}0.75, 2.81{]}).
+The strongest predictors for prediction interval were still within-participants designs (OR = 1.78, 95\% CrI = {[}0.86, 8.3{]}) and studies with larger effect sizes (OR = 0.98, 95\% CrI = {[}0.56, 1.63{]}).
 
@@
 Some of the correlates are most easily interpreted as being about the original study, and others reflect the closeness of the replication to the original.
+
 For instance, while within-participants designs are more likely to replicate than between-participants designs, this predictor could also be related to the types of experiments that tend to be run in each design.
-Given the strong relationship of this factor to replicability, slightly more skepticism and critical reading of between-participants designs may be warranted, but this correlation, by itself, does not mean scientists should prefer within-participants designs.
+Additionally, as (\protect\hyperlink{ref-greenwald1976}{25}) notes, within-participants designs can lead to practice effects, carry-over of treatments, and critically, sensitization effects, where participants reason about the contrast between conditions and respond differently due to that reasoning.
+Sensitization effects are a threat to internal validity, and could be replicable even in the absence of the effect itself being replicable.
+Given the strong relationship of within-participants designs to replicability, slightly more skepticism and critical reading of between-participants designs may be warranted, but this correlation, by itself, does not mean scientists should prefer within-participants designs.
 
@@
 The batch of replications presented here were pedagogical replications, done as part of a class.
-Trainees must learn experimental methods, and conducting replications as part of methods classes serves several purposes: it enables students to learn to do experiments in a supportive context, it often leads to more useful results than if students designed their own experiments from scratch, and it creates a resource for studying the literature (\protect\hyperlink{ref-quintana2021}{33}--\protect\hyperlink{ref-hawkins2018}{36}).
+Trainees must learn experimental methods, and conducting replications as part of methods classes serves several purposes: it enables students to learn to do experiments in a supportive context, it often leads to more useful results than if students designed their own experiments from scratch, and it creates a resource for studying the literature (\protect\hyperlink{ref-quintana2021}{34}--\protect\hyperlink{ref-hawkins2018}{37}).
 We believe that this kind of pedagogy has an important role to play in improving methodological practices in psychology more broadly.
@@
 
-Our pre-registration, code, and coded data are available at \url{https://osf.io/xwn9m/} (\protect\hyperlink{ref-osfdata}{37}).
+Our pre-registration, code, and coded data are available at \url{https://osf.io/xwn9m/} (\protect\hyperlink{ref-osfdata}{38}).
+
+At the onset of this project, all authors had some familiarity with the dataset.
+MCF taught PSYCH 254/251; MM and VB had each been students in the class.
+The coding of the data primarily took place before the pre-registration was finalized; the only way for us to know what variables were actually codeable and what forms of missingness were present in the data was to code it.
+Thus, the pre-registration was a pre-registration of the analyses and a ``locking-in'' of the coding scheme.
+VB coded both the predictor variables and was one of the coders of outcome variables, but these were coded in separate passes through the data.
+
+\hypertarget{deviations-from-pre-registration}{%
+\subsection{Deviations from pre-registration}\label{deviations-from-pre-registration}}
+
+The descriptive statistics and bivariate correlations between predictor and outcome variables were not pre-registered.
+
+In the pre-registration, our research questions mentioned publication journal, but due to the distribution of journals, journal was not a predictor in the pre-registered model plan (or the actual models).
+Our pre-registration stated that we could not include students names or reports in the released dataset; we ended up letting students opt-in to associating their names with their projects and having their replication report included.
+Our pre-registration stated that any errors found would be noted; errors are noted in the data spreadsheet of the materials.
 
@@
 Students were encouraged to do experimental replications, but some students chose to replicate correlational outcomes or do computational reproducibility projects instead.
-We cannot include the full student reports for confidentiality reasons, but we include over 50 reports that we received permission to share and the template given to students at \url{https://osf.io/xwn9m/} (\protect\hyperlink{ref-osfdata}{37}).
+We cannot include the full student reports for confidentiality reasons, but we include over 50 reports that we received permission to share and the template given to students at \url{https://osf.io/xwn9m/} (\protect\hyperlink{ref-osfdata}{38}).
 
@@
 
-Four of the replication projects were included in RP:P, and 10 were previously reported in (\protect\hyperlink{ref-hawkins2018}{36}) (which reported 11 student replications from the 2015-2016 class; one of those was excluded from the current sample for being non-experimental).
+Replications varied in how close they were to the original; while the goal was to replicate the original as closely as possible, some deviations were sometimes necessary.
+Student reports contained a section listing changes from the original.
+In response to a reviewer, we attempted to code studies using the classification scheme from (\protect\hyperlink{ref-lebel2018}{27}).
+
+Common reasons for replications being very close instead of exact were a switch from in-person to online and lack of access to the original instructions.
+(It was not always possible to tell if students had access to original wording and presentation style of materials.) Common reason for replications being only close included recreating materials when the original materials were not available and changing materials to fit the audience (ex.
+switching from UK to US English).
+(It was not always possible to determine if students had the original materials; in some cases students mentioned trying to obtain materials but did not indicate if they had succeeded.) Less common reasons for replications being only close included changing the number of trials per participant or reducing training periods.
+
+Far replications were rare, but were primarily due to a couple deviations.
+In some cases an original study had a specific population (ex.
+high schoolers or hiring managers), and the replication was on a convenience population.
+The other main reason was changing the language of materials to English when cultural or linguistic factors were potentially relevant to the construct of interest.
+
+Other common changes (that we did not consider as decreasing the closeness) were switching which convenience population was used (i.e.~from college students to crowdworkers or from one crowdwork platform to another), changing or reducing demographic surveys (which were used only in exploratory or secondary analyses, if at all), and removing secondary measures that were not part of the analyses being replicated.
+Four of the replication projects were included in RP:P, and 10 were previously reported in (\protect\hyperlink{ref-hawkins2018}{37}) (which reported 11 student replications from the 2015-2016 class; one of those was excluded from the current sample for being non-experimental).
 
@@
 This subjective replication outcome was chosen because it already existed, could be applied to all projects (regardless of type and detail of statistical reporting), and did not rely solely on one statistical measure.
-As a complement, we also identified a ``key'' statistical test for each paper (see below for details), and if possible, computed \(p\)-original and prediction interval at this statistic, following (\protect\hyperlink{ref-mathur2020}{29}).
+As a complement, we also identified a ``key'' statistical test for each paper (see below for details), and if possible, computed \(p\)-original and prediction interval at this statistic, following (\protect\hyperlink{ref-mathur2020}{30}).
 \(p\)-original was a continuous measure of the \(p\) value on the hypothesis that the original and replication samples come from the same distribution.
@@
 
-We used a horseshoe shrinkage prior on the fixed effect coefficients because we had a lot of predictors compared to the amount of data (\protect\hyperlink{ref-carvalho09}{32}).
+We used a horseshoe shrinkage prior on the fixed effect coefficients because we had a lot of predictors compared to the amount of data (\protect\hyperlink{ref-carvalho09}{33}).
 All models included random slopes for predictors nested within year the class occurred to control for variation between cohorts of students.
@@
 The priors we used were horseshoe(3) for betas, normal(0,.5) for standard deviation of random slopes, and lkj(1) for correlations between random slopes.
-Models were run in BRMS (\protect\hyperlink{ref-brms}{38}).
+Models were run in BRMS (\protect\hyperlink{ref-brms}{39}).
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-lebel2018}{}}%
+\CSLLeftMargin{27. }%
+\CSLRightInline{LeBel EP, McCarthy RJ, Earp BD, Elson M, Vanpaemel W. A {Unified Framework} to {Quantify} the {Credibility} of {Scientific Findings}. }
+
 \leavevmode\vadjust pre{\hypertarget{ref-simonsohn2015}{}}%
-\CSLLeftMargin{27. }%
+\CSLLeftMargin{28. }%
 \CSLRightInline{Simonsohn U.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-gelman2018}{}}%
-\CSLLeftMargin{28. }%
+\CSLLeftMargin{29. }%
 \CSLRightInline{Gelman A.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-mathur2020}{}}%
-\CSLLeftMargin{29. }%
+\CSLLeftMargin{30. }%
 \CSLRightInline{Mathur MB, VanderWeele TJ.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-olsson2020}{}}%
-\CSLLeftMargin{30. }%
+\CSLLeftMargin{31. }%
 \CSLRightInline{Olsson-Collentine A, Assen MA van, Wicherts J. Heterogeneity in direct replications in psychology and its association with effect size. 2020; }
@@
 \leavevmode\vadjust pre{\hypertarget{ref-crump2013}{}}%
-\CSLLeftMargin{31. }%
+\CSLLeftMargin{32. }%
 \CSLRightInline{Crump MJC, McDonnell JV, Gureckis TM.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-carvalho09}{}}%
-\CSLLeftMargin{32. }%
+\CSLLeftMargin{33. }%
 \CSLRightInline{Carvalho CM, Polson NG, Scott JG.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-quintana2021}{}}%
-\CSLLeftMargin{33. }%
+\CSLLeftMargin{34. }%
 \CSLRightInline{Quintana DS.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-wagge2019}{}}%
-\CSLLeftMargin{34. }%
+\CSLLeftMargin{35. }%
 \CSLRightInline{Wagge JR, Brandt MJ, Lazarevic LB, Legate N, Christopherson C, Wiggins B, et al.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-frank2012}{}}%
-\CSLLeftMargin{35. }%
+\CSLLeftMargin{36. }%
 \CSLRightInline{Frank MC, Saxe R.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-hawkins2018}{}}%
-\CSLLeftMargin{36. }%
+\CSLLeftMargin{37. }%
 \CSLRightInline{Hawkins RD, Smith EN, Au C, Arias JM, Catapano R, Hermann E, et al.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-osfdata}{}}%
-\CSLLeftMargin{37. }%
+\CSLLeftMargin{38. }%
 \CSLRightInline{Boyce V. Meta analysis of class replication projects from PSYCH251 {[}Internet{]}. OSF; 2023. Available from: \href{https://osf.io/xwn9m}{osf.io/xwn9m}}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-brms}{}}%
-\CSLLeftMargin{38. }%
+\CSLLeftMargin{39. }%
 \CSLRightInline{Bürkner PC. \href{https://doi.org/10.18637/jss.v080.i01}{{brms}: An {R} package for {Bayesian} multilevel models using {Stan}}. Journal of Statistical Software. 2017;80(1):1--28. }

### 2023-10-16 paper/supplement.Rmd
rerun models; add closeness and pre-reg stuff to ms

@@
  - \usetikzlibrary{positioning,arrows.meta, quotes, shapes}
+ - \usepackage{placeins}
 ---
@@
 Allowing for heterogeneity, with tau=.21, `r all_tau`/`r all_orig` (`r round(all_tau/all_orig*100)`%) of the original estimates are distributionally consistent.
+
+\FloatBarrier
 
@@
 ```
+
+\FloatBarrier
 
@@
 ```{r}
-knitr::kable(predint, col.names=NULL, align='rrlrlrlrl',position="!h", caption="Coefficients and 95\\% CrI from linear models predictiong the p-original value between the original and replicaiton effects.
+knitr::kable(porig, col.names=NULL, align='rrlrlrlrl',position="!h", caption="Coefficients and 95\\% CrI from linear models predictiong the p-original value between the original and replicaiton effects.
 All pairs indicates that all pairs with calculable prediction intervals were used, regardless of whether they had full statistical information; Full stats indicates that only data with full statistical information was used.
@@
 
-# Sub sample of Psych Science papers
+<!-- # Sub sample of Psych Science papers
 

### 2023-10-17 paper/coverletter/rsos_response.tex
work on response letter

@@
           Before we get to responses to reviewers, we should mention for transparency that we found an error in our code for calculating p-values that affected 26 rows of the data.
-This has been fixed and all analyses downstream of the problem have been rerun and the changes propagated to the manuscript, with no substantial changes to results or interpretation.
-(We were missing an absolute value function; which led to taking the wrong tail for p-values where the t-value was negative.)
+(We were missing an absolute value function; which led to taking the wrong tail for p-values where the t-value was negative.) This error has been corrected.
+Additionally, we discovered an error in one of the student reports effecting the replication effect.
+Their code was fixed and rerun on their data.
+All analyses downstream of these problems have been rerun and the changes propagated to the manuscript.
+Many model estimates and credible intervals have changed numerically, but there  were no substantial changes to results or interpretation.
 
@@
 
-          TODO our response!
+          Thanks for bringing this up and pointing us toward the LeBel paper.
+We had considered coding for closeness of replication, but weren't able to come up with something that felt rigorous enough to use as a predictor variable.
 
-          We've added TODO what we add
+          I know it wasn't asked for, but I thought it would be worthwhile to code every paper according to the LeBel taxonomy off of the student reports which had a section on ``Differences from Original Study''.
+There were sources of uncertainty, both from not being sure what exactly counted as a different IV or different population, and from unclarity in student reports (around whether they had succeeded in getting materials from original authors and if it also included exact formatting).
+But this at least gives a good estimate of the distribution, even if individual cases may be debatably classified.
 
-          can't always tell if close or very close b/c had to guess based on whether materials were open and whether student mentioned having received from authors.
+          We've added the following text to the start of the Results where we discuss the sample:
 
-		student reports has a "differences" section -- this combined with platform and open materials and if they mentioned getting materials from authors.
+          \revised{The goal was for replications to be as close as possible to the original, but budgetary constraints, inability to option original materials, and primarily using online samples meant that replications varied in their degree of closeness to the original.
+According to the schema from (LeBel et al.
+2018), 19\% of studies were exact replications, 29\% were very close replications, 44\% were close replications, and 8 were far replications (See Methods for more details on common deviations).}
 
-		not quite sure how to code in some cases
+          And we've added the following additional details to Dataset subsection of the Methods:
 
-          We considered coding for closeness (and started to do so in a preliminary stage) but couldn't come up with a scheme that felt meaningfully uniform.
-We thank the reviewer for the pointer to LeBel!
+          \revised{Replications varied in how close they were to the original; while the goal was to replicate the original as closely as possible, some deviations were sometimes necessary.
+Student reports contained a section listing changes from the original.
+In response to a reviewer, we attempted to code studies using the classification scheme from LeBel et al.
+(2018).
 
-          From memory, I think we have a range from exact replication to very close replication to close replication.
+          	Common reasons for replications being very close instead of exact were a switch from in-person to online and lack of access to the original instructions.
+(It was not always possible to tell if students had access to original wording and presentation style of materials.) Common reason for replications being only close included recreating materials when the original materials were not available and changing materials to fit the audience (ex.
+switching from UK to US English).
+(It was not always possible to determine if students had the original materials; in some cases students mentioned trying to obtain materials but did not indicate if they had succeeded.) Less common reasons for replications being only close included changing the number of trials per participant or reducing training periods.
 
-          For studies that were originally done online and had open materials, may have approached exact replication.
-(Ex.
-the study I did, there was javascript for running the study available and I rehosted it, so the procedure was identical).
+          	Far replications were rare, but were primarily due to a couple deviations.
+In some cases an original study had a specific population (ex.
+high schoolers or hiring managers), and the replication was on a convenience population.
+The other main reason was changing the language of materials to English when cultural or linguistic factors were potentially relevant to the construct of interest.
 
-          Many switched to online and may have had procedural differences as a result (or as a result of instruction text not being available and students recreating from what the manuscript said).
+          	Other common changes (that we did not consider as decreasing the closeness) were switching which convenience population was used (i.e.~from college students to crowdworkers or from one crowdwork platform to another), changing or reducing demographic surveys (which were used only in exploratory or secondary analyses, if at all), and removing secondary measures that were not part of the analyses being replicated.}
 
-          When possible the stimuli were usually the same.
-In a couple cases, populations and stimuli were farther due to language changes.
-In some cases, stimuli weren't available, and so were recreated to match as was possible.
+         We hope these additions will offer readers clarify about how and to what extent replications differed from the original studies.
 
-          Population was different in some cases due to switches from college student to crowdworker; in one case from high school to young adult crowd worker; and in some cases from "hiring manager" to crowdworker.
-
-          This is why we're careful to frame as "how well can grad students redo" -- closeness was dependent on factors like avialable and ease, and varies by study in how much it calls into question the original study results.
-
-          coded based on what is being analyzed -- sometimes there were additional measures in original or this is the behavioral portion of an fmri etc
-
-          assuming that switching from college to crowdsourced is not a difference in sample 
-          and that reducing number of trials (ex. in trade-off with number of participants) doesn't prevent "close
-
-          \theysaid{Reviewer: 2
-          	Comments to the Author(s)
+          \theysaid{Reviewer: 2\\
+          	Comments to the Author(s)\\
           	This is an excellent contribution, and I have only minor suggestions for the authors.
@@
 
-          TODO check deviations
+          Publication year was included in the pre-registered models; it is visible in the Figure with odds ratios and 95\%CrI. It's also in the (non-pre-registered) table of bivariate correlations.
 
-          We did include publication year in the models (and in the not-pre-registered list of correlations).
+          I also don't believe we have any predictors that weren't pre-registered (https://osf.io/8t6hb, on pages 8-9 has the list of model predictors and their transformations).
+However, there may have been discrepancies between what was listed in our Research Questions and Hypotheses (pages 1-2) and what made it into the Model Specification.
+
+         However, I did go back through our pre-registration looking for deviations.
+
+         We have added a Methods subsection called ``Deviations from pre-registration'' that contains the following text.
+
+         \revised{
+         The descriptive statistics and bivariate correlations between predictor and outcome variables were not pre-registered.
+
+         In the pre-registration, our research questions mentioned publication journal, but due to the distribution of journals, journal was not a predictor in the pre-registered model plan (or the actual models).
+Our pre-registration stated that we could not include students names or reports in the released dataset; we ended up letting students opt-in to associating their names with their projects and having their replication report included.
+Our pre-registration stated that any errors found would be noted; errors are noted in the data spreadsheet of the materials.}
 
@@
 
-          In fact, much of the data-coding had been done when the pre-registration was finalized, due to the need to figure out what variables were actually codeable.
+          At the time of pre-registration, much of the data had already been coded.
+(We had to code the data in order to figure out which variables were actually codeable, what data was missing, and what instantiations of predictors were feasible.)  Thus the pre-registration is a constraint on the analysis, but not on the initial data processing.
+
+          At the start of the Methods section we have added the following text to address the authors state of knowledge at the start of the project and at the time of the pre-registration.
+
+          \revised{At the onset of this project, all authors had some familiarity with the dataset.
+MCF taught PSYCH 254/251; MM and VB had each been students in the class.
+The coding of the data primarily took place before the pre-registration was finalized; the only way for us to know what variables were actually codeable and what forms of missingness were present in the data was to code it.
+Thus, the pre-registration was a pre-registration of the analyses and a ``locking-in'' of the coding scheme.
+VB coded both the predictor variables and was one of the coders of outcome variables, but these were coded in separate passes through the data.}
+
+          We hope both of these disclosures can help readers make informed judgments of our results.
 
@@
 
+          We have added all of these.
+
+          Distributions of predictor variables are in a new Table.
+
+          \revised{{Descriptive properties of the replication dataset.
+For categorical features, counts and percentages are given.
+For continuous features, the median value and interquartile range are given.
+N=176 except for original effect size and p-value where N=112.
+See Methods for full description of how these values were coded.
+}
+          	{\centering
+          	\fontsize{10}{12}\selectfont
+          	\begin{tabular}[t]{lc}
+          		\toprule
+          		Feature & Summary\\
+          		\midrule
+          		Subfield & \\
+          		\hspace{1em}Cognitive & 62 (35\%)\\
+          		\hspace{1em}Social & 70 (40\%)\\
+          		\hspace{1em}Other psych & 24 (14\%)\\
+          		\hspace{1em}Non-psych & 20 (11\%)\\
+          		Open data & 52 (30\%)\\
+          		Open materials & 83 (47\%)\\
+          		Switch from in-person to online & 94 (53\%)\\
+          		Original authors at Stanford & 16 (9.1\%)\\
+          		Within participants design & 80 (45\%)\\
+          		Single vignette (1 item/condition) & 78 (44\%)\\
+          		Number of trials & 6 (1, 60)\\
+          		Publication Year & 2015 (2011, 2017)\\
+          		Original sample size & 101 (40, 181)\\
+          		Replication sample size & 59 (31, 125)\\
+          		Ratio of replication/original sample sizes & 0.86 (0.41, 1.05)\\
+          		Original effect size (SMD) & 0.61 (0.46, 0.98)\\
+          		Original p-value & 0.0001 (0.0000, 0.0069)\\
+          		\bottomrule
+          	\end{tabular}}}
+
+          Correlations of predictor variables are in a new Figure.
+
+          \revised{
+          		\includegraphics[width=1\linewidth,height=0.4\textheight]{../manuscript_files/figure-latex/corr-plot-1}
+          		{Correlations between predictor variables. See Methods for descriptions of how each variable was coded. }
+         }
+
+         Lastly, correlations between outcome variables were added to as the following text in the subsection Overall replication rate in Results.
+
+         \revised{The subjective replication scores were moderately correlated with both prediction interval (r=0.36) and \emph{p}-original (r=0.27) values; prediction interval and \emph{p}-original were highly correlated with each other (r=0.73).
+         }
+
+         We hope these all provide readers with appropriate context for interpreting our reported results and understanding this dataset.
+
           \theysaid{
@@
 I was curious to know the magnitude of the difference in effect sizes between the original studies and replication studies, for: 1) all studies, and 2) just the "successful" replications.
+          }
+
+          We have added this. There is now a paragraph in the Overall replication rate subsection of results that reads
+
+          \revised{On average, there was a diminution of effect sizes from original to replication.
+This pattern of results is consistent with the results of RP:P (Open Science Consortium 2015).
+Specifically, the median original effect size (in SMD units) was 0.61 (interquartile range: 0.46 - 0.98), and the median replication effect size was 0.28 (0.09 - 0.76), for a median difference of 0.31 (0.04 - 0.66).
+Among the pairs with a subjective replication score of 1 (N=38 with standardized effect sizes), the median original effect size was 0.92 (interquartile range: 0.52 - 1.4), and the median replication effect size was 0.89 (0.57 - 1.24), for a median difference of 0.03 (-0.16 - 0.33).
+Thus, for the highest subjectively-rated replications, effect sizes for original and replication were similar in magnitude on average, with some replications having larger effects than their originals.
           }
@@
           }
+
+          We have added mention of these caveats to the Discussion section. A paragraph now reads
+
+          \revised{For instance, while within-participants designs are more likely to replicate than between-participants designs, this predictor could also be related to the types of experiments that tend to be run in each design.
+As Greenwald (1976) notes, within-participants designs can lead to practice effects, carry-over of treatments, and critically, sensitization effects, where participants reason about the contrast between conditions and respond differently due to that reasoning.
+Sensitization effects are a threat to internal validity, and could be replicable even in the absence of the effect itself being replicable.
+Given the strong relationship of within-participants designs to replicability, slightly more skepticism and critical reading of between-participants designs may be warranted, but this correlation, by itself, does not mean scientists should prefer within-participants designs.}
+
           \theysaid{
@@
 
-          Coauthors: In prior collaborations with students, we have invited students prospectively to be co-authors (Hawkins et al., 2018; Hardwicke et al., 2018).
+          In prior collaborations with students, we have invited students prospectively to be co-authors (Hawkins et al., 2018; Hardwicke et al., 2018).
 In those projects, we gave opportunities to engage with the research design throughout the process as well as approval over the manuscript.
@@
           }
-          We do have publication year.
-We've added a more clear mention in the text.
-It is correlated with practices that have changed over time, such as open data, open materials, and online samples, which basically means it's correlated with closeness of replication.
 
-          Psych Science makes up TODO \% of the sample, so we couldn't really use it as a predictor, since other journals are much much less represented.
+          Date of original publication was a predictor, but I've added a mention of it in the text instead of just in Figures and Tables.
+
+          The end of the Bivariate correlations of replication success subsection of results now reads
+
+          \revised{These factors -- open materials, open data, and online samples --  may have all contributed to the closeness of the replications.
+However, they are also practices that have increased over time, and so these effects may partially reflect temporal trends.
+Nonetheless, publication year only very weakly correlated with replicability, but does correlate strongly with online samples and openness (Figure 4).}
+
+          For reference, the bivariate correlation between publication year and subjective replication (reported in Table 1) was r=.064 ($p$=.399).
+
+          Psych Science makes up 45\% of the sample, so we felt we couldn't use journal as a predictor, since other journals are much much less represented.
+(I guess we could have done Psych Science versus everything else, but that wouldn't have been interpretable.)
 
           But, for your edification, we did run the descriptive summary and the bivariate correlates on the Psych Science subsample.
-
-          We were unable to use journal as a predictor in the models because of very uneven representation across journals.
-By far the most represented journal was Psychological Science, with 80 original papers.
-Other journals had at most a few papers in the sample.
-
-          Here we present bivariate analyses on the subset of the data coming from Psych Science. This is a post-hoc split of the data.
-
-          Overall, this split looks similar to the overall sample. Of note, publication year is correlated with replication success in this sample, but is not substantially correlated overall.
 
@@
 
-Notably, the Psych Science subsample is pretty similar descriptively to the overall sample.
-The biggest difference in the bi-variate correlations is the Publication Year is correlated with replication success in the Psych Science portion, but not the overall sample (possible due to more limited time frame for Psych Science, and substantial changes in how the journal was run during that time frame).
+Overall, the Psych Science subsample looks similar to the overall sample.
+Of note, publication year is correlated with replication success in the Psych Science portion, but not the overall sample (possible due to more limited time frame for Psych Science, and substantial changes in how the journal was run during that time frame).
+
           	\theysaid{

### 2023-10-17 paper/manuscript.Rmd
work on response letter

@@
 
-```{r}
-library(gtsummary)
-theme_gtsummary_language("en", big.mark = "")
-library(kableExtra)
-
-desc <- d %>% mutate(target_d_calc=ifelse(include=="stats", target_d_calc, NA),
-             target_p_calc=ifelse(include=="stats",target_p_calc, NA),
-      switch_modality=ifelse(target_on_turk!=replication_on_turk,1,0),
-         ss_ratio=replication_N/target_N)%>% 
-  select("subfield","open_data", "open_materials","switch_modality",  "stanford_internal","within_between","single_vignette","repeated_measure","target_year","target_N","replication_N", "ss_ratio", "target_d_calc", "target_p_calc") %>%
-  mutate(subfield=factor(subfield, levels=c("cognitive", "social", "other-psych", "non-psych"), labels=c("Cognitive", "Social", "Other psych", "Non-psych")),
-         within_between=ifelse(within_between=="between", 0, 1)) %>% 
-             tbl_summary(
-               label=list(
-                 subfield ~ "Subfield",
-                 stanford_internal ~ "Original authors at Stanford",
-                 target_year~ "Publication Year",
-                 single_vignette ~ "Single vignette",
-                 open_data ~ "Open data",
-                 open_materials ~ "Open materials",
-                 within_between ~ "Within participants design",
-                 repeated_measure ~ "Number of trials",
-                 target_N ~ "Original sample size",
-                 replication_N ~ "Replication sample size",
-                 ss_ratio ~ "Ratio of replication/original sample sizes",
-                 target_d_calc ~"Original effect size (SMD)",
-                 target_p_calc ~ "Original p-value",
-                 switch_modality ~ "Switch from in-person to online"
-               ),
-               statistic = list(all_continuous() ~ "{mean} ({sd})", all_continuous() ~ "{median} ({p25}, {p75})"),
-               digits=list(target_year ~ 0, target_p_calc ~4),
-    missing="no",
-             ) %>% modify_header(label="Feature", stat_0="Summary") %>% 
-    modify_footnote(update = everything() ~ NA)
-
-as_kable_extra(desc,format="latex", position="!h", caption="Descriptive properties of the replication dataset.
-For categorical features, counts and percentages are given.
-For continuous features, the median value and interquartile range are given.
-N=176 except for original effect size and p-value where N=112.
-", booktabs=TRUE, linesep="") |> kable_styling(full_width=F, font_size=10)
-
-```
-
 ```{r }
@@
 
-```{r}
-
-within <- for_cor |> group_by(is_within) |> summarize(avg=mean(sub_rep))
-
-cog <- for_cor |> group_by(subfield) |> summarize(avg=mean(sub_rep))
-vignette <- for_cor |> group_by(single_vignette) |> summarize(avg=mean(sub_rep))
-
-```
-
 ## Bivariate correlates of replication success
@@
 We investigated what features of the original study and replication were correlated with replication success, with the goal of being able to identify potential markers of replicability.
-We chose a set of predictor variables based on the correlational results of RP:P [@openscienceconsortium2015], our own intuitions of experimental design factors that might impact replication success, and some covariates related to how close the replication was; a full description of these features is given in the Methods.
+We chose a set of predictor variables based on the correlational results of RP:P [@openscienceconsortium2015], our own intuitions of experimental design factors that might impact replication success, and some covariates related to how close the replication was; Table \ref{tab:dist} has descriptive statistics of the distribution of values for these features in the dataset, and a full description of these features is given in the Methods.
+
+```{r dist}
+library(gtsummary)
+theme_gtsummary_language("en", big.mark = "")
+library(kableExtra)
+
+desc <- d %>% mutate(target_d_calc=ifelse(include=="stats", target_d_calc, NA),
+             target_p_calc=ifelse(include=="stats",target_p_calc, NA),
+      switch_modality=ifelse(target_on_turk!=replication_on_turk,1,0),
+         ss_ratio=replication_N/target_N)%>% 
+  select("subfield","open_data", "open_materials","switch_modality",  "stanford_internal","within_between","single_vignette","repeated_measure","target_year","target_N","replication_N", "ss_ratio", "target_d_calc", "target_p_calc") %>%
+  mutate(subfield=factor(subfield, levels=c("cognitive", "social", "other-psych", "non-psych"), labels=c("Cognitive", "Social", "Other psych", "Non-psych")),
+         within_between=ifelse(within_between=="between", 0, 1)) %>% 
+             tbl_summary(
+               label=list(
+                 subfield ~ "Subfield",
+                 stanford_internal ~ "Original authors at Stanford",
+                 target_year~ "Publication Year",
+                 single_vignette ~ "Single vignette (1 item/condition)",
+                 open_data ~ "Open data",
+                 open_materials ~ "Open materials",
+                 within_between ~ "Within participants design",
+                 repeated_measure ~ "Number of trials",
+                 target_N ~ "Original sample size",
+                 replication_N ~ "Replication sample size",
+                 ss_ratio ~ "Ratio of replication/original sample sizes",
+                 target_d_calc ~"Original effect size (SMD)",
+                 target_p_calc ~ "Original p-value",
+                 switch_modality ~ "Switch from in-person to online"
+               ),
+               statistic = list(all_continuous() ~ "{mean} ({sd})", all_continuous() ~ "{median} ({p25}, {p75})"),
+               digits=list(target_year ~ 0, target_p_calc ~4),
+    missing="no",
+             ) %>% modify_header(label="Feature", stat_0="Summary") %>% 
+    modify_footnote(update = everything() ~ NA)
+
+as_kable_extra(desc,format="latex", position="!h", caption="Descriptive properties of the replication dataset.
+For categorical features, counts and percentages are given.
+For continuous features, the median value and interquartile range are given.
+N=176 except for original effect size and p-value where N=112.
+See Methods for full description of how these values were coded.
+", booktabs=TRUE, linesep="") |> kable_styling(full_width=F, font_size=10)
+
+```
 
@@
 Predictors of lower replicability included single-vignette studies (those with only one experimental stimulus per condition), classification as social psychology, and study pairs where the original study was in-person and the replication switched to online.
-
-```{r corr-plot, out.height="40%", fig.width=8, fig.height=4.5, fig.pos="ht", fig.cap="Correlations between predictors. See TODO Table 1 or Methods for descriptions. "}
-dat <-  for_cor %>% mutate(cognitive=ifelse(subfield=="cognitive",1,0)) %>% select(-sub_rep, -subfield) %>% select( "social", "cognitive", "other_psych", "non_psych","is_within", "single_vignette", "stanford", "change_platform", "open_data", "open_mat", "pub_year", "log_trials", "log_sample", "log_ratio_ss", )
-
-corr_mat <- round(cor(dat),2)
-
-corr_mat[lower.tri(corr_mat)] <- NA
-
-# Install and load reshape2 package
-
-# reduce the size of correlation matrix
-melted_corr_mat <-melt(corr_mat) %>% 
-  mutate(value=ifelse(Var1==Var2, NA, value),
-         value=ifelse(Var1 %in% c("cognitive", "non_psych", "other_psych", "social") &
-                        Var2 %in% c("cognitive", "non_psych", "other_psych", "social"),
-                      NA, value)) %>% 
-    filter(Var1!="log_ratio_ss") |> 
-  mutate(Var1=factor(Var1, levels=c("social", "cognitive", "other_psych", "non_psych", "is_within", "single_vignette", "stanford", "change_platform", "open_data", "open_mat", "pub_year", "log_trials", "log_sample", "log_ratio_ss"), labels=c("Social psych", "Cognitive psych", "Other psych", "Non-psych", "Within participants design", "Single vignette ","Stanford affiliated", "Switch to online", "Open data", "Open materials", "Publication year", "Log # of trials", "Log original sample size", "Log ratio rep/original sample sizes"))) |>
-           filter(!Var2 %in% c("social", "cognitive","other_psych", "non_psych")) |> 
-         mutate(Var2=factor(Var2, levels=c("social", "cognitive", "other_psych", "non_psych", "is_within", "single_vignette", "stanford", "change_platform", "open_data", "open_mat", "pub_year", "log_trials", "log_sample", "log_ratio_ss"), labels=c("Social psych", "Cognitive psych", "Other psych", "Non-psych", "Within participants design", "Single vignette ","Stanford affiliated", "Switch to online", "Open data", "Open materials", "Publication year", "Log # of trials", "Log original sample size", "Log ratio rep/original sample sizes")))
-
-# plotting the correlation heatmap
-ggplot(data = melted_corr_mat, aes(x=Var1, y=Var2,
-                                   fill=value)) + #scale_fill_viridis()+
-  theme_classic()+
-      scale_y_discrete(limits=rev)+
-  scale_fill_gradient2(low="#763386",high="#FDE725FF", na.value="grey")+
-  labs(x="", y="")+
-  geom_tile(alpha=.7)+
-  theme(axis.text.x = element_text(angle = 40, vjust = 1, hjust=1), legend.position="none")+
-  geom_text(aes(label=value), size=3)
-
-```
-Distributions of study outcomes across some of these properties are shown in Figure \ref{fig:predictors-graph}.
-Both social and cognitive psychology studies were well represented in the replication sample, and the cognitive psychology studies replicated more often than social psychology studies (mean subjective replication scores: `r pluck(cog,2,1) |> round(2)` versus `r pluck(cog,2,4) |> round(2)`).
-Within and between participants designs were both common, and within-participants designs replicated more often than between-participants designs (mean scores: `r pluck(within,2,2) |> round(2)` versus `r pluck(within,2,1) |> round(2)`).
-Studies with multiple vignettes replicated more often than single vignetted studies (mean scores: `r pluck(vignette,2,1) |> round(2)` versus `r pluck(vignette,2,2) |> round(2)`).
-However, there were strong correlations among these experimental features as well as between these experimental features and specific subfields (Figure \ref{fig:corr-plot}).
-
-Studies with open data, which almost always also had open materials as well, tended to replicate more than studies without open data.
-Nearly all replication studies were conducted online, but original studies were split between using in-person and online recruitment.
-Replications that switched to online were less likely to replicate than those that had the same modality as the original (generally both online, in a few cases both in-person).
-While online studies in general show comparable results to studies conducted in person [@crump2013], switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well-adapted (e.g., inductions might have been weaker or instructions might have been insufficient).
-These factors -- open materials, open data, and online samples -- may have all contributed to the closeness of the replications.
-However, they are also practices that have increased over time, and so these effects may partially reflect temporal trends.
-Nonetheless, publication year only very weakly correlated with replicability, but does correlate strongly with online samples and openness (Figure \ref{fig:corr-plot}).
 
@@
 
+```{r}
+
+within <- for_cor |> group_by(is_within) |> summarize(avg=mean(sub_rep))
+
+cog <- for_cor |> group_by(subfield) |> summarize(avg=mean(sub_rep))
+vignette <- for_cor |> group_by(single_vignette) |> summarize(avg=mean(sub_rep))
+
+```
+Distributions of study outcomes across some of these properties are shown in Figure \ref{fig:predictors-graph}.
+Both social and cognitive psychology studies were well represented in the replication sample, and the cognitive psychology studies replicated more often than social psychology studies (mean subjective replication scores: `r pluck(cog,2,1) |> round(2)` versus `r pluck(cog,2,4) |> round(2)`).
+Within and between participants designs were both common, and within-participants designs replicated more often than between-participants designs (mean scores: `r pluck(within,2,2) |> round(2)` versus `r pluck(within,2,1) |> round(2)`).
+Studies with multiple vignettes replicated more often than single vignetted studies (mean scores: `r pluck(vignette,2,1) |> round(2)` versus `r pluck(vignette,2,2) |> round(2)`).
+However, there were strong correlations among these experimental features as well as between these experimental features and specific subfields (Figure \ref{fig:corr-plot}).
+
+Studies with open data, which almost always also had open materials as well, tended to replicate more than studies without open data.
+Nearly all replication studies were conducted online, but original studies were split between using in-person and online recruitment.
+Replications that switched to online were less likely to replicate than those that had the same modality as the original (generally both online, in a few cases both in-person).
+While online studies in general show comparable results to studies conducted in person [@crump2013], switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well-adapted (e.g., inductions might have been weaker or instructions might have been insufficient).
+These factors -- open materials, open data, and online samples -- may have all contributed to the closeness of the replications.
+However, they are also practices that have increased over time, and so these effects may partially reflect temporal trends.
+Nonetheless, publication year only very weakly correlated with replicability, but does correlate strongly with online samples and openness (Figure \ref{fig:corr-plot}).
+
+```{r corr-plot, out.height="40%", fig.width=8, fig.height=4.5, fig.pos="ht", fig.cap="Correlations between predictor variables. See Methods for descriptions of how each variable was coded. "}
+dat <-  for_cor %>% mutate(cognitive=ifelse(subfield=="cognitive",1,0)) %>% select(-sub_rep, -subfield) %>% select( "social", "cognitive", "other_psych", "non_psych","is_within", "single_vignette", "stanford", "change_platform", "open_data", "open_mat", "pub_year", "log_trials", "log_sample", "log_ratio_ss", )
+
+corr_mat <- round(cor(dat),2)
+
+corr_mat[lower.tri(corr_mat)] <- NA
+
+# Install and load reshape2 package
+
+# reduce the size of correlation matrix
+melted_corr_mat <-melt(corr_mat) %>% 
+  mutate(value=ifelse(Var1==Var2, NA, value),
+         value=ifelse(Var1 %in% c("cognitive", "non_psych", "other_psych", "social") &
+                        Var2 %in% c("cognitive", "non_psych", "other_psych", "social"),
+                      NA, value)) %>% 
+    filter(Var1!="log_ratio_ss") |> 
+  mutate(Var1=factor(Var1, levels=c("social", "cognitive", "other_psych", "non_psych", "is_within", "single_vignette", "stanford", "change_platform", "open_data", "open_mat", "pub_year", "log_trials", "log_sample", "log_ratio_ss"), labels=c("Social psych", "Cognitive psych", "Other psych", "Non-psych", "Within participants design", "Single vignette ","Stanford affiliated", "Switch to online", "Open data", "Open materials", "Publication year", "Log # of trials", "Log original sample size", "Log ratio rep/original sample sizes"))) |>
+           filter(!Var2 %in% c("social", "cognitive","other_psych", "non_psych")) |> 
+         mutate(Var2=factor(Var2, levels=c("social", "cognitive", "other_psych", "non_psych", "is_within", "single_vignette", "stanford", "change_platform", "open_data", "open_mat", "pub_year", "log_trials", "log_sample", "log_ratio_ss"), labels=c("Social psych", "Cognitive psych", "Other psych", "Non-psych", "Within participants design", "Single vignette ","Stanford affiliated", "Switch to online", "Open data", "Open materials", "Publication year", "Log # of trials", "Log original sample size", "Log ratio rep/original sample sizes")))
+
+# plotting the correlation heatmap
+ggplot(data = melted_corr_mat, aes(x=Var1, y=Var2,
+                                   fill=value)) + #scale_fill_viridis()+
+  theme_classic()+
+      scale_y_discrete(limits=rev)+
+  scale_fill_gradient2(low="#763386",high="#FDE725FF", na.value="grey")+
+  labs(x="", y="")+
+  geom_tile(alpha=.7)+
+  theme(axis.text.x = element_text(angle = 40, vjust = 1, hjust=1), legend.position="none")+
+  geom_text(aes(label=value), size=3)
+
+```
 ```{r}

### 2023-10-17 paper/manuscript.tex
work on response letter

@@
 
-\begin{table}[!h]
-
-\caption{\label{tab:unnamed-chunk-5}Descriptive properties of the replication dataset.
-For categorical features, counts and percentages are given.
-For continuous features, the median value and interquartile range are given.
-N=176 except for original effect size and p-value where N=112.
-}
-\centering
-\fontsize{10}{12}\selectfont
-\begin{tabular}[t]{lc}
-\toprule
-Feature & Summary\\
-\midrule
-Subfield & \\
-\hspace{1em}Cognitive & 62 (35\%)\\
-\hspace{1em}Social & 70 (40\%)\\
-\hspace{1em}Other psych & 24 (14\%)\\
-\hspace{1em}Non-psych & 20 (11\%)\\
-Open data & 52 (30\%)\\
-Open materials & 83 (47\%)\\
-Switch from in-person to online & 94 (53\%)\\
-Original authors at Stanford & 16 (9.1\%)\\
-Within participants design & 80 (45\%)\\
-Single vignette & 78 (44\%)\\
-Number of trials & 6 (1, 60)\\
-Publication Year & 2015 (2011, 2017)\\
-Original sample size & 101 (40, 181)\\
-Replication sample size & 59 (31, 125)\\
-Ratio of replication/original sample sizes & 0.86 (0.41, 1.05)\\
-Original effect size (SMD) & 0.61 (0.46, 0.98)\\
-Original p-value & 0.0001 (0.0000, 0.0069)\\
-\bottomrule
-\end{tabular}
-\end{table}
-
 Some multi-site replication projects have found heterogeneity in effect sizes across replication sites (\protect\hyperlink{ref-klein2018}{7},\protect\hyperlink{ref-ebersole2020}{19},\protect\hyperlink{ref-olsson2020}{31}).
@@
 We investigated what features of the original study and replication were correlated with replication success, with the goal of being able to identify potential markers of replicability.
-We chose a set of predictor variables based on the correlational results of RP:P (\protect\hyperlink{ref-openscienceconsortium2015}{3}), our own intuitions of experimental design factors that might impact replication success, and some covariates related to how close the replication was; a full description of these features is given in the Methods.
+We chose a set of predictor variables based on the correlational results of RP:P (\protect\hyperlink{ref-openscienceconsortium2015}{3}), our own intuitions of experimental design factors that might impact replication success, and some covariates related to how close the replication was; Table \ref{tab:dist} has descriptive statistics of the distribution of values for these features in the dataset, and a full description of these features is given in the Methods.
+
+\begin{table}[!h]
+
+\caption{\label{tab:dist}Descriptive properties of the replication dataset.
+For categorical features, counts and percentages are given.
+For continuous features, the median value and interquartile range are given.
+N=176 except for original effect size and p-value where N=112.
+See Methods for full description of how these values were coded.
+}
+\centering
+\fontsize{10}{12}\selectfont
+\begin{tabular}[t]{lc}
+\toprule
+Feature & Summary\\
+\midrule
+Subfield & \\
+\hspace{1em}Cognitive & 62 (35\%)\\
+\hspace{1em}Social & 70 (40\%)\\
+\hspace{1em}Other psych & 24 (14\%)\\
+\hspace{1em}Non-psych & 20 (11\%)\\
+Open data & 52 (30\%)\\
+Open materials & 83 (47\%)\\
+Switch from in-person to online & 94 (53\%)\\
+Original authors at Stanford & 16 (9.1\%)\\
+Within participants design & 80 (45\%)\\
+Single vignette (1 item/condition) & 78 (44\%)\\
+Number of trials & 6 (1, 60)\\
+Publication Year & 2015 (2011, 2017)\\
+Original sample size & 101 (40, 181)\\
+Replication sample size & 59 (31, 125)\\
+Ratio of replication/original sample sizes & 0.86 (0.41, 1.05)\\
+Original effect size (SMD) & 0.61 (0.46, 0.98)\\
+Original p-value & 0.0001 (0.0000, 0.0069)\\
+\bottomrule
+\end{tabular}
+\end{table}
 
@@
 \begin{figure}[ht]
-\includegraphics[width=1\linewidth,height=0.4\textheight]{manuscript_files/figure-latex/corr-plot-1} \caption{Correlations between predictors.
-See TODO Table 1 or Methods for descriptions.
-}\label{fig:corr-plot}
+\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/predictors-graph-1} \caption{Distribution of subjective replication scores within categories.
+Bar heights are counts of studies.}\label{fig:predictors-graph}
 \end{figure}
@@
 \begin{figure}[ht]
-\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/predictors-graph-1} \caption{Distribution of subjective replication scores within categories.
-Bar heights are counts of studies.}\label{fig:predictors-graph}
+\includegraphics[width=1\linewidth,height=0.4\textheight]{manuscript_files/figure-latex/corr-plot-1} \caption{Correlations between predictor variables.
+See Methods for descriptions of how each variable was coded.
+}\label{fig:corr-plot}
 \end{figure}
@@
 Collabra: Psychology {[}Internet{]}.
-2022 Apr 29 {[}cited 2023 Feb 10{]};8(1):35271.
+2022 Apr 29;8(1):35271.
 Available from: \url{https://doi.org/10.1525/collabra.35271}}
@@
 Perspect Psychol Sci {[}Internet{]}.
-2016 Jul 1 {[}cited 2023 Apr 27{]};11(4):546--73.
+2016 Jul 1;11(4):546--73.
 Available from: \url{https://doi.org/10.1177/1745691616652873}}
@@
 Science {[}Internet{]}.
-2015 {[}cited 2023 Mar 17{]}; Available from: \url{https://www.science.org/doi/full/10.1126/science.aac4716?casa_token=IJ35TwwlcjsAAAAA\%3AqiP68QbVAHleIg9zD3WugKWuV6Oa5rswS0VQnDsCq5I14ME4WIQabNGVD_T6SBSuAt6voVHNnWc0sw}}
+2015; Available from: \href{https://doi.org/10.1126/science.aac4716}{doi.org/10.1126/science.aac4716}}
 
@@
 False-positive psychology: Undisclosed flexibility in data collection and analysis allows presenting anything as significant.
-Psychological science.
+Psychological science {[}Internet{]}.
 2011;22(11):1359--66.
-}
+Available from: \url{https://doi.org/10.1177/0956797611417632}}
 
@@
 Social Psychology {[}Internet{]}.
-2014 May 1 {[}cited 2023 Feb 10{]};45(3):142--52.
-Available from: \url{https://econtent.hogrefe.com/doi/10.1027/1864-9335/a000178}}
+2014 May 1;45(3):142--52.
+Available from: \url{https://doi.org/10.1027/1864-9335/a000178}}
 
@@
 Adv Methods Pract Psychol Sci {[}Internet{]}.
-2018 Dec 1 {[}cited 2023 Feb 10{]};1(4):443--90.
+2018 Dec 1;1(4):443--90.
 Available from: \url{https://doi.org/10.1177/2515245918810225}}
@@
 Journal of Experimental Social Psychology {[}Internet{]}.
-2016 Nov 1 {[}cited 2023 Feb 10{]};67:68--82.
-Available from: \url{https://www.sciencedirect.com/science/article/pii/S0022103115300123}}
+2016 Nov 1;67:68--82.
+Available from: \url{https://doi.org/10.1016/j.jesp.2015.10.012}}
 
@@
 Nat Hum Behav {[}Internet{]}.
-2018 Aug 27 {[}cited 2023 Feb 11{]};2(9):637--44.
-Available from: \url{https://www.nature.com/articles/s41562-018-0399-z}}
+2018 Aug 27;2(9):637--44.
+Available from: \url{https://doi.org/10.1038/s41562-018-0399-z}}
 
@@
 Proc Natl Acad Sci {[}Internet{]}.
-2016 Jun 7 {[}cited 2023 Apr 5{]};113(23):6454--9.
-Available from: \url{https://www.pnas.org/doi/full/10.1073/pnas.1521897113}}
+2016 Jun 7;113(23):6454--9.
+Available from: \url{https://doi.org/10.1073/pnas.1521897113}}
 
@@
 Laypeople {Can Predict Which Social Science Studies Replicate} {[}Internet{]}.
-{PsyArXiv}; 2019 Sep {[}cited 2019 Sep 30{]}.
-Available from: \url{https://osf.io/egw9d}}
+{PsyArXiv}; 2019 Sep.
+Available from: \url{https://doi.org/10.31234/osf.io/egw9d}}
 
@@
 Proc Natl Acad Sci {[}Internet{]}.
-2015 Dec 15 {[}cited 2023 Mar 17{]};112(50):15343--7.
-Available from: \url{https://www.pnas.org/doi/abs/10.1073/pnas.1516179112}}
+2015 Dec 15;112(50):15343--7.
+Available from: \url{https://doi.org/10.1073/pnas.1516179112}}
 
@@
 Journal of Economic Psychology {[}Internet{]}.
-2019 Dec 1 {[}cited 2023 Mar 17{]};75:102117.
-Available from: \url{https://www.sciencedirect.com/science/article/pii/S0167487018303283}}
+2019 Dec 1;75:102117.
+Available from: \url{https://doi.org/10.1016/j.joep.2018.10.009}}
 
@@
 Proc Natl Acad Sci {[}Internet{]}.
-2020 May 19 {[}cited 2023 May 15{]};117(20):10762--8.
-Available from: \url{https://www.pnas.org/doi/10.1073/pnas.1909046117}}
+2020 May 19;117(20):10762--8.
+Available from: \url{https://doi.org/10.1073/pnas.1909046117}}
 
@@
 Proc Natl Acad Sci {[}Internet{]}.
-2023 Feb 7 {[}cited 2023 Jan 31{]};120(6):e2208863120.
-Available from: \url{https://www.pnas.org/doi/10.1073/pnas.2208863120}}
+2023 Feb 7;120(6):e2208863120.
+Available from: \url{https://doi.org/10.1073/pnas.2208863120}}
 
@@
 PLOS ONE {[}Internet{]}.
-2019 Dec 5 {[}cited 2023 Mar 17{]};14(12):e0225826.
-Available from: \url{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0225826}}
+2019 Dec 5;14(12):e0225826.
+Available from: \url{https://doi.org/10.1371/journal.pone.0225826}}
 
@@
 High {Replicability} of {Newly-Discovered Social-behavioral Findings} is {Achievable} {[}Internet{]}.
-{PsyArXiv}; 2020 Sep {[}cited 2023 Apr 5{]}.
-Available from: \url{https://osf.io/n2a9x}}
+{PsyArXiv}; 2020 Sep.
+Available from: \url{https://doi.org/10.31234/osf.io/n2a9x}}
 
@@
 Adv Methods Pract Psychol Sci {[}Internet{]}.
-2020 Sep 1 {[}cited 2023 Feb 10{]};3(3):309--31.
+2020 Sep 1;3(3):309--31.
 Available from: \url{https://doi.org/10.1177/2515245920958687}}
@@
 PLOS ONE {[}Internet{]}.
-2016 Feb 26 {[}cited 2023 Mar 17{]};11(2):e0149794.
-Available from: \url{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0149794}}
+2016 Feb 26;11(2):e0149794.
+Available from: \url{https://doi.org/10.1371/journal.pone.0149794}}
 
@@
 Comment on {``{Estimating} the reproducibility of psychological science.''} Science {[}Internet{]}.
-2016 Mar 4 {[}cited 2023 Mar 17{]};351(6277):1037--7.
-Available from: \url{https://www.science.org/doi/10.1126/science.aad7243}}
+2016 Mar 4;351(6277):1037--7.
+Available from: \url{https://doi.org/10.1126/science.aad7243}}
 
@@
 \CSLRightInline{Patil P, Peng RD, Leek JT.
-\href{https://doi.org/10.1177/1745691616646366}{What {Should Researchers Expect When They Replicate Studies}?
-{A Statistical View} of {Replicability} in {Psychological Science}}.
-Perspect Psychol Sci.
+What {Should Researchers Expect When They Replicate Studies}?
+{A Statistical View} of {Replicability} in {Psychological Science}.
+Perspect Psychol Sci {[}Internet{]}.
 2016 Jul;11(4):539--44.
-}
+Available from: \url{https://doi.org/10.1177/1745691616646366}}
 
@@
 Response to {Comment} on {``{Estimating} the reproducibility of psychological science.''} Science {[}Internet{]}.
-2016 Mar 4 {[}cited 2023 Apr 4{]};351(6277):1037--7.
-Available from: \url{https://www.science.org/doi/10.1126/science.aad9163}}
+2016 Mar 4;351(6277):1037--7.
+Available from: \url{https://doi.org/10.1126/science.aad9163}}
 
@@
 \CSLLeftMargin{25. }%
-\CSLRightInline{Greenwald AG. Within-subjects designs: To use or not to use? Psychological Bulletin. 1976;83(2):314. }
+\CSLRightInline{Greenwald AG. Within-subjects designs: To use or not to use? Psychological Bulletin {[}Internet{]}. 1976;83(2):314. Available from: \url{https://doi.org/10.1037/0033-2909.83.2.314}}
 
@@
 \CSLLeftMargin{27. }%
-\CSLRightInline{LeBel EP, McCarthy RJ, Earp BD, Elson M, Vanpaemel W. A {Unified Framework} to {Quantify} the {Credibility} of {Scientific Findings}. }
+\CSLRightInline{LeBel EP, McCarthy RJ, Earp BD, Elson M, Vanpaemel W.
+A unified framework to quantify the credibility of scientific findings.
+Advances in Methods and Practices in Psychological Science {[}Internet{]}.
+2018;1(3):389--402.
+Available from: \url{https://doi.org/10.1177/2515245918787489}}
 
@@
 Psychol Sci {[}Internet{]}.
-2015 May 1 {[}cited 2023 Apr 4{]};26(5):559--69.
+2015 May 1;26(5):559--69.
 Available from: \url{https://doi.org/10.1177/0956797614567341}}
@@
 \CSLLeftMargin{29. }%
-\CSLRightInline{Gelman A.
-Don't characterize replications as successes or failures.
-Behav Brain Sci {[}Internet{]}.
-2018/ed {[}cited 2023 Apr 4{]};41:e128.
-Available from: \url{https://www.cambridge.org/core/journals/behavioral-and-brain-sciences/article/abs/dont-characterize-replications-as-successes-or-failures/1AB661F1E7A08E9C5870258878DBA0EA}}
+\CSLRightInline{Gelman A. Don't characterize replications as successes or failures. Behav Brain Sci {[}Internet{]}. 2018/ed;41:e128. Available from: \url{https://doi.org/10.1017/S0140525X18000638}}
 
@@
 J R Stat Soc Ser A Stat Soc {[}Internet{]}.
-2020 {[}cited 2023 Apr 4{]};183(3):1145--66.
-Available from: \url{https://onlinelibrary.wiley.com/doi/abs/10.1111/rssa.12572}}
+2020;183(3):1145--66.
+Available from: \url{https://doi.org/10.1111/rssa.12572}}
 
@@
 \CSLLeftMargin{31. }%
-\CSLRightInline{Olsson-Collentine A, Assen MA van, Wicherts J. Heterogeneity in direct replications in psychology and its association with effect size. 2020; }
+\CSLRightInline{Olsson-Collentine A, Assen MA van, Wicherts J.
+Heterogeneity in direct replications in psychology and its association with effect size.
+2020; Available from: \url{https://doi.org/10.1037/bul0000294}}
 
@@
 PLOS ONE {[}Internet{]}.
-2013 Mar 13 {[}cited 2020 Sep 30{]};8(3):e57410.
-Available from: \url{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0057410}}
+2013 Mar 13;8(3):e57410.
+Available from: \url{https://doi.org/10.1371/journal.pone.0057410}}
 
@@
 Nat Hum Behav {[}Internet{]}.
-2021 Sep {[}cited 2023 Apr 4{]};5(9, 9):1117--8.
-Available from: \url{https://www.nature.com/articles/s41562-021-01192-8}}
+2021 Sep;5(9, 9):1117--8.
+Available from: \url{https://doi.org/10.1038/s41562-021-01192-8}}
 
@@
 Front Psychol {[}Internet{]}.
-2019 {[}cited 2023 Apr 4{]};10.
-Available from: \url{https://www.frontiersin.org/articles/10.3389/fpsyg.2019.00247}}
+2019;10.
+Available from: \url{https://doi.org/10.3389/fpsyg.2019.00247}}
 
@@
 \CSLLeftMargin{36. }%
-\CSLRightInline{Frank MC, Saxe R.
-Teaching {Replication}: Perspect Psychol Sci {[}Internet{]}.
-2012 Nov 7 {[}cited 2020 Sep 14{]}; Available from: \url{https://journals.sagepub.com/doi/10.1177/1745691612460686}}
+\CSLRightInline{Frank MC, Saxe R. Teaching {Replication}. Perspect Psychol Sci {[}Internet{]}. 2012 Nov 7; Available from: \url{https://doi.org/10.1177/1745691612460686}}
 
@@
 Improving the replicability of psychological science through pedagogy.
-Advances in Methods and Practices in Psychological Science.
+Advances in Methods and Practices in Psychological Science {[}Internet{]}.
 2018 Mar;1(1):7--18.
-}
+Available from: \url{https://doi.org/10.1177/2515245917740427}}
 
@@
 \CSLLeftMargin{38. }%
-\CSLRightInline{Boyce V. Meta analysis of class replication projects from PSYCH251 {[}Internet{]}. OSF; 2023. Available from: \href{https://osf.io/xwn9m}{osf.io/xwn9m}}
+\CSLRightInline{Boyce V. Meta analysis of class replication projects from PSYCH251 {[}Internet{]}. OSF; 2023. Available from: \href{https://10.17605/OSF.IO/XWN9M}{10.17605/OSF.IO/XWN9M}}
 
@@
 \CSLLeftMargin{39. }%
-\CSLRightInline{Bürkner PC. \href{https://doi.org/10.18637/jss.v080.i01}{{brms}: An {R} package for {Bayesian} multilevel models using {Stan}}. Journal of Statistical Software. 2017;80(1):1--28. }
+\CSLRightInline{Bürkner PC.
+{brms}: An {R} package for {Bayesian} multilevel models using {Stan}.
+Journal of Statistical Software {[}Internet{]}.
+2017;80(1):1--28.
+Available from: \url{https://doi.org/10.18637/jss.v080.i01}}
 

### 2023-10-18 paper/coverletter/rsos_response.tex
ready to resubmit!

@@
 
-          \revised{Replications varied in how close they were to the original; while the goal was to replicate the original as closely as possible, some deviations were sometimes necessary.
+          \revised{
+          	Replications varied in how close they were to the original; while the goal was to replicate the original as closely as possible, some deviations were sometimes necessary.
 Student reports contained a section listing changes from the original.
-In response to a reviewer, we attempted to code studies using the classification scheme from LeBel et al.
-(2018).
+In response to a reviewer, we attempted to code studies using the classification scheme from (LeBel et al 2018).
 
@@
 
-          	Other common changes (that we did not consider as decreasing the closeness) were switching which convenience population was used (i.e.~from college students to crowdworkers or from one crowdwork platform to another), changing or reducing demographic surveys (which were used only in exploratory or secondary analyses, if at all), and removing secondary measures that were not part of the analyses being replicated.}
+          	Other common changes were changing or reducing demographic surveys (which were used only in exploratory or secondary analyses, if at all) and removing secondary measures that were not part of the analyses being replicated.
+We did not consider these as reducing the degree of closeness.
+
+          	}
 
@@
          \revised{The subjective replication scores were moderately correlated with both prediction interval (r=0.36) and \emph{p}-original (r=0.27) values; prediction interval and \emph{p}-original were highly correlated with each other (r=0.73).
+As mentioned above, inconsistency between the subjective replication and numeric outcomes can occur in a few circumstances such as when there is a large precise original effect and a smaller, but clear replication effect; when there is a small, imprecise original effect and a smaller, null, or opposite replication effect; or when the key measure does not represent the overall pattern of the results.
          }
@@
           Psych Science makes up 45\% of the sample, so we felt we couldn't use journal as a predictor, since other journals are much much less represented.
-(I guess we could have done Psych Science versus everything else, but that wouldn't have been interpretable.)
 
-          But, for your edification, we did run the descriptive summary and the bivariate correlates on the Psych Science subsample.
+          But, since you are interested, we did run the descriptive summary and the bivariate correlates on the Psych Science subsample.
 

### 2023-10-18 paper/manuscript.Rmd
ready to resubmit!

@@
 The subjective replication scores were moderately correlated with both prediction interval (r=`r round(sub_pred,2)`) and *p*-original (r=`r round(sub_p, 2)`) values; prediction interval and *p*-original were highly correlated with each other (r=`r round(pred_p,2)`).
+As mentioned above, inconsistency between the subjective replication and numeric outcomes can occur in a few circumstances such as when there is a large precise original effect and a smaller, but clear replication effect; when there is a small, imprecise original effect and a smaller, null, or opposite replication effect; or when the key measure does not represent the overall pattern of the results.
 
@@
 
-Other common changes (that we did not consider as decreasing the closeness) were switching which convenience population was used (i.e.
-from college students to crowdworkers or from one crowdwork platform to another), changing or reducing demographic surveys (which were used only in exploratory or secondary analyses, if at all), and removing secondary measures that were not part of the analyses being replicated.
+Other common changes were changing or reducing demographic surveys (which were used only in exploratory or secondary analyses, if at all) and removing secondary measures that were not part of the analyses being replicated.
+We did not consider these as reducing the degree of closeness.
+
 Four of the replication projects were included in RP:P, and 10 were previously reported in @hawkins2018 (which reported 11 student replications from the 2015-2016 class; one of those was excluded from the current sample for being non-experimental).

### 2023-10-18 paper/manuscript.tex
ready to resubmit!

@@
 The subjective replication scores were moderately correlated with both prediction interval (r=0.36) and \emph{p}-original (r=0.27) values; prediction interval and \emph{p}-original were highly correlated with each other (r=0.73).
+As mentioned above, inconsistency between the subjective replication and numeric outcomes can occur in a few circumstances such as when there is a large precise original effect and a smaller, but clear replication effect; when there is a small, imprecise original effect and a smaller, null, or opposite replication effect; or when the key measure does not represent the overall pattern of the results.
 
@@
 
-Other common changes (that we did not consider as decreasing the closeness) were switching which convenience population was used (i.e.~from college students to crowdworkers or from one crowdwork platform to another), changing or reducing demographic surveys (which were used only in exploratory or secondary analyses, if at all), and removing secondary measures that were not part of the analyses being replicated.
+Other common changes were changing or reducing demographic surveys (which were used only in exploratory or secondary analyses, if at all) and removing secondary measures that were not part of the analyses being replicated.
+We did not consider these as reducing the degree of closeness.
+
 Four of the replication projects were included in RP:P, and 10 were previously reported in (\protect\hyperlink{ref-hawkins2018}{37}) (which reported 11 student replications from the 2015-2016 class; one of those was excluded from the current sample for being non-experimental).
